### 2021-12-17 manuscript.Rmd
adding manuscript file

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r}
library(rcrossref)
# remotes::install_github("ropensci/rcrossref") as of 12/2021 because of error in crul
# be nice to crossref
# file.edit("~/.Renviron")
# add crossref_email= "email@gmail.com"
psa001 <- cr_cn("10.1038/s41562-020-01007-2")

```

```{r}
library(rorcid)
# orcid_auth() run the first time to set up
# copy the bearer number 
# file.edit("~/.Renviron")
# ORCID_TOKEN="numberhere"

orcid_search(given_name = 'erin',
             family_name = 'buchanan')

```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-12-17 manuscript.Rmd
added notes from today's meeting

@@
 
+orcid_person("0000-0002-9689-4189")
+
 ```
+
+May need to manually edit some stuff
+Figure out how to get information
+
+Ideas from meeting:
+- Career length: from first pub, from first degree
+- Over time: are things becoming more varied
+- Maybe we can use scholar if they don't have orcid
+- Which journals are publishing this information
+- Types of big team research (social, cognitive)
+- Employment levels
+- Education levels
+- # Of works: separate to total, other/preprint, journal/book/traditional
+- Limitations of this system
 
@@
 ## Participants
+
+But type here stuff and things
 

### 2022-02-11 get_data.Rmd
testing examples

---
title: "Get Data"
author: "Erin M. Buchanan"
date: "Last Knitted: `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(dplyr)
library(purrr)
```

## Crossref

Things we need to do to update:

  - We need to put together a list of dois to pull from crossref.

Things you need to do once:

  - Install crossref from github because it has an error that hasn't been pushed to cran.
  - Add your creds to the environment file so it knows who you are.

```{r}
library(rcrossref)
# remotes::install_github("ropensci/rcrossref") as of 12/2021 because of error in crul
# be nice to crossref
# file.edit("~/.Renviron")
# add crossref_email= "email@gmail.com"

# example, here we would loop over the dois 
# psa001 <- cr_cn("10.1038/s41562-020-01007-2") bug in crossref geez

osc <- cr_cn("10.1126/science.aac4716")

manylabs1 <- cr_cn("10.1027/1864-9335/a000178")

bibs <- bib2df("papers.bib")
```

## ORCID

Things you need to do one time:

- Use `orcid_auth()` to set you up
- Copy the bearer number and put it in your environment file

```{r}
library(rorcid)
# orcid_auth() run the first time to set up
# copy the bearer number 
# file.edit("~/.Renviron")
# ORCID_TOKEN="numberhere"

orcid_search(given_name = 'erin',
             family_name = 'buchanan')

erin_example <- orcid_person("0000-0002-9689-4189")

erin_df <- rorcid::works("0000-0002-9689-4189") %>%
  as_tibble() %>%
  janitor::clean_names() %>%
  dplyr::mutate(created_date_value = anytime::anydate(created_date_value/1000))

```

May need to manually edit some stuff
Figure out how to get information

Ideas from meeting:
- Career length: from first pub, from first degree
- Over time: are things becoming more varied
- Maybe we can use scholar if they don't have orcid
- Which journals are publishing this information
- Types of big team research (social, cognitive)
- Employment levels
- Education levels
- # Of works: separate to total, other/preprint, journal/book/traditional
- Limitations of this system

### 2022-02-11 get_data.Rmd
updated from hack meeting

@@
 library(purrr)
+library(bib2df)
 ```
@@
 ## Crossref
-
-Things we need to do to update:
-
-  - We need to put together a list of dois to pull from crossref.
 
@@
 
-orcid_search(given_name = 'erin',
+# find the names
+erins_ids <- orcid_search(given_name = 'erin',
                           family_name = 'buchanan')
+# if more than one pull ids 
+nrow(erins_ids)
+for (i in erins_ids$orcid){
+  temp <- works(i)
+  # check if the works includes a specific paper 
+  # return only ones with that paper 
+}
 
-erin_example <- orcid_person("0000-0002-9689-4189")
+# erin_example <- orcid_person("0000-0002-9689-4189")
 
@@
 
+table(erin_df$type)
+
+erin_df$title_title_value <- tolower(erin_df$title_title_value)
+erin_df$title_title_value <- gsub("[[:punct:]]", "", erin_df$title_title_value)
+nrow(erin_df)
+
+# remove real duplicates
+temp <- erin_df[!duplicated(erin_df[ , c("type", "title_title_value") ]), ]
+nrow(temp)
+
+# combine types
+erin_df$our_type <- erin_df$type
+erin_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", erin_df$our_type)
+
+table(erin_df$our_type)
+
+erin_ed <- orcid_educations("0000-0002-9689-4189") %>% 
+  as_tibble() %>%
+  janitor::clean_names()
+
+orcid_employments("0000-0002-9689-4189")
+
 ```
@@
 
-Ideas from meeting:
+Person statistics: 
 - Career length: from first pub, from first degree
-- Over time: are things becoming more varied
-- Maybe we can use scholar if they don't have orcid
-- Which journals are publishing this information
-- Types of big team research (social, cognitive)
+  `publication_date_year_value` anything 
 - Employment levels
 - Education levels
-- # Of works: separate to total, other/preprint, journal/book/traditional
+- # Of works: separate to total, other/preprint/data-set, journal/book/traditional
 - Limitations of this system
+
+Journal statistics: 
+- Which journals are publishing this information
+  - make sure preprints we are using also have real journal merged in 
+- Types of big team research (social, cognitive)
+  - keywords 
+- Over time: are things becoming more varied
+  - are the publications more varied over time

### 2022-02-18 get_data.Rmd
updating the workflow

@@
 library(bib2df)
-```
+library(tidyverse)
 
-## Crossref
-
-Things you need to do once:
-
-  - Install crossref from github because it has an error that hasn't been pushed to cran.
-  - Add your creds to the environment file so it knows who you are.
-
-```{r}
-library(rcrossref)
-# remotes::install_github("ropensci/rcrossref") as of 12/2021 because of error in crul
-# be nice to crossref
-# file.edit("~/.Renviron")
-# add crossref_email= "email@gmail.com"
-
-# example, here we would loop over the dois 
-# psa001 <- cr_cn("10.1038/s41562-020-01007-2") bug in crossref geez
-
-osc <- cr_cn("10.1126/science.aac4716")
-
-manylabs1 <- cr_cn("10.1027/1864-9335/a000178")
-
-bibs <- bib2df("papers.bib")
-```
-
-## ORCID
-
-Things you need to do one time:
-
-- Use `orcid_auth()` to set you up
-- Copy the bearer number and put it in your environment file
-
-```{r}
 library(rorcid)
@@
 
-# find the names
-erins_ids <- orcid_search(given_name = 'erin',
-                          family_name = 'buchanan')
-# if more than one pull ids 
-nrow(erins_ids)
-for (i in erins_ids$orcid){
-  temp <- works(i)
-  # check if the works includes a specific paper 
-  # return only ones with that paper 
+library(scholar)
+```
+
+## Import the BibTeX File
+
+In this section, we are importing the bibtex file that includes all the papers we are going to use.
+
+Notes:
+
+  - We used the preprint manuscript for some papers because they had the entire author list, we will update their references manually for the final dataset. 
+  - We will have to manually add the names for several papers that used consortium authors. 
+  - The pre-reg of this document only examines one paper to ensure code can be run and develop workflow.
+
+```{r}
+bibs <- bib2df("papers.bib")
+```
+
+## ORCID
+
+In this section, we will figure out the ORCIDs for each author if possible.
+
+  - Data is stored in `bibs$AUTHOR` as a list. 
+  - Extract that information and loop over the author list. 
+  - Because authors will repeat, we need to put this in long format with one row per author and all other information saved. 
+  - Next, split author name, so we can look it up with orcid.
+
+```{r}
+# get data into long format
+long_bib <- bibs %>% unnest_longer(col = AUTHOR)
+
+# remove this nonsense
+long_bib$AUTHOR <- gsub("[{}]", "", long_bib$AUTHOR)
+
+# now split the names into last, first middle 
+# first split on the comma only 
+long_bib <- long_bib %>% separate(col = AUTHOR, sep = ",", 
+                                  into = c("last", "first"), 
+                                  extra = "merge")
+
+# remove the first space
+long_bib$first <- gsub("^ ", "", long_bib$first)
+
+# then split on space
+long_bib <- long_bib %>% separate(col = first, sep = " ", 
+                                  into = c("first", "middle"),
+                                  extra = "merge")
+
+# drop editor column so it is a non-nested DF
+long_bib <- long_bib %>% select(-EDITOR)
+write.csv(long_bib, "unedited_bib.csv", row.names = F)
+```
+
+To make the finalized data:
+
+  - Loop over rows and find candidates for ORCIDs.
+  - Export the candidate data.
+  - Export the bibtex data (done above).
+  - A bit of fun manual merging.
+
+```{r}
+# there are going to be a lot of duplicates
+# really only need to check them once if exact match
+# not perfect exclusion because of symbol differences and middles but ok 
+get_id <- long_bib %>% select(last, first, middle, TITLE)
+get_id <- get_id %>% filter(!duplicated(get_id[ , c("last", "first")]))
+
+# clean up titles
+get_id$TITLE <- gsub("[[:punct:]]", "", get_id$TITLE)
+get_id$TITLE <- tolower(get_id$TITLE)
+
+get_id$ORCID <- NA
+
+#for (i in 1:nrow(get_id)){
+for (i in 1:10){ #temporary do a small number
+
+  # find possible candidates 
+  possibles <- orcid_search(family_name = get_id$last[i], 
+                            given_name = get_id$first[i])
+
+  # if nrow = 0 then move on
+
+  # if nrow == 1 then figure out if there's a match
+  if (nrow(possibles) == 1){
+    temp_works <- orcid_works(possibles$orcid) 
+    temp_DF <- do.call(bind_rows, temp_works)
+
+    if (nrow(temp_DF) > 0){
+    temp_DF$title.title.value <- gsub("[[:punct:]]", "", temp_DF$title.title.value) 
+    temp_DF$title.title.value <- tolower(temp_DF$title.title.value) 
+    temp_DF <- temp_DF %>% 
+      filter(temp_DF$title.title.value == get_id$TITLE[i])
+
+    id <- unique(na.omit(temp_DF$`source.assertion-origin-orcid.path`))
+
+    if(length(id) == 1) { get_id$ORCID[i] <- id }
+    if(length(id) > 1) { get_id$ORCID[i] <- list(id) }
+
+    }
   }
 
-# erin_example <- orcid_person("0000-0002-9689-4189")
+  # if nrow > 1 figure it out which matches
+  if (nrow(possibles) > 1){
+    temp_works <- orcid_works(possibles$orcid) 
+    temp_DF <- do.call(bind_rows, temp_works)
 
+    if (nrow(temp_DF) > 0){
+    temp_DF$works$title.title.value <- gsub("[[:punct:]]", "", temp_DF$works$title.title.value) 
+    temp_DF$works$title.title.value <- tolower(temp_DF$works$title.title.value) 
+    temp_DF <- temp_DF %>% 
+      filter(temp_DF$works$title.title.value == get_id$TITLE[i])
+
+    id <- unique(na.omit(temp_DF$`source.assertion-origin-orcid.path`))
+
+    if(length(id) == 1) { get_id$ORCID[i] <- id }
+    if(length(id) > 1) { get_id$ORCID[i] <- list(id) }
+
+    }
+  }
+
+  # be nice to api take a break 
+  Sys.sleep(runif(1, 3, 5))
+
+}
+
+write.csv(get_id, "possible_orc_ids.csv", row.names = F)
+```
+
+## Google Scholar
+
+```{r}
+# thanks SO for this id for the bad coding on scholar 
+p_get_scholar_id <- possibly(get_scholar_id, otherwise = NA_character_)
+scholars <- character(nrow(get_id))
+for(i in 1:10) {
+  scholars[i] <- p_get_scholar_id(last_name = get_id$last[i], 
+                         first_name = get_id$first[i])
+
+  # be nice to api take a break 
+  Sys.sleep(runif(1, 3, 5))
+}
+
+get_id$scholar <- scholars
+
+write.csv(get_id, "possible_both_ids.csv", row.names = F)
+```
+
+## Get Person Statistics
+
+```{r}
 erin_df <- rorcid::works("0000-0002-9689-4189") %>%

### 2022-02-18 get_data.Rmd
yay figured it out

@@
 library(tidyverse)
+library(httr)
 
@@
 
+  cat(i)
+  cat("\n")
+
   # if nrow = 0 then move on
@@
 
-    id <- unique(na.omit(temp_DF$`source.assertion-origin-orcid.path`))
+    id <- unique(na.omit(temp_DF$works$`source.assertion-origin-orcid.path`))
 
@@
 
+- First, fix the scholar package issue that it doesn't correctly pull ids that have punctuation in them.
+-
+
+```{r}
+get_scholar <- function (last_name = "", first_name = "", affiliation = NA) 
+{
+    if (!any(nzchar(c(first_name, last_name)))) 
+        stop("At least one of first and last name must be specified!")
+    site <- getOption("scholar_site")
+    url <- paste0(site, "/citations?view_op=search_authors&mauthors=", 
+        first_name, "+", last_name, "&hl=en&oi=ao")
+    page <- get_scholar_resp(url)
+    if (is.null(page)) 
+        return(NA)
+    aa <- content(page, as = "text")
+    ids <- stringr::str_extract_all(string = aa, pattern = ';user=.{12}')
+
+    if (length(unlist(ids)) == 0) {
+        message("No Scholar ID found.")
+        return(NA)
+    }
+    ids <- ids %>% unlist %>% gsub(";user=", "", 
+        .) %>% unique
+
+    return(ids)
+  }
+```
+
+- Then determine if you can find scholars matching that information.
+
 ```{r}
 # thanks SO for this id for the bad coding on scholar 
-p_get_scholar_id <- possibly(get_scholar_id, otherwise = NA_character_)
+p_get_scholar_id <- possibly(get_scholar, otherwise = NA_character_)
 scholars <- character(nrow(get_id))
 for(i in 1:10) {
-  scholars[i] <- p_get_scholar_id(last_name = get_id$last[i], 
+  id <- NA
+  possibles <- p_get_scholar_id(last_name = get_id$last[i], 
                                 first_name = get_id$first[i])
+
+  for (q in 1:length(possibles)){
+
+    articles <- get_publications(possibles[q])
+    articles$title <- gsub("[[:punct:]]", "", articles$title) 
+    articles$title <- tolower(articles$title) 
+    temp_DF <- articles %>% 
+      filter(title == get_id$TITLE[i])
+
+    if (nrow(temp_DF) > 0){
+
+      if (!is.na(id)){ 
+        id <- c(id, possibles[q]) 
+        } else { id <- possibles[q] }
+    }
+
+  }
+  cat(i)
+  cat("\n")
+
+  if (length(id) == 1) { scholars[i] <- id }
+  if (length(id) > 1) { scholars[i] <- list(id) }
 
@@
 
+...average citation rates/h index/i10 index
+
 Journal statistics: 

### 2022-02-25 get_data.Rmd
updating with information

@@
 
-#for (i in 1:nrow(get_id)){
-for (i in 1:10){ #temporary do a small number
+for (i in 1:nrow(get_id)){
+#for (i in 1:10){ #temporary do a small number
 
@@
 scholars <- character(nrow(get_id))
-for(i in 1:10) {
+for(i in 39:length(scholars)) {
   id <- NA

### 2022-02-25 get_data.Rmd
updated id files

@@
 
-```{r}
+```{r eval = F}
 # there are going to be a lot of duplicates
@@
 - First, fix the scholar package issue that it doesn't correctly pull ids that have punctuation in them.
--
 
-```{r}
+```{r eval = F}
 get_scholar <- function (last_name = "", first_name = "", affiliation = NA) 
@@
 
-```{r}
+```{r eval = F}
 # thanks SO for this id for the bad coding on scholar 
@@
 scholars <- character(nrow(get_id))
-for(i in 39:length(scholars)) {
+
+for(i in 1:length(scholars)) {
+
   id <- NA

### 2022-04-07 01.get_person_ids.Rmd
sorting out files and fixing headers

--- 2022-02-25 get_data.Rmd
@@
 ---
-title: "Get Data"
+title: "Get Person Ids"
 author: "Erin M. Buchanan"
@@
   - We will have to manually add the names for several papers that used consortium authors. 
-  - The pre-reg of this document only examines one paper to ensure code can be run and develop workflow.
+  - The pre-reg of this document only examines a few authors/papers to ensure code can be run and develop workflow.
 
@@
 ```
-
-## Get Person Statistics
-
-```{r}
-erin_df <- rorcid::works("0000-0002-9689-4189") %>%
-  as_tibble() %>%
-  janitor::clean_names() %>%
-  dplyr::mutate(created_date_value = anytime::anydate(created_date_value/1000))
-
-table(erin_df$type)
-
-erin_df$title_title_value <- tolower(erin_df$title_title_value)
-erin_df$title_title_value <- gsub("[[:punct:]]", "", erin_df$title_title_value)
-nrow(erin_df)
-
-# remove real duplicates
-temp <- erin_df[!duplicated(erin_df[ , c("type", "title_title_value") ]), ]
-nrow(temp)
-
-# combine types
-erin_df$our_type <- erin_df$type
-erin_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", erin_df$our_type)
-
-table(erin_df$our_type)
-
-erin_ed <- orcid_educations("0000-0002-9689-4189") %>% 
-  as_tibble() %>%
-  janitor::clean_names()
-
-orcid_employments("0000-0002-9689-4189")
-
-```
-
-May need to manually edit some stuff
-Figure out how to get information
-
-Person statistics: 
-- Career length: from first pub, from first degree
-  `publication_date_year_value` anything 
-- Employment levels
-- Education levels
-- # Of works: separate to total, other/preprint/data-set, journal/book/traditional
-- Limitations of this system
-
-...average citation rates/h index/i10 index
-
-Journal statistics: 
-- Which journals are publishing this information
-  - make sure preprints we are using also have real journal merged in 
-- Types of big team research (social, cognitive)
-  - keywords 
-- Over time: are things becoming more varied
-  - are the publications more varied over time

### 2022-04-07 02.get_person_stats.Rmd
sorting out files and fixing headers

--- 2022-02-18 get_data.Rmd
@@
 library(dplyr)
-library(purrr)
+library(rio)
 library(bib2df)
-library(tidyverse)
-library(httr)
-
-library(rorcid)
-# orcid_auth() run the first time to set up
-# copy the bearer number 
-# file.edit("~/.Renviron")
-# ORCID_TOKEN="numberhere"
-
-library(scholar)
 ```
@@
 
-## ORCID
+## Match to IDs
 
-In this section, we will figure out the ORCIDs for each author if possible.
-
-  - Data is stored in `bibs$AUTHOR` as a list. 
-  - Extract that information and loop over the author list. 
-  - Because authors will repeat, we need to put this in long format with one row per author and all other information saved. 
-  - Next, split author name, so we can look it up with orcid.
+In trying to run our `01.get_person_ids.Rmd` file, we figured out that a lot of the data did not bring up matches. Therefore, we coded most scholar and orcids by hand.
 
 ```{r}
-# get data into long format
-long_bib <- bibs %>% unnest_longer(col = AUTHOR)
-
-# remove this nonsense
-long_bib$AUTHOR <- gsub("[{}]", "", long_bib$AUTHOR)
-
-# now split the names into last, first middle 
-# first split on the comma only 
-long_bib <- long_bib %>% separate(col = AUTHOR, sep = ",", 
-                                  into = c("last", "first"), 
-                                  extra = "merge")
-
-# remove the first space
-long_bib$first <- gsub("^ ", "", long_bib$first)
-
-# then split on space
-long_bib <- long_bib %>% separate(col = first, sep = " ", 
-                                  into = c("first", "middle"),
-                                  extra = "merge")
-
-# drop editor column so it is a non-nested DF
-long_bib <- long_bib %>% select(-EDITOR)
-write.csv(long_bib, "unedited_bib.csv", row.names = F)
-```
-
-To make the finalized data:
-
-  - Loop over rows and find candidates for ORCIDs.
-  - Export the candidate data.
-  - Export the bibtex data (done above).
-  - A bit of fun manual merging.
-
-```{r}
-# there are going to be a lot of duplicates
-# really only need to check them once if exact match
-# not perfect exclusion because of symbol differences and middles but ok 
-get_id <- long_bib %>% select(last, first, middle, TITLE)
-get_id <- get_id %>% filter(!duplicated(get_id[ , c("last", "first")]))
-
-# clean up titles
-get_id$TITLE <- gsub("[[:punct:]]", "", get_id$TITLE)
-get_id$TITLE <- tolower(get_id$TITLE)
-
-get_id$ORCID <- NA
-
-#for (i in 1:nrow(get_id)){
-for (i in 1:10){ #temporary do a small number
-
-  # find possible candidates 
-  possibles <- orcid_search(family_name = get_id$last[i], 
-                            given_name = get_id$first[i])
-
-  cat(i)
-  cat("\n")
-
-  # if nrow = 0 then move on
-
-  # if nrow == 1 then figure out if there's a match
-  if (nrow(possibles) == 1){
-    temp_works <- orcid_works(possibles$orcid) 
-    temp_DF <- do.call(bind_rows, temp_works)
-
-    if (nrow(temp_DF) > 0){
-    temp_DF$title.title.value <- gsub("[[:punct:]]", "", temp_DF$title.title.value) 
-    temp_DF$title.title.value <- tolower(temp_DF$title.title.value) 
-    temp_DF <- temp_DF %>% 
-      filter(temp_DF$title.title.value == get_id$TITLE[i])
-
-    id <- unique(na.omit(temp_DF$`source.assertion-origin-orcid.path`))
-
-    if(length(id) == 1) { get_id$ORCID[i] <- id }
-    if(length(id) > 1) { get_id$ORCID[i] <- list(id) }
-
-    }
-  }
-
-  # if nrow > 1 figure it out which matches
-  if (nrow(possibles) > 1){
-    temp_works <- orcid_works(possibles$orcid) 
-    temp_DF <- do.call(bind_rows, temp_works)
-
-    if (nrow(temp_DF) > 0){
-    temp_DF$works$title.title.value <- gsub("[[:punct:]]", "", temp_DF$works$title.title.value) 
-    temp_DF$works$title.title.value <- tolower(temp_DF$works$title.title.value) 
-    temp_DF <- temp_DF %>% 
-      filter(temp_DF$works$title.title.value == get_id$TITLE[i])
-
-    id <- unique(na.omit(temp_DF$works$`source.assertion-origin-orcid.path`))
-
-    if(length(id) == 1) { get_id$ORCID[i] <- id }
-    if(length(id) > 1) { get_id$ORCID[i] <- list(id) }
-
-    }
-  }
-
-  # be nice to api take a break 
-  Sys.sleep(runif(1, 3, 5))
-
-}
-
-write.csv(get_id, "possible_orc_ids.csv", row.names = F)
-```
-
-## Google Scholar
-
-- First, fix the scholar package issue that it doesn't correctly pull ids that have punctuation in them.
--
-
-```{r}
-get_scholar <- function (last_name = "", first_name = "", affiliation = NA) 
-{
-    if (!any(nzchar(c(first_name, last_name)))) 
-        stop("At least one of first and last name must be specified!")
-    site <- getOption("scholar_site")
-    url <- paste0(site, "/citations?view_op=search_authors&mauthors=", 
-        first_name, "+", last_name, "&hl=en&oi=ao")
-    page <- get_scholar_resp(url)
-    if (is.null(page)) 
-        return(NA)
-    aa <- content(page, as = "text")
-    ids <- stringr::str_extract_all(string = aa, pattern = ';user=.{12}')
-
-    if (length(unlist(ids)) == 0) {
-        message("No Scholar ID found.")
-        return(NA)
-    }
-    ids <- ids %>% unlist %>% gsub(";user=", "", 
-        .) %>% unique
-
-    return(ids)
-  }
-```
-
-- Then determine if you can find scholars matching that information.
-
-```{r}
-# thanks SO for this id for the bad coding on scholar 
-p_get_scholar_id <- possibly(get_scholar, otherwise = NA_character_)
-scholars <- character(nrow(get_id))
-for(i in 1:10) {
-  id <- NA
-  possibles <- p_get_scholar_id(last_name = get_id$last[i], 
-                                first_name = get_id$first[i])
-
-  for (q in 1:length(possibles)){
-
-    articles <- get_publications(possibles[q])
-    articles$title <- gsub("[[:punct:]]", "", articles$title) 
-    articles$title <- tolower(articles$title) 
-    temp_DF <- articles %>% 
-      filter(title == get_id$TITLE[i])
-
-    if (nrow(temp_DF) > 0){
-
-      if (!is.na(id)){ 
-        id <- c(id, possibles[q]) 
-        } else { id <- possibles[q] }
-    }
-
-  }
-  cat(i)
-  cat("\n")
-
-  if (length(id) == 1) { scholars[i] <- id }
-  if (length(id) > 1) { scholars[i] <- list(id) }
-
-  # be nice to api take a break 
-  Sys.sleep(runif(1, 3, 5))
-}
-
-get_id$scholar <- scholars
-
-write.csv(get_id, "possible_both_ids.csv", row.names = F)
+id_list <- import("test_utf8.xlsx")
 ```
@@
 
-May need to manually edit some stuff
-Figure out how to get information
-
 Person statistics: 

### 2022-04-07 02.get_person_stats.Rmd
working on the analysis

@@
 library(rio)
-library(bib2df)
+library(tidyr)
+library(rorcid)
+library(purrr)
+library(anytime)
+library(janitor)
 ```
 
-## Import the BibTeX File
-
-In this section, we are importing the bibtex file that includes all the papers we are going to use.
-
-Notes:
-
-  - We used the preprint manuscript for some papers because they had the entire author list, we will update their references manually for the final dataset. 
-  - We will have to manually add the names for several papers that used consortium authors. 
-  - The pre-reg of this document only examines a few authors/papers to ensure code can be run and develop workflow.
-
-```{r}
-bibs <- bib2df("papers.bib")
-```
-
-## Match to IDs
+## Import Unique People
 
@@
 
+### ORCID
+
 ```{r}
-erin_df <- rorcid::works("0000-0002-9689-4189") %>%
+id_list$ORCID <- gsub("^NA$", NA, id_list$ORCID)
+
+orc_list <- na.omit(unique(id_list$ORCID))
+author_works <- list()
+author_ed <- list()
+author_job <- list()
+
+for (ORCID in orc_list) {
+
+  # get works
+  works_df <- works(ORCID) %>%
   as_tibble() %>%
@@
 
-table(erin_df$type)
+  # make all works normalized
+  works_df$title_title_value <- tolower(works_df$title_title_value)
+  works_df$title_title_value <- gsub("[[:punct:]]", " ", works_df$title_title_value)
 
-erin_df$title_title_value <- tolower(erin_df$title_title_value)
-erin_df$title_title_value <- gsub("[[:punct:]]", "", erin_df$title_title_value)
-nrow(erin_df)
+  # combine types
+  works_df$our_type <- works_df$type
+  works_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", works_df$our_type)
 
   # remove real duplicates
-temp <- erin_df[!duplicated(erin_df[ , c("type", "title_title_value") ]), ]
-nrow(temp)
+  author_works[[ORCID]] <- works_df[!duplicated(works_df[ , c("our_type", "title_title_value") ]), ]
 
-# combine types
-erin_df$our_type <- erin_df$type
-erin_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", erin_df$our_type)
+  Sys.sleep(runif(1, 1, 2))
 
-table(erin_df$our_type)
-
-erin_ed <- orcid_educations("0000-0002-9689-4189") %>% 
-  as_tibble() %>%
+  # education 
+  author_ed[[ORCID]] <- orcid_educations(ORCID) %>% 
+    purrr::map(., purrr::pluck, "affiliation-group", "summaries") %>% 
+    purrr::flatten_dfr() %>% 
     janitor::clean_names()
 
-orcid_employments("0000-0002-9689-4189")
+  Sys.sleep(runif(1, 1, 2))
 
+  # employments
+  author_job[[ORCID]] <- orcid_employments(ORCID) %>%
+  purrr::map(., purrr::pluck, "affiliation-group", "summaries") %>% 
+  purrr::flatten_dfr() %>%
+  janitor::clean_names() 
+  Sys.sleep(runif(1, 1, 2))
+
+}
+
+works_df <- do.call(bind_rows, author_works) %>% select(-external_ids_external_id)
+works_df$ORCID <- rep(names(author_works), lapply(author_works, nrow))
+write.csv(works_df, "ORCID_works.csv", row.names = F)
+
+ed_df <- do.call(bind_rows, author_ed)
+ed_df$ORCID <- rep(names(author_ed), lapply(author_ed, nrow))
+ed_df <- ed_df %>% 
+    dplyr::mutate(education_summary_created_date_value =
+                  anytime::anydate(education_summary_created_date_value/1000),
+                education_summary_last_modified_date_value =
+                  anytime::anydate(education_summary_last_modified_date_value/1000))
+
+write.csv(ed_df, "ORCID_ed.csv", row.names = F)
+
+job_df <- do.call(bind_rows, author_job)
+job_df$ORCID <- rep(names(author_job), lapply(author_job, nrow))
+job_df <- job_df %>%
+  dplyr::mutate(employment_summary_end_date =
+                  anytime::anydate(employment_summary_end_date/1000),
+                employment_summary_created_date_value =
+                  anytime::anydate(employment_summary_created_date_value/1000),
+                employment_summary_last_modified_date_value =
+                  anytime::anydate(employment_summary_last_modified_date_value/1000))
+write.csv(job_df, "ORCID_job.csv", row.names = F)
 ```
 
-Person statistics: 
-- Career length: from first pub, from first degree
-  `publication_date_year_value` anything 
-- Employment levels
-- Education levels
-- # Of works: separate to total, other/preprint/data-set, journal/book/traditional
-- Limitations of this system
+### Scholar
 
-...average citation rates/h index/i10 index
+```{r}
+id_list$scholar <- gsub("^NA$", NA, id_list$scholar)
 
-Journal statistics: 
-- Which journals are publishing this information
-  - make sure preprints we are using also have real journal merged in 
-- Types of big team research (social, cognitive)
-  - keywords 
-- Over time: are things becoming more varied
-  - are the publications more varied over time
+scholar_list <- na.omit(unique(id_list$scholar))
+s_author_works <- list()
+s_author_info <- list()
+
+for (scholar in scholar_list) {
+
+  # works 
+  works_df <- get_publications(scholar)
+  works_df$title <- tolower(works_df$title)
+  works_df$title <- gsub("[[:punct:]]", " ", works_df$title)
+
+  Sys.sleep(runif(1, 1, 2))
+
+  # remove duplicates
+  s_author_works[[scholar]] <- works_df %>% 
+    arrange(desc(cites)) %>% 
+    filter(!duplicated(works_df %>% select(title)))
+
+  # information
+  s_author_info[[scholar]] <- get_profile(scholar)
+
+  Sys.sleep(runif(1, 1, 2))
+
+}
+
+works_df <- do.call(bind_rows, s_author_works) 
+works_df$scholar <- rep(names(s_author_works), lapply(s_author_works, nrow))
+write.csv(works_df, "scholar_works.csv", row.names = F)
+
+# paste together information 
+for (scholar in scholar_list){
+
+  s_author_info[[scholar]]$interests <- paste(s_author_info[[scholar]]$interests, collapse = ";;")
+  s_author_info[[scholar]]$coauthors <- paste(s_author_info[[scholar]]$coauthors, collapse = ";;")
+
+  if (length(s_author_info[[scholar]]$homepage) < 1){
+    s_author_info[[scholar]]$homepage <- NA
+  }
+
+  }
+
+info_df <- do.call(bind_rows, s_author_info) 
+info_df$scholar <- info_df$id
+write.csv(info_df, "scholar_info.csv", row.names = F)
+```

### 2022-04-07 03.data_analysis.Rmd
working on the analysis

--- 2022-02-18 get_data.Rmd
@@
 ---
-title: "Get Data"
+title: "Data Analysis"
 author: "Erin M. Buchanan"
@@
 library(dplyr)
-library(purrr)
 library(bib2df)
-library(tidyverse)
-library(httr)
-
-library(rorcid)
-# orcid_auth() run the first time to set up
-# copy the bearer number 
-# file.edit("~/.Renviron")
-# ORCID_TOKEN="numberhere"
-
-library(scholar)
+library(rio)
 ```
 
-## Import the BibTeX File
+## Import Bib Data
 
@@
 bibs <- bib2df("papers.bib")
-```
 
-## ORCID
-
-In this section, we will figure out the ORCIDs for each author if possible.
-
-  - Data is stored in `bibs$AUTHOR` as a list. 
-  - Extract that information and loop over the author list. 
-  - Because authors will repeat, we need to put this in long format with one row per author and all other information saved. 
-  - Next, split author name, so we can look it up with orcid.
-
-```{r}
 # get data into long format
@@
 long_bib <- long_bib %>% select(-EDITOR)
-write.csv(long_bib, "unedited_bib.csv", row.names = F)
 ```
 
-To make the finalized data:
-
-  - Loop over rows and find candidates for ORCIDs.
-  - Export the candidate data.
-  - Export the bibtex data (done above).
-  - A bit of fun manual merging.
+In this section, we will add the information for authors when they used a consortium authorship.
 
 ```{r}
-# there are going to be a lot of duplicates
-# really only need to check them once if exact match
-# not perfect exclusion because of symbol differences and middles but ok 
-get_id <- long_bib %>% select(last, first, middle, TITLE)
-get_id <- get_id %>% filter(!duplicated(get_id[ , c("last", "first")]))
-
-# clean up titles
-get_id$TITLE <- gsub("[[:punct:]]", "", get_id$TITLE)
-get_id$TITLE <- tolower(get_id$TITLE)
-
-get_id$ORCID <- NA
-
-#for (i in 1:nrow(get_id)){
-for (i in 1:10){ #temporary do a small number
-
-  # find possible candidates 
-  possibles <- orcid_search(family_name = get_id$last[i], 
-                            given_name = get_id$first[i])
-
-  cat(i)
-  cat("\n")
-
-  # if nrow = 0 then move on
-
-  # if nrow == 1 then figure out if there's a match
-  if (nrow(possibles) == 1){
-    temp_works <- orcid_works(possibles$orcid) 
-    temp_DF <- do.call(bind_rows, temp_works)
-
-    if (nrow(temp_DF) > 0){
-    temp_DF$title.title.value <- gsub("[[:punct:]]", "", temp_DF$title.title.value) 
-    temp_DF$title.title.value <- tolower(temp_DF$title.title.value) 
-    temp_DF <- temp_DF %>% 
-      filter(temp_DF$title.title.value == get_id$TITLE[i])
-
-    id <- unique(na.omit(temp_DF$`source.assertion-origin-orcid.path`))
-
-    if(length(id) == 1) { get_id$ORCID[i] <- id }
-    if(length(id) > 1) { get_id$ORCID[i] <- list(id) }
-
-    }
-  }
-
-  # if nrow > 1 figure it out which matches
-  if (nrow(possibles) > 1){
-    temp_works <- orcid_works(possibles$orcid) 
-    temp_DF <- do.call(bind_rows, temp_works)
-
-    if (nrow(temp_DF) > 0){
-    temp_DF$works$title.title.value <- gsub("[[:punct:]]", "", temp_DF$works$title.title.value) 
-    temp_DF$works$title.title.value <- tolower(temp_DF$works$title.title.value) 
-    temp_DF <- temp_DF %>% 
-      filter(temp_DF$works$title.title.value == get_id$TITLE[i])
-
-    id <- unique(na.omit(temp_DF$works$`source.assertion-origin-orcid.path`))
-
-    if(length(id) == 1) { get_id$ORCID[i] <- id }
-    if(length(id) > 1) { get_id$ORCID[i] <- list(id) }
-
-    }
-  }
-
-  # be nice to api take a break 
-  Sys.sleep(runif(1, 3, 5))
-
-}
-
-write.csv(get_id, "possible_orc_ids.csv", row.names = F)
-```
-
-## Google Scholar
-
-- First, fix the scholar package issue that it doesn't correctly pull ids that have punctuation in them.
--
-
-```{r}
-get_scholar <- function (last_name = "", first_name = "", affiliation = NA) 
-{
-    if (!any(nzchar(c(first_name, last_name)))) 
-        stop("At least one of first and last name must be specified!")
-    site <- getOption("scholar_site")
-    url <- paste0(site, "/citations?view_op=search_authors&mauthors=", 
-        first_name, "+", last_name, "&hl=en&oi=ao")
-    page <- get_scholar_resp(url)
-    if (is.null(page)) 
-        return(NA)
-    aa <- content(page, as = "text")
-    ids <- stringr::str_extract_all(string = aa, pattern = ';user=.{12}')
-
-    if (length(unlist(ids)) == 0) {
-        message("No Scholar ID found.")
-        return(NA)
-    }
-    ids <- ids %>% unlist %>% gsub(";user=", "", 
-        .) %>% unique
-
-    return(ids)
-  }
-```
-
-- Then determine if you can find scholars matching that information.
-
-```{r}
-# thanks SO for this id for the bad coding on scholar 
-p_get_scholar_id <- possibly(get_scholar, otherwise = NA_character_)
-scholars <- character(nrow(get_id))
-for(i in 1:10) {
-  id <- NA
-  possibles <- p_get_scholar_id(last_name = get_id$last[i], 
-                                first_name = get_id$first[i])
-
-  for (q in 1:length(possibles)){
-
-    articles <- get_publications(possibles[q])
-    articles$title <- gsub("[[:punct:]]", "", articles$title) 
-    articles$title <- tolower(articles$title) 
-    temp_DF <- articles %>% 
-      filter(title == get_id$TITLE[i])
-
-    if (nrow(temp_DF) > 0){
-
-      if (!is.na(id)){ 
-        id <- c(id, possibles[q]) 
-        } else { id <- possibles[q] }
-    }
-
-  }
-  cat(i)
-  cat("\n")
-
-  if (length(id) == 1) { scholars[i] <- id }
-  if (length(id) > 1) { scholars[i] <- list(id) }
-
-  # be nice to api take a break 
-  Sys.sleep(runif(1, 3, 5))
-}
-
-get_id$scholar <- scholars
-
-write.csv(get_id, "possible_both_ids.csv", row.names = F)
-```
-
-## Get Person Statistics
-
-```{r}
-erin_df <- rorcid::works("0000-0002-9689-4189") %>%
-  as_tibble() %>%
-  janitor::clean_names() %>%
-  dplyr::mutate(created_date_value = anytime::anydate(created_date_value/1000))
-
-table(erin_df$type)
-
-erin_df$title_title_value <- tolower(erin_df$title_title_value)
-erin_df$title_title_value <- gsub("[[:punct:]]", "", erin_df$title_title_value)
-nrow(erin_df)
-
-# remove real duplicates
-temp <- erin_df[!duplicated(erin_df[ , c("type", "title_title_value") ]), ]
-nrow(temp)
-
-# combine types
-erin_df$our_type <- erin_df$type
-erin_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", erin_df$our_type)
-
-table(erin_df$our_type)
-
-erin_ed <- orcid_educations("0000-0002-9689-4189") %>% 
-  as_tibble() %>%
-  janitor::clean_names()
-
-orcid_employments("0000-0002-9689-4189")
 
@@
 
-May need to manually edit some stuff
-Figure out how to get information
+## Import Author Data
+
+```{r}
+o_works <- import("ORCID_works.csv")
+o_ed <- import("ORCID_ed.csv")
+o_job <- import("ORCID_job.csv")
+
+s_works <- import("") 
+s_info <- import("")
+```
+
+## Summary Statistics
+
+```{r}
+
+```
 
@@
 - Limitations of this system
-
 ...average citation rates/h index/i10 index

### 2022-04-08 02.get_person_stats.Rmd
updating analysis

@@
 
-  # combine types
-  works_df$our_type <- works_df$type
-  works_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", works_df$our_type)
-
   # remove real duplicates
@@
 works_df$ORCID <- rep(names(author_works), lapply(author_works, nrow))
+works_df <- works_df %>% 
+      dplyr::mutate(last_modified_date_value = 
+                      anytime::anydate(last_modified_date_value/1000))
+
 write.csv(works_df, "ORCID_works.csv", row.names = F)

### 2022-04-08 03.data_analysis.Rmd
updating analysis

@@
 library(rio)
+library(tidyr)
+
+#### fix sau chins paper ####
 ```
@@
 ```{r}
+id_list <- import("test_utf8.xlsx")
+
 o_works <- import("ORCID_works.csv")
@@
 
-s_works <- import("") 
-s_info <- import("")
+s_works <- import("scholar_works.csv") 
+s_info <- import("scholar_info.csv")
 ```
@@
 ```{r}
+o_works$publication_date_year_value[o_works$publication_date_year_value < 1920] <- NA
+
+table(o_works$type)
+
+# combine types ####see issues here #### 
+# works_df$our_type <- works_df$type
+# works_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", works_df$our_type)
+
+o_works_summary <- o_works %>% 
+  group_by(ORCID) %>% 
+  summarize(o_career_1_pub = 2022 - min(publication_date_year_value, na.rm = T),
+            o_total_pub = n())
+
+s_works_summary <- s_works %>% 
+  group_by(scholar) %>% 
+  summarize(s_career_1_pub = 2022 - min(year, na.rm = T),
+            s_total_pub = n())
+####citations??####
+
+####see issues here####
+o_ed_summary <- o_ed %>% 
+  group_by(ORCID) %>% 
+  summarize(o_career_1_degree = 2022 - min(education_summary_end_date_year_value, na.rm = T))
+
+# create a table that's ORCID, job, education, year for each year within bib 2013 to 2022
 
 ```
+
+## Merge Information Back
+
+```{r}
+merged_df <- long_bib %>% 
+  left_join(
+    (id_list %>% select(first, last, ORCID, scholar)), 
+    by = c("first" = "first", "last" = "last")
+  ) %>% 
+  left_join(
+    o_works_summary, 
+    by = c("ORCID" = "ORCID")
+  ) %>% 
+  left_join(
+    s_works_summary,
+    by = c("scholar" = "scholar")
+  ) %>% 
+  left_join(
+    o_ed_summary,
+    by = c("ORCID" = "ORCID")
+  ) %>% 
+  left_join(
+    (s_info %>% select(scholar, h_index, i10_index)),
+    by = c("scholar" = "scholar")
+  )
+
+```
+
+## Journal Information
+
+```{r}
+table(bibs$JOURNAL)
+table(bibs$KEYWORDS)
+
+```
+
+## Over Time
 

### 2022-04-08 03.data_analysis.Rmd
updated from meeting

@@
 table(o_works$type)
+o_works$our_type <- o_works$type
+o_works$our_type <- gsub("edited-book|book.+", "book", o_works$our_type)
+o_works$our_type <- gsub("conference.+", "conference", o_works$our_type)
+o_works$our_type <- gsub("dissertation-thesis|supervised-student.+", "thesis", o_works$our_type)
+o_works$our_type <- gsub("magazine.+|report|dictionary-entry", "other-pub", o_works$our_type)
+o_works$our_type <- gsub("working-paper", "preprint", o_works$our_type)
+o_works$our_type <- gsub("website", "other", o_works$our_type)
 
-# combine types ####see issues here #### 
-# works_df$our_type <- works_df$type
-# works_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", works_df$our_type)
+table(o_works$our_type)
 
@@
             s_total_pub = n())
-####citations??####
 
-####see issues here####
+# remember to ignore inf 
 o_ed_summary <- o_ed %>% 
@@
 table(bibs$JOURNAL)
-table(bibs$KEYWORDS)
+table(bibs$KEYWORDS) # hand code
 
+#### impact factor grab them now #### 
 ```
@@
 ## Over Time
+
+- credit contributions ? are we using de-weirding by using those people for translation and data collection only 
+  - grab major roles and see what the diversity is 
+  - look at the first 10 people and the last author 
+  - maybe compare to the other 10 groups (1/3rd, middle, last 1/3rd)
+  - employment_summary_organization_address_country (for the weird part)
+  - average career length / publication counts 
+- across time 
+  - more varied across time
+  - more people 
+  - more different types of people - education levels, jobs levels, country
+  - more citation style things - are people publishing more who are on these teams and what indices do they have
 

### 2022-04-29 03.data_analysis.Rmd
manuscript updates

--- 2022-04-07 03.data_analysis.Rmd
@@
 
+https://www.science.org/content/page/science-information-authors
+
 ## Libraries
@@
 library(rio)
+library(tidyr)
+library(ggplot2)
+library(nlme)
+#### fix sau chins paper #### https://osf.io/gq92w/ 
 ```
@@
 
-s_works <- import("") 
-s_info <- import("")
+s_works <- import("scholar_works.csv") 
+s_info <- import("scholar_info.csv")
 ```
 
-## Summary Statistics
+## Hand Coded Variables
 
 ```{r}
+# will summarize types of research 
+table(o_works$type)
+o_works$our_type <- o_works$type
+o_works$our_type <- gsub("edited-book|book.+", "book", o_works$our_type)
+o_works$our_type <- gsub("conference.+", "conference", o_works$our_type)
+o_works$our_type <- gsub("dissertation-thesis|supervised-student.+", "thesis", o_works$our_type)
+o_works$our_type <- gsub("magazine.+|report|dictionary-entry", "other-pub", o_works$our_type)
+o_works$our_type <- gsub("working-paper", "preprint", o_works$our_type)
+o_works$our_type <- gsub("website", "other", o_works$our_type)
+table(o_works$our_type)
+
+# will code job data 
+table(o_job$employment_summary_role_title)
+o_job$our_job <- tolower(o_job$employment_summary_role_title)
+o_job$our_job <- trimws(o_job$our_job)
+o_job$our_job <- gsub("visit\\s*|visiting\\s*", "", o_job$our_job)
+o_job$our_job <- gsub("ass\\. prof\\.|.*assistant professor.*", "assistant professor", o_job$our_job)
+o_job$our_job <- gsub(".*associate professor.*", "associate professor", o_job$our_job)
+o_job$our_job <- gsub(".*lecturer.*", "lecturer", o_job$our_job)
+o_job$our_job <- gsub("assegnisti|.+post.+|juan de la cierva researcher|post-doc.*|postdoc.*", "post doc", o_job$our_job)
+o_job$our_job <- gsub("borsisti|.*fellow.*", "fellow", o_job$our_job)
+o_job$our_job <- gsub("academic|collaboratori|guest researcher|evaluation specialist|junior specialist|lab manager|personale esterno ed autonomi|research analyst|research associate|research scientist|researcher.*|scholar|senior statistician|special volunteer", "researcher", o_job$our_job)
+o_job$our_job <- gsub(".*intern.*|research asistant", "research assistant", o_job$our_job)
+o_job$our_job <- gsub("dottorandi|.*phd.*", "grad student", o_job$our_job)
+o_job$our_job <- gsub(".*educator.*|teaching assistant", "lecturer", o_job$our_job)
+o_job$our_job <- gsub(".*full.*professor.*", "full professor", o_job$our_job)
+o_job$our_job <- gsub(".*head.*", "head", o_job$our_job)
+o_job$our_job <- gsub("centennial professor|prof\\.|professor of cognitive analytics|proffessor.*|^temporal proffesor.*", "full professor", o_job$our_job)
+table(o_job$our_job)
+
+table(o_ed$education_summary_role_title)
+o_ed$our_ed <- tolower(o_ed$education_summary_role_title)
+o_ed$our_ed <- trimws(o_ed$our_ed)
+o_ed$our_ed <- gsub("[[:punct:]]", "", o_ed$our_ed)
+o_ed$our_ed <- gsub(".*phd.*|.*doctor.*|.*dr.*|^md|^jd", "doctor", o_ed$our_ed)
+o_ed$our_ed <- gsub(".*bachelor.*|.*bsc.*|psicologia|physics enginnering|filosofia|free studies|electronics enginnering|free studies|^ba$|^bs$|^ba in.*|^bs .*|bsocsci.*|biology", "bachelor", o_ed$our_ed)
+o_ed$our_ed <- gsub(".*master.*|.*msc.*|^ma$|masters.*|mse|mres.*|^magrersocoec", "masters", o_ed$our_ed)
+o_ed$our_ed <- gsub("masters of business and economics", "masters", o_ed$our_ed)
+o_ed$our_ed <- gsub("visiting researcher|venia docendi in business administration|graduate student", NA, o_ed$our_ed)
+table(o_ed$our_ed)
+
+bibs$our_keyword <- tolower(bibs$KEYWORDS)
+bibs$our_keyword <- gsub(".*social.*|.*facial feedback hypothesis.*|.*attitude.*|.*interpersonal.*|.*viral infection.*|.*moral judgment.*|.*economics.*|.*relationships.*|.*morality.*|.*ultimatum.*|.*offense.*|psychology, human behaviour", "social", bibs$our_keyword)
+bibs$our_keyword <- gsub("intelligence|.*recognition memory.*|.*cognitive.*|.*working memory.*|.*evolution.*|.*priming.*|.*multivariate.*|.*magical thinking.*|.*legal psychology.*", "cognitive", bibs$our_keyword)
+bibs$our_keyword <- gsub(".*scientific community.*|.*life course.*|.*metascience.*", "metascience", bibs$our_keyword)
+
+bibs$title2 <- tolower(gsub("[[:punct:]]", "", bibs$TITLE))
+
+bibs$our_keyword[grepl("message framing|egodepletion|facial feedback|turri|emotion|motivation|mortality salience|stereotype threat|moral judgments|trafimow|experimental philosophy", 
+                       bibs$title2)] <- "social"
+bibs$our_keyword[grepl("semantic mismatch|priming|actionsentence|memory|eeg|object orientation|cognitive|natural language", 
+                       bibs$title2)] <- "cognitive"
+bibs$our_keyword[grepl("toddlers|infancy research", 
+                       bibs$title2)] <- "developmental"
+bibs$our_keyword[grepl("researchers choices|diffusion decision|many analysts|pool quality|variation in replicability|hidden universe|psychological science", 
+                       bibs$title2)] <- "metascience"
+bibs$our_keyword[grepl("subjective wellbeing|mental illness|online alcohol survey", 
+                       bibs$title2)] <- "clinical"
+bibs$our_keyword[grepl("immediate feedback",
+                       bibs$title2)] <- "education"
+
+table(bibs$title2[is.na(bibs$our_keyword)])
+
+table(bibs$our_keyword, useNA = "ifany")
+```
+
+## Journal Information
+
+```{r}
+### figure out impact factors 
+```
+
+## Create Summary Statistics
+
+```{r}
+# will filter out bad data, here's an example
+summary(o_works$publication_date_year_value)
+o_works$publication_date_year_value[o_works$publication_date_year_value < 1920] <- NA
+
+# create summary variables
+
+# total pubs and career since first pub
+o_works_summary <- o_works %>% 
+  group_by(ORCID) %>% 
+  summarize(o_career_1_pub = min(publication_date_year_value, na.rm = T),
+            o_total_pub = n())
+
+s_works_summary <- s_works %>% 
+  group_by(scholar) %>% 
+  summarize(s_career_1_pub = min(year, na.rm = T),
+            s_total_pub = n())
+
+# career since first degree
+o_ed_summary <- o_ed %>% 
+  group_by(ORCID) %>% 
+  summarize(o_career_1_degree = min(education_summary_end_date_year_value, na.rm = T)) 
+# remember to ignore inf 
+o_ed_summary$o_career_1_degree[o_ed_summary$o_career_1_degree < 0] <- NA
+
+# create a table that's ORCID, job, education, year for each year within bib 2013 to 2022
+roles_years <- data.frame(
+  ORCID = rep(unique(o_ed$ORCID), each = (2022 - 2012)),
+  year = rep(2013:2022, length(unique(o_ed$ORCID))),
+  education = rep(NA, length(rep(unique(o_ed$ORCID), each = (2022 - 2012)))),
+  job = rep(NA, length(rep(unique(o_ed$ORCID), each = (2022 - 2012))))
+)
+
+o_ed_explode <- data.frame()
+o_job_explode <- data.frame()
+
+# for jobs fill in "current" or end date
+# Find users with blanks
+# For each one find the number of rows 
+# If 1 then make 2022
+# If more than 1 
+# Use the lead or other end function 
+o_job %>% filter(is.na(employment_summary_end_date_year_value)) %>% 
+  select(ORCID, employment_summary_start_date_year_value, employment_summary_role_title)
+
+for (year in 2013:2022){
+
+  temp <- o_ed %>% 
+    filter(education_summary_end_date_year_value <= year) %>% 
+    arrange(desc(education_summary_end_date_year_value)) %>% 
+    filter(!duplicated(ORCID)) %>% 
+    select(ORCID, education_summary_role_title, 
+           education_summary_organization_address_country) %>% 
+    mutate(year_merge = year)
+
+  o_ed_explode <- bind_rows(o_ed_explode, temp)
+
+  temp2 <- o_job %>% 
+    filter(employment_summary_end_date_year_value >= year) %>% 
+    arrange(desc(employment_summary_end_date_year_value)) %>% 
+    filter(!duplicated(ORCID)) %>% 
+    select(ORCID, employment_summary_role_title, 
+           employment_summary_organization_address_country) %>% 
+    mutate(year_merge = year)
+
+  o_job_explode <- bind_rows(o_job_explode, temp2)
+
+}
+
+ roles_years <- roles_years %>% 
+   left_join(o_ed_explode, 
+             by = c("ORCID" = "ORCID", "year" = "year_merge")) %>% 
+   left_join(o_job_explode, 
+             by = c("ORCID" = "ORCID", "year" = "year_merge"))
+```
+
+## Merge Information Back
+
+```{r}
+merged_df <- long_bib %>% 
+  left_join(
+    # note this isn't perfect ... will have to make sure all versions 
+    # get matched 
+    (id_list %>% select(first, last, ORCID, scholar)), 
+    by = c("first" = "first", "last" = "last") 
+  ) %>% 
+  left_join(
+    o_works_summary, 
+    by = c("ORCID" = "ORCID")
+  ) %>% 
+  left_join(
+    s_works_summary,
+    by = c("scholar" = "scholar")
+  ) %>% 
+  left_join(
+    o_ed_summary,
+    by = c("ORCID" = "ORCID")
+  ) %>% 
+  left_join(
+    (s_info %>% select(scholar, h_index, i10_index)),
+    by = c("scholar" = "scholar")
+  ) %>% 
+  left_join(
+    roles_years,
+    by = c("ORCID" = "ORCID", "YEAR" = "year")
+  )
 
@@
 
-Person statistics: 
-- Career length: from first pub, from first degree
-  `publication_date_year_value` anything 
-- Employment levels
-- Education levels
-- # Of works: separate to total, other/preprint/data-set, journal/book/traditional
-- Limitations of this system
-...average citation rates/h index/i10 index
+## Person Analysis
 
-Journal statistics: 
-- Which journals are publishing this information
+```{r}
+merged_df$graph_year <- factor(merged_df$YEAR)
+```
+
+### Career Length
+
+```{r}
+# since first pub ORCID
+merged_df$o_career_pub_year <- merged_df$YEAR - merged_df$o_career_1_pub
+
+ggplot(merged_df, aes(graph_year, o_career_pub_year)) + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.2, aes(color = TITLE)) + 
+  theme_classic() + 
+  ylab("Career Length (ORCID First Pub)") + 
+  xlab("Year of Publication") +
+  theme(legend.position="none")
+
+### will ask KD about this one ###
+o_career_model <- lme(o_career_1_pub ~ YEAR,
+                      data = merged_df,
+                      na.action = "na.omit",
+                      random = ~1|ORCID)
+
+summary(o_career_model)
+
+variance_df <- merged_df %>% 
+  group_by(TITLE) %>% 
+  summarize(year = mean(YEAR), 
+            var_o_career_1_pub = sd(o_career_1_pub, na.rm = T))
+
+# since first pub scholar
+merged_df$s_career_pub_year <- merged_df$YEAR - merged_df$s_career_1_pub
+
+ggplot(merged_df, aes(graph_year, s_career_pub_year)) + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.1) + 
+  theme_classic() + 
+  ylab("Career Length (Scholar First Pub)") + 
+  xlab("Year of Publication")
+
+### will ask KD about this one ###
+s_career_model <- lme(s_career_pub_year ~ YEAR,
+                      data = merged_df,
+                      na.action = "na.omit",
+                      random = ~1|JOURNAL)
+
+summary(s_career_model)
+
+# since first degree ORCID
+merged_df$o_career_degree_year <- merged_df$YEAR - merged_df$o_career_1_degree
+merged_df$o_career_degree_year[merged_df$o_career_degree_year < 0] <- NA
+
+ggplot(merged_df, aes(graph_year, o_career_degree_year)) + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.1) + 
+  theme_classic() + 
+  ylab("Career Length (ORCID First Degree)") + 
+  xlab("Year of Publication")
+
+### will ask KD about this one ###
+o_career2_model <- lme(o_career_degree_year ~ YEAR,
+                      data = merged_df,
+                      na.action = "na.omit",
+                      random = ~1|JOURNAL)
+
+summary(o_career2_model)
+```
+
+### Employment Levels
+
+```{r}
+# hand code these into categories that make sense
+table(o_job$employment_summary_role_title)
+table(merged_df$employment_summary_role_title)
+
+# table by year 
+# graph by year 
+```
+
+### Education Levels
+
+```{r}
+# hand code these into categories that make sense
+table(merged_df$education_summary_role_title)
+
+# consider coding as 1, 2, 3, 4, etc. 
+# table by year 
+# graph by year 
+```
+
+### Author Bean Counting
+
+```{r}
+# what do these people publish overall
+table(o_works$our_type)
+
+# publication rates ORCID
+ggplot(merged_df, aes(graph_year, o_total_pub)) + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.1) + 
+  theme_classic() + 
+  ylab("Total Publications (ORCID)") + 
+  xlab("Year of Publication")
+
+### will ask KD about this one ###
+o_total_model <- lme(o_total_pub ~ YEAR,
+                      data = merged_df,
+                      na.action = "na.omit",
+                      random = ~1|JOURNAL)
+
+summary(o_total_model)
+
+# publication rates scholar
+ggplot(merged_df, aes(graph_year, s_total_pub)) + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.1) + 
+  theme_classic() + 
+  ylab("Total Publications (Scholar)") + 
+  xlab("Year of Publication")
+
+### will ask KD about this one ###
+s_total_model <- lme(s_total_pub ~ YEAR,
+                      data = merged_df,
+                      na.action = "na.omit",
+                      random = ~1|JOURNAL)
+
+summary(s_total_model)
+
+# h index rates scholar
+ggplot(merged_df, aes(graph_year, h_index)) + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.1) + 
+  theme_classic() + 
+  ylab("H Index") + 
+  xlab("Year of Publication")
+
+### will ask KD about this one ###
+h_index_model <- lme(h_index ~ YEAR,
+                      data = merged_df,
+                      na.action = "na.omit",
+                      random = ~1|JOURNAL)
+
+summary(h_index_model)
+
+# i 10 rates scholar
+ggplot(merged_df, aes(graph_year, i10_index)) + 
+  geom_violin() + 
+  geom_jitter(height = 0, width = 0.1) + 
+  theme_classic() + 
+  ylab("H Index") + 
+  xlab("Year of Publication")
+
+### will ask KD about this one ###
+i_index_model <- lme(i10_index ~ YEAR,
+                      data = merged_df,
+                      na.action = "na.omit",
+                      random = ~1|JOURNAL)
+
+summary(i_index_model)
+```
+
+### More Authors Over Time?
+
+```{r}
+author_count <- 
+  merged_df %>% 
+  group_by(TITLE) %>% 
+  summarize(author_count = n(),
+            year = mean(YEAR))
+
+cor(author_count$author_count, author_count$year)
+
+ggplot(author_count, aes(factor(year), author_count)) +
+  theme_classic() + 
+  geom_point() + 
+  xlab("Year of Publication") + 
+  ylab("Number of Authors")
+```
+
+### Where are Authors?
+
+```{r}
+# where did they get their degree
+merged_df %>% 
+  filter(!duplicated(ORCID)) %>% 
+  count(education_summary_organization_address_country)
+
+table(merged_df$education_summary_organization_address_country,
+      merged_df$YEAR)
+
+# how many different countries does each year have and is that getting bigger
+
+# where do they work
+merged_df %>% 
+  filter(!duplicated(ORCID)) %>% 
+  count(employment_summary_organization_address_country)
+
+table(merged_df$employment_summary_organization_address_country,
+      merged_df$YEAR)
+```
+
+### CRediT and WEIRD
+
+```{r}
+# grab first X authors and last author
+# and the last one for 10 - 49
+num_grab <- 3
+
+# 50 to 99 use 5
+
+# over 100 do top 10
+
+# group into UN regions 
+```
+
+- credit contributions ? are we using de-weirding by using those people for translation and data collection only 
+  - grab major roles and see what the diversity is 
+  - look at the first 10 people and the last author 
+  - maybe compare to the other 10 groups (1/3rd, middle, last 1/3rd)
+
+## Journal Analysis
+
+### Which Journals
+
 - make sure preprints we are using also have real journal merged in
-- Types of big team research (social, cognitive)
-  - keywords 
+
+```{r}
+journal_count <- bibs %>% group_by(JOURNAL) %>% 
+  summarize(freq = n())
+
+journal_count$JOURNAL[is.na(journal_count$JOURNAL)] <- "Pre-Print"
+```
+
+### Article Topics Global Type
+
+- hand coded information on what the articles are about 
+- Types of big team research (social, cognitive) using keywords
+
+```{r}
+# table of hand coded type
+```
+
+### Article Types Over Time
+
 - Over time: are things becoming more varied
 - are the publications more varied over time
+
+```{r}
+# table of hand coded type by year 
+```

### 2022-04-29 04.manuscript.Rmd
manuscript updates

---
title             : "Who does big team science?"
shorttitle        : "Big Team Science"

author: 
  - name          : "Erin M. Buchanan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "326 Market St., Harrisburg, PA 17101"
    email         : "ebuchanan@harrisburgu.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Formal Analysis
      - Methodology
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Savannah C. Lewis"
    affiliation   : "2"
    role:
      - Conceptualization
      - Data curation
      - Methodology
      - Project administration
      - Writing – original draft
      - Writing – review & editing
affiliation:
  - id            : "1"
    institution   : "Harrisburg University of Science and Technology"
  - id            : "2"
    institution   : "University of Alabama"

authornote: |
  Erin M. Buchanan is a Professor of Cognitive Analytics at Harrisburg University of Science and Technology. Savannah C. Lewis is a graduate student at the University of Alabama.

  Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "big team, science, authorship, credit"
wordcount         : "X"

bibliography      : ["big_team_refs.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(538943)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, child = '03.data_analysis.Rmd', include = FALSE, results = FALSE}
```

The introduction will go here. Here's an outline:

- Big Team Science
  - one off papers 
  - collaborative teams 
- Credibility revolution
- WEIRD 
- ... more tbd, brain isn't braining

# Method

## Studies

We defined *big team science publications* as publications with at least 10 authors that were published in peer-reviewed journals or had posted a full paper pre-print for publication review. We specifically focused on social science research, primarily *psychology* for this manuscript. First, we added all known publications from collaborative teams, such as the PSA, Many Labs, and Many Babies. We examined journals that frequently publish registered replication reports (i.e., *Advances in Methods and Practices in Psychological Science*) for additional publications with at least 10 authors. From these manuscripts, we identified common authors who frequently participate in these studies, and examined their Google Scholar or Open Researcher and Contributor IDentifier (ORCID) page for other publications. We reached out to social networks on Twitter to identify other publications. Last, we used Google Scholar and EBSCO to search for large projects using XXX KEY TERMS XXX.

```{r articles-overall, echo = FALSE, include = FALSE}
nrow(bibs)
min(bibs$YEAR)
max(bibs$YEAR)
journal_count$JOURNAL[1]
journal_count$freq[1]
```

Using these criteria, we identified `r nrow(bibs)` articles for inclusion on this manuscript. The publication dates on these articles ranged from `r min(bibs$YEAR)` to `r max(bibs$YEAR)`, and we used the pre-print last updated date as the publication date for those articles. Articles were most commonly published in `r journal_count$JOURNAL[1]` (*n* = `r journal_count$freq[1]`), `r journal_count$JOURNAL[2]` (*n* = `r journal_count$freq[2]`), `r journal_count$JOURNAL[3]` (*n* = `r journal_count$freq[3]`), `r journal_count$JOURNAL[4]` (*n* = `r journal_count$freq[4]`), and `r journal_count$JOURNAL[5]` (*n* = `r journal_count$freq[5]`). A complete list of journals can be found on our Open Science Framework page XXX.

## Data Curation

### Article Information

For each publication, we coded the list of keywords into broad labels for areas of social science (i.e., Social Psychology, Cognitive Psychology). The current impact factor (i.e., 2022) for each journal was found on the journal page and included for journal statistics.

### Author Information

```{r authors, include = FALSE, echo = FALSE}
min(author_count$author_count)
max(author_count$author_count)
format(mean(author_count$author_count), nsmall = 2, digits = 2)
format(sd(author_count$author_count), nsmall = 2, digits = 2)
nrow(id_list)
```

The author list was then extracted from each publication. In the case of consortium authorship, we extracted the complete authorship from the meta-data or pre-print publication. The total number of unique authors was `r nrow(id_list)`. The number of authors on each publication ranged from `r min(author_count$author_count)` to `r max(author_count$author_count)` with an average of `r format(mean(author_count$author_count), nsmall = 2, digits = 2)` authors (*SD* = `r format(sd(author_count$author_count), nsmall = 2, digits = 2)`).

Next, we matched each author to their Google Scholar and ORCID profile pages, if available. We originally used the *R* packages, *rorcid* [CITE] and *scholar* [CITE] to try to match published author names to profile pages. This process did not result in a large number of matches, and we therefore curated the list of profile pages manually, checking each author against the publication list. We used these two packages and profile pages to collect authorship statistics described below.

**Career Length**. Career length for each author was defined using multiple variables to see if results from the two data sources would converge on similar answers. Both ORCID and Google Scholar provide a list of publications for authors, and we first calculated career length as the year of first publication listed for each author. In ORCID, a researcher can enter their educational background with completion years for each degree. We defined career length for this variable as years since first degree listed. Publication years are often curated directly from meta-data provided by Crossref (ORCID) or online sources used by Google Scholar. Authors may also directly add publications and their information into both systems. The limitation to using education as a metric for career length is that the researcher must directly enter this information into ORCID.

**Employment**. Employment information was collected from self-entered ORCID data. These values are open text, and therefore, we coded them into coherent categories for traditional educational (graduate student, post doctoral, lecturer),  tenure track (assistant, associate, full professor), and other roles (fellow, research assistant, researcher, head). Employment geopolitical region was also selected when available.

**Education**. As with employment information, we also collected education information from self-entered ORCID data. These values were coded into general categories of bachelor, master, and doctoral degrees. The geopolitical region of the listed education was included when available. For analyses, both employment and education levels were grouped into United Nation regions.

**Types of Publications**. ORCID includes information about the type of publication pulled from either researcher entered data or Crossref. We coded these publications into general categories including book, conference presentations, data-sets, journal articles, preprints, software, thesis, and other publications.

**Publication Metrics**. We calculated total number of publications of any type from both Google Scholar and ORCID. We additionally pulled both the h-index and i-10 index from Google Scholar. The h-index represents the highest *h* number of publications that have at least *h* citations, while the i-10 index represents the number of publications with at least 10 citations.

## Data analysis

what are we gonna do to answer the research questions

# Results

put stuff in here about the format/structure to answering the research questions

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2022-05-02 03.data_analysis.Rmd
working on manuscript

@@
 
-```{r setup, include=FALSE}
+```{r setup_analysis, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 
+var_o_career_model <- lm(var_o_career_1_pub ~ year, 
+                          data = variance_df,
+                          na.action = "na.omit")
+summary(var_o_career_model)
+
 # since first pub scholar
@@
 journal_count <- bibs %>% group_by(JOURNAL) %>% 
-  summarize(freq = n())
+  summarize(freq = n()) %>% 
+  arrange(desc(freq))
 

### 2022-05-02 04.manuscript.Rmd
working on manuscript

@@
 
-bibliography      : ["big_team_refs.bib"]
+#bibliography      : ["big_team_refs.bib"]
 
@@
 
-```{r, child = '03.data_analysis.Rmd', include = FALSE, results = FALSE}
+```{r, child = '03.data_analysis.Rmd', include = FALSE, results = FALSE, echo = FALSE}
 ```
@@
 
+Research Question 1: What journals publish big team science papers?
+
+Research Question 2: What are the types of articles that are being published in big team science?
+
+Research Question 3: Who is involved in big team science?
+
 # Method
@@
 
-We defined *big team science publications* as publications with at least 10 authors that were published in peer-reviewed journals or had posted a full paper pre-print for publication review.
+We defined **big team science publications** as publications with at least 10 authors that were published in peer-reviewed journals or had posted a full paper pre-print for publication review.
 We specifically focused on social science research, primarily *psychology* for this manuscript.
@@
 We reached out to social networks on Twitter to identify other publications.
-Last, we used Google Scholar and EBSCO to search for large projects using XXX KEY TERMS XXX.
+Last, we used Google Scholar and EBSCO to search for large projects using the following search terms: collaboration, multicultural, large scale, and big team science.
 
-```{r articles-overall, echo = FALSE, include = FALSE}
-nrow(bibs)
-min(bibs$YEAR)
-max(bibs$YEAR)
-journal_count$JOURNAL[1]
-journal_count$freq[1]
-```
+## Data Curation
+
+### Journal Information
 
@@
 The publication dates on these articles ranged from `r min(bibs$YEAR)` to `r max(bibs$YEAR)`, and we used the pre-print last updated date as the publication date for those articles.
-Articles were most commonly published in `r journal_count$JOURNAL[1]` (*n* = `r journal_count$freq[1]`), `r journal_count$JOURNAL[2]` (*n* = `r journal_count$freq[2]`), `r journal_count$JOURNAL[3]` (*n* = `r journal_count$freq[3]`), `r journal_count$JOURNAL[4]` (*n* = `r journal_count$freq[4]`), and `r journal_count$JOURNAL[5]` (*n* = `r journal_count$freq[5]`).
-A complete list of journals can be found on our Open Science Framework page XXX.
-
-## Data Curation
+The current impact factor (i.e., 2022) for each journal was found on the journal page and included for journal statistics.
 
@@
 For each publication, we coded the list of keywords into broad labels for areas of social science (i.e., Social Psychology, Cognitive Psychology).
-The current impact factor (i.e., 2022) for each journal was found on the journal page and included for journal statistics.
+WRITE MORE ABOUT NOT DOUBLE CODING ...
+DEFINE HOW EACH LABEL WAS DONE ...
+WHAT IS METASCIENCE GIVE OSC EXAMPLE
 
@@
 
+## RQ1: Journal Information
+
+Articles were most commonly published in `r journal_count$JOURNAL[1]` (*n* = `r journal_count$freq[1]`), `r journal_count$JOURNAL[2]` (*n* = `r journal_count$freq[2]`), `r journal_count$JOURNAL[3]` (*n* = `r journal_count$freq[3]`), `r journal_count$JOURNAL[4]` (*n* = `r journal_count$freq[4]`), and `r journal_count$JOURNAL[5]` (*n* = `r journal_count$freq[5]`).
+A complete list of journals can be found on our Open Science Framework page XXX.
+
 put stuff in here about the format/structure to answering the research questions

### 2022-05-02 04.manuscript.tex
working on manuscript

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\title{Who does big team science?}
\author{Erin M. Buchanan\textsuperscript{1} \& Savannah C. Lewis\textsuperscript{2}}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Who does big team science?},
  pdfauthor={Erin M. Buchanan1 \& Savannah C. Lewis2},
  pdflang={en-EN},
  pdfkeywords={big team, science, authorship, credit},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Big Team Science}
\keywords{big team, science, authorship, credit\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\authornote{

Erin M. Buchanan is a Professor of Cognitive Analytics at Harrisburg University of Science and Technology. Savannah C. Lewis is a graduate student at the University of Alabama.

Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript.

The authors made the following contributions. Erin M. Buchanan: Conceptualization, Data curation, Formal Analysis, Methodology, Project administration, Visualization, Writing -- original draft, Writing -- review \& editing; Savannah C. Lewis: Conceptualization, Data curation, Methodology, Project administration, Writing -- original draft, Writing -- review \& editing.

Correspondence concerning this article should be addressed to Erin M. Buchanan, 326 Market St., Harrisburg, PA 17101. E-mail: \href{mailto:ebuchanan@harrisburgu.edu}{\nolinkurl{ebuchanan@harrisburgu.edu}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Harrisburg University of Science and Technology\\\textsuperscript{2} University of Alabama}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\url{https://www.science.org/content/page/science-information-authors}

\hypertarget{libraries}{%
\subsection{Libraries}\label{libraries}}

\hypertarget{import-bib-data}{%
\subsection{Import Bib Data}\label{import-bib-data}}

In this section, we are importing the bibtex file that includes all the papers we are going to use.

Notes:

\begin{itemize}
\tightlist
\item
  We used the preprint manuscript for some papers because they had the entire author list, we will update their references manually for the final dataset.
\item
  We will have to manually add the names for several papers that used consortium authors.
\item
  The pre-reg of this document only examines a few authors/papers to ensure code can be run and develop workflow.
\end{itemize}

In this section, we will add the information for authors when they used a consortium authorship.

\hypertarget{import-author-data}{%
\subsection{Import Author Data}\label{import-author-data}}

\hypertarget{hand-coded-variables}{%
\subsection{Hand Coded Variables}\label{hand-coded-variables}}

\hypertarget{journal-information}{%
\subsection{Journal Information}\label{journal-information}}

\hypertarget{create-summary-statistics}{%
\subsection{Create Summary Statistics}\label{create-summary-statistics}}

\hypertarget{merge-information-back}{%
\subsection{Merge Information Back}\label{merge-information-back}}

\hypertarget{person-analysis}{%
\subsection{Person Analysis}\label{person-analysis}}

\hypertarget{career-length}{%
\subsubsection{Career Length}\label{career-length}}

\hypertarget{employment-levels}{%
\subsubsection{Employment Levels}\label{employment-levels}}

\hypertarget{education-levels}{%
\subsubsection{Education Levels}\label{education-levels}}

\hypertarget{author-bean-counting}{%
\subsubsection{Author Bean Counting}\label{author-bean-counting}}

\hypertarget{more-authors-over-time}{%
\subsubsection{More Authors Over Time?}\label{more-authors-over-time}}

\hypertarget{where-are-authors}{%
\subsubsection{Where are Authors?}\label{where-are-authors}}

\hypertarget{credit-and-weird}{%
\subsubsection{CRediT and WEIRD}\label{credit-and-weird}}

\begin{itemize}
\tightlist
\item
  credit contributions ? are we using de-weirding by using those people for translation and data collection only

  \begin{itemize}
  \tightlist
  \item
    grab major roles and see what the diversity is
  \item
    look at the first 10 people and the last author
  \item
    maybe compare to the other 10 groups (1/3rd, middle, last 1/3rd)
  \end{itemize}
\end{itemize}

\hypertarget{journal-analysis}{%
\subsection{Journal Analysis}\label{journal-analysis}}

\hypertarget{which-journals}{%
\subsubsection{Which Journals}\label{which-journals}}

\begin{itemize}
\tightlist
\item
  make sure preprints we are using also have real journal merged in
\end{itemize}

\hypertarget{article-topics-global-type}{%
\subsubsection{Article Topics Global Type}\label{article-topics-global-type}}

\begin{itemize}
\tightlist
\item
  hand coded information on what the articles are about
\item
  Types of big team research (social, cognitive) using keywords
\end{itemize}

\hypertarget{article-types-over-time}{%
\subsubsection{Article Types Over Time}\label{article-types-over-time}}

\begin{itemize}
\tightlist
\item
  Over time: are things becoming more varied
\item
  are the publications more varied over time
\end{itemize}

The introduction will go here. Here's an outline:

\begin{itemize}
\tightlist
\item
  Big Team Science

  \begin{itemize}
  \tightlist
  \item
    one off papers
  \item
    collaborative teams
  \end{itemize}
\item
  Credibility revolution
\item
  WEIRD
\item
  \ldots{} more tbd, brain isn't braining
\end{itemize}

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{studies}{%
\subsection{Studies}\label{studies}}

We defined \textbf{big team science publications} as publications with at least 10 authors that were published in peer-reviewed journals or had posted a full paper pre-print for publication review. We specifically focused on social science research, primarily \emph{psychology} for this manuscript. First, we added all known publications from collaborative teams, such as the PSA, Many Labs, and Many Babies. We examined journals that frequently publish registered replication reports (i.e., \emph{Advances in Methods and Practices in Psychological Science}) for additional publications with at least 10 authors. From these manuscripts, we identified common authors who frequently participate in these studies, and examined their Google Scholar or Open Researcher and Contributor IDentifier (ORCID) page for other publications. We reached out to social networks on Twitter to identify other publications. Last, we used Google Scholar and EBSCO to search for large projects using the following search terms: collaboration, multicultural, large scale, and big team science.

Using these criteria, we identified 70 articles for inclusion on this manuscript. The publication dates on these articles ranged from 2013 to 2022, and we used the pre-print last updated date as the publication date for those articles. Articles were most commonly published in Advances in Methods and Practices in Psychological Science (\emph{n} = 20), Behavior Research Methods (\emph{n} = 1), Collabra: Psychology (\emph{n} = 1), Computers in Human Behavior (\emph{n} = 1), and International Journal of Methods in Psychiatric Research (\emph{n} = 1). A complete list of journals can be found on our Open Science Framework page XXX.

\hypertarget{data-curation}{%
\subsection{Data Curation}\label{data-curation}}

\hypertarget{article-information}{%
\subsubsection{Article Information}\label{article-information}}

For each publication, we coded the list of keywords into broad labels for areas of social science (i.e., Social Psychology, Cognitive Psychology). The current impact factor (i.e., 2022) for each journal was found on the journal page and included for journal statistics.

\hypertarget{author-information}{%
\subsubsection{Author Information}\label{author-information}}

The author list was then extracted from each publication. In the case of consortium authorship, we extracted the complete authorship from the meta-data or pre-print publication. The total number of unique authors was 3336. The number of authors on each publication ranged from 1 to 482 with an average of 68.63 authors (\emph{SD} = 89.89).

Next, we matched each author to their Google Scholar and ORCID profile pages, if available. We originally used the \emph{R} packages, \emph{rorcid} {[}CITE{]} and \emph{scholar} {[}CITE{]} to try to match published author names to profile pages. This process did not result in a large number of matches, and we therefore curated the list of profile pages manually, checking each author against the publication list. We used these two packages and profile pages to collect authorship statistics described below.

\textbf{Career Length}. Career length for each author was defined using multiple variables to see if results from the two data sources would converge on similar answers. Both ORCID and Google Scholar provide a list of publications for authors, and we first calculated career length as the year of first publication listed for each author. In ORCID, a researcher can enter their educational background with completion years for each degree. We defined career length for this variable as years since first degree listed. Publication years are often curated directly from meta-data provided by Crossref (ORCID) or online sources used by Google Scholar. Authors may also directly add publications and their information into both systems. The limitation to using education as a metric for career length is that the researcher must directly enter this information into ORCID.

\textbf{Employment}. Employment information was collected from self-entered ORCID data. These values are open text, and therefore, we coded them into coherent categories for traditional educational (graduate student, post doctoral, lecturer), tenure track (assistant, associate, full professor), and other roles (fellow, research assistant, researcher, head). Employment geopolitical region was also selected when available.

\textbf{Education}. As with employment information, we also collected education information from self-entered ORCID data. These values were coded into general categories of bachelor, master, and doctoral degrees. The geopolitical region of the listed education was included when available. For analyses, both employment and education levels were grouped into United Nation regions.

\textbf{Types of Publications}. ORCID includes information about the type of publication pulled from either researcher entered data or Crossref. We coded these publications into general categories including book, conference presentations, data-sets, journal articles, preprints, software, thesis, and other publications.

\textbf{Publication Metrics}. We calculated total number of publications of any type from both Google Scholar and ORCID. We additionally pulled both the h-index and i-10 index from Google Scholar. The h-index represents the highest \emph{h} number of publications that have at least \emph{h} citations, while the i-10 index represents the number of publications with at least 10 citations.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

what are we gonna do to answer the research questions

\hypertarget{results}{%
\section{Results}\label{results}}

put stuff in here about the format/structure to answering the research questions

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

\endgroup

\end{document}

### 2022-05-06 03.data_analysis.Rmd
add the stuff

@@
 library(nlme)
+library(RColorBrewer)
 #### fix sau chins paper #### https://osf.io/gq92w/ 
@@
 ```{r}
-# will summarize types of research 
+# will summarize types of research ----
 table(o_works$type)
@@
 
-# will code job data 
+# will code job data ----
 table(o_job$employment_summary_role_title)
@@
 
+# hand code education ----
 table(o_ed$education_summary_role_title)
@@
 
+# keywords of articles ----
 bibs$our_keyword <- tolower(bibs$KEYWORDS)
-bibs$our_keyword <- gsub(".*social.*|.*facial feedback hypothesis.*|.*attitude.*|.*interpersonal.*|.*viral infection.*|.*moral judgment.*|.*economics.*|.*relationships.*|.*morality.*|.*ultimatum.*|.*offense.*|psychology, human behaviour", "social", bibs$our_keyword)
-bibs$our_keyword <- gsub("intelligence|.*recognition memory.*|.*cognitive.*|.*working memory.*|.*evolution.*|.*priming.*|.*multivariate.*|.*magical thinking.*|.*legal psychology.*", "cognitive", bibs$our_keyword)
-bibs$our_keyword <- gsub(".*scientific community.*|.*life course.*|.*metascience.*", "metascience", bibs$our_keyword)
+bibs$our_keyword <- gsub(".*social.*|.*facial feedback hypothesis.*|.*attitude.*|.*interpersonal.*|.*viral infection.*|.*moral judgment.*|.*economics.*|.*relationships.*|.*morality.*|.*ultimatum.*|.*offense.*|psychology, human behaviour", "Social", bibs$our_keyword)
+bibs$our_keyword <- gsub("intelligence|.*recognition memory.*|.*cognitive.*|.*working memory.*|.*evolution.*|.*priming.*|.*multivariate.*|.*magical thinking.*|.*legal psychology.*", "Cognitive", bibs$our_keyword)
+bibs$our_keyword <- gsub(".*scientific community.*|.*life course.*|.*metascience.*", "Metascience", bibs$our_keyword)
 
@@
 bibs$our_keyword[grepl("message framing|egodepletion|facial feedback|turri|emotion|motivation|mortality salience|stereotype threat|moral judgments|trafimow|experimental philosophy", 
-                       bibs$title2)] <- "social"
+                       bibs$title2)] <- "Social"
 bibs$our_keyword[grepl("semantic mismatch|priming|actionsentence|memory|eeg|object orientation|cognitive|natural language", 
-                       bibs$title2)] <- "cognitive"
+                       bibs$title2)] <- "Cognitive"
 bibs$our_keyword[grepl("toddlers|infancy research", 
-                       bibs$title2)] <- "developmental"
+                       bibs$title2)] <- "Developmental"
 bibs$our_keyword[grepl("researchers choices|diffusion decision|many analysts|pool quality|variation in replicability|hidden universe|psychological science", 
-                       bibs$title2)] <- "metascience"
+                       bibs$title2)] <- "Metascience"
 bibs$our_keyword[grepl("subjective wellbeing|mental illness|online alcohol survey", 
-                       bibs$title2)] <- "clinical"
+                       bibs$title2)] <- "Clinical"
 bibs$our_keyword[grepl("immediate feedback",
-                       bibs$title2)] <- "education"
+                       bibs$title2)] <- "Educational"
 
 table(bibs$title2[is.na(bibs$our_keyword)])
-
 table(bibs$our_keyword, useNA = "ifany")
@@
 ```{r}
-### figure out impact factors 
+JIF <- import("jif.xlsx")
 ```
 
-## Create Summary Statistics
+## Article Information
+
+```{r}
+article_overall <- as.data.frame(table(bibs$our_keyword)) %>% 
+  arrange(desc(Freq)) %>% 
+  mutate(Percent = Freq / sum(Freq) * 100)
+article_time <- as.data.frame(table(bibs$our_keyword, bibs$YEAR))
+
+article_time_plot <- ggplot(article_time, aes(Var2, Freq, fill = Var1)) +
+  geom_bar(position="stack", stat="identity") + 
+  theme_classic() + 
+  xlab("Publication Year") + 
+  ylab("Number of Papers") + 
+  scale_fill_brewer(palette = "RdBu", name = "Research Area")
+
+```
+
+## Person Analysis
+
+### Create Summary Statistics
 
@@
 o_ed_summary$o_career_1_degree[o_ed_summary$o_career_1_degree < 0] <- NA
+o_ed_summary$o_career_1_degree[o_ed_summary$o_career_1_degree == Inf] <- NA
 
@@
 
+####ERIN YOU STILL HAVE TO DO THIS####
 # for jobs fill in "current" or end date
@@
 
-## Merge Information Back
+### Merge Information Back
 
@@
 
-## Person Analysis
+### Graph Year Fix
 
@@
 ```{r}
-# since first pub ORCID
-merged_df$o_career_pub_year <- merged_df$YEAR - merged_df$o_career_1_pub
+# since first pub ORCID ----
+merged_df$TITLE_color <- as.numeric(factor(merged_df$TITLE))
 
-ggplot(merged_df, aes(graph_year, o_career_pub_year)) + 
+# graph
+o_career_graph <- ggplot(merged_df, aes(graph_year, o_career_1_pub)) + 
   geom_violin() + 
-  geom_jitter(height = 0, width = 0.2, aes(color = TITLE)) + 
+  geom_jitter(height = 0, width = 0.2, aes(color = TITLE_color)) + 
   theme_classic() + 
@@
 
-### will ask KD about this one ###
+# year model slope 
 o_career_model <- lme(o_career_1_pub ~ YEAR,
@@
 
-summary(o_career_model)
-
+# variance model 
 variance_df <- merged_df %>% 
@@
   summarize(year = mean(YEAR), 
-            var_o_career_1_pub = sd(o_career_1_pub, na.rm = T))
+            var_o_career_1_pub = sd(o_career_1_pub, na.rm = T),
+            var_s_career_1_pub = sd(s_career_1_pub, na.rm = T), 
+            var_o_career_1_degree = sd(o_career_1_degree, na.rm = T))
 
@@
                           na.action = "na.omit")
-summary(var_o_career_model)
+```
 
-# since first pub scholar
-merged_df$s_career_pub_year <- merged_df$YEAR - merged_df$s_career_1_pub
+```{r}
+# since first pub scholar ----
 
-ggplot(merged_df, aes(graph_year, s_career_pub_year)) + 
+# graph 
+s_career_graph <- ggplot(merged_df, aes(graph_year, s_career_1_pub)) + 
   geom_violin() + 
-  geom_jitter(height = 0, width = 0.1) + 
+  geom_jitter(height = 0, width = 0.2, aes(color = TITLE_color)) + 
   theme_classic() + 
   ylab("Career Length (Scholar First Pub)") + 
-  xlab("Year of Publication")
+  xlab("Year of Publication") +
+  theme(legend.position="none")
 
-### will ask KD about this one ###
-s_career_model <- lme(s_career_pub_year ~ YEAR,
+# year model slope 
+s_career_model <- lme(s_career_1_pub ~ YEAR,
                       data = merged_df,
                       na.action = "na.omit",
-                      random = ~1|JOURNAL)
+                      random = ~1|scholar)
 
-summary(s_career_model)
+# variance  model 
+var_s_career_model <- lm(var_s_career_1_pub ~ year, 
+                          data = variance_df,
+                          na.action = "na.omit")
+```
 
-# since first degree ORCID
-merged_df$o_career_degree_year <- merged_df$YEAR - merged_df$o_career_1_degree
-merged_df$o_career_degree_year[merged_df$o_career_degree_year < 0] <- NA
-
-ggplot(merged_df, aes(graph_year, o_career_degree_year)) + 
+```{r}
+# since first degree ORCID ----
+o_career_graph_ed <- ggplot(merged_df, aes(graph_year, o_career_1_degree)) +
   geom_violin() + 
-  geom_jitter(height = 0, width = 0.1) + 
+  geom_jitter(height = 0, width = 0.2, aes(color = TITLE_color)) + 
   theme_classic() + 
   ylab("Career Length (ORCID First Degree)") + 
-  xlab("Year of Publication")
+  xlab("Year of Publication")  +
+  theme(legend.position="none")
 
-### will ask KD about this one ###
-o_career2_model <- lme(o_career_degree_year ~ YEAR,
+# year model slope
+o_career_ed_model <- lme(o_career_1_degree ~ YEAR,
                       data = merged_df,
                       na.action = "na.omit",
-                      random = ~1|JOURNAL)
+                      random = ~1|ORCID)
 
-summary(o_career2_model)
+# variance model 
+var_o_career_ed_model <- lm(var_o_career_1_degree ~ year, 
+                          data = variance_df,
+                          na.action = "na.omit")
 ```

### 2022-05-06 04.manuscript.Rmd
add the stuff

@@
 library(papaja)
+library(knitr)
+library(cowplot)
+library(broom.mixed)
+current_year <- 2022
 ```
@@
 
-```{r, child = '03.data_analysis.Rmd', include = FALSE, results = FALSE, echo = FALSE}
+```{r bringinanalysis, include = FALSE, echo = FALSE}
+output <- knit_child("03.data_analysis.Rmd")
 ```
@@
 
-Research Question 1: What journals publish big team science papers?
+- Research Question 1: What journals publish big team science papers?
+- Research Question 2: What are the types of articles that are being published in big team science?
+- Research Question 3: Who is involved in big team science?
 
-Research Question 2: What are the types of articles that are being published in big team science?
-
-Research Question 3: Who is involved in big team science?
+For each of these research questions, we will examine the overall results of all big team research projects, and examine for change in result trends across years of publication.
 
@@
 
-### Journal Information
+### RQ1: Journal Information
 
@@
 
-### Article Information
+### RQ2: Article Information
 
 For each publication, we coded the list of keywords into broad labels for areas of social science (i.e., Social Psychology, Cognitive Psychology).
-WRITE MORE ABOUT NOT DOUBLE CODING ...
-DEFINE HOW EACH LABEL WAS DONE ...
-WHAT IS METASCIENCE GIVE OSC EXAMPLE
+In this section, we elected to code each article with only one main research area.
+Research is often cross-disciplinary, however, for simplicity, we applied one global label to each article that represented the perceived main area of study (based on what course this material might be taught in, the publication journal focus).
+The list of broad areas includes clinical, cognitive, developmental, educational, and social psychology.
+Last, we included a metascience category that covered articles that were detailing the science of science.
+The Open Science Collaboration [CITE] was included in this category because the aim of the paper was a focus on replication across multiple field types.
+Other metascience categories included papers that focused on research degrees of freedom, analysis choices, and types of samples.
 
-### Author Information
+### RQ3: Author Information
 
@@
 
-**Career Length**.
+**_Career Length_**.
 Career length for each author was defined using multiple variables to see if results from the two data sources would converge on similar answers.
@@
 
-**Employment**.
+**_Employment_**.
 Employment information was collected from self-entered ORCID data.
@@
 
-**Education**.
+**_Education_**.
 As with employment information, we also collected education information from self-entered ORCID data.
@@
 
-**Types of Publications**.
+**_Types of Publications_**.
 ORCID includes information about the type of publication pulled from either researcher entered data or Crossref.
@@
 
-**Publication Metrics**.
+**_Publication Metrics_**.
 We calculated total number of publications of any type from both Google Scholar and ORCID.
@@
 
-what are we gonna do to answer the research questions
+### RQ1: Journals
+
+Results for types of journals will include a summary of the journals that publish big-team science papers and an average of the 2-year and 5-year impact factors for the journals.
+
+### RQ2: Articles
+
+Results for types of articles will include a summary of the coded areas for each article, presented overall and across the years of publication.
+
+### RQ3: Authors. \
+
+We will use $\alpha$ < .05 for all analyses that involve hypothesis testing. We make no directional predictions.
+
+**_Career Length_**.
+For each of the three variables in career length (ORCID year of first pub, Scholar year of first pub, ORCID year of first degree), we will create a visualization of the trend and variance of researcher career length across publication years.
+To analyze trends over time, we will use the slope from a multilevel model (MLM) using the individual as a random intercept, career length as the dependent variable, and year of publication as the predictor variable.
+MLMs are regression models that control for the correlated error due to the repeated and nested nature of the data [CITE].
+In this model, each individual's starting career length is arbitrary, which we allow to vary with the random intercept by participant.
+A positive slope for year of publication would indicate increasing years of first publication (i.e., more younger scholars over time), while a negative slope would indicate older years of first publication (i.e., more older scholars over time).
+In order to show variance between individuals, we will report the variance component of the random intercept for individuals.
+Finally, to examine variance over time, we will calculate the standard deviation of the individual within each publication (i.e., one standard deviation for each article), and use a linear model with year predicting these standard deviations.
+This model is a traditional simultaneous regression, as averaging the variance by title eliminates the repeated measures variable (individuals).
+A positive slope would indicate increasing variance over time (i.e., more diversity in the career lengths of scholars), while a negative slope would indicate less variance and diversity in scholars over time.
+
+**_Employment_**.
+Employment information was collected from self-entered ORCID data.
+These values are open text, and therefore, we coded them into coherent categories for traditional educational (graduate student, post doctoral, lecturer),  tenure track (assistant, associate, full professor), and other roles (fellow, research assistant, researcher, head).
+Employment geopolitical region was also selected when available.
+
+**_Education_**.
+As with employment information, we also collected education information from self-entered ORCID data.
+These values were coded into general categories of bachelor, master, and doctoral degrees.
+The geopolitical region of the listed education was included when available.
+For analyses, both employment and education levels were grouped into United Nation regions.
+
+**_Types of Publications_**.
+ORCID includes information about the type of publication pulled from either researcher entered data or Crossref.
+We coded these publications into general categories including book, conference presentations, data-sets, journal articles, preprints, software, thesis, and other publications.
+
+**_Publication Metrics_**.
+We calculated total number of publications of any type from both Google Scholar and ORCID.
+We additionally pulled both the h-index and i-10 index from Google Scholar.
+The h-index represents the highest *h* number of publications that have at least *h* citations, while the i-10 index represents the number of publications with at least 10 citations.
 
@@
 
-## RQ1: Journal Information
+### RQ1: Journals
 
@@
 A complete list of journals can be found on our Open Science Framework page XXX.
+The average 2-year impact factor for official journal publications was `r format(mean(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)` (*SD* = `r format(sd(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)`) and the average 5-year impact factor was `r format(mean(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)` (*SD* = `r format(sd(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)`).
 
-put stuff in here about the format/structure to answering the research questions
+### RQ2: Articles
+
+Articles were primarily `r article_overall$Var1[1]` (`r format(article_overall$Percent[1], nsmall = 1, digits = 1)`%) and `r article_overall$Var1[2]` (`r format(article_overall$Percent[2], nsmall = 1, digits = 1)`%), followed by smaller categories for `r article_overall$Var1[3]` (`r format(article_overall$Percent[3], nsmall = 1, digits = 1)`%), `r article_overall$Var1[4]` (`r format(article_overall$Percent[4], nsmall = 1, digits = 1)`%), `r article_overall$Var1[5]` (`r format(article_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r article_overall$Var1[6]` (`r format(article_overall$Percent[6], nsmall = 1, digits = 1)`%).
+Here, we will talk about the figure below and how the trends occur across time.
+
+```{r figure1, echo = FALSE}
+article_time_plot
+```
+
+### RQ3: Authors. \
+
+```{r echo = FALSE}
+o_career_output <- tidy(o_career_model)
+var_o_career_output <- tidy(var_o_career_model)
+
+s_career_output <- tidy(s_career_model)
+var_s_career_output <- tidy(var_s_career_model)
+
+o_career_ed_output <- tidy(o_career_ed_model)
+var_o_career_ed_output <- tidy(var_o_career_ed_model)
+```
+
+**_Career Length_**.
+The average career length was `r format(round(current_year - mean(o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(current_year - o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`) for ORCID first publication year (i.e., current year minus year of first publication), *M* = `r format(round(current_year - mean(s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(current_year - s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`) for Scholar year of first publication, and *M* = `r format(round(current_year - mean(o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(current_year - o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`) for ORCID year of first degree.
+In each of the analyses, we use the actual year of first publication/education, as subtracting publication and using it as a predictor would create a perfect solution for each model.
+
+Next, we will talk about the results from three variables:
+
+1) ORCID year first publication:
+
+  - The slope for year of first publication was *b* = `r format(round(o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_output$df[2]`) = `r format(round(o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_output$p.value[2])`.
+  - The variance parameter was $SD$ = `r format(round(o_career_output$estimate[3], digits = 2), nsmall = 2)`. 
+  - The slope for variance across years was *b* = `r format(round(var_o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_model$df.residual`) = `r format(round(var_o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_output$p.value[2])`.
+
+2) Scholar year first publication:
+
+  - The slope for year of first publication was *b* = `r format(round(s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r s_career_output$df[2]`) = `r format(round(s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(s_career_output$p.value[2])`.
+  - The variance parameter was $SD$ = `r format(round(s_career_output$estimate[3], digits = 2), nsmall = 2)`. 
+  - The slope for variance across years was *b* = `r format(round(var_s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_s_career_model$df.residual`) = `r format(round(var_s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_s_career_output$p.value[2])`.
+
+3) ORCID year first degree:
+
+  - The slope for year of first degree was *b* = `r format(round(o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_ed_output$df[2]`) = `r format(round(o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_ed_output$p.value[2])`.
+  - The variance parameter was $SD$ = `r format(round(o_career_ed_output$estimate[3], digits = 2), nsmall = 2)`. 
+  - The slope for variance across years was *b* = `r format(round(var_o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_ed_model$df.residual`) = `r format(round(var_o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_ed_output$p.value[2])`.
+
+Then we will discuss how these results are represented in our graph (below). We will discuss any discrepancies in the results across the three different statistics.
+
+```{r figure2, echo = FALSE, warning = FALSE}
+plot_grid(o_career_graph + theme(text = element_text(size = 8), 
+                                 axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5)), 
+          s_career_graph + theme(text = element_text(size = 8), 
+                                 axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5)), 
+          o_career_graph_ed + theme(text = element_text(size = 8), 
+                                 axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5)))
+```
 
 # Discussion
+
+To be included after we have completed analyses.
 

### 2022-05-06 04.manuscript.tex
Update 04.manuscript.tex
Impact factors added to the manuscript
Update 04.manuscript.tex
minor changes to the impact factor part
see changesadd the stuff

@@
 
-\url{https://www.science.org/content/page/science-information-authors}
-
-\hypertarget{libraries}{%
-\subsection{Libraries}\label{libraries}}
-
-\hypertarget{import-bib-data}{%
-\subsection{Import Bib Data}\label{import-bib-data}}
-
-In this section, we are importing the bibtex file that includes all the papers we are going to use.
-
-Notes:
-
-\begin{itemize}
-\tightlist
-\item
-  We used the preprint manuscript for some papers because they had the entire author list, we will update their references manually for the final dataset.
-\item
-  We will have to manually add the names for several papers that used consortium authors.
-\item
-  The pre-reg of this document only examines a few authors/papers to ensure code can be run and develop workflow.
-\end{itemize}
-
-In this section, we will add the information for authors when they used a consortium authorship.
-
-\hypertarget{import-author-data}{%
-\subsection{Import Author Data}\label{import-author-data}}
-
-\hypertarget{hand-coded-variables}{%
-\subsection{Hand Coded Variables}\label{hand-coded-variables}}
-
-\hypertarget{journal-information}{%
-\subsection{Journal Information}\label{journal-information}}
-
-\hypertarget{create-summary-statistics}{%
-\subsection{Create Summary Statistics}\label{create-summary-statistics}}
-
-\hypertarget{merge-information-back}{%
-\subsection{Merge Information Back}\label{merge-information-back}}
-
-\hypertarget{person-analysis}{%
-\subsection{Person Analysis}\label{person-analysis}}
-
-\hypertarget{career-length}{%
-\subsubsection{Career Length}\label{career-length}}
-
-\hypertarget{employment-levels}{%
-\subsubsection{Employment Levels}\label{employment-levels}}
-
-\hypertarget{education-levels}{%
-\subsubsection{Education Levels}\label{education-levels}}
-
-\hypertarget{author-bean-counting}{%
-\subsubsection{Author Bean Counting}\label{author-bean-counting}}
-
-\hypertarget{more-authors-over-time}{%
-\subsubsection{More Authors Over Time?}\label{more-authors-over-time}}
-
-\hypertarget{where-are-authors}{%
-\subsubsection{Where are Authors?}\label{where-are-authors}}
-
-\hypertarget{credit-and-weird}{%
-\subsubsection{CRediT and WEIRD}\label{credit-and-weird}}
-
-\begin{itemize}
-\tightlist
-\item
-  credit contributions ? are we using de-weirding by using those people for translation and data collection only
-
-  \begin{itemize}
-  \tightlist
-  \item
-    grab major roles and see what the diversity is
-  \item
-    look at the first 10 people and the last author
-  \item
-    maybe compare to the other 10 groups (1/3rd, middle, last 1/3rd)
-  \end{itemize}
-\end{itemize}
-
-\hypertarget{journal-analysis}{%
-\subsection{Journal Analysis}\label{journal-analysis}}
-
-\hypertarget{which-journals}{%
-\subsubsection{Which Journals}\label{which-journals}}
-
-\begin{itemize}
-\tightlist
-\item
-  make sure preprints we are using also have real journal merged in
-\end{itemize}
-
-\hypertarget{article-topics-global-type}{%
-\subsubsection{Article Topics Global Type}\label{article-topics-global-type}}
-
-\begin{itemize}
-\tightlist
-\item
-  hand coded information on what the articles are about
-\item
-  Types of big team research (social, cognitive) using keywords
-\end{itemize}
-
-\hypertarget{article-types-over-time}{%
-\subsubsection{Article Types Over Time}\label{article-types-over-time}}
-
-\begin{itemize}
-\tightlist
-\item
-  Over time: are things becoming more varied
-\item
-  are the publications more varied over time
-\end{itemize}
-
 The introduction will go here. Here's an outline:
@@
 \begin{itemize}
-\tightlist
 \item
@@
   \ldots{} more tbd, brain isn't braining
+\item
+  Research Question 1: What journals publish big team science papers?
+\item
+  Research Question 2: What are the types of articles that are being published in big team science?
+\item
+  Research Question 3: Who is involved in big team science?
 \end{itemize}
+
+For each of these research questions, we will examine the overall results of all big team research projects, and examine for change in result trends across years of publication.
 
@@
 
-Using these criteria, we identified 70 articles for inclusion on this manuscript.
-The publication dates on these articles ranged from 2013 to 2022, and we used the pre-print last updated date as the publication date for those articles.
-Articles were most commonly published in Advances in Methods and Practices in Psychological Science (\emph{n} = 20), Behavior Research Methods (\emph{n} = 1), Collabra: Psychology (\emph{n} = 1), Computers in Human Behavior (\emph{n} = 1), and International Journal of Methods in Psychiatric Research (\emph{n} = 1).
-A complete list of journals can be found on our Open Science Framework page XXX.
-
 \hypertarget{data-curation}{%
@@
 
-\hypertarget{article-information}{%
-\subsubsection{Article Information}\label{article-information}}
+\hypertarget{rq1-journal-information}{%
+\subsubsection{RQ1: Journal Information}\label{rq1-journal-information}}
+
+Using these criteria, we identified 70 articles for inclusion on this manuscript.
+The publication dates on these articles ranged from 2013 to 2022, and we used the pre-print last updated date as the publication date for those articles.
+The current impact factor (i.e., 2022) for each journal was found on the journal page and included for journal statistics.
+
+\hypertarget{rq2-article-information}{%
+\subsubsection{RQ2: Article Information}\label{rq2-article-information}}
 
 For each publication, we coded the list of keywords into broad labels for areas of social science (i.e., Social Psychology, Cognitive Psychology).
-The current impact factor (i.e., 2022) for each journal was found on the journal page and included for journal statistics.
+In this section, we elected to code each article with only one main research area.
+Research is often cross-disciplinary, however, for simplicity, we applied one global label to each article that represented the perceived main area of study (based on what course this material might be taught in, the publication journal focus).
+The list of broad areas includes clinical, cognitive, developmental, educational, and social psychology.
+Last, we included a metascience category that covered articles that were detailing the science of science.
+The Open Science Collaboration {[}CITE{]} was included in this category because the aim of the paper was a focus on replication across multiple field types.
+Other metascience categories included papers that focused on research degrees of freedom, analysis choices, and types of samples.
 
-\hypertarget{author-information}{%
-\subsubsection{Author Information}\label{author-information}}
+\hypertarget{rq3-author-information}{%
+\subsubsection{RQ3: Author Information}\label{rq3-author-information}}
 
@@
 
-\textbf{Career Length}.
+\textbf{\emph{Career Length}}.
 Career length for each author was defined using multiple variables to see if results from the two data sources would converge on similar answers.
@@
 
-\textbf{Employment}.
+\textbf{\emph{Employment}}.
 Employment information was collected from self-entered ORCID data.
@@
 
-\textbf{Education}.
+\textbf{\emph{Education}}.
 As with employment information, we also collected education information from self-entered ORCID data.
@@
 
-\textbf{Types of Publications}.
+\textbf{\emph{Types of Publications}}.
 ORCID includes information about the type of publication pulled from either researcher entered data or Crossref.
@@
 
-\textbf{Publication Metrics}.
+\textbf{\emph{Publication Metrics}}.
 We calculated total number of publications of any type from both Google Scholar and ORCID.
@@
 
-what are we gonna do to answer the research questions
+\hypertarget{rq1-journals}{%
+\subsubsection{RQ1: Journals}\label{rq1-journals}}
+
+Results for types of journals will include a summary of the journals that publish big-team science papers and an average of the 2-year and 5-year impact factors for the journals.
+
+\hypertarget{rq2-articles}{%
+\subsubsection{RQ2: Articles}\label{rq2-articles}}
+
+Results for types of articles will include a summary of the coded areas for each article, presented overall and across the years of publication.
+
+\hypertarget{rq3-authors.}{%
+\subsubsection{\texorpdfstring{RQ3: Authors.\\
+}{RQ3: Authors. }}\label{rq3-authors.}}
+
+We will use \(\alpha\) \textless{} .05 for all analyses that involve hypothesis testing. We make no directional predictions.
+
+\textbf{\emph{Career Length}}.
+For each of the three variables in career length (ORCID year of first pub, Scholar year of first pub, ORCID year of first degree), we will create a visualization of the trend and variance of researcher career length across publication years.
+To analyze trends over time, we will use the slope from a multilevel model (MLM) using the individual as a random intercept, career length as the dependent variable, and year of publication as the predictor variable.
+MLMs are regression models that control for the correlated error due to the repeated and nested nature of the data {[}CITE{]}.
+In this model, each individual's starting career length is arbitrary, which we allow to vary with the random intercept by participant.
+A positive slope for year of publication would indicate increasing years of first publication (i.e., more younger scholars over time), while a negative slope would indicate older years of first publication (i.e., more older scholars over time).
+In order to show variance between individuals, we will report the variance component of the random intercept for individuals.
+Finally, to examine variance over time, we will calculate the standard deviation of the individual within each publication (i.e., one standard deviation for each article), and use a linear model with year predicting these standard deviations.
+This model is a traditional simultaneous regression, as averaging the variance by title eliminates the repeated measures variable (individuals).
+A positive slope would indicate increasing variance over time (i.e., more diversity in the career lengths of scholars), while a negative slope would indicate less variance and diversity in scholars over time.
+
+\textbf{\emph{Employment}}.
+Employment information was collected from self-entered ORCID data.
+These values are open text, and therefore, we coded them into coherent categories for traditional educational (graduate student, post doctoral, lecturer), tenure track (assistant, associate, full professor), and other roles (fellow, research assistant, researcher, head).
+Employment geopolitical region was also selected when available.
+
+\textbf{\emph{Education}}.
+As with employment information, we also collected education information from self-entered ORCID data.
+These values were coded into general categories of bachelor, master, and doctoral degrees.
+The geopolitical region of the listed education was included when available.
+For analyses, both employment and education levels were grouped into United Nation regions.
+
+\textbf{\emph{Types of Publications}}.
+ORCID includes information about the type of publication pulled from either researcher entered data or Crossref.
+We coded these publications into general categories including book, conference presentations, data-sets, journal articles, preprints, software, thesis, and other publications.
+
+\textbf{\emph{Publication Metrics}}.
+We calculated total number of publications of any type from both Google Scholar and ORCID.
+We additionally pulled both the h-index and i-10 index from Google Scholar.
+The h-index represents the highest \emph{h} number of publications that have at least \emph{h} citations, while the i-10 index represents the number of publications with at least 10 citations.
 
@@
 
-put stuff in here about the format/structure to answering the research questions
+\hypertarget{rq1-journals-1}{%
+\subsubsection{RQ1: Journals}\label{rq1-journals-1}}
+
+Articles were most commonly published in Advances in Methods and Practices in Psychological Science (\emph{n} = 20), Pre-Print (\emph{n} = 17), Perspectives on Psychological Science (\emph{n} = 7), PLOS ONE (\emph{n} = 4), and Nature Human Behaviour (\emph{n} = 3).
+A complete list of journals can be found on our Open Science Framework page XXX.
+The average 2-year impact factor for official journal publications was 8.22 (\emph{SD} = 10.67) and the average 5-year impact factor was 6.41 (\emph{SD} = 4.42).
+
+\hypertarget{rq2-articles-1}{%
+\subsubsection{RQ2: Articles}\label{rq2-articles-1}}
+
+Articles were primarily Social (41.4\%) and Cognitive (31.4\%), followed by smaller categories for Metascience (17.1\%), Clinical (4.3\%), Developmental (4.3\%), and Educational (1.4\%).
+Here, we will talk about the figure below and how the trends occur across time.
+
+\includegraphics{04.manuscript_files/figure-latex/figure1-1.pdf}
+
+\hypertarget{rq3-authors.-1}{%
+\subsubsection{\texorpdfstring{RQ3: Authors.\\
+}{RQ3: Authors. }}\label{rq3-authors.-1}}
+
+\textbf{\emph{Career Length}}.
+The average career length was 11.97 (\emph{SD} = 7.95) for ORCID first publication year (i.e., current year minus year of first publication), \emph{M} = 13.12 (\emph{SD} = 8.74) for Scholar year of first publication, and \emph{M} = 13.54 (\emph{SD} = 7.77) for ORCID year of first degree.
+In each of the analyses, we use the actual year of first publication/education, as subtracting publication and using it as a predictor would create a perfect solution for each model.
+
+Next, we will talk about the results from three variables:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  ORCID year first publication:
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(53) = 1.71, \emph{p} = .092.
+\item
+  The variance parameter was \(SD\) = 7.99.
+\item
+  The slope for variance across years was \emph{b} = 0.01, \emph{SE} = 0.48, \emph{t}(23) = 0.02, \emph{p} = .983.
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Scholar year first publication:
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(15) = 1.59, \emph{p} = .132.
+\item
+  The variance parameter was \(SD\) = 8.88.
+\item
+  The slope for variance across years was \emph{b} = 0.16, \emph{SE} = 0.61, \emph{t}(2) = 0.26, \emph{p} = .821.
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  ORCID year first degree:
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  The slope for year of first degree was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(35) = 5.14, \emph{p} = \textless{} .001.
+\item
+  The variance parameter was \(SD\) = 7.77.
+\item
+  The slope for variance across years was \emph{b} = 0.03, \emph{SE} = 0.82, \emph{t}(14) = 0.04, \emph{p} = .971.
+\end{itemize}
+
+Then we will discuss how these results are represented in our graph (below). We will discuss any discrepancies in the results across the three different statistics.
+
+\includegraphics{04.manuscript_files/figure-latex/figure2-1.pdf}
 
@@
 \section{Discussion}\label{discussion}}
+
+To be included after we have completed analyses.
 

### 2022-05-06 04.manuscript.tex
install stuff!
install stuff!

@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
 \makeatother
-\shorttitle{Big Team Science}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{big team, science, authorship, credit\newline\indent Word count: X}
@@
 
+\shorttitle{Big Team Science}
+
 \authornote{
@@
 
-\abstract{
+\abstract{%
 One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
@@
 \item
-  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(53) = 1.71, \emph{p} = .092.
+  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(53) = 0.93, \emph{p} = .358.
 \item
-  The variance parameter was \(SD\) = 7.99.
+  The variance parameter was \(SD\) = 8.02.
 \item
-  The slope for variance across years was \emph{b} = 0.01, \emph{SE} = 0.48, \emph{t}(23) = 0.02, \emph{p} = .983.
+  The slope for variance across years was \emph{b} = 0.01, \emph{SE} = 0.47, \emph{t}(23) = 0.02, \emph{p} = .984.
 \end{itemize}
@@
 \item
-  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(15) = 1.59, \emph{p} = .132.
+  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(15) = 1.04, \emph{p} = .315.
 \item
@@
 \item
-  The slope for year of first degree was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(35) = 5.14, \emph{p} = \textless{} .001.
+  The slope for year of first degree was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(35) = 2.93, \emph{p} = .006.
 \item
-  The variance parameter was \(SD\) = 7.77.
+  The variance parameter was \(SD\) = 7.86.
 \item
-  The slope for variance across years was \emph{b} = 0.03, \emph{SE} = 0.82, \emph{t}(14) = 0.04, \emph{p} = .971.
+  The slope for variance across years was \emph{b} = 0.02, \emph{SE} = 0.82, \emph{t}(14) = 0.02, \emph{p} = .982.
 \end{itemize}

### 2022-05-12 04.manuscript.Rmd
updates from last week

@@
 **_Employment_**. 
-Employment information was collected from self-entered ORCID data.
-These values are open text, and therefore, we coded them into coherent categories for traditional educational (graduate student, post doctoral, lecturer),  tenure track (assistant, associate, full professor), and other roles (fellow, research assistant, researcher, head).
-Employment geopolitical region was also selected when available.
+- print out overall
+- print out over time 
+- comment on if all normal academic
 
 **_Education_**. 
-As with employment information, we also collected education information from self-entered ORCID data.
-These values were coded into general categories of bachelor, master, and doctoral degrees.
-The geopolitical region of the listed education was included when available.
-For analyses, both employment and education levels were grouped into United Nation regions.
+- print out overall
+- print out over time
 
 **_Types of Publications_**. 
-ORCID includes information about the type of publication pulled from either researcher entered data or Crossref.
-We coded these publications into general categories including book, conference presentations, data-sets, journal articles, preprints, software, thesis, and other publications.
+- print out overall
+- print out over time 
+- open science question
 
 **_Publication Metrics_**. 
-We calculated total number of publications of any type from both Google Scholar and ORCID.
-We additionally pulled both the h-index and i-10 index from Google Scholar.
-The h-index represents the highest *h* number of publications that have at least *h* citations, while the i-10 index represents the number of publications with at least 10 citations.
+- means and SDs for i10 and hindex information, and number of publications 
+- same analyses as career length - slope of number of publications and variance of number of publications 
+- slope up means people who are publishing more are more represented in the researchers
+- slope down means more people with less publications
+- answer are we giving opportunities to people who need the bean counting
+
+**_Geopolitical Regions_**. 
+- overall map of where people get their education
+- overall map of where people are working 
+- is this diversifying over time (more countries as years go up)
+- then the weird analysis to answer about diversifying authors
 
@@
   - The slope for year of first publication was *b* = `r format(round(o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_output$df[2]`) = `r format(round(o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_output$p.value[2])`.
-  - The variance parameter was $SD$ = `r format(round(o_career_output$estimate[3], digits = 2), nsmall = 2)`. 
+  - The variance parameter was *SD* = `r format(round(o_career_output$estimate[3], digits = 2), nsmall = 2)`. 
   - The slope for variance across years was *b* = `r format(round(var_o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_model$df.residual`) = `r format(round(var_o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_output$p.value[2])`.
@@
   - The slope for year of first publication was *b* = `r format(round(s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r s_career_output$df[2]`) = `r format(round(s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(s_career_output$p.value[2])`.
-  - The variance parameter was $SD$ = `r format(round(s_career_output$estimate[3], digits = 2), nsmall = 2)`. 
+  - The variance parameter was *SD* = `r format(round(s_career_output$estimate[3], digits = 2), nsmall = 2)`. 
   - The slope for variance across years was *b* = `r format(round(var_s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_s_career_model$df.residual`) = `r format(round(var_s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_s_career_output$p.value[2])`.
@@
   - The slope for year of first degree was *b* = `r format(round(o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_ed_output$df[2]`) = `r format(round(o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_ed_output$p.value[2])`.
-  - The variance parameter was $SD$ = `r format(round(o_career_ed_output$estimate[3], digits = 2), nsmall = 2)`. 
+  - The variance parameter was *SD* = `r format(round(o_career_ed_output$estimate[3], digits = 2), nsmall = 2)`. 
   - The slope for variance across years was *b* = `r format(round(var_o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_ed_model$df.residual`) = `r format(round(var_o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_ed_output$p.value[2])`.

### 2022-05-13 03.data_analysis.Rmd
updates from last week
making pics

@@
 library(RColorBrewer)
+current_year <- 2022
 #### fix sau chins paper #### https://osf.io/gq92w/ 
@@
 o_job$our_job <- gsub(".*educator.*|teaching assistant", "lecturer", o_job$our_job)
-o_job$our_job <- gsub(".*full.*professor.*", "full professor", o_job$our_job)
+o_job$our_job <- gsub(".*full.*professor.*", "professor", o_job$our_job)
 o_job$our_job <- gsub(".*head.*", "head", o_job$our_job)
-o_job$our_job <- gsub("centennial professor|prof\\.|professor of cognitive analytics|proffessor.*|^temporal proffesor.*", "full professor", o_job$our_job)
+o_job$our_job <- gsub("centennial professor|prof\\.|professor of cognitive analytics|proffessor.*|^temporal proffesor.*", "professor", o_job$our_job)
 table(o_job$our_job)
@@
 
+# for jobs fill in "current" or end date
+# Find users with blanks
+employ_fix <- o_job %>% 
+  filter(is.na(employment_summary_end_date_year_value)) %>% 
+  select(ORCID, employment_summary_start_date_year_value, employment_summary_role_title) %>% 
+  filter(!is.na(employment_summary_role_title)) %>% 
+  pull(ORCID)
+
+for (i in 1:length(employ_fix)){
+  # For each one find the number of rows 
+  temp_fix <- o_job %>% 
+  #filter(is.na(employment_summary_end_date_year_value)) %>% 
+  select(ORCID, employment_summary_start_date_year_value,
+         employment_summary_end_date_year_value,
+         employment_summary_role_title) %>% 
+    filter(ORCID == employ_fix[i]) %>% 
+    filter(!is.na(employment_summary_role_title))
+
+  # if only one row, make it now
+  if (nrow(temp_fix) == 1){
+    o_job$employment_summary_end_date_year_value[
+      o_job$ORCID == employ_fix[i] &
+      !is.na(o_job$employment_summary_role_title)
+      ] <- current_year
+  }
+
+  if (nrow(temp_fix) > 1){
+
+    lead_values <- c(current_year,
+                     o_job$employment_summary_start_date_year_value[
+      o_job$ORCID == employ_fix[i] &
+      !is.na(o_job$employment_summary_role_title)
+    ])
+    lead_values <- lead_values[-length(lead_values)]
+
+    # Use the lead or other end function 
+    for (q in 1:length(lead_values)){
+
+      if (is.na(o_job$employment_summary_end_date_year_value[
+        o_job$ORCID == employ_fix[i] &
+        !is.na(o_job$employment_summary_role_title)
+      ][q])) {
+
+      o_job$employment_summary_end_date_year_value[
+        o_job$ORCID == employ_fix[i] &
+        !is.na(o_job$employment_summary_role_title)
+      ][q] <- lead_values[q]
+
+      } # close lead if only na
+
+    } # close lead values loop
+
+  } # close if more than one row
+
+} # close for all users
+
+# check when values don't make sense
+o_job %>% 
+  filter(employment_summary_end_date_year_value < employment_summary_start_date_year_value)
+
+# make employment by year 
 o_ed_explode <- data.frame()
 o_job_explode <- data.frame()
-
-####ERIN YOU STILL HAVE TO DO THIS####
-# for jobs fill in "current" or end date
-# Find users with blanks
-# For each one find the number of rows 
-# If 1 then make 2022
-# If more than 1 
-# Use the lead or other end function 
-o_job %>% filter(is.na(employment_summary_end_date_year_value)) %>% 
-  select(ORCID, employment_summary_start_date_year_value, employment_summary_role_title)
 
@@
     filter(!duplicated(ORCID)) %>% 
-    select(ORCID, education_summary_role_title, 
+    select(ORCID, education_summary_role_title, our_ed,
            education_summary_organization_address_country) %>% 
@@
     filter(!duplicated(ORCID)) %>% 
-    select(ORCID, employment_summary_role_title, 
+    select(ORCID, employment_summary_role_title, our_job,
            employment_summary_organization_address_country) %>% 
@@
 ```{r}
-# hand code these into categories that make sense
-table(o_job$employment_summary_role_title)
-table(merged_df$employment_summary_role_title)
+merged_df$our_job <- factor(merged_df$our_job, 
+                            levels = c("research assistant", 
+                                       "post doc", 
+                                       "researcher", 
+                                       "lecturer", 
+                                       "fellow",
+                                       "assistant professor",
+                                       "associate professor", 
+                                       "professor", "head"),
+                            labels = tools::toTitleCase(c("research assistant", 
+                                       "post doc", 
+                                       "researcher", 
+                                       "lecturer", 
+                                       "fellow",
+                                       "assistant professor",
+                                       "associate professor", 
+                                       "professor", "head")))
 
-# table by year 
-# graph by year 
+employment_overall <- as.data.frame(table(merged_df$our_job)) %>% 
+  arrange(desc(Freq)) %>% 
+  mutate(Percent = Freq / sum(Freq) * 100)
+employment_time <- as.data.frame(table(merged_df$our_job, merged_df$graph_year))
+
+employment_time_plot <- ggplot(employment_time, aes(Var2, Freq, fill = Var1)) +
+  geom_bar(position="stack", stat="identity") + 
+  theme_classic() + 
+  xlab("Publication Year") + 
+  ylab("Number of Researchers") + 
+  scale_fill_brewer(palette = "RdBu", name = "Employment Category")
 ```
@@
 ```{r}
-# hand code these into categories that make sense
-table(merged_df$education_summary_role_title)
+merged_df$our_ed <- factor(merged_df$our_ed, 
+                            levels = c("bachelor", 
+                                       "masters", 
+                                       "doctor"),
+                            labels = tools::toTitleCase(c("bachelor", 
+                                       "masters", 
+                                       "doctor")))
 
-# consider coding as 1, 2, 3, 4, etc. 
-# table by year 
-# graph by year 
+education_overall <- as.data.frame(table(merged_df$our_ed)) %>% 
+  arrange(desc(Freq)) %>% 
+  mutate(Percent = Freq / sum(Freq) * 100)
+education_time <- as.data.frame(table(merged_df$our_ed, merged_df$graph_year))
+
+edu_colors <- brewer.pal(6, "RdBu")[c(1,3,6)]
+
+education_time_plot <- ggplot(education_time, aes(Var2, Freq, fill = Var1)) +
+  geom_bar(position="stack", stat="identity") + 
+  theme_classic() + 
+  xlab("Publication Year") + 
+  ylab("Number of Researchers") + 
+  scale_fill_manual(values = edu_colors, 
+                    name = "Education Category")
 ```
 
-### Author Bean Counting
+### Types of Publications
 
@@
 ```{r}
+# un regions grouping do this above 
 # grab first X authors and last author

### 2022-05-13 04.manuscript.Rmd
making pics

@@
 
-**_Employment_**. 
-- print out overall
-- print out over time 
-- comment on if all normal academic
+**_Employment_**. We will summarize the general employment categories of individuals at the time of publication, along with a summary for change over time.
 
-**_Education_**. 
-- print out overall
-- print out over time
+**_Education_**. We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.
 
 **_Types of Publications_**.
-- print out overall
-- print out over time 
-- open science question
+We will summarize the coded types of publications for individuals and demonstrate the changes in types of publications over time visually.
+We will comment if more "open" type publications appear to be published, such as data-sets, preprints, and software.
 
@@
 
+**_Employment_**.
+Overall, individuals **at the time of publication** in big team science publications are  `r employment_overall$Var1[1]` (`r format(employment_overall$Percent[1], nsmall = 1, digits = 1)`%) and `r employment_overall$Var1[2]` (`r format(employment_overall$Percent[2], nsmall = 1, digits = 1)`%), followed by smaller categories for `r employment_overall$Var1[3]` (`r format(employment_overall$Percent[3], nsmall = 1, digits = 1)`%), `r employment_overall$Var1[4]` (`r format(employment_overall$Percent[4], nsmall = 1, digits = 1)`%), `r employment_overall$Var1[5]` (`r format(employment_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r employment_overall$Var1[6]` (`r format(employment_overall$Percent[6], nsmall = 1, digits = 1)`%).
+Here, we will talk about the figure below and how the trends occur across time.
+We will also comment on the number of jobs that would be considered "non-academic".
+
+```{r figure3, echo = FALSE, warning = FALSE}
+employment_time_plot
+```
+
+**_Education_**.
+Overall, individuals **at the time of publication** in big team science publications are  `r education_overall$Var1[1]` (`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%), `r education_overall$Var1[2]` (`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and`r education_overall$Var1[3]` (`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%).
+Here, we will talk about the figure below and how the trends occur across time.
+
+```{r figure4, echo = FALSE, warning = FALSE}
+education_time_plot
+```
+
+**_Types of Publications_**. 
+- print out overall
+- print out over time 
+- open science question
+
+**_Publication Metrics_**. 
+- means and SDs for i10 and hindex information, and number of publications 
+- same analyses as career length - slope of number of publications and variance of number of publications 
+- slope up means people who are publishing more are more represented in the researchers
+- slope down means more people with less publications
+- answer are we giving opportunities to people who need the bean counting
+
+**_Geopolitical Regions_**. 
+- overall map of where people get their education
+- overall map of where people are working 
+- is this diversifying over time (more countries as years go up)
+- then the weird analysis to answer about diversifying authors
+
 # Discussion

### 2022-05-13 04.manuscript.tex
making pics

--- 2022-05-06 04.manuscript.tex
@@
 
-\textbf{\emph{Employment}}.
-Employment information was collected from self-entered ORCID data.
-These values are open text, and therefore, we coded them into coherent categories for traditional educational (graduate student, post doctoral, lecturer), tenure track (assistant, associate, full professor), and other roles (fellow, research assistant, researcher, head).
-Employment geopolitical region was also selected when available.
+\textbf{\emph{Employment}}. We will summarize the general employment categories of individuals at the time of publication, along with a summary for change over time.
 
-\textbf{\emph{Education}}.
-As with employment information, we also collected education information from self-entered ORCID data.
-These values were coded into general categories of bachelor, master, and doctoral degrees.
-The geopolitical region of the listed education was included when available.
-For analyses, both employment and education levels were grouped into United Nation regions.
+\textbf{\emph{Education}}. We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.
 
 \textbf{\emph{Types of Publications}}.
-ORCID includes information about the type of publication pulled from either researcher entered data or Crossref.
-We coded these publications into general categories including book, conference presentations, data-sets, journal articles, preprints, software, thesis, and other publications.
+- print out overall
+- print out over time
+- open science question
 
 \textbf{\emph{Publication Metrics}}.
-We calculated total number of publications of any type from both Google Scholar and ORCID.
-We additionally pulled both the h-index and i-10 index from Google Scholar.
-The h-index represents the highest \emph{h} number of publications that have at least \emph{h} citations, while the i-10 index represents the number of publications with at least 10 citations.
+- means and SDs for i10 and hindex information, and number of publications
+- same analyses as career length - slope of number of publications and variance of number of publications
+- slope up means people who are publishing more are more represented in the researchers
+- slope down means more people with less publications
+- answer are we giving opportunities to people who need the bean counting
+
+\textbf{\emph{Geopolitical Regions}}.
+- overall map of where people get their education
+- overall map of where people are working
+- is this diversifying over time (more countries as years go up)
+- then the weird analysis to answer about diversifying authors
 
@@
 \item
-  The variance parameter was \(SD\) = 7.99.
+  The variance parameter was \emph{SD} = 7.99.
 \item
@@
 \item
-  The variance parameter was \(SD\) = 8.88.
+  The variance parameter was \emph{SD} = 8.88.
 \item
@@
 \item
-  The variance parameter was \(SD\) = 7.77.
+  The variance parameter was \emph{SD} = 7.77.
 \item
@@
 \includegraphics{04.manuscript_files/figure-latex/figure2-1.pdf}
+
+\textbf{\emph{Employment}}.
+Overall, individuals \textbf{at the time of publication} in big team science publications are Professor (28.8\%) and Assistant Professor (24.7\%), followed by smaller categories for Lecturer (16.4\%), Associate Professor ( 9.6\%), Post Doc (8.2\%), and Head (6.8\%).
+Here, we will talk about the figure below and how the trends occur across time.
+We will also comment on the number of jobs that would be considered ``non-academic.''
+
+\includegraphics{04.manuscript_files/figure-latex/figure3-1.pdf}
+
+\textbf{\emph{Education}}.
+Overall, individuals \textbf{at the time of publication} in big team science publications are Doctor (79.7\%), Masters (16.5\%), andBachelor (3.8\%).
+Here, we will talk about the figure below and how the trends occur across time.
+
+\includegraphics{04.manuscript_files/figure-latex/figure4-1.pdf}
+
+\textbf{\emph{Types of Publications}}.
+- print out overall
+- print out over time
+- open science question
+
+\textbf{\emph{Publication Metrics}}.
+- means and SDs for i10 and hindex information, and number of publications
+- same analyses as career length - slope of number of publications and variance of number of publications
+- slope up means people who are publishing more are more represented in the researchers
+- slope down means more people with less publications
+- answer are we giving opportunities to people who need the bean counting
+
+\textbf{\emph{Geopolitical Regions}}.
+- overall map of where people get their education
+- overall map of where people are working
+- is this diversifying over time (more countries as years go up)
+- then the weird analysis to answer about diversifying authors
 

### 2022-06-03 03.data_analysis.Rmd
pushing old updates

@@
 library(RColorBrewer)
+library(countrycode)
 current_year <- 2022
@@
 JIF <- import("jif.xlsx")
+```
+
+- make sure preprints we are using also have real journal merged in
+
+```{r}
+journal_count <- bibs %>% group_by(JOURNAL) %>% 
+  summarize(freq = n()) %>% 
+  arrange(desc(freq))
+
+journal_count$JOURNAL[is.na(journal_count$JOURNAL)] <- "Pre-Print"
 ```
@@
 
+```{r}
+# total count of authors
+author_count <- 
+  merged_df %>% 
+  group_by(TITLE) %>% 
+  summarize(author_count = n(),
+            year = mean(YEAR))
+```
+
 ### Graph Year Fix
@@
             var_s_career_1_pub = sd(s_career_1_pub, na.rm = T), 
-            var_o_career_1_degree = sd(o_career_1_degree, na.rm = T))
+            var_o_career_1_degree = sd(o_career_1_degree, na.rm = T),
+            var_o_total = sd(o_total_pub, na.rm = T), 
+            var_s_total = sd(s_total_pub, na.rm = T))
 
@@
 ```{r}
-# what do these people publish overall
-table(o_works$our_type)
+publication_overall <- as.data.frame(table(o_works$our_type)) %>% 
+  arrange(desc(Freq)) %>% 
+  mutate(Percent = Freq / sum(Freq) * 100)
+```
 
-# publication rates ORCID
-ggplot(merged_df, aes(graph_year, o_total_pub)) + 
+### Publication Metrics
+
+```{r}
+# total pubs orcid ----
+
+# graph 
+o_total_graph <- ggplot(merged_df, aes(graph_year, o_total_pub)) + 
   geom_violin() + 
-  geom_jitter(height = 0, width = 0.1) + 
+  geom_jitter(height = 0, width = 0.2, aes(color = TITLE_color)) + 
   theme_classic() + 
-  ylab("Total Publications (ORCID)") + 
-  xlab("Year of Publication")
+  ylab("Total Number of Publications (ORCID)") + 
+  xlab("Year of Publication") +
+  theme(legend.position="none")
 
-### will ask KD about this one ###
+# year model slope 
 o_total_model <- lme(o_total_pub ~ YEAR,
@@
                       na.action = "na.omit",
-                      random = ~1|JOURNAL)
+                      random = ~1|scholar)
 
-summary(o_total_model)
+# variance  model 
+var_o_total_model <- lm(var_o_total ~ year, 
+                          data = variance_df,
+                          na.action = "na.omit")
+```
 
-# publication rates scholar
-ggplot(merged_df, aes(graph_year, s_total_pub)) + 
+```{r}
+# total pubs scholar ----
+
+# graph 
+s_total_graph <- ggplot(merged_df, aes(graph_year, s_total_pub)) + 
   geom_violin() + 
-  geom_jitter(height = 0, width = 0.1) + 
+  geom_jitter(height = 0, width = 0.2, aes(color = TITLE_color)) + 
   theme_classic() + 
-  ylab("Total Publications (Scholar)") + 
-  xlab("Year of Publication")
+  ylab("Total Number of Publications (ORCID)") + 
+  xlab("Year of Publication") +
+  theme(legend.position="none")
 
-### will ask KD about this one ###
+# year model slope 
 s_total_model <- lme(s_total_pub ~ YEAR,
@@
                       na.action = "na.omit",
-                      random = ~1|JOURNAL)
+                      random = ~1|scholar)
 
-summary(s_total_model)
-
-# h index rates scholar
-ggplot(merged_df, aes(graph_year, h_index)) + 
-  geom_violin() + 
-  geom_jitter(height = 0, width = 0.1) + 
-  theme_classic() + 
-  ylab("H Index") + 
-  xlab("Year of Publication")
-
-### will ask KD about this one ###
-h_index_model <- lme(h_index ~ YEAR,
-                      data = merged_df,
-                      na.action = "na.omit",
-                      random = ~1|JOURNAL)
-
-summary(h_index_model)
-
-# i 10 rates scholar
-ggplot(merged_df, aes(graph_year, i10_index)) + 
-  geom_violin() + 
-  geom_jitter(height = 0, width = 0.1) + 
-  theme_classic() + 
-  ylab("H Index") + 
-  xlab("Year of Publication")
-
-### will ask KD about this one ###
-i_index_model <- lme(i10_index ~ YEAR,
-                      data = merged_df,
-                      na.action = "na.omit",
-                      random = ~1|JOURNAL)
-
-summary(i_index_model)
+# variance  model 
+var_s_total_model <- lm(var_s_total ~ year, 
+                          data = variance_df,
+                          na.action = "na.omit")
 ```
 
-### More Authors Over Time?
+### Geopolitical Regions
 
 ```{r}
-author_count <- 
-  merged_df %>% 
-  group_by(TITLE) %>% 
-  summarize(author_count = n(),
-            year = mean(YEAR))
+# map of degree representation
 
-cor(author_count$author_count, author_count$year)
-
-ggplot(author_count, aes(factor(year), author_count)) +
-  theme_classic() + 
-  geom_point() + 
-  xlab("Year of Publication") + 
-  ylab("Number of Authors")
-```
-
-### Where are Authors?
-
-```{r}
-# where did they get their degree
-merged_df %>% 
-  filter(!duplicated(ORCID)) %>% 
-  count(education_summary_organization_address_country)
-
-table(merged_df$education_summary_organization_address_country,
-      merged_df$YEAR)
+# map of last job representation
 
 # how many different countries does each year have and is that getting bigger
+country_summary <- merged_df %>% 
+  group_by(TITLE) %>% 
+  summarize(year = mean(YEAR), 
+            edu_country = length(table(education_summary_organization_address_country)),
+            job_country = length(table(employment_summary_organization_address_country)))
 
-# where do they work
-merged_df %>% 
-  filter(!duplicated(ORCID)) %>% 
-  count(employment_summary_organization_address_country)
+# totals by edu
+edu_country_model <- lm(edu_country ~ year, 
+                          data = country_summary,
+                          na.action = "na.omit")
 
-table(merged_df$employment_summary_organization_address_country,
-      merged_df$YEAR)
+# totals by job
+job_country_model <- lm(job_country ~ year, 
+                          data = country_summary,
+                          na.action = "na.omit")
+
 ```
@@
 ```{r}
-# un regions grouping do this above 
+# transform to un regions
+merged_df$un_region_ed <- 
+  countrycode(
+    sourcevar = merged_df$education_summary_organization_address_country,
+    origin = "iso2c",
+    destination = "un.regionsub.name")
+
+merged_df$un_region_job <- 
+  countrycode(
+    sourcevar = merged_df$employment_summary_organization_address_country,
+    origin = "iso2c",
+    destination = "un.regionsub.name")
+
 # grab first X authors and last author
@@
 
-# group into UN regions 
 ```
 
-- credit contributions ? are we using de-weirding by using those people for translation and data collection only 
-  - grab major roles and see what the diversity is 
-  - look at the first 10 people and the last author 
-  - maybe compare to the other 10 groups (1/3rd, middle, last 1/3rd)
-
-## Journal Analysis
-
-### Which Journals
-
-- make sure preprints we are using also have real journal merged in
-
-```{r}
-journal_count <- bibs %>% group_by(JOURNAL) %>% 
-  summarize(freq = n()) %>% 
-  arrange(desc(freq))
-
-journal_count$JOURNAL[is.na(journal_count$JOURNAL)] <- "Pre-Print"
-```
-
-### Article Topics Global Type
-
-- hand coded information on what the articles are about 
-- Types of big team research (social, cognitive) using keywords
-
-```{r}
-# table of hand coded type
-```
-
-### Article Types Over Time
-
-- Over time: are things becoming more varied
-- are the publications more varied over time
-
-```{r}
-# table of hand coded type by year 
-```
+- grab the first X authors and the last authors
+- compare to random samples of other authors of the same size chunk 
+- calculate the probability of having *anyone* from a un region in that chunk
+- make two graphs one of probability of being in the first group, one of probability of being in second group

### 2022-06-03 04.manuscript.Rmd
pushing old updates

@@
 
-**_Types of Publications_**.
-We will summarize the coded types of publications for individuals and demonstrate the changes in types of publications over time visually.
-We will comment if more "open" type publications appear to be published, such as data-sets, preprints, and software.
+**_Types of Publications_**. We will summarize the coded types of publications for individuals.
 
 **_Publication Metrics_**.
-- means and SDs for i10 and hindex information, and number of publications 
-- same analyses as career length - slope of number of publications and variance of number of publications 
-- slope up means people who are publishing more are more represented in the researchers
-- slope down means more people with less publications
-- answer are we giving opportunities to people who need the bean counting
+We will report descriptive statistics on the total number of publications, i10 index, and h-index for individuals overall.
+Next, we will use the same analyses described in the career length section to analyze trends over time.
+An increasing slope over time indicates that individuals who are publishing more are more represented in big-team science over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
+A positive slope for variance indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
+While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.
 
@@
 **_Education_**.
-Overall, individuals **at the time of publication** in big team science publications are  `r education_overall$Var1[1]` (`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%), `r education_overall$Var1[2]` (`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and`r education_overall$Var1[3]` (`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%).
+Overall, individuals **at the time of publication** in big team science publications are  `r education_overall$Var1[1]` (`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%), `r education_overall$Var1[2]` (`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and `r education_overall$Var1[3]` (`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%).
 Here, we will talk about the figure below and how the trends occur across time.
@@
 **_Types of Publications_**.
-- print out overall
-- print out over time 
-- open science question
+In general, the most common type of publication was `r publication_overall$Var1[1]` (`r format(publication_overall$Percent[1], nsmall = 1, digits = 1)`%), followed by `r publication_overall$Var1[2]` (`r format(publication_overall$Percent[2], nsmall = 1, digits = 1)`%), and smaller categories for `r publication_overall$Var1[3]` (`r format(publication_overall$Percent[3], nsmall = 1, digits = 1)`%), `r publication_overall$Var1[4]` (`r format(publication_overall$Percent[4], nsmall = 1, digits = 1)`%), `r publication_overall$Var1[5]` (`r format(publication_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r publication_overall$Var1[6]` (`r format(publication_overall$Percent[6], nsmall = 1, digits = 1)`%).
+We will include all information over 1% of the publication totals.
+
+```{r echo = FALSE}
+o_total_output <- tidy(o_total_model)
+var_o_total_output <- tidy(var_o_total_model)
+
+s_total_output <- tidy(s_total_model)
+var_s_total_output <- tidy(var_s_total_model)
+```
 
 **_Publication Metrics_**.
-- means and SDs for i10 and hindex information, and number of publications 
-- same analyses as career length - slope of number of publications and variance of number of publications 
-- slope up means people who are publishing more are more represented in the researchers
-- slope down means more people with less publications
-- answer are we giving opportunities to people who need the bean counting
+The average number of all publications per individual was *M* = `r format(round(mean(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`) using ORCID and *M* = `r format(round(mean(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`) using Google Scholar.
+The average i10 index was *M* = `r format(round(mean(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`) and the average h-index was *M* = `r format(round(mean(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`).
+
+Using the same analyses as career length, we will report:
+
+1) Number of publications ORCID:
+
+  - The slope for number of publications was *b* = `r format(round(o_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_total_output$df[2]`) = `r format(round(o_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_total_output$p.value[2])`.
+  - The variance parameter was *SD* = `r format(round(o_total_output$estimate[3], digits = 2), nsmall = 2)`. 
+  - The slope for variance across years was *b* = `r format(round(var_o_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_total_model$df.residual`) = `r format(round(var_o_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_total_output$p.value[2])`.
+
+2) The number of publications for Scholar:
+
+  - The slope for year of first publication was *b* = `r format(round(s_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(s_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r s_total_output$df[2]`) = `r format(round(s_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(s_total_output$p.value[2])`.
+  - The variance parameter was *SD* = `r format(round(s_total_output$estimate[3], digits = 2), nsmall = 2)`. 
+  - The slope for variance across years was *b* = `r format(round(var_s_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_s_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_s_total_model$df.residual`) = `r format(round(var_s_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_s_total_output$p.value[2])`.
 
@@
 
+Discuss the limitation of "who is using ORCID and Scholar" which is likely biasing our results.
+
 \newpage

### 2022-06-03 04.manuscript.tex
pushing old updates

@@
 
-\textbf{\emph{Types of Publications}}.
-- print out overall
-- print out over time
-- open science question
+\textbf{\emph{Types of Publications}}. We will summarize the coded types of publications for individuals.
 
 \textbf{\emph{Publication Metrics}}.
-- means and SDs for i10 and hindex information, and number of publications
-- same analyses as career length - slope of number of publications and variance of number of publications
-- slope up means people who are publishing more are more represented in the researchers
-- slope down means more people with less publications
-- answer are we giving opportunities to people who need the bean counting
+We will report descriptive statistics on the total number of publications, i10 index, and h-index for individuals overall.
+Next, we will use the same analyses described in the career length section to analyze trends over time.
+An increasing slope over time indicates that individuals who are publishing more are more represented in big-team science over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
+A positive slope for variance indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
+While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.
 
@@
 \textbf{\emph{Types of Publications}}.
-- print out overall
-- print out over time
-- open science question
+In general, the most common type of publication was journal-article (78.7\%), followed by other (7.7\%), and smaller categories for conference (5.4\%), book (5.1\%), preprint (1.3\%), and software (0.7\%).
+We will include all information over 1\% of the publication totals.
 
 \textbf{\emph{Publication Metrics}}.
-- means and SDs for i10 and hindex information, and number of publications
-- same analyses as career length - slope of number of publications and variance of number of publications
-- slope up means people who are publishing more are more represented in the researchers
-- slope down means more people with less publications
-- answer are we giving opportunities to people who need the bean counting
+The average number of all publications per individual was \emph{M} = 52.69 (\emph{SD} = 70.37) using ORCID and \emph{M} = 64.20 (\emph{SD} = 110.06) using Google Scholar.
+The average i10 index was \emph{M} = 30.96 (\emph{SD} = 56.44) and the average h-index was \emph{M} = 18.55 (\emph{SD} = 21.89).
+
+Using the same analyses as career length, we will report:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  Number of publications ORCID:
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  The slope for number of publications was \emph{b} = -0.02, \emph{SE} = 2.02, \emph{t}(22) = -0.01, \emph{p} = .991.
+\item
+  The variance parameter was \emph{SD} = 29.13.
+\item
+  The slope for variance across years was \emph{b} = 1.94, \emph{SE} = 5.44, \emph{t}(23) = 0.36, \emph{p} = .725.
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  The number of publications for Scholar:
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(15) = 1.68, \emph{p} = .114.
+\item
+  The variance parameter was \emph{SD} = 100.62.
+\item
+  The slope for variance across years was \emph{b} = -38.52, \emph{SE} = 6.27, \emph{t}(2) = -6.14, \emph{p} = .026.
+\end{itemize}
 
@@
 To be included after we have completed analyses.
+
+Discuss the limitation of ``who is using ORCID and Scholar'' which is likely biasing our results.
 

### 2022-06-03 03.data_analysis.Rmd
updates!

@@
 ```{r setup_analysis, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
 ```
@@
 library(countrycode)
+library(maps)
+library(MOTE)
 current_year <- 2022
@@
 ```{r}
-# map of degree representation
+# create a world map 
+world_map <- map_data(map = "world")
+world_map$region <- iso.alpha(world_map$region)
+world_map <- subset(world_map, region != "AQ")
 
-# map of last job representation
+# map of degree representation ----
+o_ed_summary <- o_ed %>% 
+  group_by(ORCID) %>% 
+  arrange(desc(education_summary_start_date_year_value)) %>% 
+  ungroup() %>% 
+  filter(!duplicated(ORCID)) %>% 
+  select(ORCID, education_summary_organization_address_country)
 
-# how many different countries does each year have and is that getting bigger
+# summarize the same samples
+o_ed_country <- o_ed_summary %>% 
+      group_by(education_summary_organization_address_country) %>% 
+      summarize(n = n()) %>% 
+      filter(!is.na(education_summary_organization_address_country))
+
+# make a map on a continuous scale
+o_ed_country_graph <- 
+  ggplot(o_ed_country) +
+  geom_map(aes(map_id = education_summary_organization_address_country, fill = n), map = world_map) +
+  geom_polygon(data = world_map, 
+               aes(x = long, y = lat, group = group), 
+               colour = 'black', fill = NA) + 
+  theme_void() + 
+  scale_fill_distiller(name = "Sample Size",
+                       palette = "Greys",
+                       direction = 1,
+                       na.value = "white")
+
+# map of last job representation ----
+o_job_summary <- o_job %>% 
+  group_by(ORCID) %>% 
+  arrange(desc(employment_summary_start_date_year_value)) %>% 
+  ungroup() %>% 
+  filter(!duplicated(ORCID)) %>% 
+  select(ORCID, employment_summary_organization_address_country)
+
+# summarize the same samples
+o_job_country <- o_job_summary %>% 
+      group_by(employment_summary_organization_address_country) %>% 
+      summarize(n = n()) %>% 
+      filter(!is.na(employment_summary_organization_address_country))
+
+# make a map on a continuous scale
+o_job_country_graph <- 
+  ggplot(o_job_country) +
+  geom_map(aes(map_id = employment_summary_organization_address_country, fill = n), map = world_map) +
+  geom_polygon(data = world_map, 
+               aes(x = long, y = lat, group = group), 
+               colour = 'black', fill = NA) + 
+  theme_void() + 
+  scale_fill_distiller(name = "Sample Size",
+                       palette = "Greys",
+                       direction = 1,
+                       na.value = "white")
+
+# how many different countries does each year have and is that getting bigger -----
 country_summary <- merged_df %>% 
@@
 
-# grab first X authors and last author
-# and the last one for 10 - 49
-num_grab <- 3
+# for each paper 
+first_probs_ed <- list()
+first_probs_job <- list()
+last_probs_ed <- list()
+last_probs_job <- list()
 
-# 50 to 99 use 5
+# titles
+titles <- author_count$TITLE[author_count$author_count >= 10]
+years <- author_count$year[author_count$author_count >= 10]
 
-# over 100 do top 10
+for (i in 1:length(titles)){
 
+  # number of authors
+  temp_count <- author_count$author_count[author_count$TITLE == titles[i]]
+  # just this paper
+  temp_DF <- merged_df %>% filter(TITLE == titles[i])
+  # skip short
+  if (temp_count < 10){ next }
+  # number of size
+  if (temp_count >=10 & temp_count < 50){ number_grab <- 3 }
+  if (temp_count >=50 & temp_count < 100){ number_grab <- 5 }
+  if (temp_count >= 100){ number_grab <- 10 }
+
+  # first authors 
+  first_probs_ed[[i]] <- as.data.frame(table(temp_DF$un_region_ed[c(1:number_grab, temp_count)], useNA = "ifany"))
+  first_probs_job[[i]] <- as.data.frame(table(temp_DF$un_region_job[c(1:number_grab, temp_count)], useNA = "ifany"))
+
+  # all other authors
+  running_ed <- list()
+  running_job <- list()
+
+  #for (q in 1:temp_count){ # officially do this 
+  for (q in 1:10){ #unofficially test with this 
+    running_ed[[q]] <- temp_DF[-c(1:number_grab, temp_count), ] %>% 
+      sample_n(number_grab+1) %>% 
+      pull(un_region_ed) %>% 
+      table(., useNA = "ifany") %>% 
+      as.data.frame()
+
+    running_job[[q]] <- temp_DF[-c(1:number_grab, temp_count), ] %>% 
+      sample_n(number_grab+1) %>% 
+      pull(un_region_job) %>% 
+      table(., useNA = "ifany") %>% 
+      as.data.frame()
+
+  }
+
+  ed_DF <- suppressMessages(bind_rows(running_ed))
+  job_DF <- suppressMessages(bind_rows(running_job))
+  colnames(ed_DF) <- colnames(job_DF) <- c("Var1", "Freq")
+
+  last_probs_ed[[i]] <- ed_DF %>% group_by(Var1) %>% summarize(Freq = round(mean(Freq)))
+  last_probs_job[[i]] <- job_DF %>% group_by(Var1) %>% summarize(Freq = round(mean(Freq)))
+
+}
+
+gpr_effects_ed <- data.frame(
+  TITLE = titles, 
+  year = years, 
+  v = NA, 
+  low_v = NA, 
+  high_v = NA
+)
+
+gpr_effects_job <- data.frame(
+  TITLE = titles, 
+  year = years, 
+  v = NA, 
+  low_v = NA, 
+  high_v = NA
+)
+
+# for (i in 1:length(first_probs_ed)){
+#   first_ed <- first_probs_ed[[i]]
+#   first_job <- first_probs_job[[i]]
+#   last_ed <- last_probs_ed[[i]]
+#   last_job <- last_probs_job[[i]]
+#   
+#   ed <- first_ed %>% full_join(last_ed, by = c("Var1" = "Var1")) %>% filter(Var1 != "<NA>")
+#   ed$Freq.x[is.na(ed$Freq.x)] <- 0
+#   ed$Freq.y[is.na(ed$Freq.y)] <- 0
+#   ed_chi <- chisq.test(ed[ , c("Freq.x", "Freq.y")])
+#   
+#   ed_mote <- v.chi.sq(x2 = ed_chi$statistic, 
+#                       n = sum(ed_chi$observed), 
+#                       r = nrow(ed_chi$observed),
+#                       c = ncol(ed_chi$observed))
+#   
+#   gpr_effects_ed$v[i] <- ed_mote$v
+#   gpr_effects_ed$low_v[i] <- ed_mote$vlow
+#   gpr_effects_ed$high_v[i] <- ed_mote$vhigh
+#   
+#   job <- first_job %>% full_join(last_job, by = c("Var1" = "Var1")) %>% filter(Var1 != "<NA>")
+#   job$Freq.x[is.na(job$Freq.x)] <- 0
+#   job$Freq.y[is.na(job$Freq.y)] <- 0
+#   job_chi <- chisq.test(job[ , c("Freq.x", "Freq.y")])
+#   
+#   job_mote <- v.chi.sq(x2 = job_chi$statistic, 
+#                       n = sum(job_chi$observed), 
+#                       r = nrow(job_chi$observed),
+#                       c = ncol(job_chi$observed))
+#   
+#   gpr_effects_job$v[i] <- job_mote$v
+#   gpr_effects_job$low_v[i] <- job_mote$vlow
+#   gpr_effects_job$high_v[i] <- job_mote$vhigh
+# 
+# }
 ```
-
-- grab the first X authors and the last authors
-- compare to random samples of other authors of the same size chunk 
-- calculate the probability of having *anyone* from a un region in that chunk
-- make two graphs one of probability of being in the first group, one of probability of being in second group

### 2022-06-03 04.manuscript.Rmd
updates!

@@
 **_Geopolitical Regions_**.
-- overall map of where people get their education
-- overall map of where people are working 
-- is this diversifying over time (more countries as years go up)
-- then the weird analysis to answer about diversifying authors
+We will present visualizations of the last listed education and job location, and we will discuss the areas of world in which authors generally come from, as well as the lowest representation of authors.
+To understand the change in representation diversity, we will summarize the total number of geopolitical regions for each paper.
+Using a linear model, we will examine if the number of regions present is predicted by the year of publication.
+Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope.
+Last, we will examine the differences in representation for corresponding author sets versus all other authors.
+For papers with 10 to 49 authors, we will use the three first authors and the last author to compare against random samples of other authors.
+For 50 to 99 authors, five first authors plus last will be used, and for all papers with more than 100 authors, we will use ten first authors and the last author.
+We will calculate the frequencies of each of the UN Sub-Regions for first authors.
+Then we will randomly sample all authors in subsets of the same size (i.e., 3+1, 5+1, 10+1), and average the frequencies of UN Sub-Regions across these random samples.
+We will randomly sample the same number of times as the size of the author list (i.e., a paper that has 54 authors will be randomly sampled 54 times with a sample size of six).
+For each year, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors.
+Since this data is categorical, we will use Cramer's V to represent the effect size.
+If the effect size includes zero in it's confidence interval, this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity.
+Any confidence interval that does include zero represents a difference in diversity.
+We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero.
 
@@
 
-**_Geopolitical Regions_**. 
-- overall map of where people get their education
-- overall map of where people are working 
-- is this diversifying over time (more countries as years go up)
-- then the weird analysis to answer about diversifying authors
+**_Geopolitical Regions_**. We will first present two figures for education and employment geopolitical regions representation in scholars.
+
+Education Graph
+
+```{r figure5, echo = FALSE, warning = FALSE}
+o_ed_country_graph
+```
+
+Employment Graph
+
+```{r figure6, echo = FALSE, warning = FALSE}
+o_job_country_graph
+```
+
+```{r}
+edu_country_output <- tidy(edu_country_model)
+job_country_output <- tidy(job_country_model)
+```
+
+Next, we will report the results of two linear regression models.
+The independent variable is year of publication, and the dependent variables include the summary of the total number of different geopolitical regions represented in each publication.
+- The slope for the education model was *b* = `r format(round(edu_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(edu_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r edu_country_output$df[2]`) = `r format(round(edu_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(edu_country_output$p.value[2])`.
+
+- The slope for the employment model was *b* = `r format(round(job_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(job_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r job_country_output$df[2]`) = `r format(round(job_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(job_country_output$p.value[2])`.
+
+```{r eval = F}
+gpr_effects_ed_summary <- 
+  gpr_effects_ed %>% 
+  group_by(year) %>% 
+  summarize(v = mean(v, na.rm = T), 
+            vlow = mean(low_v, na.rm = T), 
+            vhigh = mean(high_v, na.rm = T))
+
+gpr_effects_job_summary <- 
+  gpr_effects_job %>% 
+  group_by(year) %>% 
+  summarize(v = mean(v, na.rm = T), 
+            vlow = mean(low_v, na.rm = T), 
+            vhigh = mean(high_v, na.rm = T))
+```
+
+Last, we will examine the effect sizes of the UN Sub-Regions represented for each year of analysis. We will present a visualization of the effect sizes.
+
+- add a quick random demo of this simulating fake data
+- create a picture of this idea
+
+**All models will also include a measure of effect size.**
+#### erin you need to do this #####
 
@@
 
-Discuss the limitation of "who is using ORCID and Scholar" which is likely biasing our results.
+Discuss the limitation of "who is using ORCID and Scholar" which can bias our results.
 

### 2022-06-06 03.data_analysis.Rmd
updating manuscript pre-reg

@@
 # map of degree representation ----
-o_ed_summary <- o_ed %>% 
+o_ed_summary_map <- o_ed %>% 
   group_by(ORCID) %>% 
@@
 # summarize the same samples
-o_ed_country <- o_ed_summary %>% 
+o_ed_country <- o_ed_summary_map %>% 
       group_by(education_summary_organization_address_country) %>% 
@@
 
-gpr_effects_ed <- data.frame(
-  TITLE = titles, 
-  year = years, 
-  v = NA, 
-  low_v = NA, 
-  high_v = NA
+gpr_effects_ed <- bind_rows(first_probs_ed, .id = "source") %>% 
+  full_join(
+    bind_rows(last_probs_ed, .id = "source"), 
+    by = c("source" = "source", "Var1" = "Var1")
+  ) %>% 
+  full_join(
+    data.frame(TITLE = titles, year = years, 
+               source = as.character(1:length(titles))),
+    by = c("source" = "source")
   )
+colnames(gpr_effects_ed) <- c("source", "unregion", "freq_first", 
+                              "freq_last", "TITLE", "year")
 
-gpr_effects_job <- data.frame(
-  TITLE = titles, 
-  year = years, 
-  v = NA, 
-  low_v = NA, 
-  high_v = NA
+gpr_effects_job <- bind_rows(first_probs_job, .id = "source") %>% 
+  full_join(
+    bind_rows(last_probs_job, .id = "source"), 
+    by = c("source" = "source", "Var1" = "Var1")
+  ) %>% 
+  full_join(
+    data.frame(TITLE = titles, year = years, 
+               source = as.character(1:length(titles))),
+    by = c("source" = "source")
   )
+colnames(gpr_effects_job) <- c("source", "unregion", "freq_first", 
+                               "freq_last","TITLE", "year")
 
-# for (i in 1:length(first_probs_ed)){
-#   first_ed <- first_probs_ed[[i]]
-#   first_job <- first_probs_job[[i]]
-#   last_ed <- last_probs_ed[[i]]
-#   last_job <- last_probs_job[[i]]
-#   
-#   ed <- first_ed %>% full_join(last_ed, by = c("Var1" = "Var1")) %>% filter(Var1 != "<NA>")
-#   ed$Freq.x[is.na(ed$Freq.x)] <- 0
-#   ed$Freq.y[is.na(ed$Freq.y)] <- 0
-#   ed_chi <- chisq.test(ed[ , c("Freq.x", "Freq.y")])
-#   
-#   ed_mote <- v.chi.sq(x2 = ed_chi$statistic, 
-#                       n = sum(ed_chi$observed), 
-#                       r = nrow(ed_chi$observed),
-#                       c = ncol(ed_chi$observed))
-#   
-#   gpr_effects_ed$v[i] <- ed_mote$v
-#   gpr_effects_ed$low_v[i] <- ed_mote$vlow
-#   gpr_effects_ed$high_v[i] <- ed_mote$vhigh
-#   
-#   job <- first_job %>% full_join(last_job, by = c("Var1" = "Var1")) %>% filter(Var1 != "<NA>")
-#   job$Freq.x[is.na(job$Freq.x)] <- 0
-#   job$Freq.y[is.na(job$Freq.y)] <- 0
-#   job_chi <- chisq.test(job[ , c("Freq.x", "Freq.y")])
-#   
-#   job_mote <- v.chi.sq(x2 = job_chi$statistic, 
-#                       n = sum(job_chi$observed), 
-#                       r = nrow(job_chi$observed),
-#                       c = ncol(job_chi$observed))
-#   
-#   gpr_effects_job$v[i] <- job_mote$v
-#   gpr_effects_job$low_v[i] <- job_mote$vlow
-#   gpr_effects_job$high_v[i] <- job_mote$vhigh
-# 
-# }
+# flatten down by year breakdown 
+gpr_effects_ed$group <- NA
+gpr_effects_ed$year <- as.numeric(gpr_effects_ed$year)
+gpr_effects_ed$group[gpr_effects_ed$year < 2020] <- "Pre-2020"
+gpr_effects_ed$group[gpr_effects_ed$year == 2020] <- "2020"
+gpr_effects_ed$group[gpr_effects_ed$year > 2020] <- "Post-2020"
+
+gpr_effects_ed_summary <- gpr_effects_ed %>% 
+  select(group, unregion, freq_first, freq_last) %>% 
+  group_by(group, unregion) %>% 
+  summarize(total_first = sum(freq_first, na.rm = T),
+            total_last = sum(freq_last, na.rm = T)) %>% 
+  filter(!is.na(unregion))
+
+gpr_effects_job$group <- NA
+gpr_effects_job$year <- as.numeric(gpr_effects_job$year)
+gpr_effects_job$group[gpr_effects_job$year < 2020] <- "Pre-2020"
+gpr_effects_job$group[gpr_effects_job$year == 2020] <- "2020"
+gpr_effects_job$group[gpr_effects_job$year > 2020] <- "Post-2020"
+
+gpr_effects_job_summary <- gpr_effects_job %>% 
+  select(group, unregion, freq_first, freq_last) %>% 
+  group_by(group, unregion) %>% 
+  summarize(total_first = sum(freq_first, na.rm = T),
+            total_last = sum(freq_last, na.rm = T)) %>% 
+  filter(!is.na(unregion))
+
+# pre 2020 ----
+x_pre2020 <- chisq.test(gpr_effects_ed_summary[gpr_effects_ed_summary$group == "Pre-2020", c("total_first", "total_last")])
+v_pre2020 <- v.chi.sq(x2 = x_pre2020$statistic, 
+                      n = sum(x_pre2020$observed),
+                      r = nrow(x_pre2020$observed),
+                      c = ncol(x_pre2020$observed))
+
+# 2020 ----
+x_2020 <- chisq.test(gpr_effects_ed_summary[gpr_effects_ed_summary$group == "2020", c("total_first", "total_last")])
+v_2020 <- v.chi.sq(x2 = x_2020$statistic, 
+                      n = sum(x_2020$observed),
+                      r = nrow(x_2020$observed),
+                      c = ncol(x_2020$observed))
+
+# post 2020 ----
+x_post2020 <- chisq.test(gpr_effects_ed_summary[gpr_effects_ed_summary$group == "Post-2020", c("total_first", "total_last")])
+v_post2020 <- v.chi.sq(x2 = x_post2020$statistic, 
+                      n = sum(x_post2020$observed),
+                      r = nrow(x_post2020$observed),
+                      c = ncol(x_post2020$observed))
 ```

### 2022-06-06 04.manuscript.Rmd
updating manuscript pre-reg

@@
 We will randomly sample the same number of times as the size of the author list (i.e., a paper that has 54 authors will be randomly sampled 54 times with a sample size of six).
-For each year, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors.
+
+Given the expected small sample sizes of these contingency tables (i.e., the largest could be *n* = 22 if all author information is available), we will group together titles based on time period using pre-2020, 2020, and post-2020 to show change over time.
+The choice of these groupings is based on the number of articles avaliable within these time brackets.
+For each grouping, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors.
 Since this data is categorical, we will use Cramer's V to represent the effect size.
@@
 Any confidence interval that does include zero represents a difference in diversity.
-We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero.
+We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero using standardized residuals.
 
@@
 
-```{r}
+```{r echo = F}
 edu_country_output <- tidy(edu_country_model)
@@
 The independent variable is year of publication, and the dependent variables include the summary of the total number of different geopolitical regions represented in each publication.
-- The slope for the education model was *b* = `r format(round(edu_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(edu_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r edu_country_output$df[2]`) = `r format(round(edu_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(edu_country_output$p.value[2])`.
+- The slope for the education model was *b* = `r format(round(edu_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(edu_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r edu_country_model$df.residual`) = `r format(round(edu_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(edu_country_output$p.value[2])`.
 
-- The slope for the employment model was *b* = `r format(round(job_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(job_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r job_country_output$df[2]`) = `r format(round(job_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(job_country_output$p.value[2])`.
+- The slope for the employment model was *b* = `r format(round(job_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(job_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r job_country_model$df.residual`) = `r format(round(job_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(job_country_output$p.value[2])`.
 
-```{r eval = F}
-gpr_effects_ed_summary <- 
-  gpr_effects_ed %>% 
-  group_by(year) %>% 
-  summarize(v = mean(v, na.rm = T), 
-            vlow = mean(low_v, na.rm = T), 
-            vhigh = mean(high_v, na.rm = T))
+Last, we will examine the effect sizes of the UN Sub-Regions represented for each grouped year of analysis. Tables of the UN Sub-Regions will be presented in our supplemental documents.
 
-gpr_effects_job_summary <- 
-  gpr_effects_job %>% 
-  group_by(year) %>% 
-  summarize(v = mean(v, na.rm = T), 
-            vlow = mean(low_v, na.rm = T), 
-            vhigh = mean(high_v, na.rm = T))
-```
+- Pre-2020: `r v_pre2020$estimate` and `r x_pre2020$stdres` will be used to discuss pre-2020 manuscripts.
 
-Last, we will examine the effect sizes of the UN Sub-Regions represented for each year of analysis. We will present a visualization of the effect sizes.
+- 2020: `r v_2020$estimate` and `r x_2020$stdres` will be used to discuss 2020 manuscripts.
 
-- add a quick random demo of this simulating fake data
-- create a picture of this idea
-
-**All models will also include a measure of effect size.**
-#### erin you need to do this #####
+- Post-2020: `r v_post2020$estimate` and `r x_post2020$stdres` will be used to discuss post-2020 manuscripts.
 
@@
 
-Discuss the limitation of "who is using ORCID and Scholar" which can bias our results.
+## Limitations
+
+- Discuss the limitation of "who is using ORCID and Scholar" which can bias our results. 
+- Other limitations will be included.
 

### 2022-06-06 04.manuscript.tex
updating manuscript pre-reg

@@
 \documentclass[
-  english,
   man]{apa6}
-\title{Who does big team science?}
-\author{Erin M. Buchanan\textsuperscript{1} \& Savannah C. Lewis\textsuperscript{2}}
-\date{}
-
 \usepackage{amsmath,amssymb}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 \usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifLuaTeX
@@
 \fi
+
+\title{Who does big team science?}
+\author{Erin M. Buchanan\textsuperscript{1} \& Savannah C. Lewis\textsuperscript{2}}
+\date{}
+
+\shorttitle{Big Team Science}
 
@@
 \textbf{\emph{Geopolitical Regions}}.
-- overall map of where people get their education
-- overall map of where people are working
-- is this diversifying over time (more countries as years go up)
-- then the weird analysis to answer about diversifying authors
+We will present visualizations of the last listed education and job location, and we will discuss the areas of world in which authors generally come from, as well as the lowest representation of authors.
+To understand the change in representation diversity, we will summarize the total number of geopolitical regions for each paper.
+Using a linear model, we will examine if the number of regions present is predicted by the year of publication.
+Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope.
+Last, we will examine the differences in representation for corresponding author sets versus all other authors.
+For papers with 10 to 49 authors, we will use the three first authors and the last author to compare against random samples of other authors.
+For 50 to 99 authors, five first authors plus last will be used, and for all papers with more than 100 authors, we will use ten first authors and the last author.
+We will calculate the frequencies of each of the UN Sub-Regions for first authors.
+Then we will randomly sample all authors in subsets of the same size (i.e., 3+1, 5+1, 10+1), and average the frequencies of UN Sub-Regions across these random samples.
+We will randomly sample the same number of times as the size of the author list (i.e., a paper that has 54 authors will be randomly sampled 54 times with a sample size of six).
+
+Given the expected small sample sizes of these contingency tables (i.e., the largest could be \emph{n} = 22 if all author information is available), we will group together titles based on time period using pre-2020, 2020, and post-2020 to show change over time.
+The choice of these groupings is based on the number of articles avaliable within these time brackets.
+For each grouping, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors.
+Since this data is categorical, we will use Cramer's V to represent the effect size.
+If the effect size includes zero in it's confidence interval, this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity.
+Any confidence interval that does include zero represents a difference in diversity.
+We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero using standardized residuals.
 
@@
 Here, we will talk about the figure below and how the trends occur across time.
-We will also comment on the number of jobs that would be considered ``non-academic.''
+We will also comment on the number of jobs that would be considered ``non-academic''.
 
@@
 \textbf{\emph{Education}}.
-Overall, individuals \textbf{at the time of publication} in big team science publications are Doctor (79.7\%), Masters (16.5\%), andBachelor (3.8\%).
+Overall, individuals \textbf{at the time of publication} in big team science publications are Doctor (79.7\%), Masters (16.5\%), and Bachelor (3.8\%).
 Here, we will talk about the figure below and how the trends occur across time.
@@
 
-\textbf{\emph{Geopolitical Regions}}.
-- overall map of where people get their education
-- overall map of where people are working
-- is this diversifying over time (more countries as years go up)
-- then the weird analysis to answer about diversifying authors
+\textbf{\emph{Geopolitical Regions}}. We will first present two figures for education and employment geopolitical regions representation in scholars.
+
+Education Graph
+
+\includegraphics{04.manuscript_files/figure-latex/figure5-1.pdf}
+
+Employment Graph
+
+\includegraphics{04.manuscript_files/figure-latex/figure6-1.pdf}
+
+Next, we will report the results of two linear regression models.
+The independent variable is year of publication, and the dependent variables include the summary of the total number of different geopolitical regions represented in each publication.
+- The slope for the education model was \emph{b} = 0.06, \emph{SE} = 0.09, \emph{t}(68) = 0.63, \emph{p} = .531.
+
+\begin{itemize}
+\tightlist
+\item
+  The slope for the employment model was \emph{b} = 0.01, \emph{SE} = 0.09, \emph{t}(68) = 0.12, \emph{p} = .903.
+\end{itemize}
+
+Last, we will examine the effect sizes of the UN Sub-Regions represented for each grouped year of analysis. Tables of the UN Sub-Regions will be presented in our supplemental documents.
+
+\begin{itemize}
+\item
+  Pre-2020: \(V\) = .36, 95\% CI {[}.54, .78{]} and 0.13, 0.44, 0.94, -0.57, -0.84, -0.57, -0.13, -0.44, -0.94, 0.57, 0.84, and 0.57 will be used to discuss pre-2020 manuscripts.
+\item
+  2020: \(V\) = .64, 95\% CI {[}.48, 1.19{]} and -0.66, 2.31, -1.02, -0.84, 0.66, -2.31, 1.02, and 0.84 will be used to discuss 2020 manuscripts.
+\item
+  Post-2020: \(V\) = .55, 95\% CI {[}.65, 1.28{]} and 1.45, -0.68, -0.68, -0.68, -1.45, 0.68, 0.68, and 0.68 will be used to discuss post-2020 manuscripts.
+\end{itemize}
 
@@
 
-Discuss the limitation of ``who is using ORCID and Scholar'' which is likely biasing our results.
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
+
+\begin{itemize}
+\tightlist
+\item
+  Discuss the limitation of ``who is using ORCID and Scholar'' which can bias our results.
+\item
+  Other limitations will be included.
+\end{itemize}
 

### 2022-06-17 03.data_analysis.Rmd
update the things

@@
 current_year <- 2022
-#### fix sau chins paper #### https://osf.io/gq92w/ 
+
+## fixes
+## update sau chins paper with new list https://osf.io/gq92w/ 
+## make list of OSC
+## add Many Primates list 
+## update Dorison et al.
+
+## double check each publication for proper year and journal
+## look at merged id and incorrect ids 
 ```
@@
 s_info <- import("scholar_info.csv")
+```
+
+- test the merge
+
+```{r}
+merged_test <- 
+  long_bib %>% 
+  select(first, last, TITLE) %>% 
+  full_join(
+    # note this isn't perfect ... will have to make sure all versions 
+    # get matched 
+    (id_list %>% select(first, last, full, ORCID, scholar)), 
+    by = c("first" = "first", "last" = "last") 
+  )
+
+# if full name is blank, then the person is not in our id_list
+merged_test %>% 
+  filter(!duplicated(merged_test %>% select(first, last))) %>% 
+  filter(is.na(full)) %>% 
+  export("missing_id_list.xlsx")
+
+# if no title they are in id_list but aren't merging correctly 
+merged_test %>% 
+  filter(is.na(TITLE)) %>% 
+  export("incorrect_id_list.xlsx")
 ```

### 2022-06-17 03.data_analysis.Rmd
updating list

@@
 current_year <- 2022
-
-## fixes
-## update sau chins paper with new list https://osf.io/gq92w/ 
-## make list of OSC
-## add Many Primates list 
-## update Dorison et al.
-
-## double check each publication for proper year and journal
-## look at merged id and incorrect ids 
 ```
@@
 ```{r}
-bibs <- bib2df("papers.bib")
+# bibs <- bib2df("papers.bib") original data
+bibs <- bib2df("papers_06_17_22.bib")
 
@@
 
-In this section, we will add the information for authors when they used a consortium authorship.
-
-```{r}
-
-```
+Note that we edited the references in Zotero directly to fill in corstium authorships.
 
@@
 
-- test the merge
+- test the merge to make sure we have all authors included
 
@@
 journal_count$JOURNAL[is.na(journal_count$JOURNAL)] <- "Pre-Print"
+
+# also add information about the preprint RR acceptances 
 ```

### 2022-07-07 temp_test.Rmd
adding new orcs

---
title: "temp_test"
author: "Erin M. Buchanan"
date: '2022-07-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(googlesheets4)
library(dplyr)
library(rorcid)
library(rio)
library(scholar)
library(purrr)
library(httr)
```

## Get Data

```{r}
DF <- read_sheet("https://docs.google.com/spreadsheets/d/1dSlIQXeLcFgkITyfy15_yAdtjct1AedjD6s5D4qTzCw/edit#gid=1698777071")
```

## Work on ORC

```{r eval = F}
ORC <- DF %>% 
  filter(ORCID == "FIND")

for (i in 2447:nrow(ORC)){
#for (i in 1:10){ #temporary do a small number

  # find possible candidates 
  possibles <- orcid_search(family_name = ORC$last[i], 
                            given_name = ORC$first[i])

  cat(i)
  cat("\n")

  # if nrow == 1 then figure out if there's a match
  if (nrow(possibles) == 1){
    ORC$ORCID[i] <- possibles$orcid
  }

  # be nice to api take a break 
  Sys.sleep(runif(1, 3, 5))

}

DF <- DF %>% 
  full_join(ORCF %>% select(first, last, ORCID), 
            by = c("first" = "first", "last" = "last"))

export(DF, "orc_final.xlsx")
```

## Scholar Function

```{r}
get_scholar <- function (last_name = "", first_name = "", affiliation = NA) 
{
    if (!any(nzchar(c(first_name, last_name)))) 
        stop("At least one of first and last name must be specified!")
    site <- getOption("scholar_site")
    url <- paste0(site, "/citations?view_op=search_authors&mauthors=", 
        first_name, "+", last_name, "&hl=en&oi=ao")
    page <- get_scholar_resp(url)
    if (is.null(page)) 
        return(NA)
    aa <- content(page, as = "text")
    ids <- stringr::str_extract_all(string = aa, pattern = ';user=.{12}')

    if (length(unlist(ids)) == 0) {
        message("No Scholar ID found.")
        return(NA)
    }
    ids <- ids %>% unlist %>% gsub(";user=", "", 
        .) %>% unique

    return(ids)
  }
```

## Get Scholar IDs

```{r}
scholars <- DF %>% filter(scholar == "FIND")
p_get_scholar_id <- possibly(get_scholar, otherwise = NA_character_)

nrow(scholars)
# we are on 1:50

for(i in 1:50) {

  possibles <- p_get_scholar_id(last_name = scholars$last[i], 
                                first_name = scholars$first[i])

  if (length(possibles) == 1) { scholars$scholar[i] <- possibles }

  # be nice to api take a break 
  Sys.sleep(runif(1, 3, 5))

  # if divisible by 10
  if (i %% 10 == 0){
    export(scholars, "scholars_update.xlsx")
  }
}

```

### 2022-07-08 01.get_person_ids.Rmd
rearranging

@@
 library(httr)
+library(googlesheets4)
 
@@
 library(scholar)
+library(rio)
 ```
@@
 
-```{r}
-bibs <- bib2df("papers.bib")
+```{r eval = F}
+# bibs <- bib2df("papers.bib")
+bibs <- bib2df("manuscript_data/papers_06_17_22.bib")
 ```
@@
 
-```{r}
+```{r eval = F}
 # get data into long format
@@
 long_bib <- long_bib %>% select(-EDITOR)
-write.csv(long_bib, "unedited_bib.csv", row.names = F)
+write.csv(long_bib, "id_output/unedited_bib.csv", row.names = F)
 ```
@@
 
-write.csv(get_id, "possible_orc_ids.csv", row.names = F)
+write.csv(get_id, "id_output/possible_orc_ids.csv", row.names = F)
 ```
@@
 
-```{r eval = F}
+```{r}
 get_scholar <- function (last_name = "", first_name = "", affiliation = NA) 
@@
 
-write.csv(get_id, "possible_both_ids.csv", row.names = F)
+write.csv(get_id, "id_output/possible_both_ids.csv", row.names = F)
 ```
+
+## Get Data Round 2
+
+```{r}
+DF <- read_sheet("https://docs.google.com/spreadsheets/d/1dSlIQXeLcFgkITyfy15_yAdtjct1AedjD6s5D4qTzCw/edit#gid=1698777071")
+```
+
+## Work on ORC
+
+```{r eval = F}
+ORC <- DF %>% 
+  filter(ORCID == "FIND")
+
+for (i in 2447:nrow(ORC)){
+#for (i in 1:10){ #temporary do a small number
+
+  # find possible candidates 
+  possibles <- orcid_search(family_name = ORC$last[i], 
+                            given_name = ORC$first[i])
+
+  cat(i)
+  cat("\n")
+
+  # if nrow == 1 then figure out if there's a match
+  if (nrow(possibles) == 1){
+    ORC$ORCID[i] <- possibles$orcid
+  }
+
+  # be nice to api take a break 
+  Sys.sleep(runif(1, 3, 5))
+
+}
+
+DF <- DF %>% 
+  full_join(ORCF %>% select(first, last, ORCID), 
+            by = c("first" = "first", "last" = "last"))
+
+export(DF, "id_output/orc_final.xlsx")
+```
+
+## Get Scholar IDs
+
+```{r}
+scholars <- DF %>% filter(scholar == "FIND")
+p_get_scholar_id <- possibly(get_scholar, otherwise = NA_character_)
+
+nrow(scholars)
+# start at Bergmann 134
+
+for(i in 258:300) {
+
+  possibles <- p_get_scholar_id(last_name = scholars$last[i], 
+                                first_name = scholars$first[i])
+
+  if (length(possibles) == 1) { scholars$scholar[i] <- possibles }
+
+  # be nice to api take a break 
+  Sys.sleep(runif(5, 3, 5))
+
+  # if divisible by 10
+  if (i %% 10 == 0){
+    export(scholars, "id_output/scholar_update.xlsx")
+  }
+}
+
+DF <- DF %>% 
+  full_join(scholars %>% select(first, last, scholar), 
+            by = c("first" = "first", "last" = "last"))
+
+export(DF, "id_output/scholar_final.xlsx")
+
+```

### 2022-07-08 02.get_person_stats.Rmd
rearranging

@@
 
-write.csv(works_df, "ORCID_works.csv", row.names = F)
+write.csv(works_df, "works_output/ORCID_works.csv", row.names = F)
 
@@
 
-write.csv(ed_df, "ORCID_ed.csv", row.names = F)
+write.csv(ed_df, "works_output/ORCID_ed.csv", row.names = F)
 
@@
                   anytime::anydate(employment_summary_last_modified_date_value/1000))
-write.csv(job_df, "ORCID_job.csv", row.names = F)
+write.csv(job_df, "works_output/ORCID_job.csv", row.names = F)
 ```
@@
 works_df$scholar <- rep(names(s_author_works), lapply(s_author_works, nrow))
-write.csv(works_df, "scholar_works.csv", row.names = F)
+write.csv(works_df, "works_output/scholar_works.csv", row.names = F)
 
@@
 info_df$scholar <- info_df$id
-write.csv(info_df, "scholar_info.csv", row.names = F)
+write.csv(info_df, "works_output/scholar_info.csv", row.names = F)
 ```

### 2022-07-08 03.data_analysis.Rmd
rearranging

@@
 # bibs <- bib2df("papers.bib") original data
-bibs <- bib2df("papers_06_17_22.bib")
+bibs <- bib2df("manuscript_data/papers_06_17_22.bib")
 
@@
 ```{r}
-id_list <- import("test_utf8.xlsx")
+id_list <- import("manuscript_data/test_utf8.xlsx")
 
-o_works <- import("ORCID_works.csv")
-o_ed <- import("ORCID_ed.csv")
-o_job <- import("ORCID_job.csv")
+o_works <- import("works_output/ORCID_works.csv")
+o_ed <- import("works_output/ORCID_ed.csv")
+o_job <- import("works_output/ORCID_job.csv")
 
-s_works <- import("scholar_works.csv") 
-s_info <- import("scholar_info.csv")
+s_works <- import("works_output/scholar_works.csv") 
+s_info <- import("works_output/scholar_info.csv")
 ```
@@
   filter(is.na(full)) %>% 
-  export("missing_id_list.xlsx")
+  export("id_output/missing_id_list.xlsx")
 
@@
   filter(is.na(TITLE)) %>% 
-  export("incorrect_id_list.xlsx")
+  export("id_output/incorrect_id_list.xlsx")
 ```
@@
 ```{r}
-JIF <- import("jif.xlsx")
+JIF <- import("manuscript_data/jif.xlsx")
 ```

### 2022-07-26 04.manuscript_scopus.Rmd
updated manuscript draft

--- 2022-06-06 04.manuscript.Rmd
@@
 
-The introduction will go here. Here's an outline:
+# Significance
 
-- Big Team Science
-  - one off papers 
-  - collaborative teams 
-- Credibility revolution
-- WEIRD 
-- ... more tbd, brain isn't braining
+science collaboration overall 
+  - what is collaboration
+  - is it increasing 
+  - globalization should help
+
+rise of big team science because the need for resources, replication, reproducibility, generalization  
+  - physics
+  - biology 
+  - psychology
+
+metascience
+  - most research is on lessons learned, why bts is useful
+  - little research on who/fields has done bts
+  - has the globalization of science actually impacted people other than NA and Europe
+
+Collaboration in scientific endeavors involves multiple researchers at multiple institutions to communicate and work together to advance knowledge in their chosen field.
+While collaboration is not new in science, the current interest of "big team science" is increasing.
+We define big team science as at least ten authors with ten different institutional affiliations.
+The globalization of science has allowed researchers across the world to contribute to research projects, but little research has examined *who* participates in big team science projects.
+
+idea of BTS is not new, but interest is new, and globalization allows us to do BTS with projects such as PSA/CERN/Reproducibility projects.
+But we don't know if this uptick in large scale projects has diversified the *people* involved in BTS.
+Is this increasing inclusivity?
+At what level of career are people doing BTS?
+Is that changing over time?
+And how is that including new and varied researchers outside NA and Europe?
+Are we including people in positions that may impact their career?
+WERID thing is innovative
+
+    Significance: Describe how the project addresses an important problem or a critical barrier to progress in the field and how it can advance knowledge in the ICSR Research Themes.
+
+We specifically expect to examine ICSR's Research Themes of inclusivity, research careers, and research globalization.
+As we examine these themes, it will a bring new knowledge of how big team science projects impact each theme and field of study.
+
+# Potential Outlets
+
+We will aim for high impact broad scope journals such as *Science*, *Nature* or *Nature Human Behaviour*.
+Other journals would include review publications within psychology to compare the social sciences to other sciences: *Perspectives in Psychological Science*, *Psychological Bulletin*, *Psychological Review*, or *Current Directions in Psychological Science*.
+
+# Approach
+
+    Approach: Please describe:
+        An explicit research question or hypothesis you plan to test, and specific aims/objective related to that question.
+        The project’s overall strategy and planned methodology.
+        How the proposed project will make use of one or more of the available ICSR Lab datasets.
+        Any especially innovative or novel aspect of the proposed project.
 
@@
 
+- definition for big team size: 10 authors + at least 10 different institutions
+- we will use all categories but break into the big four: https://service.elsevier.com/app/answers/detail/a_id/14882/supporthub/scopus/~/what-are-the-most-frequent-subject-area-categories-and-classifications-used-in/
+- we would get everything from df_ani 
+- only use 1970 and forward
+
 ## Data Curation
@@
 The current impact factor (i.e., 2022) for each journal was found on the journal page and included for journal statistics.
+
+journal information we could include:
+  - total number of articles overall 
+  - number of distinct journals in each of the four areas 
+  - JIF df_sources, snip
+  - https://liu.cwp.libguides.com/c.php?g=45770&p=4417804
 
@@
 Other metascience categories included papers that focused on research degrees of freedom, analysis choices, and types of samples.
+
+- keywords are easier now - could use the ASJC smaller subfield areas to create a list 
+- https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/
+- table of all the codes
 
@@
 
+- calculate the min to max
+- average authors 
+- SD authors
+
 Next, we matched each author to their Google Scholar and ORCID profile pages, if available.
@@
 We used these two packages and profile pages to collect authorship statistics described below.
+If a researcher was not present in either of these databases, their information was excluded from the relevant analyses below.
+
+- here we would pull all author ids and then grab all their papers - grab from the whole dataset not just 1970
 
@@
 
+- year from first publication should be what we would do
+
 **_Employment_**.
@@
 Employment geopolitical region was also selected when available.
+
+- can't get this part really - we could get institution from publication and country from publication
 
@@
 
+- we can get the degrees from the author table
+
 **_Types of Publications_**.
@@
 We coded these publications into general categories including book, conference presentations, data-sets, journal articles, preprints, software, thesis, and other publications.
+
+- publication type:
+
+The classification of the publication, which may be: ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.
+
+- just make a graph of the options
 
@@
 The h-index represents the highest *h* number of publications that have at least *h* citations, while the i-10 index represents the number of publications with at least 10 citations.
+
+- for each author:
+  - total number of publications
+  - h index
+  - i 10 index
 
@@
 
+- so we cant do MLM 
+- for each paper we could calculate an average career length, then run the regression 
+- then calculate the standard deviation and do the same analysis as described
+
 **_Employment_**. We will summarize the general employment categories of individuals at the time of publication, along with a summary for change over time. 
-
 **_Education_**. We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.
@@
 While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.
+same idea average down by paper for mean and standard deviation
 
@@
 
+- may not need to do this random sample thing if we have large enough datasets? 
+- pool them together and then compare? 
+- maybe group them in the sizes we are interested in, then convert to proportions
+- average those proportions ? plot comparisons of the proportions and confidence intervals for each group
+
 Given the expected small sample sizes of these contingency tables (i.e., the largest could be *n* = 22 if all author information is available), we will group together titles based on time period using pre-2020, 2020, and post-2020 to show change over time.
-The choice of these groupings is based on the number of articles avaliable within these time brackets.
+The choice of these groupings is based on the number of articles available within these time brackets.
 For each grouping, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors.

### 2022-08-26 04.manuscript_scopus.Rmd
adding outline

@@
 
-science collaboration overall 
+science collaboration overall (sav)
   - what is collaboration
@@
 
-rise of big team science because the need for resources, replication, reproducibility, generalization  
+rise of big team science because the need for resources, replication, reproducibility, generalization (erin)
   - physics
@@
 
-metascience
+metascience (erin)
   - most research is on lessons learned, why bts is useful
@@
   - has the globalization of science actually impacted people other than NA and Europe
+
+about this project paragraph (erin)
 

### 2022-08-30 04.manuscript_scopus.Rmd
Update 04.manuscript_scopus.Rmd
Pancake becomes an author...

@@
 
+According to the Oxford English dictionary, collaboration is two or more people working together to achieve a certain goal.
+Collaboration in scientific endeavors involves multiple researchers at multiple institutions to communicate and work together to advance knowledge in their chosen field.
+Collaboration can look differently in every project dependent on the skill sets, questions and perspectives of your collaborators.
+While collaboration is not new in science, the current interest of "big team science" is increasing.
+Big team science organizations utilize and run on collaboration to ensure that diverse populations and ideas are brought into research projects, which in turn allows for more reliability and generalizability in the results and method of the study.
+In regards to this project, the definitions of Big Team Science will be defined as a collaboration of ten or more authors from ten different institutions.
+Big Team Science seems to be increasing as a result of the current state of the scientific field and with the increase in technology in the world.The idea of BTS is not new, but interest is new, and globalization allows us to do BTS with projects such as PSA/CERN/Reproducibility projects.
+Technological advances have provided easier ways to collaborate with people who are from other universities and countries through document sharing platforms (i.e.
+Google, github, and Open Science Framework), video chatting platforms (i.e.
+as zoom, skype, microsoft teams) and messaging and data tracking platforms (i.e.
+Slack, Shiny app, Trello boards, when2meet, etc.).
+The credibility movement seems to suggest that by having both collaborations that span across the globe and subfield of psychology, age groups and education levels should help to drive psychological science in the path of better materials, reliability, generalizability and more robust sample size in a study.
+
+ADD STUFF ABOUT THE CREDIBILITY MOVEMENT HERE….
+
 rise of big team science because the need for resources, replication, reproducibility, generalization (erin)
@@
 
-Collaboration in scientific endeavors involves multiple researchers at multiple institutions to communicate and work together to advance knowledge in their chosen field.
-While collaboration is not new in science, the current interest of "big team science" is increasing.
-We define big team science as at least ten authors with ten different institutional affiliations.
+    Significance: Describe how the project addresses an important problem or a critical barrier to progress in the field and how it can advance knowledge in the ICSR Research Themes.
+
+We specifically expect to examine ICSR's Research Themes of inclusivity, research careers, and research globalization.
+As we examine these themes, it will bring new knowledge of how big team science projects impact each theme and field of study.
+
 The globalization of science has allowed researchers across the world to contribute to research projects, but little research has examined *who* participates in big team science projects.
-
-idea of BTS is not new, but interest is new, and globalization allows us to do BTS with projects such as PSA/CERN/Reproducibility projects.
-But we don't know if this uptick in large scale projects has diversified the *people* involved in BTS.
+We see an increase in BTS but we don't know if this uptick in large scale projects has diversified the *people* involved in BTS.
 Is this increasing inclusivity?
@@
 Are we including people in positions that may impact their career?
-WERID thing is innovative
-
-    Significance: Describe how the project addresses an important problem or a critical barrier to progress in the field and how it can advance knowledge in the ICSR Research Themes.
-
-We specifically expect to examine ICSR's Research Themes of inclusivity, research careers, and research globalization.
-As we examine these themes, it will a bring new knowledge of how big team science projects impact each theme and field of study.
+WEIRD thing is innovative
 

### 2022-09-02 04.manuscript_scopus.Rmd
edits and clean up

--- 2022-08-26 04.manuscript_scopus.Rmd
@@
 shorttitle        : "Big Team Science"
-
 author: 
@@
 affiliation:
+
   - id            : "1"
@@
     institution   : "University of Alabama"
-
 authornote: |
@@
   Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript. 
-
 abstract: |
@@
   <!-- https://tinyurl.com/ybremelq -->
-
 keywords          : "big team, science, authorship, credit"
 wordcount         : "X"
-
 #bibliography      : ["big_team_refs.bib"]
-
 floatsintext      : no
@@
 draft             : no
-
 documentclass     : "apa6"
@@
 output            : papaja::apa6_pdf
+editor_options: 
+  markdown: 
+    wrap: 72
+bibliography: references.bib
 ---
@@
 
-science collaboration overall (sav)
-  - what is collaboration
-  - is it increasing 
-  - globalization should help
+According to the Oxford English dictionary, collaboration is two or more
+people working together to achieve a certain goal [@oed2016].
+Collaboration in scientific endeavors involves multiple researchers at
+(potentially) multiple institutions to communicate and work together to
+advance knowledge in their chosen field. Collaboration can look
+differently in every project dependent on the skill sets, hypotheses,
+and perspectives of your collaborators. While collaboration is not new
+in science, the current interest of "big team science" is increasing
+[@forscher2020; @stewart2017; @coles2022]. Big team science projects
+and/or organizations utilize and run on large-scale collaboration to
+ensure that diverse populations and ideas are brought into research
+projects, which in turn allows for more reliability and generalizability
+in the results and method of the study. For this study, Big Team Science
+(BTS) will be defined as a collaboration of ten or more authors from at
+least ten different institutions.
 
-rise of big team science because the need for resources, replication, reproducibility, generalization (erin)
-  - physics
-  - biology 
-  - psychology
+Big Team Science appears to be increasing as a result of two sources: 1)
+increasing globalization and technology that allows for real-time
+interdisciplinary research, and 2) increasing interest in
+reproducibility, replication, and generalizability [@maxwell2015;
+@nelson2018; @zwaan2018]. Technological advances have provided easier
+ways to collaborate with people who are from other universities and
+countries through document sharing platforms (e.g., Google, GitHub, and
+the Open Science Framework), video chatting platforms (e.g., Zoom,
+Microsoft Teams), and messaging and project management platforms (e.g.,
+Slack, Trello, when2meet, etc.). The credibility movement seems to
+suggest that by having both collaborations that span across the globe
+and subfield of psychology, age groups and education levels should help
+to drive psychological science in the path of better materials,
+reliability, generalizability and more robust sample size in a study.
+(ADD CITES)
 
-metascience (erin)
-  - most research is on lessons learned, why bts is useful
-  - little research on who/fields has done bts
-  - has the globalization of science actually impacted people other than NA and Europe
+ADD STUFF ABOUT THE CREDIBILITY MOVEMENT HERE....
+
+rise of big team science because the need for resources, replication,
+reproducibility, generalization (erin) - physics - biology - psychology
+
+metascience (erin) - most research is on lessons learned, why bts is
+useful - little research on who/fields has done bts - has the
+globalization of science actually impacted people other than NA and
+Europe
 
@@
 
-Collaboration in scientific endeavors involves multiple researchers at multiple institutions to communicate and work together to advance knowledge in their chosen field.
-While collaboration is not new in science, the current interest of "big team science" is increasing.
-We define big team science as at least ten authors with ten different institutional affiliations.
-The globalization of science has allowed researchers across the world to contribute to research projects, but little research has examined *who* participates in big team science projects.
-
-idea of BTS is not new, but interest is new, and globalization allows us to do BTS with projects such as PSA/CERN/Reproducibility projects.
-But we don't know if this uptick in large scale projects has diversified the *people* involved in BTS.
-Is this increasing inclusivity?
-At what level of career are people doing BTS?
-Is that changing over time?
-And how is that including new and varied researchers outside NA and Europe?
-Are we including people in positions that may impact their career?
-WERID thing is innovative
-
     Significance: Describe how the project addresses an important problem or a critical barrier to progress in the field and how it can advance knowledge in the ICSR Research Themes.
 
-We specifically expect to examine ICSR's Research Themes of inclusivity, research careers, and research globalization.
-As we examine these themes, it will a bring new knowledge of how big team science projects impact each theme and field of study.
+We specifically expect to examine ICSR's Research Themes of inclusivity,
+research careers, and research globalization. As we examine these
+themes, it will bring new knowledge of how big team science projects
+impact each theme and field of study.
+
+The globalization of science has allowed researchers across the world to
+contribute to research projects, but little research has examined *who*
+participates in big team science projects. We see an increase in BTS but
+we don't know if this uptick in large scale projects has diversified the
+*people* involved in BTS. Is this increasing inclusivity? At what level
+of career are people doing BTS? Is that changing over time? And how is
+that including new and varied researchers outside NA and Europe? Are we
+including people in positions that may impact their career? WEIRD thing
+is innovative
 
@@
 
-We will aim for high impact broad scope journals such as *Science*, *Nature* or *Nature Human Behaviour*.
-Other journals would include review publications within psychology to compare the social sciences to other sciences: *Perspectives in Psychological Science*, *Psychological Bulletin*, *Psychological Review*, or *Current Directions in Psychological Science*.
+We will aim for high impact broad scope journals such as *Science*,
+*Nature* or *Nature Human Behaviour*. Other journals would include
+review publications within psychology to compare the social sciences to
+other sciences: *Perspectives in Psychological Science*, *Psychological
+Bulletin*, *Psychological Review*, or *Current Directions in
+Psychological Science*.
 
@@
 -   Research Question 1: What journals publish big team science papers?
-- Research Question 2: What are the types of articles that are being published in big team science?
+-   Research Question 2: What are the types of articles that are being
+    published in big team science?
 -   Research Question 3: Who is involved in big team science?
 
-For each of these research questions, we will examine the overall results of all big team research projects, and examine for change in result trends across years of publication.
+For each of these research questions, we will examine the overall
+results of all big team research projects, and examine for change in
+result trends across years of publication.
 
@@
 
-We defined **big team science publications** as publications with at least 10 authors that were published in peer-reviewed journals or had posted a full paper pre-print for publication review.
-We specifically focused on social science research, primarily *psychology* for this manuscript.
-First, we added all known publications from collaborative teams, such as the PSA, Many Labs, and Many Babies.
-We examined journals that frequently publish registered replication reports (i.e., *Advances in Methods and Practices in Psychological Science*) for additional publications with at least 10 authors.
-From these manuscripts, we identified common authors who frequently participate in these studies, and examined their Google Scholar or Open Researcher and Contributor IDentifier (ORCID) page for other publications.
-We reached out to social networks on Twitter to identify other publications.
-Last, we used Google Scholar and EBSCO to search for large projects using the following search terms: collaboration, multicultural, large scale, and big team science.
+We defined **big team science publications** as publications with at
+least 10 authors that were published in peer-reviewed journals or had
+posted a full paper pre-print for publication review. We specifically
+focused on social science research, primarily *psychology* for this
+manuscript. First, we added all known publications from collaborative
+teams, such as the PSA, Many Labs, and Many Babies. We examined journals
+that frequently publish registered replication reports (i.e., *Advances
+in Methods and Practices in Psychological Science*) for additional
+publications with at least 10 authors. From these manuscripts, we
+identified common authors who frequently participate in these studies,
+and examined their Google Scholar or Open Researcher and Contributor
+IDentifier (ORCID) page for other publications. We reached out to social
+networks on Twitter to identify other publications. Last, we used Google
+Scholar and EBSCO to search for large projects using the following
+search terms: collaboration, multicultural, large scale, and big team
+science.
 
-- definition for big team size: 10 authors + at least 10 different institutions
-- we will use all categories but break into the big four: https://service.elsevier.com/app/answers/detail/a_id/14882/supporthub/scopus/~/what-are-the-most-frequent-subject-area-categories-and-classifications-used-in/
+-   definition for big team size: 10 authors + at least 10 different
+    institutions
+-   we will use all categories but break into the big four:
+    <https://service.elsevier.com/app/answers/detail/a_id/14882/supporthub/scopus/~/what-are-the-most-frequent-subject-area-categories-and-classifications-used-in/>
 -   we would get everything from df_ani
@@
 
-Using these criteria, we identified `r nrow(bibs)` articles for inclusion on this manuscript.
-The publication dates on these articles ranged from `r min(bibs$YEAR)` to `r max(bibs$YEAR)`, and we used the pre-print last updated date as the publication date for those articles.
-The current impact factor (i.e., 2022) for each journal was found on the journal page and included for journal statistics.
+Using these criteria, we identified `r nrow(bibs)` articles for
+inclusion on this manuscript. The publication dates on these articles
+ranged from `r min(bibs$YEAR)` to `r max(bibs$YEAR)`, and we used the
+pre-print last updated date as the publication date for those articles.
+The current impact factor (i.e., 2022) for each journal was found on the
+journal page and included for journal statistics.
 
-journal information we could include:
-  - total number of articles overall 
-  - number of distinct journals in each of the four areas 
-  - JIF df_sources, snip
-  - https://liu.cwp.libguides.com/c.php?g=45770&p=4417804
+journal information we could include: - total number of articles
+overall - number of distinct journals in each of the four areas - JIF
+df_sources, snip -
+<https://liu.cwp.libguides.com/c.php?g=45770&p=4417804>
 
@@
 
-For each publication, we coded the list of keywords into broad labels for areas of social science (i.e., Social Psychology, Cognitive Psychology).
-In this section, we elected to code each article with only one main research area.
-Research is often cross-disciplinary, however, for simplicity, we applied one global label to each article that represented the perceived main area of study (based on what course this material might be taught in, the publication journal focus).
-The list of broad areas includes clinical, cognitive, developmental, educational, and social psychology.
-Last, we included a metascience category that covered articles that were detailing the science of science.
-The Open Science Collaboration [CITE] was included in this category because the aim of the paper was a focus on replication across multiple field types.
-Other metascience categories included papers that focused on research degrees of freedom, analysis choices, and types of samples.
+For each publication, we coded the list of keywords into broad labels
+for areas of social science (i.e., Social Psychology, Cognitive
+Psychology). In this section, we elected to code each article with only
+one main research area. Research is often cross-disciplinary, however,
+for simplicity, we applied one global label to each article that
+represented the perceived main area of study (based on what course this
+material might be taught in, the publication journal focus). The list of
+broad areas includes clinical, cognitive, developmental, educational,
+and social psychology. Last, we included a metascience category that
+covered articles that were detailing the science of science. The Open
+Science Collaboration [CITE] was included in this category because the
+aim of the paper was a focus on replication across multiple field types.
+Other metascience categories included papers that focused on research
+degrees of freedom, analysis choices, and types of samples.
 
-- keywords are easier now - could use the ASJC smaller subfield areas to create a list 
-- https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/
+-   keywords are easier now - could use the ASJC smaller subfield areas
+    to create a list
+-   <https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/>
 -   table of all the codes
@@
 
-The author list was then extracted from each publication.
-In the case of consortium authorship, we extracted the complete authorship from the meta-data or pre-print publication.
-The total number of unique authors was `r nrow(id_list)`.
-The number of authors on each publication ranged from `r min(author_count$author_count)` to `r max(author_count$author_count)` with an average of `r format(mean(author_count$author_count), nsmall = 2, digits = 2)` authors (*SD* = `r format(sd(author_count$author_count), nsmall = 2, digits = 2)`).
+The author list was then extracted from each publication. In the case of
+consortium authorship, we extracted the complete authorship from the
+meta-data or pre-print publication. The total number of unique authors
+was `r nrow(id_list)`. The number of authors on each publication ranged
+from `r min(author_count$author_count)` to
+`r max(author_count$author_count)` with an average of
+`r format(mean(author_count$author_count), nsmall = 2, digits = 2)`
+authors (*SD* =
+`r format(sd(author_count$author_count), nsmall = 2, digits = 2)`).
 
@@
 
-Next, we matched each author to their Google Scholar and ORCID profile pages, if available.
-We originally used the *R* packages, *rorcid* [CITE] and *scholar* [CITE] to try to match published author names to profile pages.
-This process did not result in a large number of matches, and we therefore curated the list of profile pages manually, checking each author against the publication list.
-We used these two packages and profile pages to collect authorship statistics described below.
-If a researcher was not present in either of these databases, their information was excluded from the relevant analyses below.
+Next, we matched each author to their Google Scholar and ORCID profile
+pages, if available. We originally used the *R* packages, *rorcid*
+[CITE] and *scholar* [CITE] to try to match published author names to
+profile pages. This process did not result in a large number of matches,
+and we therefore curated the list of profile pages manually, checking
+each author against the publication list. We used these two packages and
+profile pages to collect authorship statistics described below. If a
+researcher was not present in either of these databases, their
+information was excluded from the relevant analyses below.
 
-- here we would pull all author ids and then grab all their papers - grab from the whole dataset not just 1970
+-   here we would pull all author ids and then grab all their papers -
+    grab from the whole dataset not just 1970
 
-**_Career Length_**.
-Career length for each author was defined using multiple variables to see if results from the two data sources would converge on similar answers.
-Both ORCID and Google Scholar provide a list of publications for authors, and we first calculated career length as the year of first publication listed for each author.
-In ORCID, a researcher can enter their educational background with completion years for each degree.
-We defined career length for this variable as years since first degree listed.
-Publication years are often curated directly from meta-data provided by Crossref (ORCID) or online sources used by Google Scholar.
-Authors may also directly add publications and their information into both systems.
-The limitation to using education as a metric for career length is that the researcher must directly enter this information into ORCID.
+***Career Length***. Career length for each author was defined using
+multiple variables to see if results from the two data sources would
+converge on similar answers. Both ORCID and Google Scholar provide a
+list of publications for authors, and we first calculated career length
+as the year of first publication listed for each author. In ORCID, a
+researcher can enter their educational background with completion years
+for each degree. We defined career length for this variable as years
+since first degree listed. Publication years are often curated directly
+from meta-data provided by Crossref (ORCID) or online sources used by
+Google Scholar. Authors may also directly add publications and their
+information into both systems. The limitation to using education as a
+metric for career length is that the researcher must directly enter this
+information into ORCID.
 
@@
 
-**_Employment_**.
-Employment information was collected from self-entered ORCID data.
-These values are open text, and therefore, we coded them into coherent categories for traditional educational (graduate student, post doctoral, lecturer),  tenure track (assistant, associate, full professor), and other roles (fellow, research assistant, researcher, head).
-Employment geopolitical region was also selected when available.
+***Employment***. Employment information was collected from self-entered
+ORCID data. These values are open text, and therefore, we coded them
+into coherent categories for traditional educational (graduate student,
+post doctoral, lecturer), tenure track (assistant, associate, full
+professor), and other roles (fellow, research assistant, researcher,
+head). Employment geopolitical region was also selected when available.
 
-- can't get this part really - we could get institution from publication and country from publication
+-   can't get this part really - we could get institution from
+    publication and country from publication
 
-**_Education_**.
-As with employment information, we also collected education information from self-entered ORCID data.
-These values were coded into general categories of bachelor, master, and doctoral degrees.
-The geopolitical region of the listed education was included when available.
-For analyses, both employment and education levels were grouped into United Nation regions.
+***Education***. As with employment information, we also collected
+education information from self-entered ORCID data. These values were
+coded into general categories of bachelor, master, and doctoral degrees.
+The geopolitical region of the listed education was included when
+available. For analyses, both employment and education levels were
+grouped into United Nation regions.
 
@@
 
-**_Types of Publications_**.
-ORCID includes information about the type of publication pulled from either researcher entered data or Crossref.
-We coded these publications into general categories including book, conference presentations, data-sets, journal articles, preprints, software, thesis, and other publications.
+***Types of Publications***. ORCID includes information about the type
+of publication pulled from either researcher entered data or Crossref.
+We coded these publications into general categories including book,
+conference presentations, data-sets, journal articles, preprints,
+software, thesis, and other publications.
 
@@
 
-The classification of the publication, which may be: ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.
+The classification of the publication, which may be: ab Abstract Report,
+ar Article, ip Article in Press, bk Book, bz Business Article, ch Book
+Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed
+Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press
+Release, rp Report, re Review, sh Survey, tb Retracted.
 
@@
 
-**_Publication Metrics_**.
-We calculated total number of publications of any type from both Google Scholar and ORCID.
-We additionally pulled both the h-index and i-10 index from Google Scholar.
-The h-index represents the highest *h* number of publications that have at least *h* citations, while the i-10 index represents the number of publications with at least 10 citations.
+***Publication Metrics***. We calculated total number of publications of
+any type from both Google Scholar and ORCID. We additionally pulled both
+the h-index and i-10 index from Google Scholar. The h-index represents
+the highest *h* number of publications that have at least *h* citations,
+while the i-10 index represents the number of publications with at least
+10 citations.
 
@@
 
-Results for types of journals will include a summary of the journals that publish big-team science papers and an average of the 2-year and 5-year impact factors for the journals.
+Results for types of journals will include a summary of the journals
+that publish big-team science papers and an average of the 2-year and
+5-year impact factors for the journals.
 
@@
 
-Results for types of articles will include a summary of the coded areas for each article, presented overall and across the years of publication.
+Results for types of articles will include a summary of the coded areas
+for each article, presented overall and across the years of publication.
 
-### RQ3: Authors. \
+### RQ3: Authors.
 
-We will use $\alpha$ < .05 for all analyses that involve hypothesis testing. We make no directional predictions.
+We will use $\alpha$ \< .05 for all analyses that involve hypothesis
+testing. We make no directional predictions.
 
-**_Career Length_**.
-For each of the three variables in career length (ORCID year of first pub, Scholar year of first pub, ORCID year of first degree), we will create a visualization of the trend and variance of researcher career length across publication years.
-To analyze trends over time, we will use the slope from a multilevel model (MLM) using the individual as a random intercept, career length as the dependent variable, and year of publication as the predictor variable.
-MLMs are regression models that control for the correlated error due to the repeated and nested nature of the data [CITE].
-In this model, each individual's starting career length is arbitrary, which we allow to vary with the random intercept by participant.
-A positive slope for year of publication would indicate increasing years of first publication (i.e., more younger scholars over time), while a negative slope would indicate older years of first publication (i.e., more older scholars over time).
-In order to show variance between individuals, we will report the variance component of the random intercept for individuals.
-Finally, to examine variance over time, we will calculate the standard deviation of the individual within each publication (i.e., one standard deviation for each article), and use a linear model with year predicting these standard deviations.
-This model is a traditional simultaneous regression, as averaging the variance by title eliminates the repeated measures variable (individuals).
-A positive slope would indicate increasing variance over time (i.e., more diversity in the career lengths of scholars), while a negative slope would indicate less variance and diversity in scholars over time.
+***Career Length***. For each of the three variables in career length
+(ORCID year of first pub, Scholar year of first pub, ORCID year of first
+degree), we will create a visualization of the trend and variance of
+researcher career length across publication years. To analyze trends
+over time, we will use the slope from a multilevel model (MLM) using the
+individual as a random intercept, career length as the dependent
+variable, and year of publication as the predictor variable. MLMs are
+regression models that control for the correlated error due to the
+repeated and nested nature of the data [CITE]. In this model, each
+individual's starting career length is arbitrary, which we allow to vary
+with the random intercept by participant. A positive slope for year of
+publication would indicate increasing years of first publication (i.e.,
+more younger scholars over time), while a negative slope would indicate
+older years of first publication (i.e., more older scholars over time).
+In order to show variance between individuals, we will report the
+variance component of the random intercept for individuals. Finally, to
+examine variance over time, we will calculate the standard deviation of
+the individual within each publication (i.e., one standard deviation for
+each article), and use a linear model with year predicting these
+standard deviations. This model is a traditional simultaneous
+regression, as averaging the variance by title eliminates the repeated
+measures variable (individuals). A positive slope would indicate
+increasing variance over time (i.e., more diversity in the career
+lengths of scholars), while a negative slope would indicate less
+variance and diversity in scholars over time.
 
 -   so we cant do MLM
-- for each paper we could calculate an average career length, then run the regression 
-- then calculate the standard deviation and do the same analysis as described
+-   for each paper we could calculate an average career length, then run
+    the regression
+-   then calculate the standard deviation and do the same analysis as
+    described
 
-**_Employment_**. We will summarize the general employment categories of individuals at the time of publication, along with a summary for change over time. 
-**_Education_**. We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.
+***Employment***. We will summarize the general employment categories of
+individuals at the time of publication, along with a summary for change
+over time. ***Education***. We will summarize the general education
+categories of individuals at the time of publication, along with a
+summary for change over time.
 
-**_Types of Publications_**. We will summarize the coded types of publications for individuals.
+***Types of Publications***. We will summarize the coded types of
+publications for individuals.
 
-**_Publication Metrics_**.
-We will report descriptive statistics on the total number of publications, i10 index, and h-index for individuals overall.
-Next, we will use the same analyses described in the career length section to analyze trends over time.
-An increasing slope over time indicates that individuals who are publishing more are more represented in big-team science over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
-A positive slope for variance indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
-While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.
-same idea average down by paper for mean and standard deviation
+***Publication Metrics***. We will report descriptive statistics on the
+total number of publications, i10 index, and h-index for individuals
+overall. Next, we will use the same analyses described in the career
+length section to analyze trends over time. An increasing slope over
+time indicates that individuals who are publishing more are more
+represented in big-team science over time (i.e., increasing numbers of
+scholars with higher publication rates), while a negative slope
+indicates more researchers with less publications. A positive slope for
+variance indicates increasing variance over time (i.e., more diversity
+in the individual publication rates), while a negative slope would
+indicate less diversity in researchers over time. While publication
+rates do not represent value as a researcher, they are often used in
+hiring and promotion decisions, and we will use this variable as a proxy
+to gauge the diversity in scholars represented in big teams. same idea
+average down by paper for mean and standard deviation
 
-**_Geopolitical Regions_**.
-We will present visualizations of the last listed education and job location, and we will discuss the areas of world in which authors generally come from, as well as the lowest representation of authors.
-To understand the change in representation diversity, we will summarize the total number of geopolitical regions for each paper.
-Using a linear model, we will examine if the number of regions present is predicted by the year of publication.
-Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope.
-Last, we will examine the differences in representation for corresponding author sets versus all other authors.
-For papers with 10 to 49 authors, we will use the three first authors and the last author to compare against random samples of other authors.
-For 50 to 99 authors, five first authors plus last will be used, and for all papers with more than 100 authors, we will use ten first authors and the last author.
-We will calculate the frequencies of each of the UN Sub-Regions for first authors.
-Then we will randomly sample all authors in subsets of the same size (i.e., 3+1, 5+1, 10+1), and average the frequencies of UN Sub-Regions across these random samples.
-We will randomly sample the same number of times as the size of the author list (i.e., a paper that has 54 authors will be randomly sampled 54 times with a sample size of six).
+***Geopolitical Regions***. We will present visualizations of the last
+listed education and job location, and we will discuss the areas of
+world in which authors generally come from, as well as the lowest
+representation of authors. To understand the change in representation
+diversity, we will summarize the total number of geopolitical regions
+for each paper. Using a linear model, we will examine if the number of
+regions present is predicted by the year of publication. Increasing
+diversity would be represented by a positive slope, while decreasing
+diversity would be represented by a negative slope. Last, we will
+examine the differences in representation for corresponding author sets
+versus all other authors. For papers with 10 to 49 authors, we will use
+the three first authors and the last author to compare against random
+samples of other authors. For 50 to 99 authors, five first authors plus
+last will be used, and for all papers with more than 100 authors, we
+will use ten first authors and the last author. We will calculate the
+frequencies of each of the UN Sub-Regions for first authors. Then we
+will randomly sample all authors in subsets of the same size (i.e., 3+1,
+5+1, 10+1), and average the frequencies of UN Sub-Regions across these
+random samples. We will randomly sample the same number of times as the
+size of the author list (i.e., a paper that has 54 authors will be
+randomly sampled 54 times with a sample size of six).
 
-- may not need to do this random sample thing if we have large enough datasets? 
+-   may not need to do this random sample thing if we have large enough
+    datasets?
 -   pool them together and then compare?
-- maybe group them in the sizes we are interested in, then convert to proportions
-- average those proportions ? plot comparisons of the proportions and confidence intervals for each group
+-   maybe group them in the sizes we are interested in, then convert to
+    proportions
+-   average those proportions ? plot comparisons of the proportions and
+    confidence intervals for each group
 
-Given the expected small sample sizes of these contingency tables (i.e., the largest could be *n* = 22 if all author information is available), we will group together titles based on time period using pre-2020, 2020, and post-2020 to show change over time.
-The choice of these groupings is based on the number of articles available within these time brackets.
-For each grouping, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors.
-Since this data is categorical, we will use Cramer's V to represent the effect size.
-If the effect size includes zero in it's confidence interval, this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity.
-Any confidence interval that does include zero represents a difference in diversity.
-We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero using standardized residuals.
+Given the expected small sample sizes of these contingency tables (i.e.,
+the largest could be *n* = 22 if all author information is available),
+we will group together titles based on time period using pre-2020, 2020,
+and post-2020 to show change over time. The choice of these groupings is
+based on the number of articles available within these time brackets.
+For each grouping, we will calculate the effect size of the differences
+in frequencies comparing first authors to all other authors. Since this
+data is categorical, we will use Cramer's V to represent the effect
+size. If the effect size includes zero in it's confidence interval, this
+result will imply that first and all other authors represent the same
+pattern of UN Sub-Region diversity. Any confidence interval that does
+include zero represents a difference in diversity. We will report these
+values and discuss what regions of the world are represented when effect
+sizes indicate a different from zero using standardized residuals.
 
@@
 
-Articles were most commonly published in `r journal_count$JOURNAL[1]` (*n* = `r journal_count$freq[1]`), `r journal_count$JOURNAL[2]` (*n* = `r journal_count$freq[2]`), `r journal_count$JOURNAL[3]` (*n* = `r journal_count$freq[3]`), `r journal_count$JOURNAL[4]` (*n* = `r journal_count$freq[4]`), and `r journal_count$JOURNAL[5]` (*n* = `r journal_count$freq[5]`).
-A complete list of journals can be found on our Open Science Framework page XXX.
-The average 2-year impact factor for official journal publications was `r format(mean(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)` (*SD* = `r format(sd(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)`) and the average 5-year impact factor was `r format(mean(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)` (*SD* = `r format(sd(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)`).
+Articles were most commonly published in `r journal_count$JOURNAL[1]`
+(*n* = `r journal_count$freq[1]`), `r journal_count$JOURNAL[2]` (*n* =
+`r journal_count$freq[2]`), `r journal_count$JOURNAL[3]` (*n* =
+`r journal_count$freq[3]`), `r journal_count$JOURNAL[4]` (*n* =
+`r journal_count$freq[4]`), and `r journal_count$JOURNAL[5]` (*n* =
+`r journal_count$freq[5]`). A complete list of journals can be found on
+our Open Science Framework page XXX. The average 2-year impact factor
+for official journal publications was
+`r format(mean(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)` (*SD* =
+`r format(sd(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)`) and the
+average 5-year impact factor was
+`r format(mean(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)` (*SD* =
+`r format(sd(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)`).
 
@@
 
-Articles were primarily `r article_overall$Var1[1]` (`r format(article_overall$Percent[1], nsmall = 1, digits = 1)`%) and `r article_overall$Var1[2]` (`r format(article_overall$Percent[2], nsmall = 1, digits = 1)`%), followed by smaller categories for `r article_overall$Var1[3]` (`r format(article_overall$Percent[3], nsmall = 1, digits = 1)`%), `r article_overall$Var1[4]` (`r format(article_overall$Percent[4], nsmall = 1, digits = 1)`%), `r article_overall$Var1[5]` (`r format(article_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r article_overall$Var1[6]` (`r format(article_overall$Percent[6], nsmall = 1, digits = 1)`%).
-Here, we will talk about the figure below and how the trends occur across time.
+Articles were primarily `r article_overall$Var1[1]`
+(`r format(article_overall$Percent[1], nsmall = 1, digits = 1)`%) and
+`r article_overall$Var1[2]`
+(`r format(article_overall$Percent[2], nsmall = 1, digits = 1)`%),
+followed by smaller categories for `r article_overall$Var1[3]`
+(`r format(article_overall$Percent[3], nsmall = 1, digits = 1)`%),
+`r article_overall$Var1[4]`
+(`r format(article_overall$Percent[4], nsmall = 1, digits = 1)`%),
+`r article_overall$Var1[5]`
+(`r format(article_overall$Percent[5], nsmall = 1, digits = 1)`%), and
+`r article_overall$Var1[6]`
+(`r format(article_overall$Percent[6], nsmall = 1, digits = 1)`%). Here,
+we will talk about the figure below and how the trends occur across
+time.
 
@@
 
-### RQ3: Authors. \
+### RQ3: Authors.
 
@@
 
-**_Career Length_**.
-The average career length was `r format(round(current_year - mean(o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(current_year - o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`) for ORCID first publication year (i.e., current year minus year of first publication), *M* = `r format(round(current_year - mean(s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(current_year - s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`) for Scholar year of first publication, and *M* = `r format(round(current_year - mean(o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(current_year - o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`) for ORCID year of first degree.
-In each of the analyses, we use the actual year of first publication/education, as subtracting publication and using it as a predictor would create a perfect solution for each model.
+***Career Length***. The average career length was
+`r format(round(current_year - mean(o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`
+(*SD* =
+`r format(round(sd(current_year - o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`)
+for ORCID first publication year (i.e., current year minus year of first
+publication), *M* =
+`r format(round(current_year - mean(s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`
+(*SD* =
+`r format(round(sd(current_year - s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`)
+for Scholar year of first publication, and *M* =
+`r format(round(current_year - mean(o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`
+(*SD* =
+`r format(round(sd(current_year - o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`)
+for ORCID year of first degree. In each of the analyses, we use the
+actual year of first publication/education, as subtracting publication
+and using it as a predictor would create a perfect solution for each
+model.
 
@@
 
-  - The slope for year of first publication was *b* = `r format(round(o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_output$df[2]`) = `r format(round(o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_output$p.value[2])`.
-  - The variance parameter was *SD* = `r format(round(o_career_output$estimate[3], digits = 2), nsmall = 2)`. 
-  - The slope for variance across years was *b* = `r format(round(var_o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_model$df.residual`) = `r format(round(var_o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_output$p.value[2])`.
+-   The slope for year of first publication was *b* =
+    `r format(round(o_career_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(o_career_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r o_career_output$df[2]`) =
+    `r format(round(o_career_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(o_career_output$p.value[2])`.
+-   The variance parameter was *SD* =
+    `r format(round(o_career_output$estimate[3], digits = 2), nsmall = 2)`.
+-   The slope for variance across years was *b* =
+    `r format(round(var_o_career_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(var_o_career_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r var_o_career_model$df.residual`) =
+    `r format(round(var_o_career_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(var_o_career_output$p.value[2])`.
 
@@
 
-  - The slope for year of first publication was *b* = `r format(round(s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r s_career_output$df[2]`) = `r format(round(s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(s_career_output$p.value[2])`.
-  - The variance parameter was *SD* = `r format(round(s_career_output$estimate[3], digits = 2), nsmall = 2)`. 
-  - The slope for variance across years was *b* = `r format(round(var_s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_s_career_model$df.residual`) = `r format(round(var_s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_s_career_output$p.value[2])`.
+-   The slope for year of first publication was *b* =
+    `r format(round(s_career_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(s_career_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r s_career_output$df[2]`) =
+    `r format(round(s_career_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(s_career_output$p.value[2])`.
+-   The variance parameter was *SD* =
+    `r format(round(s_career_output$estimate[3], digits = 2), nsmall = 2)`.
+-   The slope for variance across years was *b* =
+    `r format(round(var_s_career_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(var_s_career_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r var_s_career_model$df.residual`) =
+    `r format(round(var_s_career_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(var_s_career_output$p.value[2])`.
 
@@
 
-  - The slope for year of first degree was *b* = `r format(round(o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_ed_output$df[2]`) = `r format(round(o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_ed_output$p.value[2])`.
-  - The variance parameter was *SD* = `r format(round(o_career_ed_output$estimate[3], digits = 2), nsmall = 2)`. 
-  - The slope for variance across years was *b* = `r format(round(var_o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_ed_model$df.residual`) = `r format(round(var_o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_ed_output$p.value[2])`.
+-   The slope for year of first degree was *b* =
+    `r format(round(o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r o_career_ed_output$df[2]`) =
+    `r format(round(o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(o_career_ed_output$p.value[2])`.
+-   The variance parameter was *SD* =
+    `r format(round(o_career_ed_output$estimate[3], digits = 2), nsmall = 2)`.
+-   The slope for variance across years was *b* =
+    `r format(round(var_o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(var_o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r var_o_career_ed_model$df.residual`) =
+    `r format(round(var_o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(var_o_career_ed_output$p.value[2])`.
 
-Then we will discuss how these results are represented in our graph (below). We will discuss any discrepancies in the results across the three different statistics.
+Then we will discuss how these results are represented in our graph
+(below). We will discuss any discrepancies in the results across the
+three different statistics.
 
@@
 
-**_Employment_**.
-Overall, individuals **at the time of publication** in big team science publications are  `r employment_overall$Var1[1]` (`r format(employment_overall$Percent[1], nsmall = 1, digits = 1)`%) and `r employment_overall$Var1[2]` (`r format(employment_overall$Percent[2], nsmall = 1, digits = 1)`%), followed by smaller categories for `r employment_overall$Var1[3]` (`r format(employment_overall$Percent[3], nsmall = 1, digits = 1)`%), `r employment_overall$Var1[4]` (`r format(employment_overall$Percent[4], nsmall = 1, digits = 1)`%), `r employment_overall$Var1[5]` (`r format(employment_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r employment_overall$Var1[6]` (`r format(employment_overall$Percent[6], nsmall = 1, digits = 1)`%).
-Here, we will talk about the figure below and how the trends occur across time.
-We will also comment on the number of jobs that would be considered "non-academic".
+***Employment***. Overall, individuals **at the time of publication** in
+big team science publications are `r employment_overall$Var1[1]`
+(`r format(employment_overall$Percent[1], nsmall = 1, digits = 1)`%) and
+`r employment_overall$Var1[2]`
+(`r format(employment_overall$Percent[2], nsmall = 1, digits = 1)`%),
+followed by smaller categories for `r employment_overall$Var1[3]`
+(`r format(employment_overall$Percent[3], nsmall = 1, digits = 1)`%),
+`r employment_overall$Var1[4]`
+(`r format(employment_overall$Percent[4], nsmall = 1, digits = 1)`%),
+`r employment_overall$Var1[5]`
+(`r format(employment_overall$Percent[5], nsmall = 1, digits = 1)`%),
+and `r employment_overall$Var1[6]`
+(`r format(employment_overall$Percent[6], nsmall = 1, digits = 1)`%).
+Here, we will talk about the figure below and how the trends occur
+across time. We will also comment on the number of jobs that would be
+considered "non-academic".
 
@@
 
-**_Education_**.
-Overall, individuals **at the time of publication** in big team science publications are  `r education_overall$Var1[1]` (`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%), `r education_overall$Var1[2]` (`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and `r education_overall$Var1[3]` (`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%).
-Here, we will talk about the figure below and how the trends occur across time.
+***Education***. Overall, individuals **at the time of publication** in
+big team science publications are `r education_overall$Var1[1]`
+(`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%),
+`r education_overall$Var1[2]`
+(`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and
+`r education_overall$Var1[3]`
+(`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%).
+Here, we will talk about the figure below and how the trends occur
+across time.
 
@@
 
-**_Types of Publications_**.
-In general, the most common type of publication was `r publication_overall$Var1[1]` (`r format(publication_overall$Percent[1], nsmall = 1, digits = 1)`%), followed by `r publication_overall$Var1[2]` (`r format(publication_overall$Percent[2], nsmall = 1, digits = 1)`%), and smaller categories for `r publication_overall$Var1[3]` (`r format(publication_overall$Percent[3], nsmall = 1, digits = 1)`%), `r publication_overall$Var1[4]` (`r format(publication_overall$Percent[4], nsmall = 1, digits = 1)`%), `r publication_overall$Var1[5]` (`r format(publication_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r publication_overall$Var1[6]` (`r format(publication_overall$Percent[6], nsmall = 1, digits = 1)`%).
+***Types of Publications***. In general, the most common type of
+publication was `r publication_overall$Var1[1]`
+(`r format(publication_overall$Percent[1], nsmall = 1, digits = 1)`%),
+followed by `r publication_overall$Var1[2]`
+(`r format(publication_overall$Percent[2], nsmall = 1, digits = 1)`%),
+and smaller categories for `r publication_overall$Var1[3]`
+(`r format(publication_overall$Percent[3], nsmall = 1, digits = 1)`%),
+`r publication_overall$Var1[4]`
+(`r format(publication_overall$Percent[4], nsmall = 1, digits = 1)`%),
+`r publication_overall$Var1[5]`
+(`r format(publication_overall$Percent[5], nsmall = 1, digits = 1)`%),
+and `r publication_overall$Var1[6]`
+(`r format(publication_overall$Percent[6], nsmall = 1, digits = 1)`%).
 We will include all information over 1% of the publication totals.
@@
 
-**_Publication Metrics_**.
-The average number of all publications per individual was *M* = `r format(round(mean(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`) using ORCID and *M* = `r format(round(mean(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`) using Google Scholar.
-The average i10 index was *M* = `r format(round(mean(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`) and the average h-index was *M* = `r format(round(mean(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`).
+***Publication Metrics***. The average number of all publications per
+individual was *M* =
+`r format(round(mean(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`
+(*SD* =
+`r format(round(sd(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`)
+using ORCID and *M* =
+`r format(round(mean(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`
+(*SD* =
+`r format(round(sd(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`)
+using Google Scholar. The average i10 index was *M* =
+`r format(round(mean(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`
+(*SD* =
+`r format(round(sd(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`)
+and the average h-index was *M* =
+`r format(round(mean(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`
+(*SD* =
+`r format(round(sd(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`).
 
@@
 
-  - The slope for number of publications was *b* = `r format(round(o_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_total_output$df[2]`) = `r format(round(o_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_total_output$p.value[2])`.
-  - The variance parameter was *SD* = `r format(round(o_total_output$estimate[3], digits = 2), nsmall = 2)`. 
-  - The slope for variance across years was *b* = `r format(round(var_o_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_total_model$df.residual`) = `r format(round(var_o_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_total_output$p.value[2])`.
+-   The slope for number of publications was *b* =
+    `r format(round(o_total_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(o_total_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r o_total_output$df[2]`) =
+    `r format(round(o_total_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(o_total_output$p.value[2])`.
+-   The variance parameter was *SD* =
+    `r format(round(o_total_output$estimate[3], digits = 2), nsmall = 2)`.
+-   The slope for variance across years was *b* =
+    `r format(round(var_o_total_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(var_o_total_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r var_o_total_model$df.residual`) =
+    `r format(round(var_o_total_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(var_o_total_output$p.value[2])`.
 
@@
 
-  - The slope for year of first publication was *b* = `r format(round(s_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(s_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r s_total_output$df[2]`) = `r format(round(s_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(s_total_output$p.value[2])`.
-  - The variance parameter was *SD* = `r format(round(s_total_output$estimate[3], digits = 2), nsmall = 2)`. 
-  - The slope for variance across years was *b* = `r format(round(var_s_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_s_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_s_total_model$df.residual`) = `r format(round(var_s_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_s_total_output$p.value[2])`.
+-   The slope for year of first publication was *b* =
+    `r format(round(s_total_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(s_total_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r s_total_output$df[2]`) =
+    `r format(round(s_total_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(s_total_output$p.value[2])`.
+-   The variance parameter was *SD* =
+    `r format(round(s_total_output$estimate[3], digits = 2), nsmall = 2)`.
+-   The slope for variance across years was *b* =
+    `r format(round(var_s_total_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(var_s_total_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r var_s_total_model$df.residual`) =
+    `r format(round(var_s_total_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(var_s_total_output$p.value[2])`.
 
-**_Geopolitical Regions_**. We will first present two figures for education and employment geopolitical regions representation in scholars.
+***Geopolitical Regions***. We will first present two figures for
+education and employment geopolitical regions representation in
+scholars.
 
@@
 
-Next, we will report the results of two linear regression models.
-The independent variable is year of publication, and the dependent variables include the summary of the total number of different geopolitical regions represented in each publication.
-- The slope for the education model was *b* = `r format(round(edu_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(edu_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r edu_country_model$df.residual`) = `r format(round(edu_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(edu_country_output$p.value[2])`.
+Next, we will report the results of two linear regression models. The
+independent variable is year of publication, and the dependent variables
+include the summary of the total number of different geopolitical
+regions represented in each publication. - The slope for the education
+model was *b* =
+`r format(round(edu_country_output$estimate[2], digits = 2), nsmall = 2)`,
+*SE* =
+`r format(round(edu_country_output$std.error[2], digits = 2), nsmall = 2)`,
+*t*(`r edu_country_model$df.residual`) =
+`r format(round(edu_country_output$statistic[2], digits = 2), nsmall = 2)`,
+*p* = `r printp(edu_country_output$p.value[2])`.
 
-- The slope for the employment model was *b* = `r format(round(job_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(job_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r job_country_model$df.residual`) = `r format(round(job_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(job_country_output$p.value[2])`.
+-   The slope for the employment model was *b* =
+    `r format(round(job_country_output$estimate[2], digits = 2), nsmall = 2)`,
+    *SE* =
+    `r format(round(job_country_output$std.error[2], digits = 2), nsmall = 2)`,
+    *t*(`r job_country_model$df.residual`) =
+    `r format(round(job_country_output$statistic[2], digits = 2), nsmall = 2)`,
+    *p* = `r printp(job_country_output$p.value[2])`.
 
-Last, we will examine the effect sizes of the UN Sub-Regions represented for each grouped year of analysis. Tables of the UN Sub-Regions will be presented in our supplemental documents.
+Last, we will examine the effect sizes of the UN Sub-Regions represented
+for each grouped year of analysis. Tables of the UN Sub-Regions will be
+presented in our supplemental documents.
 
-- Pre-2020: `r v_pre2020$estimate` and `r x_pre2020$stdres` will be used to discuss pre-2020 manuscripts.
+-   Pre-2020: `r v_pre2020$estimate` and `r x_pre2020$stdres` will be
+    used to discuss pre-2020 manuscripts.
 
-- 2020: `r v_2020$estimate` and `r x_2020$stdres` will be used to discuss 2020 manuscripts.
+-   2020: `r v_2020$estimate` and `r x_2020$stdres` will be used to
+    discuss 2020 manuscripts.
 
-- Post-2020: `r v_post2020$estimate` and `r x_post2020$stdres` will be used to discuss post-2020 manuscripts.
+-   Post-2020: `r v_post2020$estimate` and `r x_post2020$stdres` will be
+    used to discuss post-2020 manuscripts.
 
@@
 
-- Discuss the limitation of "who is using ORCID and Scholar" which can bias our results. 
+-   Discuss the limitation of "who is using ORCID and Scholar" which can
+    bias our results.
 -   Other limitations will be included.
@@
 
+```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
 
-<div id="refs" custom-style="Bibliography"></div>
+```{=tex}
 \endgroup
+```

### 2022-09-09 04.manuscript_scopus.Rmd
finish up the else draft

@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+  This paper will examine the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions.
+As interest in BTS increases, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
+The types of publication outlets, number of publications, and subject areas of publication will be presented to summarize the publications in BTS.
+Information about authors included in BTS will be presented including career length, numbers of publications/impact variables, education, and affiliation.
+Last, we will explore the representation of geopolitical regions by examining affiliation location to explore the impact of BTS on the de-WEIRD movement to diversify researcher representation.
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
 keywords          : "big team, science, authorship, credit"
 wordcount         : "X"
-#bibliography      : ["big_team_refs.bib"]
 floatsintext      : no
@@
 draft             : no
-documentclass     : "apa6"
+#documentclass     : "apa6"
 classoption       : "man"
-output            : papaja::apa6_pdf
+#output            : papaja::apa6_pdf
 editor_options: 
@@
 bibliography: references.bib
+
+header-includes:
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass     : "apa7"
+output            : papaja::apa6_pdf
 ---
@@
 library(knitr)
-library(cowplot)
-library(broom.mixed)
-current_year <- 2022
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(538943)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
-
-```{r bringinanalysis, include = FALSE, echo = FALSE}
-output <- knit_child("03.data_analysis.Rmd")
 ```
@@
 (potentially) multiple institutions to communicate and work together to
-advance knowledge in their chosen field. Collaboration can look
-differently in every project dependent on the skill sets, hypotheses,
-and perspectives of your collaborators. While collaboration is not new
-in science, the current interest of "big team science" is increasing
+advance knowledge in their chosen field. Collaboration can manifest
+uniquely in each project dependent on the skill sets, hypotheses, and
+perspectives of collaborators. While collaboration is not new in
+science, the current interest of "big team science" is increasing
 [@forscher2020; @stewart2017; @coles2022]. Big team science projects
@@
 
-Big Team Science appears to be increasing as a result of two sources: 1)
-increasing globalization and technology that allows for real-time
-interdisciplinary research, and 2) increasing interest in
-reproducibility, replication, and generalizability [@maxwell2015;
-@nelson2018; @zwaan2018]. Technological advances have provided easier
-ways to collaborate with people who are from other universities and
-countries through document sharing platforms (e.g., Google, GitHub, and
-the Open Science Framework), video chatting platforms (e.g., Zoom,
-Microsoft Teams), and messaging and project management platforms (e.g.,
-Slack, Trello, when2meet, etc.). The credibility movement seems to
-suggest that by having both collaborations that span across the globe
-and subfield of psychology, age groups and education levels should help
-to drive psychological science in the path of better materials,
-reliability, generalizability and more robust sample size in a study.
-(ADD CITES)
+BTS appears to be increasing as a result of two sources: 1) increasing
+globalization and technology that allows for real-time interdisciplinary
+research, and 2) increasing interest in reproducibility, replication,
+and generalizability [@maxwell2015; @nelson2018; @zwaan2018].
+Technological advances have provided easier ways to collaborate with
+people who are from other universities and countries through document
+sharing platforms (e.g., Google, GitHub, and the Open Science
+Framework), video chatting platforms (e.g., Zoom, Microsoft Teams), and
+messaging and project management platforms (e.g., Slack, Trello,
+when2meet, etc.). The credibility movement seems to suggest that by
+having both collaborations that span across the globe and subfield of
+psychology, age groups, and education levels should help to drive
+psychological science in the path of better materials, reliability,
+generalizability and more robust sample size in a study
+[@auspurg2021has; @nosek2014method; @lebel2018].
 
-ADD STUFF ABOUT THE CREDIBILITY MOVEMENT HERE....
+The credibility movement was originally defined by a focus on large
+scale replications using in collaborative environments [@vazire2022].
+Generally, the movement has been driven by early career researchers
+(i.e., those who are within five years of their first appointment)
+[@maizey2019]; however, there are no large meta-scientific
+investigations on this specific topic to date. Potentially, the lack of
+investigation is tied to the newness of the large-scale research in many
+fields, as it is only in recent years that publications like the Open
+Science Collaboration [@opensciencecollaboration2015], Many Labs
+Collaborations [for example, @klein2018; @ebersole2020; @ebersole2016;
+@klein2022; @mathur2020; @buttrick2020; @skorb2020] or the first papers
+from the Psychological Science Accelerator [@moshontz2018; @jones2021;
+@dorison2022; @wang2021; @legate2022; @bago2022]. Generally, the
+researcher incentive for replication was low: journals often prioritize
+"novel" or new results which led to rejection of replication manuscripts
+and publication bias [@hubbard1997; @franco2014; @nosek2012], the
+"failure" to replicate was often placed on the replication team as "bad
+science" rather than a careful consideration of publication biases and
+(potential) questionable research practices [@ioannidis2015;
+@maxwell2015; @klein2022], and why should someone want to spend time and
+resources on an answer we already "know" [@isager2021; @isager2021a]?
 
-rise of big team science because the need for resources, replication,
-reproducibility, generalization (erin) - physics - biology - psychology
+However, the success and interest in the large-scale reproducibility
+projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired
+with the meta-scienctific publications focusing on researcher practices
+and incentive structures [@silberzahn2018many; @john2012] led to a
+change in journal guidelines and incentives for researchers interested
+in participating in large-scale replication studies [@grahe2014;
+@kidwell2016; @nosek2015; @mayo-wilson2021]. For example, the support
+for Registered Reports, papers accepted before the data has been
+collected [@nosek2014; @stewart2020], and entire sub-sections of
+journals devoted to only replication studies (e.g., *Nature, Royal
+Society Open Science, Advances in Methods and Practices in Psychological
+Science*) has allowed researchers to invest in projects that they know
+should be published when the project is complete. Further, the
+implementation of the Transparency and Openness Guidelines [@nosek2015]
+and the Contributor Role Taxonomy (CRediT) system [@allen2019] have
+pushed journals and researchers to promote more open, inclusive
+publication practices.
 
-metascience (erin) - most research is on lessons learned, why bts is
-useful - little research on who/fields has done bts - has the
-globalization of science actually impacted people other than NA and
-Europe
+The credibility movement has been mirrored by the calls for
+diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
+Rich, and Democratic) scientific research [@henrich2010; @newson2021;
+@rad2018] by improving representation in research samples. Like the
+large-scale studies in Physics [@aphilos2021; @castelnovo2018] and
+Biology [@collins2003], the social sciences struggle to represent the
+breadth of humanity across both researcher and population
+characteristics. Now, grassroots organizations, such as the
+Psychological Science Accelerator [@moshontz2018], ManyBabies
+(<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and
+DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these
+issues by recruiting research labs from all over the globe to provide
+diversity in geographic, linguistic, and researcher representation.
+Publications have examined the global understanding of morality, face
+processing, COVID-19 information signaling, and more [@dorison2022;
+@wang2021; @legate2022; @bago2022; @jones2021; @vanbavel2022]. While
+these organizations and one-time groups for BTS studies have provided an
+incredible wealth of data for the scientific community, we do not yet
+know exactly *who* is involved with, and benefits from, the BTS and
+credibility movement. Publications on BTS generally explore challenges,
+lessons learned, the need for BTS [@forscher2020; @coles2022].
 
-about this project paragraph (erin)
-
-    Significance: Describe how the project addresses an important problem or a critical barrier to progress in the field and how it can advance knowledge in the ICSR Research Themes.
-
-We specifically expect to examine ICSR's Research Themes of inclusivity,
-research careers, and research globalization. As we examine these
-themes, it will bring new knowledge of how big team science projects
-impact each theme and field of study.
-
-The globalization of science has allowed researchers across the world to
-contribute to research projects, but little research has examined *who*
-participates in big team science projects. We see an increase in BTS but
-we don't know if this uptick in large scale projects has diversified the
-*people* involved in BTS. Is this increasing inclusivity? At what level
-of career are people doing BTS? Is that changing over time? And how is
-that including new and varied researchers outside NA and Europe? Are we
-including people in positions that may impact their career? WEIRD thing
-is innovative
+Therefore, the goal of this manuscript is to examine the *people*
+involved in BTS projects. We specifically expect to examine ICSR's
+Research Themes of inclusivity, research careers, and research
+globalization. As we examine these themes, it will bring new knowledge
+of how BTS projects impact each theme and field of study. We see an
+increase in interest and publications in BTS but we do not yet know if
+this uptick in large-scale projects has diversified the *people*
+involved in BTS. While a few publications have noted that BTS appears to
+be early career researchers [@maizey2019], no one has systematically
+investigated this perception. Further, it is unclear if the focus of
+de-WEIRDing science has only focused on the representation of the
+research participants or if it has also improved the representation of
+researchers outside of North America and Europe. Last, who runs these
+BTS projects? Do we see an increase in diversity for the authors who
+generally receive the most credit for these projects (i.e., first
+several author(s) and last author)? As hiring and promoting practices
+often place a heavy weight on publications and especially "influential"
+publications, it becomes necessary to critically examine the
+representation present in authorship in BTS projects.
 
@@
 
-    Approach: Please describe:
-        An explicit research question or hypothesis you plan to test, and specific aims/objective related to that question.
-        The project’s overall strategy and planned methodology.
-        How the proposed project will make use of one or more of the available ICSR Lab datasets.
-        Any especially innovative or novel aspect of the proposed project.
-
--   Research Question 1: What journals publish big team science papers?
+-   Research Question 1: What publication sources publish big team
+    science papers?
 -   Research Question 2: What are the types of articles that are being
@@
 results of all big team research projects, and examine for change in
-result trends across years of publication.
+result trends across years of publication. Below we detail our methods
+and the ICSR/Scopus data to answer these questions, along with examples
+of the statistical results we expect to report in the manuscript. We
+began this project with data using Google Scholar and ORCID information.
+These sources were severely limited in their scope and breadth, as they
+are often curated with automatic processes or self-entered data, and we
+believe that access to Scopus and ICSR would allow us to accurately
+portray the BTS movement and its impact on diversity across many fields.
+The novelty of this project is that it would focus on all of published
+works, rather than a specific subfield (like Psychology) and give a lens
+into global representation in science that would otherwise not be
+achieved with open-source databases.
 
@@
 
-## Studies
+## Publications
 
-We defined **big team science publications** as publications with at
-least 10 authors that were published in peer-reviewed journals or had
-posted a full paper pre-print for publication review. We specifically
-focused on social science research, primarily *psychology* for this
-manuscript. First, we added all known publications from collaborative
-teams, such as the PSA, Many Labs, and Many Babies. We examined journals
-that frequently publish registered replication reports (i.e., *Advances
-in Methods and Practices in Psychological Science*) for additional
-publications with at least 10 authors. From these manuscripts, we
-identified common authors who frequently participate in these studies,
-and examined their Google Scholar or Open Researcher and Contributor
-IDentifier (ORCID) page for other publications. We reached out to social
-networks on Twitter to identify other publications. Last, we used Google
-Scholar and EBSCO to search for large projects using the following
-search terms: collaboration, multicultural, large scale, and big team
-science.
-
--   definition for big team size: 10 authors + at least 10 different
-    institutions
--   we will use all categories but break into the big four:
-    <https://service.elsevier.com/app/answers/detail/a_id/14882/supporthub/scopus/~/what-are-the-most-frequent-subject-area-categories-and-classifications-used-in/>
--   we would get everything from df_ani
--   only use 1970 and forward
+We have defined **BTS publications** as publications with at least 10
+authors at 10 different institutions that were published in
+peer-reviewed journals or had posted a full paper pre-print. We will use
+data from 1970 and forward in the publications (`ani)` database, as it
+is noted online that this time period includes cited references for
+calculation of several of our variables described below. We will analyze
+our results based on the big four subject areas: Physical Sciences,
+Health Sciences, Social Sciences, and Life Sciences.
 
@@
 
-### RQ1: Journal Information
+### RQ1: Publisher Information.
 
-Using these criteria, we identified `r nrow(bibs)` articles for
-inclusion on this manuscript. The publication dates on these articles
-ranged from `r min(bibs$YEAR)` to `r max(bibs$YEAR)`, and we used the
-pre-print last updated date as the publication date for those articles.
-The current impact factor (i.e., 2022) for each journal was found on the
-journal page and included for journal statistics.
+Using these criteria, we will extract the following information for
+publication sources: the name of the publication (source title), subject
+area (both the large four subject areas and the smaller four digit all
+science journal classification ASJC codes). We will examine journal
+impact using the Source Normalized Impact per Paper from the journal
+(`sources)` database.
 
-journal information we could include: - total number of articles
-overall - number of distinct journals in each of the four areas - JIF
-df_sources, snip -
-<https://liu.cwp.libguides.com/c.php?g=45770&p=4417804>
+### RQ2: Publication Information.
 
-### RQ2: Article Information
+For each publication of the identified BTS publications, we will analyze
+the full four digit ASJC subject areas codes for each of the larger four
+subject areas and the keywords present for these publications.
 
-For each publication, we coded the list of keywords into broad labels
-for areas of social science (i.e., Social Psychology, Cognitive
-Psychology). In this section, we elected to code each article with only
-one main research area. Research is often cross-disciplinary, however,
-for simplicity, we applied one global label to each article that
-represented the perceived main area of study (based on what course this
-material might be taught in, the publication journal focus). The list of
-broad areas includes clinical, cognitive, developmental, educational,
-and social psychology. Last, we included a metascience category that
-covered articles that were detailing the science of science. The Open
-Science Collaboration [CITE] was included in this category because the
-aim of the paper was a focus on replication across multiple field types.
-Other metascience categories included papers that focused on research
-degrees of freedom, analysis choices, and types of samples.
+### RQ3: Author Information.
 
--   keywords are easier now - could use the ASJC smaller subfield areas
-    to create a list
--   <https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/>
--   table of all the codes
+The author list will then be extracted from each publication. Next, we
+will use the author (`au`) and affiliation (`af`) array to curate a list
+of all publications and author information included in BTS papers. We
+will use these two arrays with the publication array to calculate the
+variables described below.
 
-### RQ3: Author Information
+***Career Length***. Career length for each author will be defined as
+the year of the first publication listed for each author.
 
-```{r authors, include = FALSE, echo = FALSE}
-min(author_count$author_count)
-max(author_count$author_count)
-format(mean(author_count$author_count), nsmall = 2, digits = 2)
-format(sd(author_count$author_count), nsmall = 2, digits = 2)
-nrow(id_list)
-```
+***Institution***. We will use the affiliation ids and country to gather
+information about the places of education and/or employment for authors.
+Country will likely be binned into United Nation Sub-Region for
+analyses.
 
-The author list was then extracted from each publication. In the case of
-consortium authorship, we extracted the complete authorship from the
-meta-data or pre-print publication. The total number of unique authors
-was `r nrow(id_list)`. The number of authors on each publication ranged
-from `r min(author_count$author_count)` to
-`r max(author_count$author_count)` with an average of
-`r format(mean(author_count$author_count), nsmall = 2, digits = 2)`
-authors (*SD* =
-`r format(sd(author_count$author_count), nsmall = 2, digits = 2)`).
+***Education***. We will also collect degree information from the author
+table.
 
--   calculate the min to max
--   average authors
--   SD authors
+***Types of Publications***. We will gather information from the
+publication type variable for each author publication to present
+information about the types of papers BTS authors publish.
 
-Next, we matched each author to their Google Scholar and ORCID profile
-pages, if available. We originally used the *R* packages, *rorcid*
-[CITE] and *scholar* [CITE] to try to match published author names to
-profile pages. This process did not result in a large number of matches,
-and we therefore curated the list of profile pages manually, checking
-each author against the publication list. We used these two packages and
-profile pages to collect authorship statistics described below. If a
-researcher was not present in either of these databases, their
-information was excluded from the relevant analyses below.
-
--   here we would pull all author ids and then grab all their papers -
-    grab from the whole dataset not just 1970
-
-***Career Length***. Career length for each author was defined using
-multiple variables to see if results from the two data sources would
-converge on similar answers. Both ORCID and Google Scholar provide a
-list of publications for authors, and we first calculated career length
-as the year of first publication listed for each author. In ORCID, a
-researcher can enter their educational background with completion years
-for each degree. We defined career length for this variable as years
-since first degree listed. Publication years are often curated directly
-from meta-data provided by Crossref (ORCID) or online sources used by
-Google Scholar. Authors may also directly add publications and their
-information into both systems. The limitation to using education as a
-metric for career length is that the researcher must directly enter this
-information into ORCID.
-
--   year from first publication should be what we would do
-
-***Employment***. Employment information was collected from self-entered
-ORCID data. These values are open text, and therefore, we coded them
-into coherent categories for traditional educational (graduate student,
-post doctoral, lecturer), tenure track (assistant, associate, full
-professor), and other roles (fellow, research assistant, researcher,
-head). Employment geopolitical region was also selected when available.
-
--   can't get this part really - we could get institution from
-    publication and country from publication
-
-***Education***. As with employment information, we also collected
-education information from self-entered ORCID data. These values were
-coded into general categories of bachelor, master, and doctoral degrees.
-The geopolitical region of the listed education was included when
-available. For analyses, both employment and education levels were
-grouped into United Nation regions.
-
--   we can get the degrees from the author table
-
-***Types of Publications***. ORCID includes information about the type
-of publication pulled from either researcher entered data or Crossref.
-We coded these publications into general categories including book,
-conference presentations, data-sets, journal articles, preprints,
-software, thesis, and other publications.
-
--   publication type:
-
-The classification of the publication, which may be: ab Abstract Report,
-ar Article, ip Article in Press, bk Book, bz Business Article, ch Book
-Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed
-Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press
-Release, rp Report, re Review, sh Survey, tb Retracted.
-
--   just make a graph of the options
-
-***Publication Metrics***. We calculated total number of publications of
-any type from both Google Scholar and ORCID. We additionally pulled both
-the h-index and i-10 index from Google Scholar. The h-index represents
-the highest *h* number of publications that have at least *h* citations,
-while the i-10 index represents the number of publications with at least
-10 citations.
-
--   for each author:
-    -   total number of publications
-    -   h index
-    -   i 10 index
+***Publication Metrics***. For each author, we will calculate the total
+number of publications, the h-index, and the i-10 index. The h-index
+represents the highest *h* number of publications that have at least *h*
+citations, while the i-10 index represents the number of publications
+with at least 10 citations.
 
@@
 
-### RQ1: Journals
+### RQ1: Publisher Information.
 
-Results for types of journals will include a summary of the journals
-that publish big-team science papers and an average of the 2-year and
-5-year impact factors for the journals.
+To present results on this research question, we will analyze:
 
-### RQ2: Articles
+-   Number of articles for inclusion: total, separated by four subject
+    areas, presenting graphics of the number of publication across time
+-   Number of distinct journals within each of the four subject areas
+-   Statistics (mean, median, standard deviation, minimum, maximum) of
+    the journal impact using Source Normalized Impact per Paper for the
+    four subject areas.
 
-Results for types of articles will include a summary of the coded areas
-for each article, presented overall and across the years of publication.
+### RQ2: Publication Information.
+
+For each publication, we will examine:
+
+-   The totals of the number of articles published within the smaller
+    subject area classifications. We will visualize these differences
+    over time to determine if there is increasing interest in a specific
+    subarea over time for each of the four larger subject area
+    classifications.
+-   The keywords present in the publications data overall to identify
+    trends and common themes in the publications for the four subject
+    areas using visualizations (wordclouds) to depict the common
+    keywords.
 
 ### RQ3: Authors.
+
+We will first present:
+
+-   The total number of unique authors
+-   Statistics (mean, standard deviation, minimum, maximum, median) on
+    the number of authors included on publications.
+-   We will present visualizations of these results across time.
 
@@
 
-***Career Length***. For each of the three variables in career length
-(ORCID year of first pub, Scholar year of first pub, ORCID year of first
-degree), we will create a visualization of the trend and variance of
-researcher career length across publication years. To analyze trends
-over time, we will use the slope from a multilevel model (MLM) using the
-individual as a random intercept, career length as the dependent
-variable, and year of publication as the predictor variable. MLMs are
-regression models that control for the correlated error due to the
-repeated and nested nature of the data [CITE]. In this model, each
-individual's starting career length is arbitrary, which we allow to vary
-with the random intercept by participant. A positive slope for year of
-publication would indicate increasing years of first publication (i.e.,
-more younger scholars over time), while a negative slope would indicate
-older years of first publication (i.e., more older scholars over time).
-In order to show variance between individuals, we will report the
-variance component of the random intercept for individuals. Finally, to
-examine variance over time, we will calculate the standard deviation of
-the individual within each publication (i.e., one standard deviation for
-each article), and use a linear model with year predicting these
-standard deviations. This model is a traditional simultaneous
-regression, as averaging the variance by title eliminates the repeated
-measures variable (individuals). A positive slope would indicate
-increasing variance over time (i.e., more diversity in the career
-lengths of scholars), while a negative slope would indicate less
-variance and diversity in scholars over time.
+***Career Length***.
 
--   so we cant do MLM
--   for each paper we could calculate an average career length, then run
-    the regression
--   then calculate the standard deviation and do the same analysis as
-    described
+-   We will create a visualization of the trend and variance of
+    researcher career length across publication years.
+-   To analyze trends over time, we will calculate the average career
+    length for each publication (i.e., average the author career length
+    to create one score for each paper) and run a regression analysis
+    using career length to predict year of publication. A positive slope
+    for year of publication would indicate increasing years of first
+    publication (i.e., more younger scholars over time), while a
+    negative slope would indicate older years of first publication
+    (i.e., more older scholars over time).
+-   In order to show variance between individuals, we calculate the
+    standard deviation of career length for each publication and run a
+    regression analysis using this variance representation to predict
+    publication year. A positive slope would indicate increasing
+    variance over time (i.e., more diversity in the career lengths of
+    scholars), while a negative slope would indicate less variance and
+    diversity in scholars over time.
+-   These analyses will be completed separately for each of the four
+    large subject areas.
 
-***Employment***. We will summarize the general employment categories of
-individuals at the time of publication, along with a summary for change
-over time. ***Education***. We will summarize the general education
-categories of individuals at the time of publication, along with a
-summary for change over time.
+***Institution***.
 
-***Types of Publications***. We will summarize the coded types of
-publications for individuals.
+-   We will summarize the number of affiliation ids present in BTS
+    publications by subject area and visualize these results across
+    time. These visualizations will be presented separately for each of
+    the four subject areas.
 
-***Publication Metrics***. We will report descriptive statistics on the
-total number of publications, i10 index, and h-index for individuals
-overall. Next, we will use the same analyses described in the career
-length section to analyze trends over time. An increasing slope over
-time indicates that individuals who are publishing more are more
-represented in big-team science over time (i.e., increasing numbers of
-scholars with higher publication rates), while a negative slope
-indicates more researchers with less publications. A positive slope for
-variance indicates increasing variance over time (i.e., more diversity
-in the individual publication rates), while a negative slope would
-indicate less diversity in researchers over time. While publication
-rates do not represent value as a researcher, they are often used in
-hiring and promotion decisions, and we will use this variable as a proxy
-to gauge the diversity in scholars represented in big teams. same idea
-average down by paper for mean and standard deviation
+***Education***.
 
-***Geopolitical Regions***. We will present visualizations of the last
-listed education and job location, and we will discuss the areas of
-world in which authors generally come from, as well as the lowest
-representation of authors. To understand the change in representation
-diversity, we will summarize the total number of geopolitical regions
-for each paper. Using a linear model, we will examine if the number of
-regions present is predicted by the year of publication. Increasing
+-   We will summarize the general education categories of individuals at
+    the time of publication, along with a summary for change over time.
+
+***Types of Publications***.
+
+-   We will summarize the coded types of publications for individuals.
+
+***Publication Metrics***.
+
+-   We will report descriptive statistics on the total number of
+    publications, i10 index, and h-index for individuals overall.
+-   Next, we will use the same analyses described in the career length
+    section to analyze trends over time. An increasing slope over time
+    indicates that individuals who are publishing more are more
+    represented in BTS over time (i.e., increasing numbers of scholars
+    with higher publication rates), while a negative slope indicates
+    more researchers with less publications.
+-   A positive slope for standard deviation indicates increasing
+    variance over time (i.e., more diversity in the individual
+    publication rates), while a negative slope would indicate less
+    diversity in researchers over time. While publication rates do not
+    represent value as a researcher, they are often used in hiring and
+    promotion decisions, and we will use this variable as a proxy to
+    gauge the diversity in scholars represented in big teams.
+
+***Geopolitical Regions***.
+
+-   We will present visualizations of the country information listed for
+    authors, and we will discuss the areas of world in which authors
+    generally come from, as well as the lowest representation of
+    authors.
+-   To understand the change in representation diversity, we will
+    summarize the total number of geopolitical regions for each paper.
+    Using a linear model, we will examine if the number of regions
+    present is predicted by the year of publication. Increasing
     diversity would be represented by a positive slope, while decreasing
-diversity would be represented by a negative slope. Last, we will
-examine the differences in representation for corresponding author sets
-versus all other authors. For papers with 10 to 49 authors, we will use
-the three first authors and the last author to compare against random
-samples of other authors. For 50 to 99 authors, five first authors plus
-last will be used, and for all papers with more than 100 authors, we
-will use ten first authors and the last author. We will calculate the
-frequencies of each of the UN Sub-Regions for first authors. Then we
-will randomly sample all authors in subsets of the same size (i.e., 3+1,
-5+1, 10+1), and average the frequencies of UN Sub-Regions across these
-random samples. We will randomly sample the same number of times as the
-size of the author list (i.e., a paper that has 54 authors will be
-randomly sampled 54 times with a sample size of six).
-
--   may not need to do this random sample thing if we have large enough
-    datasets?
--   pool them together and then compare?
--   maybe group them in the sizes we are interested in, then convert to
-    proportions
--   average those proportions ? plot comparisons of the proportions and
-    confidence intervals for each group
-
-Given the expected small sample sizes of these contingency tables (i.e.,
-the largest could be *n* = 22 if all author information is available),
-we will group together titles based on time period using pre-2020, 2020,
-and post-2020 to show change over time. The choice of these groupings is
-based on the number of articles available within these time brackets.
-For each grouping, we will calculate the effect size of the differences
-in frequencies comparing first authors to all other authors. Since this
-data is categorical, we will use Cramer's V to represent the effect
-size. If the effect size includes zero in it's confidence interval, this
-result will imply that first and all other authors represent the same
-pattern of UN Sub-Region diversity. Any confidence interval that does
-include zero represents a difference in diversity. We will report these
-values and discuss what regions of the world are represented when effect
-sizes indicate a different from zero using standardized residuals.
-
-# Results
-
-### RQ1: Journals
-
-Articles were most commonly published in `r journal_count$JOURNAL[1]`
-(*n* = `r journal_count$freq[1]`), `r journal_count$JOURNAL[2]` (*n* =
-`r journal_count$freq[2]`), `r journal_count$JOURNAL[3]` (*n* =
-`r journal_count$freq[3]`), `r journal_count$JOURNAL[4]` (*n* =
-`r journal_count$freq[4]`), and `r journal_count$JOURNAL[5]` (*n* =
-`r journal_count$freq[5]`). A complete list of journals can be found on
-our Open Science Framework page XXX. The average 2-year impact factor
-for official journal publications was
-`r format(mean(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)` (*SD* =
-`r format(sd(JIF$JIF2, na.rm = T), nsmall = 2, digits = 2)`) and the
-average 5-year impact factor was
-`r format(mean(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)` (*SD* =
-`r format(sd(JIF$JIF5, na.rm = T), nsmall = 2, digits = 2)`).
-
-### RQ2: Articles
-
-Articles were primarily `r article_overall$Var1[1]`
-(`r format(article_overall$Percent[1], nsmall = 1, digits = 1)`%) and
-`r article_overall$Var1[2]`
-(`r format(article_overall$Percent[2], nsmall = 1, digits = 1)`%),
-followed by smaller categories for `r article_overall$Var1[3]`
-(`r format(article_overall$Percent[3], nsmall = 1, digits = 1)`%),
-`r article_overall$Var1[4]`
-(`r format(article_overall$Percent[4], nsmall = 1, digits = 1)`%),
-`r article_overall$Var1[5]`
-(`r format(article_overall$Percent[5], nsmall = 1, digits = 1)`%), and
-`r article_overall$Var1[6]`
-(`r format(article_overall$Percent[6], nsmall = 1, digits = 1)`%). Here,
-we will talk about the figure below and how the trends occur across
-time.
-
-```{r figure1, echo = FALSE}
-article_time_plot
-```
-
-### RQ3: Authors.
-
-```{r echo = FALSE}
-o_career_output <- tidy(o_career_model)
-var_o_career_output <- tidy(var_o_career_model)
-
-s_career_output <- tidy(s_career_model)
-var_s_career_output <- tidy(var_s_career_model)
-
-o_career_ed_output <- tidy(o_career_ed_model)
-var_o_career_ed_output <- tidy(var_o_career_ed_model)
-```
-
-***Career Length***. The average career length was
-`r format(round(current_year - mean(o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`
-(*SD* =
-`r format(round(sd(current_year - o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`)
-for ORCID first publication year (i.e., current year minus year of first
-publication), *M* =
-`r format(round(current_year - mean(s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`
-(*SD* =
-`r format(round(sd(current_year - s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`)
-for Scholar year of first publication, and *M* =
-`r format(round(current_year - mean(o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`
-(*SD* =
-`r format(round(sd(current_year - o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`)
-for ORCID year of first degree. In each of the analyses, we use the
-actual year of first publication/education, as subtracting publication
-and using it as a predictor would create a perfect solution for each
-model.
-
-Next, we will talk about the results from three variables:
-
-1)  ORCID year first publication:
-
--   The slope for year of first publication was *b* =
-    `r format(round(o_career_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(o_career_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r o_career_output$df[2]`) =
-    `r format(round(o_career_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(o_career_output$p.value[2])`.
--   The variance parameter was *SD* =
-    `r format(round(o_career_output$estimate[3], digits = 2), nsmall = 2)`.
--   The slope for variance across years was *b* =
-    `r format(round(var_o_career_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(var_o_career_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r var_o_career_model$df.residual`) =
-    `r format(round(var_o_career_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(var_o_career_output$p.value[2])`.
-
-2)  Scholar year first publication:
-
--   The slope for year of first publication was *b* =
-    `r format(round(s_career_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(s_career_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r s_career_output$df[2]`) =
-    `r format(round(s_career_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(s_career_output$p.value[2])`.
--   The variance parameter was *SD* =
-    `r format(round(s_career_output$estimate[3], digits = 2), nsmall = 2)`.
--   The slope for variance across years was *b* =
-    `r format(round(var_s_career_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(var_s_career_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r var_s_career_model$df.residual`) =
-    `r format(round(var_s_career_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(var_s_career_output$p.value[2])`.
-
-3)  ORCID year first degree:
-
--   The slope for year of first degree was *b* =
-    `r format(round(o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r o_career_ed_output$df[2]`) =
-    `r format(round(o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(o_career_ed_output$p.value[2])`.
--   The variance parameter was *SD* =
-    `r format(round(o_career_ed_output$estimate[3], digits = 2), nsmall = 2)`.
--   The slope for variance across years was *b* =
-    `r format(round(var_o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(var_o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r var_o_career_ed_model$df.residual`) =
-    `r format(round(var_o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(var_o_career_ed_output$p.value[2])`.
-
-Then we will discuss how these results are represented in our graph
-(below). We will discuss any discrepancies in the results across the
-three different statistics.
-
-```{r figure2, echo = FALSE, warning = FALSE}
-plot_grid(o_career_graph + theme(text = element_text(size = 8), 
-                                 axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5)), 
-          s_career_graph + theme(text = element_text(size = 8), 
-                                 axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5)), 
-          o_career_graph_ed + theme(text = element_text(size = 8), 
-                                 axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5)))
-```
-
-***Employment***. Overall, individuals **at the time of publication** in
-big team science publications are `r employment_overall$Var1[1]`
-(`r format(employment_overall$Percent[1], nsmall = 1, digits = 1)`%) and
-`r employment_overall$Var1[2]`
-(`r format(employment_overall$Percent[2], nsmall = 1, digits = 1)`%),
-followed by smaller categories for `r employment_overall$Var1[3]`
-(`r format(employment_overall$Percent[3], nsmall = 1, digits = 1)`%),
-`r employment_overall$Var1[4]`
-(`r format(employment_overall$Percent[4], nsmall = 1, digits = 1)`%),
-`r employment_overall$Var1[5]`
-(`r format(employment_overall$Percent[5], nsmall = 1, digits = 1)`%),
-and `r employment_overall$Var1[6]`
-(`r format(employment_overall$Percent[6], nsmall = 1, digits = 1)`%).
-Here, we will talk about the figure below and how the trends occur
-across time. We will also comment on the number of jobs that would be
-considered "non-academic".
-
-```{r figure3, echo = FALSE, warning = FALSE}
-employment_time_plot
-```
-
-***Education***. Overall, individuals **at the time of publication** in
-big team science publications are `r education_overall$Var1[1]`
-(`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%),
-`r education_overall$Var1[2]`
-(`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and
-`r education_overall$Var1[3]`
-(`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%).
-Here, we will talk about the figure below and how the trends occur
-across time.
-
-```{r figure4, echo = FALSE, warning = FALSE}
-education_time_plot
-```
-
-***Types of Publications***. In general, the most common type of
-publication was `r publication_overall$Var1[1]`
-(`r format(publication_overall$Percent[1], nsmall = 1, digits = 1)`%),
-followed by `r publication_overall$Var1[2]`
-(`r format(publication_overall$Percent[2], nsmall = 1, digits = 1)`%),
-and smaller categories for `r publication_overall$Var1[3]`
-(`r format(publication_overall$Percent[3], nsmall = 1, digits = 1)`%),
-`r publication_overall$Var1[4]`
-(`r format(publication_overall$Percent[4], nsmall = 1, digits = 1)`%),
-`r publication_overall$Var1[5]`
-(`r format(publication_overall$Percent[5], nsmall = 1, digits = 1)`%),
-and `r publication_overall$Var1[6]`
-(`r format(publication_overall$Percent[6], nsmall = 1, digits = 1)`%).
-We will include all information over 1% of the publication totals.
-
-```{r echo = FALSE}
-o_total_output <- tidy(o_total_model)
-var_o_total_output <- tidy(var_o_total_model)
-
-s_total_output <- tidy(s_total_model)
-var_s_total_output <- tidy(var_s_total_model)
-```
-
-***Publication Metrics***. The average number of all publications per
-individual was *M* =
-`r format(round(mean(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`
-(*SD* =
-`r format(round(sd(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`)
-using ORCID and *M* =
-`r format(round(mean(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`
-(*SD* =
-`r format(round(sd(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`)
-using Google Scholar. The average i10 index was *M* =
-`r format(round(mean(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`
-(*SD* =
-`r format(round(sd(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`)
-and the average h-index was *M* =
-`r format(round(mean(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`
-(*SD* =
-`r format(round(sd(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`).
-
-Using the same analyses as career length, we will report:
-
-1)  Number of publications ORCID:
-
--   The slope for number of publications was *b* =
-    `r format(round(o_total_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(o_total_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r o_total_output$df[2]`) =
-    `r format(round(o_total_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(o_total_output$p.value[2])`.
--   The variance parameter was *SD* =
-    `r format(round(o_total_output$estimate[3], digits = 2), nsmall = 2)`.
--   The slope for variance across years was *b* =
-    `r format(round(var_o_total_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(var_o_total_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r var_o_total_model$df.residual`) =
-    `r format(round(var_o_total_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(var_o_total_output$p.value[2])`.
-
-2)  The number of publications for Scholar:
-
--   The slope for year of first publication was *b* =
-    `r format(round(s_total_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(s_total_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r s_total_output$df[2]`) =
-    `r format(round(s_total_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(s_total_output$p.value[2])`.
--   The variance parameter was *SD* =
-    `r format(round(s_total_output$estimate[3], digits = 2), nsmall = 2)`.
--   The slope for variance across years was *b* =
-    `r format(round(var_s_total_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(var_s_total_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r var_s_total_model$df.residual`) =
-    `r format(round(var_s_total_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(var_s_total_output$p.value[2])`.
-
-***Geopolitical Regions***. We will first present two figures for
-education and employment geopolitical regions representation in
-scholars.
-
-Education Graph
-
-```{r figure5, echo = FALSE, warning = FALSE}
-o_ed_country_graph
-```
-
-Employment Graph
-
-```{r figure6, echo = FALSE, warning = FALSE}
-o_job_country_graph
-```
-
-```{r echo = F}
-edu_country_output <- tidy(edu_country_model)
-job_country_output <- tidy(job_country_model)
-```
-
-Next, we will report the results of two linear regression models. The
-independent variable is year of publication, and the dependent variables
-include the summary of the total number of different geopolitical
-regions represented in each publication. - The slope for the education
-model was *b* =
-`r format(round(edu_country_output$estimate[2], digits = 2), nsmall = 2)`,
-*SE* =
-`r format(round(edu_country_output$std.error[2], digits = 2), nsmall = 2)`,
-*t*(`r edu_country_model$df.residual`) =
-`r format(round(edu_country_output$statistic[2], digits = 2), nsmall = 2)`,
-*p* = `r printp(edu_country_output$p.value[2])`.
-
--   The slope for the employment model was *b* =
-    `r format(round(job_country_output$estimate[2], digits = 2), nsmall = 2)`,
-    *SE* =
-    `r format(round(job_country_output$std.error[2], digits = 2), nsmall = 2)`,
-    *t*(`r job_country_model$df.residual`) =
-    `r format(round(job_country_output$statistic[2], digits = 2), nsmall = 2)`,
-    *p* = `r printp(job_country_output$p.value[2])`.
-
-Last, we will examine the effect sizes of the UN Sub-Regions represented
-for each grouped year of analysis. Tables of the UN Sub-Regions will be
-presented in our supplemental documents.
-
--   Pre-2020: `r v_pre2020$estimate` and `r x_pre2020$stdres` will be
-    used to discuss pre-2020 manuscripts.
-
--   2020: `r v_2020$estimate` and `r x_2020$stdres` will be used to
-    discuss 2020 manuscripts.
-
--   Post-2020: `r v_post2020$estimate` and `r x_post2020$stdres` will be
-    used to discuss post-2020 manuscripts.
-
-# Discussion
-
-To be included after we have completed analyses.
-
-## Limitations
-
--   Discuss the limitation of "who is using ORCID and Scholar" which can
-    bias our results.
--   Other limitations will be included.
+    diversity would be represented by a negative slope.
+-   Last, we will examine the differences in representation for
+    corresponding author sets versus all other authors. For papers with
+    10 to 49 authors, we will use the three first authors and the last
+    author to compare against other authors. For 50 to 99 authors, five
+    first authors plus last will be used, and for all papers with more
+    than 100 authors, we will use ten first authors and the last author.
+    We will calculate the frequencies of each of the UN Sub-Regions for
+    first authors versus other authors, converting these values to
+    proportions. Given the expected small sample sizes of these
+    contingency tables, we will group together titles based on the year
+    of publication (assuming at least 5 publications per year, these may
+    be binned by 5-year or smaller increments to increase sample size).
+    For each grouping, we will calculate the effect size of the
+    differences in frequencies comparing first authors to all other
+    authors. Since this data is categorical, we will use Cramer's V to
+    represent the effect size. If the effect size includes zero in its
+    confidence interval, this result will imply that first and all other
+    authors represent the same pattern of UN Sub-Region diversity. Any
+    confidence interval that does include zero represents a difference
+    in diversity. We will report these values and discuss what regions
+    of the world are represented when effect sizes indicate a different
+    from zero using standardized residuals.
 

### 2022-09-09 04.manuscript_scopus.tex
finish up the else draft

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{big team, science, authorship, credit\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Who does big team science?},
  pdfauthor={Erin M. Buchanan1 \& Savannah C. Lewis2},
  pdflang={en-EN},
  pdfkeywords={big team, science, authorship, credit},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Who does big team science?}
\author{Erin M. Buchanan\textsuperscript{1} \& Savannah C. Lewis\textsuperscript{2}}
\date{}

\shorttitle{Big Team Science}

\authornote{

Erin M. Buchanan is a Professor of Cognitive Analytics at Harrisburg University of Science and Technology. Savannah C. Lewis is a graduate student at the University of Alabama.

Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript.

The authors made the following contributions. Erin M. Buchanan: Conceptualization, Data curation, Formal Analysis, Methodology, Project administration, Visualization, Writing -- original draft, Writing -- review \& editing; Savannah C. Lewis: Conceptualization, Data curation, Methodology, Project administration, Writing -- original draft, Writing -- review \& editing.

Correspondence concerning this article should be addressed to Erin M. Buchanan, 326 Market St., Harrisburg, PA 17101. E-mail: \href{mailto:ebuchanan@harrisburgu.edu}{\nolinkurl{ebuchanan@harrisburgu.edu}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Harrisburg University of Science and Technology\\\textsuperscript{2} University of Alabama}

\abstract{%
This paper will examine the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions. As interest in BTS increases, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation. The types of publication outlets, number of publications, and subject areas of publication will be presented to summarize the publications in BTS. Information about authors included in BTS will be presented including career length, numbers of publications/impact variables, education, and affiliation. Last, we will explore the representation of geopolitical regions by examining affiliation location to explore the impact of BTS on the de-WEIRD movement to diversify researcher representation.
}

\begin{document}
\maketitle

\hypertarget{significance}{%
\section{Significance}\label{significance}}

According to the Oxford English dictionary, collaboration is two or more
people working together to achieve a certain goal (OED, 2016).
Collaboration in scientific endeavors involves multiple researchers at
(potentially) multiple institutions to communicate and work together to
advance knowledge in their chosen field. Collaboration can manifest
uniquely in each project dependent on the skill sets, hypotheses, and
perspectives of collaborators. While collaboration is not new in
science, the current interest of ``big team science'' is increasing
(Coles et al., 2022; Forscher et al., 2020; N. Stewart et al., 2017). Big team science projects
and/or organizations utilize and run on large-scale collaboration to
ensure that diverse populations and ideas are brought into research
projects, which in turn allows for more reliability and generalizability
in the results and method of the study. For this study, Big Team Science
(BTS) will be defined as a collaboration of ten or more authors from at
least ten different institutions.

BTS appears to be increasing as a result of two sources: 1) increasing
globalization and technology that allows for real-time interdisciplinary
research, and 2) increasing interest in reproducibility, replication,
and generalizability (Maxwell et al., 2015; Nelson et al., 2018; Zwaan et al., 2018).
Technological advances have provided easier ways to collaborate with
people who are from other universities and countries through document
sharing platforms (e.g., Google, GitHub, and the Open Science
Framework), video chatting platforms (e.g., Zoom, Microsoft Teams), and
messaging and project management platforms (e.g., Slack, Trello,
when2meet, etc.). The credibility movement seems to suggest that by
having both collaborations that span across the globe and subfield of
psychology, age groups, and education levels should help to drive
psychological science in the path of better materials, reliability,
generalizability and more robust sample size in a study
(Auspurg \& Brüderl, 2021; LeBel et al., 2018; Nosek \& Lakens, 2014b).

The credibility movement was originally defined by a focus on large
scale replications using in collaborative environments (Vazire et al., 2022).
Generally, the movement has been driven by early career researchers
(i.e., those who are within five years of their first appointment)
(Maizey \& Tzavella, 2019); however, there are no large meta-scientific
investigations on this specific topic to date. Potentially, the lack of
investigation is tied to the newness of the large-scale research in many
fields, as it is only in recent years that publications like the Open
Science Collaboration (Open Science Collaboration, 2015), Many Labs
Collaborations (Buttrick et al., 2020; Ebersole et al., 2020, 2016; Klein et al., 2022; for example, Klein et al., 2018; Mathur et al., 2020; Skorb et al., 2020) or the first papers
from the Psychological Science Accelerator (Bago et al., 2022; Dorison et al., 2022; Jones et al., 2021; Legate et al., 2022; Moshontz et al., 2018; Wang et al., 2021). Generally, the
researcher incentive for replication was low: journals often prioritize
``novel'' or new results which led to rejection of replication manuscripts
and publication bias (Franco et al., 2014; Hubbard \& Armstrong, 1997; Nosek et al., 2012), the
``failure'' to replicate was often placed on the replication team as ``bad
science'' rather than a careful consideration of publication biases and
(potential) questionable research practices (Ioannidis, 2015; Klein et al., 2022; Maxwell et al., 2015), and why should someone want to spend time and
resources on an answer we already ``know'' (Isager et al., 2021a, 2021b)?

However, the success and interest in the large-scale reproducibility
projects (Errington et al., 2021; Open Science Collaboration, 2015), paired
with the meta-scienctific publications focusing on researcher practices
and incentive structures (John et al., 2012; Silberzahn et al., 2018) led to a
change in journal guidelines and incentives for researchers interested
in participating in large-scale replication studies (Grahe, 2014; Kidwell et al., 2016; Mayo-Wilson et al., 2021; Nosek et al., 2015). For example, the support
for Registered Reports, papers accepted before the data has been
collected (Nosek \& Lakens, 2014a; S. Stewart et al., 2020), and entire sub-sections of
journals devoted to only replication studies (e.g., \emph{Nature, Royal
Society Open Science, Advances in Methods and Practices in Psychological
Science}) has allowed researchers to invest in projects that they know
should be published when the project is complete. Further, the
implementation of the Transparency and Openness Guidelines (Nosek et al., 2015)
and the Contributor Role Taxonomy (CRediT) system (Allen et al., 2019) have
pushed journals and researchers to promote more open, inclusive
publication practices.

The credibility movement has been mirrored by the calls for
diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
Rich, and Democratic) scientific research (Henrich et al., 2010; Newson et al., 2021; Rad et al., 2018) by improving representation in research samples. Like the
large-scale studies in Physics ({``A Philosophical Case for Big Physics,''} 2021; Castelnovo et al., 2018) and
Biology (Collins et al., 2003), the social sciences struggle to represent the
breadth of humanity across both researcher and population
characteristics. Now, grassroots organizations, such as the
Psychological Science Accelerator (Moshontz et al., 2018), ManyBabies
(\url{https://manybabies.github.io/}), NutNet (\url{https://nutnet.org/}), and
DRAGNet (\url{https://dragnetglobal.weebly.com/}) can begin to tackle these
issues by recruiting research labs from all over the globe to provide
diversity in geographic, linguistic, and researcher representation.
Publications have examined the global understanding of morality, face
processing, COVID-19 information signaling, and more (Bago et al., 2022; Dorison et al., 2022; Jones et al., 2021; Legate et al., 2022; Van Bavel et al., 2022; Wang et al., 2021). While
these organizations and one-time groups for BTS studies have provided an
incredible wealth of data for the scientific community, we do not yet
know exactly \emph{who} is involved with, and benefits from, the BTS and
credibility movement. Publications on BTS generally explore challenges,
lessons learned, the need for BTS (Coles et al., 2022; Forscher et al., 2020).

Therefore, the goal of this manuscript is to examine the \emph{people}
involved in BTS projects. We specifically expect to examine ICSR's
Research Themes of inclusivity, research careers, and research
globalization. As we examine these themes, it will bring new knowledge
of how BTS projects impact each theme and field of study. We see an
increase in interest and publications in BTS but we do not yet know if
this uptick in large-scale projects has diversified the \emph{people}
involved in BTS. While a few publications have noted that BTS appears to
be early career researchers (Maizey \& Tzavella, 2019), no one has systematically
investigated this perception. Further, it is unclear if the focus of
de-WEIRDing science has only focused on the representation of the
research participants or if it has also improved the representation of
researchers outside of North America and Europe. Last, who runs these
BTS projects? Do we see an increase in diversity for the authors who
generally receive the most credit for these projects (i.e., first
several author(s) and last author)? As hiring and promoting practices
often place a heavy weight on publications and especially ``influential''
publications, it becomes necessary to critically examine the
representation present in authorship in BTS projects.

\hypertarget{potential-outlets}{%
\section{Potential Outlets}\label{potential-outlets}}

We will aim for high impact broad scope journals such as \emph{Science},
\emph{Nature} or \emph{Nature Human Behaviour}. Other journals would include
review publications within psychology to compare the social sciences to
other sciences: \emph{Perspectives in Psychological Science}, \emph{Psychological
Bulletin}, \emph{Psychological Review}, or \emph{Current Directions in
Psychological Science}.

\hypertarget{approach}{%
\section{Approach}\label{approach}}

\begin{itemize}
\tightlist
\item
  Research Question 1: What publication sources publish big team
  science papers?
\item
  Research Question 2: What are the types of articles that are being
  published in big team science?
\item
  Research Question 3: Who is involved in big team science?
\end{itemize}

For each of these research questions, we will examine the overall
results of all big team research projects, and examine for change in
result trends across years of publication. Below we detail our methods
and the ICSR/Scopus data to answer these questions, along with examples
of the statistical results we expect to report in the manuscript. We
began this project with data using Google Scholar and ORCID information.
These sources were severely limited in their scope and breadth, as they
are often curated with automatic processes or self-entered data, and we
believe that access to Scopus and ICSR would allow us to accurately
portray the BTS movement and its impact on diversity across many fields.
The novelty of this project is that it would focus on all of published
works, rather than a specific subfield (like Psychology) and give a lens
into global representation in science that would otherwise not be
achieved with open-source databases.

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{publications}{%
\subsection{Publications}\label{publications}}

We have defined \textbf{BTS publications} as publications with at least 10
authors at 10 different institutions that were published in
peer-reviewed journals or had posted a full paper pre-print. We will use
data from 1970 and forward in the publications (\texttt{ani)} database, as it
is noted online that this time period includes cited references for
calculation of several of our variables described below. We will analyze
our results based on the big four subject areas: Physical Sciences,
Health Sciences, Social Sciences, and Life Sciences.

\hypertarget{data-curation}{%
\subsection{Data Curation}\label{data-curation}}

\hypertarget{rq1-publisher-information.}{%
\subsubsection{RQ1: Publisher Information.}\label{rq1-publisher-information.}}

Using these criteria, we will extract the following information for
publication sources: the name of the publication (source title), subject
area (both the large four subject areas and the smaller four digit all
science journal classification ASJC codes). We will examine journal
impact using the Source Normalized Impact per Paper from the journal
(\texttt{sources)} database.

\hypertarget{rq2-publication-information.}{%
\subsubsection{RQ2: Publication Information.}\label{rq2-publication-information.}}

For each publication of the identified BTS publications, we will analyze
the full four digit ASJC subject areas codes for each of the larger four
subject areas and the keywords present for these publications.

\hypertarget{rq3-author-information.}{%
\subsubsection{RQ3: Author Information.}\label{rq3-author-information.}}

The author list will then be extracted from each publication. Next, we
will use the author (\texttt{au}) and affiliation (\texttt{af}) array to curate a list
of all publications and author information included in BTS papers. We
will use these two arrays with the publication array to calculate the
variables described below.

\textbf{\emph{Career Length}}. Career length for each author will be defined as
the year of the first publication listed for each author.

\textbf{\emph{Institution}}. We will use the affiliation ids and country to gather
information about the places of education and/or employment for authors.
Country will likely be binned into United Nation Sub-Region for
analyses.

\textbf{\emph{Education}}. We will also collect degree information from the author
table.

\textbf{\emph{Types of Publications}}. We will gather information from the
publication type variable for each author publication to present
information about the types of papers BTS authors publish.

\textbf{\emph{Publication Metrics}}. For each author, we will calculate the total
number of publications, the h-index, and the i-10 index. The h-index
represents the highest \emph{h} number of publications that have at least \emph{h}
citations, while the i-10 index represents the number of publications
with at least 10 citations.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

\hypertarget{rq1-publisher-information.-1}{%
\subsubsection{RQ1: Publisher Information.}\label{rq1-publisher-information.-1}}

To present results on this research question, we will analyze:

\begin{itemize}
\tightlist
\item
  Number of articles for inclusion: total, separated by four subject
  areas, presenting graphics of the number of publication across time
\item
  Number of distinct journals within each of the four subject areas
\item
  Statistics (mean, median, standard deviation, minimum, maximum) of
  the journal impact using Source Normalized Impact per Paper for the
  four subject areas.
\end{itemize}

\hypertarget{rq2-publication-information.-1}{%
\subsubsection{RQ2: Publication Information.}\label{rq2-publication-information.-1}}

For each publication, we will examine:

\begin{itemize}
\tightlist
\item
  The totals of the number of articles published within the smaller
  subject area classifications. We will visualize these differences
  over time to determine if there is increasing interest in a specific
  subarea over time for each of the four larger subject area
  classifications.
\item
  The keywords present in the publications data overall to identify
  trends and common themes in the publications for the four subject
  areas using visualizations (wordclouds) to depict the common
  keywords.
\end{itemize}

\hypertarget{rq3-authors.}{%
\subsubsection{RQ3: Authors.}\label{rq3-authors.}}

We will first present:

\begin{itemize}
\tightlist
\item
  The total number of unique authors
\item
  Statistics (mean, standard deviation, minimum, maximum, median) on
  the number of authors included on publications.
\item
  We will present visualizations of these results across time.
\end{itemize}

We will use \(\alpha\) \textless{} .05 for all analyses that involve hypothesis
testing. We make no directional predictions.

\textbf{\emph{Career Length}}.

\begin{itemize}
\tightlist
\item
  We will create a visualization of the trend and variance of
  researcher career length across publication years.
\item
  To analyze trends over time, we will calculate the average career
  length for each publication (i.e., average the author career length
  to create one score for each paper) and run a regression analysis
  using career length to predict year of publication. A positive slope
  for year of publication would indicate increasing years of first
  publication (i.e., more younger scholars over time), while a
  negative slope would indicate older years of first publication
  (i.e., more older scholars over time).
\item
  In order to show variance between individuals, we calculate the
  standard deviation of career length for each publication and run a
  regression analysis using this variance representation to predict
  publication year. A positive slope would indicate increasing
  variance over time (i.e., more diversity in the career lengths of
  scholars), while a negative slope would indicate less variance and
  diversity in scholars over time.
\item
  These analyses will be completed separately for each of the four
  large subject areas.
\end{itemize}

\textbf{\emph{Institution}}.

\begin{itemize}
\tightlist
\item
  We will summarize the number of affiliation ids present in BTS
  publications by subject area and visualize these results across
  time. These visualizations will be presented separately for each of
  the four subject areas.
\end{itemize}

\textbf{\emph{Education}}.

\begin{itemize}
\tightlist
\item
  We will summarize the general education categories of individuals at
  the time of publication, along with a summary for change over time.
\end{itemize}

\textbf{\emph{Types of Publications}}.

\begin{itemize}
\tightlist
\item
  We will summarize the coded types of publications for individuals.
\end{itemize}

\textbf{\emph{Publication Metrics}}.

\begin{itemize}
\tightlist
\item
  We will report descriptive statistics on the total number of
  publications, i10 index, and h-index for individuals overall.
\item
  Next, we will use the same analyses described in the career length
  section to analyze trends over time. An increasing slope over time
  indicates that individuals who are publishing more are more
  represented in BTS over time (i.e., increasing numbers of scholars
  with higher publication rates), while a negative slope indicates
  more researchers with less publications.
\item
  A positive slope for standard deviation indicates increasing
  variance over time (i.e., more diversity in the individual
  publication rates), while a negative slope would indicate less
  diversity in researchers over time. While publication rates do not
  represent value as a researcher, they are often used in hiring and
  promotion decisions, and we will use this variable as a proxy to
  gauge the diversity in scholars represented in big teams.
\end{itemize}

\textbf{\emph{Geopolitical Regions}}.

\begin{itemize}
\tightlist
\item
  We will present visualizations of the country information listed for
  authors, and we will discuss the areas of world in which authors
  generally come from, as well as the lowest representation of
  authors.
\item
  To understand the change in representation diversity, we will
  summarize the total number of geopolitical regions for each paper.
  Using a linear model, we will examine if the number of regions
  present is predicted by the year of publication. Increasing
  diversity would be represented by a positive slope, while decreasing
  diversity would be represented by a negative slope.
\item
  Last, we will examine the differences in representation for
  corresponding author sets versus all other authors. For papers with
  10 to 49 authors, we will use the three first authors and the last
  author to compare against other authors. For 50 to 99 authors, five
  first authors plus last will be used, and for all papers with more
  than 100 authors, we will use ten first authors and the last author.
  We will calculate the frequencies of each of the UN Sub-Regions for
  first authors versus other authors, converting these values to
  proportions. Given the expected small sample sizes of these
  contingency tables, we will group together titles based on the year
  of publication (assuming at least 5 publications per year, these may
  be binned by 5-year or smaller increments to increase sample size).
  For each grouping, we will calculate the effect size of the
  differences in frequencies comparing first authors to all other
  authors. Since this data is categorical, we will use Cramer's V to
  represent the effect size. If the effect size includes zero in its
  confidence interval, this result will imply that first and all other
  authors represent the same pattern of UN Sub-Region diversity. Any
  confidence interval that does include zero represents a difference
  in diversity. We will report these values and discuss what regions
  of the world are represented when effect sizes indicate a different
  from zero using standardized residuals.
\end{itemize}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-aphilos2021}{}}%
A philosophical case for big physics. (2021). \emph{Nature Physics}, \emph{17}(6), 661--661. \url{https://doi.org/10.1038/s41567-021-01278-0}

\leavevmode\vadjust pre{\hypertarget{ref-allen2019}{}}%
Allen, L., O'Connell, A., \& Kiermer, V. (2019). How can we ensure visibility and diversity in research contributions? How the Contributor Role Taxonomy (CRediT) is helping the shift from authorship to contributorship. \emph{Learned Publishing}, \emph{32}(1), 71--74. \url{https://doi.org/10.1002/leap.1210}

\leavevmode\vadjust pre{\hypertarget{ref-auspurg2021has}{}}%
Auspurg, K., \& Brüderl, J. (2021). Has the credibility of the social sciences been credibly destroyed? Reanalyzing the {``}many analysts, one data set{''} project. \emph{Socius : Sociological Research for a Dynamic World}, \emph{7}, 23780231211024420.

\leavevmode\vadjust pre{\hypertarget{ref-bago2022}{}}%
Bago, B., Kovacs, M., Protzko, J., Nagy, T., Kekecs, Z., Palfi, B., Adamkovic, M., Adamus, S., Albalooshi, S., Albayrak-Aydemir, N., Alfian, I. N., Alper, S., Alvarez-Solas, S., Alves, S. G., Amaya, S., Andresen, P. K., Anjum, G., Ansari, D., Arriaga, P., \ldots{} Aczel, B. (2022). Situational factors shape moral judgements in the trolley dilemma in Eastern, Southern and Western countries in a culturally diverse sample. \emph{Nature Human Behaviour}, 1--13. \url{https://doi.org/10.1038/s41562-022-01319-5}

\leavevmode\vadjust pre{\hypertarget{ref-buttrick2020}{}}%
Buttrick, N. R., Aczel, B., Aeschbach, L. F., Bakos, B. E., Brühlmann, F., Claypool, H. M., Hüffmeier, J., Kovacs, M., Schuepfer, K., Szecsi, P., Szuts, A., Szöke, O., Thomae, M., Torka, A.-K., Walker, R. J., \& Wood, M. J. (2020). Many Labs 5: Registered Replication of Vohs and Schooler (2008), Experiment 1. \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 429--438. \url{https://doi.org/10.1177/2515245920917931}

\leavevmode\vadjust pre{\hypertarget{ref-castelnovo2018}{}}%
Castelnovo, P., Florio, M., Forte, S., Rossi, L., \& Sirtori, E. (2018). The economic impact of technological procurement for large-scale research infrastructures: Evidence from the Large Hadron Collider at CERN. \emph{Research Policy}, \emph{47}(9), 1853--1867. \url{https://doi.org/10.1016/j.respol.2018.06.018}

\leavevmode\vadjust pre{\hypertarget{ref-coles2022}{}}%
Coles, N. A., Hamlin, J. K., Sullivan, L. L., Parker, T. H., \& Altschul, D. (2022). Build up big-team science. \emph{Nature}, \emph{601}(7894), 505--507. \url{https://doi.org/10.1038/d41586-022-00150-2}

\leavevmode\vadjust pre{\hypertarget{ref-collins2003}{}}%
Collins, F. S., Morgan, M., \& Patrinos, A. (2003). The human genome project: Lessons from large-scale biology. \emph{Science}, \emph{300}(5617), 286--290. \url{https://doi.org/10.1126/science.1084564}

\leavevmode\vadjust pre{\hypertarget{ref-dorison2022}{}}%
Dorison, C., Lerner, J., Heller, B., Rothman, A., Kawachi, I., Wang, K., Rees, V., Gill, B., Gibbs, N., Ebersole, C., Vally, Z., Tajchman, Z., Zsido, A., Zrimsek, M., Chen, Z., Ziano, I., Gialitaki, Z., Ceary, C., Jang, Y., \ldots{} Coles, N. (2022). A global test of message framing on behavioural intentions, policy support, information seeking, and experienced anxiety during the COVID-19 pandemic. \emph{Affective Science}. \url{https://doi.org/10.31234/osf.io/sevkf}

\leavevmode\vadjust pre{\hypertarget{ref-ebersole2016}{}}%
Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., Baranski, E., Bernstein, M. J., Bonfiglio, D. B. V., Boucher, L., Brown, E. R., Budiman, N. I., Cairo, A. H., Capaldi, C. A., Chartier, C. R., Chung, J. M., Cicero, D. C., Coleman, J. A., Conway, J. G., \ldots{} Nosek, B. A. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication. \emph{Journal of Experimental Social Psychology}, \emph{67}, 68--82. \url{https://doi.org/10.1016/j.jesp.2015.10.012}

\leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
Ebersole, C. R., Mathur, M. B., Baranski, E., Bart-Plange, D.-J., Buttrick, N. R., Chartier, C. R., Corker, K. S., Corley, M., Hartshorne, J. K., IJzerman, H., Lazarević, L. B., Rabagliati, H., Ropovik, I., Aczel, B., Aeschbach, L. F., Andrighetto, L., Arnal, J. D., Arrow, H., Babincak, P., \ldots{} Nosek, B. A. (2020). Many Labs 5: Testing Pre-Data-Collection Peer Review as an Intervention to Increase Replicability. \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 309--331. \url{https://doi.org/10.1177/2515245920958687}

\leavevmode\vadjust pre{\hypertarget{ref-10.7554ux2feLife.71601}{}}%
Errington, T. M., Mathur, M., Soderberg, C. K., Denis, A., Perfito, N., Iorns, E., \& Nosek, B. A. (2021). Investigating the replicability of preclinical cancer biology. \emph{eLife}, \emph{10}, e71601. \url{https://doi.org/10.7554/eLife.71601}

\leavevmode\vadjust pre{\hypertarget{ref-forscher2020}{}}%
Forscher, P. S., Wagenmakers, E.-J., Coles, N. A., Silan, M. A. A., Dutra, N. B., Basnight-Brown, D., \& IJzerman, H. (2020). \emph{The benefits, barriers, and risks of big team science}. \url{https://doi.org/10.31234/osf.io/2mdxh}

\leavevmode\vadjust pre{\hypertarget{ref-franco2014}{}}%
Franco, A., Malhotra, N., \& Simonovits, G. (2014). Publication bias in the social sciences: Unlocking the file drawer. \emph{Science}, \emph{345}(6203), 1502--1505. \url{https://doi.org/10.1126/science.1255484}

\leavevmode\vadjust pre{\hypertarget{ref-grahe2014}{}}%
Grahe, J. E. (2014). Announcing open science badges and reaching for the sky. \emph{The Journal of Social Psychology}, \emph{154}(1), 1--3. \url{https://doi.org/10.1080/00224545.2014.853582}

\leavevmode\vadjust pre{\hypertarget{ref-henrich2010}{}}%
Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--83. \url{https://doi.org/10.1017/S0140525X0999152X}

\leavevmode\vadjust pre{\hypertarget{ref-hubbard1997}{}}%
Hubbard, R., \& Armstrong, J. S. (1997). Publication Bias against Null Results. \emph{Psychological Reports}, \emph{80}(1), 337--338. \url{https://doi.org/10.2466/pr0.1997.80.1.337}

\leavevmode\vadjust pre{\hypertarget{ref-ioannidis2015}{}}%
Ioannidis, J. P. A. (2015). Failure to replicate: Sound the alarm. \emph{Cerebrum: The Dana Forum on Brain Science}, \emph{2015}. \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4938249/}

\leavevmode\vadjust pre{\hypertarget{ref-isager2021}{}}%
Isager, P. M., Aert, R. C. M. van, Bahník, Š., Brandt, M. J., DeSoto, K. A., Giner-Sorolla, R., Krueger, J. I., Perugini, M., Ropovik, I., van 't Veer, A. E., Vranka, M., \& Lakens, D. (2021a). Deciding what to replicate: A decision model for replication study selection under resource and knowledge constraints. \emph{Psychological Methods}. \url{https://doi.org/10.1037/met0000438}

\leavevmode\vadjust pre{\hypertarget{ref-isager2021a}{}}%
Isager, P. M., Aert, R. C. M. van, Bahník, Š., Brandt, M. J., DeSoto, K. A., Giner-Sorolla, R., Krueger, J. I., Perugini, M., Ropovik, I., van 't Veer, A. E., Vranka, M., \& Lakens, D. (2021b). Deciding what to replicate: A decision model for replication study selection under resource and knowledge constraints. \emph{Psychological Methods}. \url{https://doi.org/10.1037/met0000438}

\leavevmode\vadjust pre{\hypertarget{ref-john2012}{}}%
John, L. K., Loewenstein, G., \& Prelec, D. (2012). Measuring the Prevalence of Questionable Research Practices With Incentives for Truth Telling. \emph{Psychological Science}, \emph{23}(5), 524--532. \url{https://doi.org/10.1177/0956797611430953}

\leavevmode\vadjust pre{\hypertarget{ref-jones2021}{}}%
Jones, B. C., DeBruine, L. M., Flake, J. K., Liuzza, M. T., Antfolk, J., Arinze, N. C., Ndukaihe, I. L. G., Bloxsom, N. G., Lewis, S. C., Foroni, F., Willis, M. L., Cubillas, C. P., Vadillo, M. A., Turiegano, E., Gilead, M., Simchon, A., Saribay, S. A., Owsley, N. C., Jang, C., \ldots{} Coles, N. A. (2021). To which world regions does the valence{\textendash}dominance model of social perception apply? \emph{Nature Human Behaviour}, \emph{5}(1), 159--169. \url{https://doi.org/10.1038/s41562-020-01007-2}

\leavevmode\vadjust pre{\hypertarget{ref-kidwell2016}{}}%
Kidwell, M. C., Lazarević, L. B., Baranski, E., Hardwicke, T. E., Piechowski, S., Falkenberg, L.-S., Kennett, C., Slowik, A., Sonnleitner, C., Hess-Holden, C., Errington, T. M., Fiedler, S., \& Nosek, B. A. (2016). Badges to Acknowledge Open Practices: A Simple, Low-Cost, Effective Method for Increasing Transparency. \emph{PLOS Biology}, \emph{14}(5), e1002456. \url{https://doi.org/10.1371/journal.pbio.1002456}

\leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
Klein, R. A., Cook, C. L., Ebersole, C. R., Vitiello, C., Nosek, B. A., Hilgard, J., Ahn, P. H., Brady, A. J., Chartier, C. R., Christopherson, C. D., Clay, S., Collisson, B., Crawford, J. T., Cromar, R., Gardiner, G., Gosnell, C. L., Grahe, J., Hall, C., Howard, I., \ldots{} Ratliff, K. A. (2022). Many Labs 4: Failure to Replicate Mortality Salience Effect With and Without Original Author Involvement. \emph{Collabra: Psychology}, \emph{8}(1), 35271. \url{https://doi.org/10.1525/collabra.35271}

\leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
Klein, R. A., Vianello, M., Hasselman, F., Adams, B. G., Adams, R. B., Alper, S., Aveyard, M., Axt, J. R., Babalola, M. T., Bahník, Š., Batra, R., Berkics, M., Bernstein, M. J., Berry, D. R., Bialobrzeska, O., Binan, E. D., Bocian, K., Brandt, M. J., Busching, R., \ldots{} Nosek, B. A. (2018). Many Labs 2: Investigating Variation in Replicability Across Samples and Settings. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490. \url{https://doi.org/10.1177/2515245918810225}

\leavevmode\vadjust pre{\hypertarget{ref-lebel2018}{}}%
LeBel, E. P., McCarthy, R. J., Earp, B. D., Elson, M., \& Vanpaemel, W. (2018). A Unified Framework to Quantify the Credibility of Scientific Findings. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 389--402. \url{https://doi.org/10.1177/2515245918787489}

\leavevmode\vadjust pre{\hypertarget{ref-legate2022}{}}%
Legate, N., Nguyen, T., Weinstein, N., Moller, A., Legault, L., Maniaci, M. R., Ebersole, C. R., Adamkovic, M., Adetula, D. G. A., Agesin, B. B., Ahlgren, L., Akkas, H., Almeida, I., Anjum, G., Antoniadi, M., Arinze, A. I., Arvanitis, A., Rana, K., Badalyan, V., \ldots{} Primbs, M. (2022). A global experiment on motivating social distancing during the COVID-19 pandemic. \emph{Proceedings of the National Academy of Sciences}. \url{https://doi.org/10.31234/osf.io/n3dyf}

\leavevmode\vadjust pre{\hypertarget{ref-maizey2019}{}}%
Maizey, L., \& Tzavella, L. (2019). Barriers and solutions for early career researchers in tackling the reproducibility crisis in cognitive neuroscience. \emph{Cortex}, \emph{113}, 357--359. \url{https://doi.org/10.1016/j.cortex.2018.12.015}

\leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
Mathur, M. B., Bart-Plange, D.-J., Aczel, B., Bernstein, M. H., Ciunci, A. M., Ebersole, C. R., Falcão, F., Ashbaugh, K., Hilliard, R. A., Jern, A., Kellier, D. J., Kessinger, G., Kolb, V. S., Kovacs, M., Lage, C. A., Langford, E. V., Lins, S., Manfredi, D., Meyet, V., \ldots{} Frank, M. C. (2020). Many Labs 5: Registered Multisite Replication of the Tempting-Fate Effects in Risen and Gilovich (2008). \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 394--404. \url{https://doi.org/10.1177/2515245918785165}

\leavevmode\vadjust pre{\hypertarget{ref-maxwell2015}{}}%
Maxwell, S. E., Lau, M. Y., \& Howard, G. S. (2015). Is psychology suffering from a replication crisis?: What does 'failure to replicate' really mean? \emph{American Psychologist}, \emph{70}(6), 487--498. \url{https://doi.org/10.1037/a0039400}

\leavevmode\vadjust pre{\hypertarget{ref-mayo-wilson2021}{}}%
Mayo-Wilson, E., Grant, S., Supplee, L., Kianersi, S., Amin, A., DeHaven, A., \& Mellor, D. (2021). Evaluating implementation of the transparency and openness promotion~(TOP) guidelines:~The TRUST process for rating journal policies, procedures, and practices. \emph{Research Integrity and Peer Review}, \emph{6}(1), 9. \url{https://doi.org/10.1186/s41073-021-00112-8}

\leavevmode\vadjust pre{\hypertarget{ref-moshontz2018}{}}%
Moshontz, H., Campbell, L., Ebersole, C. R., IJzerman, H., Urry, H. L., Forscher, P. S., Grahe, J. E., McCarthy, R. J., Musser, E. D., Antfolk, J., Castille, C. M., Evans, T. R., Fiedler, S., Flake, J. K., Forero, D. A., Janssen, S. M. J., Keene, J. R., Protzko, J., Aczel, B., \ldots{} Chartier, C. R. (2018). The Psychological Science Accelerator: Advancing Psychology Through a Distributed Collaborative Network. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 501--515. \url{https://doi.org/10.1177/2515245918797607}

\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}

\leavevmode\vadjust pre{\hypertarget{ref-newson2021}{}}%
Newson, M., Buhrmester, M., Xygalatas, D., \& Whitehouse, H. (2021). Go WILD, not WEIRD. \emph{Journal for the Cognitive Science of Religion}, \emph{6}(1-2). \url{https://doi.org/10.1558/jcsr.38413}

\leavevmode\vadjust pre{\hypertarget{ref-nosek2015}{}}%
Nosek, B. A., Alter, G., Banks, G. C., Borsboom, D., Bowman, S. D., Breckler, S. J., Buck, S., Chambers, C. D., Chin, G., Christensen, G., Contestabile, M., Dafoe, A., Eich, E., Freese, J., Glennerster, R., Goroff, D., Green, D. P., Hesse, B., Humphreys, M., \ldots{} Yarkoni, T. (2015). Promoting an open research culture. \emph{Science}, \emph{348}(6242), 1422--1425. \url{https://doi.org/10.1126/science.aab2374}

\leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
Nosek, B. A., \& Lakens, D. (2014a). Registered Reports: A Method to Increase the Credibility of Published Results. \emph{Social Psychology}, \emph{45}(3), 137--141. \url{https://doi.org/10.1027/1864-9335/a000192}

\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
Nosek, B. A., \& Lakens, D. (2014b). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137141.

\leavevmode\vadjust pre{\hypertarget{ref-nosek2012}{}}%
Nosek, B. A., Spies, J. R., \& Motyl, M. (2012). Scientific Utopia: II. Restructuring Incentives and Practices to Promote Truth Over Publishability. \emph{Perspectives on Psychological Science}, \emph{7}(6), 615--631. \url{https://doi.org/10.1177/1745691612459058}

\leavevmode\vadjust pre{\hypertarget{ref-oed2016}{}}%
OED. (2016). \emph{Collaboration} (Vol. 3). Oxford University.

\leavevmode\vadjust pre{\hypertarget{ref-opensciencecollaboration2015}{}}%
Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716--aac4716. \url{https://doi.org/10.1126/science.aac4716}

\leavevmode\vadjust pre{\hypertarget{ref-rad2018}{}}%
Rad, M. S., Martingano, A. J., \& Ginges, J. (2018). Toward a psychology of homo sapiens: Making psychological science more representative of the human population. \emph{Proceedings of the National Academy of Sciences}, \emph{115}(45), 11401--11405. \url{https://doi.org/10.1073/pnas.1721165115}

\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
Silberzahn, R., Uhlmann, E. L., Martin, D. P., Anselmi, P., Aust, F., Awtrey, E., Bahník, Š., Bai, F., Bannard, C., Bonnier, E., \& others. (2018). Many analysts, one data set: Making transparent how variations in analytic choices affect results. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337356.

\leavevmode\vadjust pre{\hypertarget{ref-skorb2020}{}}%
Skorb, L., Aczel, B., Bakos, B. E., Feinberg, L., Hałasa, E., Kauff, M., Kovacs, M., Krasuska, K., Kuchno, K., Manfredi, D., Montealegre, A., Pękala, E., Pieńkosz, D., Ravid, J., Rentzsch, K., Szaszi, B., Schulz-Hardt, S., Sioma, B., Szecsi, P., \ldots{} Hartshorne, J. K. (2020). Many Labs 5: Replication of van Dijk, van Kleef, Steinel, and van Beest (2008). \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 418--428. \url{https://doi.org/10.1177/2515245920927643}

\leavevmode\vadjust pre{\hypertarget{ref-stewart2017}{}}%
Stewart, N., Chandler, J., \& Paolacci, G. (2017). Crowdsourcing samples in cognitive science. \emph{Trends in Cognitive Sciences}, \emph{21}(10), 736--748. \url{https://doi.org/10.1016/j.tics.2017.06.007}

\leavevmode\vadjust pre{\hypertarget{ref-stewart2020}{}}%
Stewart, S., Rinke, E. M., McGarrigle, R., Lynott, D., Lunny, C., Lautarescu, A., Galizzi, M. M., Farran, E. K., \& Crook, Z. (2020). \emph{Pre-registration and registered reports: A primer from UKRN}. \url{https://doi.org/10.31219/osf.io/8v2n7}

\leavevmode\vadjust pre{\hypertarget{ref-vanbavel2022}{}}%
Van Bavel, J. J., Cichocka, A., Capraro, V., Sjåstad, H., Nezlek, J. B., Pavlović, T., Alfano, M., Gelfand, M. J., Azevedo, F., Birtel, M. D., Cislak, A., Lockwood, P. L., Ross, R. M., Abts, K., Agadullina, E., Aruta, J. J. B., Besharati, S. N., Bor, A., Choma, B. L., \ldots{} Boggio, P. S. (2022). National identity predicts public health support during a global pandemic. \emph{Nature Communications}, \emph{13}(1), 517. \url{https://doi.org/10.1038/s41467-021-27668-9}

\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
Vazire, S., Schiavone, S. R., \& Bottesini, J. G. (2022). Credibility Beyond Replicability: Improving the Four Validities in Psychological Science. \emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168. \url{https://doi.org/10.1177/09637214211067779}

\leavevmode\vadjust pre{\hypertarget{ref-wang2021}{}}%
Wang, K., Goldenberg, A., Dorison, C. A., Miller, J. K., Uusberg, A., Lerner, J. S., Gross, J. J., Agesin, B. B., Bernardo, M., Campos, O., Eudave, L., Grzech, K., Ozery, D. H., Jackson, E. A., Garcia, E. O. L., Drexler, S. M., Jurković, A. P., Rana, K., Wilson, J. P., \ldots{} Moshontz, H. (2021). A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic. \emph{Nature Human Behaviour}, \emph{5}(8), 1089--1110. \url{https://doi.org/10.1038/s41562-021-01173-x}

\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}

\end{CSLReferences}

\endgroup

\end{document}

### 2022-09-09 04.manuscript_scopus.Rmd
updated with no typos

@@
 documentclass     : "apa7"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 ---
@@
 projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired
-with the meta-scienctific publications focusing on researcher practices
+with the meta-scientific publications focusing on researcher practices
 and incentive structures [@silberzahn2018many; @john2012] led to a

### 2022-09-09 04.manuscript_scopus.tex
updated with no typos

@@
 projects (Errington et al., 2021; Open Science Collaboration, 2015), paired
-with the meta-scienctific publications focusing on researcher practices
+with the meta-scientific publications focusing on researcher practices
 and incentive structures (John et al., 2012; Silberzahn et al., 2018) led to a

### 2023-03-02 manuscript_scopus.Rmd
rearranging for clarity
adding pictures for sav

--- 2022-09-09 04.manuscript_scopus.Rmd
@@
 
-csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja'`)"
 documentclass     : "apa7"
@@
 ```{r setup, include = FALSE}
+#knitr::opts_knit(echo = TRUE)
 library(papaja)
 library(knitr)
+library(ggplot2)
+library(treemapify)
+library(countrycode)
+library(rio)
+library(maps)
+library(dplyr)
 ```
 
-# Significance
+```{r data, include = FALSE}
+geo_country <- import("py_outputs/geo_country.xlsx")
+```
 
@@
 credibility movement. Publications on BTS generally explore challenges,
-lessons learned, the need for BTS [@forscher2020; @coles2022].
+lessons learned, and the need for BTS [@forscher2020; @coles2022].
 
@@
 
-# Approach
+# Research Questions
 
@@
 peer-reviewed journals or had posted a full paper pre-print. We will use
-data from 1970 and forward in the publications (`ani)` database, as it
+data from 1970 and forward in the publications (`ani`) database, as it
 is noted online that this time period includes cited references for
@@
 impact using the Source Normalized Impact per Paper from the journal
-(`sources)` database.
+(`sources`) database.
 
@@
     authors.
+
+```{r geo-map}
+# serbia has changed codes
+geo_country$affiliation_tag_country <- toupper(geo_country$affiliation_tag_country)
+geo_country <- subset(geo_country, affiliation_tag_country != "NONE")
+geo_country$affiliation_tag_country[geo_country$affiliation_tag_country == "SCG"] <- "SRB"
+
+geo_country <- geo_country %>% 
+  group_by(affiliation_tag_country) %>% 
+  summarize(count = sum(count))
+
+# convert country code to region code
+# this will warn you about the ones that have multiple countries 
+# create a world map 
+world_map <- map_data(map = "world")
+world_map$orig_region <- world_map$region
+world_map$region <- iso.alpha(world_map$region, n = 3)
+world_map <- subset(world_map, region != "ATA")
+
+# make a map on a continuous scale
+ggplot(geo_country) +
+  geom_map(aes(map_id = affiliation_tag_country, fill = count), map = world_map) +
+  geom_polygon(data = world_map, 
+               aes(x = long, y = lat, group = group), 
+               colour = 'black', fill = NA) + 
+  theme_void() + 
+  scale_fill_distiller(name = "Sample Size",
+                       palette = "Greys",
+                       direction = 1,
+                       na.value = "white")
+
+ggsave("figure/continuous_country.png")
+
+# maybe try binning
+geo_country$count_binned <- if_else(
+  geo_country$count >= 10000, "10,000+", 
+  if_else(
+    geo_country$count < 10000 & geo_country$count >= 5000, "5,000-9,999",
+    if_else(
+      geo_country$count < 5000 & geo_country$count >= 1000, "1,000-4,999",
+      if_else(
+        geo_country$count < 1000 & geo_country$count >= 100, "100-999",
+        "< 100"
+      )
+    )
+  )
+)
+
+geo_country$count_binned <- factor(geo_country$count_binned, 
+                                   levels = unique(geo_country$count_binned))
+
+# map of binned data 
+bin_country <- ggplot(geo_country) +
+  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned), map = world_map) +
+  geom_polygon(data = world_map, 
+               aes(x = long, y = lat, group = group), 
+               colour = 'black', fill = NA) + 
+  theme_void() + 
+  scale_fill_manual(name = "Sample Size",
+                    values = c( "black", "#323232", "#646464","#969696","#c8c8c8"))
+
+bin_country
+
+ggsave("figure/binned_country.png", bin_country)
+
+# tree map
+geo_country$un_region_sub <- countrycode(
+  sourcevar = geo_country$affiliation_tag_country,
+  origin = 'iso3c', 
+  destination = 'un.regionsub.name'
+)
+
+geo_country$un_region <- countrycode(
+  sourcevar = geo_country$affiliation_tag_country,
+  origin = 'iso3c', 
+  destination = 'un.region.name'
+)
+
+geo_country$un_region[geo_country$affiliation_tag_country == "TWN"] <- "Asia"
+geo_country$un_region_sub[geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
+
+geo_country <- geo_country %>% 
+  na.omit()
+
+tree <- ggplot(geo_country, aes(area = count, fill = count_binned,
+               label = affiliation_tag_country, subgroup = un_region_sub)) +
+  geom_treemap() +
+  geom_treemap_subgroup_border(colour = "white", size = 5) +
+  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
+  #                            alpha = 0.25, colour = "black",
+  #                            fontface = "italic") +
+  geom_treemap_text(colour = "white", place = "centre",
+                    size = 15, grow = FALSE) +  
+  scale_fill_manual(name = "Sample Size",
+                    values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
+  # scale_fill_gradient(name = "Sample Size",
+  #                     low = "#c8c8c8", 
+  #                     high = "#323232")
+
+tree
+
+ggsave("figure/treemap.png",
+       tree)
+```
+
 -   To understand the change in representation diversity, we will
@@
     diversity would be represented by a negative slope.
+
 -   Last, we will examine the differences in representation for

### 2023-03-10 manuscript_scopus.Rmd
adding all the outputs

@@
 geo_country <- import("py_outputs/geo_country.xlsx")
+geo_region <- import("py_outputs/geo_region.xlsx")
 ```
@@
     areas, presenting graphics of the number of publication across time
+
+total
+
+13581
+
++----------------+-----+
+|publication_type|count|
++----------------+-----+
+|              sh|   41|
+|              cp|  266|
+|              ar|12689|
+|              dp|    4|
+|              pp|  580|
+|              ip|    1|
++----------------+-----+
+
+subject area 
++-----------------+-----+
+|      SubjectArea|count|
++-----------------+-----+
+|  Health Sciences|10685|
+|Physical Sciences| 6151|
+|Multidisciplinary| 1569|
+|  Social Sciences|  543|
+|    Life Sciences| 7686|
++-----------------+-----+
+
+time
+
+pub_time_count
+
 -   Number of distinct journals within each of the four subject areas
+
+Out[52]: 2534
+
++-----------------+------------+
+|      SubjectArea|count(srcid)|
++-----------------+------------+
+|  Health Sciences|        1472|
+|Physical Sciences|         641|
+|Multidisciplinary|          14|
+|  Social Sciences|         206|
+|    Life Sciences|        1024|
++-----------------+------------+
+
 -   Statistics (mean, median, standard deviation, minimum, maximum) of
@@
     four subject areas.
+
++-----------------+------------------+------------------+---------+------------+---------+
+|      SubjectArea|         avg(snip)| stddev_samp(snip)|min(snip)|median(snip)|max(snip)|
++-----------------+------------------+------------------+---------+------------+---------+
+|  Health Sciences|  4.39848449724717|7.1846479513521615|      0.0|       2.078|  173.932|
+|Physical Sciences|1.7298434289762685| 1.336672368345959|    0.155|       1.278|   30.405|
+|Multidisciplinary| 6.092944123314063|   4.3151334953509|    0.032|       3.341|   11.342|
+|  Social Sciences| 2.204784860557769|2.1441319264666743|    0.017|       1.605|   30.405|
+|    Life Sciences| 2.524247249015079| 2.044898988084329|    0.017|       1.742|   12.624|
++-----------------+------------------+------------------+---------+------------+---------+
 
@@
     classifications.
+
+pub_time_subject
+
 -   The keywords present in the publications data overall to identify
@@
     keywords.
+
+keywords
 
@@
 -   The total number of unique authors
+
++-----------+
+|count(auid)|
++-----------+
+|     257536|
++-----------+
+
 -   Statistics (mean, standard deviation, minimum, maximum, median) on
     the number of authors included on publications.
+
+	count(Authorseq)	avg(Authorseq)	stddev_samp(Authorseq)	min(Authorseq)	median(Authorseq)	max(Authorseq)
+0	13581	49.904646	207.006114	10	19.0	5155
+
 -   We will present visualizations of these results across time.
+
+author_time
 
@@
     researcher career length across publication years.
+
+career_time
+
 -   To analyze trends over time, we will calculate the average career
@@
 
+------ Physical Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.531373   0.030990  -17.146   0.000000
+##  -0.207000   0.059698   -3.467   0.000533
+## 2020.342936   0.367600 5496.040   0.000000
+## ---
+## Mean squared error:  30.862113 , RMSE:  5.555368
+## Multiple R-squared: 0.145118 ,             Total iterations: 0
+------------
+
+------ Social Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.437422   0.093563   -4.675   0.000004
+##  -0.104549   0.146459   -0.714   0.475750
+## 2019.182625   0.764850 2639.973   0.000000
+## ---
+## Mean squared error:  30.685713 , RMSE:  5.539469
+## Multiple R-squared: 0.118772 ,             Total iterations: 0
+------------
+
+------ Health Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.460876   0.019674  -23.425   0.000000
+##  -0.218675   0.037611   -5.814   0.000000
+## 2019.076458   0.231406 8725.260   0.000000
+## ---
+## Mean squared error:  30.039405 , RMSE:  5.480822
+## Multiple R-squared: 0.144584 ,             Total iterations: 0
+------------
+
+------ Life Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.604957   0.026519  -22.812   0.000000
+##  -0.056843   0.046915   -1.212   0.225716
+## 2019.490201   0.276602 7301.067   0.000000
+## ---
+## Mean squared error:  27.654316 , RMSE:  5.258737
+## Multiple R-squared: 0.175747 ,             Total iterations: 0
+------------
+
 ***Institution***.
@@
 
++----------------------+
+|count(affiliation_ids)|
++----------------------+
+|                 35114|
++----------------------+
+
+inst time
+
 ***Education***.
 
--   We will summarize the general education categories of individuals at
-    the time of publication, along with a summary for change over time.
+We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.
+
+    Figure out how messy this is for text processing requirements
+    For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are "normal" academics/researchers)
+    We will only perform this analysis if the proportion of information avaliable is over 50%.
+
++-----------+------+
+|    degrees| count|
++-----------+------+
+|       null|656440|
+|         MD|  8190|
+|        PhD|  3879|
+|    MD, PhD|  1267|
+|       M.D.|  1002|
+|        Dr.|   490|
+|        MSc|   461|
+|        MPH|   368|
+| Prof., PhD|   349|
+|      Ph.D.|   348|
+|         MS|   330|
+|     MD PhD|   285|
+|        MD.|   279|
+|   Prof. MD|   266|
+|  Prof. PhD|   239|
+|         BS|   232|
+|       Prof|   220|
+|         BA|   196|
+|M.D., Ph.D.|   191|
+|    MD, MPH|   158|
++-----------+------+
 
@@
 
+pub_type versus normal_pub_type
+
 ***Publication Metrics***.
 
--   We will report descriptive statistics on the total number of
-    publications, i10 index, and h-index for individuals overall.
--   Next, we will use the same analyses described in the career length
-    section to analyze trends over time. An increasing slope over time
-    indicates that individuals who are publishing more are more
-    represented in BTS over time (i.e., increasing numbers of scholars
-    with higher publication rates), while a negative slope indicates
-    more researchers with less publications.
--   A positive slope for standard deviation indicates increasing
-    variance over time (i.e., more diversity in the individual
-    publication rates), while a negative slope would indicate less
-    diversity in researchers over time. While publication rates do not
-    represent value as a researcher, they are often used in hiring and
-    promotion decisions, and we will use this variable as a proxy to
-    gauge the diversity in scholars represented in big teams.
+    We will report descriptive statistics on the total number of publications and h-index for individuals overall.
+        Do this for each unique person and report averages
+        Do this for each publication and create an average for each publication
+    Next, we will use the same analyses described in the career length section to analyze trends over time.
+An increasing slope over time indicates that individuals who are publishing more are more represented in BTS over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
+    A positive slope for standard deviation indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
+While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.
+    We will separate these by each of the four subject areas.
+
+	avg_pub_count	std_pub_count
+0	4.451816	6.901369
+
+	avg(avg_pub_count AS mean_of_avg_pub_count)	stddev_samp(avg_pub_count AS std_of_avg_pub_count)	avg(std_pub_count AS mean_of_std_pub_count)	stddev_samp(std_pub_count AS std_of_std_pub_count)
+0	7.581413	5.797233	7.140015	5.10383
+
+	avg_HIndex	std_HIndex	med_HIndex
+0	14.242142	43.798203	2.0
+
+	avg_of_avg_HIndex	std_of_avg_HIndex	avg_of_std_HIndex	std_of_std_HIndex	med_of_med_HIndex
+0	28.136255	38.013819	36.430509	46.474619	5.0
+
+------ Physical Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.004420   0.022715   -0.195   0.845717
+##  -0.105746   0.034058   -3.105   0.001922
+## 2015.347578   0.195556 10305.717   0.000000
+## ---
+## Mean squared error:  35.756076 , RMSE:  5.979638
+## Multiple R-squared: 0.009554 ,             Total iterations: 0
+------------
+
+------ Social Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.335536   0.179536   -1.869   0.062389
+##   0.130796   0.186924    0.700   0.484517
+## 2016.658826   0.487148 4139.727   0.000000
+## ---
+## Mean squared error:  34.070868 , RMSE:  5.837026
+## Multiple R-squared: 0.021558 ,             Total iterations: 0
+------------
+
+------ Health Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.235551   0.028158   -8.365   0.000000
+##  -0.006692   0.026612   -0.251   0.801476
+## 2014.979175   0.119976 16794.893   0.000000
+## ---
+## Mean squared error:  33.860172 , RMSE:  5.818949
+## Multiple R-squared: 0.035782 ,             Total iterations: 0
+------------
+
+------ Life Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.430599   0.037807  -11.389   0.000000
+##   0.133215   0.034255    3.889   0.000102
+## 2016.008237   0.147870 13633.624   0.000000
+## ---
+## Mean squared error:  31.736306 , RMSE:  5.633499
+## Multiple R-squared: 0.054081 ,             Total iterations: 0
+------------
 
@@
 
-ggsave("figure/treemap.png",
-       tree)
+ggsave("figure/treemap.png", tree)
 ```
@@
     diversity would be represented by a negative slope.
+
+total number of unique GP for each publication 
+using year to predict GP 
+positive slope means that as year goes up number of GP goes up 
+negative slope means that as year goes up number of GP goes down 
+forest plot of the effects + confidence interval
+
+------ Physical Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.061001   0.022958   -2.657   0.007923
+## 130.518393  46.247823    2.822   0.004802
+## ---
+## Mean squared error:  56.853041 , RMSE:  7.540096
+## Multiple R-squared: 0.002357 ,             Total iterations: 0
+------------
+
+------ Social Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.077040   0.058153   -1.325   0.186023
+## 160.766462 117.214988    1.372   0.170993
+## ---
+## Mean squared error:  45.807761 , RMSE:  6.768143
+## Multiple R-squared: 0.004491 ,             Total iterations: 0
+------------
+
+------ Health Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.017775   0.009794   -1.815   0.069578
+##  40.118948  19.718323    2.035   0.041926
+## ---
+## Mean squared error:  25.532574 , RMSE:  5.052977
+## Multiple R-squared: 0.000434 ,             Total iterations: 0
+------------
+
+------ Life Sciences ------
+
+Note: the last rows are the information for Intercept
+## -------------------------------------------------
+##   Estimate   |   Std.Error | t Values  |  P-value
+##  -0.014946   0.010485   -1.425   0.154081
+##  34.499812  21.117788    1.634   0.102392
+## ---
+## Mean squared error:  17.279398 , RMSE:  4.156850
+## Multiple R-squared: 0.000434 ,             Total iterations: 0
+------------
 
@@
     in diversity. We will report these values and discuss what regions
-    of the world are represented when effect sizes indicate a different
+    of the world are represented when effect sizes indicate a difference
     from zero using standardized residuals.
+
+```{r}
+library(tidyr)
+geo_region_wide <- geo_region %>% 
+  pivot_wider(id_cols = Year, 
+              names_from = aff_un, 
+              values_from = count,
+              values_fill = 0)
+```
+
+end up with a list of effect sizes by year by small medium large 
+x axis is year
+y axis is the effect size and the confidence interval 
+if diversity is increasing then the patterns would be more similar (effect size of zero)
+if diversity is not increasing then the patterns would be different (effect size does not include zero)
+
+who is not represented in the "corresponding" spots - proportion chart by decades stacked bar chart of the decades
 

### 2023-03-10 manuscript_scopus.Rmd
adding new stuff

@@
 library(dplyr)
+library(tidyr)
+library(MOTE)
 ```
@@
 ```{r data, include = FALSE}
-geo_country <- import("py_outputs/geo_country.xlsx")
-geo_region <- import("py_outputs/geo_region.xlsx")
+# things to import
+var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
+              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
+              "medium_other_gp", "normal_pub_type", "pub_time_count", 
+              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp")
+
+var_list_import <- paste0("py_outputs/", var_list, ".xlsx")
+
+DF <- lapply(var_list_import, import)
+names(DF) <- var_list
 ```
@@
 # serbia has changed codes
-geo_country$affiliation_tag_country <- toupper(geo_country$affiliation_tag_country)
-geo_country <- subset(geo_country, affiliation_tag_country != "NONE")
-geo_country$affiliation_tag_country[geo_country$affiliation_tag_country == "SCG"] <- "SRB"
+DF$geo_country$affiliation_tag_country <- toupper(DF$geo_country$affiliation_tag_country)
+DF$geo_country <- subset(DF$geo_country, affiliation_tag_country != "NONE")
+DF$geo_country$affiliation_tag_country[DF$geo_country$affiliation_tag_country == "SCG"] <- "SRB"
 
-geo_country <- geo_country %>% 
+DF$geo_country <- DF$geo_country %>% 
   group_by(affiliation_tag_country) %>% 
@@
 # make a map on a continuous scale
-ggplot(geo_country) +
+ggplot(DF$geo_country) +
   geom_map(aes(map_id = affiliation_tag_country, fill = count), map = world_map) +
@@
 # maybe try binning
-geo_country$count_binned <- if_else(
-  geo_country$count >= 10000, "10,000+", 
+DF$geo_country$count_binned <- if_else(
+  DF$geo_country$count >= 10000, "10,000+", 
   if_else(
-    geo_country$count < 10000 & geo_country$count >= 5000, "5,000-9,999",
+    DF$geo_country$count < 10000 & DF$geo_country$count >= 5000, "5,000-9,999",
     if_else(
-      geo_country$count < 5000 & geo_country$count >= 1000, "1,000-4,999",
+      DF$geo_country$count < 5000 & DF$geo_country$count >= 1000, "1,000-4,999",
       if_else(
-        geo_country$count < 1000 & geo_country$count >= 100, "100-999",
+        DF$geo_country$count < 1000 & DF$geo_country$count >= 100, "100-999",
         "< 100"
@@
 
-geo_country$count_binned <- factor(geo_country$count_binned, 
-                                   levels = unique(geo_country$count_binned))
+DF$geo_country$count_binned <- factor(DF$geo_country$count_binned, 
+                                   levels = unique(DF$geo_country$count_binned))
 
 # map of binned data 
-bin_country <- ggplot(geo_country) +
+bin_country <- ggplot(DF$geo_country) +
   geom_map(aes(map_id = affiliation_tag_country, fill = count_binned), map = world_map) +
@@
 # tree map
-geo_country$un_region_sub <- countrycode(
-  sourcevar = geo_country$affiliation_tag_country,
+DF$geo_country$un_region_sub <- countrycode(
+  sourcevar = DF$geo_country$affiliation_tag_country,
   origin = 'iso3c', 
@@
 
-geo_country$un_region <- countrycode(
-  sourcevar = geo_country$affiliation_tag_country,
+DF$geo_country$un_region <- countrycode(
+  sourcevar = DF$geo_country$affiliation_tag_country,
   origin = 'iso3c', 
@@
 
-geo_country$un_region[geo_country$affiliation_tag_country == "TWN"] <- "Asia"
-geo_country$un_region_sub[geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
+DF$geo_country$un_region[DF$geo_country$affiliation_tag_country == "TWN"] <- "Asia"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
 
-geo_country <- geo_country %>% 
+DF$geo_country <- DF$geo_country %>% 
   na.omit()
 
-tree <- ggplot(geo_country, aes(area = count, fill = count_binned,
+tree <- ggplot(DF$geo_country, aes(area = count, fill = count_binned,
                label = affiliation_tag_country, subgroup = un_region_sub)) +
@@
     diversity would be represented by a negative slope.
+
+```{r}
+label <- c("Physical", "Social", "Health", "Life")
+b_values <- c(-0.061001, -0.077040, -0.017775, -0.014946)
+se_values <- c(0.022958, 0.058153, 0.009794, 0.010485)
+r2_values <- c(0.002357, 0.004491, 0.000434, 0.000434)
+sample_size <- 13000
+
+r2_low <- 1:length(r2_values)
+r2_high <- 1:length(r2_values)
+for (i in 1:length(r2_values)){
+  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
+  r2_low[i] <- temp$Lower.Conf.Limit.R2
+  r2_high[i] <- temp$Upper.Conf.Limit.R2
+}
+
+graph_data <- data.frame(
+  "label" = label,
+  "estimate" = b_values,
+  "type" = "Coefficient",
+  "low" = b_values - qt(.025, sample_size, lower.tail = F)*se_values,
+  "high" = b_values + qt(.025, sample_size, lower.tail = F)*se_values) %>% 
+  bind_rows(
+    data.frame(  
+      "label" = label, 
+      "estimate" = r2_values,
+      "type" = "Effect Size",
+      "low" = r2_low,
+      "high" = r2_high)
+  )
+
+ggplot(graph_data, aes(label, estimate)) + 
+  geom_point() +
+  geom_pointrange(aes(ymin = low, ymax = high)) +
+  theme_classic() + 
+  facet_wrap(~type) + 
+  geom_hline(yintercept = 0) + 
+  coord_flip() + 
+  xlab("Subject Area") + 
+  ylab("")
+```
 
@@
 ```{r}
-library(tidyr)
-geo_region_wide <- geo_region %>% 
+DF$small_first_gp <- DF$small_first_gp %>% 
   pivot_wider(id_cols = Year, 
@@
               values_fill = 0)
+
+DF$small_other_gp <- DF$small_other_gp %>% 
+  pivot_wider(id_cols = Year, 
+              names_from = aff_un, 
+              values_from = count,
+              values_fill = 0) %>% 
+  select(colnames(DF$small_first_gp))
+
+small_effect <- data.frame(
+  year = 1:length(unique(DF$small_first_gp$Year)),
+  v = 1:length(unique(DF$small_first_gp$Year)),
+  low = 1:length(unique(DF$small_first_gp$Year)),
+  high = 1:length(unique(DF$small_first_gp$Year))
+)
+i <- 1
+for (year in unique(DF$small_first_gp$Year)){
+  temp_table <- DF$small_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
+    bind_rows(DF$small_other_gp %>% filter(Year == year) %>% select(-Year))
+
+  col_total <- colSums(temp_table)
+  temp_table <- temp_table %>% 
+    select(names(col_total)[col_total > 0])
+  #### FIX WARNING ISSUE HERE#####
+  temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
+  mote_temp <- suppressWarnings(v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
+                        r = nrow(temp_table), c = ncol(temp_table), 
+                        a = .05))
+  small_effect$year[i] <- year
+  small_effect$v[i] <- mote_temp$v
+  small_effect$low[i] <- mote_temp$vlow
+  small_effect$high[i] <- mote_temp$vhigh
+  i <- i + 1
+}
+
+ggplot(small_effect, aes(year,v)) + 
+  geom_point() + 
+  theme_classic() + 
+  geom_pointrange(aes(ymin = low, ymax = high)) + 
+  xlab("Year") + 
+  ylab("Effect Size")
+
+DF_decade <- DF$small_first_gp %>% 
+  mutate(who = "First") %>% 
+  bind_rows(
+    DF$small_other_gp %>% 
+      mutate(who = "Other")
+  ) %>% 
+  mutate(Decade = ifelse(Year < 1990, "1980s", 
+                         ifelse(Year < 2000, "1990s", 
+                                ifelse(Year < 2010, "2000s", 
+                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
+  group_by(who, Decade) %>% 
+  summarize_all(sum) %>% 
+  pivot_longer(cols = `Western Europe`:Mirconesia,
+               names_to = "Country", 
+               values_to = "Count")
+
+DF_decade$region <- factor(
+  DF_decade$Country,
+  levels = unique(DF_decade$Country),
+  labels = 
+)
+
+"Africa"
+"Americas"
+"Asia"
+"Europe"
+"Oceania"
+
+ggplot(DF_decade, aes(who, Count, fill = Country)) + 
+    geom_bar(position="fill", stat="identity") + 
+  theme_classic() + 
+  facet_grid(~Decade) + 
+  xlab("Author Type") + 
+  ylab("Percent")
+
+## do the seven big regions
 ```

### 2023-03-15 manuscript_scopus.Rmd
you get a doc!

@@
 draft             : no
-#documentclass     : "apa6"
 classoption       : "man"
-#output            : papaja::apa6_pdf
 editor_options: 
@@
 
-csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja'`)"
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
 documentclass     : "apa7"
@@
 library(MOTE)
+library(MBESS)
 ```

### 2023-03-16 manuscript_scopus.Rmd
adding pictures

@@
 library(MBESS)
+library(patchwork)
 ```
@@
 
-```{r}
+    ## fix the stupid CIs
+
+```{r small-effects}
 DF$small_first_gp <- DF$small_first_gp %>% 
+  filter(aff_un != "other") %>% 
   pivot_wider(id_cols = Year, 
@@
 DF$small_other_gp <- DF$small_other_gp %>% 
+  filter(aff_un != "other") %>% 
   pivot_wider(id_cols = Year, 
@@
     select(names(col_total)[col_total > 0])
-  #### FIX WARNING ISSUE HERE#####
   temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
-  mote_temp <- suppressWarnings(v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
+
+  tryCatch(mote_temp <- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
                         r = nrow(temp_table), c = ncol(temp_table), 
-                        a = .05))
+                        a = .05), 
+       warning = function(w) { 
+         mote_temp <<- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
+                        r = nrow(temp_table), c = ncol(temp_table), 
+                        a = .05)
+         mote_temp$vlow <<- 0
+  }
+  )
+
   small_effect$year[i] <- year
@@
   small_effect$high[i] <- mote_temp$vhigh
+  small_effect$people[i] <- mote_temp$n
   i <- i + 1
@@
 
-ggplot(small_effect, aes(year,v)) + 
-  geom_point() + 
+small_effect$high[is.na(small_effect$high)] <- 0
+small_effect <- 
+  small_effect %>% 
+  filter(v != Inf)
+
+small_dot <- ggplot(small_effect, aes(year,v)) + 
+  geom_point(aes(size = people)) + 
   theme_classic() + 
@@
   xlab("Year") + 
-  ylab("Effect Size")
+  ylab("Effect Size") + 
+  scale_size_continuous(name = "Num Authors")
 
@@
 
-DF_decade$region <- factor(
-  DF_decade$Country,
-  levels = unique(DF_decade$Country),
-  labels = 
-)
-
-"Africa"
-"Americas"
-"Asia"
-"Europe"
-"Oceania"
-
-ggplot(DF_decade, aes(who, Count, fill = Country)) + 
-    geom_bar(position="fill", stat="identity") + 
+# North America, Africa (combine), NWS Europe, Eastern Asia, Latin America, Rest of Europe, Rest of Asia, Everything Else
+
+DF_decade$Country_2 <- DF_decade$Country
+DF_decade$Country_2 <- gsub(".*Africa.*", "Africa", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Northern Europe|Southern Europe|Western Europe", "NWS Europe", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("South-Eastern Europe|Eastern Europe", "ESE Europe", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Central Asia|South-Eastern Asia|Southern Asia|Western Asia", "Asia", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Melanesia|Mirconesia|New zealand and Australia|Polynesia", "Other", DF_decade$Country_2)
+
+DF_decade_sm <- DF_decade %>% 
+  group_by(Country_2, Decade, who) %>% 
+  summarize(Count = sum(Count), .groups = "keep")
+
+small_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
+    geom_bar(position="fill", stat="identity", color = "black") + 
   theme_classic() + 
@@
   xlab("Author Type") + 
-  ylab("Percent")
-
-## do the seven big regions
+  ylab("Percent of Authors") + 
+  scale_fill_brewer(name = "Region", palette = "Spectral")
+```
+
+```{r medium-effects}
+DF$medium_first_gp <- DF$medium_first_gp %>% 
+  filter(aff_un != "other") %>% 
+  pivot_wider(id_cols = Year, 
+              names_from = aff_un, 
+              values_from = count,
+              values_fill = 0)
+
+DF$medium_other_gp <- DF$medium_other_gp %>% 
+  filter(aff_un != "other") %>% 
+  pivot_wider(id_cols = Year, 
+              names_from = aff_un, 
+              values_from = count,
+              values_fill = 0) %>% 
+  select(colnames(DF$medium_first_gp))
+
+medium_effect <- data.frame(
+  year = 1:length(unique(DF$medium_first_gp$Year)),
+  v = 1:length(unique(DF$medium_first_gp$Year)),
+  low = 1:length(unique(DF$medium_first_gp$Year)),
+  high = 1:length(unique(DF$medium_first_gp$Year))
+)
+i <- 1
+for (year in unique(DF$medium_first_gp$Year)){
+  temp_table <- DF$medium_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
+    bind_rows(DF$medium_other_gp %>% filter(Year == year) %>% select(-Year))
+
+  col_total <- colSums(temp_table)
+  temp_table <- temp_table %>% 
+    select(names(col_total)[col_total > 0])
+  temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
+  tryCatch(mote_temp <- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
+                        r = nrow(temp_table), c = ncol(temp_table), 
+                        a = .05), 
+       warning = function(w) { 
+         mote_temp <<- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
+                        r = nrow(temp_table), c = ncol(temp_table), 
+                        a = .05)
+         mote_temp$vlow <<- 0
+  }
+  )
+  medium_effect$year[i] <- year
+  medium_effect$v[i] <- mote_temp$v
+  medium_effect$low[i] <- mote_temp$vlow
+  medium_effect$high[i] <- mote_temp$vhigh
+  medium_effect$people[i] <- mote_temp$n
+  i <- i + 1
+}
+
+medium_effect$high[is.na(medium_effect$high)] <- 0
+medium_effect <- 
+  medium_effect %>% 
+  filter(v != Inf)
+
+medium_dot <- ggplot(medium_effect, aes(year,v)) + 
+  geom_point(aes(size = people)) + 
+  theme_classic() + 
+  geom_pointrange(aes(ymin = low, ymax = high)) + 
+  xlab("Year") + 
+  ylab("Effect Size") + 
+  scale_size_continuous(name = "Num Authors")
+
+DF_decade <- DF$medium_first_gp %>% 
+  mutate(who = "First") %>% 
+  bind_rows(
+    DF$medium_other_gp %>% 
+      mutate(who = "Other")
+  ) %>% 
+  mutate(Decade = ifelse(Year < 1990, "1980s", 
+                         ifelse(Year < 2000, "1990s", 
+                                ifelse(Year < 2010, "2000s", 
+                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
+  group_by(who, Decade) %>% 
+  summarize_all(sum) %>% 
+  pivot_longer(cols = `Western Europe`:Melanesia, 
+               #### check this later ####
+               names_to = "Country", 
+               values_to = "Count")
+
+# North America, Africa (combine), NWS Europe, Eastern Asia, Latin America, Rest of Europe, Rest of Asia, Everything Else
+
+DF_decade$Country_2 <- DF_decade$Country
+DF_decade$Country_2 <- gsub(".*Africa.*", "Africa", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Northern Europe|Southern Europe|Western Europe", "NWS Europe", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("South-Eastern Europe|Eastern Europe", "ESE Europe", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Central Asia|South-Eastern Asia|Southern Asia|Western Asia", "Asia", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Melanesia|Mirconesia|New zealand and Australia|Polynesia", "Other", DF_decade$Country_2)
+
+DF_decade_sm <- DF_decade %>% 
+  group_by(Country_2, Decade, who) %>% 
+  summarize(Count = sum(Count), .groups = "keep")
+
+medium_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
+    geom_bar(position="fill", stat="identity", color = "black") + 
+  theme_classic() + 
+  facet_grid(~Decade) + 
+  xlab("Author Type") + 
+  ylab("Percent of Authors") + 
+  scale_fill_brewer(name = "Region", palette = "Spectral")
+```
+
+```{r large-effects}
+DF$large_first_gp <- DF$large_first_gp %>% 
+  filter(aff_un != "other") %>% 
+  pivot_wider(id_cols = Year, 
+              names_from = aff_un, 
+              values_from = count,
+              values_fill = 0)
+
+DF$large_other_gp <- DF$large_other_gp %>% 
+  filter(aff_un != "other") %>% 
+  pivot_wider(id_cols = Year, 
+              names_from = aff_un, 
+              values_from = count,
+              values_fill = 0) %>% 
+  select(colnames(DF$large_first_gp))
+
+large_effect <- data.frame(
+  year = 1:length(unique(DF$large_first_gp$Year)),
+  v = 1:length(unique(DF$large_first_gp$Year)),
+  low = 1:length(unique(DF$large_first_gp$Year)),
+  high = 1:length(unique(DF$large_first_gp$Year))
+)
+i <- 1
+for (year in unique(DF$large_first_gp$Year)){
+  temp_table <- DF$large_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
+    bind_rows(DF$large_other_gp %>% filter(Year == year) %>% select(-Year))
+
+  col_total <- colSums(temp_table)
+  temp_table <- temp_table %>% 
+    select(names(col_total)[col_total > 0])
+  temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
+  tryCatch(mote_temp <- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
+                        r = nrow(temp_table), c = ncol(temp_table), 
+                        a = .05), 
+       warning = function(w) { 
+         mote_temp <<- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
+                        r = nrow(temp_table), c = ncol(temp_table), 
+                        a = .05)
+         mote_temp$vlow <<- 0
+  }
+  )
+  large_effect$year[i] <- year
+  large_effect$v[i] <- mote_temp$v
+  large_effect$low[i] <- mote_temp$vlow
+  large_effect$high[i] <- mote_temp$vhigh
+  large_effect$people[i] <- mote_temp$n
+  i <- i + 1
+}
+
+large_effect$high[is.na(large_effect$high)] <- 0
+large_effect <- 
+  large_effect %>% 
+  filter(v != Inf)
+
+large_dot <- ggplot(large_effect, aes(year,v)) + 
+  geom_point(aes(size = people)) + 
+  theme_classic() + 
+  geom_pointrange(aes(ymin = low, ymax = high)) + 
+  xlab("Year") + 
+  ylab("Effect Size") + 
+  scale_size_continuous(name = "Num Authors")
+
+DF_decade <- DF$large_first_gp %>% 
+  mutate(who = "First") %>% 
+  bind_rows(
+    DF$large_other_gp %>% 
+      mutate(who = "Other")
+  ) %>% 
+  mutate(Decade = ifelse(Year < 1990, "1980s", 
+                         ifelse(Year < 2000, "1990s", 
+                                ifelse(Year < 2010, "2000s", 
+                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
+  group_by(who, Decade) %>% 
+  summarize_all(sum) %>% 
+  pivot_longer(cols = `Western Europe`:`Central Asia`, 
+               #### check this later ####
+               names_to = "Country", 
+               values_to = "Count")
+
+# North America, Africa (combine), NWS Europe, Eastern Asia, Latin America, Rest of Europe, Rest of Asia, Everything Else
+
+DF_decade$Country_2 <- DF_decade$Country
+DF_decade$Country_2 <- gsub(".*Africa.*", "Africa", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Northern Europe|Southern Europe|Western Europe", "NWS Europe", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("South-Eastern Europe|Eastern Europe", "ESE Europe", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Central Asia|South-Eastern Asia|Southern Asia|Western Asia", "Asia", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Melanesia|Mirconesia|New zealand and Australia|Polynesia", "Other", DF_decade$Country_2)
+
+DF_decade_sm <- DF_decade %>% 
+  group_by(Country_2, Decade, who) %>% 
+  summarize(Count = sum(Count), .groups = "keep")
+
+large_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
+    geom_bar(position="fill", stat="identity", color = "black") + 
+  theme_classic() + 
+  facet_grid(~Decade) + 
+  xlab("Author Type") + 
+  ylab("Percent of Authors") + 
+  scale_fill_brewer(name = "Region", palette = "Spectral")
+```
+
+```{r final-graphs}
+small_author + #theme(legend.position = "none") + 
+medium_author + #theme(legend.position = "none") + 
+large_author + #theme(legend.position = "none") + 
+guide_area() + 
+plot_layout(
+  ncol = 2,
+  nrow = 2, 
+  guides = "collect")
+
+ggsave("figure/author_country.png", width = 10, height = 7, 
+       units = "in")
+
+small_dot + 
+  theme(legend.position = "none") + 
+  coord_cartesian(ylim = c(0,1)) +
+medium_dot + 
+  theme(legend.position = "none") + 
+  coord_cartesian(ylim = c(0,1)) +
+large_dot + 
+  theme(legend.position = "none") + 
+  coord_cartesian(ylim = c(0,1)) +
+guide_area() + 
+plot_layout(
+  ncol = 2,
+  nrow = 2, 
+  guides = "collect")
+
+ggsave("figure/effect_country.png", width = 10, height = 7, 
+       units = "in")
 ```
@@
 ```
+
 ::: {#refs custom-style="Bibliography"}

### 2023-03-16 manuscript_scopus.Rmd
adding all the parts

@@
 library(patchwork)
+library(flextable)
+library(wordcloud2)
+library(htmlwidgets)
+library(webshot)
+library(figpatch)
 ```
@@
               "medium_other_gp", "normal_pub_type", "pub_time_count", 
-              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp")
+              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
+              "snip")
 
@@
 Health Sciences, Social Sciences, and Life Sciences.
+We filtered the database to include articles, articles in press, business articles, conference papers, data papers, preprints, and surveys using Elsevier's classification system.
 
@@
 ***Publication Metrics***. For each author, we will calculate the total
-number of publications, the h-index, and the i-10 index. The h-index
-represents the highest *h* number of publications that have at least *h*
-citations, while the i-10 index represents the number of publications
-with at least 10 citations.
+number of publications, and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.
 
@@
     areas, presenting graphics of the number of publication across time
-
     total
 
-13581
-
-+----------------+-----+
-|publication_type|count|
-+----------------+-----+
-|              sh|   41|
-|              cp|  266|
-|              ar|12689|
-|              dp|    4|
-|              pp|  580|
-|              ip|    1|
-+----------------+-----+
-
-subject area 
-+-----------------+-----+
-|      SubjectArea|count|
-+-----------------+-----+
-|  Health Sciences|10685|
-|Physical Sciences| 6151|
-|Multidisciplinary| 1569|
-|  Social Sciences|  543|
-|    Life Sciences| 7686|
-+-----------------+-----+
-
-time
-
-pub_time_count
+```{r}
+total_num <- 13581
+health_num <- 10685
+physical_num <- 6151
+social_num <- 543
+life_num <- 7686
+```
+
+The total number of articles included in this analysis was `r total_num` including `r health_num` Health Sciences articles, `r physical_num` Physical Sciences articles, `r social_num` Social Sciences articles, and `r life_num` Life Sciences articles.
+Articles could be classified into multiple categories.
+
+```{r}
+ggplot(DF$pub_time_count %>% 
+         filter(SubjectArea != "Multidisciplinary"), aes(Year, count, color = SubjectArea)) + 
+  theme_classic() + 
+  geom_point() + 
+  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
+  ylab("Number of Articles Per Year") + 
+  xlab("Publication Year") + 
+  theme(legend.position = "bottom")
+```
 
@@
 
-Out[52]: 2534
-
-+-----------------+------------+
-|      SubjectArea|count(srcid)|
-+-----------------+------------+
-|  Health Sciences|        1472|
-|Physical Sciences|         641|
-|Multidisciplinary|          14|
-|  Social Sciences|         206|
-|    Life Sciences|        1024|
-+-----------------+------------+
-
--   Statistics (mean, median, standard deviation, minimum, maximum) of
-    the journal impact using Source Normalized Impact per Paper for the
-    four subject areas.
-
-+-----------------+------------------+------------------+---------+------------+---------+
-|      SubjectArea|         avg(snip)| stddev_samp(snip)|min(snip)|median(snip)|max(snip)|
-+-----------------+------------------+------------------+---------+------------+---------+
-|  Health Sciences|  4.39848449724717|7.1846479513521615|      0.0|       2.078|  173.932|
-|Physical Sciences|1.7298434289762685| 1.336672368345959|    0.155|       1.278|   30.405|
-|Multidisciplinary| 6.092944123314063|   4.3151334953509|    0.032|       3.341|   11.342|
-|  Social Sciences| 2.204784860557769|2.1441319264666743|    0.017|       1.605|   30.405|
-|    Life Sciences| 2.524247249015079| 2.044898988084329|    0.017|       1.742|   12.624|
-+-----------------+------------------+------------------+---------+------------+---------+
+```{r}
+journals <- 2534
+health_journal <- 1472
+physical_journal <- 641
+social_journal <- 206
+life_journal <- 1024
+```
+
+The number of distinct journals big team science articles were published in was `r journals` with `r health_journal` journals in Health Sciences, `r physical_journal` journals in Physical Sciences, `r social_journal` journals in Social Sciences, and `r life_journal` journals in Life Sciences.
+The descriptive statistics for the Source Normalized Impact per Paper is presented in Table X.
+
+```{r results = 'asis', include = TRUE}
+flextable(
+  DF$snip %>% 
+    mutate(M = apa_num(M), 
+           SD = apa_num(SD), 
+           Minimum = apa_num(Minimum), 
+           Median = apa_num(Median), 
+           Maximum = apa_num(Maximum))
+)
+```
 
@@
 
-pub_time_subject
+```{r}
+#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
+pub_total <- DF$pub_time_subject %>% 
+  group_by(SubjectArea, ASJC) %>% 
+  summarize(count = sum(count), .groups = "keep") %>% 
+  filter(SubjectArea != "Multidisciplinary")
+
+health_cloud <- wordcloud2(pub_total %>% 
+             filter(SubjectArea == "Health Sciences") %>% 
+             ungroup() %>% 
+             select(ASJC, count))
+
+saveWidget(health_cloud, "tmp.html", selfcontained = F)
+webshot("tmp.html", "figure/health_cloud.png", vwidth = 600, vheight = 600)
+
+physical_cloud <- wordcloud2(pub_total %>% 
+             filter(SubjectArea == "Physical Sciences") %>% 
+             ungroup() %>% 
+             select(ASJC, count))
+
+saveWidget(physical_cloud, "tmp.html", selfcontained = F)
+webshot("tmp.html", "figure/physical_cloud.png", vwidth = 600, vheight = 600)
+
+life_cloud <- wordcloud2(pub_total %>% 
+             filter(SubjectArea == "Life Sciences") %>% 
+             ungroup() %>% 
+             select(ASJC, count))
+
+saveWidget(life_cloud, "tmp.html", selfcontained = F)
+webshot("tmp.html", "figure/life_cloud.png", vwidth = 600, vheight = 600)
+
+social_cloud <- wordcloud2(pub_total %>% 
+             filter(SubjectArea == "Social Sciences") %>% 
+             ungroup() %>% 
+             select(ASJC, count))
+
+saveWidget(social_cloud, "tmp.html", selfcontained = F)
+webshot("tmp.html", "figure/social_cloud.png", vwidth = 600, vheight = 600)
+```
+
+```{r}
+h <- fig("figure/health_cloud.png")
+p <- fig("figure/physical_cloud.png") 
+l <- fig("figure/life_cloud.png") 
+s <- fig("figure/social_cloud.png")
+
+h + ggtitle("Health Sciences") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+p + ggtitle("Physical Sciences") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+l + ggtitle("Life Sciences") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+s + ggtitle("Social Sciences") + 
+  theme(plot.title = element_text(hjust = 0.5)) +
+  plot_layout(ncol = 2, 
+              nrow = 2)
+```
 
@@
 
-keywords
+```{r}
+health_cloud <- wordcloud2(DF$keywords %>% 
+             filter(SubjectArea == "Health Sciences") %>% 
+             ungroup() %>% 
+             select(keywords_nostop, count))
+
+saveWidget(health_cloud, "tmp.html", selfcontained = F)
+webshot("tmp.html", "figure/health_key.png", vwidth = 600, vheight = 600)
+
+physical_cloud <- wordcloud2(DF$keywords %>% 
+             filter(SubjectArea == "Physical Sciences") %>% 
+             ungroup() %>% 
+             select(keywords_nostop, count), 
+             minSize = 20)
+
+saveWidget(physical_cloud, "tmp.html", selfcontained = F)
+webshot("tmp.html", "figure/physical_key.png", vwidth = 600, vheight = 600)
+
+life_cloud <- wordcloud2(DF$keywords %>% 
+             filter(SubjectArea == "Life Sciences") %>% 
+             ungroup() %>% 
+             select(keywords_nostop, count))
+
+saveWidget(life_cloud, "tmp.html", selfcontained = F)
+webshot("tmp.html", "figure/life_key.png", vwidth = 600, vheight = 600)
+
+social_cloud <- wordcloud2(DF$keywords  %>% 
+             filter(SubjectArea == "Social Sciences") %>% 
+             ungroup() %>% 
+             select(keywords_nostop, count))
+
+saveWidget(social_cloud, "tmp.html", selfcontained = F)
+webshot("tmp.html", "figure/social_key.png", vwidth = 600, vheight = 600)
+```
+
+```{r}
+h <- fig("figure/health_key.png")
+p <- fig("figure/physical_key.png") 
+l <- fig("figure/life_key.png") 
+s <- fig("figure/social_key.png")
+
+h + ggtitle("Health Sciences") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+p + ggtitle("Physical Sciences") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+l + ggtitle("Life Sciences") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+s + ggtitle("Social Sciences") + 
+  theme(plot.title = element_text(hjust = 0.5)) +
+  plot_layout(ncol = 2, 
+              nrow = 2)
+```
 
@@
 
-+-----------+
-|count(auid)|
-+-----------+
-|     257536|
-+-----------+
+```{r}
+total_authors <- 257536
+avg_authors <- apa_num(49.904646)
+sd_authors <- apa_num(207.006114)
+min_authors <- 10
+med_authors <- 19
+max_authors <- 5155
+```
+
+The total number of unique authors across all publications was `r total_authors`.
 
@@
 
-	count(Authorseq)	avg(Authorseq)	stddev_samp(Authorseq)	min(Authorseq)	median(Authorseq)	max(Authorseq)
-0	13581	49.904646	207.006114	10	19.0	5155
+The mean number of authors per publication was *M* = `r avg_authors` (*SD* = `r sd_authors`, *Med* = `r med_authors`) with a range of `r min_authors` to `r max_authors`.
 
@@
 
-author_time
-
-We will use $\alpha$ \< .05 for all analyses that involve hypothesis
-testing. We make no directional predictions.
+```{r}
+avg_author_time <- 
+  DF$author_time %>% 
+  filter(SubjectArea != "Multidisciplinary") %>% 
+  filter(Number_Papers >= 3) %>% 
+  mutate(low = (Average_Num_Authors - as.numeric(SD_Num_Authors)), 
+         high = (Average_Num_Authors + as.numeric(SD_Num_Authors)))
+
+ggplot(avg_author_time, aes(Year, Average_Num_Authors)) + 
+  theme_classic() + 
+  geom_point(aes(size = Number_Papers)) + 
+  #geom_point() + 
+  #geom_pointrange(aes(ymin = low, ymax = high)) + 
+  facet_wrap(~SubjectArea) + 
+  ylab("Average Number of Authors") + 
+  xlab("Publication Year") + 
+  theme(legend.position = "none")
+```
+
+We will use the 95% confidence interval to make all claims of predictors or effects different zero.
+The confidence interval that does not include zero would be considered different from zero (to four decimal places).
+We make no directional predictions.
 
@@
 
-career_time
-
--   To analyze trends over time, we will calculate the average career
-    length for each publication (i.e., average the author career length
-    to create one score for each paper) and run a regression analysis
-    using career length to predict year of publication. A positive slope
-    for year of publication would indicate increasing years of first
-    publication (i.e., more younger scholars over time), while a
-    negative slope would indicate older years of first publication
-    (i.e., more older scholars over time).
--   In order to show variance between individuals, we calculate the
-    standard deviation of career length for each publication and run a
-    regression analysis using this variance representation to predict
-    publication year. A positive slope would indicate increasing
-    variance over time (i.e., more diversity in the career lengths of
-    scholars), while a negative slope would indicate less variance and
-    diversity in scholars over time.
--   These analyses will be completed separately for each of the four
-    large subject areas.
-
------- Physical Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.531373   0.030990  -17.146   0.000000
-##  -0.207000   0.059698   -3.467   0.000533
-## 2020.342936   0.367600 5496.040   0.000000
-## ---
-## Mean squared error:  30.862113 , RMSE:  5.555368
-## Multiple R-squared: 0.145118 ,             Total iterations: 0
-------------
-
------- Social Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.437422   0.093563   -4.675   0.000004
-##  -0.104549   0.146459   -0.714   0.475750
-## 2019.182625   0.764850 2639.973   0.000000
-## ---
-## Mean squared error:  30.685713 , RMSE:  5.539469
-## Multiple R-squared: 0.118772 ,             Total iterations: 0
-------------
-
------- Health Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.460876   0.019674  -23.425   0.000000
-##  -0.218675   0.037611   -5.814   0.000000
-## 2019.076458   0.231406 8725.260   0.000000
-## ---
-## Mean squared error:  30.039405 , RMSE:  5.480822
-## Multiple R-squared: 0.144584 ,             Total iterations: 0
-------------
-
------- Life Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.604957   0.026519  -22.812   0.000000
-##  -0.056843   0.046915   -1.212   0.225716
-## 2019.490201   0.276602 7301.067   0.000000
-## ---
-## Mean squared error:  27.654316 , RMSE:  5.258737
-## Multiple R-squared: 0.175747 ,             Total iterations: 0
-------------
+```{r}
+ggplot(DF$career_time %>% 
+         filter(SubjectArea != "Multidisciplinary"), 
+       aes(Year, avg_career, color = sd_career)) +
+  theme_classic() + 
+  geom_point() +
+  facet_wrap(~SubjectArea) + 
+  theme(legend.position = "non") + 
+  ylab("Average Career Length") +
+  xlab("Year of Publication")
+```
+
+-  To analyze trends over time, we will calculate the average career length for each publication (i.e., average the author career length to create one score for each paper) and run a regression analysis using career length to predict year of publication.
+In order to show variance between individuals, we calculate the standard deviation of career length for each publication and run a regression analysis using this variance representation to predict publication year.
+These two variables will be used together.
+- Negative slopes would indicate more young scholars in later years (i.e., lower average career length as time increases).
+Positive slopes would indicate older scholars in later years (i.e., higher average career length as time increases).
+- Negative slopes imply that variability decreases over the years, so the average career length is more homogeneous.
+Positive slopes imply that variability increases over the years, so the average career length is varied across individuals (lots of different types of scholars).
+-   These analyses will be completed separately for each of the four large subject areas.
+
+```{r}
+label <- c("Physical", "Social", "Health", "Life")
+avg_b_values <- c(-0.531373, -0.437422, -0.460876, -0.604957)
+avg_se_values <- c(0.030990, 0.058153, 0.009794, 0.026519)
+sd_b_values <- c(-0.207000, -0.104549, -0.218675, -0.056843)
+sd_se_values <- c(0.059698, 0.058153, 0.009794, 0.046915)
+r2_values <- c(0.145118, 0.118772, 0.144584, 0.175747)
+sample_size <- 13000
+
+r2_low <- 1:length(r2_values)
+r2_high <- 1:length(r2_values)
+for (i in 1:length(r2_values)){
+  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
+  r2_low[i] <- temp$Lower.Conf.Limit.R2
+  r2_high[i] <- temp$Upper.Conf.Limit.R2
+}
+
+graph_data <- data.frame(
+  "label" = label,
+  "estimate" = avg_b_values,
+  "type" = "M Coefficient",
+  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
+  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
+    bind_rows(
+    data.frame(
+    "label" = label,
+    "estimate" = sd_b_values,
+    "type" = "SD Coefficient",
+    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
+    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
+    ) %>% 
+  bind_rows(
+    data.frame(  
+      "label" = label, 
+      "estimate" = r2_values,
+      "type" = "Effect Size",
+      "low" = r2_low,
+      "high" = r2_high)
+  )
+
+ggplot(graph_data, aes(label, estimate)) + 
+  geom_point() +
+  geom_pointrange(aes(ymin = low, ymax = high)) +
+  theme_classic() + 
+  facet_wrap(~type) + 
+  geom_hline(yintercept = 0) + 
+  coord_flip() + 
+  xlab("Subject Area") + 
+  ylab("")
+```
 
@@
 
-+----------------------+
-|count(affiliation_ids)|
-+----------------------+
-|                 35114|
-+----------------------+
-
-inst time
+```{r}
+affs <- 35114
+```
+
+The total number of unique affiliation across all papers was `r affs`.
+
+```{r}
+ggplot(DF$inst_time %>% 
+         filter(SubjectArea != "Multidisciplinary") %>% 
+         mutate(Decade = ifelse(Year < 1990, "1980s", 
+                         ifelse(Year < 2000, "1990s", 
+                                ifelse(Year < 2010, "2000s", 
+                                       ifelse(Year < 2020, "2010s", "2020s"))))), 
+       aes(Decade, `count(affiliation_ids)`)) + 
+  #geom_point() + 
+  geom_violin() + 
+  theme_classic() + 
+  facet_wrap(~SubjectArea) + 
+  ylab("Number of Affiliations") + 
+  xlab("Decade")
+```
 
@@
 
-pub_type versus normal_pub_type
+```{r}
+pub_types <- bind_rows(
+  DF$pub_types %>% mutate(type = "Big Team"), 
+  DF$normal_pub_type %>% mutate(type = "Normal")
+)
+
+ggplot(pub_types, aes(type, count, fill = publication_type)) + 
+    geom_bar(position="fill", stat="identity", color = "black") + 
+  theme_classic() +  
+  xlab("Author Type") + 
+  ylab("Percent of Paper Types") + 
+  theme(legend.position = "none")
+
+# can probably figure out how to combine these feasibly to make it readable
+# ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.
+```
+
+# can probably figure out how to combine these feasibly to make it readable
+
+# ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.
 
@@
 
-    We will report descriptive statistics on the total number of publications and h-index for individuals overall.
-        Do this for each unique person and report averages
-        Do this for each publication and create an average for each publication
-    Next, we will use the same analyses described in the career length section to analyze trends over time.
+- We will report descriptive statistics on the total number of publications and h-index for individuals overall.
+  - Do this for each unique person and report averages
+  - Do this for each publication and create an average for each publication
+
+```{r}
+avg_pub_count_author	<- apa_num(4.451816)
+std_pub_count_author <- apa_num(6.901369)
+
+avg_pub_count_paper <- apa_num(7.581413)
+sd_pub_count_paper <- apa_num(5.797233)
+avg_SD_pub_count_paper <- apa_num(7.140015)
+SD_SD_pub_count_paper <- apa_num(5.10383)
+
+avg_HIndex <- apa_num(14.242142)
+std_HIndex <- apa_num(43.798203)
+med_HIndex <- apa_num(2.0)
+
+avg_of_avg_HIndex <- apa_num(28.136255)
+std_of_avg_HIndex <- apa_num(38.013819)
+avg_of_std_HIndex <- apa_num(36.430509)
+std_of_std_HIndex <- apa_num(46.474619)
+med_of_med_HIndex <- apa_num(5.0)
+```
+
+The average number of publications by authors on big team sciences papers is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`).
+The publication counts were averaged across authors for each publication, and then these average publication counts were averaged across publications *M* = `r avg_pub_count_paper` (*SD* = `r sd_pub_count_paper`).
+The average variability (i.e., the average standard deviation with authors of a manuscript) with publication counts of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ = `r SD_SD_pub_count_paper`).
+
+The same process was completed with *h*-index for each author and publication.
+The average *h*-index for authors overall was *M* = `r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`).
+The average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD* = `r std_of_avg_HIndex`), and the variability of *h*-index across manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ = `r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).
+
+- Next, we will use the same analyses described in the career length section to analyze trends over time.
 An increasing slope over time indicates that individuals who are publishing more are more represented in BTS over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
-    A positive slope for standard deviation indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
+- A positive slope for standard deviation indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
 While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.
-    We will separate these by each of the four subject areas.
-
-	avg_pub_count	std_pub_count
-0	4.451816	6.901369
-
-	avg(avg_pub_count AS mean_of_avg_pub_count)	stddev_samp(avg_pub_count AS std_of_avg_pub_count)	avg(std_pub_count AS mean_of_std_pub_count)	stddev_samp(std_pub_count AS std_of_std_pub_count)
-0	7.581413	5.797233	7.140015	5.10383
-
-	avg_HIndex	std_HIndex	med_HIndex
-0	14.242142	43.798203	2.0
-
-	avg_of_avg_HIndex	std_of_avg_HIndex	avg_of_std_HIndex	std_of_std_HIndex	med_of_med_HIndex
-0	28.136255	38.013819	36.430509	46.474619	5.0
-
------- Physical Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.004420   0.022715   -0.195   0.845717
-##  -0.105746   0.034058   -3.105   0.001922
-## 2015.347578   0.195556 10305.717   0.000000
-## ---
-## Mean squared error:  35.756076 , RMSE:  5.979638
-## Multiple R-squared: 0.009554 ,             Total iterations: 0
-------------
-
------- Social Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.335536   0.179536   -1.869   0.062389
-##   0.130796   0.186924    0.700   0.484517
-## 2016.658826   0.487148 4139.727   0.000000
-## ---
-## Mean squared error:  34.070868 , RMSE:  5.837026
-## Multiple R-squared: 0.021558 ,             Total iterations: 0
-------------
-
------- Health Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.235551   0.028158   -8.365   0.000000
-##  -0.006692   0.026612   -0.251   0.801476
-## 2014.979175   0.119976 16794.893   0.000000
-## ---
-## Mean squared error:  33.860172 , RMSE:  5.818949
-## Multiple R-squared: 0.035782 ,             Total iterations: 0
-------------
-
------- Life Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.430599   0.037807  -11.389   0.000000
-##   0.133215   0.034255    3.889   0.000102
-## 2016.008237   0.147870 13633.624   0.000000
-## ---
-## Mean squared error:  31.736306 , RMSE:  5.633499
-## Multiple R-squared: 0.054081 ,             Total iterations: 0
-------------
+- We will separate these by each of the four subject areas.
+
+```{r}
+label <- c("Physical", "Social", "Health", "Life")
+avg_b_values <- c(-0.004420, -0.335536, -0.235551, -0.430599)
+avg_se_values <- c(0.022715, 0.179536, 0.028158, 0.037807)
+sd_b_values <- c(-0.105746, 0.130796, -0.006692, 0.133215)
+sd_se_values <- c(0.034058, 0.186924, 0.026612, 0.034255)
+r2_values <- c(0.009554, 0.021558, 0.035782, 0.054081)
+sample_size <- 13000
+
+r2_low <- 1:length(r2_values)
+r2_high <- 1:length(r2_values)
+for (i in 1:length(r2_values)){
+  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
+  r2_low[i] <- temp$Lower.Conf.Limit.R2
+  r2_high[i] <- temp$Upper.Conf.Limit.R2
+}
+
+graph_data <- data.frame(
+  "label" = label,
+  "estimate" = avg_b_values,
+  "type" = "M Coefficient",
+  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
+  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
+    bind_rows(
+    data.frame(
+    "label" = label,
+    "estimate" = sd_b_values,
+    "type" = "SD Coefficient",
+    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
+    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
+    ) %>% 
+  bind_rows(
+    data.frame(  
+      "label" = label, 
+      "estimate" = r2_values,
+      "type" = "Effect Size",
+      "low" = r2_low,
+      "high" = r2_high)
+  )
+
+ggplot(graph_data, aes(label, estimate)) + 
+  geom_point() +
+  geom_pointrange(aes(ymin = low, ymax = high)) +
+  theme_classic() + 
+  facet_wrap(~type) + 
+  geom_hline(yintercept = 0) + 
+  coord_flip() + 
+  xlab("Subject Area") + 
+  ylab("")
+```
 
@@
 
-total number of unique GP for each publication 
-using year to predict GP 
-positive slope means that as year goes up number of GP goes up 
-negative slope means that as year goes up number of GP goes down 
-forest plot of the effects + confidence interval
-
------- Physical Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.061001   0.022958   -2.657   0.007923
-## 130.518393  46.247823    2.822   0.004802
-## ---
-## Mean squared error:  56.853041 , RMSE:  7.540096
-## Multiple R-squared: 0.002357 ,             Total iterations: 0
-------------
-
------- Social Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.077040   0.058153   -1.325   0.186023
-## 160.766462 117.214988    1.372   0.170993
-## ---
-## Mean squared error:  45.807761 , RMSE:  6.768143
-## Multiple R-squared: 0.004491 ,             Total iterations: 0
-------------
-
------- Health Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.017775   0.009794   -1.815   0.069578
-##  40.118948  19.718323    2.035   0.041926
-## ---
-## Mean squared error:  25.532574 , RMSE:  5.052977
-## Multiple R-squared: 0.000434 ,             Total iterations: 0
-------------
-
------- Life Sciences ------
-
-Note: the last rows are the information for Intercept
-## -------------------------------------------------
-##   Estimate   |   Std.Error | t Values  |  P-value
-##  -0.014946   0.010485   -1.425   0.154081
-##  34.499812  21.117788    1.634   0.102392
-## ---
-## Mean squared error:  17.279398 , RMSE:  4.156850
-## Multiple R-squared: 0.000434 ,             Total iterations: 0
-------------
-
 -   Last, we will examine the differences in representation for
@@
     differences in frequencies comparing first authors to all other
-    authors. Since this data is categorical, we will use Cramer's V to
+    authors. Since this data is categorical, we will use Cramer's *V* to
     represent the effect size. If the effect size includes zero in its
@@
     confidence interval that does include zero represents a difference
-    in diversity. We will report these values and discuss what regions
-    of the world are represented when effect sizes indicate a difference
-    from zero using standardized residuals.
-
-    ## fix the stupid CIs
-
-```{r small-effects}
+    in diversity.
+
+```{r small-effects, warning = FALSE}
 DF$small_first_gp <- DF$small_first_gp %>% 
@@
 
-```{r medium-effects}
+```{r medium-effects, warning = FALSE}
 DF$medium_first_gp <- DF$medium_first_gp %>% 
@@
 
-```{r large-effects}
+```{r large-effects, warning = FALSE}
 DF$large_first_gp <- DF$large_first_gp %>% 
@@
 
-```{r final-graphs}
+```{r author-gpe-figure, include = TRUE}
 small_author + #theme(legend.position = "none") + 
@@
        units = "in")
-
+```
+
+```{r effect-gpe-figure, include = TRUE}
 small_dot + 

### 2023-03-23 manuscript_scopus.Rmd
all the updates

@@
 library(figpatch)
+
+strip_labels <- expression(
+  "M Coefficient" = b[M],
+  "SD Coefficient" = b[SD],
+  "Effect Size" = R^2
+)
+
+label_expressions <- function(values) {
+  stopifnot(is.expression(values))
+  as_labeller(function(x) {
+    if (is.null(names(values))) {
+      x <- seq_along(x)
+      if (length(x)!=length(values)) warning(paste0("Number of labels(", 
+        length(values), ") does not match number of values (", length(x), ")"))
+    }
+    as.list(values[x])
+  }, default=identity)
+}
+
 ```
@@
               "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
-              "snip")
+              "snip", "ASJC_codes", "snip_all")
 
@@
 
-***Institution***. We will use the affiliation ids and country to gather
+***Institution and Geopolitical Region ***. We will use the affiliation ids and country to gather
 information about the places of education and/or employment for authors.
-Country will likely be binned into United Nation Sub-Region for
+Country will likely be binned into United Nation Region, Sub-Region,  or smaller clusters for
 analyses.
@@
 The descriptive statistics for the Source Normalized Impact per Paper is presented in Table X.
+For comparison, the SNIP descriptive statistics for all papers is shown in Table X.
+
+Big-Team Science SNIP
 
@@
 
+All Journal Articles SNIP
+
+```{r results = 'asis', include = TRUE}
+flextable(
+  DF$snip_all %>% 
+    mutate(M = apa_num(M), 
+           SD = apa_num(SD), 
+           Minimum = apa_num(Minimum), 
+           Median = apa_num(Median), 
+           Maximum = apa_num(Maximum))
+)
+```
+
 ### RQ2: Publication Information.
@@
   summarize(count = sum(count), .groups = "keep") %>% 
-  filter(SubjectArea != "Multidisciplinary")
+  filter(SubjectArea != "Multidisciplinary") %>% 
+  left_join(DF$ASJC_codes %>% select(Name, Code), by = c("ASJC" = "Code"))
 
@@
              ungroup() %>% 
-             select(ASJC, count))
+             select(Name, count) %>% 
+               arrange(desc(count)) %>% 
+               slice_head(n = 20),
+             minRotation = -pi/6, 
+             maxRotation = -pi/6,
+             rotateRatio = 0)
 
@@
              ungroup() %>% 
-             select(ASJC, count))
+             select(Name, count) %>% 
+               arrange(desc(count)) %>% 
+               slice_head(n = 20),
+             minRotation = -pi/6, 
+             maxRotation = -pi/6,
+             rotateRatio = 0, 
+             size = 1.5)
 
@@
              ungroup() %>% 
-             select(ASJC, count))
+             select(Name, count) %>% 
+               arrange(desc(count)) %>% 
+               slice_head(n = 20),
+             minRotation = -pi/6, 
+             maxRotation = -pi/6,
+             rotateRatio = 0, 
+             size = .2)
 
@@
   theme_classic() + 
-  facet_wrap(~type) + 
+  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
   geom_hline(yintercept = 0) + 
@@
 ```{r}
+DF$inst_time$normalized <- DF$inst_time$unique / DF$inst_time$total * 100
+
 ggplot(DF$inst_time %>% 
@@
                                        ifelse(Year < 2020, "2010s", "2020s"))))), 
-       aes(Decade, `count(affiliation_ids)`)) + 
+       aes(Decade, `normalized`)) + 
   #geom_point() + 
@@
   facet_wrap(~SubjectArea) + 
-  ylab("Number of Affiliations") + 
+  ylab("Percent of Unique Affiliations") + 
   xlab("Decade")
@@
   group_by(affiliation_tag_country) %>% 
-  summarize(count = sum(count))
+  summarize(count = sum(count),
+            count_all = sum(all_count))
 
@@
 
+DF$geo_country$count_binned <- factor(DF$geo_country$count_binned, 
+                                      levels = c("< 100", 
+                                                 "100-999", 
+                                                 "1,000-4,999", 
+                                                 "5,000-9,999", 
+                                                 "10,000+"))
+
 # map of binned data 
@@
   theme_void() + 
-  scale_fill_manual(name = "Sample Size",
-                    values = c( "black", "#323232", "#646464","#969696","#c8c8c8"))
+  # scale_fill_manual(name = "Sample Size",
+  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
+  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
 
@@
   #                            fontface = "italic") +
-  geom_treemap_text(colour = "white", place = "centre",
+  geom_treemap_text(colour = "black", place = "centre",
                     size = 15, grow = FALSE) +  
-  scale_fill_manual(name = "Sample Size",
-                    values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
+  # scale_fill_manual(name = "Sample Size",
+  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
+  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
   # scale_fill_gradient(name = "Sample Size",
@@
 ggsave("figure/treemap.png", tree)
+```
+
+```{r geo-map-all}
+# make a map on a continuous scale
+ggplot(DF$geo_country) +
+  geom_map(aes(map_id = affiliation_tag_country, fill = count_all), map = world_map) +
+  geom_polygon(data = world_map, 
+               aes(x = long, y = lat, group = group), 
+               colour = 'black', fill = NA) + 
+  theme_void() + 
+  scale_fill_distiller(name = "Sample Size",
+                       palette = "Greys",
+                       direction = 1,
+                       na.value = "white")
+
+ggsave("figure/continuous_country_all.png")
+
+# maybe try binning
+DF$geo_country$count_binned_all <- if_else(
+  DF$geo_country$count_all >= 10000, "10,000+", 
+  if_else(
+    DF$geo_country$count_all < 10000 & DF$geo_country$count_all >= 5000, "5,000-9,999",
+    if_else(
+      DF$geo_country$count_all < 5000 & DF$geo_country$count_all >= 1000, "1,000-4,999",
+      if_else(
+        DF$geo_country$count_all < 1000 & DF$geo_country$count_all >= 100, "100-999",
+        "< 100"
+      )
+    )
+  )
+)
+
+DF$geo_country$count_binned_all <- factor(DF$geo_country$count_binned_all, 
+                                   levels = unique(DF$geo_country$count_binned_all))
+
+DF$geo_country$count_binned_all <- factor(DF$geo_country$count_binned_all, 
+                                      levels = c("< 100", 
+                                                 "100-999", 
+                                                 "1,000-4,999", 
+                                                 "5,000-9,999", 
+                                                 "10,000+"))
+
+# map of binned data 
+bin_country_all <- ggplot(DF$geo_country) +
+  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned_all), map = world_map) +
+  geom_polygon(data = world_map, 
+               aes(x = long, y = lat, group = group), 
+               colour = 'black', fill = NA) + 
+  theme_void() + 
+  # scale_fill_manual(name = "Sample Size",
+  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
+  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
+
+bin_country_all
+
+ggsave("figure/binned_country_all.png", bin_country_all)
+
+tree_all <- ggplot(DF$geo_country, aes(area = count_all, fill = count_binned_all,
+               label = affiliation_tag_country, subgroup = un_region_sub)) +
+  geom_treemap() +
+  geom_treemap_subgroup_border(colour = "white", size = 5) +
+  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
+  #                            alpha = 0.25, colour = "black",
+  #                            fontface = "italic") +
+  geom_treemap_text(colour = "black", place = "centre",
+                    size = 15, grow = FALSE) +  
+  # scale_fill_manual(name = "Sample Size",
+  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
+  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
+  # scale_fill_gradient(name = "Sample Size",
+  #                     low = "#c8c8c8", 
+  #                     high = "#323232")
+
+tree_all
+
+ggsave("figure/treemap_all.png", tree_all)
 ```
@@
   xlab("Year") + 
-  ylab("Effect Size") + 
+  ylab(expression(R^2)) + 
   scale_size_continuous(name = "Num Authors")
@@
 ```{r author-gpe-figure, include = TRUE}
-small_author + #theme(legend.position = "none") + 
-medium_author + #theme(legend.position = "none") + 
-large_author + #theme(legend.position = "none") + 
+small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
+medium_author + ggtitle("50-99 Authors") + #theme(legend.position = "none") + 
+large_author + ggtitle("100 + Authors") + #theme(legend.position = "none") + 
 guide_area() + 
@@
   coord_cartesian(ylim = c(0,1)) +
+  ggtitle("10-49 Authors") + 
 medium_dot + 
@@
   coord_cartesian(ylim = c(0,1)) +
+  ggtitle("50-99 Authors") +
 large_dot + 
@@
   coord_cartesian(ylim = c(0,1)) +
+  ggtitle("100 + Authors") + 
 guide_area() + 

### 2023-03-23 manuscript_scopus.Rmd
updated pictures

@@
   xlab("Year") + 
-  ylab(expression(R^2)) + 
+  ylab(expression(phi)) + 
   scale_size_continuous(name = "Num Authors")
@@
   theme(legend.position = "none") + 
-  coord_cartesian(ylim = c(0,1)) +
+  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
   ggtitle("10-49 Authors") + 
@@
   theme(legend.position = "none") + 
-  coord_cartesian(ylim = c(0,1)) +
+  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
   ggtitle("50-99 Authors") +
@@
   theme(legend.position = "none") + 
-  coord_cartesian(ylim = c(0,1)) +
+  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
   ggtitle("100 + Authors") + 

### 2023-03-23 manuscript_scopus.Rmd
old
old things

--- 2023-03-16 manuscript_scopus.Rmd
@@
   ylab("Percent of Paper Types") + 
-  theme(legend.position = "none")
+  theme(legend.position = "right")
 
@@
 DF_decade <- DF$small_first_gp %>% 
-  mutate(who = "First") %>% 
+  mutate(who = "F") %>% 
   bind_rows(
     DF$small_other_gp %>% 
-      mutate(who = "Other")
+      mutate(who = "O")
   ) %>% 
@@
 DF_decade <- DF$medium_first_gp %>% 
-  mutate(who = "First") %>% 
+  mutate(who = "F") %>% 
   bind_rows(
     DF$medium_other_gp %>% 
-      mutate(who = "Other")
+      mutate(who = "O")
   ) %>% 
@@
 DF_decade <- DF$large_first_gp %>% 
-  mutate(who = "First") %>% 
+  mutate(who = "F") %>% 
   bind_rows(
     DF$large_other_gp %>% 
-      mutate(who = "Other")
+      mutate(who = "O")
   ) %>% 

### 2023-04-06 manuscript_scopus.Rmd
fixes

@@
     as.list(values[x])
-  }, default=identity)
+  }, default = identity)
 }
@@
   DF$snip %>% 
+    filter(`Subject Area` != "Multidisciplinary") %>% 
     mutate(M = apa_num(M), 
@@
   DF$snip_all %>% 
+    filter(`Subject Area` != "Multidisciplinary") %>% 
     mutate(M = apa_num(M), 
@@
     classifications.
+
+#### REDO THIS WITH QUANTEDA ####
 
@@
 
+##### FIX CAPTIONS #####
+
 ```{r}
@@
 
-ggplot(avg_author_time, aes(Year, Average_Num_Authors)) + 
+ggplot(avg_author_time, aes(Year, Med_Num_Authors)) + 
   theme_classic() + 
   geom_point(aes(size = Number_Papers)) + 
-  #geom_point() + 
+  geom_point(aes(Year, Average_Num_Authors, color = "red")) + 
   #geom_pointrange(aes(ymin = low, ymax = high)) + 
@@
   xlab("Publication Year") + 
-  theme(legend.position = "none")
+  theme(legend.position = "bottom")
 ```
@@
   theme_classic() + 
-  geom_point() +
+  geom_point(aes(size = num_papers)) +
   facet_wrap(~SubjectArea) + 
-  theme(legend.position = "non") + 
+  theme(legend.position = "bottom") + 
   ylab("Average Career Length") +
@@
 -   These analyses will be completed separately for each of the four large subject areas.
+
+#### MOVE R2 to the right #####
 
@@
   DF$normal_pub_type %>% mutate(type = "Normal")
-)
+) %>% 
+  filter(publication_type == "ar" | publication_type == "pp" | 
+           publication_type == "dp")
 
@@
 
+#### four panel plot with tree and country next to each other ####
+
 -   To understand the change in representation diversity, we will
@@
 
-end up with a list of effect sizes by year by small medium large 
-x axis is year
-y axis is the effect size and the confidence interval 
-if diversity is increasing then the patterns would be more similar (effect size of zero)
-if diversity is not increasing then the patterns would be different (effect size does not include zero)
-
-who is not represented in the "corresponding" spots - proportion chart by decades stacked bar chart of the decades
-
 \newpage

### 2023-04-20 manuscript_scopus.Rmd
finalizing pre-reg

@@
 affiliation:
-
   - id            : "1"
@@
 documentclass     : "apa7"
-output            : papaja::apa6_docx
+output            : papaja::apa6_pdf
 ---
@@
 ```{r setup, include = FALSE}
-#knitr::opts_knit(echo = TRUE)
+knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, error = FALSE)
 library(papaja)
@@
 library(patchwork)
-library(flextable)
-library(wordcloud2)
-library(htmlwidgets)
-library(webshot)
+library(ggplot2)
+library(ggwordcloud)
 library(figpatch)
@@
 our results based on the big four subject areas: Physical Sciences,
-Health Sciences, Social Sciences, and Life Sciences.
-We filtered the database to include articles, articles in press, business articles, conference papers, data papers, preprints, and surveys using Elsevier's classification system.
+Health Sciences, Social Sciences, and Life Sciences. We filtered the
+database to include articles, articles in press, business articles,
+conference papers, data papers, preprints, and surveys using Elsevier's
+classification system.
 
@@
 
-***Institution and Geopolitical Region ***. We will use the affiliation ids and country to gather
-information about the places of education and/or employment for authors.
-Country will likely be binned into United Nation Region, Sub-Region,  or smaller clusters for
-analyses.
-
-***Education***. We will also collect degree information from the author
-table.
+***Institution and Geopolitical Region*** . We will use the affiliation
+ids and country to gather information about the places of education
+and/or employment for authors. Country will likely be binned into United Nation Region, Sub-Region, or smaller clusters for analyses.
+
+***Education***. We will also collect degree information from the author table.
 
@@
 ***Publication Metrics***. For each author, we will calculate the total
-number of publications, and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.
+number of publications, and the h-index. The h-index represents the
+highest *h* number of publications that have at least *h* citations.
 
@@
 
-The total number of articles included in this analysis was `r total_num` including `r health_num` Health Sciences articles, `r physical_num` Physical Sciences articles, `r social_num` Social Sciences articles, and `r life_num` Life Sciences articles.
-Articles could be classified into multiple categories.
-
-```{r}
+*Number of articles*. The total number of articles included in this analysis was `r total_num` including `r health_num` Health Sciences articles, `r physical_num`
+Physical Sciences articles, `r social_num` Social Sciences articles, and
+`r life_num` Life Sciences articles. Articles could be classified into
+multiple categories. Figure X shows the number of articles published across time for each of the four large subject areas.
+
+```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years."}
 ggplot(DF$pub_time_count %>% 
@@
 
-The number of distinct journals big team science articles were published in was `r journals` with `r health_journal` journals in Health Sciences, `r physical_journal` journals in Physical Sciences, `r social_journal` journals in Social Sciences, and `r life_journal` journals in Life Sciences.
-The descriptive statistics for the Source Normalized Impact per Paper is presented in Table X.
-For comparison, the SNIP descriptive statistics for all papers is shown in Table X.
-
-Big-Team Science SNIP
-
-```{r results = 'asis', include = TRUE}
-flextable(
+*Number of journals*. The number of distinct journals big team science articles were published
+in was `r journals` with `r health_journal` journals in Health Sciences,
+`r physical_journal` journals in Physical Sciences, `r social_journal`
+journals in Social Sciences, and `r life_journal` journals in Life
+Sciences. The descriptive statistics for the Source Normalized Impact
+per Paper is presented in Table X. For comparison, the SNIP descriptive
+statistics for all papers is shown in Table X.
+
+```{r tab-snip, results = 'asis', include = TRUE}
+apa_table(
   DF$snip %>% 
@@
            Median = apa_num(Median), 
-           Maximum = apa_num(Maximum))
-)
-```
-
-All Journal Articles SNIP
+           Maximum = apa_num(Maximum)), 
+  caption = "Big-Team Science SNIP Values")
+```
 
 ```{r results = 'asis', include = TRUE}
-flextable(
+apa_table(
   DF$snip_all %>% 
@@
            Median = apa_num(Median), 
-           Maximum = apa_num(Maximum))
-)
+           Maximum = apa_num(Maximum)),
+  caption = "All Journal Articles SNIP Values")
 ```
@@
 -   The totals of the number of articles published within the smaller
-    subject area classifications. We will visualize these differences
-    over time to determine if there is increasing interest in a specific
-    subarea over time for each of the four larger subject area
-    classifications.
-
-#### REDO THIS WITH QUANTEDA ####
-
-```{r}
+    subject area classifications. We will visualize these differences to show the areas of interest for each of the four large subject areas.
+
+```{r eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
+### NOTE YOU WILL NEED TO RUN THIS ###
 #DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
@@
   group_by(SubjectArea, ASJC) %>% 
-  summarize(count = sum(count), .groups = "keep") %>% 
+  summarize(Count_Size = sum(count), .groups = "keep") %>% 
   filter(SubjectArea != "Multidisciplinary") %>% 
@@
 
-health_cloud <- wordcloud2(pub_total %>% 
+# health
+
+health_cloud <- pub_total %>% 
   filter(SubjectArea == "Health Sciences") %>% 
   ungroup() %>%
-             select(Name, count) %>% 
-               arrange(desc(count)) %>% 
-               slice_head(n = 20),
-             minRotation = -pi/6, 
-             maxRotation = -pi/6,
-             rotateRatio = 0)
-
-saveWidget(health_cloud, "tmp.html", selfcontained = F)
-webshot("tmp.html", "figure/health_cloud.png", vwidth = 600, vheight = 600)
-
-physical_cloud <- wordcloud2(pub_total %>% 
+  arrange(desc(Count_Size)) %>% 
+  ggplot() + 
+  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
+  theme_minimal() + 
+  scale_size_area(max_size = 15)
+
+ggsave("figure/health_cloud.png", dpi = 300, width = 8,
+       height = 4, units = "in")
+
+physical_cloud <- pub_total %>% 
   filter(SubjectArea == "Physical Sciences") %>% 
   ungroup() %>%
-             select(Name, count) %>% 
-               arrange(desc(count)) %>% 
-               slice_head(n = 20),
-             minRotation = -pi/6, 
-             maxRotation = -pi/6,
-             rotateRatio = 0, 
-             size = 1.5)
-
-saveWidget(physical_cloud, "tmp.html", selfcontained = F)
-webshot("tmp.html", "figure/physical_cloud.png", vwidth = 600, vheight = 600)
-
-life_cloud <- wordcloud2(pub_total %>% 
+  arrange(desc(Count_Size)) %>% 
+  ggplot() + 
+  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
+  theme_minimal() + 
+  scale_size_area(max_size = 15)
+
+ggsave("figure/physical_cloud.png", dpi = 300, width = 8,
+       height = 4, units = "in")
+
+life_cloud <- pub_total %>% 
   filter(SubjectArea == "Life Sciences") %>% 
   ungroup() %>%
-             select(Name, count) %>% 
-               arrange(desc(count)) %>% 
-               slice_head(n = 20),
-             minRotation = -pi/6, 
-             maxRotation = -pi/6,
-             rotateRatio = 0)
-
-saveWidget(life_cloud, "tmp.html", selfcontained = F)
-webshot("tmp.html", "figure/life_cloud.png", vwidth = 600, vheight = 600)
-
-social_cloud <- wordcloud2(pub_total %>% 
+  arrange(desc(Count_Size)) %>% 
+  ggplot() + 
+  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
+  theme_minimal() + 
+  scale_size_area(max_size = 15)
+
+ggsave("figure/life_cloud.png", dpi = 300, width = 8,
+       height = 4, units = "in")
+
+social_cloud <- pub_total %>% 
   filter(SubjectArea == "Social Sciences") %>% 
   ungroup() %>%
-             select(Name, count) %>% 
-               arrange(desc(count)) %>% 
-               slice_head(n = 20),
-             minRotation = -pi/6, 
-             maxRotation = -pi/6,
-             rotateRatio = 0, 
-             size = .2)
-
-saveWidget(social_cloud, "tmp.html", selfcontained = F)
-webshot("tmp.html", "figure/social_cloud.png", vwidth = 600, vheight = 600)
-```
-
-```{r}
-h <- fig("figure/health_cloud.png")
-p <- fig("figure/physical_cloud.png") 
-l <- fig("figure/life_cloud.png") 
-s <- fig("figure/social_cloud.png")
-
-h + ggtitle("Health Sciences") + 
+  arrange(desc(Count_Size)) %>% 
+  ggplot() + 
+  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
+  theme_minimal() + 
+  scale_size_area(max_size = 15)
+
+ggsave("figure/social_cloud.png", dpi = 300, width = 8,
+       height = 4, units = "in")
+```
+
+```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area"}
+
+health_cloud <- fig("figure/health_cloud.png")
+physical_cloud <- fig("figure/physical_cloud.png") 
+life_cloud <- fig("figure/life_cloud.png") 
+social_cloud <- fig("figure/social_cloud.png")
+
+health_cloud + ggtitle("Health Sciences") + 
   theme(plot.title = element_text(hjust = 0.5)) + 
-p + ggtitle("Physical Sciences") + 
+physical_cloud + ggtitle("Physical Sciences") + 
   theme(plot.title = element_text(hjust = 0.5)) + 
-l + ggtitle("Life Sciences") + 
+life_cloud + ggtitle("Life Sciences") + 
   theme(plot.title = element_text(hjust = 0.5)) + 
-s + ggtitle("Social Sciences") + 
+social_cloud + ggtitle("Social Sciences") + 
   theme(plot.title = element_text(hjust = 0.5)) +
@@
 
-```{r}
-health_cloud <- wordcloud2(DF$keywords %>% 
+```{r eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
+### NOTE YOU WILL NEED TO RERUN THIS ###
+health_cloud <- DF$keywords %>% 
    filter(SubjectArea == "Health Sciences") %>% 
    ungroup() %>% 
-             select(keywords_nostop, count))
-
-saveWidget(health_cloud, "tmp.html", selfcontained = F)
-webshot("tmp.html", "figure/health_key.png", vwidth = 600, vheight = 600)
-
-physical_cloud <- wordcloud2(DF$keywords %>% 
+   select(keywords_nostop, count) %>% 
+  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
+  ggplot() + 
+  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
+  theme_minimal() + 
+  scale_size_area(max_size = 15)
+
+ggsave("figure/health_key.png", dpi = 300, width = 8,
+       height = 4, units = "in")
+
+physical_cloud <- DF$keywords %>% 
    filter(SubjectArea == "Physical Sciences") %>% 
    ungroup() %>% 
-             select(keywords_nostop, count), 
-             minSize = 20)
-
-saveWidget(physical_cloud, "tmp.html", selfcontained = F)
-webshot("tmp.html", "figure/physical_key.png", vwidth = 600, vheight = 600)
-
-life_cloud <- wordcloud2(DF$keywords %>% 
+   select(keywords_nostop, count) %>% 
+  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
+  ggplot() + 
+  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
+  theme_minimal() + 
+  scale_size_area(max_size = 15)
+
+ggsave("figure/physical_key.png", dpi = 300, width = 8,
+       height = 4, units = "in")
+
+life_cloud <- DF$keywords %>% 
    filter(SubjectArea == "Life Sciences") %>% 
    ungroup() %>% 
-             select(keywords_nostop, count))
-
-saveWidget(life_cloud, "tmp.html", selfcontained = F)
-webshot("tmp.html", "figure/life_key.png", vwidth = 600, vheight = 600)
-
-social_cloud <- wordcloud2(DF$keywords  %>% 
+   select(keywords_nostop, count) %>% 
+  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
+  ggplot() + 
+  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
+  theme_minimal() + 
+  scale_size_area(max_size = 15)
+
+ggsave("figure/life_key.png", dpi = 300, width = 8,
+       height = 4, units = "in")
+
+social_cloud <- DF$keywords %>% 
    filter(SubjectArea == "Social Sciences") %>% 
    ungroup() %>% 
-             select(keywords_nostop, count))
-
-saveWidget(social_cloud, "tmp.html", selfcontained = F)
-webshot("tmp.html", "figure/social_key.png", vwidth = 600, vheight = 600)
-```
-
-```{r}
-h <- fig("figure/health_key.png")
-p <- fig("figure/physical_key.png") 
-l <- fig("figure/life_key.png") 
-s <- fig("figure/social_key.png")
-
-h + ggtitle("Health Sciences") + 
+   select(keywords_nostop, count) %>% 
+  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
+  ggplot() + 
+  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
+  theme_minimal() + 
+  scale_size_area(max_size = 15)
+
+ggsave("figure/social_key.png", dpi = 300, width = 8,
+       height = 4, units = "in")
+```
+
+```{r fig-keywords, include = TRUE, fig.cap="Keyword Analysis for Each of the Four Subject Areas."}
+health_key <- fig("figure/health_key.png")
+physical_key <- fig("figure/physical_key.png") 
+life_key <- fig("figure/life_key.png") 
+social_key <- fig("figure/social_key.png")
+
+health_key + ggtitle("Health Sciences") + 
   theme(plot.title = element_text(hjust = 0.5)) + 
-p + ggtitle("Physical Sciences") + 
+physical_key + ggtitle("Physical Sciences") + 
   theme(plot.title = element_text(hjust = 0.5)) + 
-l + ggtitle("Life Sciences") + 
+life_key + ggtitle("Life Sciences") + 
   theme(plot.title = element_text(hjust = 0.5)) + 
-s + ggtitle("Social Sciences") + 
+social_key + ggtitle("Social Sciences") + 
   theme(plot.title = element_text(hjust = 0.5)) +
@@
 
-The total number of unique authors across all publications was `r total_authors`.
+The total number of unique authors across all publications was
+`r total_authors`.
 
@@
 
-The mean number of authors per publication was *M* = `r avg_authors` (*SD* = `r sd_authors`, *Med* = `r med_authors`) with a range of `r min_authors` to `r max_authors`.
+The mean number of authors per publication was *M* = `r avg_authors`
+(*SD* = `r sd_authors`, *Med* = `r med_authors`) with a range of
+`r min_authors` to `r max_authors`.
 
@@
 
-##### FIX CAPTIONS #####
-
-```{r}
+```{r fig-author-year, include = TRUE, fig.cap="Number of authors included on big-team science papers per year by subject area.
+Colored dots indicate the mean number of authors, while the black dots represent the median number of authors.
+The size of the black dots indicate the number of papers in that year."}
 avg_author_time <- 
@@
   xlab("Publication Year") + 
-  theme(legend.position = "bottom")
-```
-
-We will use the 95% confidence interval to make all claims of predictors or effects different zero.
-The confidence interval that does not include zero would be considered different from zero (to four decimal places).
+  theme(legend.position = "bottom") + 
+  guides(color = "none") + 
+  scale_size_continuous(name = "Number Papers")
+```
+
+We will use the 95% confidence interval to make all claims of predictors
+or effects different zero. The confidence interval that does not include
+zero would be considered different from zero (to four decimal places).
 We make no directional predictions.
@@
 
-```{r}
+```{r fig-career, include = TRUE, fig.cap = "Average career length for big-team science authors.
+Larger dots indicate more papers for each estimation.
+Lighter colored dots mean less variability in author career length, while darker dots mean more variability in career length."}
 ggplot(DF$career_time %>% 
@@
   ylab("Average Career Length") +
-  xlab("Year of Publication")
-```
-
--  To analyze trends over time, we will calculate the average career length for each publication (i.e., average the author career length to create one score for each paper) and run a regression analysis using career length to predict year of publication.
-In order to show variance between individuals, we calculate the standard deviation of career length for each publication and run a regression analysis using this variance representation to predict publication year.
+  xlab("Year of Publication") + 
+  guides(color = "none") + 
+  scale_size_continuous(name = "Number Papers")
+```
+
+-   To analyze trends over time, we will calculate the average career
+    length for each publication (i.e., average the author career length
+    to create one score for each paper) and run a regression analysis
+    using career length to predict year of publication. In order to show
+    variance between individuals, we calculate the standard deviation of
+    career length for each publication and run a regression analysis
+    using this variance representation to predict publication year.
     These two variables will be used together.
-- Negative slopes would indicate more young scholars in later years (i.e., lower average career length as time increases).
-Positive slopes would indicate older scholars in later years (i.e., higher average career length as time increases).
-- Negative slopes imply that variability decreases over the years, so the average career length is more homogeneous.
-Positive slopes imply that variability increases over the years, so the average career length is varied across individuals (lots of different types of scholars).
--   These analyses will be completed separately for each of the four large subject areas.
-
-#### MOVE R2 to the right #####
-
-```{r}
+-   Negative slopes would indicate more young scholars in later years
+    (i.e., lower average career length as time increases). Positive
+    slopes would indicate older scholars in later years (i.e., higher
+    average career length as time increases).
+-   Negative slopes imply that variability decreases over the years, so
+    the average career length is more homogeneous. Positive slopes imply
+    that variability increases over the years, so the average career
+    length is varied across individuals (lots of different types of
+    scholars).
+-   These analyses will be completed separately for each of the four
+    large subject areas.
+
+```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}
 label <- c("Physical", "Social", "Health", "Life")
@@
 
+graph_data$type <- factor(
+  graph_data$type, 
+  levels = c("M Coefficient", "SD Coefficient", "Effect Size")
+)
+
 ggplot(graph_data, aes(label, estimate)) + 
@@
 
-```{r}
+```{r fig-inst, include = TRUE, fig.cap="Number of unique institutions involved in big-team science papers across decades."}
 DF$inst_time$normalized <- DF$inst_time$unique / DF$inst_time$total * 100
@@
 
-We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.
-
-    Figure out how messy this is for text processing requirements
-    For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are "normal" academics/researchers)
-    We will only perform this analysis if the proportion of information avaliable is over 50%.
-
-+-----------+------+
-|    degrees| count|
-+-----------+------+
-|       null|656440|
-|         MD|  8190|
-|        PhD|  3879|
-|    MD, PhD|  1267|
-|       M.D.|  1002|
-|        Dr.|   490|
-|        MSc|   461|
-|        MPH|   368|
-| Prof., PhD|   349|
-|      Ph.D.|   348|
-|         MS|   330|
-|     MD PhD|   285|
-|        MD.|   279|
-|   Prof. MD|   266|
-|  Prof. PhD|   239|
-|         BS|   232|
-|       Prof|   220|
-|         BA|   196|
-|M.D., Ph.D.|   191|
-|    MD, MPH|   158|
-+-----------+------+
+We will summarize the general education categories of individuals at the
+time of publication, along with a summary for change over time.
+
+- For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are "normal" academics/researchers)
+- We will only perform this analysis if the proportion of information avaliable is over 50%.
+
++--------+--------+
+| d      | count  |
+| egrees |        |
++--------+--------+
+| ``` CE | 656440 |
+| F7FA46 | 8190   |
+|        | 3879   |
+|   null | 1267   |
+|        | 1002   |
+|     MD | 490    |
+|        | 461    |
+|    PhD | 368    |
+| M      | 349    |
+| D, PhD | 348    |
+|        | 330    |
+|   M.D. | 285    |
+|        | 279    |
+|    Dr. | 266    |
+|        | 239    |
+|    MSc | 232    |
+|        | 220    |
+|    MPH | 196    |
+| ```    | 191    |
+|        | 158    |
+| Prof., |        |
+| PhD    |        |
+| Ph.D.  |        |
+| MS MD  |        |
+| PhD    |        |
+| MD.    |        |
+| Prof.  |        |
+| MD     |        |
+| Prof.  |        |
+| PhD BS |        |
+| Prof   |        |
+| BA     |        |
+| M.D.,  |        |
+| Ph.D.  |        |
+| MD,    |        |
+| MPH    |        |
++--------+--------+
 
@@
 
-```{r}
+```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
 pub_types <- bind_rows(
@@
   ylab("Percent of Paper Types") + 
-  theme(legend.position = "right")
+  theme(legend.position = "bottom") + 
+  scale_fill_discrete(name = "Publication Type", labels = c("Article", "Data Paper", "Pre-Print"))
 
@@
 
-# can probably figure out how to combine these feasibly to make it readable
-
-# ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.
-
 ***Publication Metrics***.
 
-- We will report descriptive statistics on the total number of publications and h-index for individuals overall.
+-   We will report descriptive statistics on the total number of
+    publications and h-index for individuals overall.
     -   Do this for each unique person and report averages
-  - Do this for each publication and create an average for each publication
+    -   Do this for each publication and create an average for each
+        publication
 
@@
 
-The average number of publications by authors on big team sciences papers is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`).
-The publication counts were averaged across authors for each publication, and then these average publication counts were averaged across publications *M* = `r avg_pub_count_paper` (*SD* = `r sd_pub_count_paper`).
-The average variability (i.e., the average standard deviation with authors of a manuscript) with publication counts of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ = `r SD_SD_pub_count_paper`).
-
-The same process was completed with *h*-index for each author and publication.
-The average *h*-index for authors overall was *M* = `r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`).
-The average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD* = `r std_of_avg_HIndex`), and the variability of *h*-index across manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ = `r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).
-
-- Next, we will use the same analyses described in the career length section to analyze trends over time.
-An increasing slope over time indicates that individuals who are publishing more are more represented in BTS over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
-- A positive slope for standard deviation indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
-While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.
+The average number of publications by authors on big team sciences
+papers is *M* = `r avg_pub_count_author` (*SD* =
+`r std_pub_count_author`). The publication counts were averaged across
+authors for each publication, and then these average publication counts
+were averaged across publications *M* = `r avg_pub_count_paper` (*SD* =
+`r sd_pub_count_paper`). The average variability (i.e., the average
+standard deviation with authors of a manuscript) with publication counts
+of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
+`r SD_SD_pub_count_paper`).
+
+The same process was completed with *h*-index for each author and
+publication. The average *h*-index for authors overall was *M* =
+`r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`). The
+average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD*
+= `r std_of_avg_HIndex`), and the variability of *h*-index across
+manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ =
+`r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).
+
+-   Next, we will use the same analyses described in the career length
+    section to analyze trends over time. An increasing slope over time
+    indicates that individuals who are publishing more are more
+    represented in BTS over time (i.e., increasing numbers of scholars
+    with higher publication rates), while a negative slope indicates
+    more researchers with less publications.
+-   A positive slope for standard deviation indicates increasing
+    variance over time (i.e., more diversity in the individual
+    publication rates), while a negative slope would indicate less
+    diversity in researchers over time. While publication rates do not
+    represent value as a researcher, they are often used in hiring and
+    promotion decisions, and we will use this variable as a proxy to
+    gauge the diversity in scholars represented in big teams.
 -   We will separate these by each of the four subject areas.
 
-```{r}
+```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}
 label <- c("Physical", "Social", "Health", "Life")
@@
 world_map <- subset(world_map, region != "ATA")
-
-# make a map on a continuous scale
-ggplot(DF$geo_country) +
-  geom_map(aes(map_id = affiliation_tag_country, fill = count), map = world_map) +
-  geom_polygon(data = world_map, 
-               aes(x = long, y = lat, group = group), 
-               colour = 'black', fill = NA) + 
-  theme_void() + 
-  scale_fill_distiller(name = "Sample Size",
-                       palette = "Greys",
-                       direction = 1,
-                       na.value = "white")
-
-ggsave("figure/continuous_country.png")
 
@@
   scale_fill_brewer(name = "Sample Size", palette = "Spectral")
-
-bin_country
-
-ggsave("figure/binned_country.png", bin_country)
 
@@
   #                     high = "#323232") 
-
-tree
-
-ggsave("figure/treemap.png", tree)
 ```
@@
 ```{r geo-map-all}
-# make a map on a continuous scale
-ggplot(DF$geo_country) +
-  geom_map(aes(map_id = affiliation_tag_country, fill = count_all), map = world_map) +
-  geom_polygon(data = world_map, 
-               aes(x = long, y = lat, group = group), 
-               colour = 'black', fill = NA) + 
-  theme_void() + 
-  scale_fill_distiller(name = "Sample Size",
-                       palette = "Greys",
-                       direction = 1,
-                       na.value = "white")
-
-ggsave("figure/continuous_country_all.png")
-
 # maybe try binning
@@
   scale_fill_brewer(name = "Sample Size", palette = "Spectral")
-
-bin_country_all
-
-ggsave("figure/binned_country_all.png", bin_country_all)
 
@@
   #                     high = "#323232") 
-
-tree_all
-
-ggsave("figure/treemap_all.png", tree_all)
-```
-
-#### four panel plot with tree and country next to each other ####
+```
+
+```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications."}
+bin_country + ggtitle("Big-Team Publication Map") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+  theme(legend.position = "none") + 
+tree + ggtitle("Big-Team Publication Mosiac Chart") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+  guides(fill = "none") + 
+bin_country_all + ggtitle("All Publications Map") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+  guides(fill = "none") + 
+tree_all + ggtitle("All Publications Mosiac Chart") + 
+  theme(plot.title = element_text(hjust = 0.5)) + 
+  guides(fill = "none") + 
+  plot_layout(ncol = 2, 
+              nrow = 2) + 
+  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
+
+# need to do the legend 
+```
 
@@
 
-```{r}
+```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions and variance in the number of regions represented in big-team science publiactions predicting time and the overall mode effect size."}
 label <- c("Physical", "Social", "Health", "Life")
@@
       "high" = r2_high)
+  )
+
+graph_data$type <- factor(
+  graph_data$type, 
+  levels = c("M Coefficient", "SD Coefficient", "Effect Size")
 )
@@
 
-```{r author-gpe-figure, include = TRUE}
+```{r author-gpe-figure, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades."}
 small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
@@
 
-```{r effect-gpe-figure, include = TRUE}
+```{r effect-gpe-figure, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year."}
 small_dot + 
@@
 ```
-
 ::: {#refs custom-style="Bibliography"}

### 2023-04-20 manuscript_scopus.tex
finalizing pre-reg

--- 2022-09-09 04.manuscript_scopus.tex
@@
 \usepackage{xcolor}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 \maketitle
-
-\hypertarget{significance}{%
-\section{Significance}\label{significance}}
 
@@
 credibility movement. Publications on BTS generally explore challenges,
-lessons learned, the need for BTS (Coles et al., 2022; Forscher et al., 2020).
+lessons learned, and the need for BTS (Coles et al., 2022; Forscher et al., 2020).
 
@@
 
-\hypertarget{approach}{%
-\section{Approach}\label{approach}}
+\hypertarget{research-questions}{%
+\section{Research Questions}\label{research-questions}}
 
@@
 peer-reviewed journals or had posted a full paper pre-print. We will use
-data from 1970 and forward in the publications (\texttt{ani)} database, as it
+data from 1970 and forward in the publications (\texttt{ani}) database, as it
 is noted online that this time period includes cited references for
@@
 our results based on the big four subject areas: Physical Sciences,
-Health Sciences, Social Sciences, and Life Sciences.
+Health Sciences, Social Sciences, and Life Sciences. We filtered the
+database to include articles, articles in press, business articles,
+conference papers, data papers, preprints, and surveys using Elsevier's
+classification system.
 
@@
 impact using the Source Normalized Impact per Paper from the journal
-(\texttt{sources)} database.
+(\texttt{sources}) database.
 
@@
 
-\textbf{\emph{Institution}}. We will use the affiliation ids and country to gather
-information about the places of education and/or employment for authors.
-Country will likely be binned into United Nation Sub-Region for
-analyses.
-
-\textbf{\emph{Education}}. We will also collect degree information from the author
-table.
+\textbf{\emph{Institution and Geopolitical Region}} . We will use the affiliation
+ids and country to gather information about the places of education
+and/or employment for authors. Country will likely be binned into United Nation Region, Sub-Region, or smaller clusters for analyses.
+
+\textbf{\emph{Education}}. We will also collect degree information from the author table.
 
@@
 \textbf{\emph{Publication Metrics}}. For each author, we will calculate the total
-number of publications, the h-index, and the i-10 index. The h-index
-represents the highest \emph{h} number of publications that have at least \emph{h}
-citations, while the i-10 index represents the number of publications
-with at least 10 citations.
+number of publications, and the h-index. The h-index represents the
+highest \emph{h} number of publications that have at least \emph{h} citations.
 
@@
   areas, presenting graphics of the number of publication across time
+  total
+\end{itemize}
+
+\emph{Number of articles}. The total number of articles included in this analysis was 13581 including 10685 Health Sciences articles, 6151
+Physical Sciences articles, 543 Social Sciences articles, and
+7686 Life Sciences articles. Articles could be classified into
+multiple categories. Figure X shows the number of articles published across time for each of the four large subject areas.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-time-1.pdf}
+\caption{\label{fig:fig-pub-time}Number of big-team science publications separated by four large subject areas across years.}
+\end{figure}
+
+\begin{itemize}
+\tightlist
 \item
   Number of distinct journals within each of the four subject areas
-\item
-  Statistics (mean, median, standard deviation, minimum, maximum) of
-  the journal impact using Source Normalized Impact per Paper for the
-  four subject areas.
-\end{itemize}
+\end{itemize}
+
+\emph{Number of journals}. The number of distinct journals big team science articles were published
+in was 2534 with 1472 journals in Health Sciences,
+641 journals in Physical Sciences, 206
+journals in Social Sciences, and 1024 journals in Life
+Sciences. The descriptive statistics for the Source Normalized Impact
+per Paper is presented in Table X. For comparison, the SNIP descriptive
+statistics for all papers is shown in Table X.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab-snip}Big-Team Science SNIP Values}
+
+\begin{tabular}{llllll}
+\toprule
+Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
+\midrule
+Health Sciences & 4.40 & 7.18 & 0.00 & 2.08 & 173.93\\
+Physical Sciences & 1.73 & 1.34 & 0.16 & 1.28 & 30.40\\
+Social Sciences & 2.20 & 2.14 & 0.02 & 1.60 & 30.40\\
+Life Sciences & 2.52 & 2.04 & 0.02 & 1.74 & 12.62\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-3}All Journal Articles SNIP Values}
+
+\begin{tabular}{llllll}
+\toprule
+Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
+\midrule
+Health Sciences & 2.13 & 4.21 & 0.00 & 1.44 & 173.93\\
+Physical Sciences & 1.48 & 1.10 & 0.00 & 1.26 & 30.40\\
+Social Sciences & 1.98 & 1.41 & 0.00 & 1.66 & 30.40\\
+Life Sciences & 1.53 & 1.23 & 0.00 & 1.24 & 19.07\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
   The totals of the number of articles published within the smaller
-  subject area classifications. We will visualize these differences
-  over time to determine if there is increasing interest in a specific
-  subarea over time for each of the four larger subject area
-  classifications.
+  subject area classifications. We will visualize these differences to show the areas of interest for each of the four large subject areas.
+\end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-clouds-1.pdf}
+\caption{\label{fig:fig-clouds}Journal Areas for Big-Team Science Publications by Subject Area}
+\end{figure}
+
+\begin{itemize}
+\tightlist
 \item
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-keywords-1.pdf}
+\caption{\label{fig:fig-keywords}Keyword Analysis for Each of the Four Subject Areas.}
+\end{figure}
+
 \hypertarget{rq3-authors.}{%
@@
   The total number of unique authors
+\end{itemize}
+
+The total number of unique authors across all publications was
+257536.
+
+\begin{itemize}
+\tightlist
 \item
@@
   the number of authors included on publications.
+\end{itemize}
+
+The mean number of authors per publication was \emph{M} = 49.90
+(\emph{SD} = 207.01, \emph{Med} = 19) with a range of
+10 to 5155.
+
+\begin{itemize}
+\tightlist
 \item
@@
 
-We will use \(\alpha\) \textless{} .05 for all analyses that involve hypothesis
-testing. We make no directional predictions.
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-author-year-1.pdf}
+\caption{\label{fig:fig-author-year}Number of authors included on big-team science papers per year by subject area.
+Colored dots indicate the mean number of authors, while the black dots represent the median number of authors.
+The size of the black dots indicate the number of papers in that year.}
+\end{figure}
+
+We will use the 95\% confidence interval to make all claims of predictors
+or effects different zero. The confidence interval that does not include
+zero would be considered different from zero (to four decimal places).
+We make no directional predictions.
 
@@
   researcher career length across publication years.
+\end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-career-1.pdf}
+\caption{\label{fig:fig-career}Average career length for big-team science authors.
+Larger dots indicate more papers for each estimation.
+Lighter colored dots mean less variability in author career length, while darker dots mean more variability in career length.}
+\end{figure}
+
+\begin{itemize}
+\tightlist
 \item
@@
   to create one score for each paper) and run a regression analysis
-  using career length to predict year of publication. A positive slope
-  for year of publication would indicate increasing years of first
-  publication (i.e., more younger scholars over time), while a
-  negative slope would indicate older years of first publication
-  (i.e., more older scholars over time).
-\item
-  In order to show variance between individuals, we calculate the
-  standard deviation of career length for each publication and run a
-  regression analysis using this variance representation to predict
-  publication year. A positive slope would indicate increasing
-  variance over time (i.e., more diversity in the career lengths of
-  scholars), while a negative slope would indicate less variance and
-  diversity in scholars over time.
+  using career length to predict year of publication. In order to show
+  variance between individuals, we calculate the standard deviation of
+  career length for each publication and run a regression analysis
+  using this variance representation to predict publication year.
+  These two variables will be used together.
+\item
+  Negative slopes would indicate more young scholars in later years
+  (i.e., lower average career length as time increases). Positive
+  slopes would indicate older scholars in later years (i.e., higher
+  average career length as time increases).
+\item
+  Negative slopes imply that variability decreases over the years, so
+  the average career length is more homogeneous. Positive slopes imply
+  that variability increases over the years, so the average career
+  length is varied across individuals (lots of different types of
+  scholars).
 \item
@@
 \end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-career-results-1.pdf}
+\caption{\label{fig:fig-career-results}Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication.}
+\end{figure}
 
@@
 
+The total number of unique affiliation across all papers was 35114.
+
+\begin{verbatim}
+## Warning: Groups with fewer than two data points have been dropped.
+## Groups with fewer than two data points have been dropped.
+## Groups with fewer than two data points have been dropped.
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-inst-1.pdf}
+\caption{\label{fig:fig-inst}Number of unique institutions involved in big-team science papers across decades.}
+\end{figure}
+
 \textbf{\emph{Education}}.
 
-\begin{itemize}
-\tightlist
-\item
-  We will summarize the general education categories of individuals at
-  the time of publication, along with a summary for change over time.
-\end{itemize}
+We will summarize the general education categories of individuals at the
+time of publication, along with a summary for change over time.
+
+\begin{itemize}
+\tightlist
+\item
+  For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are ``normal'' academics/researchers)
+\item
+  We will only perform this analysis if the proportion of information avaliable is over 50\%.
+\end{itemize}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1250}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1250}}@{}}
+\toprule()
+\endhead
+d
+egrees & count \\
+\begin{minipage}[t]{\linewidth}\raggedright
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{F7FA46}
+
+\NormalTok{  null}
+
+\NormalTok{    MD}
+
+\NormalTok{   PhD}
+\NormalTok{M}
+\NormalTok{D, PhD}
+
+\NormalTok{  M.D.}
+
+\NormalTok{   Dr.}
+
+\NormalTok{   MSc}
+
+\NormalTok{   MPH}
+\end{Highlighting}
+\end{Shaded}
+
+Prof.,
+PhD
+Ph.D.
+MS MD
+PhD
+MD.
+Prof.
+MD
+Prof.
+PhD BS
+Prof
+BA
+M.D.,
+Ph.D.
+MD,
+MPH
+\end{minipage} & 656440
+8190
+3879
+1267
+1002
+490
+461
+368
+349
+348
+330
+285
+279
+266
+239
+232
+220
+196
+191
+158 \\
+\bottomrule()
+\end{longtable}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-types-1.pdf}
+\caption{\label{fig:fig-pub-types}Types of publications for big-team science and all authors.}
+\end{figure}
+
 \textbf{\emph{Publication Metrics}}.
@@
   We will report descriptive statistics on the total number of
-  publications, i10 index, and h-index for individuals overall.
+  publications and h-index for individuals overall.
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Do this for each unique person and report averages
+  \item
+    Do this for each publication and create an average for each
+    publication
+  \end{itemize}
+\end{itemize}
+
+The average number of publications by authors on big team sciences
+papers is \emph{M} = 4.45 (\emph{SD} =
+6.90). The publication counts were averaged across
+authors for each publication, and then these average publication counts
+were averaged across publications \emph{M} = 7.58 (\emph{SD} =
+5.80). The average variability (i.e., the average
+standard deviation with authors of a manuscript) with publication counts
+of a paper was \(M_{SD}\) = 7.14 (\(SD_{SD}\) =
+5.10).
+
+The same process was completed with \emph{h}-index for each author and
+publication. The average \emph{h}-index for authors overall was \emph{M} =
+14.24 (\emph{SD} = 43.80, \emph{Med} = 2.00). The
+average \emph{h}-index for publications was \emph{M} = 28.14 (\emph{SD}
+= 38.01), and the variability of \emph{h}-index across
+manuscripts was \(M_{SD}\) = 36.43 (\(SD_{SD}\) =
+46.47, \(Med_{Med}\) = 5.00).
+
+\begin{itemize}
+\tightlist
 \item
@@
   gauge the diversity in scholars represented in big teams.
-\end{itemize}
+\item
+  We will separate these by each of the four subject areas.
+\end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-results-1.pdf}
+\caption{\label{fig:fig-pub-results}Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication.}
+\end{figure}
 
@@
   authors.
+\end{itemize}
+
+\begin{verbatim}
+## Warning in countrycode_convert(sourcevar = sourcevar, origin = origin, destination = dest, : Some values were not matched unambiguously: ANT, EUE, TWN
+
+## Warning in countrycode_convert(sourcevar = sourcevar, origin = origin, destination = dest, : Some values were not matched unambiguously: ANT, EUE, TWN
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-map-both-1.pdf}
+\caption{\label{fig:fig-map-both}Geopolitical regions represented in big-team science publications versus all publications.}
+\end{figure}
+
+\begin{itemize}
+\tightlist
 \item
@@
   diversity would be represented by a negative slope.
+\end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-diversity-1.pdf}
+\caption{\label{fig:fig-diversity}Number of geopolitical regions and variance in the number of regions represented in big-team science publiactions predicting time and the overall mode effect size.}
+\end{figure}
+
+\begin{itemize}
+\tightlist
 \item
@@
   differences in frequencies comparing first authors to all other
-  authors. Since this data is categorical, we will use Cramer's V to
+  authors. Since this data is categorical, we will use Cramer's \emph{V} to
   represent the effect size. If the effect size includes zero in its
@@
   confidence interval that does include zero represents a difference
-  in diversity. We will report these values and discuss what regions
-  of the world are represented when effect sizes indicate a different
-  from zero using standardized residuals.
-\end{itemize}
+  in diversity.
+\end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/author-gpe-figure-1.pdf}
+\caption{\label{fig:author-gpe-figure}A comparison of author affiliation geopolitical region across decades.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/effect-gpe-figure-1.pdf}
+\caption{\label{fig:effect-gpe-figure}Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.}
+\end{figure}
 

### 2023-04-20 manuscript_scopus.Rmd
small typo fixes

@@
 
+strip_labels_2 <- expression(
+  "Coefficient" = b,
+  "Effect Size" = R^2
+)
+
 label_expressions <- function(values) {
@@
 
-ggplot(DF$inst_time %>% 
+picture <- ggplot(DF$inst_time %>% 
          filter(SubjectArea != "Multidisciplinary") %>% 
@@
   xlab("Decade")
+
+suppressWarnings(print(picture))
 ```
@@
 # tree map
-DF$geo_country$un_region_sub <- countrycode(
+DF$geo_country$un_region_sub <- suppressWarnings(
+  countrycode(
   sourcevar = DF$geo_country$affiliation_tag_country,
   origin = 'iso3c', 
-  destination = 'un.regionsub.name'
-)
-
-DF$geo_country$un_region <- countrycode(
+  destination = 'un.regionsub.name')
+)
+
+DF$geo_country$un_region <- suppressWarnings(
+  countrycode(
   sourcevar = DF$geo_country$affiliation_tag_country,
   origin = 'iso3c', 
-  destination = 'un.region.name'
+  destination = 'un.region.name')
 )
@@
 
-```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions and variance in the number of regions represented in big-team science publiactions predicting time and the overall mode effect size."}
+```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}
 label <- c("Physical", "Social", "Health", "Life")
@@
 
-graph_data$type <- factor(
-  graph_data$type, 
-  levels = c("M Coefficient", "SD Coefficient", "Effect Size")
-)
+# graph_data$type <- factor(
+#   graph_data$type, 
+#   levels = c("Coefficient", "Effect Size")
+# )
 
@@
   theme_classic() + 
-  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
+  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels_2))) + 
   geom_hline(yintercept = 0) + 
@@
 
-```{r author-gpe-figure, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades."}
+```{r author-gpe-figure, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors."}
 small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +

### 2023-04-20 manuscript_scopus.tex
small typo fixes

@@
 
-\begin{verbatim}
-## Warning: Groups with fewer than two data points have been dropped.
-## Groups with fewer than two data points have been dropped.
-## Groups with fewer than two data points have been dropped.
-\end{verbatim}
-
 \begin{figure}
@@
 
-\begin{verbatim}
-## Warning in countrycode_convert(sourcevar = sourcevar, origin = origin, destination = dest, : Some values were not matched unambiguously: ANT, EUE, TWN
-
-## Warning in countrycode_convert(sourcevar = sourcevar, origin = origin, destination = dest, : Some values were not matched unambiguously: ANT, EUE, TWN
-\end{verbatim}
-
 \begin{figure}
@@
 \includegraphics{manuscript_scopus_files/figure-latex/fig-diversity-1.pdf}
-\caption{\label{fig:fig-diversity}Number of geopolitical regions and variance in the number of regions represented in big-team science publiactions predicting time and the overall mode effect size.}
+\caption{\label{fig:fig-diversity}Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size.}
 \end{figure}
@@
 \includegraphics{manuscript_scopus_files/figure-latex/author-gpe-figure-1.pdf}
-\caption{\label{fig:author-gpe-figure}A comparison of author affiliation geopolitical region across decades.}
+\caption{\label{fig:author-gpe-figure}A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors.}
 \end{figure}

### 2023-05-07 combine_outputs.Rmd
manuscript files

---
title: "Combine Files"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(rio)
library(dplyr)
```

## Combinations

```{r}
## geo political region 
# row	affiliation_tag_country	count	all_count
# 0	None	128448	1201063
# geo_country.xlsx

geo1 <- import("scopus_combine/geo_country_1.csv")
geo2 <- import("scopus_combine/geo_country_2.csv")

geo_together <- geo1 %>% 
  full_join(
    geo2, by = c("affiliation_tag_country" = "country")
  )
colnames(geo_together) <- c("affiliation_tag_country", "count", "all_count")

geo_together$count[is.na(geo_together$count)] <- 0

export(geo_together, "py_outputs/geo_country.xlsx", rownames = F)
```

### 2023-05-07 manuscript_scopus.Rmd
manuscript files

@@
 DF$geo_country$count_binned <- if_else(
-  DF$geo_country$count >= 10000, "10,000+", 
+  DF$geo_country$count >= 1000000, "1,000,000+", 
+  if_else(
+    DF$geo_country$count >= 500000 & DF$geo_country$count < 1000000, "500,000-999,999",
+    if_else(
+      DF$geo_country$count >= 100000 & DF$geo_country$count < 500000, "100,000-499,999",
+      if_else(
+        DF$geo_country$count >= 10000 & DF$geo_country$count < 100000, "10,000-99,999", 
         if_else(
@@
       )
+    )
+  )
+)
 
@@
                                                  "5,000-9,999", 
-                                                 "10,000+"))
+                                                 "10,000-99,999",
+                                                 "100,000-499,999",
+                                                 "500,000-999,999",
+                                                 "1,000,000+"))
 
@@
   scale_fill_brewer(name = "Sample Size", palette = "Spectral")
+
+# Warning: Some values were not matched unambiguously: ANT, ATA, BUR, BUX, BYS, CAI, CSK, CZH, DDR, EUE, HVO, PCI, ROM, SUN, SUX, TWN, UNO, YMD, YUG, ZAR
 
@@
 DF$geo_country$count_binned_all <- if_else(
-  DF$geo_country$count_all >= 10000, "10,000+", 
+  DF$geo_country$count_all >= 1000000, "1,000,000+", 
+  if_else(
+    DF$geo_country$count_all >= 500000 & DF$geo_country$count_all < 1000000, "500,000-999,999",
+    if_else(
+      DF$geo_country$count_all >= 100000 & DF$geo_country$count_all < 500000, "100,000-499,999",
+      if_else(
+        DF$geo_country$count_all >= 10000 & DF$geo_country$count_all < 100000, "10,000-99,999", 
         if_else(

### 2023-05-25 manuscript_scopus.Rmd
updating with a couple things

@@
 
-```{r}
-total_num <- 13581
-health_num <- 10685
-physical_num <- 6151
-social_num <- 543
-life_num <- 7686
+```{r total-articles}
+# updated 
+total_num <- 462970
+health_num <- 403697
+physical_num <- 207192
+social_num <- 23020
+life_num <- 275249
 ```
@@
 
-```{r}
-journals <- 2534
-health_journal <- 1472
-physical_journal <- 641
-social_journal <- 206
-life_journal <- 1024
+```{r total-journals}
+# updated
+journals <- 14263
+health_journal <- 6301
+physical_journal <- 5505
+social_journal <- 2314
+life_journal <- 4030
 ```
@@
 ```{r tab-snip, results = 'asis', include = TRUE}
+# updated
 apa_table(
@@
 ```{r results = 'asis', include = TRUE}
+# updated
 apa_table(
@@
 
-```{r eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
+```{r make-clouds, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
 ### NOTE YOU WILL NEED TO RUN THIS ###
@@
 
-```{r eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
+```{r make-clouds2, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
 ### NOTE YOU WILL NEED TO RERUN THIS ###
@@
 
-```{r}
-total_authors <- 257536
+```{r total-authors}
+total_authors <- 2786877 # only this updated
 avg_authors <- apa_num(49.904646)
@@
 ```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}
+# updated
 label <- c("Physical", "Social", "Health", "Life")
-avg_b_values <- c(-0.531373, -0.437422, -0.460876, -0.604957)
-avg_se_values <- c(0.030990, 0.058153, 0.009794, 0.026519)
-sd_b_values <- c(-0.207000, -0.104549, -0.218675, -0.056843)
-sd_se_values <- c(0.059698, 0.058153, 0.009794, 0.046915)
-r2_values <- c(0.145118, 0.118772, 0.144584, 0.175747)
-sample_size <- 13000
+avg_b_values <- c(-0.694505, -0.364097, -0.450156, -0.510173)
+avg_se_values <- c(0.002903, 0.006058, 0.001443, 0.001924)
+sd_b_values <- c(-0.284249, -0.134722, -0.136871, -0.052559)
+sd_se_values <- c(0.007381, 0.014757, 0.003646, 0.004821)
+r2_values <- c(0.461106, 0.253958, 0.299746, 0.346628)
+sample_size <- total_num
 
@@
 
-```{r}
-affs <- 35114
+```{r total-aff}
+# updated
+affs <- 434092
 ```
@@
 ```
-
-***Education***.
-
-We will summarize the general education categories of individuals at the
-time of publication, along with a summary for change over time.
-
-- For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are "normal" academics/researchers)
-- We will only perform this analysis if the proportion of information avaliable is over 50%.
-
-+--------+--------+
-| d      | count  |
-| egrees |        |
-+--------+--------+
-| ``` CE | 656440 |
-| F7FA46 | 8190   |
-|        | 3879   |
-|   null | 1267   |
-|        | 1002   |
-|     MD | 490    |
-|        | 461    |
-|    PhD | 368    |
-| M      | 349    |
-| D, PhD | 348    |
-|        | 330    |
-|   M.D. | 285    |
-|        | 279    |
-|    Dr. | 266    |
-|        | 239    |
-|    MSc | 232    |
-|        | 220    |
-|    MPH | 196    |
-| ```    | 191    |
-|        | 158    |
-| Prof., |        |
-| PhD    |        |
-| Ph.D.  |        |
-| MS MD  |        |
-| PhD    |        |
-| MD.    |        |
-| Prof.  |        |
-| MD     |        |
-| Prof.  |        |
-| PhD BS |        |
-| Prof   |        |
-| BA     |        |
-| M.D.,  |        |
-| Ph.D.  |        |
-| MD,    |        |
-| MPH    |        |
-+--------+--------+
 
@@
 ```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}
+# updated 
 label <- c("Physical", "Social", "Health", "Life")
-avg_b_values <- c(-0.004420, -0.335536, -0.235551, -0.430599)
-avg_se_values <- c(0.022715, 0.179536, 0.028158, 0.037807)
-sd_b_values <- c(-0.105746, 0.130796, -0.006692, 0.133215)
-sd_se_values <- c(0.034058, 0.186924, 0.026612, 0.034255)
-r2_values <- c(0.009554, 0.021558, 0.035782, 0.054081)
-sample_size <- 13000
+avg_b_values <- c(0.005832, -0.026835, -0.020444, -0.007609)
+avg_se_values <- c(0.000189, 0.001245, 0.000230, 0.000231)
+sd_b_values <- c(-0.023375, 0.015881, 0.008203, -0.003291)
+sd_se_values <- c(0.000255, 0.001118, 0.000220, 0.000265)
+r2_values <- c(0.137207, 0.033117, 0.046249, 0.030199)
+sample_size <- total_num
 
@@
 # serbia has changed codes
+# updated but needs work
 DF$geo_country$affiliation_tag_country <- toupper(DF$geo_country$affiliation_tag_country)
@@
 ```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}
+# updated 
 label <- c("Physical", "Social", "Health", "Life")
-b_values <- c(-0.061001, -0.077040, -0.017775, -0.014946)
-se_values <- c(0.022958, 0.058153, 0.009794, 0.010485)
-r2_values <- c(0.002357, 0.004491, 0.000434, 0.000434)
-sample_size <- 13000
+b_values <- c(0.015622, 0.034822, 0.019287, 0.011870)
+se_values <- c(0.002748, 0.006295, 0.001209, 0.001552)
+r2_values <- c(0.000315, 0.001822, 0.000926, 0.000371)
+sample_size <- total_num
 

### 2023-06-08 manuscript_scopus.Rmd
updating with new data

@@
     wrap: 72
+  chunk_output_type: inline
 bibliography: references.bib
-
 header-includes:
@@
       {\normalfont\normalsize\bfseries\typesectitle}}
-
-    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
@@
       {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-    \makeatother
-
 csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
@@
 # updated 
-total_num <- 462970
-health_num <- 403697
-physical_num <- 207192
-social_num <- 23020
-life_num <- 275249
+total_num <- 510334
+health_num <- 445301
+physical_num <- 228194
+social_num <- 26652
+life_num <- 307514
 ```
@@
 ggplot(DF$pub_time_count %>% 
-         filter(SubjectArea != "Multidisciplinary"), aes(Year, count, color = SubjectArea)) + 
+         filter(SubjectArea != "Multidisciplinary") %>% 
+         filter(Year < 2023), 
+       aes(Year, count, color = SubjectArea)) + 
   theme_classic() + 
@@
 # updated
-journals <- 14263
-health_journal <- 6301
-physical_journal <- 5505
-social_journal <- 2314
-life_journal <- 4030
+journals <- 14924
+health_journal <- 6559
+physical_journal <- 5787
+social_journal <- 2500
+life_journal <- 4187
 ```
@@
 # updated
+#### make this one table #### 
 apa_table(
@@
 
-```{r results = 'asis', include = TRUE}
+```{r tab-snip-all, results = 'asis', include = TRUE}
 # updated
@@
 # health
-
 health_cloud <- pub_total %>% 
@@
 
+# physical
 physical_cloud <- pub_total %>% 
@@
 
+# life
 life_cloud <- pub_total %>% 
@@
 
+# social
 social_cloud <- pub_total %>% 
@@
 ### NOTE YOU WILL NEED TO RERUN THIS ###
+# health
 health_cloud <- DF$keywords %>% 
@@
 
+# physical
 physical_cloud <- DF$keywords %>% 
@@
 
+# life
 life_cloud <- DF$keywords %>% 
@@
 
+# social 
 social_cloud <- DF$keywords %>% 
@@
 ```{r total-authors}
-total_authors <- 2786877 # only this updated
+total_authors <- 3047067 # only this updated
+#### DAMMIT FORGOT THIS ####
 avg_authors <- apa_num(49.904646)
@@
   filter(SubjectArea != "Multidisciplinary") %>% 
-  filter(Number_Papers >= 3) %>% 
+  # filter(Number_Papers >= 3) %>% 
   mutate(low = (Average_Num_Authors - as.numeric(SD_Num_Authors)), 
@@
 ```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}
-# updated
+
 label <- c("Physical", "Social", "Health", "Life")
-avg_b_values <- c(-0.694505, -0.364097, -0.450156, -0.510173)
-avg_se_values <- c(0.002903, 0.006058, 0.001443, 0.001924)
-sd_b_values <- c(-0.284249, -0.134722, -0.136871, -0.052559)
-sd_se_values <- c(0.007381, 0.014757, 0.003646, 0.004821)
-r2_values <- c(0.461106, 0.253958, 0.299746, 0.346628)
+avg_b_values <- c(-0.692014, -0.365357, -0.451827, -0.508350)
+avg_se_values <- c(0.002727, 0.005525, 0.001348, 0.001786)
+sd_b_values <- c(-0.265538, -0.097108, -0.096730, -0.013958)
+sd_se_values <- c(0.007018, 0.013409, 0.003451, 0.004523)
+r2_values <- c(0.465446, 0.254312, 0.303781, 0.350923)
 sample_size <- total_num
@@
 # updated
-affs <- 434092
+affs <- 463876
 ```
@@
 ```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
+#### try donut chart ####
 pub_types <- bind_rows(
   DF$pub_types %>% mutate(type = "Big Team"), 
-  DF$normal_pub_type %>% mutate(type = "Normal")
-) %>% 
-  filter(publication_type == "ar" | publication_type == "pp" | 
-           publication_type == "dp")
+  DF$normal_pub_type %>% mutate(type = "Normal")) %>% 
+    filter(!is.na(publication_type)) %>% 
+  filter(publication_type != "cb")
 
@@
   theme(legend.position = "bottom") + 
-  scale_fill_discrete(name = "Publication Type", labels = c("Article", "Data Paper", "Pre-Print"))
+  scale_fill_discrete(name = "Publication Type")
 
@@
 
-```{r}
-avg_pub_count_author	<- apa_num(4.451816)
-std_pub_count_author <- apa_num(6.901369)
-
-avg_pub_count_paper <- apa_num(7.581413)
-sd_pub_count_paper <- apa_num(5.797233)
-avg_SD_pub_count_paper <- apa_num(7.140015)
-SD_SD_pub_count_paper <- apa_num(5.10383)
-
-avg_HIndex <- apa_num(14.242142)
-std_HIndex <- apa_num(43.798203)
-med_HIndex <- apa_num(2.0)
-
-avg_of_avg_HIndex <- apa_num(28.136255)
-std_of_avg_HIndex <- apa_num(38.013819)
-avg_of_std_HIndex <- apa_num(36.430509)
-std_of_std_HIndex <- apa_num(46.474619)
-med_of_med_HIndex <- apa_num(5.0)
+```{r pub-hindex}
+avg_pub_count_author	<- apa_num(38.368910766896065)
+std_pub_count_author <- apa_num(102.53740454680472)
+
+avg_pub_count_paper <- apa_num(162.50184385336053)
+sd_pub_count_paper <- apa_num(155.1665533053519)
+avg_SD_pub_count_paper <- apa_num(164.27249797983876)
+SD_SD_pub_count_paper <- apa_num(127.20989934008757)
+
+avg_HIndex <- apa_num(33.64589690529209)
+std_HIndex <- apa_num(127.33565834550778)
+med_HIndex <- apa_num(8.0)
+
+avg_of_avg_HIndex <- apa_num(198.87318851400775)
+std_of_avg_HIndex <- apa_num(248.7847084313958)
+avg_of_std_HIndex <- apa_num(211.7985924228093)
+std_of_std_HIndex <- apa_num(238.53141146314053)
+med_of_med_HIndex <- apa_num(68.0)
 ```
@@
 ```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}
-# updated 
+
 label <- c("Physical", "Social", "Health", "Life")
-avg_b_values <- c(0.005832, -0.026835, -0.020444, -0.007609)
-avg_se_values <- c(0.000189, 0.001245, 0.000230, 0.000231)
-sd_b_values <- c(-0.023375, 0.015881, 0.008203, -0.003291)
-sd_se_values <- c(0.000255, 0.001118, 0.000220, 0.000265)
-r2_values <- c(0.137207, 0.033117, 0.046249, 0.030199)
+avg_b_values <- c(0.004248, -0.027315, -0.021713, -0.009466)
+avg_se_values <- c(0.000179, 0.001073, 0.000211, 0.000213)
+sd_b_values <- c(-0.021552, 0.016810, 0.010139, -0.000378)
+sd_se_values <- c(0.000241, 0.000921, 0.000198, 0.000235)
+r2_values <- c(0.135965, 0.035968, 0.048999, 0.030748)
 sample_size <- total_num
@@
 
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "ANT"] <- "Western Europe"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "BUR"] <- "Western Africa"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
+
+#### stopped here ####
+
+# BUX-
+# BYS -Byelorussian SSR – From June 1992
+# CAI-
+# CSK-Czechoslovakia – From June 1993
+# CZH-
+# DDR -East Germany from 1974 to 1990
+# EUE  -European Union laissez-passer[6
+# HVO -Upper Volta
+# PCI -Pacific Islands (Trust Territory)
+# ROM- Romania – From February 2002; Code changed to ROU[
+# SUN  -USSR From June 2008; Transitionally reserved from September 1992; Officially assigned before being deleted
+# SUX-
+# TWN- Taiwan still
+# UNO-
+# YMD -Yemen, Democratic
+# YUG -Yugoslavia – From July 2003
+# ZAR -Zaire – From July 1997
+
 DF$geo_country <- DF$geo_country %>% 
@@
 ```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}
-# updated 
+
 label <- c("Physical", "Social", "Health", "Life")
-b_values <- c(0.015622, 0.034822, 0.019287, 0.011870)
-se_values <- c(0.002748, 0.006295, 0.001209, 0.001552)
-r2_values <- c(0.000315, 0.001822, 0.000926, 0.000371)
+b_values <- c(0.002175, 0.033175, 0.016824, 0.008029)
+se_values <- c(0.002578, 0.006039, 0.001150, 0.001476)
+r2_values <- c(0.000006, 0.001542, 0.000708, 0.000170)
 sample_size <- total_num

### 2023-06-08 manuscript_scopus.tex
updating with new data

@@
 \usepackage{xcolor}
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 
-\emph{Number of articles}. The total number of articles included in this analysis was 13581 including 10685 Health Sciences articles, 6151
-Physical Sciences articles, 543 Social Sciences articles, and
-7686 Life Sciences articles. Articles could be classified into
+\emph{Number of articles}. The total number of articles included in this analysis was 510334 including 445301 Health Sciences articles, 228194
+Physical Sciences articles, 26652 Social Sciences articles, and
+307514 Life Sciences articles. Articles could be classified into
 multiple categories. Figure X shows the number of articles published across time for each of the four large subject areas.
@@
 \emph{Number of journals}. The number of distinct journals big team science articles were published
-in was 2534 with 1472 journals in Health Sciences,
-641 journals in Physical Sciences, 206
-journals in Social Sciences, and 1024 journals in Life
+in was 14924 with 6559 journals in Health Sciences,
+5787 journals in Physical Sciences, 2500
+journals in Social Sciences, and 4187 journals in Life
 Sciences. The descriptive statistics for the Source Normalized Impact
@@
 \midrule
-Health Sciences & 4.40 & 7.18 & 0.00 & 2.08 & 173.93\\
-Physical Sciences & 1.73 & 1.34 & 0.16 & 1.28 & 30.40\\
-Social Sciences & 2.20 & 2.14 & 0.02 & 1.60 & 30.40\\
-Life Sciences & 2.52 & 2.04 & 0.02 & 1.74 & 12.62\\
+Health Sciences & 2.36 & 3.59 & 0.00 & 1.58 & 173.93\\
+Physical Sciences & 1.57 & 1.17 & 0.00 & 1.27 & 30.40\\
+Social Sciences & 1.94 & 1.72 & 0.00 & 1.52 & 30.40\\
+Life Sciences & 2.02 & 1.60 & 0.00 & 1.51 & 19.07\\
 \bottomrule
@@
 
-\caption{\label{tab:unnamed-chunk-3}All Journal Articles SNIP Values}
+\caption{\label{tab:tab-snip-all}All Journal Articles SNIP Values}
 
@@
 \midrule
-Health Sciences & 2.13 & 4.21 & 0.00 & 1.44 & 173.93\\
-Physical Sciences & 1.48 & 1.10 & 0.00 & 1.26 & 30.40\\
-Social Sciences & 1.98 & 1.41 & 0.00 & 1.66 & 30.40\\
-Life Sciences & 1.53 & 1.23 & 0.00 & 1.24 & 19.07\\
+Health Sciences & 1.45 & 2.87 & 0.00 & 1.15 & 173.93\\
+Physical Sciences & 1.08 & 0.77 & 0.00 & 0.97 & 30.40\\
+Social Sciences & 1.32 & 1.03 & 0.00 & 1.15 & 30.40\\
+Life Sciences & 1.19 & 0.86 & 0.00 & 1.06 & 19.07\\
 \bottomrule
@@
 The total number of unique authors across all publications was
-257536.
+3047067.
 
@@
 
-The total number of unique affiliation across all papers was 35114.
+The total number of unique affiliation across all papers was 463876.
 
@@
 
-\textbf{\emph{Education}}.
-
-We will summarize the general education categories of individuals at the
-time of publication, along with a summary for change over time.
-
-\begin{itemize}
-\tightlist
-\item
-  For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are ``normal'' academics/researchers)
-\item
-  We will only perform this analysis if the proportion of information avaliable is over 50\%.
-\end{itemize}
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1250}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1250}}@{}}
-\toprule()
-\endhead
-d
-egrees & count \\
-\begin{minipage}[t]{\linewidth}\raggedright
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{F7FA46}
-
-\NormalTok{  null}
-
-\NormalTok{    MD}
-
-\NormalTok{   PhD}
-\NormalTok{M}
-\NormalTok{D, PhD}
-
-\NormalTok{  M.D.}
-
-\NormalTok{   Dr.}
-
-\NormalTok{   MSc}
-
-\NormalTok{   MPH}
-\end{Highlighting}
-\end{Shaded}
-
-Prof.,
-PhD
-Ph.D.
-MS MD
-PhD
-MD.
-Prof.
-MD
-Prof.
-PhD BS
-Prof
-BA
-M.D.,
-Ph.D.
-MD,
-MPH
-\end{minipage} & 656440
-8190
-3879
-1267
-1002
-490
-461
-368
-349
-348
-330
-285
-279
-266
-239
-232
-220
-196
-191
-158 \\
-\bottomrule()
-\end{longtable}
-
 \textbf{\emph{Types of Publications}}.
@@
 The average number of publications by authors on big team sciences
-papers is \emph{M} = 4.45 (\emph{SD} =
-6.90). The publication counts were averaged across
+papers is \emph{M} = 38.37 (\emph{SD} =
+102.54). The publication counts were averaged across
 authors for each publication, and then these average publication counts
-were averaged across publications \emph{M} = 7.58 (\emph{SD} =
-5.80). The average variability (i.e., the average
+were averaged across publications \emph{M} = 162.50 (\emph{SD} =
+155.17). The average variability (i.e., the average
 standard deviation with authors of a manuscript) with publication counts
-of a paper was \(M_{SD}\) = 7.14 (\(SD_{SD}\) =
-5.10).
+of a paper was \(M_{SD}\) = 164.27 (\(SD_{SD}\) =
+127.21).
 
@@
 publication. The average \emph{h}-index for authors overall was \emph{M} =
-14.24 (\emph{SD} = 43.80, \emph{Med} = 2.00). The
-average \emph{h}-index for publications was \emph{M} = 28.14 (\emph{SD}
-= 38.01), and the variability of \emph{h}-index across
-manuscripts was \(M_{SD}\) = 36.43 (\(SD_{SD}\) =
-46.47, \(Med_{Med}\) = 5.00).
+33.65 (\emph{SD} = 127.34, \emph{Med} = 8.00). The
+average \emph{h}-index for publications was \emph{M} = 198.87 (\emph{SD}
+= 248.78), and the variability of \emph{h}-index across
+manuscripts was \(M_{SD}\) = 211.80 (\(SD_{SD}\) =
+238.53, \(Med_{Med}\) = 68.00).
 

### 2023-06-15 manuscript_scopus.Rmd
updated authors

@@
 ```{r total-authors}
-total_authors <- 3047067 # only this updated
+total_authors <- 510334 # only this updated
 #### DAMMIT FORGOT THIS ####
-avg_authors <- apa_num(49.904646)
-sd_authors <- apa_num(207.006114)
+avg_authors <- apa_num(49.30516877182394)
+sd_authors <- apa_num(212.9786134634032)
 min_authors <- 10
-med_authors <- 19
-max_authors <- 5155
+med_authors <- 18
+max_authors <- 5568
 ```

### 2023-07-06 manuscript_scopus.Rmd
updates

@@
 DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
-
 DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "ANT"] <- "Western Europe"
 DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "BUR"] <- "Western Africa"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
-
-#### stopped here ####
-
-# BUX-
-# BYS -Byelorussian SSR – From June 1992
-# CAI-
-# CSK-Czechoslovakia – From June 1993
-# CZH-
-# DDR -East Germany from 1974 to 1990
-# EUE  -European Union laissez-passer[6
-# HVO -Upper Volta
-# PCI -Pacific Islands (Trust Territory)
-# ROM- Romania – From February 2002; Code changed to ROU[
-# SUN  -USSR From June 2008; Transitionally reserved from September 1992; Officially assigned before being deleted
-# SUX-
-# TWN- Taiwan still
-# UNO-
-# YMD -Yemen, Democratic
-# YUG -Yugoslavia – From July 2003
-# ZAR -Zaire – From July 1997
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "BYS"] <- "Eastern Europe"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "CSK"] <- "Eastern Europe"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "DOR"] <- "Eastern Europe"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "HVO"] <- "Sub-Saharan Africa"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "PCI"] <- "Eastern Asia"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "ROM"] <- "Eastern Europe"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "SUN"] <- "Eastern Europe"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "YMD"] <- "Western Asia"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "YUG"] <- "Eastern Europe"
+DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "ZAR"] <- "Sub-Saharan Africa"
 
@@
        units = "in")
+
+# fix the legend
 ```

### 2023-07-06 manuscript_scopus.tex
updates

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
   {\normalfont\normalsize\bfseries\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
   {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
@@
   {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
 
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 generalizability and more robust sample size in a study
-(Auspurg \& Brüderl, 2021; LeBel et al., 2018; Nosek \& Lakens, 2014b).
+(Auspurg \& Brüderl, 2021; LeBel et al., 2018; Nosek \& Lakens, 2014a).
 
@@
 Science Collaboration (Open Science Collaboration, 2015), Many Labs
-Collaborations (Buttrick et al., 2020; Ebersole et al., 2020, 2016; Klein et al., 2022; for example, Klein et al., 2018; Mathur et al., 2020; Skorb et al., 2020) or the first papers
+Collaborations (Buttrick et al., 2020; Ebersole et al., 2016, 2020; for example, Klein et al., 2018; Klein et al., 2022; Mathur et al., 2020; Skorb et al., 2020) or the first papers
 from the Psychological Science Accelerator (Bago et al., 2022; Dorison et al., 2022; Jones et al., 2021; Legate et al., 2022; Moshontz et al., 2018; Wang et al., 2021). Generally, the
@@
 for Registered Reports, papers accepted before the data has been
-collected (Nosek \& Lakens, 2014a; S. Stewart et al., 2020), and entire sub-sections of
+collected (Nosek \& Lakens, 2014b; S. Stewart et al., 2020), and entire sub-sections of
 journals devoted to only replication studies (e.g., \emph{Nature, Royal
@@
 The total number of unique authors across all publications was
-3047067.
+510334.
 
@@
 
-The mean number of authors per publication was \emph{M} = 49.90
-(\emph{SD} = 207.01, \emph{Med} = 19) with a range of
-10 to 5155.
+The mean number of authors per publication was \emph{M} = 49.31
+(\emph{SD} = 212.98, \emph{Med} = 18) with a range of
+10 to 5568.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
+Nosek, B. A., \& Lakens, D. (2014a). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137141.
+
 \leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
@@
 A., \& Lakens, D.
-(2014a).
+(2014b).
 Registered Reports: A Method to Increase the Credibility of Published Results.
@@
 \url{https://doi.org/10.1027/1864-9335/a000192}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
-Nosek, B. A., \& Lakens, D. (2014b). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137141.
 

### 2023-08-09 appendix.Rmd
moving things around

--- 2023-07-06 manuscript_scopus.Rmd
@@
 ---
-title             : "Who does big team science?"
-shorttitle        : "Big Team Science"
-author: 
-  - name          : "Erin M. Buchanan"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "326 Market St., Harrisburg, PA 17101"
-    email         : "ebuchanan@harrisburgu.edu"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Data curation
-      - Formal Analysis
-      - Methodology
-      - Project administration
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing
-  - name          : "Savannah C. Lewis"
-    affiliation   : "2"
-    role:
-      - Conceptualization
-      - Data curation
-      - Methodology
-      - Project administration
-      - Writing – original draft
-      - Writing – review & editing
-affiliation:
-  - id            : "1"
-    institution   : "Harrisburg University of Science and Technology"
-  - id            : "2"
-    institution   : "University of Alabama"
-authornote: |
-  Erin M. Buchanan is a Professor of Cognitive Analytics at Harrisburg University of Science and Technology. Savannah C. Lewis is a graduate student at the University of Alabama.
-
-  Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript. 
-abstract: |
-  This paper will examine the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions.
-As interest in BTS increases, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
-The types of publication outlets, number of publications, and subject areas of publication will be presented to summarize the publications in BTS.
-Information about authors included in BTS will be presented including career length, numbers of publications/impact variables, education, and affiliation.
-Last, we will explore the representation of geopolitical regions by examining affiliation location to explore the impact of BTS on the de-WEIRD movement to diversify researcher representation.
-
-keywords          : "big team, science, authorship, credit"
-wordcount         : "X"
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-classoption       : "man"
-editor_options: 
-  markdown: 
-    wrap: 72
-  chunk_output_type: inline
-bibliography: references.bib
-header-includes:
-  - |
-    \makeatletter
-    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-1em}%
-      {\normalfont\normalsize\bfseries\typesectitle}}
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-\z@\relax}%
-      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
-documentclass     : "apa7"
-output            : papaja::apa6_docx
+appendix: "appendix.Rmd"
 ---
 
-```{r setup, include = FALSE}
+# Supplemental Materials
+
+## RQ1: Publisher Information.
+
+```{r setup-appendix}
 knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, error = FALSE)
@@
 library(figpatch)
-
-strip_labels <- expression(
-  "M Coefficient" = b[M],
-  "SD Coefficient" = b[SD],
-  "Effect Size" = R^2
-)
-
-strip_labels_2 <- expression(
-  "Coefficient" = b,
-  "Effect Size" = R^2
-)
-
-label_expressions <- function(values) {
-  stopifnot(is.expression(values))
-  as_labeller(function(x) {
-    if (is.null(names(values))) {
-      x <- seq_along(x)
-      if (length(x)!=length(values)) warning(paste0("Number of labels(", 
-        length(values), ") does not match number of values (", length(x), ")"))
-    }
-    as.list(values[x])
-  }, default = identity)
-}
-
+library(RColorBrewer)
+library(latex2exp)
+library(ggridges)
 ```
 
-```{r data, include = FALSE}
-# things to import
-var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
-              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
-              "medium_other_gp", "normal_pub_type", "pub_time_count", 
-              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
-              "snip", "ASJC_codes", "snip_all")
+**Number of Journals**.
 
-var_list_import <- paste0("py_outputs/", var_list, ".xlsx")
-
-DF <- lapply(var_list_import, import)
-names(DF) <- var_list
-```
-
-According to the Oxford English dictionary, collaboration is two or more
-people working together to achieve a certain goal [@oed2016].
-Collaboration in scientific endeavors involves multiple researchers at
-(potentially) multiple institutions to communicate and work together to
-advance knowledge in their chosen field. Collaboration can manifest
-uniquely in each project dependent on the skill sets, hypotheses, and
-perspectives of collaborators. While collaboration is not new in
-science, the current interest of "big team science" is increasing
-[@forscher2020; @stewart2017; @coles2022]. Big team science projects
-and/or organizations utilize and run on large-scale collaboration to
-ensure that diverse populations and ideas are brought into research
-projects, which in turn allows for more reliability and generalizability
-in the results and method of the study. For this study, Big Team Science
-(BTS) will be defined as a collaboration of ten or more authors from at
-least ten different institutions.
-
-BTS appears to be increasing as a result of two sources: 1) increasing
-globalization and technology that allows for real-time interdisciplinary
-research, and 2) increasing interest in reproducibility, replication,
-and generalizability [@maxwell2015; @nelson2018; @zwaan2018].
-Technological advances have provided easier ways to collaborate with
-people who are from other universities and countries through document
-sharing platforms (e.g., Google, GitHub, and the Open Science
-Framework), video chatting platforms (e.g., Zoom, Microsoft Teams), and
-messaging and project management platforms (e.g., Slack, Trello,
-when2meet, etc.). The credibility movement seems to suggest that by
-having both collaborations that span across the globe and subfield of
-psychology, age groups, and education levels should help to drive
-psychological science in the path of better materials, reliability,
-generalizability and more robust sample size in a study
-[@auspurg2021has; @nosek2014method; @lebel2018].
-
-The credibility movement was originally defined by a focus on large
-scale replications using in collaborative environments [@vazire2022].
-Generally, the movement has been driven by early career researchers
-(i.e., those who are within five years of their first appointment)
-[@maizey2019]; however, there are no large meta-scientific
-investigations on this specific topic to date. Potentially, the lack of
-investigation is tied to the newness of the large-scale research in many
-fields, as it is only in recent years that publications like the Open
-Science Collaboration [@opensciencecollaboration2015], Many Labs
-Collaborations [for example, @klein2018; @ebersole2020; @ebersole2016;
-@klein2022; @mathur2020; @buttrick2020; @skorb2020] or the first papers
-from the Psychological Science Accelerator [@moshontz2018; @jones2021;
-@dorison2022; @wang2021; @legate2022; @bago2022]. Generally, the
-researcher incentive for replication was low: journals often prioritize
-"novel" or new results which led to rejection of replication manuscripts
-and publication bias [@hubbard1997; @franco2014; @nosek2012], the
-"failure" to replicate was often placed on the replication team as "bad
-science" rather than a careful consideration of publication biases and
-(potential) questionable research practices [@ioannidis2015;
-@maxwell2015; @klein2022], and why should someone want to spend time and
-resources on an answer we already "know" [@isager2021; @isager2021a]?
-
-However, the success and interest in the large-scale reproducibility
-projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired
-with the meta-scientific publications focusing on researcher practices
-and incentive structures [@silberzahn2018many; @john2012] led to a
-change in journal guidelines and incentives for researchers interested
-in participating in large-scale replication studies [@grahe2014;
-@kidwell2016; @nosek2015; @mayo-wilson2021]. For example, the support
-for Registered Reports, papers accepted before the data has been
-collected [@nosek2014; @stewart2020], and entire sub-sections of
-journals devoted to only replication studies (e.g., *Nature, Royal
-Society Open Science, Advances in Methods and Practices in Psychological
-Science*) has allowed researchers to invest in projects that they know
-should be published when the project is complete. Further, the
-implementation of the Transparency and Openness Guidelines [@nosek2015]
-and the Contributor Role Taxonomy (CRediT) system [@allen2019] have
-pushed journals and researchers to promote more open, inclusive
-publication practices.
-
-The credibility movement has been mirrored by the calls for
-diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
-Rich, and Democratic) scientific research [@henrich2010; @newson2021;
-@rad2018] by improving representation in research samples. Like the
-large-scale studies in Physics [@aphilos2021; @castelnovo2018] and
-Biology [@collins2003], the social sciences struggle to represent the
-breadth of humanity across both researcher and population
-characteristics. Now, grassroots organizations, such as the
-Psychological Science Accelerator [@moshontz2018], ManyBabies
-(<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and
-DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these
-issues by recruiting research labs from all over the globe to provide
-diversity in geographic, linguistic, and researcher representation.
-Publications have examined the global understanding of morality, face
-processing, COVID-19 information signaling, and more [@dorison2022;
-@wang2021; @legate2022; @bago2022; @jones2021; @vanbavel2022]. While
-these organizations and one-time groups for BTS studies have provided an
-incredible wealth of data for the scientific community, we do not yet
-know exactly *who* is involved with, and benefits from, the BTS and
-credibility movement. Publications on BTS generally explore challenges,
-lessons learned, and the need for BTS [@forscher2020; @coles2022].
-
-Therefore, the goal of this manuscript is to examine the *people*
-involved in BTS projects. We specifically expect to examine ICSR's
-Research Themes of inclusivity, research careers, and research
-globalization. As we examine these themes, it will bring new knowledge
-of how BTS projects impact each theme and field of study. We see an
-increase in interest and publications in BTS but we do not yet know if
-this uptick in large-scale projects has diversified the *people*
-involved in BTS. While a few publications have noted that BTS appears to
-be early career researchers [@maizey2019], no one has systematically
-investigated this perception. Further, it is unclear if the focus of
-de-WEIRDing science has only focused on the representation of the
-research participants or if it has also improved the representation of
-researchers outside of North America and Europe. Last, who runs these
-BTS projects? Do we see an increase in diversity for the authors who
-generally receive the most credit for these projects (i.e., first
-several author(s) and last author)? As hiring and promoting practices
-often place a heavy weight on publications and especially "influential"
-publications, it becomes necessary to critically examine the
-representation present in authorship in BTS projects.
-
-# Potential Outlets
-
-We will aim for high impact broad scope journals such as *Science*,
-*Nature* or *Nature Human Behaviour*. Other journals would include
-review publications within psychology to compare the social sciences to
-other sciences: *Perspectives in Psychological Science*, *Psychological
-Bulletin*, *Psychological Review*, or *Current Directions in
-Psychological Science*.
-
-# Research Questions
-
--   Research Question 1: What publication sources publish big team
-    science papers?
--   Research Question 2: What are the types of articles that are being
-    published in big team science?
--   Research Question 3: Who is involved in big team science?
-
-For each of these research questions, we will examine the overall
-results of all big team research projects, and examine for change in
-result trends across years of publication. Below we detail our methods
-and the ICSR/Scopus data to answer these questions, along with examples
-of the statistical results we expect to report in the manuscript. We
-began this project with data using Google Scholar and ORCID information.
-These sources were severely limited in their scope and breadth, as they
-are often curated with automatic processes or self-entered data, and we
-believe that access to Scopus and ICSR would allow us to accurately
-portray the BTS movement and its impact on diversity across many fields.
-The novelty of this project is that it would focus on all of published
-works, rather than a specific subfield (like Psychology) and give a lens
-into global representation in science that would otherwise not be
-achieved with open-source databases.
-
-# Method
-
-## Publications
-
-We have defined **BTS publications** as publications with at least 10
-authors at 10 different institutions that were published in
-peer-reviewed journals or had posted a full paper pre-print. We will use
-data from 1970 and forward in the publications (`ani`) database, as it
-is noted online that this time period includes cited references for
-calculation of several of our variables described below. We will analyze
-our results based on the big four subject areas: Physical Sciences,
-Health Sciences, Social Sciences, and Life Sciences. We filtered the
-database to include articles, articles in press, business articles,
-conference papers, data papers, preprints, and surveys using Elsevier's
-classification system.
-
-## Data Curation
-
-### RQ1: Publisher Information.
-
-Using these criteria, we will extract the following information for
-publication sources: the name of the publication (source title), subject
-area (both the large four subject areas and the smaller four digit all
-science journal classification ASJC codes). We will examine journal
-impact using the Source Normalized Impact per Paper from the journal
-(`sources`) database.
-
-### RQ2: Publication Information.
-
-For each publication of the identified BTS publications, we will analyze
-the full four digit ASJC subject areas codes for each of the larger four
-subject areas and the keywords present for these publications.
-
-### RQ3: Author Information.
-
-The author list will then be extracted from each publication. Next, we
-will use the author (`au`) and affiliation (`af`) array to curate a list
-of all publications and author information included in BTS papers. We
-will use these two arrays with the publication array to calculate the
-variables described below.
-
-***Career Length***. Career length for each author will be defined as
-the year of the first publication listed for each author.
-
-***Institution and Geopolitical Region*** . We will use the affiliation
-ids and country to gather information about the places of education
-and/or employment for authors. Country will likely be binned into United Nation Region, Sub-Region, or smaller clusters for analyses.
-
-***Education***. We will also collect degree information from the author table.
-
-***Types of Publications***. We will gather information from the
-publication type variable for each author publication to present
-information about the types of papers BTS authors publish.
-
-***Publication Metrics***. For each author, we will calculate the total
-number of publications, and the h-index. The h-index represents the
-highest *h* number of publications that have at least *h* citations.
-
-## Data analysis
-
-### RQ1: Publisher Information.
-
-To present results on this research question, we will analyze:
-
--   Number of articles for inclusion: total, separated by four subject
-    areas, presenting graphics of the number of publication across time
-    total
-
-```{r total-articles}
-# updated 
-total_num <- 510334
-health_num <- 445301
-physical_num <- 228194
-social_num <- 26652
-life_num <- 307514
-```
-
-*Number of articles*. The total number of articles included in this analysis was `r total_num` including `r health_num` Health Sciences articles, `r physical_num`
-Physical Sciences articles, `r social_num` Social Sciences articles, and
-`r life_num` Life Sciences articles. Articles could be classified into
-multiple categories. Figure X shows the number of articles published across time for each of the four large subject areas.
-
-```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years."}
-ggplot(DF$pub_time_count %>% 
-         filter(SubjectArea != "Multidisciplinary") %>% 
-         filter(Year < 2023), 
-       aes(Year, count, color = SubjectArea)) + 
-  theme_classic() + 
-  geom_point() + 
-  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
-  ylab("Number of Articles Per Year") + 
-  xlab("Publication Year") + 
-  theme(legend.position = "bottom")
-```
-
--   Number of distinct journals within each of the four subject areas
-
-```{r total-journals}
-# updated
-journals <- 14924
-health_journal <- 6559
-physical_journal <- 5787
-social_journal <- 2500
-life_journal <- 4187
-```
-
-*Number of journals*. The number of distinct journals big team science articles were published
-in was `r journals` with `r health_journal` journals in Health Sciences,
-`r physical_journal` journals in Physical Sciences, `r social_journal`
-journals in Social Sciences, and `r life_journal` journals in Life
-Sciences. The descriptive statistics for the Source Normalized Impact
-per Paper is presented in Table X. For comparison, the SNIP descriptive
-statistics for all papers is shown in Table X.
+Table \@ref(tab:tab-snip) indicates the SNIP values for BTS publications, while Table \@ref(tab:tab-snip-all).
+The results from these tables indicate that impact values are slightly higher for BTS publications, while the overall median, minimum, and maximum are the same for each grouping.
 
@@
 # updated
-#### make this one table #### 
 apa_table(
@@
 
-### RQ2: Publication Information.
+## RQ2: Publication Information.
 
-For each publication, we will examine:
-
--   The totals of the number of articles published within the smaller
-    subject area classifications. We will visualize these differences to show the areas of interest for each of the four large subject areas.
-
-```{r make-clouds, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
-### NOTE YOU WILL NEED TO RUN THIS ###
-#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
-pub_total <- DF$pub_time_subject %>% 
-  group_by(SubjectArea, ASJC) %>% 
-  summarize(Count_Size = sum(count), .groups = "keep") %>% 
-  filter(SubjectArea != "Multidisciplinary") %>% 
-  left_join(DF$ASJC_codes %>% select(Name, Code), by = c("ASJC" = "Code"))
-
-# health
-health_cloud <- pub_total %>% 
-  filter(SubjectArea == "Health Sciences") %>% 
-  ungroup() %>%
-  arrange(desc(Count_Size)) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/health_cloud.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# physical
-physical_cloud <- pub_total %>% 
-  filter(SubjectArea == "Physical Sciences") %>% 
-  ungroup() %>%
-  arrange(desc(Count_Size)) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/physical_cloud.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# life
-life_cloud <- pub_total %>% 
-  filter(SubjectArea == "Life Sciences") %>% 
-  ungroup() %>%
-  arrange(desc(Count_Size)) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/life_cloud.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# social
-social_cloud <- pub_total %>% 
-  filter(SubjectArea == "Social Sciences") %>% 
-  ungroup() %>%
-  arrange(desc(Count_Size)) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/social_cloud.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-```
-
-```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area"}
-
-health_cloud <- fig("figure/health_cloud.png")
-physical_cloud <- fig("figure/physical_cloud.png") 
-life_cloud <- fig("figure/life_cloud.png") 
-social_cloud <- fig("figure/social_cloud.png")
-
-health_cloud + ggtitle("Health Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-physical_cloud + ggtitle("Physical Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-life_cloud + ggtitle("Life Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-social_cloud + ggtitle("Social Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) +
-  plot_layout(ncol = 2, 
-              nrow = 2)
-```
-
--   The keywords present in the publications data overall to identify
-    trends and common themes in the publications for the four subject
-    areas using visualizations (wordclouds) to depict the common
-    keywords.
+**Keywords**.
+Figure \@ref(fig:fig-keywords) indicates the most common keywords present for the BTS publications by subject area.
+The keywords were tokenized into single tokens.
+Keywords were then lowercased, and all stop words (for example, the, an, of, into, for) were removed.
+Finally, a frequency count of tokens was tabulated for each subject area, and this count is used to create the final word cloud presented.
 
@@
 
-### RQ3: Authors.
+## RQ3: Authors
 
-We will first present:
+**Institution**.
 
--   The total number of unique authors
-
-```{r total-authors}
-total_authors <- 510334 # only this updated
-#### DAMMIT FORGOT THIS ####
-avg_authors <- apa_num(49.30516877182394)
-sd_authors <- apa_num(212.9786134634032)
-min_authors <- 10
-med_authors <- 18
-max_authors <- 5568
-```
-
-The total number of unique authors across all publications was
-`r total_authors`.
-
--   Statistics (mean, standard deviation, minimum, maximum, median) on
-    the number of authors included on publications.
-
-The mean number of authors per publication was *M* = `r avg_authors`
-(*SD* = `r sd_authors`, *Med* = `r med_authors`) with a range of
-`r min_authors` to `r max_authors`.
-
--   We will present visualizations of these results across time.
-
-```{r fig-author-year, include = TRUE, fig.cap="Number of authors included on big-team science papers per year by subject area.
-Colored dots indicate the mean number of authors, while the black dots represent the median number of authors.
-The size of the black dots indicate the number of papers in that year."}
-avg_author_time <- 
-  DF$author_time %>% 
-  filter(SubjectArea != "Multidisciplinary") %>% 
-  # filter(Number_Papers >= 3) %>% 
-  mutate(low = (Average_Num_Authors - as.numeric(SD_Num_Authors)), 
-         high = (Average_Num_Authors + as.numeric(SD_Num_Authors)))
-
-ggplot(avg_author_time, aes(Year, Med_Num_Authors)) + 
-  theme_classic() + 
-  geom_point(aes(size = Number_Papers)) + 
-  geom_point(aes(Year, Average_Num_Authors, color = "red")) + 
-  #geom_pointrange(aes(ymin = low, ymax = high)) + 
-  facet_wrap(~SubjectArea) + 
-  ylab("Average Number of Authors") + 
-  xlab("Publication Year") + 
-  theme(legend.position = "bottom") + 
-  guides(color = "none") + 
-  scale_size_continuous(name = "Number Papers")
-```
-
-We will use the 95% confidence interval to make all claims of predictors
-or effects different zero. The confidence interval that does not include
-zero would be considered different from zero (to four decimal places).
-We make no directional predictions.
-
-***Career Length***.
-
--   We will create a visualization of the trend and variance of
-    researcher career length across publication years.
-
-```{r fig-career, include = TRUE, fig.cap = "Average career length for big-team science authors.
-Larger dots indicate more papers for each estimation.
-Lighter colored dots mean less variability in author career length, while darker dots mean more variability in career length."}
-ggplot(DF$career_time %>% 
-         filter(SubjectArea != "Multidisciplinary"), 
-       aes(Year, avg_career, color = sd_career)) +
-  theme_classic() + 
-  geom_point(aes(size = num_papers)) +
-  facet_wrap(~SubjectArea) + 
-  theme(legend.position = "bottom") + 
-  ylab("Average Career Length") +
-  xlab("Year of Publication") + 
-  guides(color = "none") + 
-  scale_size_continuous(name = "Number Papers")
-```
-
--   To analyze trends over time, we will calculate the average career
-    length for each publication (i.e., average the author career length
-    to create one score for each paper) and run a regression analysis
-    using career length to predict year of publication. In order to show
-    variance between individuals, we calculate the standard deviation of
-    career length for each publication and run a regression analysis
-    using this variance representation to predict publication year.
-    These two variables will be used together.
--   Negative slopes would indicate more young scholars in later years
-    (i.e., lower average career length as time increases). Positive
-    slopes would indicate older scholars in later years (i.e., higher
-    average career length as time increases).
--   Negative slopes imply that variability decreases over the years, so
-    the average career length is more homogeneous. Positive slopes imply
-    that variability increases over the years, so the average career
-    length is varied across individuals (lots of different types of
-    scholars).
--   These analyses will be completed separately for each of the four
-    large subject areas.
-
-```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}
-
-label <- c("Physical", "Social", "Health", "Life")
-avg_b_values <- c(-0.692014, -0.365357, -0.451827, -0.508350)
-avg_se_values <- c(0.002727, 0.005525, 0.001348, 0.001786)
-sd_b_values <- c(-0.265538, -0.097108, -0.096730, -0.013958)
-sd_se_values <- c(0.007018, 0.013409, 0.003451, 0.004523)
-r2_values <- c(0.465446, 0.254312, 0.303781, 0.350923)
-sample_size <- total_num
-
-r2_low <- 1:length(r2_values)
-r2_high <- 1:length(r2_values)
-for (i in 1:length(r2_values)){
-  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
-  r2_low[i] <- temp$Lower.Conf.Limit.R2
-  r2_high[i] <- temp$Upper.Conf.Limit.R2
-}
-
-graph_data <- data.frame(
-  "label" = label,
-  "estimate" = avg_b_values,
-  "type" = "M Coefficient",
-  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
-  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
-    bind_rows(
-    data.frame(
-    "label" = label,
-    "estimate" = sd_b_values,
-    "type" = "SD Coefficient",
-    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
-    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
-    ) %>% 
-  bind_rows(
-    data.frame(  
-      "label" = label, 
-      "estimate" = r2_values,
-      "type" = "Effect Size",
-      "low" = r2_low,
-      "high" = r2_high)
-  )
-
-graph_data$type <- factor(
-  graph_data$type, 
-  levels = c("M Coefficient", "SD Coefficient", "Effect Size")
-)
-
-ggplot(graph_data, aes(label, estimate)) + 
-  geom_point() +
-  geom_pointrange(aes(ymin = low, ymax = high)) +
-  theme_classic() + 
-  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
-  geom_hline(yintercept = 0) + 
-  coord_flip() + 
-  xlab("Subject Area") + 
-  ylab("")
-```
-
-***Institution***.
-
--   We will summarize the number of affiliation ids present in BTS
-    publications by subject area and visualize these results across
-    time. These visualizations will be presented separately for each of
-    the four subject areas.
-
-```{r total-aff}
-# updated
-affs <- 463876
-```
-
-The total number of unique affiliation across all papers was `r affs`.
+Institution was normalized by taking the total number of unique institutions and dividing by the total number of institution listings.
+The patterns are similar for each decade in that papers are often either half unique institutions or mostly unique institutions overall as show in Figure \@ref(fig:fig-inst).
 
@@
 
-picture <- ggplot(DF$inst_time %>% 
+graph_data_inst <- DF$inst_time %>% 
          filter(SubjectArea != "Multidisciplinary") %>% 
@@
                                 ifelse(Year < 2010, "2000s", 
-                                       ifelse(Year < 2020, "2010s", "2020s"))))), 
-       aes(Decade, `normalized`)) + 
-  #geom_point() + 
-  geom_violin() + 
+                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
+  mutate(Decade = as.factor(Decade))
+
+picture <- ggplot(graph_data_inst,
+                  aes(y = Decade, x = normalized)) + 
+  geom_density_ridges2() + 
   theme_classic() + 
   facet_wrap(~SubjectArea) + 
-  ylab("Percent of Unique Affiliations") + 
-  xlab("Decade")
+  xlab("Percent of Unique Affiliations") + 
+  ylab("Decade") +
+  coord_cartesian(xlim = c(0, 100))
 
@@
 
--   We will summarize the coded types of publications for individuals.
+```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
 
-```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
-#### try donut chart ####
 pub_types <- bind_rows(
@@
 
-ggplot(pub_types, aes(type, count, fill = publication_type)) + 
-    geom_bar(position="fill", stat="identity", color = "black") + 
-  theme_classic() +  
-  xlab("Author Type") + 
-  ylab("Percent of Paper Types") + 
-  theme(legend.position = "bottom") + 
-  scale_fill_discrete(name = "Publication Type")
+ggplot(pub_types, aes(area = count, fill = count,
+               label = publication_type)) +
+  geom_treemap() +
+  facet_wrap(~type) + 
+  geom_treemap_text(colour = "black", place = "centre",
+                    size = 15, grow = FALSE) +  
+  #scale_fill_brewer(name = "Sample Size", palette = "Spectral") +
+  theme_classic()
+
+# ggplot(pub_types, aes(type, count, fill = publication_type)) + 
+#     geom_bar(position="fill", stat="identity", color = "black") + 
+#   theme_classic() +  
+#   xlab("Author Type") + 
+#   ylab("Percent of Paper Types") + 
+#   theme(legend.position = "bottom") + 
+#   scale_fill_discrete(name = "Publication Type")
 
@@
 ```
-
-***Publication Metrics***.
-
--   We will report descriptive statistics on the total number of
-    publications and h-index for individuals overall.
-    -   Do this for each unique person and report averages
-    -   Do this for each publication and create an average for each
-        publication
-
-```{r pub-hindex}
-avg_pub_count_author	<- apa_num(38.368910766896065)
-std_pub_count_author <- apa_num(102.53740454680472)
-
-avg_pub_count_paper <- apa_num(162.50184385336053)
-sd_pub_count_paper <- apa_num(155.1665533053519)
-avg_SD_pub_count_paper <- apa_num(164.27249797983876)
-SD_SD_pub_count_paper <- apa_num(127.20989934008757)
-
-avg_HIndex <- apa_num(33.64589690529209)
-std_HIndex <- apa_num(127.33565834550778)
-med_HIndex <- apa_num(8.0)
-
-avg_of_avg_HIndex <- apa_num(198.87318851400775)
-std_of_avg_HIndex <- apa_num(248.7847084313958)
-avg_of_std_HIndex <- apa_num(211.7985924228093)
-std_of_std_HIndex <- apa_num(238.53141146314053)
-med_of_med_HIndex <- apa_num(68.0)
-```
-
-The average number of publications by authors on big team sciences
-papers is *M* = `r avg_pub_count_author` (*SD* =
-`r std_pub_count_author`). The publication counts were averaged across
-authors for each publication, and then these average publication counts
-were averaged across publications *M* = `r avg_pub_count_paper` (*SD* =
-`r sd_pub_count_paper`). The average variability (i.e., the average
-standard deviation with authors of a manuscript) with publication counts
-of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
-`r SD_SD_pub_count_paper`).
-
-The same process was completed with *h*-index for each author and
-publication. The average *h*-index for authors overall was *M* =
-`r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`). The
-average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD*
-= `r std_of_avg_HIndex`), and the variability of *h*-index across
-manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ =
-`r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).
-
--   Next, we will use the same analyses described in the career length
-    section to analyze trends over time. An increasing slope over time
-    indicates that individuals who are publishing more are more
-    represented in BTS over time (i.e., increasing numbers of scholars
-    with higher publication rates), while a negative slope indicates
-    more researchers with less publications.
--   A positive slope for standard deviation indicates increasing
-    variance over time (i.e., more diversity in the individual
-    publication rates), while a negative slope would indicate less
-    diversity in researchers over time. While publication rates do not
-    represent value as a researcher, they are often used in hiring and
-    promotion decisions, and we will use this variable as a proxy to
-    gauge the diversity in scholars represented in big teams.
--   We will separate these by each of the four subject areas.
-
-```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}
-
-label <- c("Physical", "Social", "Health", "Life")
-avg_b_values <- c(0.004248, -0.027315, -0.021713, -0.009466)
-avg_se_values <- c(0.000179, 0.001073, 0.000211, 0.000213)
-sd_b_values <- c(-0.021552, 0.016810, 0.010139, -0.000378)
-sd_se_values <- c(0.000241, 0.000921, 0.000198, 0.000235)
-r2_values <- c(0.135965, 0.035968, 0.048999, 0.030748)
-sample_size <- total_num
-
-r2_low <- 1:length(r2_values)
-r2_high <- 1:length(r2_values)
-for (i in 1:length(r2_values)){
-  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
-  r2_low[i] <- temp$Lower.Conf.Limit.R2
-  r2_high[i] <- temp$Upper.Conf.Limit.R2
-}
-
-graph_data <- data.frame(
-  "label" = label,
-  "estimate" = avg_b_values,
-  "type" = "M Coefficient",
-  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
-  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
-    bind_rows(
-    data.frame(
-    "label" = label,
-    "estimate" = sd_b_values,
-    "type" = "SD Coefficient",
-    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
-    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
-    ) %>% 
-  bind_rows(
-    data.frame(  
-      "label" = label, 
-      "estimate" = r2_values,
-      "type" = "Effect Size",
-      "low" = r2_low,
-      "high" = r2_high)
-  )
-
-graph_data$type <- factor(
-  graph_data$type, 
-  levels = c("M Coefficient", "SD Coefficient", "Effect Size")
-)
-
-ggplot(graph_data, aes(label, estimate)) + 
-  geom_point() +
-  geom_pointrange(aes(ymin = low, ymax = high)) +
-  theme_classic() + 
-  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
-  geom_hline(yintercept = 0) + 
-  coord_flip() + 
-  xlab("Subject Area") + 
-  ylab("")
-```
-
-***Geopolitical Regions***.
-
--   We will present visualizations of the country information listed for
-    authors, and we will discuss the areas of world in which authors
-    generally come from, as well as the lowest representation of
-    authors.
-
-```{r geo-map}
-# serbia has changed codes
-# updated but needs work
-DF$geo_country$affiliation_tag_country <- toupper(DF$geo_country$affiliation_tag_country)
-DF$geo_country <- subset(DF$geo_country, affiliation_tag_country != "NONE")
-DF$geo_country$affiliation_tag_country[DF$geo_country$affiliation_tag_country == "SCG"] <- "SRB"
-
-DF$geo_country <- DF$geo_country %>% 
-  group_by(affiliation_tag_country) %>% 
-  summarize(count = sum(count),
-            count_all = sum(all_count))
-
-# convert country code to region code
-# this will warn you about the ones that have multiple countries 
-# create a world map 
-world_map <- map_data(map = "world")
-world_map$orig_region <- world_map$region
-world_map$region <- iso.alpha(world_map$region, n = 3)
-world_map <- subset(world_map, region != "ATA")
-
-# maybe try binning
-DF$geo_country$count_binned <- if_else(
-  DF$geo_country$count >= 1000000, "1,000,000+", 
-  if_else(
-    DF$geo_country$count >= 500000 & DF$geo_country$count < 1000000, "500,000-999,999",
-    if_else(
-      DF$geo_country$count >= 100000 & DF$geo_country$count < 500000, "100,000-499,999",
-      if_else(
-        DF$geo_country$count >= 10000 & DF$geo_country$count < 100000, "10,000-99,999", 
-        if_else(
-          DF$geo_country$count < 10000 & DF$geo_country$count >= 5000, "5,000-9,999",
-          if_else(
-            DF$geo_country$count < 5000 & DF$geo_country$count >= 1000, "1,000-4,999",
-            if_else(
-              DF$geo_country$count < 1000 & DF$geo_country$count >= 100, "100-999",
-              "< 100"
-            )
-          )
-        )
-      )
-    )
-  )
-)
-
-DF$geo_country$count_binned <- factor(DF$geo_country$count_binned, 
-                                   levels = unique(DF$geo_country$count_binned))
-
-DF$geo_country$count_binned <- factor(DF$geo_country$count_binned, 
-                                      levels = c("< 100", 
-                                                 "100-999", 
-                                                 "1,000-4,999", 
-                                                 "5,000-9,999", 
-                                                 "10,000-99,999",
-                                                 "100,000-499,999",
-                                                 "500,000-999,999",
-                                                 "1,000,000+"))
-
-# map of binned data 
-bin_country <- ggplot(DF$geo_country) +
-  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned), map = world_map) +
-  geom_polygon(data = world_map, 
-               aes(x = long, y = lat, group = group), 
-               colour = 'black', fill = NA) + 
-  theme_void() + 
-  # scale_fill_manual(name = "Sample Size",
-  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
-  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
-
-# Warning: Some values were not matched unambiguously: ANT, ATA, BUR, BUX, BYS, CAI, CSK, CZH, DDR, EUE, HVO, PCI, ROM, SUN, SUX, TWN, UNO, YMD, YUG, ZAR
-
-# tree map
-DF$geo_country$un_region_sub <- suppressWarnings(
-  countrycode(
-  sourcevar = DF$geo_country$affiliation_tag_country,
-  origin = 'iso3c', 
-  destination = 'un.regionsub.name')
-)
-
-DF$geo_country$un_region <- suppressWarnings(
-  countrycode(
-  sourcevar = DF$geo_country$affiliation_tag_country,
-  origin = 'iso3c', 
-  destination = 'un.region.name')
-)
-
-DF$geo_country$un_region[DF$geo_country$affiliation_tag_country == "TWN"] <- "Asia"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "ANT"] <- "Western Europe"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "BUR"] <- "Western Africa"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "BYS"] <- "Eastern Europe"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "CSK"] <- "Eastern Europe"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "DOR"] <- "Eastern Europe"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "HVO"] <- "Sub-Saharan Africa"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "PCI"] <- "Eastern Asia"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "ROM"] <- "Eastern Europe"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "SUN"] <- "Eastern Europe"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "YMD"] <- "Western Asia"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "YUG"] <- "Eastern Europe"
-DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "ZAR"] <- "Sub-Saharan Africa"
-
-DF$geo_country <- DF$geo_country %>% 
-  na.omit()
-
-tree <- ggplot(DF$geo_country, aes(area = count, fill = count_binned,
-               label = affiliation_tag_country, subgroup = un_region_sub)) +
-  geom_treemap() +
-  geom_treemap_subgroup_border(colour = "white", size = 5) +
-  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
-  #                            alpha = 0.25, colour = "black",
-  #                            fontface = "italic") +
-  geom_treemap_text(colour = "black", place = "centre",
-                    size = 15, grow = FALSE) +  
-  # scale_fill_manual(name = "Sample Size",
-  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
-  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
-  # scale_fill_gradient(name = "Sample Size",
-  #                     low = "#c8c8c8", 
-  #                     high = "#323232") 
-```
-
-```{r geo-map-all}
-# maybe try binning
-DF$geo_country$count_binned_all <- if_else(
-  DF$geo_country$count_all >= 1000000, "1,000,000+", 
-  if_else(
-    DF$geo_country$count_all >= 500000 & DF$geo_country$count_all < 1000000, "500,000-999,999",
-    if_else(
-      DF$geo_country$count_all >= 100000 & DF$geo_country$count_all < 500000, "100,000-499,999",
-      if_else(
-        DF$geo_country$count_all >= 10000 & DF$geo_country$count_all < 100000, "10,000-99,999", 
-        if_else(
-          DF$geo_country$count_all < 10000 & DF$geo_country$count_all >= 5000, "5,000-9,999",
-          if_else(
-            DF$geo_country$count_all < 5000 & DF$geo_country$count_all >= 1000, "1,000-4,999",
-            if_else(
-              DF$geo_country$count_all < 1000 & DF$geo_country$count_all >= 100, "100-999",
-              "< 100"
-            )
-          )
-        )
-      )
-    )
-  )
-)
-
-DF$geo_country$count_binned_all <- factor(DF$geo_country$count_binned_all, 
-                                   levels = unique(DF$geo_country$count_binned_all))
-
-DF$geo_country$count_binned_all <- factor(DF$geo_country$count_binned_all, 
-                                      levels = c("< 100", 
-                                                 "100-999", 
-                                                 "1,000-4,999", 
-                                                 "5,000-9,999", 
-                                                 "10,000-99,999",
-                                                 "100,000-499,999",
-                                                 "500,000-999,999",
-                                                 "1,000,000+"))
-
-# map of binned data 
-bin_country_all <- ggplot(DF$geo_country) +
-  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned_all), map = world_map) +
-  geom_polygon(data = world_map, 
-               aes(x = long, y = lat, group = group), 
-               colour = 'black', fill = NA) + 
-  theme_void() + 
-  # scale_fill_manual(name = "Sample Size",
-  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
-  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
-
-tree_all <- ggplot(DF$geo_country, aes(area = count_all, fill = count_binned_all,
-               label = affiliation_tag_country, subgroup = un_region_sub)) +
-  geom_treemap() +
-  geom_treemap_subgroup_border(colour = "white", size = 5) +
-  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
-  #                            alpha = 0.25, colour = "black",
-  #                            fontface = "italic") +
-  geom_treemap_text(colour = "black", place = "centre",
-                    size = 15, grow = FALSE) +  
-  # scale_fill_manual(name = "Sample Size",
-  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
-  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
-  # scale_fill_gradient(name = "Sample Size",
-  #                     low = "#c8c8c8", 
-  #                     high = "#323232") 
-```
-
-```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications."}
-bin_country + ggtitle("Big-Team Publication Map") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-  theme(legend.position = "none") + 
-tree + ggtitle("Big-Team Publication Mosiac Chart") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-  guides(fill = "none") + 
-bin_country_all + ggtitle("All Publications Map") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-  guides(fill = "none") + 
-tree_all + ggtitle("All Publications Mosiac Chart") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-  guides(fill = "none") + 
-  plot_layout(ncol = 2, 
-              nrow = 2) + 
-  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
-
-# need to do the legend 
-```
-
--   To understand the change in representation diversity, we will
-    summarize the total number of geopolitical regions for each paper.
-    Using a linear model, we will examine if the number of regions
-    present is predicted by the year of publication. Increasing
-    diversity would be represented by a positive slope, while decreasing
-    diversity would be represented by a negative slope.
-
-```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}
-
-label <- c("Physical", "Social", "Health", "Life")
-b_values <- c(0.002175, 0.033175, 0.016824, 0.008029)
-se_values <- c(0.002578, 0.006039, 0.001150, 0.001476)
-r2_values <- c(0.000006, 0.001542, 0.000708, 0.000170)
-sample_size <- total_num
-
-r2_low <- 1:length(r2_values)
-r2_high <- 1:length(r2_values)
-for (i in 1:length(r2_values)){
-  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
-  r2_low[i] <- temp$Lower.Conf.Limit.R2
-  r2_high[i] <- temp$Upper.Conf.Limit.R2
-}
-
-graph_data <- data.frame(
-  "label" = label,
-  "estimate" = b_values,
-  "type" = "Coefficient",
-  "low" = b_values - qt(.025, sample_size, lower.tail = F)*se_values,
-  "high" = b_values + qt(.025, sample_size, lower.tail = F)*se_values) %>% 
-  bind_rows(
-    data.frame(  
-      "label" = label, 
-      "estimate" = r2_values,
-      "type" = "Effect Size",
-      "low" = r2_low,
-      "high" = r2_high)
-  )
-
-# graph_data$type <- factor(
-#   graph_data$type, 
-#   levels = c("Coefficient", "Effect Size")
-# )
-
-ggplot(graph_data, aes(label, estimate)) + 
-  geom_point() +
-  geom_pointrange(aes(ymin = low, ymax = high)) +
-  theme_classic() + 
-  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels_2))) + 
-  geom_hline(yintercept = 0) + 
-  coord_flip() + 
-  xlab("Subject Area") + 
-  ylab("")
-```
-
--   Last, we will examine the differences in representation for
-    corresponding author sets versus all other authors. For papers with
-    10 to 49 authors, we will use the three first authors and the last
-    author to compare against other authors. For 50 to 99 authors, five
-    first authors plus last will be used, and for all papers with more
-    than 100 authors, we will use ten first authors and the last author.
-    We will calculate the frequencies of each of the UN Sub-Regions for
-    first authors versus other authors, converting these values to
-    proportions. Given the expected small sample sizes of these
-    contingency tables, we will group together titles based on the year
-    of publication (assuming at least 5 publications per year, these may
-    be binned by 5-year or smaller increments to increase sample size).
-    For each grouping, we will calculate the effect size of the
-    differences in frequencies comparing first authors to all other
-    authors. Since this data is categorical, we will use Cramer's *V* to
-    represent the effect size. If the effect size includes zero in its
-    confidence interval, this result will imply that first and all other
-    authors represent the same pattern of UN Sub-Region diversity. Any
-    confidence interval that does include zero represents a difference
-    in diversity.
-
-```{r small-effects, warning = FALSE}
-DF$small_first_gp <- DF$small_first_gp %>% 
-  filter(aff_un != "other") %>% 
-  pivot_wider(id_cols = Year, 
-              names_from = aff_un, 
-              values_from = count,
-              values_fill = 0)
-
-DF$small_other_gp <- DF$small_other_gp %>% 
-  filter(aff_un != "other") %>% 
-  pivot_wider(id_cols = Year, 
-              names_from = aff_un, 
-              values_from = count,
-              values_fill = 0) %>% 
-  select(colnames(DF$small_first_gp))
-
-small_effect <- data.frame(
-  year = 1:length(unique(DF$small_first_gp$Year)),
-  v = 1:length(unique(DF$small_first_gp$Year)),
-  low = 1:length(unique(DF$small_first_gp$Year)),
-  high = 1:length(unique(DF$small_first_gp$Year))
-)
-i <- 1
-for (year in unique(DF$small_first_gp$Year)){
-  temp_table <- DF$small_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
-    bind_rows(DF$small_other_gp %>% filter(Year == year) %>% select(-Year))
-
-  col_total <- colSums(temp_table)
-  temp_table <- temp_table %>% 
-    select(names(col_total)[col_total > 0])
-  temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
-
-  tryCatch(mote_temp <- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
-                        r = nrow(temp_table), c = ncol(temp_table), 
-                        a = .05), 
-       warning = function(w) { 
-         mote_temp <<- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
-                        r = nrow(temp_table), c = ncol(temp_table), 
-                        a = .05)
-         mote_temp$vlow <<- 0
-  }
-  )
-
-  small_effect$year[i] <- year
-  small_effect$v[i] <- mote_temp$v
-  small_effect$low[i] <- mote_temp$vlow
-  small_effect$high[i] <- mote_temp$vhigh
-  small_effect$people[i] <- mote_temp$n
-  i <- i + 1
-}
-
-small_effect$high[is.na(small_effect$high)] <- 0
-small_effect <- 
-  small_effect %>% 
-  filter(v != Inf)
-
-small_dot <- ggplot(small_effect, aes(year,v)) + 
-  geom_point(aes(size = people)) + 
-  theme_classic() + 
-  geom_pointrange(aes(ymin = low, ymax = high)) + 
-  xlab("Year") + 
-  ylab(expression(phi)) + 
-  scale_size_continuous(name = "Num Authors")
-
-DF_decade <- DF$small_first_gp %>% 
-  mutate(who = "F") %>% 
-  bind_rows(
-    DF$small_other_gp %>% 
-      mutate(who = "O")
-  ) %>% 
-  mutate(Decade = ifelse(Year < 1990, "1980s", 
-                         ifelse(Year < 2000, "1990s", 
-                                ifelse(Year < 2010, "2000s", 
-                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
-  group_by(who, Decade) %>% 
-  summarize_all(sum) %>% 
-  pivot_longer(cols = `Western Europe`:Mirconesia,
-               names_to = "Country", 
-               values_to = "Count")
-
-# North America, Africa (combine), NWS Europe, Eastern Asia, Latin America, Rest of Europe, Rest of Asia, Everything Else
-
-DF_decade$Country_2 <- DF_decade$Country
-DF_decade$Country_2 <- gsub(".*Africa.*", "Africa", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Northern Europe|Southern Europe|Western Europe", "NWS Europe", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("South-Eastern Europe|Eastern Europe", "ESE Europe", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Central Asia|South-Eastern Asia|Southern Asia|Western Asia", "Asia", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Melanesia|Mirconesia|New zealand and Australia|Polynesia", "Other", DF_decade$Country_2)
-
-DF_decade_sm <- DF_decade %>% 
-  group_by(Country_2, Decade, who) %>% 
-  summarize(Count = sum(Count), .groups = "keep")
-
-small_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
-    geom_bar(position="fill", stat="identity", color = "black") + 
-  theme_classic() + 
-  facet_grid(~Decade) + 
-  xlab("Author Type") + 
-  ylab("Percent of Authors") + 
-  scale_fill_brewer(name = "Region", palette = "Spectral")
-```
-
-```{r medium-effects, warning = FALSE}
-DF$medium_first_gp <- DF$medium_first_gp %>% 
-  filter(aff_un != "other") %>% 
-  pivot_wider(id_cols = Year, 
-              names_from = aff_un, 
-              values_from = count,
-              values_fill = 0)
-
-DF$medium_other_gp <- DF$medium_other_gp %>% 
-  filter(aff_un != "other") %>% 
-  pivot_wider(id_cols = Year, 
-              names_from = aff_un, 
-              values_from = count,
-              values_fill = 0) %>% 
-  select(colnames(DF$medium_first_gp))
-
-medium_effect <- data.frame(
-  year = 1:length(unique(DF$medium_first_gp$Year)),
-  v = 1:length(unique(DF$medium_first_gp$Year)),
-  low = 1:length(unique(DF$medium_first_gp$Year)),
-  high = 1:length(unique(DF$medium_first_gp$Year))
-)
-i <- 1
-for (year in unique(DF$medium_first_gp$Year)){
-  temp_table <- DF$medium_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
-    bind_rows(DF$medium_other_gp %>% filter(Year == year) %>% select(-Year))
-
-  col_total <- colSums(temp_table)
-  temp_table <- temp_table %>% 
-    select(names(col_total)[col_total > 0])
-  temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
-  tryCatch(mote_temp <- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
-                        r = nrow(temp_table), c = ncol(temp_table), 
-                        a = .05), 
-       warning = function(w) { 
-         mote_temp <<- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
-                        r = nrow(temp_table), c = ncol(temp_table), 
-                        a = .05)
-         mote_temp$vlow <<- 0
-  }
-  )
-  medium_effect$year[i] <- year
-  medium_effect$v[i] <- mote_temp$v
-  medium_effect$low[i] <- mote_temp$vlow
-  medium_effect$high[i] <- mote_temp$vhigh
-  medium_effect$people[i] <- mote_temp$n
-  i <- i + 1
-}
-
-medium_effect$high[is.na(medium_effect$high)] <- 0
-medium_effect <- 
-  medium_effect %>% 
-  filter(v != Inf)
-
-medium_dot <- ggplot(medium_effect, aes(year,v)) + 
-  geom_point(aes(size = people)) + 
-  theme_classic() + 
-  geom_pointrange(aes(ymin = low, ymax = high)) + 
-  xlab("Year") + 
-  ylab(expression(phi)) + 
-  scale_size_continuous(name = "Num Authors")
-
-DF_decade <- DF$medium_first_gp %>% 
-  mutate(who = "F") %>% 
-  bind_rows(
-    DF$medium_other_gp %>% 
-      mutate(who = "O")
-  ) %>% 
-  mutate(Decade = ifelse(Year < 1990, "1980s", 
-                         ifelse(Year < 2000, "1990s", 
-                                ifelse(Year < 2010, "2000s", 
-                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
-  group_by(who, Decade) %>% 
-  summarize_all(sum) %>% 
-  pivot_longer(cols = `Western Europe`:Melanesia, 
-               #### check this later ####
-               names_to = "Country", 
-               values_to = "Count")
-
-# North America, Africa (combine), NWS Europe, Eastern Asia, Latin America, Rest of Europe, Rest of Asia, Everything Else
-
-DF_decade$Country_2 <- DF_decade$Country
-DF_decade$Country_2 <- gsub(".*Africa.*", "Africa", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Northern Europe|Southern Europe|Western Europe", "NWS Europe", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("South-Eastern Europe|Eastern Europe", "ESE Europe", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Central Asia|South-Eastern Asia|Southern Asia|Western Asia", "Asia", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Melanesia|Mirconesia|New zealand and Australia|Polynesia", "Other", DF_decade$Country_2)
-
-DF_decade_sm <- DF_decade %>% 
-  group_by(Country_2, Decade, who) %>% 
-  summarize(Count = sum(Count), .groups = "keep")
-
-medium_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
-    geom_bar(position="fill", stat="identity", color = "black") + 
-  theme_classic() + 
-  facet_grid(~Decade) + 
-  xlab("Author Type") + 
-  ylab("Percent of Authors") + 
-  scale_fill_brewer(name = "Region", palette = "Spectral")
-```
-
-```{r large-effects, warning = FALSE}
-DF$large_first_gp <- DF$large_first_gp %>% 
-  filter(aff_un != "other") %>% 
-  pivot_wider(id_cols = Year, 
-              names_from = aff_un, 
-              values_from = count,
-              values_fill = 0)
-
-DF$large_other_gp <- DF$large_other_gp %>% 
-  filter(aff_un != "other") %>% 
-  pivot_wider(id_cols = Year, 
-              names_from = aff_un, 
-              values_from = count,
-              values_fill = 0) %>% 
-  select(colnames(DF$large_first_gp))
-
-large_effect <- data.frame(
-  year = 1:length(unique(DF$large_first_gp$Year)),
-  v = 1:length(unique(DF$large_first_gp$Year)),
-  low = 1:length(unique(DF$large_first_gp$Year)),
-  high = 1:length(unique(DF$large_first_gp$Year))
-)
-i <- 1
-for (year in unique(DF$large_first_gp$Year)){
-  temp_table <- DF$large_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
-    bind_rows(DF$large_other_gp %>% filter(Year == year) %>% select(-Year))
-
-  col_total <- colSums(temp_table)
-  temp_table <- temp_table %>% 
-    select(names(col_total)[col_total > 0])
-  temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
-  tryCatch(mote_temp <- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
-                        r = nrow(temp_table), c = ncol(temp_table), 
-                        a = .05), 
-       warning = function(w) { 
-         mote_temp <<- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
-                        r = nrow(temp_table), c = ncol(temp_table), 
-                        a = .05)
-         mote_temp$vlow <<- 0
-  }
-  )
-  large_effect$year[i] <- year
-  large_effect$v[i] <- mote_temp$v
-  large_effect$low[i] <- mote_temp$vlow
-  large_effect$high[i] <- mote_temp$vhigh
-  large_effect$people[i] <- mote_temp$n
-  i <- i + 1
-}
-
-large_effect$high[is.na(large_effect$high)] <- 0
-large_effect <- 
-  large_effect %>% 
-  filter(v != Inf)
-
-large_dot <- ggplot(large_effect, aes(year,v)) + 
-  geom_point(aes(size = people)) + 
-  theme_classic() + 
-  geom_pointrange(aes(ymin = low, ymax = high)) + 
-  xlab("Year") + 
-  ylab(expression(phi)) + 
-  scale_size_continuous(name = "Num Authors")
-
-DF_decade <- DF$large_first_gp %>% 
-  mutate(who = "F") %>% 
-  bind_rows(
-    DF$large_other_gp %>% 
-      mutate(who = "O")
-  ) %>% 
-  mutate(Decade = ifelse(Year < 1990, "1980s", 
-                         ifelse(Year < 2000, "1990s", 
-                                ifelse(Year < 2010, "2000s", 
-                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
-  group_by(who, Decade) %>% 
-  summarize_all(sum) %>% 
-  pivot_longer(cols = `Western Europe`:`Central Asia`, 
-               #### check this later ####
-               names_to = "Country", 
-               values_to = "Count")
-
-# North America, Africa (combine), NWS Europe, Eastern Asia, Latin America, Rest of Europe, Rest of Asia, Everything Else
-
-DF_decade$Country_2 <- DF_decade$Country
-DF_decade$Country_2 <- gsub(".*Africa.*", "Africa", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Northern Europe|Southern Europe|Western Europe", "NWS Europe", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("South-Eastern Europe|Eastern Europe", "ESE Europe", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Central Asia|South-Eastern Asia|Southern Asia|Western Asia", "Asia", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Melanesia|Mirconesia|New zealand and Australia|Polynesia", "Other", DF_decade$Country_2)
-
-DF_decade_sm <- DF_decade %>% 
-  group_by(Country_2, Decade, who) %>% 
-  summarize(Count = sum(Count), .groups = "keep")
-
-large_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
-    geom_bar(position="fill", stat="identity", color = "black") + 
-  theme_classic() + 
-  facet_grid(~Decade) + 
-  xlab("Author Type") + 
-  ylab("Percent of Authors") + 
-  scale_fill_brewer(name = "Region", palette = "Spectral")
-```
-
-```{r author-gpe-figure, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors."}
-small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
-medium_author + ggtitle("50-99 Authors") + #theme(legend.position = "none") + 
-large_author + ggtitle("100 + Authors") + #theme(legend.position = "none") + 
-guide_area() + 
-plot_layout(
-  ncol = 2,
-  nrow = 2, 
-  guides = "collect")
-
-ggsave("figure/author_country.png", width = 10, height = 7, 
-       units = "in")
-
-# fix the legend
-```
-
-```{r effect-gpe-figure, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year."}
-small_dot + 
-  theme(legend.position = "none") + 
-  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
-  ggtitle("10-49 Authors") + 
-medium_dot + 
-  theme(legend.position = "none") + 
-  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
-  ggtitle("50-99 Authors") +
-large_dot + 
-  theme(legend.position = "none") + 
-  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
-  ggtitle("100 + Authors") + 
-guide_area() + 
-plot_layout(
-  ncol = 2,
-  nrow = 2, 
-  guides = "collect")
-
-ggsave("figure/effect_country.png", width = 10, height = 7, 
-       units = "in")
-```
-
-\newpage
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-
-::: {#refs custom-style="Bibliography"}
-:::
-
-```{=tex}
-\endgroup
-```

### 2023-08-09 data/combine_outputs.Rmd
moving things around

--- 2023-05-07 combine_outputs.Rmd
@@
 
-geo1 <- import("scopus_combine/geo_country_1.csv")
-geo2 <- import("scopus_combine/geo_country_2.csv")
+geo1 <- import("data/scopus_combine/geo_country_1.csv")
+geo2 <- import("data/scopus_combine/geo_country_2.csv")
 
@@
 
-export(geo_together, "py_outputs/geo_country.xlsx", rownames = F)
+export(geo_together, "data/scopus_outputs/geo_country.xlsx", rowNames = F)
 ```

### 2023-08-09 manuscript_scopus.Rmd
moving things around

@@
 abstract: |
-  This paper will examine the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions.
+  This paper examined the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions.
 As interest in BTS increases, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
-The types of publication outlets, number of publications, and subject areas of publication will be presented to summarize the publications in BTS.
+The types of publication outlets, number of publications, and subject areas of publication are presented to summarize the publications in BTS.
 Information about authors included in BTS will be presented including career length, numbers of publications/impact variables, education, and affiliation.
 Last, we will explore the representation of geopolitical regions by examining affiliation location to explore the impact of BTS on the de-WEIRD movement to diversify researcher representation.
+REWRITE THIS
 
 keywords          : "big team, science, authorship, credit"
-wordcount         : "X"
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 bibliography: references.bib
-header-includes:
-  - |
-    \makeatletter
-    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-1em}%
-      {\normalfont\normalsize\bfseries\typesectitle}}
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-\z@\relax}%
-      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
-documentclass     : "apa7"
-output            : papaja::apa6_docx
+# header-includes:
+#   - |
+#     \makeatletter
+#     \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+#       {-1em}%
+#       {\normalfont\normalsize\bfseries\typesectitle}}
+#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+#       {-\z@\relax}%
+#       {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+# csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+# documentclass     : "apa7"
+output            : papaja::apa6_pdf
+appendix          :
+  - "appendix.Rmd"
 ---
@@
 library(figpatch)
+library(RColorBrewer)
+library(latex2exp)
 
 strip_labels <- expression(
-  "M Coefficient" = b[M],
+  "M Coefficient " = b[M],
   "SD Coefficient" = b[SD],
-  "Effect Size" = R^2
-)
-
-strip_labels_2 <- expression(
-  "Coefficient" = b,
-  "Effect Size" = R^2
+  "Effect Size" = R^2,
+  "Coefficient" = b
 )
@@
 
-var_list_import <- paste0("py_outputs/", var_list, ".xlsx")
+var_list_import <- paste0("data/scopus_outputs/", var_list, ".xlsx")
 
@@
 when2meet, etc.). The credibility movement seems to suggest that by
-having both collaborations that span across the globe and subfield of
-psychology, age groups, and education levels should help to drive
-psychological science in the path of better materials, reliability,
-generalizability and more robust sample size in a study
+having both collaborations that span across the globe and subfields of
+research areas, age groups, and education levels should help to drive science in the path of better materials, reliability,
+generalizability and more robust sample sizes (when necessary) in a study
 [@auspurg2021has; @nosek2014method; @lebel2018].
@@
 scale replications using in collaborative environments [@vazire2022].
-Generally, the movement has been driven by early career researchers
+Generally, the movement appears to have been driven by early career researchers
 (i.e., those who are within five years of their first appointment)
@@
 collected [@nosek2014; @stewart2020], and entire sub-sections of
-journals devoted to only replication studies (e.g., *Nature, Royal
-Society Open Science, Advances in Methods and Practices in Psychological
-Science*) has allowed researchers to invest in projects that they know
+journals devoted to only replication studies (e.g., *Nature, Royal Society Open Science, Advances in Methods and Practices in Psychological Science*) has allowed researchers to invest in projects that they know
 should be published when the project is complete. Further, the
@@
 Therefore, the goal of this manuscript is to examine the *people*
-involved in BTS projects. We specifically expect to examine ICSR's
-Research Themes of inclusivity, research careers, and research
-globalization. As we examine these themes, it will bring new knowledge
-of how BTS projects impact each theme and field of study. We see an
-increase in interest and publications in BTS but we do not yet know if
+involved in BTS projects. We specifically examined the themes of inclusivity, research careers, and research globalization. We see an
+increasing interest and number of publications in BTS but we do not yet know if
 this uptick in large-scale projects has diversified the *people*
@@
 
-# Potential Outlets
-
-We will aim for high impact broad scope journals such as *Science*,
-*Nature* or *Nature Human Behaviour*. Other journals would include
-review publications within psychology to compare the social sciences to
-other sciences: *Perspectives in Psychological Science*, *Psychological
-Bulletin*, *Psychological Review*, or *Current Directions in
-Psychological Science*.
-
 # Research Questions
@@
 
-For each of these research questions, we will examine the overall
-results of all big team research projects, and examine for change in
-result trends across years of publication. Below we detail our methods
-and the ICSR/Scopus data to answer these questions, along with examples
-of the statistical results we expect to report in the manuscript. We
-began this project with data using Google Scholar and ORCID information.
-These sources were severely limited in their scope and breadth, as they
-are often curated with automatic processes or self-entered data, and we
-believe that access to Scopus and ICSR would allow us to accurately
-portray the BTS movement and its impact on diversity across many fields.
-The novelty of this project is that it would focus on all of published
-works, rather than a specific subfield (like Psychology) and give a lens
-into global representation in science that would otherwise not be
-achieved with open-source databases.
+This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (https://osf.io/f2dtr) but then was updated with access to the Scopus database for a broader picture of BTS projects (https://osf.io/fheun).
+All materials and code can be found on our OSF page: https://osf.io/cgx6u/ or corresponding GitHub archive: https://github.com/doomlab/big_team_who.
 
@@
 
-We have defined **BTS publications** as publications with at least 10
-authors at 10 different institutions that were published in
-peer-reviewed journals or had posted a full paper pre-print. We will use
-data from 1970 and forward in the publications (`ani`) database, as it
+We have defined BTS publications as publications with at least ten
+authors at ten different institutions that were published in
+peer-reviewed journals or had posted a full paper pre-print. We used
+data from 1970 and forward in the Scopus database, as it
 is noted online that this time period includes cited references for
 calculation of several of our variables described below. We will analyze
-our results based on the big four subject areas: Physical Sciences,
+our results based on four subject areas present in the Scopus database: Physical Sciences,
 Health Sciences, Social Sciences, and Life Sciences. We filtered the
@@
 conference papers, data papers, preprints, and surveys using Elsevier's
-classification system.
+classification system. This project was supported by access to the Scopus database through the International Center for the Study of Research.
 
@@
 
-Using these criteria, we will extract the following information for
-publication sources: the name of the publication (source title), subject
-area (both the large four subject areas and the smaller four digit all
-science journal classification ASJC codes). We will examine journal
-impact using the Source Normalized Impact per Paper from the journal
-(`sources`) database.
+We extracted the following information for publication sources: the name of the publication (source title), subject area (both the large four subject areas and the smaller four digit all science journal classification [ASJC] code), and the journal
+impact using the Source Normalized Impact per Paper (SNIP).
 
@@
 
-For each publication of the identified BTS publications, we will analyze
+For each publication of the identified BTS publications, we examined
 the full four digit ASJC subject areas codes for each of the larger four
@@
 
-The author list will then be extracted from each publication. Next, we
-will use the author (`au`) and affiliation (`af`) array to curate a list
-of all publications and author information included in BTS papers. We
-will use these two arrays with the publication array to calculate the
-variables described below.
-
-***Career Length***. Career length for each author will be defined as
-the year of the first publication listed for each author.
-
-***Institution and Geopolitical Region*** . We will use the affiliation
+The author list was extracted from each publication.
+Next, we used the author and affiliation arrays to curate a list of all publications and author information included in BTS papers to calculate the variables described below.
+
+***Career Length***. Career length for each author was defined as
+the year of the first publication minus the current year listed for each author.
+
+***Institution and Geopolitical Region***. We used the affiliation
 ids and country to gather information about the places of education
-and/or employment for authors. Country will likely be binned into United Nation Region, Sub-Region, or smaller clusters for analyses.
-
-***Education***. We will also collect degree information from the author table.
-
-***Types of Publications***. We will gather information from the
-publication type variable for each author publication to present
+and/or employment for authors. Geopolitical region was created by binning these codes into United Nation Regions.
+
+***Education***. We collected degree information from the author table.
+
+***Types of Publications***. We took information from the
+publication type variable for each author's publications to present
 information about the types of papers BTS authors publish.
 
-***Publication Metrics***. For each author, we will calculate the total
+***Publication Metrics***. For each author, we calculated the total
 number of publications, and the h-index. The h-index represents the
@@
 
-## Data analysis
-
-### RQ1: Publisher Information.
-
-To present results on this research question, we will analyze:
-
--   Number of articles for inclusion: total, separated by four subject
-    areas, presenting graphics of the number of publication across time
-    total
+# Results
+
+We used the 95% confidence interval to make decisions on predictor or effect size differences from zero.
+The confidence interval that does not include zero would be considered different from zero (to four decimal places).
+We made no directional predictions.
+
+## RQ1: Publisher Information.
 
@@
 `r life_num` Life Sciences articles. Articles could be classified into
-multiple categories. Figure X shows the number of articles published across time for each of the four large subject areas.
+multiple categories. Figure \@ref(fig:fig-pub-time) shows the number of articles published across time for each of the four large subject areas.
 
@@
 
--   Number of distinct journals within each of the four subject areas
-
 ```{r total-journals}
@@
 Sciences. The descriptive statistics for the Source Normalized Impact
-per Paper is presented in Table X. For comparison, the SNIP descriptive
-statistics for all papers is shown in Table X.
-
-```{r tab-snip, results = 'asis', include = TRUE}
-# updated
-#### make this one table #### 
-apa_table(
-  DF$snip %>% 
-    filter(`Subject Area` != "Multidisciplinary") %>% 
-    mutate(M = apa_num(M), 
-           SD = apa_num(SD), 
-           Minimum = apa_num(Minimum), 
-           Median = apa_num(Median), 
-           Maximum = apa_num(Maximum)), 
-  caption = "Big-Team Science SNIP Values")
-```
-
-```{r tab-snip-all, results = 'asis', include = TRUE}
-# updated
-apa_table(
-  DF$snip_all %>% 
-    filter(`Subject Area` != "Multidisciplinary") %>% 
-    mutate(M = apa_num(M), 
-           SD = apa_num(SD), 
-           Minimum = apa_num(Minimum), 
-           Median = apa_num(Median), 
-           Maximum = apa_num(Maximum)),
-  caption = "All Journal Articles SNIP Values")
-```
-
-### RQ2: Publication Information.
-
-For each publication, we will examine:
-
--   The totals of the number of articles published within the smaller
-    subject area classifications. We will visualize these differences to show the areas of interest for each of the four large subject areas.
+per Paper is presented the supplemental materials with a comparison for all papers.
+
+## RQ2: Publication Information.
+
+Publication interest area was summarized by the four large subject areas creating a word cloud plot of the total number of publications within the ASJCs.
+Figure \@ref(fig:fig-clouds) displays that the health sciences tends to publish within medicine and oncology, with a corresponding focus of cancer research and genetics for the life sciences.
+The physical sciences is mostly dominated by physics research, chemistry, and ecology.
+The BTS publications in the social sciences are mostly within psychology, education, and health.
 
@@
 
--   The keywords present in the publications data overall to identify
-    trends and common themes in the publications for the four subject
-    areas using visualizations (wordclouds) to depict the common
-    keywords.
-
-```{r make-clouds2, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
-### NOTE YOU WILL NEED TO RERUN THIS ###
-# health
-health_cloud <- DF$keywords %>% 
-   filter(SubjectArea == "Health Sciences") %>% 
-   ungroup() %>% 
-   select(keywords_nostop, count) %>% 
-  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/health_key.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# physical
-physical_cloud <- DF$keywords %>% 
-   filter(SubjectArea == "Physical Sciences") %>% 
-   ungroup() %>% 
-   select(keywords_nostop, count) %>% 
-  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/physical_key.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# life
-life_cloud <- DF$keywords %>% 
-   filter(SubjectArea == "Life Sciences") %>% 
-   ungroup() %>% 
-   select(keywords_nostop, count) %>% 
-  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/life_key.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# social 
-social_cloud <- DF$keywords %>% 
-   filter(SubjectArea == "Social Sciences") %>% 
-   ungroup() %>% 
-   select(keywords_nostop, count) %>% 
-  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/social_key.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-```
-
-```{r fig-keywords, include = TRUE, fig.cap="Keyword Analysis for Each of the Four Subject Areas."}
-health_key <- fig("figure/health_key.png")
-physical_key <- fig("figure/physical_key.png") 
-life_key <- fig("figure/life_key.png") 
-social_key <- fig("figure/social_key.png")
-
-health_key + ggtitle("Health Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-physical_key + ggtitle("Physical Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-life_key + ggtitle("Life Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-social_key + ggtitle("Social Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) +
-  plot_layout(ncol = 2, 
-              nrow = 2)
-```
-
-### RQ3: Authors.
-
-We will first present:
-
--   The total number of unique authors
+## RQ3: Authors.
 
 ```{r total-authors}
-total_authors <- 510334 # only this updated
-#### DAMMIT FORGOT THIS ####
+# updated
+total_authors <- 510334
 avg_authors <- apa_num(49.30516877182394)
@@
 
-The total number of unique authors across all publications was
-`r total_authors`.
-
--   Statistics (mean, standard deviation, minimum, maximum, median) on
-    the number of authors included on publications.
-
-The mean number of authors per publication was *M* = `r avg_authors`
-(*SD* = `r sd_authors`, *Med* = `r med_authors`) with a range of
-`r min_authors` to `r max_authors`.
-
--   We will present visualizations of these results across time.
+The total number of unique authors across all publications was `r total_authors`.
+The mean number of authors per publication was *M* = `r avg_authors` (*SD* = `r sd_authors`, *Med* = `r med_authors`) with a range of `r min_authors` to `r max_authors`.
+The median and average number of authors by subject area are displayed in Figure \@ref(fig:fig-author-year).
+In general, the average and median number of authors increased over time, with the exception of the skew in the physical sciences.
+Interestingly, the effect in the physical sciences appears to be declining toward the general trends seen in other areas in the last few decades.
 
 ```{r fig-author-year, include = TRUE, fig.cap="Number of authors included on big-team science papers per year by subject area.
-Colored dots indicate the mean number of authors, while the black dots represent the median number of authors.
-The size of the black dots indicate the number of papers in that year."}
+Given the large skew in the data, the left panel presents the median number of authors per manuscript, and the right panel presents the average number of authors per manuscript by year."}
 avg_author_time <- 
@@
 
-ggplot(avg_author_time, aes(Year, Med_Num_Authors)) + 
+# ggplot(avg_author_time, aes(Year, Med_Num_Authors)) + 
+#   theme_classic() + 
+#   geom_point(aes(size = Number_Papers)) + 
+#   geom_point(aes(Year, Average_Num_Authors, color = "red")) + 
+#   #geom_pointrange(aes(ymin = low, ymax = high)) + 
+#   facet_wrap(~SubjectArea) + 
+#   ylab("Average Number of Authors") + 
+#   xlab("Publication Year") + 
+#   theme(legend.position = "bottom") + 
+#   guides(color = "none") + 
+#   scale_size_continuous(name = "Number Papers")
+
+median_authors <- 
+  ggplot(avg_author_time, aes(Year, Med_Num_Authors, color = SubjectArea)) + 
   theme_classic() + 
-  geom_point(aes(size = Number_Papers)) + 
-  geom_point(aes(Year, Average_Num_Authors, color = "red")) + 
-  #geom_pointrange(aes(ymin = low, ymax = high)) + 
-  facet_wrap(~SubjectArea) + 
+  geom_point() + 
+    ylab("Median Number of Authors") + 
+    xlab("Publication Year")
+
+mean_authors <- 
+  ggplot(avg_author_time, aes(Year, Average_Num_Authors, color = SubjectArea)) + 
+  theme_classic() + 
+  geom_point() + 
     ylab("Average Number of Authors") + 
-  xlab("Publication Year") + 
-  theme(legend.position = "bottom") + 
-  guides(color = "none") + 
-  scale_size_continuous(name = "Number Papers")
-```
-
-We will use the 95% confidence interval to make all claims of predictors
-or effects different zero. The confidence interval that does not include
-zero would be considered different from zero (to four decimal places).
-We make no directional predictions.
+    xlab("Publication Year")
+
+median_authors + 
+  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
+  mean_authors + 
+  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
+  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
+```
 
@@
 
--   We will create a visualization of the trend and variance of
-    researcher career length across publication years.
+Figure \@ref(fig:fig-career) portrays the average career length for authors involved in BTS publications across years.
+Career length was defined as the year of first publication minus the current year, and higher numbers mean longer careers.
+To analyze trends over time, we  calculated the average career length for each publication (i.e., average author career lengths to create one score for each paper) and analyzed a regression analysis using career length to predict year of publication.
+In order to show variance between individuals, we calculated the standard deviation of career length for each publication and used variance as an additional predictor.
+
+Negative career length slopes would indicate more young scholars in later years (i.e., lower average career length as time increases).
+Positive career length slopes would indicate older scholars in later years (i.e., higher average career length as time increases).
+Negative career variance slopes imply that variability decreases over the years, so the average career length is more homogeneous.
+Positive career length slopes imply that variability increases over the years, so the average career length is varied across individuals (i.e., different stages of scholars).
+Figure \@ref(fig:fig-heatmap) displays the results for all regression analyses to compare coefficient strength across and within hypothesis.
+
+All values for this analyses were different from zero.
+The slopes for the average career length were negative for all four subject areas, indicating a trend toward younger scientist involvement over time for each area, with the strongest effect in the Physical sciences.
+The coefficient for variability in career length was also negative for each of the four subject areas with the highest in the Physical sciences and lowest in the Life Sciences.
+This result indicates a decrease in the variability of career lengths over time, likely from two sources: 1) more publications with more authors, thus, lowering variance estimations, and 2) more young scholars overall.
+The effect sizes for this analysis were surprisingly large ranging from $R^2$ to .25 to .47.
+All values and their confidence intervals can be found on our OSF page.
 
 ```{r fig-career, include = TRUE, fig.cap = "Average career length for big-team science authors.
-Larger dots indicate more papers for each estimation.
-Lighter colored dots mean less variability in author career length, while darker dots mean more variability in career length."}
+Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year.
+The data has been filtered to at least 10 publications in a year for this graph."}
 ggplot(DF$career_time %>% 
-         filter(SubjectArea != "Multidisciplinary"), 
-       aes(Year, avg_career, color = sd_career)) +
+         filter(SubjectArea != "Multidisciplinary") %>% 
+         filter(num_papers >= 10), 
+       aes(Year, avg_career, color = SubjectArea)) +
   theme_classic() + 
-  geom_point(aes(size = num_papers)) +
-  facet_wrap(~SubjectArea) + 
+  geom_point(aes(size = sd_career)) +
+  # geom_point() + 
+  # facet_wrap(~SubjectArea) + 
   theme(legend.position = "bottom") + 
@@
   xlab("Year of Publication") + 
-  guides(color = "none") + 
-  scale_size_continuous(name = "Number Papers")
-```
-
--   To analyze trends over time, we will calculate the average career
-    length for each publication (i.e., average the author career length
-    to create one score for each paper) and run a regression analysis
-    using career length to predict year of publication. In order to show
-    variance between individuals, we calculate the standard deviation of
-    career length for each publication and run a regression analysis
-    using this variance representation to predict publication year.
-    These two variables will be used together.
--   Negative slopes would indicate more young scholars in later years
-    (i.e., lower average career length as time increases). Positive
-    slopes would indicate older scholars in later years (i.e., higher
-    average career length as time increases).
--   Negative slopes imply that variability decreases over the years, so
-    the average career length is more homogeneous. Positive slopes imply
-    that variability increases over the years, so the average career
-    length is varied across individuals (lots of different types of
-    scholars).
--   These analyses will be completed separately for each of the four
-    large subject areas.
-
-```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}
+  scale_color_brewer(palette = "Spectral", name = "Subject Area") +
+  guides(size = "none")  
+  #scale_size_continuous(name = "Number Papers")
+```
+
+```{r career-results, include = FALSE}
 
@@
   "estimate" = avg_b_values,
-  "type" = "M Coefficient",
+  "type" = "Coefficient",
   "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
@@
   graph_data$type, 
-  levels = c("M Coefficient", "SD Coefficient", "Effect Size")
-)
-
-ggplot(graph_data, aes(label, estimate)) + 
-  geom_point() +
-  geom_pointrange(aes(ymin = low, ymax = high)) +
-  theme_classic() + 
-  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
-  geom_hline(yintercept = 0) + 
-  coord_flip() + 
-  xlab("Subject Area") + 
-  ylab("")
-```
-
-***Institution***.
-
--   We will summarize the number of affiliation ids present in BTS
-    publications by subject area and visualize these results across
-    time. These visualizations will be presented separately for each of
-    the four subject areas.
-
-```{r total-aff}
-# updated
-affs <- 463876
-```
-
-The total number of unique affiliation across all papers was `r affs`.
-
-```{r fig-inst, include = TRUE, fig.cap="Number of unique institutions involved in big-team science papers across decades."}
-DF$inst_time$normalized <- DF$inst_time$unique / DF$inst_time$total * 100
-
-picture <- ggplot(DF$inst_time %>% 
-         filter(SubjectArea != "Multidisciplinary") %>% 
-         mutate(Decade = ifelse(Year < 1990, "1980s", 
-                         ifelse(Year < 2000, "1990s", 
-                                ifelse(Year < 2010, "2000s", 
-                                       ifelse(Year < 2020, "2010s", "2020s"))))), 
-       aes(Decade, `normalized`)) + 
-  #geom_point() + 
-  geom_violin() + 
-  theme_classic() + 
-  facet_wrap(~SubjectArea) + 
-  ylab("Percent of Unique Affiliations") + 
-  xlab("Decade")
-
-suppressWarnings(print(picture))
-```
-
-***Types of Publications***.
-
--   We will summarize the coded types of publications for individuals.
-
-```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
-#### try donut chart ####
-pub_types <- bind_rows(
-  DF$pub_types %>% mutate(type = "Big Team"), 
-  DF$normal_pub_type %>% mutate(type = "Normal")) %>% 
-    filter(!is.na(publication_type)) %>% 
-  filter(publication_type != "cb")
-
-ggplot(pub_types, aes(type, count, fill = publication_type)) + 
-    geom_bar(position="fill", stat="identity", color = "black") + 
-  theme_classic() +  
-  xlab("Author Type") + 
-  ylab("Percent of Paper Types") + 
-  theme(legend.position = "bottom") + 
-  scale_fill_discrete(name = "Publication Type")
-
-# can probably figure out how to combine these feasibly to make it readable
-# ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.
-```
-
-***Publication Metrics***.
-
--   We will report descriptive statistics on the total number of
-    publications and h-index for individuals overall.
-    -   Do this for each unique person and report averages
-    -   Do this for each publication and create an average for each
-        publication
-
-```{r pub-hindex}
-avg_pub_count_author	<- apa_num(38.368910766896065)
-std_pub_count_author <- apa_num(102.53740454680472)
-
-avg_pub_count_paper <- apa_num(162.50184385336053)
-sd_pub_count_paper <- apa_num(155.1665533053519)
-avg_SD_pub_count_paper <- apa_num(164.27249797983876)
-SD_SD_pub_count_paper <- apa_num(127.20989934008757)
-
-avg_HIndex <- apa_num(33.64589690529209)
-std_HIndex <- apa_num(127.33565834550778)
-med_HIndex <- apa_num(8.0)
-
-avg_of_avg_HIndex <- apa_num(198.87318851400775)
-std_of_avg_HIndex <- apa_num(248.7847084313958)
-avg_of_std_HIndex <- apa_num(211.7985924228093)
-std_of_std_HIndex <- apa_num(238.53141146314053)
-med_of_med_HIndex <- apa_num(68.0)
-```
-
-The average number of publications by authors on big team sciences
-papers is *M* = `r avg_pub_count_author` (*SD* =
-`r std_pub_count_author`). The publication counts were averaged across
-authors for each publication, and then these average publication counts
-were averaged across publications *M* = `r avg_pub_count_paper` (*SD* =
-`r sd_pub_count_paper`). The average variability (i.e., the average
-standard deviation with authors of a manuscript) with publication counts
-of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
-`r SD_SD_pub_count_paper`).
-
-The same process was completed with *h*-index for each author and
-publication. The average *h*-index for authors overall was *M* =
-`r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`). The
-average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD*
-= `r std_of_avg_HIndex`), and the variability of *h*-index across
-manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ =
-`r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).
-
--   Next, we will use the same analyses described in the career length
-    section to analyze trends over time. An increasing slope over time
-    indicates that individuals who are publishing more are more
-    represented in BTS over time (i.e., increasing numbers of scholars
-    with higher publication rates), while a negative slope indicates
-    more researchers with less publications.
--   A positive slope for standard deviation indicates increasing
-    variance over time (i.e., more diversity in the individual
-    publication rates), while a negative slope would indicate less
-    diversity in researchers over time. While publication rates do not
-    represent value as a researcher, they are often used in hiring and
-    promotion decisions, and we will use this variable as a proxy to
-    gauge the diversity in scholars represented in big teams.
--   We will separate these by each of the four subject areas.
-
-```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}
+  levels = c("Coefficient", "SD Coefficient", "Effect Size")
+)
+
+graph_data$analysis <- "Career"
+
+# ggplot(graph_data, aes(label, estimate)) + 
+#   geom_point() +
+#   geom_pointrange(aes(ymin = low, ymax = high)) +
+#   theme_classic() + 
+#   facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
+#   geom_hline(yintercept = 0) + 
+#   coord_flip() + 
+#   xlab("Subject Area") + 
+#   ylab("")
+```
+
+```{r pub-results, include = FALSE}
 
@@
 
-graph_data <- data.frame(
+graph_data_2 <- data.frame(
   "label" = label,
   "estimate" = avg_b_values,
-  "type" = "M Coefficient",
+  "type" = "Coefficient",
   "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
@@
 
-graph_data$type <- factor(
-  graph_data$type, 
-  levels = c("M Coefficient", "SD Coefficient", "Effect Size")
-)
-
-ggplot(graph_data, aes(label, estimate)) + 
-  geom_point() +
-  geom_pointrange(aes(ymin = low, ymax = high)) +
+graph_data_2$type <- factor(
+  graph_data_2$type, 
+  levels = c("Coefficient", "SD Coefficient", "Effect Size")
+)
+
+graph_data_2$analysis <- "Publication"
+
+# ggplot(graph_data, aes(label, estimate)) + 
+#   geom_point() +
+#   geom_pointrange(aes(ymin = low, ymax = high)) +
+#   theme_classic() + 
+#   facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
+#   geom_hline(yintercept = 0) + 
+#   coord_flip() + 
+#   xlab("Subject Area") + 
+#   ylab("")
+```
+
+```{r diversity-results, include = FALSE}
+
+label <- c("Physical", "Social", "Health", "Life")
+b_values <- c(0.002175, 0.033175, 0.016824, 0.008029)
+se_values <- c(0.002578, 0.006039, 0.001150, 0.001476)
+r2_values <- c(0.000006, 0.001542, 0.000708, 0.000170)
+sample_size <- total_num
+
+r2_low <- 1:length(r2_values)
+r2_high <- 1:length(r2_values)
+for (i in 1:length(r2_values)){
+  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
+  r2_low[i] <- temp$Lower.Conf.Limit.R2
+  r2_high[i] <- temp$Upper.Conf.Limit.R2
+}
+
+graph_data_3 <- data.frame(
+  "label" = label,
+  "estimate" = b_values,
+  "type" = "Coefficient",
+  "low" = b_values - qt(.025, sample_size, lower.tail = F)*se_values,
+  "high" = b_values + qt(.025, sample_size, lower.tail = F)*se_values) %>% 
+  bind_rows(
+    data.frame(  
+      "label" = label, 
+      "estimate" = r2_values,
+      "type" = "Effect Size",
+      "low" = r2_low,
+      "high" = r2_high)
+  )
+
+graph_data_3$type <- factor(
+  graph_data_3$type,
+  levels = c("Coefficient", "Effect Size")
+)
+
+graph_data_3$analysis <- "Regions"
+
+# ggplot(graph_data, aes(label, estimate)) + 
+#   geom_point() +
+#   geom_pointrange(aes(ymin = low, ymax = high)) +
+#   theme_classic() + 
+#   facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels_2))) + 
+#   geom_hline(yintercept = 0) + 
+#   coord_flip() + 
+#   xlab("Subject Area") + 
+#   ylab("")
+```
+
+```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity in region.
+The top figure represents all results together for comparison across analyses.
+The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.
+Non-significant results are indicated with NS on the plot."}
+graph_overall <- graph_data %>% 
+  bind_rows(graph_data_2) %>% 
+  bind_rows(graph_data_3) %>% 
+  mutate(type = factor(type, levels = c("Effect Size", "SD Coefficient", "Coefficient"))) %>% 
+  mutate(Estimate = estimate) %>% 
+  mutate(heat_label = ifelse(
+    low < .00001 & high > .00001, "NS", ""
+  ))
+
+heat_results <- ggplot(graph_overall, aes(label, type, fill = Estimate)) + 
+  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
+  coord_fixed() + 
+  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b$"))) + 
+  ylab("") + 
+  xlab("") + 
+  facet_wrap(~analysis) + 
   theme_classic() + 
-  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
-  geom_hline(yintercept = 0) + 
-  coord_flip() + 
-  xlab("Subject Area") + 
-  ylab("")
-```
+  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
+        legend.position = "right", 
+        legend.key.size = unit(.75, 'cm')) + 
+  scale_fill_distiller(palette = "Spectral") + 
+  geom_text(aes(label=heat_label))
+
+# heat_results
+
+heat_results_1 <- ggplot(graph_overall %>% 
+                           filter(analysis == "Career"), 
+                         aes(label, type, fill = Estimate)) + 
+  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
+  coord_fixed() + 
+  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b_M$"))) + 
+  ylab("") + 
+  xlab("") + 
+  theme_classic() + 
+  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
+        legend.position = "right") + 
+  scale_fill_distiller(palette = "RdBu") + 
+  ggtitle("Career")  + 
+  geom_text(aes(label=heat_label))
+
+heat_results_2 <- ggplot(graph_overall %>% 
+                           filter(analysis == "Publication"), 
+                         aes(label, type, fill = Estimate)) + 
+  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
+  coord_fixed() + 
+  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b_M$"))) + 
+  ylab("") + 
+  xlab("") + 
+  theme_classic() + 
+  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
+        legend.position = "right") + 
+  scale_fill_distiller(palette = "PuOr") + 
+  ggtitle("Publication") + 
+  geom_text(aes(label=heat_label))
+
+heat_results_3 <- ggplot(graph_overall %>% 
+                           filter(analysis == "Regions"), 
+                         aes(label, type, fill = Estimate)) + 
+  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
+  coord_fixed() + 
+  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b$"))) + 
+  ylab("") + 
+  xlab("") + 
+  theme_classic() + 
+  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
+        legend.position = "right") + 
+  scale_fill_distiller(palette = "PiYG") +
+  ggtitle("Regions") + 
+  geom_text(aes(label=heat_label))
+
+layout <- "
+AAA
+BCD
+"
+suppressWarnings(heat_results + 
+  heat_results_1 + heat_results_2 + heat_results_3 + 
+  plot_layout(design = layout))
+```
+
+***Institution***.
+
+```{r total-aff}
+# updated
+affs <- 463876
+```
+
+The total number of unique affiliation across all papers was `r affs`.
+
+***Publication Metrics***.
+
+-   We will report descriptive statistics on the total number of
+    publications and h-index for individuals overall.
+    -   Do this for each unique person and report averages
+    -   Do this for each publication and create an average for each
+        publication
+
+```{r pub-hindex}
+avg_pub_count_author	<- apa_num(38.368910766896065)
+std_pub_count_author <- apa_num(102.53740454680472)
+
+avg_pub_count_paper <- apa_num(162.50184385336053)
+sd_pub_count_paper <- apa_num(155.1665533053519)
+avg_SD_pub_count_paper <- apa_num(164.27249797983876)
+SD_SD_pub_count_paper <- apa_num(127.20989934008757)
+
+avg_HIndex <- apa_num(33.64589690529209)
+std_HIndex <- apa_num(127.33565834550778)
+med_HIndex <- apa_num(8.0)
+
+avg_of_avg_HIndex <- apa_num(198.87318851400775)
+std_of_avg_HIndex <- apa_num(248.7847084313958)
+avg_of_std_HIndex <- apa_num(211.7985924228093)
+std_of_std_HIndex <- apa_num(238.53141146314053)
+med_of_med_HIndex <- apa_num(68.0)
+```
+
+The average number of publications by authors on big team sciences
+papers is *M* = `r avg_pub_count_author` (*SD* =
+`r std_pub_count_author`). The publication counts were averaged across
+authors for each publication, and then these average publication counts
+were averaged across publications *M* = `r avg_pub_count_paper` (*SD* =
+`r sd_pub_count_paper`). The average variability (i.e., the average
+standard deviation with authors of a manuscript) with publication counts
+of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
+`r SD_SD_pub_count_paper`).
+
+The same process was completed with *h*-index for each author and
+publication. The average *h*-index for authors overall was *M* =
+`r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`). The
+average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD*
+= `r std_of_avg_HIndex`), and the variability of *h*-index across
+manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ =
+`r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).
+
+-   Next, we will use the same analyses described in the career length
+    section to analyze trends over time. An increasing slope over time
+    indicates that individuals who are publishing more are more
+    represented in BTS over time (i.e., increasing numbers of scholars
+    with higher publication rates), while a negative slope indicates
+    more researchers with less publications.
+-   A positive slope for standard deviation indicates increasing
+    variance over time (i.e., more diversity in the individual
+    publication rates), while a negative slope would indicate less
+    diversity in researchers over time. While publication rates do not
+    represent value as a researcher, they are often used in hiring and
+    promotion decisions, and we will use this variable as a proxy to
+    gauge the diversity in scholars represented in big teams.
+-   We will separate these by each of the four subject areas.
 
@@
     diversity would be represented by a negative slope.
-
-```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}
-
-label <- c("Physical", "Social", "Health", "Life")
-b_values <- c(0.002175, 0.033175, 0.016824, 0.008029)
-se_values <- c(0.002578, 0.006039, 0.001150, 0.001476)
-r2_values <- c(0.000006, 0.001542, 0.000708, 0.000170)
-sample_size <- total_num
-
-r2_low <- 1:length(r2_values)
-r2_high <- 1:length(r2_values)
-for (i in 1:length(r2_values)){
-  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
-  r2_low[i] <- temp$Lower.Conf.Limit.R2
-  r2_high[i] <- temp$Upper.Conf.Limit.R2
-}
-
-graph_data <- data.frame(
-  "label" = label,
-  "estimate" = b_values,
-  "type" = "Coefficient",
-  "low" = b_values - qt(.025, sample_size, lower.tail = F)*se_values,
-  "high" = b_values + qt(.025, sample_size, lower.tail = F)*se_values) %>% 
-  bind_rows(
-    data.frame(  
-      "label" = label, 
-      "estimate" = r2_values,
-      "type" = "Effect Size",
-      "low" = r2_low,
-      "high" = r2_high)
-  )
-
-# graph_data$type <- factor(
-#   graph_data$type, 
-#   levels = c("Coefficient", "Effect Size")
-# )
-
-ggplot(graph_data, aes(label, estimate)) + 
-  geom_point() +
-  geom_pointrange(aes(ymin = low, ymax = high)) +
-  theme_classic() + 
-  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels_2))) + 
-  geom_hline(yintercept = 0) + 
-  coord_flip() + 
-  xlab("Subject Area") + 
-  ylab("")
-```
 
@@
 
+ggplot(large_effect %>% 
+         arrange(v) %>% 
+         mutate(count = 1:nrow(large_effect)),
+       aes(count, v)) + 
+  geom_point(aes(size = people)) +
+  geom_linerange(aes(ymin = low, ymax = high), alpha = .5) +
+  theme_classic()  
+  #ylab(TeX("Raw Effect: $t$ Log RT")) + 
+  #xlab("Different Processing Scenarios") + 
+  # geom_hline(yintercept = 0) + 
+  #theme(text = element_text(size = 8))
+
 DF_decade <- DF$large_first_gp %>% 
@@
 ```
+
+\newpage
+
+# (APPENDIX) Appendix {-}
+
+```{r child = "appendix.Rmd"}
+```

### 2023-08-09 manuscript_scopus.tex
moving things around

@@
 \documentclass[
-  man]{apa7}
+  man,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\keywords{big team, science, authorship, credit\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
+\keywords{big team, science, authorship, credit}
 \usepackage{lineno}
@@
 \usepackage{csquotes}
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\typesectitle}}
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-
 \ifLuaTeX
@@
 \abstract{%
-This paper will examine the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions.
+This paper examined the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions.
 As interest in BTS increases, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
-The types of publication outlets, number of publications, and subject areas of publication will be presented to summarize the publications in BTS.
+The types of publication outlets, number of publications, and subject areas of publication are presented to summarize the publications in BTS.
 Information about authors included in BTS will be presented including career length, numbers of publications/impact variables, education, and affiliation.
 Last, we will explore the representation of geopolitical regions by examining affiliation location to explore the impact of BTS on the de-WEIRD movement to diversify researcher representation.
+REWRITE THIS
 }
@@
 science, the current interest of ``big team science'' is increasing
-(Coles et al., 2022; Forscher et al., 2020; N. Stewart et al., 2017). Big team science projects
+(Coles, Hamlin, Sullivan, Parker, \& Altschul, 2022; Forscher et al., 2020; N. Stewart, Chandler, \& Paolacci, 2017). Big team science projects
 and/or organizations utilize and run on large-scale collaboration to
@@
 research, and 2) increasing interest in reproducibility, replication,
-and generalizability (Maxwell et al., 2015; Nelson et al., 2018; Zwaan et al., 2018).
+and generalizability (Maxwell, Lau, \& Howard, 2015; Nelson, Simmons, \& Simonsohn, 2018; Zwaan, Etz, Lucas, \& Donnellan, 2018).
 Technological advances have provided easier ways to collaborate with
@@
 when2meet, etc.). The credibility movement seems to suggest that by
-having both collaborations that span across the globe and subfield of
-psychology, age groups, and education levels should help to drive
-psychological science in the path of better materials, reliability,
-generalizability and more robust sample size in a study
-(Auspurg \& Brüderl, 2021; LeBel et al., 2018; Nosek \& Lakens, 2014a).
+having both collaborations that span across the globe and subfields of
+research areas, age groups, and education levels should help to drive science in the path of better materials, reliability,
+generalizability and more robust sample sizes (when necessary) in a study
+(Auspurg \& Brüderl, 2021; LeBel, McCarthy, Earp, Elson, \& Vanpaemel, 2018; Brian A. Nosek \& Lakens, 2014a).
 
 The credibility movement was originally defined by a focus on large
-scale replications using in collaborative environments (Vazire et al., 2022).
-Generally, the movement has been driven by early career researchers
+scale replications using in collaborative environments (Vazire, Schiavone, \& Bottesini, 2022).
+Generally, the movement appears to have been driven by early career researchers
 (i.e., those who are within five years of their first appointment)
@@
 Science Collaboration (Open Science Collaboration, 2015), Many Labs
-Collaborations (Buttrick et al., 2020; Ebersole et al., 2016, 2020; for example, Klein et al., 2018; Klein et al., 2022; Mathur et al., 2020; Skorb et al., 2020) or the first papers
+Collaborations (Buttrick et al., 2020; Ebersole et al., 2016, 2020; Richard A.
+Klein et al., 2022; for example, Richard A.
+Klein et al., 2018; Mathur et al., 2020; Skorb et al., 2020) or the first papers
 from the Psychological Science Accelerator (Bago et al., 2022; Dorison et al., 2022; Jones et al., 2021; Legate et al., 2022; Moshontz et al., 2018; Wang et al., 2021). Generally, the
@@
 ``novel'' or new results which led to rejection of replication manuscripts
-and publication bias (Franco et al., 2014; Hubbard \& Armstrong, 1997; Nosek et al., 2012), the
+and publication bias (Franco, Malhotra, \& Simonovits, 2014; Hubbard \& Armstrong, 1997; Brian A. Nosek, Spies, \& Motyl, 2012), the
 ``failure'' to replicate was often placed on the replication team as ``bad
 science'' rather than a careful consideration of publication biases and
-(potential) questionable research practices (Ioannidis, 2015; Klein et al., 2022; Maxwell et al., 2015), and why should someone want to spend time and
+(potential) questionable research practices (Ioannidis, 2015; Richard A. Klein et al., 2022; Maxwell et al., 2015), and why should someone want to spend time and
 resources on an answer we already ``know'' (Isager et al., 2021a, 2021b)?
@@
 with the meta-scientific publications focusing on researcher practices
-and incentive structures (John et al., 2012; Silberzahn et al., 2018) led to a
+and incentive structures (John, Loewenstein, \& Prelec, 2012; Silberzahn et al., 2018) led to a
 change in journal guidelines and incentives for researchers interested
-in participating in large-scale replication studies (Grahe, 2014; Kidwell et al., 2016; Mayo-Wilson et al., 2021; Nosek et al., 2015). For example, the support
+in participating in large-scale replication studies (Grahe, 2014; Kidwell et al., 2016; Mayo-Wilson et al., 2021; B. A. Nosek et al., 2015). For example, the support
 for Registered Reports, papers accepted before the data has been
-collected (Nosek \& Lakens, 2014b; S. Stewart et al., 2020), and entire sub-sections of
-journals devoted to only replication studies (e.g., \emph{Nature, Royal
-Society Open Science, Advances in Methods and Practices in Psychological
-Science}) has allowed researchers to invest in projects that they know
+collected (Brian A. Nosek \& Lakens, 2014b; S. Stewart et al., 2020), and entire sub-sections of
+journals devoted to only replication studies (e.g., \emph{Nature, Royal Society Open Science, Advances in Methods and Practices in Psychological Science}) has allowed researchers to invest in projects that they know
 should be published when the project is complete. Further, the
-implementation of the Transparency and Openness Guidelines (Nosek et al., 2015)
-and the Contributor Role Taxonomy (CRediT) system (Allen et al., 2019) have
+implementation of the Transparency and Openness Guidelines (B. A. Nosek et al., 2015)
+and the Contributor Role Taxonomy (CRediT) system (Allen, O'Connell, \& Kiermer, 2019) have
 pushed journals and researchers to promote more open, inclusive
@@
 diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
-Rich, and Democratic) scientific research (Henrich et al., 2010; Newson et al., 2021; Rad et al., 2018) by improving representation in research samples. Like the
-large-scale studies in Physics ({``A Philosophical Case for Big Physics,''} 2021; Castelnovo et al., 2018) and
-Biology (Collins et al., 2003), the social sciences struggle to represent the
+Rich, and Democratic) scientific research (Henrich, Heine, \& Norenzayan, 2010; Newson, Buhrmester, Xygalatas, \& Whitehouse, 2021; Rad, Martingano, \& Ginges, 2018) by improving representation in research samples.
+Like the
+large-scale studies in Physics ({``A Philosophical Case for Big Physics,''} 2021; Castelnovo, Florio, Forte, Rossi, \& Sirtori, 2018) and
+Biology (Collins, Morgan, \& Patrinos, 2003), the social sciences struggle to represent the
 breadth of humanity across both researcher and population
@@
 Therefore, the goal of this manuscript is to examine the \emph{people}
-involved in BTS projects. We specifically expect to examine ICSR's
-Research Themes of inclusivity, research careers, and research
-globalization. As we examine these themes, it will bring new knowledge
-of how BTS projects impact each theme and field of study. We see an
-increase in interest and publications in BTS but we do not yet know if
+involved in BTS projects. We specifically examined the themes of inclusivity, research careers, and research globalization. We see an
+increasing interest and number of publications in BTS but we do not yet know if
 this uptick in large-scale projects has diversified the \emph{people}
@@
 
-\hypertarget{potential-outlets}{%
-\section{Potential Outlets}\label{potential-outlets}}
-
-We will aim for high impact broad scope journals such as \emph{Science},
-\emph{Nature} or \emph{Nature Human Behaviour}. Other journals would include
-review publications within psychology to compare the social sciences to
-other sciences: \emph{Perspectives in Psychological Science}, \emph{Psychological
-Bulletin}, \emph{Psychological Review}, or \emph{Current Directions in
-Psychological Science}.
-
 \hypertarget{research-questions}{%
@@
 
-For each of these research questions, we will examine the overall
-results of all big team research projects, and examine for change in
-result trends across years of publication. Below we detail our methods
-and the ICSR/Scopus data to answer these questions, along with examples
-of the statistical results we expect to report in the manuscript. We
-began this project with data using Google Scholar and ORCID information.
-These sources were severely limited in their scope and breadth, as they
-are often curated with automatic processes or self-entered data, and we
-believe that access to Scopus and ICSR would allow us to accurately
-portray the BTS movement and its impact on diversity across many fields.
-The novelty of this project is that it would focus on all of published
-works, rather than a specific subfield (like Psychology) and give a lens
-into global representation in science that would otherwise not be
-achieved with open-source databases.
+This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr}) but then was updated with access to the Scopus database for a broader picture of BTS projects (\url{https://osf.io/fheun}).
+All materials and code can be found on our OSF page: \url{https://osf.io/cgx6u/} or corresponding GitHub archive: \url{https://github.com/doomlab/big_team_who}.
 
@@
 
-We have defined \textbf{BTS publications} as publications with at least 10
-authors at 10 different institutions that were published in
-peer-reviewed journals or had posted a full paper pre-print. We will use
-data from 1970 and forward in the publications (\texttt{ani}) database, as it
+We have defined BTS publications as publications with at least ten
+authors at ten different institutions that were published in
+peer-reviewed journals or had posted a full paper pre-print. We used
+data from 1970 and forward in the Scopus database, as it
 is noted online that this time period includes cited references for
 calculation of several of our variables described below. We will analyze
-our results based on the big four subject areas: Physical Sciences,
+our results based on four subject areas present in the Scopus database: Physical Sciences,
 Health Sciences, Social Sciences, and Life Sciences. We filtered the
@@
 
-Using these criteria, we will extract the following information for
-publication sources: the name of the publication (source title), subject
-area (both the large four subject areas and the smaller four digit all
-science journal classification ASJC codes). We will examine journal
-impact using the Source Normalized Impact per Paper from the journal
-(\texttt{sources}) database.
+We extracted the following information for publication sources: the name of the publication (source title), subject area (both the large four subject areas and the smaller four digit all science journal classification {[}ASJC{]} code), and the journal
+impact using the Source Normalized Impact per Paper (SNIP).
 
@@
 
-The author list will then be extracted from each publication. Next, we
-will use the author (\texttt{au}) and affiliation (\texttt{af}) array to curate a list
-of all publications and author information included in BTS papers. We
-will use these two arrays with the publication array to calculate the
-variables described below.
-
-\textbf{\emph{Career Length}}. Career length for each author will be defined as
-the year of the first publication listed for each author.
-
-\textbf{\emph{Institution and Geopolitical Region}} . We will use the affiliation
+The author list was extracted from each publication.
+Next, we used the author and affiliation arrays to curate a list of all publications and author information included in BTS papers to calculate the variables described below.
+
+\textbf{\emph{Career Length}}. Career length for each author was defined as
+the year of the first publication minus the current year listed for each author.
+
+\textbf{\emph{Institution and Geopolitical Region}}. We used the affiliation
 ids and country to gather information about the places of education
-and/or employment for authors. Country will likely be binned into United Nation Region, Sub-Region, or smaller clusters for analyses.
-
-\textbf{\emph{Education}}. We will also collect degree information from the author table.
-
-\textbf{\emph{Types of Publications}}. We will gather information from the
-publication type variable for each author publication to present
+and/or employment for authors. Geopolitical region was created by binning these codes into United Nation Regions.
+
+\textbf{\emph{Education}}. We collected degree information from the author table.
+
+\textbf{\emph{Types of Publications}}. We took information from the
+publication type variable for each author's publications to present
 information about the types of papers BTS authors publish.
 
-\textbf{\emph{Publication Metrics}}. For each author, we will calculate the total
+\textbf{\emph{Publication Metrics}}. For each author, we calculated the total
 number of publications, and the h-index. The h-index represents the
@@
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+We used the 95\% confidence interval to make decisions on predictor or effect size differences from zero.
+The confidence interval that does not include zero would be considered different from zero (to four decimal places).
+We made no directional predictions.
 
 \hypertarget{rq1-publisher-information.-1}{%
-\subsubsection{RQ1: Publisher Information.}\label{rq1-publisher-information.-1}}
-
-To present results on this research question, we will analyze:
-
-\begin{itemize}
-\tightlist
-\item
-  Number of articles for inclusion: total, separated by four subject
-  areas, presenting graphics of the number of publication across time
-  total
-\end{itemize}
+\subsection{RQ1: Publisher Information.}\label{rq1-publisher-information.-1}}
 
@@
 307514 Life Sciences articles. Articles could be classified into
-multiple categories. Figure X shows the number of articles published across time for each of the four large subject areas.
+multiple categories. Figure \ref{fig:fig-pub-time} shows the number of articles published across time for each of the four large subject areas.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Number of distinct journals within each of the four subject areas
-\end{itemize}
-
 \emph{Number of journals}. The number of distinct journals big team science articles were published
@@
 Sciences. The descriptive statistics for the Source Normalized Impact
-per Paper is presented in Table X. For comparison, the SNIP descriptive
-statistics for all papers is shown in Table X.
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab-snip}Big-Team Science SNIP Values}
-
-\begin{tabular}{llllll}
-\toprule
-Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
-\midrule
-Health Sciences & 2.36 & 3.59 & 0.00 & 1.58 & 173.93\\
-Physical Sciences & 1.57 & 1.17 & 0.00 & 1.27 & 30.40\\
-Social Sciences & 1.94 & 1.72 & 0.00 & 1.52 & 30.40\\
-Life Sciences & 2.02 & 1.60 & 0.00 & 1.51 & 19.07\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab-snip-all}All Journal Articles SNIP Values}
-
-\begin{tabular}{llllll}
-\toprule
-Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
-\midrule
-Health Sciences & 1.45 & 2.87 & 0.00 & 1.15 & 173.93\\
-Physical Sciences & 1.08 & 0.77 & 0.00 & 0.97 & 30.40\\
-Social Sciences & 1.32 & 1.03 & 0.00 & 1.15 & 30.40\\
-Life Sciences & 1.19 & 0.86 & 0.00 & 1.06 & 19.07\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
+per Paper is presented the supplemental materials with a comparison for all papers.
 
 \hypertarget{rq2-publication-information.-1}{%
-\subsubsection{RQ2: Publication Information.}\label{rq2-publication-information.-1}}
-
-For each publication, we will examine:
-
-\begin{itemize}
-\tightlist
-\item
-  The totals of the number of articles published within the smaller
-  subject area classifications. We will visualize these differences to show the areas of interest for each of the four large subject areas.
-\end{itemize}
+\subsection{RQ2: Publication Information.}\label{rq2-publication-information.-1}}
+
+Publication interest area was summarized by the four large subject areas creating a word cloud plot of the total number of publications within the ASJCs.
+Figure @\ref(fig:fig-clouds) displays that the health sciences tends to publish within medicine and oncology, with a corresponding focus of cancer research and genetics for the life sciences.
+The physical sciences is mostly dominated by physics research, chemistry, and ecology.
+The BTS publications in the social sciences are mostly within psychology, education, and health.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  The keywords present in the publications data overall to identify
-  trends and common themes in the publications for the four subject
-  areas using visualizations (wordclouds) to depict the common
-  keywords.
-\end{itemize}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-keywords-1.pdf}
-\caption{\label{fig:fig-keywords}Keyword Analysis for Each of the Four Subject Areas.}
-\end{figure}
-
 \hypertarget{rq3-authors.}{%
-\subsubsection{RQ3: Authors.}\label{rq3-authors.}}
-
-We will first present:
-
-\begin{itemize}
-\tightlist
-\item
-  The total number of unique authors
-\end{itemize}
-
-The total number of unique authors across all publications was
-510334.
-
-\begin{itemize}
-\tightlist
-\item
-  Statistics (mean, standard deviation, minimum, maximum, median) on
-  the number of authors included on publications.
-\end{itemize}
-
-The mean number of authors per publication was \emph{M} = 49.31
-(\emph{SD} = 212.98, \emph{Med} = 18) with a range of
-10 to 5568.
-
-\begin{itemize}
-\tightlist
-\item
-  We will present visualizations of these results across time.
-\end{itemize}
+\subsection{RQ3: Authors.}\label{rq3-authors.}}
+
+The total number of unique authors across all publications was 510334.
+The mean number of authors per publication was \emph{M} = 49.31 (\emph{SD} = 212.98, \emph{Med} = 18) with a range of 10 to 5568.
+The median and average number of authors by subject area are displayed in Figure \ref{fig:fig-author-year}.
+In general, the average and median number of authors increased over time, with the exception of the skew in the physical sciences.
+Interestingly, the effect in the physical sciences appears to be declining toward the general trends seen in other areas in the last few decades.
 
@@
 \caption{\label{fig:fig-author-year}Number of authors included on big-team science papers per year by subject area.
-Colored dots indicate the mean number of authors, while the black dots represent the median number of authors.
-The size of the black dots indicate the number of papers in that year.}
+Given the large skew in the data, the left panel presents the median number of authors per manuscript, and the right panel presents the average number of authors per manuscript by year.}
 \end{figure}
 
-We will use the 95\% confidence interval to make all claims of predictors
-or effects different zero. The confidence interval that does not include
-zero would be considered different from zero (to four decimal places).
-We make no directional predictions.
-
 \textbf{\emph{Career Length}}.
 
-\begin{itemize}
-\tightlist
-\item
-  We will create a visualization of the trend and variance of
-  researcher career length across publication years.
-\end{itemize}
+Figure \ref{fig:fig-career} portrays the average career length for authors involved in BTS publications across years.
+Career length was defined as the year of first publication minus the current year, and higher numbers mean longer careers.
+To analyze trends over time, we calculated the average career length for each publication (i.e., average author career lengths to create one score for each paper) and analyzed a regression analysis using career length to predict year of publication.
+In order to show variance between individuals, we calculated the standard deviation of career length for each publication and used variance as an additional predictor.
+
+Negative career length slopes would indicate more young scholars in later years (i.e., lower average career length as time increases).
+Positive career length slopes would indicate older scholars in later years (i.e., higher average career length as time increases).
+Negative career variance slopes imply that variability decreases over the years, so the average career length is more homogeneous.
+Positive career length slopes imply that variability increases over the years, so the average career length is varied across individuals (i.e., different stages of scholars).
+Figure \ref{fig:fig-heatmap} displays the results for all regression analyses to compare coefficient strength across and within hypothesis.
+
+All values for this analyses were different from zero.
+The slopes for the average career length were negative for all four subject areas, indicating a trend toward younger scientist involvement over time for each area, with the strongest effect in the Physical sciences.
+The coefficient for variability in career length was also negative for each of the four subject areas with the highest in the Physical sciences and lowest in the Life Sciences.
+This result indicates a decrease in the variability of career lengths over time, likely from two sources: 1) more publications with more authors, thus, lowering variance estimations, and 2) more young scholars overall.
+The effect sizes for this analysis were surprisingly large ranging from \(R^2\) to .25 to .47.
+All values and their confidence intervals can be found on our OSF page.
 
@@
 \caption{\label{fig:fig-career}Average career length for big-team science authors.
-Larger dots indicate more papers for each estimation.
-Lighter colored dots mean less variability in author career length, while darker dots mean more variability in career length.}
+Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year.}
 \end{figure}
 
-\begin{itemize}
-\tightlist
-\item
-  To analyze trends over time, we will calculate the average career
-  length for each publication (i.e., average the author career length
-  to create one score for each paper) and run a regression analysis
-  using career length to predict year of publication. In order to show
-  variance between individuals, we calculate the standard deviation of
-  career length for each publication and run a regression analysis
-  using this variance representation to predict publication year.
-  These two variables will be used together.
-\item
-  Negative slopes would indicate more young scholars in later years
-  (i.e., lower average career length as time increases). Positive
-  slopes would indicate older scholars in later years (i.e., higher
-  average career length as time increases).
-\item
-  Negative slopes imply that variability decreases over the years, so
-  the average career length is more homogeneous. Positive slopes imply
-  that variability increases over the years, so the average career
-  length is varied across individuals (lots of different types of
-  scholars).
-\item
-  These analyses will be completed separately for each of the four
-  large subject areas.
-\end{itemize}
+\begin{verbatim}
+## Warning in width_strings[fixed_areas[[i]]$cols] == "-1null" && length(w) == :
+## 'length(x) = 3 > 1' in coercion to 'logical(1)'
+\end{verbatim}
 
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-career-results-1.pdf}
-\caption{\label{fig:fig-career-results}Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication.}
+\includegraphics{manuscript_scopus_files/figure-latex/fig-heatmap-1.pdf}
+\caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity in region.
+The top figure represents all results together for comparison across analyses.
+The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.
+Non-significant results are indicated with NS on the plot.}
 \end{figure}
@@
 
-\begin{itemize}
-\tightlist
-\item
-  We will summarize the number of affiliation ids present in BTS
-  publications by subject area and visualize these results across
-  time. These visualizations will be presented separately for each of
-  the four subject areas.
-\end{itemize}
-
 The total number of unique affiliation across all papers was 463876.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-inst-1.pdf}
-\caption{\label{fig:fig-inst}Number of unique institutions involved in big-team science papers across decades.}
-\end{figure}
-
-\textbf{\emph{Types of Publications}}.
-
-\begin{itemize}
-\tightlist
-\item
-  We will summarize the coded types of publications for individuals.
-\end{itemize}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-types-1.pdf}
-\caption{\label{fig:fig-pub-types}Types of publications for big-team science and all authors.}
-\end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-results-1.pdf}
-\caption{\label{fig:fig-pub-results}Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication.}
-\end{figure}
-
 \textbf{\emph{Geopolitical Regions}}.
@@
   diversity would be represented by a negative slope.
-\end{itemize}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-diversity-1.pdf}
-\caption{\label{fig:fig-diversity}Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size.}
-\end{figure}
-
-\begin{itemize}
-\tightlist
 \item
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bago2022}{}}%
-Bago, B., Kovacs, M., Protzko, J., Nagy, T., Kekecs, Z., Palfi, B., Adamkovic, M., Adamus, S., Albalooshi, S., Albayrak-Aydemir, N., Alfian, I.
-N., Alper, S., Alvarez-Solas, S., Alves, S.
-G., Amaya, S., Andresen, P.
-K., Anjum, G., Ansari, D., Arriaga, P., \ldots{} Aczel, B.
+Bago, B., Kovacs, M., Protzko, J., Nagy, T., Kekecs, Z., Palfi, B., \ldots{} Aczel, B.
 (2022).
@@
 E., Brühlmann, F., Claypool, H.
-M., Hüffmeier, J., Kovacs, M., Schuepfer, K., Szecsi, P., Szuts, A., Szöke, O., Thomae, M., Torka, A.-K., Walker, R.
-J., \& Wood, M.
+M., \ldots{} Wood, M.
 J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dorison2022}{}}%
-Dorison, C., Lerner, J., Heller, B., Rothman, A., Kawachi, I., Wang, K., Rees, V., Gill, B., Gibbs, N., Ebersole, C., Vally, Z., Tajchman, Z., Zsido, A., Zrimsek, M., Chen, Z., Ziano, I., Gialitaki, Z., Ceary, C., Jang, Y., \ldots{} Coles, N.
+Dorison, C., Lerner, J., Heller, B., Rothman, A., Kawachi, I., Wang, K., \ldots{} Coles, N.
 (2022).
@@
 M., Banks, J.
-B., Baranski, E., Bernstein, M.
-J., Bonfiglio, D.
-B.
-V., Boucher, L., Brown, E.
-R., Budiman, N.
-I., Cairo, A.
-H., Capaldi, C.
-A., Chartier, C.
-R., Chung, J.
-M., Cicero, D.
-C., Coleman, J.
-A., Conway, J.
-G., \ldots{} Nosek, B.
+B., \ldots{} Nosek, B.
 A.
@@
 R., Chartier, C.
-R., Corker, K.
-S., Corley, M., Hartshorne, J.
-K., IJzerman, H., Lazarević, L.
-B., Rabagliati, H., Ropovik, I., Aczel, B., Aeschbach, L.
-F., Andrighetto, L., Arnal, J.
-D., Arrow, H., Babincak, P., \ldots{} Nosek, B.
+R., \ldots{} Nosek, B.
 A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ioannidis2015}{}}%
-Ioannidis, J. P. A. (2015). Failure to replicate: Sound the alarm. \emph{Cerebrum: The Dana Forum on Brain Science}, \emph{2015}. \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4938249/}
+Ioannidis, J.
+P.
+A.
+(2015).
+Failure to replicate: Sound the alarm.
+\emph{Cerebrum: The Dana Forum on Brain Science}, \emph{2015}.
+Retrieved from \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4938249/}
 
@@
 J., DeSoto, K.
-A., Giner-Sorolla, R., Krueger, J.
-I., Perugini, M., Ropovik, I., van 't Veer, A.
-E., Vranka, M., \& Lakens, D.
+A., Giner-Sorolla, R., \ldots{} Lakens, D.
 (2021a).
@@
 J., DeSoto, K.
-A., Giner-Sorolla, R., Krueger, J.
-I., Perugini, M., Ropovik, I., van 't Veer, A.
-E., Vranka, M., \& Lakens, D.
+A., Giner-Sorolla, R., \ldots{} Lakens, D.
 (2021b).
@@
 T., Antfolk, J., Arinze, N.
-C., Ndukaihe, I.
-L.
-G., Bloxsom, N.
-G., Lewis, S.
-C., Foroni, F., Willis, M.
-L., Cubillas, C.
-P., Vadillo, M.
-A., Turiegano, E., Gilead, M., Simchon, A., Saribay, S.
-A., Owsley, N.
-C., Jang, C., \ldots{} Coles, N.
+C., \ldots{} Coles, N.
 A.
@@
 B., Baranski, E., Hardwicke, T.
-E., Piechowski, S., Falkenberg, L.-S., Kennett, C., Slowik, A., Sonnleitner, C., Hess-Holden, C., Errington, T.
-M., Fiedler, S., \& Nosek, B.
+E., Piechowski, S., Falkenberg, L.-S., \ldots{} Nosek, B.
 A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
-Klein, R.
-A., Cook, C.
+Klein, Richard A., Cook, C.
 L., Ebersole, C.
 R., Vitiello, C., Nosek, B.
-A., Hilgard, J., Ahn, P.
-H., Brady, A.
-J., Chartier, C.
-R., Christopherson, C.
-D., Clay, S., Collisson, B., Crawford, J.
-T., Cromar, R., Gardiner, G., Gosnell, C.
-L., Grahe, J., Hall, C., Howard, I., \ldots{} Ratliff, K.
+A., Hilgard, J., \ldots{} Ratliff, K.
 A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
-Klein, R.
-A., Vianello, M., Hasselman, F., Adams, B.
+Klein, Richard A., Vianello, M., Hasselman, F., Adams, B.
 G., Adams, R.
-B., Alper, S., Aveyard, M., Axt, J.
-R., Babalola, M.
-T., Bahník, Š., Batra, R., Berkics, M., Bernstein, M.
-J., Berry, D.
-R., Bialobrzeska, O., Binan, E.
-D., Bocian, K., Brandt, M.
-J., Busching, R., \ldots{} Nosek, B.
+B., Alper, S., \ldots{} Nosek, B.
 A.
@@
 Legate, N., Nguyen, T., Weinstein, N., Moller, A., Legault, L., Maniaci, M.
-R., Ebersole, C.
-R., Adamkovic, M., Adetula, D.
-G.
-A., Agesin, B.
-B., Ahlgren, L., Akkas, H., Almeida, I., Anjum, G., Antoniadi, M., Arinze, A.
-I., Arvanitis, A., Rana, K., Badalyan, V., \ldots{} Primbs, M.
+R., \ldots{} Primbs, M.
 (2022).
@@
 M., Ebersole, C.
-R., Falcão, F., Ashbaugh, K., Hilliard, R.
-A., Jern, A., Kellier, D.
-J., Kessinger, G., Kolb, V.
-S., Kovacs, M., Lage, C.
-A., Langford, E.
-V., Lins, S., Manfredi, D., Meyet, V., \ldots{} Frank, M.
+R., \ldots{} Frank, M.
 C.
@@
 L., Forscher, P.
-S., Grahe, J.
-E., McCarthy, R.
-J., Musser, E.
-D., Antfolk, J., Castille, C.
-M., Evans, T.
-R., Fiedler, S., Flake, J.
-K., Forero, D.
-A., Janssen, S.
-M.
-J., Keene, J.
-R., Protzko, J., Aczel, B., \ldots{} Chartier, C.
+S., \ldots{} Chartier, C.
 R.
@@
 D., Breckler, S.
-J., Buck, S., Chambers, C.
-D., Chin, G., Christensen, G., Contestabile, M., Dafoe, A., Eich, E., Freese, J., Glennerster, R., Goroff, D., Green, D.
-P., Hesse, B., Humphreys, M., \ldots{} Yarkoni, T.
+J., \ldots{} Yarkoni, T.
 (2015).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
-Nosek, B. A., \& Lakens, D. (2014a). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137141.
+Nosek, Brian A., \& Lakens, D. (2014a). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137141.
 
 \leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
-Nosek, B.
-A., \& Lakens, D.
+Nosek, Brian A., \& Lakens, D.
 (2014b).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-nosek2012}{}}%
-Nosek, B.
-A., Spies, J.
+Nosek, Brian A., Spies, J.
 R., \& Motyl, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oed2016}{}}%
-OED. (2016). \emph{Collaboration} (Vol. 3). Oxford University.
+OED. (2016). \emph{Collaboration}. Oxford: Oxford University.
 
@@
 L., Martin, D.
-P., Anselmi, P., Aust, F., Awtrey, E., Bahník, Š., Bai, F., Bannard, C., Bonnier, E., \& others.
+P., Anselmi, P., Aust, F., Awtrey, E., \ldots{} others.
 (2018).
@@
 Skorb, L., Aczel, B., Bakos, B.
-E., Feinberg, L., Hałasa, E., Kauff, M., Kovacs, M., Krasuska, K., Kuchno, K., Manfredi, D., Montealegre, A., Pękala, E., Pieńkosz, D., Ravid, J., Rentzsch, K., Szaszi, B., Schulz-Hardt, S., Sioma, B., Szecsi, P., \ldots{} Hartshorne, J.
+E., Feinberg, L., Hałasa, E., Kauff, M., \ldots{} Hartshorne, J.
 K.
@@
 Stewart, S., Rinke, E.
-M., McGarrigle, R., Lynott, D., Lunny, C., Lautarescu, A., Galizzi, M.
-M., Farran, E.
-K., \& Crook, Z.
+M., McGarrigle, R., Lynott, D., Lunny, C., Lautarescu, A., \ldots{} Crook, Z.
 (2020).
@@
 J., Cichocka, A., Capraro, V., Sjåstad, H., Nezlek, J.
-B., Pavlović, T., Alfano, M., Gelfand, M.
-J., Azevedo, F., Birtel, M.
-D., Cislak, A., Lockwood, P.
-L., Ross, R.
-M., Abts, K., Agadullina, E., Aruta, J.
-J.
-B., Besharati, S.
-N., Bor, A., Choma, B.
-L., \ldots{} Boggio, P.
+B., Pavlović, T., \ldots{} Boggio, P.
 S.
@@
 K., Uusberg, A., Lerner, J.
-S., Gross, J.
-J., Agesin, B.
-B., Bernardo, M., Campos, O., Eudave, L., Grzech, K., Ozery, D.
-H., Jackson, E.
-A., Garcia, E.
-O.
-L., Drexler, S.
-M., Jurković, A.
-P., Rana, K., Wilson, J.
-P., \ldots{} Moshontz, H.
+S., \ldots{} Moshontz, H.
 (2021).
@@
 
+\newpage
+
+\hypertarget{appendix-appendix}{%
+\appendix}
+
+\hypertarget{rq1-publisher-information.-2}{%
+\subsection{RQ1: Publisher Information.}\label{rq1-publisher-information.-2}}
+
+\textbf{Number of Journals}.
+
+Table \ref{tab:tab-snip} indicates the SNIP values for BTS publications, while Table \ref{tab:tab-snip-all}.
+The results from these tables indicate that impact values are slightly higher for BTS publications, while the overall median, minimum, and maximum are the same for each grouping.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab-snip}Big-Team Science SNIP Values}
+
+\begin{tabular}{llllll}
+\toprule
+Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
+\midrule
+Health Sciences & 2.36 & 3.59 & 0.00 & 1.58 & 173.93\\
+Physical Sciences & 1.57 & 1.17 & 0.00 & 1.27 & 30.40\\
+Social Sciences & 1.94 & 1.72 & 0.00 & 1.52 & 30.40\\
+Life Sciences & 2.02 & 1.60 & 0.00 & 1.51 & 19.07\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab-snip-all}All Journal Articles SNIP Values}
+
+\begin{tabular}{llllll}
+\toprule
+Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
+\midrule
+Health Sciences & 1.45 & 2.87 & 0.00 & 1.15 & 173.93\\
+Physical Sciences & 1.08 & 0.77 & 0.00 & 0.97 & 30.40\\
+Social Sciences & 1.32 & 1.03 & 0.00 & 1.15 & 30.40\\
+Life Sciences & 1.19 & 0.86 & 0.00 & 1.06 & 19.07\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\hypertarget{rq2-publication-information.-2}{%
+\subsection{RQ2: Publication Information.}\label{rq2-publication-information.-2}}
+
+\textbf{Keywords}.
+Figure \ref{fig:fig-keywords} indicates the most common keywords present for the BTS publications by subject area.
+The keywords were tokenized into single tokens.
+Keywords were then lowercased, and all stop words (for example, the, an, of, into, for) were removed.
+Finally, a frequency count of tokens was tabulated for each subject area, and this count is used to create the final word cloud presented.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-keywords-1.pdf}
+\caption{\label{fig:fig-keywords}Keyword Analysis for Each of the Four Subject Areas.}
+\end{figure}
+
+\hypertarget{rq3-authors}{%
+\subsection{RQ3: Authors}\label{rq3-authors}}
+
+\textbf{Institution}.
+
+Institution was normalized by taking the total number of unique institutions and dividing by the total number of institution listings.
+The patterns are similar for each decade in that papers are often either half unique institutions or mostly unique institutions overall as show in Figure \ref{fig:fig-inst}.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-inst-1.pdf}
+\caption{\label{fig:fig-inst}Number of unique institutions involved in big-team science papers across decades.}
+\end{figure}
+
+\textbf{\emph{Types of Publications}}.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-types-1.pdf}
+\caption{\label{fig:fig-pub-types}Types of publications for big-team science and all authors.}
+\end{figure}
+
 \end{document}

### 2023-08-15 appendix.Rmd
all the pictures and updates

@@
               nrow = 2)
+
+ggsave("figure/figure_app_1.png")
 ```
@@
 suppressWarnings(print(picture))
+
+ggsave("figure/figure_app_2.png")
 ```
+
+***Education***.
+As noted in our pre-registration, we would only present this variable if we could obtain at least 50% information on the authors who publish in big team science papers.
+`r apa_num(24228428/25282810*100)`% of the data was not available.
 
@@
 
+Types of publications are presented in Figure \@ref(fig:fig-pub-types).
+The patterns of publications are roughly similar for big team science authors and all authors.
+It appears that porportionally, big team members are more likely to post preprints in comparison to all authors.
+
 ```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
+pub_levels <- c("ab", "ar", "ip", "bk", "bz", "ch", "cp", 
+                "cr", "dp", "ed", "er", "le", "no", "pp", 
+                "pr", "rp", "re", "sh", "tb")
+pub_labels <- c("Abstract", "Article", "In Press", "Book", "Business", "Book Chapter", "Conference Paper", 
+                "Conference Report", "Data Paper", "Editorial", "Erratum", "Letter", "Note", 
+                "Preprint", "Press Release", "Report", "Review", "Survey", "Retracted")
 
@@
   DF$pub_types %>% mutate(type = "Big Team"), 
-  DF$normal_pub_type %>% mutate(type = "Normal")) %>% 
+  DF$normal_pub_type %>% mutate(type = "All Papers")) %>% 
     filter(!is.na(publication_type)) %>% 
-  filter(publication_type != "cb")
+  filter(publication_type != "cb") %>% 
+  mutate(publication_type = factor(publication_type, 
+                                   levels = pub_levels,
+                                   labels = pub_labels)) %>% 
+  mutate(binned_count = ifelse(
+    count < 10000, "< 10,000", ifelse(
+      count > 10000 & count < 100000, "10,000 - 99,999", ifelse(
+        count > 100000 & count < 1000000, "100,000 - 999,999", ifelse(
+          count > 1000000 & count < 10000000, "1,000,000 - 9,999,999", "> 10,000,000"
+        )
+      )
+    )
+  )) %>% 
+  mutate(binned_count = factor(binned_count,
+                               levels = c("< 10,000", 
+                                          "10,000 - 99,999",
+                                          "100,000 - 999,999", 
+                                          "1,000,000 - 9,999,999",
+                                          "> 10,000,000")))
 
-ggplot(pub_types, aes(area = count, fill = count,
+ggplot(pub_types, aes(area = count, fill = binned_count,
                label = publication_type)) +
@@
                     size = 15, grow = FALSE) +  
-  #scale_fill_brewer(name = "Sample Size", palette = "Spectral") +
+  # scale_fill_brewer(name = "Sample Size", palette = "Spectral") +
   theme_classic()
 
-# ggplot(pub_types, aes(type, count, fill = publication_type)) + 
-#     geom_bar(position="fill", stat="identity", color = "black") + 
-#   theme_classic() +  
-#   xlab("Author Type") + 
-#   ylab("Percent of Paper Types") + 
-#   theme(legend.position = "bottom") + 
-#   scale_fill_discrete(name = "Publication Type")
-
+ggsave("figure/figure_app_3.png")
 # can probably figure out how to combine these feasibly to make it readable

### 2023-08-15 manuscript_scopus.Rmd
all the pictures and updates

@@
 # documentclass     : "apa7"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 appendix          :
@@
 
-***Education***. We collected degree information from the author table.
+***Education***. We collected degree information from the author table. Information on this variable is in the appendix.
 
@@
 publication type variable for each author's publications to present
-information about the types of papers BTS authors publish.
+information about the types of papers BTS authors publish. Information on this variable is in the appendix.
 
@@
 number of publications, and the h-index. The h-index represents the
-highest *h* number of publications that have at least *h* citations.
+highest *h* number of publications that have at least *h* citations. *h*-count was only used for descriptive statistics.
 
@@
   theme(legend.position = "bottom")
+
+ggsave(filename = "figure/figure_1_pub_time.png")
 ```
@@
               nrow = 2)
+
+ggsave(filename = "figure/figure_2_cloud.png")
 ```
@@
   plot_layout(guides = "collect") & theme(legend.position = 'bottom')
+
+ggsave(filename = "figure/figure_3_num_authors.png")
 ```
@@
          filter(SubjectArea != "Multidisciplinary") %>% 
-         filter(num_papers >= 10), 
+         filter(num_papers >= 10) %>% 
+         filter(Year < 2024), 
        aes(Year, avg_career, color = SubjectArea)) +
@@
   #scale_size_continuous(name = "Number Papers")
+
+ggsave(filename = "figure/figure_4_career.png")
 ```
@@
   plot_layout(design = layout))
+
+ggsave(filename = "figure/figure_5_heatmap.png", width = 10, height = 6, units = "in")
 ```
@@
 ***Publication Metrics***.
-
--   We will report descriptive statistics on the total number of
-    publications and h-index for individuals overall.
-    -   Do this for each unique person and report averages
-    -   Do this for each publication and create an average for each
-        publication
 
@@
 
--   Next, we will use the same analyses described in the career length
-    section to analyze trends over time. An increasing slope over time
-    indicates that individuals who are publishing more are more
-    represented in BTS over time (i.e., increasing numbers of scholars
-    with higher publication rates), while a negative slope indicates
-    more researchers with less publications.
--   A positive slope for standard deviation indicates increasing
-    variance over time (i.e., more diversity in the individual
-    publication rates), while a negative slope would indicate less
-    diversity in researchers over time. While publication rates do not
-    represent value as a researcher, they are often used in hiring and
-    promotion decisions, and we will use this variable as a proxy to
-    gauge the diversity in scholars represented in big teams.
--   We will separate these by each of the four subject areas.
+We used the same analyses described in the career length section to analyze trends over time.
+An increasing slope over time indicates that individuals who are publishing more are more represented in BTS over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
+A positive slope for the standard deviation of publication metrics indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
+While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we used this variable as a proxy to gauge the diversity in scholars represented in big teams.
+As shown in Figure \@ref(fig:fig-heatmap) publication metrics were generally negative for the average publication metrics, indicating more scholars over time with lower numbers of citations with the strongest effects in health and social sciences.
+The variability of publication counts was not significant for the life sciences but was negative for the physical sciences (less variability over time) and positive for social and health sciences (more variability and over time).
+This result indicates that the physical sciences are trending toward scholars with less publications but also less diverse in number of publications, while the health and social sciences see more diversity in publication counts and less published scholars overall.
 
 ***Geopolitical Regions***.
-
--   We will present visualizations of the country information listed for
-    authors, and we will discuss the areas of world in which authors
-    generally come from, as well as the lowest representation of
-    authors.
 
@@
   #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
-  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
+  scale_fill_brewer(name = "Sample Size", palette = "Spectral", drop = FALSE)
 
@@
   #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
-  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
+  scale_fill_brewer(name = "Sample Size", palette = "Spectral", drop = FALSE)
   # scale_fill_gradient(name = "Sample Size",
@@
 
-# need to do the legend 
-```
-
--   To understand the change in representation diversity, we will
-    summarize the total number of geopolitical regions for each paper.
-    Using a linear model, we will examine if the number of regions
-    present is predicted by the year of publication. Increasing
-    diversity would be represented by a positive slope, while decreasing
-    diversity would be represented by a negative slope.
-
--   Last, we will examine the differences in representation for
-    corresponding author sets versus all other authors. For papers with
-    10 to 49 authors, we will use the three first authors and the last
-    author to compare against other authors. For 50 to 99 authors, five
-    first authors plus last will be used, and for all papers with more
-    than 100 authors, we will use ten first authors and the last author.
-    We will calculate the frequencies of each of the UN Sub-Regions for
-    first authors versus other authors, converting these values to
-    proportions. Given the expected small sample sizes of these
-    contingency tables, we will group together titles based on the year
-    of publication (assuming at least 5 publications per year, these may
-    be binned by 5-year or smaller increments to increase sample size).
-    For each grouping, we will calculate the effect size of the
-    differences in frequencies comparing first authors to all other
-    authors. Since this data is categorical, we will use Cramer's *V* to
-    represent the effect size. If the effect size includes zero in its
-    confidence interval, this result will imply that first and all other
-    authors represent the same pattern of UN Sub-Region diversity. Any
-    confidence interval that does include zero represents a difference
-    in diversity.
+ggsave(filename = "figure/figure_6_map.png", width = 10, height = 6, units = "in")
+```
+
+Author geopoligical region is displayed in Figure \@ref(fig:fig-map-both).
+Big team publications appear to be lead by North America and Western Europe, while all publications are lead by North America and East Asia.
+To understand the change in representation diversity, we examined if the number of regions in a publication is predicted by the year of publication.
+Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope.
+As shown in Figure \@ref(fig:fig-heatmap), the physical sciences do not show a trend of change in representation, while all other sciences showed a positive effect increasing in the number of geopolitical regions authors represent on publications.
+
+Last, we examined the differences in representation for corresponding author sets versus all other authors.
+For papers with 10 to 49 authors, we used the three first authors and the last author to compare against other authors.
+For 50 to 99 authors, five first authors plus last were used, and for all papers with more than 100 authors, we used ten first authors and the last author as the corresponding author set.
+We then calculated the frequencies of each of the UN Sub-Regions for corresponding authors versus all other authors, converting these values to proportions.
+Given the expected small sample sizes of these contingency tables, we grouped together titles based on the year of publication.
+For each grouping, we then calculated the effect size of the differences in frequencies comparing corresponding authors to all other authors.
+Since this data is categorical, we used Cramer's *V* to represent the effect size.
+If the effect size includes zero in its confidence interval (to four decimal places), this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity.
+Any confidence interval that does include zero represents a difference in diversity.
 
@@
   summarize_all(sum) %>% 
-  pivot_longer(cols = `Western Europe`:Mirconesia,
+  pivot_longer(cols = -c(who, Decade, Year),
                names_to = "Country", 
@@
 
+DF_decade$Country_2 <- factor(DF_decade$Country_2, 
+                              levels = c("Africa", "Asia", "Eastern Asia", 
+                                         "ESE Europe", 
+                                         "Latin America and the Caribbean",
+                                         "North America", 
+                                         "NWS Europe", "Other"))
 DF_decade_sm <- DF_decade %>% 
@@
   ylab("Percent of Authors") + 
-  scale_fill_brewer(name = "Region", palette = "Spectral")
+  scale_fill_brewer(name = "Region", palette = "Spectral", drop = FALSE)
 ```
@@
   summarize_all(sum) %>% 
-  pivot_longer(cols = `Western Europe`:Melanesia, 
-               #### check this later ####
+  pivot_longer(cols = -c(who, Decade, Year),
                names_to = "Country", 
@@
 
+DF_decade$Country_2 <- factor(DF_decade$Country_2, 
+                              levels = c("Africa", "Asia", "Eastern Asia", 
+                                         "ESE Europe", 
+                                         "Latin America and the Caribbean",
+                                         "North America", 
+                                         "NWS Europe", "Other"))
+
 DF_decade_sm <- DF_decade %>% 
@@
 
-ggplot(large_effect %>% 
-         arrange(v) %>% 
-         mutate(count = 1:nrow(large_effect)),
-       aes(count, v)) + 
-  geom_point(aes(size = people)) +
-  geom_linerange(aes(ymin = low, ymax = high), alpha = .5) +
-  theme_classic()  
-  #ylab(TeX("Raw Effect: $t$ Log RT")) + 
-  #xlab("Different Processing Scenarios") + 
-  # geom_hline(yintercept = 0) + 
-  #theme(text = element_text(size = 8))
-
 DF_decade <- DF$large_first_gp %>% 
@@
   summarize_all(sum) %>% 
-  pivot_longer(cols = `Western Europe`:`Central Asia`, 
-               #### check this later ####
+  pivot_longer(cols = -c(who, Decade, Year),
                names_to = "Country", 
@@
   ylab("Percent of Authors") + 
-  scale_fill_brewer(name = "Region", palette = "Spectral")
-```
-
-```{r author-gpe-figure, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors."}
+  scale_fill_brewer(name = "Region", palette = "Spectral", drop = FALSE)
+```
+
+```{r fig-author-gpe, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors."}
 small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
@@
 
-ggsave("figure/author_country.png", width = 10, height = 7, 
-       units = "in")
-
-# fix the legend
-```
-
-```{r effect-gpe-figure, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year."}
-small_dot + 
+ggsave("figure/figure_7_author_gpe.png", width = 10, height = 6, units = "in")
+```
+
+```{r fig-effect-gpe, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
+Larger dots indicate more papers and authors represented in the calculation of effect size."}
+all_effects <- bind_rows(
+  small_effect %>% 
+    mutate(type = "Small"),
+  medium_effect %>% 
+    mutate(type = "Medium"), 
+  large_effect %>% 
+    mutate(type = "Large") 
+) %>% 
+  mutate(type = factor(type, levels = c("Small", "Medium", "Large"),
+                       labels = c("10-49 Authors", 
+                                  "50-99 Authors", 
+                                  "100+ Authors"))) %>% 
+  mutate(Decade = ifelse(year < 1990, "1980s", 
+                         ifelse(year < 2000, "1990s", 
+                                ifelse(year < 2010, "2000s", 
+                                       ifelse(year < 2020, "2010s", "2020s")))))
+
+ggplot(all_effects %>% 
+         arrange(v) %>% 
+         mutate(count = 1:nrow(all_effects)) %>% 
+         filter(year < 2024),
+       aes(year, v)) + 
+  facet_wrap(~type) + 
+  geom_point(aes(size = people)) +
+  geom_linerange(aes(ymin = low, ymax = high), alpha = .5) +
+  theme_classic() +
   theme(legend.position = "none") + 
-  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
-  ggtitle("10-49 Authors") + 
-medium_dot + 
-  theme(legend.position = "none") + 
-  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
-  ggtitle("50-99 Authors") +
-large_dot + 
-  theme(legend.position = "none") + 
-  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
-  ggtitle("100 + Authors") + 
-guide_area() + 
-plot_layout(
-  ncol = 2,
-  nrow = 2, 
-  guides = "collect")
-
-ggsave("figure/effect_country.png", width = 10, height = 7, 
-       units = "in")
-```
+  xlab("Year of Publication") + 
+  ylab("Cramer's V")
+
+ggsave("figure/figure_8_author_effect_gpe.png", width = 10, height = 6, units = "in")
+```
+
+Figure \@ref(fig:fig-author-gpe) indicates the percent of authors in regions.
+In general, we found the same pattern as the overall analysis wherein most authors are from Europe and North America.
+The pattern of representation is roughly similar for the separation of small, medium, and large numbers of authors on papers.
+Across time, the representation does appear to diversify, with more representation in Asia, Latin American, and Africa.
+Figure \@ref(fig:fig-effect-gpe) represents the size of the differences in first/corresponding authors and other authors across time and number of authors.
+The differences in representation are larger for papers with more authors; however, the effects are non-zero for many of the comparisons.
+Encouragingly, over time these effects appear to diminish in size.
+One limitation with the calculation of effect sizes for count data is the sensitivity of the data to sample size (i.e., $\chi^2$ is upwardly biased by sample size, and $V$ is calculated based on this value).
+While we used the inclusion of zero as our boundary for "significance", the interpretation of the effects is that most are likely small: $V$ < .05: `r apa_num(sum(all_effects$v <.05)/nrow(all_effects)*100)`%, < .10: `r apa_num(sum(all_effects$v < .10)/nrow(all_effects)*100)`%, < .20: `r apa_num(sum(all_effects$v < .20)/nrow(all_effects)*100)`%.
+
+# Discussion
+
+- number of publications increasing
+- research areas appear to be cancer, physics, and psychology
+- the number of authors is increasing as well 
+- career length is decreasing, number of publications necessary to be involved is decreasing
+- number of gpe increasing 
+- appears to be slowly diversifying, yet still not equal in first and other authors in diversity
+
+limitations - based on the data we could get, we made up the definition of BTS, under-representation of articles in other languages/that they don't collect
+
+future: incentives for bts and why people do it
 

### 2023-08-16 manuscript_scopus.Rmd
adding the discussion

@@
 having both collaborations that span across the globe and subfields of
-research areas, age groups, and education levels should help to drive science in the path of better materials, reliability,
-generalizability and more robust sample sizes (when necessary) in a study
+research areas, age groups, and education levels should help to drive
+science in the path of better materials, reliability, generalizability
+and more robust sample sizes (when necessary) in a study
 [@auspurg2021has; @nosek2014method; @lebel2018].
@@
 scale replications using in collaborative environments [@vazire2022].
-Generally, the movement appears to have been driven by early career researchers
-(i.e., those who are within five years of their first appointment)
-[@maizey2019]; however, there are no large meta-scientific
+Generally, the movement appears to have been driven by early career
+researchers (i.e., those who are within five years of their first
+appointment) [@maizey2019]; however, there are no large meta-scientific
 investigations on this specific topic to date. Potentially, the lack of
@@
 collected [@nosek2014; @stewart2020], and entire sub-sections of
-journals devoted to only replication studies (e.g., *Nature, Royal Society Open Science, Advances in Methods and Practices in Psychological Science*) has allowed researchers to invest in projects that they know
+journals devoted to only replication studies (e.g., *Nature, Royal
+Society Open Science, Advances in Methods and Practices in Psychological
+Science*) has allowed researchers to invest in projects that they know
 should be published when the project is complete. Further, the
@@
 Therefore, the goal of this manuscript is to examine the *people*
-involved in BTS projects. We specifically examined the themes of inclusivity, research careers, and research globalization. We see an
-increasing interest and number of publications in BTS but we do not yet know if
-this uptick in large-scale projects has diversified the *people*
+involved in BTS projects. We specifically examined the themes of
+inclusivity, research careers, and research globalization. We see an
+increasing interest and number of publications in BTS but we do not yet
+know if this uptick in large-scale projects has diversified the *people*
 involved in BTS. While a few publications have noted that BTS appears to
@@
 
-This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (https://osf.io/f2dtr) but then was updated with access to the Scopus database for a broader picture of BTS projects (https://osf.io/fheun).
-All materials and code can be found on our OSF page: https://osf.io/cgx6u/ or corresponding GitHub archive: https://github.com/doomlab/big_team_who.
+This manuscript was preregistered with the same conceptual ideas using
+Google Scholar and ORC-ID databases (<https://osf.io/f2dtr>) but then
+was updated with access to the Scopus database for a broader picture of
+BTS projects (<https://osf.io/fheun>). All materials and code can be
+found on our OSF page: <https://osf.io/cgx6u/> or corresponding GitHub
+archive: <https://github.com/doomlab/big_team_who>.
 
@@
 peer-reviewed journals or had posted a full paper pre-print. We used
-data from 1970 and forward in the Scopus database, as it
-is noted online that this time period includes cited references for
-calculation of several of our variables described below. We will analyze
-our results based on four subject areas present in the Scopus database: Physical Sciences,
-Health Sciences, Social Sciences, and Life Sciences. We filtered the
-database to include articles, articles in press, business articles,
-conference papers, data papers, preprints, and surveys using Elsevier's
-classification system. This project was supported by access to the Scopus database through the International Center for the Study of Research.
+data from 1970 and forward in the Scopus database, as it is noted online
+that this time period includes cited references for calculation of
+several of our variables described below. We will analyze our results
+based on four subject areas present in the Scopus database: Physical
+Sciences, Health Sciences, Social Sciences, and Life Sciences. We
+filtered the database to include articles, articles in press, business
+articles, conference papers, data papers, preprints, and surveys using
+Elsevier's classification system. This project was supported by access
+to the Scopus database through the International Center for the Study of
+Research.
 
@@
 
-### RQ1: Publisher Information.
-
-We extracted the following information for publication sources: the name of the publication (source title), subject area (both the large four subject areas and the smaller four digit all science journal classification [ASJC] code), and the journal
-impact using the Source Normalized Impact per Paper (SNIP).
-
-### RQ2: Publication Information.
-
-For each publication of the identified BTS publications, we examined
-the full four digit ASJC subject areas codes for each of the larger four
+### RQ1: Publisher Information
+
+We extracted the following information for publication sources: the name
+of the publication (source title), subject area (both the large four
+subject areas and the smaller four digit all science journal
+classification [ASJC] code), and the journal impact using the Source
+Normalized Impact per Paper (SNIP).
+
+### RQ2: Publication Information
+
+For each publication of the identified BTS publications, we examined the
+full four digit ASJC subject areas codes for each of the larger four
 subject areas and the keywords present for these publications.
 
-### RQ3: Author Information.
-
-The author list was extracted from each publication.
-Next, we used the author and affiliation arrays to curate a list of all publications and author information included in BTS papers to calculate the variables described below.
-
-***Career Length***. Career length for each author was defined as
-the year of the first publication minus the current year listed for each author.
-
-***Institution and Geopolitical Region***. We used the affiliation
-ids and country to gather information about the places of education
-and/or employment for authors. Geopolitical region was created by binning these codes into United Nation Regions.
-
-***Education***. We collected degree information from the author table. Information on this variable is in the appendix.
-
-***Types of Publications***. We took information from the
-publication type variable for each author's publications to present
-information about the types of papers BTS authors publish. Information on this variable is in the appendix.
+### RQ3: Author Information
+
+The author list was extracted from each publication. Next, we used the
+author and affiliation arrays to curate a list of all publications and
+author information included in BTS papers to calculate the variables
+described below.
+
+***Career Length***. Career length for each author was defined as the
+year of the first publication minus the current year listed for each
+author.
+
+***Institution and Geopolitical Region***. We used the affiliation ids
+and country to gather information about the places of education and/or
+employment for authors. Geopolitical region was created by binning these
+codes into United Nation Regions.
+
+***Education***. We collected degree information from the author table.
+Information on this variable is in the appendix.
+
+***Types of Publications***. We took information from the publication
+type variable for each author's publications to present information
+about the types of papers BTS authors publish. Information on this
+variable is in the appendix.
 
@@
 number of publications, and the h-index. The h-index represents the
-highest *h* number of publications that have at least *h* citations. *h*-count was only used for descriptive statistics.
+highest *h* number of publications that have at least *h* citations.
+*h*-count was only used for descriptive statistics.
 
@@
 
-We used the 95% confidence interval to make decisions on predictor or effect size differences from zero.
-The confidence interval that does not include zero would be considered different from zero (to four decimal places).
-We made no directional predictions.
+We used the 95% confidence interval to make decisions on predictor or
+effect size differences from zero. The confidence interval that does not
+include zero would be considered different from zero (to four decimal
+places). We made no directional predictions.
 
@@
 
-*Number of articles*. The total number of articles included in this analysis was `r total_num` including `r health_num` Health Sciences articles, `r physical_num`
-Physical Sciences articles, `r social_num` Social Sciences articles, and
-`r life_num` Life Sciences articles. Articles could be classified into
-multiple categories. Figure \@ref(fig:fig-pub-time) shows the number of articles published across time for each of the four large subject areas.
+*Number of articles*. The total number of articles included in this
+analysis was `r total_num` including `r health_num` Health Sciences
+articles, `r physical_num` Physical Sciences articles, `r social_num`
+Social Sciences articles, and `r life_num` Life Sciences articles.
+Articles could be classified into multiple categories. Figure
+\@ref(fig:fig-pub-time) shows the number of articles published across
+time for each of the four large subject areas.
 
@@
 
-*Number of journals*. The number of distinct journals big team science articles were published
-in was `r journals` with `r health_journal` journals in Health Sciences,
-`r physical_journal` journals in Physical Sciences, `r social_journal`
-journals in Social Sciences, and `r life_journal` journals in Life
-Sciences. The descriptive statistics for the Source Normalized Impact
-per Paper is presented the supplemental materials with a comparison for all papers.
+*Number of journals*. The number of distinct journals big team science
+articles were published in was `r journals` with `r health_journal`
+journals in Health Sciences, `r physical_journal` journals in Physical
+Sciences, `r social_journal` journals in Social Sciences, and
+`r life_journal` journals in Life Sciences. The descriptive statistics
+for the Source Normalized Impact per Paper is presented the supplemental
+materials with a comparison for all papers.
 
@@
 
-Publication interest area was summarized by the four large subject areas creating a word cloud plot of the total number of publications within the ASJCs.
-Figure \@ref(fig:fig-clouds) displays that the health sciences tends to publish within medicine and oncology, with a corresponding focus of cancer research and genetics for the life sciences.
-The physical sciences is mostly dominated by physics research, chemistry, and ecology.
-The BTS publications in the social sciences are mostly within psychology, education, and health.
+Publication interest area was summarized by the four large subject areas
+creating a word cloud plot of the total number of publications within
+the ASJCs. Figure \@ref(fig:fig-clouds) displays that the health
+sciences tends to publish within medicine and oncology, with a
+corresponding focus of cancer research and genetics for the life
+sciences. The physical sciences is mostly dominated by physics research,
+chemistry, and ecology. The BTS publications in the social sciences are
+mostly within psychology, education, and health.
 
@@
 
-The total number of unique authors across all publications was `r total_authors`.
-The mean number of authors per publication was *M* = `r avg_authors` (*SD* = `r sd_authors`, *Med* = `r med_authors`) with a range of `r min_authors` to `r max_authors`.
-The median and average number of authors by subject area are displayed in Figure \@ref(fig:fig-author-year).
-In general, the average and median number of authors increased over time, with the exception of the skew in the physical sciences.
-Interestingly, the effect in the physical sciences appears to be declining toward the general trends seen in other areas in the last few decades.
+The total number of unique authors across all publications was
+`r total_authors`. The mean number of authors per publication was *M* =
+`r avg_authors` (*SD* = `r sd_authors`, *Med* = `r med_authors`) with a
+range of `r min_authors` to `r max_authors`. The median and average
+number of authors by subject area are displayed in Figure
+\@ref(fig:fig-author-year). In general, the average and median number of
+authors increased over time, with the exception of the skew in the
+physical sciences. Interestingly, the effect in the physical sciences
+appears to be declining toward the general trends seen in other areas in
+the last few decades.
 
@@
 
-Figure \@ref(fig:fig-career) portrays the average career length for authors involved in BTS publications across years.
-Career length was defined as the year of first publication minus the current year, and higher numbers mean longer careers.
-To analyze trends over time, we  calculated the average career length for each publication (i.e., average author career lengths to create one score for each paper) and analyzed a regression analysis using career length to predict year of publication.
-In order to show variance between individuals, we calculated the standard deviation of career length for each publication and used variance as an additional predictor.
-
-Negative career length slopes would indicate more young scholars in later years (i.e., lower average career length as time increases).
-Positive career length slopes would indicate older scholars in later years (i.e., higher average career length as time increases).
-Negative career variance slopes imply that variability decreases over the years, so the average career length is more homogeneous.
-Positive career length slopes imply that variability increases over the years, so the average career length is varied across individuals (i.e., different stages of scholars).
-Figure \@ref(fig:fig-heatmap) displays the results for all regression analyses to compare coefficient strength across and within hypothesis.
-
-All values for this analyses were different from zero.
-The slopes for the average career length were negative for all four subject areas, indicating a trend toward younger scientist involvement over time for each area, with the strongest effect in the Physical sciences.
-The coefficient for variability in career length was also negative for each of the four subject areas with the highest in the Physical sciences and lowest in the Life Sciences.
-This result indicates a decrease in the variability of career lengths over time, likely from two sources: 1) more publications with more authors, thus, lowering variance estimations, and 2) more young scholars overall.
-The effect sizes for this analysis were surprisingly large ranging from $R^2$ to .25 to .47.
+Figure \@ref(fig:fig-career) portrays the average career length for
+authors involved in BTS publications across years. Career length was
+defined as the year of first publication minus the current year, and
+higher numbers mean longer careers. To analyze trends over time, we
+calculated the average career length for each publication (i.e., average
+author career lengths to create one score for each paper) and analyzed a
+regression analysis using career length to predict year of publication.
+In order to show variance between individuals, we calculated the
+standard deviation of career length for each publication and used this
+variance as an additional predictor.
+
+Negative career length slopes would indicate more young scholars in
+later years (i.e., lower average career length as time increases).
+Positive career length slopes would indicate older scholars in later
+years (i.e., higher average career length as time increases). Negative
+career variance slopes imply that variability decreases over the years,
+so the average career length is more homogeneous. Positive career length
+slopes imply that variability increases over the years, so the average
+career length is varied across individuals (i.e., different stages of
+scholars). Figure \@ref(fig:fig-heatmap) displays the results for all
+regression analyses to compare coefficient strength across and within
+hypothesis.
+
+All values for this analyses were different from zero. The slopes for
+the average career length were negative for all four subject areas,
+indicating a trend toward younger scientist involvement over time for
+each area, with the strongest effect in the Physical sciences. The
+coefficient for variability in career length was also negative for each
+of the four subject areas with the highest in the Physical sciences and
+lowest in the Life Sciences. This result indicates a decrease in the
+variability of career lengths over time, likely from two sources: 1)
+more publications with more authors, thus, lowering variance
+estimations, and 2) more young scholars overall. The effect sizes for
+this analysis were surprisingly large ranging from $R^2$ to .25 to .47.
 All values and their confidence intervals can be found on our OSF page.
@@
 
-We used the same analyses described in the career length section to analyze trends over time.
-An increasing slope over time indicates that individuals who are publishing more are more represented in BTS over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
-A positive slope for the standard deviation of publication metrics indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
-While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we used this variable as a proxy to gauge the diversity in scholars represented in big teams.
-As shown in Figure \@ref(fig:fig-heatmap) publication metrics were generally negative for the average publication metrics, indicating more scholars over time with lower numbers of citations with the strongest effects in health and social sciences.
-The variability of publication counts was not significant for the life sciences but was negative for the physical sciences (less variability over time) and positive for social and health sciences (more variability and over time).
-This result indicates that the physical sciences are trending toward scholars with less publications but also less diverse in number of publications, while the health and social sciences see more diversity in publication counts and less published scholars overall.
+We used the same analyses described in the career length section to
+analyze trends over time. An increasing slope over time indicates that
+individuals who are publishing more are more represented in BTS over
+time (i.e., increasing numbers of scholars with higher publication
+rates), while a negative slope indicates more researchers with less
+publications. A positive slope for the standard deviation of publication
+metrics indicates increasing variance over time (i.e., more diversity in
+the individual publication rates), while a negative slope would indicate
+less diversity in researchers over time. While publication rates do not
+represent value as a researcher, they are often used in hiring and
+promotion decisions, and we used this variable as a proxy to gauge the
+diversity in scholars represented in big teams. As shown in Figure
+\@ref(fig:fig-heatmap) publication metrics were generally negative for
+the average publication metrics, indicating more scholars over time with
+lower numbers of publications with the strongest effects in health and
+social sciences. The variability of publication counts was not
+significant for the life sciences but was negative for the physical
+sciences (less variability over time) and positive for social and health
+sciences (more variability and over time). This result indicates that
+the physical sciences are trending toward scholars with less
+publications but also less diverse in number of publications, while the
+health and social sciences see more diversity in publication counts and
+less published scholars overall.
 
@@
 
-Author geopoligical region is displayed in Figure \@ref(fig:fig-map-both).
-Big team publications appear to be lead by North America and Western Europe, while all publications are lead by North America and East Asia.
-To understand the change in representation diversity, we examined if the number of regions in a publication is predicted by the year of publication.
-Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope.
-As shown in Figure \@ref(fig:fig-heatmap), the physical sciences do not show a trend of change in representation, while all other sciences showed a positive effect increasing in the number of geopolitical regions authors represent on publications.
-
-Last, we examined the differences in representation for corresponding author sets versus all other authors.
-For papers with 10 to 49 authors, we used the three first authors and the last author to compare against other authors.
-For 50 to 99 authors, five first authors plus last were used, and for all papers with more than 100 authors, we used ten first authors and the last author as the corresponding author set.
-We then calculated the frequencies of each of the UN Sub-Regions for corresponding authors versus all other authors, converting these values to proportions.
-Given the expected small sample sizes of these contingency tables, we grouped together titles based on the year of publication.
-For each grouping, we then calculated the effect size of the differences in frequencies comparing corresponding authors to all other authors.
-Since this data is categorical, we used Cramer's *V* to represent the effect size.
-If the effect size includes zero in its confidence interval (to four decimal places), this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity.
-Any confidence interval that does include zero represents a difference in diversity.
+Author geopolitical region is displayed in Figure
+\@ref(fig:fig-map-both). Big team publications appear to be lead by
+North America and Western Europe, while all publications are lead by
+North America and East Asia. To understand the change in representation
+diversity, we examined if the number of regions in a publication is
+predicted by the year of publication. Increasing diversity would be
+represented by a positive slope, while decreasing diversity would be
+represented by a negative slope. As shown in Figure
+\@ref(fig:fig-heatmap), the physical sciences do not show a trend of
+change in representation, while all other sciences showed a positive
+effect increasing in the number of geopolitical regions authors
+represent on publications.
+
+Last, we examined the differences in representation for corresponding
+author sets versus all other authors. For papers with 10 to 49 authors,
+we used the three first authors and the last author to compare against
+other authors. For 50 to 99 authors, five first authors plus last were
+used, and for all papers with more than 100 authors, we used ten first
+authors and the last author as the corresponding author set. We then
+calculated the frequencies of each of the UN Sub-Regions for
+corresponding authors versus all other authors, converting these values
+to proportions. Given the expected small sample sizes of these
+contingency tables, we grouped together titles based on the year of
+publication. For each grouping, we then calculated the effect size of
+the differences in frequencies comparing corresponding authors to all
+other authors. Since this data is categorical, we used Cramer's *V* to
+represent the effect size. If the effect size includes zero in its
+confidence interval (to four decimal places), this result will imply
+that first and all other authors represent the same pattern of UN
+Sub-Region diversity. Any confidence interval that does include zero
+represents a difference in diversity.
 
@@
 
-Figure \@ref(fig:fig-author-gpe) indicates the percent of authors in regions.
-In general, we found the same pattern as the overall analysis wherein most authors are from Europe and North America.
-The pattern of representation is roughly similar for the separation of small, medium, and large numbers of authors on papers.
-Across time, the representation does appear to diversify, with more representation in Asia, Latin American, and Africa.
-Figure \@ref(fig:fig-effect-gpe) represents the size of the differences in first/corresponding authors and other authors across time and number of authors.
-The differences in representation are larger for papers with more authors; however, the effects are non-zero for many of the comparisons.
-Encouragingly, over time these effects appear to diminish in size.
-One limitation with the calculation of effect sizes for count data is the sensitivity of the data to sample size (i.e., $\chi^2$ is upwardly biased by sample size, and $V$ is calculated based on this value).
-While we used the inclusion of zero as our boundary for "significance", the interpretation of the effects is that most are likely small: $V$ < .05: `r apa_num(sum(all_effects$v <.05)/nrow(all_effects)*100)`%, < .10: `r apa_num(sum(all_effects$v < .10)/nrow(all_effects)*100)`%, < .20: `r apa_num(sum(all_effects$v < .20)/nrow(all_effects)*100)`%.
+Figure \@ref(fig:fig-author-gpe) indicates the percent of authors in
+regions. In general, we found the same pattern as the overall analysis
+wherein most authors are from Europe and North America. The pattern of
+representation is roughly similar for the separation of small, medium,
+and large numbers of authors on papers. Across time, the representation
+does appear to diversify, with more representation in Asia, Latin
+American, and Africa. Figure \@ref(fig:fig-effect-gpe) represents the
+size of the differences in first/corresponding authors and other authors
+across time and number of authors. The differences in representation are
+larger for papers with more authors; however, the effects are non-zero
+for many of the comparisons. Encouragingly, over time these effects
+appear to diminish in size. One limitation with the calculation of
+effect sizes for count data is the sensitivity of the data to sample
+size (i.e., $\chi^2$ is upwardly biased by sample size, and $V$ is
+calculated based on this value). While we used the inclusion of zero as
+our boundary for "significance", the interpretation of the effects is
+that most are likely small: $V$ \< .05:
+`r apa_num(sum(all_effects$v <.05)/nrow(all_effects)*100)`%, \< .10:
+`r apa_num(sum(all_effects$v < .10)/nrow(all_effects)*100)`%, \< .20:
+`r apa_num(sum(all_effects$v < .20)/nrow(all_effects)*100)`%.
 
@@
 
-- number of publications increasing
-- research areas appear to be cancer, physics, and psychology
-- the number of authors is increasing as well 
-- career length is decreasing, number of publications necessary to be involved is decreasing
-- number of gpe increasing 
-- appears to be slowly diversifying, yet still not equal in first and other authors in diversity
-
-limitations - based on the data we could get, we made up the definition of BTS, under-representation of articles in other languages/that they don't collect
-
-future: incentives for bts and why people do it
+In this investigation, we explored the publication rates, areas, and
+researchers involved in big team science publications. Over a
+half-million articles were published in nearly 15,000 journals since
+1970 that qualified as big team science articles with at least ten
+authors and ten different affiliations. The areas of publication aligned
+to cancer and genetics research in medicine and oncology for medical and
+life sciences, physics and chemistry for the physical sciences, and
+psychology for the social sciences. All areas of research show an
+explosion in growth in the number of publications and the number of
+author included on manuscripts, replicating previous investigations into
+this topic area [@sinatra2015; @wuchty2007; @hunter2008].
+
+Our investigation expands into an exploration of the researchers who
+publish in big teams focusing on career length, publication metrics, and
+geopolitical affiliation. The number of earlier career scholars is
+increasing in publications across the years, indicating that big teams
+may be more accessible to different types of individuals, not just
+older, more established researchers. This result is especially
+interesting given the publish-or-perish model still present in most
+institutions, as it may seem that large-scale projects could be a risky
+choice for non-permanent researchers. In the authors' experience, big
+team projects are often quite slow to publication, incentives may be low
+for non corresponding authors if institutions do not value papers
+without lead authorship, and there is no guarantee for publication even
+with a large group. However, with a large team the distribution of work
+could imply less effort on individual non-leading members, and research
+has shown that larger-team publications do receive more citations and
+appear to have higher impact [@larivière2015].
+
+The results for number of publications by big team researchers mimics
+the findings from career length, with a smaller effect size. In general,
+it appears that there is a decrease in the average number of
+publications a researcher has when publishing on a big team science
+paper over time. This result is likely attributable to the number of
+early career scholars joining projects, but also may support increased
+accessibility for individuals to be involved in this type of research.
+Globalization, the internet, and the focus on interdisciplinary research
+are potentially driving forces behind our results, but, hopefully, the
+results also point to a decline in scientific gatekeeping [@siler2015;
+@lu2007].
+
+The variability in the types of researchers involved in publications
+also decreased across time in most areas of science with a decrease in
+variability for career length. As mention, an increase in early career
+researchers and numbers of publications could explain this effect
+mathematically, potentially with other social influences mentioned
+above. The variability in number of publications is decreasing in the
+physical sciences, mirroring the career length results, but the opposite
+effect was found in the health and social sciences. We see no clear
+reason why career variability would decrease while the variability in
+the number of publications would increase. The effect sizes for career
+length were much larger than the effects for number of publications. One
+speculation is the increasing requirements for a competitive faculty
+role application. Given the limited number of positions, one potential
+way to distinguish their application would be a larger number
+publications in their early career [@caplow2017; @kyvik2003].
+
+The number of geopolitical entities for researcher affiliation is
+increasing over time, showing the results of globalization and the
+ability to connect across time zones and cultures [@xie2014]. While our
+definition of big team science required at least ten different
+institutional affiliations, we did not filter papers by geopolitical
+region, and thus, a manuscript could rely solely on institutions within
+a single country. The physical sciences did not show an increase in
+diversity of regions represented, however, it could be argued that the
+development of large research centers like CERN forced earlier diversity
+than other sciences (i.e., because CERN specifically recruited
+scientists from sponsoring nations). The life, health, and social
+sciences saw an increase in the number of regions represented with the
+highest increase in the social science. This result likely corresponds
+with an increased interest in big team science publications in
+psychology [@coles2022; @forscher2020], and the desire to diversify the
+populations represented in psychological research [@henrich2010;
+@newson2021].
+
+While publications on the whole are diversifying, we did not yet find
+equality in the representation for first/corresponding author spots
+versus all other authors. In general, first authors appear to be less
+diverse, representing more European and North American authors, while
+other authors include more Asian and African authors. These effect sizes
+were often small, but the inequality still persists across years, even
+if they are slowly decreasing. Diverse teams are more likely to have
+papers with stronger "impact" [@jones2008; @hinnant2012; @yang2022;
+@freeman2015] with higher citation metrics for more diverse author
+lists. The introduction of contributorship models [e.g., CRediT;
+@allen2019] will hopefully continue to push these effects down, as they
+highlight each individual's contribution to a manuscript.
+
+The limitations for this research are tied to the availability and
+curation of the Scopus dataset. While the number of articles analyzed
+for this investigation was large, the criteria for inclusion requires
+the correct entry of author affiliations, the correct author linkages
+for career length and publication rates, and the correctly marked
+geopolitical entity. We had planned to analyze educational levels to
+determine if the number of student coauthors (i.e., non-terminal degree)
+had increased over time; however, this data was mostly blank within the
+Scopus archive. Scopus is a carefully curated dataset, but these
+limitations must be kept in mind when interpreting the results.
+Publication language diversity was not investigated, and a previous
+study indicates that the majority of publications in big databases are
+in English [@albarillo2014]. Certainly, publications in non-English
+languages would improve the statistics on diversity in scientific
+publishing - but the English language barrier likely exists regardless
+of inclusion in databases [@meneghini2007; @ramírez-castañeda2020].
+
+Big teams have the ability to provide high-impact, important research
+within scientific publishing, and this report suggests a promising trend
+of increasing numbers of publications that include earlier career and
+more diverse scholars. These partnerships introduce new challenges to
+collaboration from interpersonal conflict, infrastructure, incentives,
+to international political situations [@forscher2020]. Directed studies
+into ways to navigate these situations would be beneficial for policy
+makers at institutions, as well as lead teams who organize and complete
+these projects. The implications for retention and promotion processes
+across a broad span of regions should be explored to improve diversity
+with the understanding of the differential impact of incentives for
+participating in big team studies.
 
@@
 ```
-
 \newpage
 
-# (APPENDIX) Appendix {-}
+# (APPENDIX) Appendix {.unnumbered}
 

### 2023-08-16 manuscript_scopus.Rmd
making sure the figures are right

@@
 # header-includes:
-#   - |
-#     \makeatletter
-#     \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-#       {-1em}%
-#       {\normalfont\normalsize\bfseries\typesectitle}}
-#       {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-#       {-\z@\relax}%
-#       {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
 # csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
@@
 
-```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years."}
+```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years.", fig.width=10, fig.height=6}
 ggplot(DF$pub_time_count %>% 
@@
 
-ggsave(filename = "figure/figure_1_pub_time.png")
+ggsave(filename = "figure/figure_1_pub_time.png", width = 10, height = 6)
 ```
@@
 
-```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area"}
+```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area", fig.width=10, fig.height=6}
 
@@
 
-ggsave(filename = "figure/figure_2_cloud.png")
+ggsave(filename = "figure/figure_2_cloud.png", width = 10, height = 6)
 ```
@@
 ```{r fig-author-year, include = TRUE, fig.cap="Number of authors included on big-team science papers per year by subject area.
-Given the large skew in the data, the left panel presents the median number of authors per manuscript, and the right panel presents the average number of authors per manuscript by year."}
+Given the large skew in the data, the left panel presents the median number of authors per manuscript, and the right panel presents the average number of authors per manuscript by year.", fig.width=10, fig.height=6}
 avg_author_time <- 
@@
 
-ggsave(filename = "figure/figure_3_num_authors.png")
+ggsave(filename = "figure/figure_3_num_authors.png", width = 10, height = 6)
 ```
@@
 Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year.
-The data has been filtered to at least 10 publications in a year for this graph."}
+The data has been filtered to at least 10 publications in a year for this graph.", fig.width=10, fig.height=6}
 ggplot(DF$career_time %>% 
@@
 
-ggsave(filename = "figure/figure_4_career.png")
+ggsave(filename = "figure/figure_4_career.png", width = 10, height = 6)
 ```
@@
 The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.
-Non-significant results are indicated with NS on the plot."}
+Non-significant results are indicated with NS on the plot.", fig.width=10, fig.height=6}
 graph_overall <- graph_data %>% 
@@
 
-```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications."}
+```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.", fig.width=10, fig.height=6}
 bin_country + ggtitle("Big-Team Publication Map") + 
@@
 
-```{r fig-author-gpe, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors."}
+```{r fig-author-gpe, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades.
+F stands for first authors and O stands for other authors.", fig.width=10, fig.height=6}
 small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
@@
 ```{r fig-effect-gpe, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
-Larger dots indicate more papers and authors represented in the calculation of effect size."}
+Larger dots indicate more papers and authors represented in the calculation of effect size.", fig.width=10, fig.height=6}
 all_effects <- bind_rows(

### 2023-08-16 appendix.Rmd
making sure the figures are right
fixed aspect ratio

@@
 
-```{r fig-keywords, include = TRUE, fig.cap="Keyword Analysis for Each of the Four Subject Areas."}
+```{r fig-keywords, include = TRUE, fig.cap="Keyword Analysis for Each of the Four Subject Areas.", fig.width=10, fig.height=6}
 health_key <- fig("figure/health_key.png")
@@
 
-ggsave("figure/figure_app_1.png")
+ggsave("figure/figure_app_1.png", width = 10, height = 6)
 ```
@@
 
-```{r fig-inst, include = TRUE, fig.cap="Number of unique institutions involved in big-team science papers across decades."}
+```{r fig-inst, include = TRUE, fig.cap="Number of unique institutions involved in big-team science papers across decades.", fig.width=10, fig.height=6}
 DF$inst_time$normalized <- DF$inst_time$unique / DF$inst_time$total * 100
@@
 The patterns of publications are roughly similar for big team science authors and all authors.
-It appears that porportionally, big team members are more likely to post preprints in comparison to all authors.
+It appears that proportionally, big team members are more likely to post preprints in comparison to all authors.
 
-```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
+```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors.", fig.width=10, fig.height=6}
 pub_levels <- c("ab", "ar", "ip", "bk", "bz", "ch", "cp", 
@@
                     size = 15, grow = FALSE) +  
-  # scale_fill_brewer(name = "Sample Size", palette = "Spectral") +
+  scale_fill_brewer(name = "Sample Size", palette = "Spectral") +
   theme_classic()
 
-ggsave("figure/figure_app_3.png")
+ggsave("figure/figure_app_3.png", width = 10, height = 6)
 # can probably figure out how to combine these feasibly to make it readable

### 2023-08-16 manuscript_scopus.tex
fixed aspect ratio

@@
 
-\textbf{\emph{Education}}. We collected degree information from the author table.
+\textbf{\emph{Education}}. We collected degree information from the author table. Information on this variable is in the appendix.
 
@@
 number of publications, and the h-index. The h-index represents the
-highest \emph{h} number of publications that have at least \emph{h} citations.
+highest \emph{h} number of publications that have at least \emph{h} citations. \emph{h}-count was only used for descriptive statistics.
 
@@
 Publication interest area was summarized by the four large subject areas creating a word cloud plot of the total number of publications within the ASJCs.
-Figure @\ref(fig:fig-clouds) displays that the health sciences tends to publish within medicine and oncology, with a corresponding focus of cancer research and genetics for the life sciences.
+Figure \ref{fig:fig-clouds} displays that the health sciences tends to publish within medicine and oncology, with a corresponding focus of cancer research and genetics for the life sciences.
 The physical sciences is mostly dominated by physics research, chemistry, and ecology.
@@
 \caption{\label{fig:fig-career}Average career length for big-team science authors.
-Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year.}
+Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year.
+The data has been filtered to at least 10 publications in a year for this graph.}
 \end{figure}
@@
 
+\begin{verbatim}
+## Warning in width_strings[fixed_areas[[i]]$cols] == "-1null" && length(w) == :
+## 'length(x) = 3 > 1' in coercion to 'logical(1)'
+\end{verbatim}
+
 \textbf{\emph{Institution}}.
@@
 \textbf{\emph{Publication Metrics}}.
-
-\begin{itemize}
-\tightlist
-\item
-  We will report descriptive statistics on the total number of
-  publications and h-index for individuals overall.
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Do this for each unique person and report averages
-  \item
-    Do this for each publication and create an average for each
-    publication
-  \end{itemize}
-\end{itemize}
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Next, we will use the same analyses described in the career length
-  section to analyze trends over time. An increasing slope over time
-  indicates that individuals who are publishing more are more
-  represented in BTS over time (i.e., increasing numbers of scholars
-  with higher publication rates), while a negative slope indicates
-  more researchers with less publications.
-\item
-  A positive slope for standard deviation indicates increasing
-  variance over time (i.e., more diversity in the individual
-  publication rates), while a negative slope would indicate less
-  diversity in researchers over time. While publication rates do not
-  represent value as a researcher, they are often used in hiring and
-  promotion decisions, and we will use this variable as a proxy to
-  gauge the diversity in scholars represented in big teams.
-\item
-  We will separate these by each of the four subject areas.
-\end{itemize}
+We used the same analyses described in the career length section to analyze trends over time.
+An increasing slope over time indicates that individuals who are publishing more are more represented in BTS over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
+A positive slope for the standard deviation of publication metrics indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
+While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we used this variable as a proxy to gauge the diversity in scholars represented in big teams.
+As shown in Figure \ref{fig:fig-heatmap} publication metrics were generally negative for the average publication metrics, indicating more scholars over time with lower numbers of citations with the strongest effects in health and social sciences.
+The variability of publication counts was not significant for the life sciences but was negative for the physical sciences (less variability over time) and positive for social and health sciences (more variability and over time).
+This result indicates that the physical sciences are trending toward scholars with less publications but also less diverse in number of publications, while the health and social sciences see more diversity in publication counts and less published scholars overall.
 
 \textbf{\emph{Geopolitical Regions}}.
-
-\begin{itemize}
-\tightlist
-\item
-  We will present visualizations of the country information listed for
-  authors, and we will discuss the areas of world in which authors
-  generally come from, as well as the lowest representation of
-  authors.
-\end{itemize}
 
@@
 
-\begin{itemize}
-\item
-  To understand the change in representation diversity, we will
-  summarize the total number of geopolitical regions for each paper.
-  Using a linear model, we will examine if the number of regions
-  present is predicted by the year of publication. Increasing
-  diversity would be represented by a positive slope, while decreasing
-  diversity would be represented by a negative slope.
-\item
-  Last, we will examine the differences in representation for
-  corresponding author sets versus all other authors. For papers with
-  10 to 49 authors, we will use the three first authors and the last
-  author to compare against other authors. For 50 to 99 authors, five
-  first authors plus last will be used, and for all papers with more
-  than 100 authors, we will use ten first authors and the last author.
-  We will calculate the frequencies of each of the UN Sub-Regions for
-  first authors versus other authors, converting these values to
-  proportions. Given the expected small sample sizes of these
-  contingency tables, we will group together titles based on the year
-  of publication (assuming at least 5 publications per year, these may
-  be binned by 5-year or smaller increments to increase sample size).
-  For each grouping, we will calculate the effect size of the
-  differences in frequencies comparing first authors to all other
-  authors. Since this data is categorical, we will use Cramer's \emph{V} to
-  represent the effect size. If the effect size includes zero in its
-  confidence interval, this result will imply that first and all other
-  authors represent the same pattern of UN Sub-Region diversity. Any
-  confidence interval that does include zero represents a difference
-  in diversity.
-\end{itemize}
+Author geopoligical region is displayed in Figure \ref{fig:fig-map-both}.
+Big team publications appear to be lead by North America and Western Europe, while all publications are lead by North America and East Asia.
+To understand the change in representation diversity, we examined if the number of regions in a publication is predicted by the year of publication.
+Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope.
+As shown in Figure \ref{fig:fig-heatmap}, the physical sciences do not show a trend of change in representation, while all other sciences showed a positive effect increasing in the number of geopolitical regions authors represent on publications.
+
+Last, we examined the differences in representation for corresponding author sets versus all other authors.
+For papers with 10 to 49 authors, we used the three first authors and the last author to compare against other authors.
+For 50 to 99 authors, five first authors plus last were used, and for all papers with more than 100 authors, we used ten first authors and the last author as the corresponding author set.
+We then calculated the frequencies of each of the UN Sub-Regions for corresponding authors versus all other authors, converting these values to proportions.
+Given the expected small sample sizes of these contingency tables, we grouped together titles based on the year of publication.
+For each grouping, we then calculated the effect size of the differences in frequencies comparing corresponding authors to all other authors.
+Since this data is categorical, we used Cramer's \emph{V} to represent the effect size.
+If the effect size includes zero in its confidence interval (to four decimal places), this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity.
+Any confidence interval that does include zero represents a difference in diversity.
 
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/author-gpe-figure-1.pdf}
-\caption{\label{fig:author-gpe-figure}A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors.}
+\includegraphics{manuscript_scopus_files/figure-latex/fig-author-gpe-1.pdf}
+\caption{\label{fig:fig-author-gpe}A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors.}
 \end{figure}
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/effect-gpe-figure-1.pdf}
-\caption{\label{fig:effect-gpe-figure}Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.}
+\includegraphics{manuscript_scopus_files/figure-latex/fig-effect-gpe-1.pdf}
+\caption{\label{fig:fig-effect-gpe}Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
+Larger dots indicate more papers and authors represented in the calculation of effect size.}
 \end{figure}
+
+Figure \ref{fig:fig-author-gpe} indicates the percent of authors in regions.
+In general, we found the same pattern as the overall analysis wherein most authors are from Europe and North America.
+The pattern of representation is roughly similar for the separation of small, medium, and large numbers of authors on papers.
+Across time, the representation does appear to diversify, with more representation in Asia, Latin American, and Africa.
+Figure \ref{fig:fig-effect-gpe} represents the size of the differences in first/corresponding authors and other authors across time and number of authors.
+The differences in representation are larger for papers with more authors; however, the effects are non-zero for many of the comparisons.
+Encouragingly, over time these effects appear to diminish in size.
+One limitation with the calculation of effect sizes for count data is the sensitivity of the data to sample size (i.e., \(\chi^2\) is upwardly biased by sample size, and \(V\) is calculated based on this value).
+While we used the inclusion of zero as our boundary for ``significance'', the interpretation of the effects is that most are likely small: \(V\) \textless{} .05: 31.79\%, \textless{} .10: 70.20\%, \textless{} .20: 94.04\%.
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\begin{itemize}
+\tightlist
+\item
+  number of publications increasing
+\item
+  research areas appear to be cancer, physics, and psychology
+\item
+  the number of authors is increasing as well
+\item
+  career length is decreasing, number of publications necessary to be involved is decreasing
+\item
+  number of gpe increasing
+\item
+  appears to be slowly diversifying, yet still not equal in first and other authors in diversity
+\end{itemize}
+
+limitations - based on the data we could get, we made up the definition of BTS, under-representation of articles in other languages/that they don't collect
+
+future: incentives for bts and why people do it
 
@@
 
+\hypertarget{supplemental-materials}{%
+\section{Supplemental Materials}\label{supplemental-materials}}
+
 \hypertarget{rq1-publisher-information.-2}{%
@@
 
+\textbf{\emph{Education}}.
+As noted in our pre-registration, we would only present this variable if we could obtain at least 50\% information on the authors who publish in big team science papers.
+95.83\% of the data was not available.
+
 \textbf{\emph{Types of Publications}}.
+
+Types of publications are presented in Figure \ref{fig:fig-pub-types}.
+The patterns of publications are roughly similar for big team science authors and all authors.
+It appears that porportionally, big team members are more likely to post preprints in comparison to all authors.
 

### 2023-08-29 manuscript_scopus.Rmd
updating manuscript

@@
 abstract: |
-  This paper examined the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions.
-As interest in BTS increases, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
-The types of publication outlets, number of publications, and subject areas of publication are presented to summarize the publications in BTS.
-Information about authors included in BTS will be presented including career length, numbers of publications/impact variables, education, and affiliation.
-Last, we will explore the representation of geopolitical regions by examining affiliation location to explore the impact of BTS on the de-WEIRD movement to diversify researcher representation.
-REWRITE THIS
+  This paper examined the nature of publications in Big Team Science (BTS): large-scale collaborations between multiple researchers at multiple institutions.
+These projects can improve research by initiating collaborations that span across the globe, age groups, education levels, and subfields of research.
+As the number of BTS publications increase, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
+We examined the diversity of BTS publications and authors across more than half a million articles to investigate where and what is currently published, and author characteristics including differences in career length, publication metrics, affiliation, and affiliation geopolitical regions.
+Interestingly, BTS publications are increasingly dominated by early career researchers from WEIRD geopolitical regions with Health and Physical Science accounting for the majority of BTS articles.
+However, the increase in preprints, BTS articles, and non-WEIRD authors across time demonstrate the efforts of the science community to diversify its researchers.
 
@@
 projects, which in turn allows for more reliability and generalizability
-in the results and method of the study. For this study, Big Team Science
-(BTS) will be defined as a collaboration of ten or more authors from at
-least ten different institutions.
-
-BTS appears to be increasing as a result of two sources: 1) increasing
+in the results and method of the study.
+
+BTS appears to be expanding as a result of two sources: 1) increasing
 globalization and technology that allows for real-time interdisciplinary
-research, and 2) increasing interest in reproducibility, replication,
+research, and 2) expanding interest in reproducibility, replication,
 and generalizability [@maxwell2015; @nelson2018; @zwaan2018].
@@
 messaging and project management platforms (e.g., Slack, Trello,
-when2meet, etc.). The credibility movement seems to suggest that by
-having both collaborations that span across the globe and subfields of
-research areas, age groups, and education levels should help to drive
-science in the path of better materials, reliability, generalizability
-and more robust sample sizes (when necessary) in a study
-[@auspurg2021has; @nosek2014method; @lebel2018].
-
-The credibility movement was originally defined by a focus on large
-scale replications using in collaborative environments [@vazire2022].
+when2meet, etc.).
+The credibility movement seems to suggest that by having both collaborations that span across the globe and subfields of research areas, age groups, and education levels should help to drive science in the path of better materials, reliability, generalizability and more robust sample sizes (when necessary) in a study [@auspurg2021has; @nosek2014method; @lebel2018].
+
+The credibility movement was originally defined by a focus on large scale replications used in collaborative environments [@vazire2022].
 Generally, the movement appears to have been driven by early career
@@
 Science Collaboration [@opensciencecollaboration2015], Many Labs
-Collaborations [for example, @klein2018; @ebersole2020; @ebersole2016;
+Collaborations [@klein2018; @ebersole2020; @ebersole2016;
 @klein2022; @mathur2020; @buttrick2020; @skorb2020] or the first papers
 from the Psychological Science Accelerator [@moshontz2018; @jones2021;
-@dorison2022; @wang2021; @legate2022; @bago2022]. Generally, the
-researcher incentive for replication was low: journals often prioritize
-"novel" or new results which led to rejection of replication manuscripts
-and publication bias [@hubbard1997; @franco2014; @nosek2012], the
+@dorison2022; @wang2021; @legate2022; @bago2022].
+Generally, the researcher incentive for replication was low for three reasons.
+First, journals often prioritize “novel” or new results which led to rejection of replication manuscripts and publication bias [@hubbard1997; @franco2014; @nosek2012].
+Second, the
 "failure" to replicate was often placed on the replication team as "bad
@@
 (potential) questionable research practices [@ioannidis2015;
-@maxwell2015; @klein2022], and why should someone want to spend time and
+@maxwell2015; @klein2022]. Last, why should someone want to spend time and
 resources on an answer we already "know" [@isager2021; @isager2021a]?
@@
 large-scale studies in Physics [@aphilos2021; @castelnovo2018] and
-Biology [@collins2003], the social sciences struggle to represent the
+Biology [@collins2003], the Social Sciences struggle to represent the
 breadth of humanity across both researcher and population
@@
 
-```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years.", fig.width=10, fig.height=6}
+```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years.
+All four subject areas show an exponential number of publications in the last decade.
+", fig.width=10, fig.height=6}
 ggplot(DF$pub_time_count %>% 
@@
        aes(Year, count, color = SubjectArea)) + 
-  theme_classic() + 
+  theme_classic(base_size = 15) + 
   geom_point() + 
@@
 creating a word cloud plot of the total number of publications within
-the ASJCs. Figure \@ref(fig:fig-clouds) displays that the health
-sciences tends to publish within medicine and oncology, with a
-corresponding focus of cancer research and genetics for the life
-sciences. The physical sciences is mostly dominated by physics research,
-chemistry, and ecology. The BTS publications in the social sciences are
+the ASJCs. Figure \@ref(fig:fig-clouds) displays that the Health
+Sciences tends to publish within medicine and oncology, with a
+corresponding focus of cancer research and genetics for the Life
+Sciences. The Physical Sciences is mostly dominated by physics research,
+chemistry, and ecology. The BTS publications in the Social Sciences are
 mostly within psychology, education, and health.
@@
 authors increased over time, with the exception of the skew in the
-physical sciences. Interestingly, the effect in the physical sciences
+Physical Sciences. Interestingly, the effect in the Physical Sciences
 appears to be declining toward the general trends seen in other areas in
@@
 indicating a trend toward younger scientist involvement over time for
-each area, with the strongest effect in the Physical sciences. The
+each area, with the strongest effect in the Physical Sciences. The
 coefficient for variability in career length was also negative for each
-of the four subject areas with the highest in the Physical sciences and
+of the four subject areas with the highest in the Physical Sciences and
 lowest in the Life Sciences. This result indicates a decrease in the
@@
 the average publication metrics, indicating more scholars over time with
-lower numbers of publications with the strongest effects in health and
-social sciences. The variability of publication counts was not
-significant for the life sciences but was negative for the physical
-sciences (less variability over time) and positive for social and health
-sciences (more variability and over time). This result indicates that
-the physical sciences are trending toward scholars with less
+lower numbers of publications with the strongest effects in Health and
+Social Sciences. The variability of publication counts was not
+significant for the Life Sciences but was negative for the Physical
+Sciences (less variability over time) and positive for Social and Health
+Sciences (more variability and over time). This result indicates that
+the Physical Sciences are trending toward scholars with less
 publications but also less diverse in number of publications, while the
-health and social sciences see more diversity in publication counts and
+Health and Social Sciences see more diversity in publication counts and
 less published scholars overall.
@@
 represented by a negative slope. As shown in Figure
-\@ref(fig:fig-heatmap), the physical sciences do not show a trend of
+\@ref(fig:fig-heatmap), the Physical Sciences do not show a trend of
 change in representation, while all other sciences showed a positive
@@
 authors and ten different affiliations. The areas of publication aligned
-to cancer and genetics research in medicine and oncology for medical and
-life sciences, physics and chemistry for the physical sciences, and
-psychology for the social sciences. All areas of research show an
+to cancer and genetics research in medicine and oncology for Health and
+Life Sciences, physics and chemistry for the Physical Sciences, and
+psychology for the Social Sciences All areas of research show an
 explosion in growth in the number of publications and the number of
@@
 above. The variability in number of publications is decreasing in the
-physical sciences, mirroring the career length results, but the opposite
-effect was found in the health and social sciences. We see no clear
+Physical Sciences, mirroring the career length results, but the opposite
+effect was found in the Health and Social Sciences. We see no clear
 reason why career variability would decrease while the variability in
@@
 region, and thus, a manuscript could rely solely on institutions within
-a single country. The physical sciences did not show an increase in
+a single country. The Physical Sciences did not show an increase in
 diversity of regions represented, however, it could be argued that the
@@
 than other sciences (i.e., because CERN specifically recruited
-scientists from sponsoring nations). The life, health, and social
-sciences saw an increase in the number of regions represented with the
-highest increase in the social science. This result likely corresponds
+scientists from sponsoring nations). The Life, Health, and Social
+Sciences saw an increase in the number of regions represented with the
+highest increase in the Social Science. This result likely corresponds
 with an increased interest in big team science publications in

### 2023-08-29 appendix.Rmd
update the pictures for reading

@@
 Institution was normalized by taking the total number of unique institutions and dividing by the total number of institution listings.
-The patterns are similar for each decade in that papers are often either half unique institutions or mostly unique institutions overall as show in Figure \@ref(fig:fig-inst).
+The patterns are similar for each decade in that papers are often either half unique institutions or mostly unique institutions overall as shown in Figure \@ref(fig:fig-inst).
 
@@
   geom_density_ridges2() + 
-  theme_classic() + 
+  theme_classic(base_size = 15) + 
   facet_wrap(~SubjectArea) + 
@@
   scale_fill_brewer(name = "Sample Size", palette = "Spectral") +
-  theme_classic()
+  theme_classic(base_size = 15)
 

### 2023-08-29 manuscript_scopus.Rmd
update the pictures for reading

@@
 # header-includes:
-# csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+csl               : "includes/nature.csl"
 # documentclass     : "apa7"
-output            : papaja::apa6_docx
+output            : papaja::apa6_pdf
 appendix          :
@@
 
-```
-
-```{r data, include = FALSE}
 # things to import
@@
 science, the current interest of "big team science" is increasing
-[@forscher2020; @stewart2017; @coles2022]. Big team science projects
+[@coles2022; @forscher2022a; @stewart2017]. Big team science projects
 and/or organizations utilize and run on large-scale collaboration to
@@
 globalization and technology that allows for real-time interdisciplinary
-research, and 2) expanding interest in reproducibility, replication,
-and generalizability [@maxwell2015; @nelson2018; @zwaan2018].
-Technological advances have provided easier ways to collaborate with
-people who are from other universities and countries through document
-sharing platforms (e.g., Google, GitHub, and the Open Science
-Framework), video chatting platforms (e.g., Zoom, Microsoft Teams), and
-messaging and project management platforms (e.g., Slack, Trello,
-when2meet, etc.).
-The credibility movement seems to suggest that by having both collaborations that span across the globe and subfields of research areas, age groups, and education levels should help to drive science in the path of better materials, reliability, generalizability and more robust sample sizes (when necessary) in a study [@auspurg2021has; @nosek2014method; @lebel2018].
-
-The credibility movement was originally defined by a focus on large scale replications used in collaborative environments [@vazire2022].
+research, and 2) expanding interest in reproducibility, replication, and
+generalizability [@maxwell2015; @nelson2018; @zwaan2018]. Technological
+advances have provided easier ways to collaborate with people who are
+from other universities and countries through document sharing platforms
+(e.g., Google, GitHub, and the Open Science Framework), video chatting
+platforms (e.g., Zoom, Microsoft Teams), and messaging and project
+management platforms (e.g., Slack, Trello, when2meet, etc.). The
+credibility movement seems to suggest that by having both collaborations
+that span across the globe and subfields of research areas, age groups,
+and education levels should help to drive science in the path of better
+materials, reliability, generalizability and more robust sample sizes
+(when necessary) in a study [@auspurg2021]; @nosek2014method;
+@lebel2018].
+
+The credibility movement was originally defined by a focus on large
+scale replications used in collaborative environments [@vazire2022].
 Generally, the movement appears to have been driven by early career
@@
 Science Collaboration [@opensciencecollaboration2015], Many Labs
-Collaborations [@klein2018; @ebersole2020; @ebersole2016;
-@klein2022; @mathur2020; @buttrick2020; @skorb2020] or the first papers
-from the Psychological Science Accelerator [@moshontz2018; @jones2021;
-@dorison2022; @wang2021; @legate2022; @bago2022].
-Generally, the researcher incentive for replication was low for three reasons.
-First, journals often prioritize “novel” or new results which led to rejection of replication manuscripts and publication bias [@hubbard1997; @franco2014; @nosek2012].
-Second, the
-"failure" to replicate was often placed on the replication team as "bad
-science" rather than a careful consideration of publication biases and
-(potential) questionable research practices [@ioannidis2015;
-@maxwell2015; @klein2022]. Last, why should someone want to spend time and
-resources on an answer we already "know" [@isager2021; @isager2021a]?
+Collaborations [@buttrick2020; @ebersole2016; @ebersole2020; @klein2018;
+@klein2022; @mathur2020; @skorb2020] or the first papers from the
+Psychological Science Accelerator [@bago2022; @buchanan2023;
+@dorison2022; @jones2021;
+@psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
+@moshontz2018; @wang2021]. Generally, the researcher incentive for
+replication was low for three reasons. First, journals often prioritize
+"novel" or new results which led to rejection of replication manuscripts
+and publication bias [@franco2014; @hubbard1997; @nosek2012]. Second,
+the "failure" to replicate was often placed on the replication team as
+"bad science" rather than a careful consideration of publication biases
+and (potential) questionable research practices [@klein2022;
+@maxwell2015]. Last, why should someone want to spend time and resources
+on an answer we already "know" [@isager2021; @isager2021a]?
 
@@
 Publications have examined the global understanding of morality, face
-processing, COVID-19 information signaling, and more [@dorison2022;
-@wang2021; @legate2022; @bago2022; @jones2021; @vanbavel2022]. While
-these organizations and one-time groups for BTS studies have provided an
-incredible wealth of data for the scientific community, we do not yet
-know exactly *who* is involved with, and benefits from, the BTS and
-credibility movement. Publications on BTS generally explore challenges,
-lessons learned, and the need for BTS [@forscher2020; @coles2022].
+processing, COVID-19 information signaling, and more [@bago2022;
+@dorison2022; @jones2021;
+@psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
+@vanbavel2022; @wang2021]. While these organizations and one-time groups
+for BTS studies have provided an incredible wealth of data for the
+scientific community, we do not yet know exactly *who* is involved with,
+and benefits from, the BTS and credibility movement. Publications on BTS
+generally explore challenges, lessons learned, and the need for BTS
+[@forscher2022a; @coles2022].
 
@@
 `r life_journal` journals in Life Sciences. The descriptive statistics
-for the Source Normalized Impact per Paper is presented the supplemental
-materials with a comparison for all papers.
+for the Source Normalized Impact per Paper is presented in the
+supplemental materials with a comparison for all papers.
 
@@
 corresponding focus of cancer research and genetics for the Life
-Sciences. The Physical Sciences is mostly dominated by physics research,
-chemistry, and ecology. The BTS publications in the Social Sciences are
-mostly within psychology, education, and health.
+Sciences. The Physical Sciences was mostly dominated by physics
+research, chemistry, and ecology. The BTS publications in the Social
+Sciences are mostly within psychology, education, and health.
 
@@
 
-```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area", fig.width=10, fig.height=6}
+```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area.
+Larger words indicate more publications in those ASJC areas.
+", fig.width=10, fig.height=6}
 
@@
   ggplot(avg_author_time, aes(Year, Med_Num_Authors, color = SubjectArea)) + 
-  theme_classic() + 
+  theme_classic(base_size = 15) + 
   geom_point() + 
@@
   ggplot(avg_author_time, aes(Year, Average_Num_Authors, color = SubjectArea)) + 
-  theme_classic() + 
+  theme_classic(base_size = 15) + 
   geom_point() + 
@@
 regression analyses to compare coefficient strength across and within
-hypothesis.
-
-All values for this analyses were different from zero. The slopes for
+each hypothesis.
+
+All values for these analyses were different from zero. The slopes for
 the average career length were negative for all four subject areas,
@@
 estimations, and 2) more young scholars overall. The effect sizes for
-this analysis were surprisingly large ranging from $R^2$ to .25 to .47.
+this analysis were surprisingly large ranging from $R^2$ = .25 to .47.
 All values and their confidence intervals can be found on our OSF page.
 
-```{r fig-career, include = TRUE, fig.cap = "Average career length for big-team science authors.
+```{r fig-career, include = TRUE,  warning = FALSE, message = FALSE, fig.cap = "Average career length for big-team science authors.
 Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year.
 The data has been filtered to at least 10 publications in a year for this graph.", fig.width=10, fig.height=6}
-ggplot(DF$career_time %>% 
+temp <- ggplot(DF$career_time %>% 
          filter(SubjectArea != "Multidisciplinary") %>% 
@@
        aes(Year, avg_career, color = SubjectArea)) +
-  theme_classic() + 
+  theme_classic(base_size = 15) + 
   geom_point(aes(size = sd_career)) +
@@
   #scale_size_continuous(name = "Number Papers")
+
+suppressWarnings(suppressMessages(temp))
 
@@
 
-```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity in region.
+```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region.
 The top figure represents all results together for comparison across analyses.
 The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.
-Non-significant results are indicated with NS on the plot.", fig.width=10, fig.height=6}
+Non-significant results are indicated with NS on the plot.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6}
 graph_overall <- graph_data %>% 
@@
   facet_wrap(~analysis) + 
-  theme_classic() + 
+  theme_classic(base_size = 15) + 
   theme(axis.text.x = element_text(angle = 60, vjust = .5), 
@@
   xlab("") + 
-  theme_classic() + 
+  theme_classic(base_size = 15) + 
   theme(axis.text.x = element_text(angle = 60, vjust = .5), 
@@
 "
-suppressWarnings(heat_results + 
+suppressMessages(suppressWarnings(heat_results + 
   heat_results_1 + heat_results_2 + heat_results_3 + 
-  plot_layout(design = layout))
+  plot_layout(design = layout)))
 
@@
 
-The average number of publications by authors on big team sciences
-papers is *M* = `r avg_pub_count_author` (*SD* =
-`r std_pub_count_author`). The publication counts were averaged across
-authors for each publication, and then these average publication counts
-were averaged across publications *M* = `r avg_pub_count_paper` (*SD* =
+The average number of publications by authors on big team science papers
+is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`). The
+publication counts were averaged across authors for each publication,
+and then these average publication counts were averaged across
+publications *M* = `r avg_pub_count_paper` (*SD* =
 `r sd_pub_count_paper`). The average variability (i.e., the average
@@
                colour = 'black', fill = NA) + 
-  theme_void() + 
+  theme_void(base_size = 15) + 
   # scale_fill_manual(name = "Sample Size",
@@
 
-```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.", fig.width=10, fig.height=6}
+```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.
+The mosaic plot is grouped by UN subregion with the largest number of publications on the left and smallest on the top right.
+", fig.width=10, fig.height=6}
 bin_country + ggtitle("Big-Team Publication Map") + 
@@
 Author geopolitical region is displayed in Figure
-\@ref(fig:fig-map-both). Big team publications appear to be lead by
-North America and Western Europe, while all publications are lead by
-North America and East Asia. To understand the change in representation
+\@ref(fig:fig-map-both). Big team publications appear to be led by North
+America and Western Europe, while all publications are led by North
+America and East Asia. To understand the change in representation
 diversity, we examined if the number of regions in a publication is
@@
   geom_point(aes(size = people)) + 
-  theme_classic() + 
+  theme_classic(base_size = 15) + 
   geom_pointrange(aes(ymin = low, ymax = high)) + 
@@
     geom_bar(position="fill", stat="identity", color = "black") + 
-  theme_classic() + 
+  theme_classic(base_size = 15) + 
   facet_grid(~Decade) + 
@@
 
-```{r fig-author-gpe, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades.
+```{r fig-author-gpe, include = TRUE, fig.cap="A comparison of author affiliation geopolitical regions across decades.
 F stands for first authors and O stands for other authors.", fig.width=10, fig.height=6}
@@
   geom_linerange(aes(ymin = low, ymax = high), alpha = .5) +
-  theme_classic() +
+  theme_classic(base_size = 15) +
   theme(legend.position = "none") + 
@@
 that most are likely small: $V$ \< .05:
-`r apa_num(sum(all_effects$v <.05)/nrow(all_effects)*100)`%, \< .10:
-`r apa_num(sum(all_effects$v < .10)/nrow(all_effects)*100)`%, \< .20:
-`r apa_num(sum(all_effects$v < .20)/nrow(all_effects)*100)`%.
+`r apa_num(sum(all_effects$v <.05)/nrow(all_effects)*100)`%, $V$ \< .10:
+`r apa_num(sum(all_effects$v < .10)/nrow(all_effects)*100)`%, $V$ \<
+.20: `r apa_num(sum(all_effects$v < .20)/nrow(all_effects)*100)`%.
 
@@
 half-million articles were published in nearly 15,000 journals since
-1970 that qualified as big team science articles with at least ten
-authors and ten different affiliations. The areas of publication aligned
+1970 that qualified as big team science articles (at least ten authors
+and ten different affiliations). The areas of publication were aligned
 to cancer and genetics research in medicine and oncology for Health and
@@
 explosion in growth in the number of publications and the number of
-author included on manuscripts, replicating previous investigations into
-this topic area [@sinatra2015; @wuchty2007; @hunter2008].
+authors included on manuscripts, replicating previous investigations
+into this topic area [@sinatra2015; @wuchty2007; @hunter2008].
 
@@
 
-The results for number of publications by big team researchers mimics
-the findings from career length, with a smaller effect size. In general,
-it appears that there is a decrease in the average number of
+The results for the number of publications by big team researchers
+mimics the findings from career length, with a smaller effect size. In
+general, it appears that there is a decrease in the average number of
 publications a researcher has when publishing on a big team science
@@
 are potentially driving forces behind our results, but, hopefully, the
-results also point to a decline in scientific gatekeeping [@siler2015;
-@lu2007].
+results also point to a decline in scientific gatekeeping [@lu2007;
+@siler2015].
 
@@
 also decreased across time in most areas of science with a decrease in
-variability for career length. As mention, an increase in early career
+variability for career length. As mentioned, an increase in early career
 researchers and numbers of publications could explain this effect
 mathematically, potentially with other social influences mentioned
-above. The variability in number of publications is decreasing in the
-Physical Sciences, mirroring the career length results, but the opposite
-effect was found in the Health and Social Sciences. We see no clear
-reason why career variability would decrease while the variability in
-the number of publications would increase. The effect sizes for career
-length were much larger than the effects for number of publications. One
-speculation is the increasing requirements for a competitive faculty
-role application. Given the limited number of positions, one potential
-way to distinguish their application would be a larger number
-publications in their early career [@caplow2017; @kyvik2003].
+above. The variability in the number of publications is decreasing in
+the Physical Sciences, mirroring the career length results, but the
+opposite effect was found in the Health and Social Sciences. We see no
+clear reason why career variability would decrease while the variability
+in the number of publications would increase. The effect sizes for
+career length were much larger than the effects for number of
+publications. One speculation is the increasing requirements for a
+competitive faculty role application. Given the limited number of
+positions, one potential way to distinguish their application would be a
+larger number of publications in their early career [@caplow2017;
+@kyvik2003].
 
@@
 Sciences saw an increase in the number of regions represented with the
-highest increase in the Social Science. This result likely corresponds
+highest increase in the Social Sciences. This result likely corresponds
 with an increased interest in big team science publications in
-psychology [@coles2022; @forscher2020], and the desire to diversify the
+psychology [@coles2022; @forscher2022a], and the desire to diversify the
 populations represented in psychological research [@henrich2010;
@@
 if they are slowly decreasing. Diverse teams are more likely to have
-papers with stronger "impact" [@jones2008; @hinnant2012; @yang2022;
-@freeman2015] with higher citation metrics for more diverse author
-lists. The introduction of contributorship models [e.g., CRediT;
-@allen2019] will hopefully continue to push these effects down, as they
-highlight each individual's contribution to a manuscript.
+papers with stronger "impact" [@freeman2015; @hinnant2012; @jones2008;
+@yang2022] with higher citation metrics for more diverse author lists.
+The introduction of contributorship models [e.g., CRediT @allen2019]
+will hopefully continue to push these effects down, as they highlight
+each individual's contribution to a manuscript.
 
@@
 collaboration from interpersonal conflict, infrastructure, incentives,
-to international political situations [@forscher2020]. Directed studies
+to international political situations [@forscher2022a]. Directed studies
 into ways to navigate these situations would be beneficial for policy

### 2023-08-29 manuscript_scopus.tex
update the pictures for reading

@@
 \abstract{%
-This paper examined the nature of publications in Big Team Science (BTS) - large-scale collaborations between multiple researchers at multiple institutions.
-As interest in BTS increases, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
-The types of publication outlets, number of publications, and subject areas of publication are presented to summarize the publications in BTS.
-Information about authors included in BTS will be presented including career length, numbers of publications/impact variables, education, and affiliation.
-Last, we will explore the representation of geopolitical regions by examining affiliation location to explore the impact of BTS on the de-WEIRD movement to diversify researcher representation.
-REWRITE THIS
+This paper examined the nature of publications in Big Team Science (BTS): large-scale collaborations between multiple researchers at multiple institutions.
+These projects can improve research by initiating collaborations that span across the globe, age groups, education levels, and subfields of research.
+As the number of BTS publications increase, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
+We examined the diversity of BTS publications and authors across more than half a million articles to investigate where and what is currently published, and author characteristics including differences in career length, publication metrics, affiliation, and affiliation geopolitical regions.
+Interestingly, BTS publications are increasingly dominated by early career researchers from WEIRD geopolitical regions with Health and Physical Science accounting for the majority of BTS articles.
+However, the increase in preprints, BTS articles, and non-WEIRD authors across time demonstrate the efforts of the science community to diversify its researchers.
 }
@@
 According to the Oxford English dictionary, collaboration is two or more
-people working together to achieve a certain goal (OED, 2016).
+people working together to achieve a certain goal\textsuperscript{1}.
 Collaboration in scientific endeavors involves multiple researchers at
@@
 perspectives of collaborators. While collaboration is not new in
-science, the current interest of ``big team science'' is increasing
-(Coles, Hamlin, Sullivan, Parker, \& Altschul, 2022; Forscher et al., 2020; N. Stewart, Chandler, \& Paolacci, 2017). Big team science projects
+science, the current interest of ``big team science'' is increasing\textsuperscript{2--4}. Big team science projects
 and/or organizations utilize and run on large-scale collaboration to
@@
 projects, which in turn allows for more reliability and generalizability
-in the results and method of the study. For this study, Big Team Science
-(BTS) will be defined as a collaboration of ten or more authors from at
-least ten different institutions.
-
-BTS appears to be increasing as a result of two sources: 1) increasing
+in the results and method of the study.
+
+BTS appears to be expanding as a result of two sources: 1) increasing
 globalization and technology that allows for real-time interdisciplinary
-research, and 2) increasing interest in reproducibility, replication,
-and generalizability (Maxwell, Lau, \& Howard, 2015; Nelson, Simmons, \& Simonsohn, 2018; Zwaan, Etz, Lucas, \& Donnellan, 2018).
-Technological advances have provided easier ways to collaborate with
-people who are from other universities and countries through document
-sharing platforms (e.g., Google, GitHub, and the Open Science
-Framework), video chatting platforms (e.g., Zoom, Microsoft Teams), and
-messaging and project management platforms (e.g., Slack, Trello,
-when2meet, etc.). The credibility movement seems to suggest that by
-having both collaborations that span across the globe and subfields of
-research areas, age groups, and education levels should help to drive science in the path of better materials, reliability,
-generalizability and more robust sample sizes (when necessary) in a study
-(Auspurg \& Brüderl, 2021; LeBel, McCarthy, Earp, Elson, \& Vanpaemel, 2018; Brian A. Nosek \& Lakens, 2014a).
+research, and 2) expanding interest in reproducibility, replication, and
+generalizability\textsuperscript{5--7}. Technological
+advances have provided easier ways to collaborate with people who are
+from other universities and countries through document sharing platforms
+(e.g., Google, GitHub, and the Open Science Framework), video chatting
+platforms (e.g., Zoom, Microsoft Teams), and messaging and project
+management platforms (e.g., Slack, Trello, when2meet, etc.). The
+credibility movement seems to suggest that by having both collaborations
+that span across the globe and subfields of research areas, age groups,
+and education levels should help to drive science in the path of better
+materials, reliability, generalizability and more robust sample sizes
+(when necessary) in a study\textsuperscript{8};\textsuperscript{9};\textsuperscript{10}{]}.
 
 The credibility movement was originally defined by a focus on large
-scale replications using in collaborative environments (Vazire, Schiavone, \& Bottesini, 2022).
-Generally, the movement appears to have been driven by early career researchers
-(i.e., those who are within five years of their first appointment)
-(Maizey \& Tzavella, 2019); however, there are no large meta-scientific
+scale replications used in collaborative environments\textsuperscript{11}.
+Generally, the movement appears to have been driven by early career
+researchers (i.e., those who are within five years of their first
+appointment)\textsuperscript{12}; however, there are no large meta-scientific
 investigations on this specific topic to date. Potentially, the lack of
@@
 fields, as it is only in recent years that publications like the Open
-Science Collaboration (Open Science Collaboration, 2015), Many Labs
-Collaborations (Buttrick et al., 2020; Ebersole et al., 2016, 2020; Richard A.
-Klein et al., 2022; for example, Richard A.
-Klein et al., 2018; Mathur et al., 2020; Skorb et al., 2020) or the first papers
-from the Psychological Science Accelerator (Bago et al., 2022; Dorison et al., 2022; Jones et al., 2021; Legate et al., 2022; Moshontz et al., 2018; Wang et al., 2021). Generally, the
-researcher incentive for replication was low: journals often prioritize
+Science Collaboration\textsuperscript{13}, Many Labs
+Collaborations\textsuperscript{14--20} or the first papers from the
+Psychological Science Accelerator\textsuperscript{21--27}. Generally, the researcher incentive for
+replication was low for three reasons. First, journals often prioritize
 ``novel'' or new results which led to rejection of replication manuscripts
-and publication bias (Franco, Malhotra, \& Simonovits, 2014; Hubbard \& Armstrong, 1997; Brian A. Nosek, Spies, \& Motyl, 2012), the
-``failure'' to replicate was often placed on the replication team as ``bad
-science'' rather than a careful consideration of publication biases and
-(potential) questionable research practices (Ioannidis, 2015; Richard A. Klein et al., 2022; Maxwell et al., 2015), and why should someone want to spend time and
-resources on an answer we already ``know'' (Isager et al., 2021a, 2021b)?
+and publication bias\textsuperscript{28--30}. Second,
+the ``failure'' to replicate was often placed on the replication team as
+``bad science'' rather than a careful consideration of publication biases
+and (potential) questionable research practices\textsuperscript{5,18}. Last, why should someone want to spend time and resources
+on an answer we already ``know''\textsuperscript{31,32}?
 
 However, the success and interest in the large-scale reproducibility
-projects (Errington et al., 2021; Open Science Collaboration, 2015), paired
+projects\textsuperscript{13,33}, paired
 with the meta-scientific publications focusing on researcher practices
-and incentive structures (John, Loewenstein, \& Prelec, 2012; Silberzahn et al., 2018) led to a
+and incentive structures\textsuperscript{34,35} led to a
 change in journal guidelines and incentives for researchers interested
-in participating in large-scale replication studies (Grahe, 2014; Kidwell et al., 2016; Mayo-Wilson et al., 2021; B. A. Nosek et al., 2015). For example, the support
+in participating in large-scale replication studies\textsuperscript{36--39}. For example, the support
 for Registered Reports, papers accepted before the data has been
-collected (Brian A. Nosek \& Lakens, 2014b; S. Stewart et al., 2020), and entire sub-sections of
-journals devoted to only replication studies (e.g., \emph{Nature, Royal Society Open Science, Advances in Methods and Practices in Psychological Science}) has allowed researchers to invest in projects that they know
+collected\textsuperscript{40,41}, and entire sub-sections of
+journals devoted to only replication studies (e.g., \emph{Nature, Royal
+Society Open Science, Advances in Methods and Practices in Psychological
+Science}) has allowed researchers to invest in projects that they know
 should be published when the project is complete. Further, the
-implementation of the Transparency and Openness Guidelines (B. A. Nosek et al., 2015)
-and the Contributor Role Taxonomy (CRediT) system (Allen, O'Connell, \& Kiermer, 2019) have
+implementation of the Transparency and Openness Guidelines\textsuperscript{38}
+and the Contributor Role Taxonomy (CRediT) system\textsuperscript{42} have
 pushed journals and researchers to promote more open, inclusive
@@
 diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
-Rich, and Democratic) scientific research (Henrich, Heine, \& Norenzayan, 2010; Newson, Buhrmester, Xygalatas, \& Whitehouse, 2021; Rad, Martingano, \& Ginges, 2018) by improving representation in research samples.
-Like the
-large-scale studies in Physics ({``A Philosophical Case for Big Physics,''} 2021; Castelnovo, Florio, Forte, Rossi, \& Sirtori, 2018) and
-Biology (Collins, Morgan, \& Patrinos, 2003), the social sciences struggle to represent the
+Rich, and Democratic) scientific research\textsuperscript{43--45} by improving representation in research samples. Like the
+large-scale studies in Physics\textsuperscript{46,47} and
+Biology\textsuperscript{48}, the Social Sciences struggle to represent the
 breadth of humanity across both researcher and population
 characteristics. Now, grassroots organizations, such as the
-Psychological Science Accelerator (Moshontz et al., 2018), ManyBabies
+Psychological Science Accelerator\textsuperscript{26}, ManyBabies
 (\url{https://manybabies.github.io/}), NutNet (\url{https://nutnet.org/}), and
@@
 Publications have examined the global understanding of morality, face
-processing, COVID-19 information signaling, and more (Bago et al., 2022; Dorison et al., 2022; Jones et al., 2021; Legate et al., 2022; Van Bavel et al., 2022; Wang et al., 2021). While
-these organizations and one-time groups for BTS studies have provided an
-incredible wealth of data for the scientific community, we do not yet
-know exactly \emph{who} is involved with, and benefits from, the BTS and
-credibility movement. Publications on BTS generally explore challenges,
-lessons learned, and the need for BTS (Coles et al., 2022; Forscher et al., 2020).
+processing, COVID-19 information signaling, and more\textsuperscript{21,23--25,27,49}. While these organizations and one-time groups
+for BTS studies have provided an incredible wealth of data for the
+scientific community, we do not yet know exactly \emph{who} is involved with,
+and benefits from, the BTS and credibility movement. Publications on BTS
+generally explore challenges, lessons learned, and the need for BTS\textsuperscript{2,3}.
 
 Therefore, the goal of this manuscript is to examine the \emph{people}
-involved in BTS projects. We specifically examined the themes of inclusivity, research careers, and research globalization. We see an
-increasing interest and number of publications in BTS but we do not yet know if
-this uptick in large-scale projects has diversified the \emph{people}
+involved in BTS projects. We specifically examined the themes of
+inclusivity, research careers, and research globalization. We see an
+increasing interest and number of publications in BTS but we do not yet
+know if this uptick in large-scale projects has diversified the \emph{people}
 involved in BTS. While a few publications have noted that BTS appears to
-be early career researchers (Maizey \& Tzavella, 2019), no one has systematically
+be early career researchers\textsuperscript{12}, no one has systematically
 investigated this perception. Further, it is unclear if the focus of
@@
 
-This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr}) but then was updated with access to the Scopus database for a broader picture of BTS projects (\url{https://osf.io/fheun}).
-All materials and code can be found on our OSF page: \url{https://osf.io/cgx6u/} or corresponding GitHub archive: \url{https://github.com/doomlab/big_team_who}.
+This manuscript was preregistered with the same conceptual ideas using
+Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr}) but then
+was updated with access to the Scopus database for a broader picture of
+BTS projects (\url{https://osf.io/fheun}). All materials and code can be
+found on our OSF page: \url{https://osf.io/cgx6u/} or corresponding GitHub
+archive: \url{https://github.com/doomlab/big_team_who}.
 
@@
 
-\hypertarget{rq1-publisher-information.}{%
-\subsubsection{RQ1: Publisher Information.}\label{rq1-publisher-information.}}
-
-We extracted the following information for publication sources: the name of the publication (source title), subject area (both the large four subject areas and the smaller four digit all science journal classification {[}ASJC{]} code), and the journal
-impact using the Source Normalized Impact per Paper (SNIP).
-
-\hypertarget{rq2-publication-information.}{%
-\subsubsection{RQ2: Publication Information.}\label{rq2-publication-information.}}
-
-For each publication of the identified BTS publications, we examined
-the full four digit ASJC subject areas codes for each of the larger four
+\hypertarget{rq1-publisher-information}{%
+\subsubsection{RQ1: Publisher Information}\label{rq1-publisher-information}}
+
+We extracted the following information for publication sources: the name
+of the publication (source title), subject area (both the large four
+subject areas and the smaller four digit all science journal
+classification {[}ASJC{]} code), and the journal impact using the Source
+Normalized Impact per Paper (SNIP).
+
+\hypertarget{rq2-publication-information}{%
+\subsubsection{RQ2: Publication Information}\label{rq2-publication-information}}
+
+For each publication of the identified BTS publications, we examined the
+full four digit ASJC subject areas codes for each of the larger four
 subject areas and the keywords present for these publications.
 
-\hypertarget{rq3-author-information.}{%
-\subsubsection{RQ3: Author Information.}\label{rq3-author-information.}}
-
-The author list was extracted from each publication.
-Next, we used the author and affiliation arrays to curate a list of all publications and author information included in BTS papers to calculate the variables described below.
-
-\textbf{\emph{Career Length}}. Career length for each author was defined as
-the year of the first publication minus the current year listed for each author.
-
-\textbf{\emph{Institution and Geopolitical Region}}. We used the affiliation
-ids and country to gather information about the places of education
-and/or employment for authors. Geopolitical region was created by binning these codes into United Nation Regions.
-
-\textbf{\emph{Education}}. We collected degree information from the author table. Information on this variable is in the appendix.
-
-\textbf{\emph{Types of Publications}}. We took information from the
-publication type variable for each author's publications to present
-information about the types of papers BTS authors publish. Information on this variable is in the appendix.
+\hypertarget{rq3-author-information}{%
+\subsubsection{RQ3: Author Information}\label{rq3-author-information}}
+
+The author list was extracted from each publication. Next, we used the
+author and affiliation arrays to curate a list of all publications and
+author information included in BTS papers to calculate the variables
+described below.
+
+\textbf{\emph{Career Length}}. Career length for each author was defined as the
+year of the first publication minus the current year listed for each
+author.
+
+\textbf{\emph{Institution and Geopolitical Region}}. We used the affiliation ids
+and country to gather information about the places of education and/or
+employment for authors. Geopolitical region was created by binning these
+codes into United Nation Regions.
+
+\textbf{\emph{Education}}. We collected degree information from the author table.
+Information on this variable is in the appendix.
+
+\textbf{\emph{Types of Publications}}. We took information from the publication
+type variable for each author's publications to present information
+about the types of papers BTS authors publish. Information on this
+variable is in the appendix.
 
@@
 number of publications, and the h-index. The h-index represents the
-highest \emph{h} number of publications that have at least \emph{h} citations. \emph{h}-count was only used for descriptive statistics.
+highest \emph{h} number of publications that have at least \emph{h} citations.
+\emph{h}-count was only used for descriptive statistics.
 
@@
 
-We used the 95\% confidence interval to make decisions on predictor or effect size differences from zero.
-The confidence interval that does not include zero would be considered different from zero (to four decimal places).
-We made no directional predictions.
-
-\hypertarget{rq1-publisher-information.-1}{%
-\subsection{RQ1: Publisher Information.}\label{rq1-publisher-information.-1}}
-
-\emph{Number of articles}. The total number of articles included in this analysis was 510334 including 445301 Health Sciences articles, 228194
-Physical Sciences articles, 26652 Social Sciences articles, and
-307514 Life Sciences articles. Articles could be classified into
-multiple categories. Figure \ref{fig:fig-pub-time} shows the number of articles published across time for each of the four large subject areas.
+We used the 95\% confidence interval to make decisions on predictor or
+effect size differences from zero. The confidence interval that does not
+include zero would be considered different from zero (to four decimal
+places). We made no directional predictions.
+
+\hypertarget{rq1-publisher-information.}{%
+\subsection{RQ1: Publisher Information.}\label{rq1-publisher-information.}}
+
+\emph{Number of articles}. The total number of articles included in this
+analysis was 510334 including 445301 Health Sciences
+articles, 228194 Physical Sciences articles, 26652
+Social Sciences articles, and 307514 Life Sciences articles.
+Articles could be classified into multiple categories. Figure
+\ref{fig:fig-pub-time} shows the number of articles published across
+time for each of the four large subject areas.
 
@@
 \includegraphics{manuscript_scopus_files/figure-latex/fig-pub-time-1.pdf}
-\caption{\label{fig:fig-pub-time}Number of big-team science publications separated by four large subject areas across years.}
+\caption{\label{fig:fig-pub-time}Number of big-team science publications separated by four large subject areas across years.
+All four subject areas show an exponential number of publications in the last decade.}
 \end{figure}
 
-\emph{Number of journals}. The number of distinct journals big team science articles were published
-in was 14924 with 6559 journals in Health Sciences,
-5787 journals in Physical Sciences, 2500
-journals in Social Sciences, and 4187 journals in Life
-Sciences. The descriptive statistics for the Source Normalized Impact
-per Paper is presented the supplemental materials with a comparison for all papers.
-
-\hypertarget{rq2-publication-information.-1}{%
-\subsection{RQ2: Publication Information.}\label{rq2-publication-information.-1}}
-
-Publication interest area was summarized by the four large subject areas creating a word cloud plot of the total number of publications within the ASJCs.
-Figure \ref{fig:fig-clouds} displays that the health sciences tends to publish within medicine and oncology, with a corresponding focus of cancer research and genetics for the life sciences.
-The physical sciences is mostly dominated by physics research, chemistry, and ecology.
-The BTS publications in the social sciences are mostly within psychology, education, and health.
+\emph{Number of journals}. The number of distinct journals big team science
+articles were published in was 14924 with 6559
+journals in Health Sciences, 5787 journals in Physical
+Sciences, 2500 journals in Social Sciences, and
+4187 journals in Life Sciences. The descriptive statistics
+for the Source Normalized Impact per Paper is presented in the
+supplemental materials with a comparison for all papers.
+
+\hypertarget{rq2-publication-information.}{%
+\subsection{RQ2: Publication Information.}\label{rq2-publication-information.}}
+
+Publication interest area was summarized by the four large subject areas
+creating a word cloud plot of the total number of publications within
+the ASJCs. Figure \ref{fig:fig-clouds} displays that the Health
+Sciences tends to publish within medicine and oncology, with a
+corresponding focus of cancer research and genetics for the Life
+Sciences. The Physical Sciences was mostly dominated by physics
+research, chemistry, and ecology. The BTS publications in the Social
+Sciences are mostly within psychology, education, and health.
 
@@
 \includegraphics{manuscript_scopus_files/figure-latex/fig-clouds-1.pdf}
-\caption{\label{fig:fig-clouds}Journal Areas for Big-Team Science Publications by Subject Area}
+\caption{\label{fig:fig-clouds}Journal Areas for Big-Team Science Publications by Subject Area. Larger words indicate more publications in those ASJC areas.}
 \end{figure}
@@
 
-The total number of unique authors across all publications was 510334.
-The mean number of authors per publication was \emph{M} = 49.31 (\emph{SD} = 212.98, \emph{Med} = 18) with a range of 10 to 5568.
-The median and average number of authors by subject area are displayed in Figure \ref{fig:fig-author-year}.
-In general, the average and median number of authors increased over time, with the exception of the skew in the physical sciences.
-Interestingly, the effect in the physical sciences appears to be declining toward the general trends seen in other areas in the last few decades.
+The total number of unique authors across all publications was
+510334. The mean number of authors per publication was \emph{M} =
+49.31 (\emph{SD} = 212.98, \emph{Med} = 18) with a
+range of 10 to 5568. The median and average
+number of authors by subject area are displayed in Figure
+\ref{fig:fig-author-year}. In general, the average and median number of
+authors increased over time, with the exception of the skew in the
+Physical Sciences. Interestingly, the effect in the Physical Sciences
+appears to be declining toward the general trends seen in other areas in
+the last few decades.
 
@@
 
-Figure \ref{fig:fig-career} portrays the average career length for authors involved in BTS publications across years.
-Career length was defined as the year of first publication minus the current year, and higher numbers mean longer careers.
-To analyze trends over time, we calculated the average career length for each publication (i.e., average author career lengths to create one score for each paper) and analyzed a regression analysis using career length to predict year of publication.
-In order to show variance between individuals, we calculated the standard deviation of career length for each publication and used variance as an additional predictor.
-
-Negative career length slopes would indicate more young scholars in later years (i.e., lower average career length as time increases).
-Positive career length slopes would indicate older scholars in later years (i.e., higher average career length as time increases).
-Negative career variance slopes imply that variability decreases over the years, so the average career length is more homogeneous.
-Positive career length slopes imply that variability increases over the years, so the average career length is varied across individuals (i.e., different stages of scholars).
-Figure \ref{fig:fig-heatmap} displays the results for all regression analyses to compare coefficient strength across and within hypothesis.
-
-All values for this analyses were different from zero.
-The slopes for the average career length were negative for all four subject areas, indicating a trend toward younger scientist involvement over time for each area, with the strongest effect in the Physical sciences.
-The coefficient for variability in career length was also negative for each of the four subject areas with the highest in the Physical sciences and lowest in the Life Sciences.
-This result indicates a decrease in the variability of career lengths over time, likely from two sources: 1) more publications with more authors, thus, lowering variance estimations, and 2) more young scholars overall.
-The effect sizes for this analysis were surprisingly large ranging from \(R^2\) to .25 to .47.
+Figure \ref{fig:fig-career} portrays the average career length for
+authors involved in BTS publications across years. Career length was
+defined as the year of first publication minus the current year, and
+higher numbers mean longer careers. To analyze trends over time, we
+calculated the average career length for each publication (i.e., average
+author career lengths to create one score for each paper) and analyzed a
+regression analysis using career length to predict year of publication.
+In order to show variance between individuals, we calculated the
+standard deviation of career length for each publication and used this
+variance as an additional predictor.
+
+Negative career length slopes would indicate more young scholars in
+later years (i.e., lower average career length as time increases).
+Positive career length slopes would indicate older scholars in later
+years (i.e., higher average career length as time increases). Negative
+career variance slopes imply that variability decreases over the years,
+so the average career length is more homogeneous. Positive career length
+slopes imply that variability increases over the years, so the average
+career length is varied across individuals (i.e., different stages of
+scholars). Figure \ref{fig:fig-heatmap} displays the results for all
+regression analyses to compare coefficient strength across and within
+each hypothesis.
+
+All values for these analyses were different from zero. The slopes for
+the average career length were negative for all four subject areas,
+indicating a trend toward younger scientist involvement over time for
+each area, with the strongest effect in the Physical Sciences. The
+coefficient for variability in career length was also negative for each
+of the four subject areas with the highest in the Physical Sciences and
+lowest in the Life Sciences. This result indicates a decrease in the
+variability of career lengths over time, likely from two sources: 1)
+more publications with more authors, thus, lowering variance
+estimations, and 2) more young scholars overall. The effect sizes for
+this analysis were surprisingly large ranging from \(R^2\) = .25 to .47.
 All values and their confidence intervals can be found on our OSF page.
@@
 
-\begin{verbatim}
-## Warning in width_strings[fixed_areas[[i]]$cols] == "-1null" && length(w) == :
-## 'length(x) = 3 > 1' in coercion to 'logical(1)'
-\end{verbatim}
-
 \begin{figure}
@@
 \includegraphics{manuscript_scopus_files/figure-latex/fig-heatmap-1.pdf}
-\caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity in region.
+\caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region.
 The top figure represents all results together for comparison across analyses.
@@
 
-\begin{verbatim}
-## Warning in width_strings[fixed_areas[[i]]$cols] == "-1null" && length(w) == :
-## 'length(x) = 3 > 1' in coercion to 'logical(1)'
-\end{verbatim}
-
 \textbf{\emph{Institution}}.
@@
 
-The average number of publications by authors on big team sciences
-papers is \emph{M} = 38.37 (\emph{SD} =
-102.54). The publication counts were averaged across
-authors for each publication, and then these average publication counts
-were averaged across publications \emph{M} = 162.50 (\emph{SD} =
+The average number of publications by authors on big team science papers
+is \emph{M} = 38.37 (\emph{SD} = 102.54). The
+publication counts were averaged across authors for each publication,
+and then these average publication counts were averaged across
+publications \emph{M} = 162.50 (\emph{SD} =
 155.17). The average variability (i.e., the average
@@
 
-We used the same analyses described in the career length section to analyze trends over time.
-An increasing slope over time indicates that individuals who are publishing more are more represented in BTS over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications.
-A positive slope for the standard deviation of publication metrics indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time.
-While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we used this variable as a proxy to gauge the diversity in scholars represented in big teams.
-As shown in Figure \ref{fig:fig-heatmap} publication metrics were generally negative for the average publication metrics, indicating more scholars over time with lower numbers of citations with the strongest effects in health and social sciences.
-The variability of publication counts was not significant for the life sciences but was negative for the physical sciences (less variability over time) and positive for social and health sciences (more variability and over time).
-This result indicates that the physical sciences are trending toward scholars with less publications but also less diverse in number of publications, while the health and social sciences see more diversity in publication counts and less published scholars overall.
+We used the same analyses described in the career length section to
+analyze trends over time. An increasing slope over time indicates that
+individuals who are publishing more are more represented in BTS over
+time (i.e., increasing numbers of scholars with higher publication
+rates), while a negative slope indicates more researchers with less
+publications. A positive slope for the standard deviation of publication
+metrics indicates increasing variance over time (i.e., more diversity in
+the individual publication rates), while a negative slope would indicate
+less diversity in researchers over time. While publication rates do not
+represent value as a researcher, they are often used in hiring and
+promotion decisions, and we used this variable as a proxy to gauge the
+diversity in scholars represented in big teams. As shown in Figure
+\ref{fig:fig-heatmap} publication metrics were generally negative for
+the average publication metrics, indicating more scholars over time with
+lower numbers of publications with the strongest effects in Health and
+Social Sciences. The variability of publication counts was not
+significant for the Life Sciences but was negative for the Physical
+Sciences (less variability over time) and positive for Social and Health
+Sciences (more variability and over time). This result indicates that
+the Physical Sciences are trending toward scholars with less
+publications but also less diverse in number of publications, while the
+Health and Social Sciences see more diversity in publication counts and
+less published scholars overall.
 
@@
 \includegraphics{manuscript_scopus_files/figure-latex/fig-map-both-1.pdf}
-\caption{\label{fig:fig-map-both}Geopolitical regions represented in big-team science publications versus all publications.}
+\caption{\label{fig:fig-map-both}Geopolitical regions represented in big-team science publications versus all publications.
+The mosaic plot is grouped by UN subregion with the largest number of publications on the left and smallest on the top right.}
 \end{figure}
 
-Author geopoligical region is displayed in Figure \ref{fig:fig-map-both}.
-Big team publications appear to be lead by North America and Western Europe, while all publications are lead by North America and East Asia.
-To understand the change in representation diversity, we examined if the number of regions in a publication is predicted by the year of publication.
-Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope.
-As shown in Figure \ref{fig:fig-heatmap}, the physical sciences do not show a trend of change in representation, while all other sciences showed a positive effect increasing in the number of geopolitical regions authors represent on publications.
-
-Last, we examined the differences in representation for corresponding author sets versus all other authors.
-For papers with 10 to 49 authors, we used the three first authors and the last author to compare against other authors.
-For 50 to 99 authors, five first authors plus last were used, and for all papers with more than 100 authors, we used ten first authors and the last author as the corresponding author set.
-We then calculated the frequencies of each of the UN Sub-Regions for corresponding authors versus all other authors, converting these values to proportions.
-Given the expected small sample sizes of these contingency tables, we grouped together titles based on the year of publication.
-For each grouping, we then calculated the effect size of the differences in frequencies comparing corresponding authors to all other authors.
-Since this data is categorical, we used Cramer's \emph{V} to represent the effect size.
-If the effect size includes zero in its confidence interval (to four decimal places), this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity.
-Any confidence interval that does include zero represents a difference in diversity.
+Author geopolitical region is displayed in Figure
+\ref{fig:fig-map-both}. Big team publications appear to be led by North
+America and Western Europe, while all publications are led by North
+America and East Asia. To understand the change in representation
+diversity, we examined if the number of regions in a publication is
+predicted by the year of publication. Increasing diversity would be
+represented by a positive slope, while decreasing diversity would be
+represented by a negative slope. As shown in Figure
+\ref{fig:fig-heatmap}, the Physical Sciences do not show a trend of
+change in representation, while all other sciences showed a positive
+effect increasing in the number of geopolitical regions authors
+represent on publications.
+
+Last, we examined the differences in representation for corresponding
+author sets versus all other authors. For papers with 10 to 49 authors,
+we used the three first authors and the last author to compare against
+other authors. For 50 to 99 authors, five first authors plus last were
+used, and for all papers with more than 100 authors, we used ten first
+authors and the last author as the corresponding author set. We then
+calculated the frequencies of each of the UN Sub-Regions for
+corresponding authors versus all other authors, converting these values
+to proportions. Given the expected small sample sizes of these
+contingency tables, we grouped together titles based on the year of
+publication. For each grouping, we then calculated the effect size of
+the differences in frequencies comparing corresponding authors to all
+other authors. Since this data is categorical, we used Cramer's \emph{V} to
+represent the effect size. If the effect size includes zero in its
+confidence interval (to four decimal places), this result will imply
+that first and all other authors represent the same pattern of UN
+Sub-Region diversity. Any confidence interval that does include zero
+represents a difference in diversity.
 
@@
 \includegraphics{manuscript_scopus_files/figure-latex/fig-author-gpe-1.pdf}
-\caption{\label{fig:fig-author-gpe}A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors.}
+\caption{\label{fig:fig-author-gpe}A comparison of author affiliation geopolitical regions across decades. F stands for first authors and O stands for other authors.}
 \end{figure}
@@
 
-Figure \ref{fig:fig-author-gpe} indicates the percent of authors in regions.
-In general, we found the same pattern as the overall analysis wherein most authors are from Europe and North America.
-The pattern of representation is roughly similar for the separation of small, medium, and large numbers of authors on papers.
-Across time, the representation does appear to diversify, with more representation in Asia, Latin American, and Africa.
-Figure \ref{fig:fig-effect-gpe} represents the size of the differences in first/corresponding authors and other authors across time and number of authors.
-The differences in representation are larger for papers with more authors; however, the effects are non-zero for many of the comparisons.
-Encouragingly, over time these effects appear to diminish in size.
-One limitation with the calculation of effect sizes for count data is the sensitivity of the data to sample size (i.e., \(\chi^2\) is upwardly biased by sample size, and \(V\) is calculated based on this value).
-While we used the inclusion of zero as our boundary for ``significance'', the interpretation of the effects is that most are likely small: \(V\) \textless{} .05: 31.79\%, \textless{} .10: 70.20\%, \textless{} .20: 94.04\%.
+Figure \ref{fig:fig-author-gpe} indicates the percent of authors in
+regions. In general, we found the same pattern as the overall analysis
+wherein most authors are from Europe and North America. The pattern of
+representation is roughly similar for the separation of small, medium,
+and large numbers of authors on papers. Across time, the representation
+does appear to diversify, with more representation in Asia, Latin
+American, and Africa. Figure \ref{fig:fig-effect-gpe} represents the
+size of the differences in first/corresponding authors and other authors
+across time and number of authors. The differences in representation are
+larger for papers with more authors; however, the effects are non-zero
+for many of the comparisons. Encouragingly, over time these effects
+appear to diminish in size. One limitation with the calculation of
+effect sizes for count data is the sensitivity of the data to sample
+size (i.e., \(\chi^2\) is upwardly biased by sample size, and \(V\) is
+calculated based on this value). While we used the inclusion of zero as
+our boundary for ``significance'', the interpretation of the effects is
+that most are likely small: \(V\) \textless{} .05:
+31.79\%, \(V\) \textless{} .10:
+70.20\%, \(V\) \textless{}
+.20: 94.04\%.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  number of publications increasing
-\item
-  research areas appear to be cancer, physics, and psychology
-\item
-  the number of authors is increasing as well
-\item
-  career length is decreasing, number of publications necessary to be involved is decreasing
-\item
-  number of gpe increasing
-\item
-  appears to be slowly diversifying, yet still not equal in first and other authors in diversity
-\end{itemize}
-
-limitations - based on the data we could get, we made up the definition of BTS, under-representation of articles in other languages/that they don't collect
-
-future: incentives for bts and why people do it
+In this investigation, we explored the publication rates, areas, and
+researchers involved in big team science publications. Over a
+half-million articles were published in nearly 15,000 journals since
+1970 that qualified as big team science articles (at least ten authors
+and ten different affiliations). The areas of publication were aligned
+to cancer and genetics research in medicine and oncology for Health and
+Life Sciences, physics and chemistry for the Physical Sciences, and
+psychology for the Social Sciences All areas of research show an
+explosion in growth in the number of publications and the number of
+authors included on manuscripts, replicating previous investigations
+into this topic area\textsuperscript{50--52}.
+
+Our investigation expands into an exploration of the researchers who
+publish in big teams focusing on career length, publication metrics, and
+geopolitical affiliation. The number of earlier career scholars is
+increasing in publications across the years, indicating that big teams
+may be more accessible to different types of individuals, not just
+older, more established researchers. This result is especially
+interesting given the publish-or-perish model still present in most
+institutions, as it may seem that large-scale projects could be a risky
+choice for non-permanent researchers. In the authors' experience, big
+team projects are often quite slow to publication, incentives may be low
+for non corresponding authors if institutions do not value papers
+without lead authorship, and there is no guarantee for publication even
+with a large group. However, with a large team the distribution of work
+could imply less effort on individual non-leading members, and research
+has shown that larger-team publications do receive more citations and
+appear to have higher impact\textsuperscript{53}.
+
+The results for the number of publications by big team researchers
+mimics the findings from career length, with a smaller effect size. In
+general, it appears that there is a decrease in the average number of
+publications a researcher has when publishing on a big team science
+paper over time. This result is likely attributable to the number of
+early career scholars joining projects, but also may support increased
+accessibility for individuals to be involved in this type of research.
+Globalization, the internet, and the focus on interdisciplinary research
+are potentially driving forces behind our results, but, hopefully, the
+results also point to a decline in scientific gatekeeping\textsuperscript{54,55}.
+
+The variability in the types of researchers involved in publications
+also decreased across time in most areas of science with a decrease in
+variability for career length. As mentioned, an increase in early career
+researchers and numbers of publications could explain this effect
+mathematically, potentially with other social influences mentioned
+above. The variability in the number of publications is decreasing in
+the Physical Sciences, mirroring the career length results, but the
+opposite effect was found in the Health and Social Sciences. We see no
+clear reason why career variability would decrease while the variability
+in the number of publications would increase. The effect sizes for
+career length were much larger than the effects for number of
+publications. One speculation is the increasing requirements for a
+competitive faculty role application. Given the limited number of
+positions, one potential way to distinguish their application would be a
+larger number of publications in their early career\textsuperscript{56,57}.
+
+The number of geopolitical entities for researcher affiliation is
+increasing over time, showing the results of globalization and the
+ability to connect across time zones and cultures\textsuperscript{58}. While our
+definition of big team science required at least ten different
+institutional affiliations, we did not filter papers by geopolitical
+region, and thus, a manuscript could rely solely on institutions within
+a single country. The Physical Sciences did not show an increase in
+diversity of regions represented, however, it could be argued that the
+development of large research centers like CERN forced earlier diversity
+than other sciences (i.e., because CERN specifically recruited
+scientists from sponsoring nations). The Life, Health, and Social
+Sciences saw an increase in the number of regions represented with the
+highest increase in the Social Sciences. This result likely corresponds
+with an increased interest in big team science publications in
+psychology\textsuperscript{2,3}, and the desire to diversify the
+populations represented in psychological research\textsuperscript{43,44}.
+
+While publications on the whole are diversifying, we did not yet find
+equality in the representation for first/corresponding author spots
+versus all other authors. In general, first authors appear to be less
+diverse, representing more European and North American authors, while
+other authors include more Asian and African authors. These effect sizes
+were often small, but the inequality still persists across years, even
+if they are slowly decreasing. Diverse teams are more likely to have
+papers with stronger ``impact''\textsuperscript{59--62} with higher citation metrics for more diverse author lists.
+The introduction of contributorship models\textsuperscript{e.g., CRediT 42}
+will hopefully continue to push these effects down, as they highlight
+each individual's contribution to a manuscript.
+
+The limitations for this research are tied to the availability and
+curation of the Scopus dataset. While the number of articles analyzed
+for this investigation was large, the criteria for inclusion requires
+the correct entry of author affiliations, the correct author linkages
+for career length and publication rates, and the correctly marked
+geopolitical entity. We had planned to analyze educational levels to
+determine if the number of student coauthors (i.e., non-terminal degree)
+had increased over time; however, this data was mostly blank within the
+Scopus archive. Scopus is a carefully curated dataset, but these
+limitations must be kept in mind when interpreting the results.
+Publication language diversity was not investigated, and a previous
+study indicates that the majority of publications in big databases are
+in English\textsuperscript{63}. Certainly, publications in non-English
+languages would improve the statistics on diversity in scientific
+publishing - but the English language barrier likely exists regardless
+of inclusion in databases\textsuperscript{64,65}.
+
+Big teams have the ability to provide high-impact, important research
+within scientific publishing, and this report suggests a promising trend
+of increasing numbers of publications that include earlier career and
+more diverse scholars. These partnerships introduce new challenges to
+collaboration from interpersonal conflict, infrastructure, incentives,
+to international political situations\textsuperscript{3}. Directed studies
+into ways to navigate these situations would be beneficial for policy
+makers at institutions, as well as lead teams who organize and complete
+these projects. The implications for retention and promotion processes
+across a broad span of regions should be explored to improve diversity
+with the understanding of the differential impact of incentives for
+participating in big team studies.
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-aphilos2021}{}}%
-A philosophical case for big physics. (2021). \emph{Nature Physics}, \emph{17}(6), 661--661. \url{https://doi.org/10.1038/s41567-021-01278-0}
-
-\leavevmode\vadjust pre{\hypertarget{ref-allen2019}{}}%
-Allen, L., O'Connell, A., \& Kiermer, V.
-(2019).
-How can we ensure visibility and diversity in research contributions?
-How the Contributor Role Taxonomy (CRediT) is helping the shift from authorship to contributorship.
-\emph{Learned Publishing}, \emph{32}(1), 71--74.
-\url{https://doi.org/10.1002/leap.1210}
-
-\leavevmode\vadjust pre{\hypertarget{ref-auspurg2021has}{}}%
-Auspurg, K., \& Brüderl, J.
-(2021).
-Has the credibility of the social sciences been credibly destroyed?
-Reanalyzing the {``}many analysts, one data set{''} project.
-\emph{Socius : Sociological Research for a Dynamic World}, \emph{7}, 23780231211024420.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bago2022}{}}%
-Bago, B., Kovacs, M., Protzko, J., Nagy, T., Kekecs, Z., Palfi, B., \ldots{} Aczel, B.
-(2022).
-Situational factors shape moral judgements in the trolley dilemma in Eastern, Southern and Western countries in a culturally diverse sample.
-\emph{Nature Human Behaviour}, 1--13.
-\url{https://doi.org/10.1038/s41562-022-01319-5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buttrick2020}{}}%
-Buttrick, N.
-R., Aczel, B., Aeschbach, L.
-F., Bakos, B.
-E., Brühlmann, F., Claypool, H.
-M., \ldots{} Wood, M.
-J.
-(2020).
-Many Labs 5: Registered Replication of Vohs and Schooler (2008), Experiment 1.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 429--438.
-\url{https://doi.org/10.1177/2515245920917931}
-
-\leavevmode\vadjust pre{\hypertarget{ref-castelnovo2018}{}}%
-Castelnovo, P., Florio, M., Forte, S., Rossi, L., \& Sirtori, E.
-(2018).
-The economic impact of technological procurement for large-scale research infrastructures: Evidence from the Large Hadron Collider at CERN.
-\emph{Research Policy}, \emph{47}(9), 1853--1867.
-\url{https://doi.org/10.1016/j.respol.2018.06.018}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-oed2016}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{OED. Collaboration. vol. 3 (2016).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-coles2022}{}}%
-Coles, N.
+\CSLLeftMargin{2. }%
+\CSLRightInline{Coles, N.
 A., Hamlin, J.
@@
 L., Parker, T.
-H., \& Altschul, D.
-(2022).
-Build up big-team science.
-\emph{Nature}, \emph{601}(7894), 505--507.
-\url{https://doi.org/10.1038/d41586-022-00150-2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-collins2003}{}}%
-Collins, F.
-S., Morgan, M., \& Patrinos, A.
-(2003).
-The human genome project: Lessons from large-scale biology.
-\emph{Science}, \emph{300}(5617), 286--290.
-\url{https://doi.org/10.1126/science.1084564}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dorison2022}{}}%
-Dorison, C., Lerner, J., Heller, B., Rothman, A., Kawachi, I., Wang, K., \ldots{} Coles, N.
-(2022).
-A global test of message framing on behavioural intentions, policy support, information seeking, and experienced anxiety during the COVID-19 pandemic.
-\emph{Affective Science}.
-\url{https://doi.org/10.31234/osf.io/sevkf}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ebersole2016}{}}%
-Ebersole, C.
-R., Atherton, O.
-E., Belanger, A.
-L., Skulborstad, H.
-M., Allen, J.
-M., Banks, J.
-B., \ldots{} Nosek, B.
-A.
-(2016).
-Many Labs 3: Evaluating participant pool quality across the academic semester via replication.
-\emph{Journal of Experimental Social Psychology}, \emph{67}, 68--82.
-\url{https://doi.org/10.1016/j.jesp.2015.10.012}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
-Ebersole, C.
-R., Mathur, M.
-B., Baranski, E., Bart-Plange, D.-J., Buttrick, N.
-R., Chartier, C.
-R., \ldots{} Nosek, B.
-A.
-(2020).
-Many Labs 5: Testing Pre-Data-Collection Peer Review as an Intervention to Increase Replicability.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 309--331.
-\url{https://doi.org/10.1177/2515245920958687}
-
-\leavevmode\vadjust pre{\hypertarget{ref-10.7554ux2feLife.71601}{}}%
-Errington, T.
-M., Mathur, M., Soderberg, C.
-K., Denis, A., Perfito, N., Iorns, E., \& Nosek, B.
-A.
-(2021).
-Investigating the replicability of preclinical cancer biology.
-\emph{eLife}, \emph{10}, e71601.
-\url{https://doi.org/10.7554/eLife.71601}
-
-\leavevmode\vadjust pre{\hypertarget{ref-forscher2020}{}}%
-Forscher, P.
-S., Wagenmakers, E.-J., Coles, N.
-A., Silan, M.
-A.
-A., Dutra, N.
-B., Basnight-Brown, D., \& IJzerman, H.
-(2020).
-\emph{The benefits, barriers, and risks of big team science}.
-\url{https://doi.org/10.31234/osf.io/2mdxh}
-
-\leavevmode\vadjust pre{\hypertarget{ref-franco2014}{}}%
-Franco, A., Malhotra, N., \& Simonovits, G.
-(2014).
-Publication bias in the social sciences: Unlocking the file drawer.
-\emph{Science}, \emph{345}(6203), 1502--1505.
-\url{https://doi.org/10.1126/science.1255484}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grahe2014}{}}%
-Grahe, J. E. (2014). Announcing open science badges and reaching for the sky. \emph{The Journal of Social Psychology}, \emph{154}(1), 1--3. \url{https://doi.org/10.1080/00224545.2014.853582}
-
-\leavevmode\vadjust pre{\hypertarget{ref-henrich2010}{}}%
-Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--83. \url{https://doi.org/10.1017/S0140525X0999152X}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hubbard1997}{}}%
-Hubbard, R., \& Armstrong, J. S. (1997). Publication Bias against Null Results. \emph{Psychological Reports}, \emph{80}(1), 337--338. \url{https://doi.org/10.2466/pr0.1997.80.1.337}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ioannidis2015}{}}%
-Ioannidis, J.
-P.
-A.
-(2015).
-Failure to replicate: Sound the alarm.
-\emph{Cerebrum: The Dana Forum on Brain Science}, \emph{2015}.
-Retrieved from \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4938249/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-isager2021}{}}%
-Isager, P.
-M., Aert, R.
-C.
-M.
-van, Bahník, Š., Brandt, M.
-J., DeSoto, K.
-A., Giner-Sorolla, R., \ldots{} Lakens, D.
-(2021a).
-Deciding what to replicate: A decision model for replication study selection under resource and knowledge constraints.
-\emph{Psychological Methods}.
-\url{https://doi.org/10.1037/met0000438}
-
-\leavevmode\vadjust pre{\hypertarget{ref-isager2021a}{}}%
-Isager, P.
-M., Aert, R.
-C.
-M.
-van, Bahník, Š., Brandt, M.
-J., DeSoto, K.
-A., Giner-Sorolla, R., \ldots{} Lakens, D.
-(2021b).
-Deciding what to replicate: A decision model for replication study selection under resource and knowledge constraints.
-\emph{Psychological Methods}.
-\url{https://doi.org/10.1037/met0000438}
-
-\leavevmode\vadjust pre{\hypertarget{ref-john2012}{}}%
-John, L.
-K., Loewenstein, G., \& Prelec, D.
-(2012).
-Measuring the Prevalence of Questionable Research Practices With Incentives for Truth Telling.
-\emph{Psychological Science}, \emph{23}(5), 524--532.
-\url{https://doi.org/10.1177/0956797611430953}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jones2021}{}}%
-Jones, B.
-C., DeBruine, L.
-M., Flake, J.
-K., Liuzza, M.
-T., Antfolk, J., Arinze, N.
-C., \ldots{} Coles, N.
-A.
-(2021).
-To which world regions does the valence{\textendash}dominance model of social perception apply?
-\emph{Nature Human Behaviour}, \emph{5}(1), 159--169.
-\url{https://doi.org/10.1038/s41562-020-01007-2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kidwell2016}{}}%
-Kidwell, M.
-C., Lazarević, L.
-B., Baranski, E., Hardwicke, T.
-E., Piechowski, S., Falkenberg, L.-S., \ldots{} Nosek, B.
-A.
-(2016).
-Badges to Acknowledge Open Practices: A Simple, Low-Cost, Effective Method for Increasing Transparency.
-\emph{PLOS Biology}, \emph{14}(5), e1002456.
-\url{https://doi.org/10.1371/journal.pbio.1002456}
-
-\leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
-Klein, Richard A., Cook, C.
-L., Ebersole, C.
-R., Vitiello, C., Nosek, B.
-A., Hilgard, J., \ldots{} Ratliff, K.
-A.
-(2022).
-Many Labs 4: Failure to Replicate Mortality Salience Effect With and Without Original Author Involvement.
-\emph{Collabra: Psychology}, \emph{8}(1), 35271.
-\url{https://doi.org/10.1525/collabra.35271}
-
-\leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
-Klein, Richard A., Vianello, M., Hasselman, F., Adams, B.
-G., Adams, R.
-B., Alper, S., \ldots{} Nosek, B.
-A.
-(2018).
-Many Labs 2: Investigating Variation in Replicability Across Samples and Settings.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490.
-\url{https://doi.org/10.1177/2515245918810225}
+H.
+\& Altschul, D.
+\href{https://doi.org/10.1038/d41586-022-00150-2}{Build up big-team science}.
+\emph{Nature} \textbf{601}, 505--507 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-forscher2022a}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{Forscher, P.
+S.
+\emph{et al.} \href{https://doi.org/10.1177/17456916221082970}{The Benefits, Barriers, and Risks of Big-Team Science}.
+\emph{Perspectives on Psychological Science} \textbf{18}, 607623 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stewart2017}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Stewart, N., Chandler, J.
+\& Paolacci, G.
+\href{https://doi.org/10.1016/j.tics.2017.06.007}{Crowdsourcing samples in cognitive science}.
+\emph{Trends in Cognitive Sciences} \textbf{21}, 736--748 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-maxwell2015}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Maxwell, S.
+E., Lau, M.
+Y.
+\& Howard, G.
+S.
+\href{https://doi.org/10.1037/a0039400}{Is psychology suffering from a replication crisis?: What does 'failure to replicate' really mean?} \emph{American Psychologist} \textbf{70}, 487--498 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Nelson, L.
+D., Simmons, J.
+\& Simonsohn, U.
+\href{https://doi.org/10.1146/annurev-psych-122216-011836}{Psychology's renaissance}.
+\emph{Annual Review of Psychology} \textbf{69}, 511--534 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Zwaan, R.
+A., Etz, A., Lucas, R.
+E.
+\& Donnellan, M.
+B.
+\href{https://doi.org/10.1017/S0140525X17001972}{Making replication mainstream}.
+\emph{Behavioral and Brain Sciences} \textbf{41}, e120 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-auspurg2021}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Auspurg, K.
+\& Brüderl, J.
+\href{https://doi.org/10.1177/23780231211024421}{Has the Credibility of the Social Sciences Been Credibly Destroyed?
+Reanalyzing the {``}Many Analysts, One Data Set{''} Project}.
+\emph{Socius: Sociological Research for a Dynamic World} \textbf{7}, (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Nosek, B. A. \& Lakens, D. A method to increase the credibility of published results. \emph{Social Psychology} \textbf{45}, 137141 (2014).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lebel2018}{}}%
-LeBel, E.
+\CSLLeftMargin{10. }%
+\CSLRightInline{LeBel, E.
 P., McCarthy, R.
 J., Earp, B.
-D., Elson, M., \& Vanpaemel, W.
-(2018).
-A Unified Framework to Quantify the Credibility of Scientific Findings.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 389--402.
-\url{https://doi.org/10.1177/2515245918787489}
-
-\leavevmode\vadjust pre{\hypertarget{ref-legate2022}{}}%
-Legate, N., Nguyen, T., Weinstein, N., Moller, A., Legault, L., Maniaci, M.
-R., \ldots{} Primbs, M.
-(2022).
-A global experiment on motivating social distancing during the COVID-19 pandemic.
-\emph{Proceedings of the National Academy of Sciences}.
-\url{https://doi.org/10.31234/osf.io/n3dyf}
+D., Elson, M.
+\& Vanpaemel, W.
+\href{https://doi.org/10.1177/2515245918787489}{A Unified Framework to Quantify the Credibility of Scientific Findings}.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}, 389--402 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Vazire, S., Schiavone, S.
+R.
+\& Bottesini, J.
+G.
+\href{https://doi.org/10.1177/09637214211067779}{Credibility Beyond Replicability: Improving the Four Validities in Psychological Science}.
+\emph{Current Directions in Psychological Science} \textbf{31}, 162--168 (2022).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-maizey2019}{}}%
-Maizey, L., \& Tzavella, L.
-(2019).
-Barriers and solutions for early career researchers in tackling the reproducibility crisis in cognitive neuroscience.
-\emph{Cortex}, \emph{113}, 357--359.
-\url{https://doi.org/10.1016/j.cortex.2018.12.015}
+\CSLLeftMargin{12. }%
+\CSLRightInline{Maizey, L.
+\& Tzavella, L.
+\href{https://doi.org/10.1016/j.cortex.2018.12.015}{Barriers and solutions for early career researchers in tackling the reproducibility crisis in cognitive neuroscience}.
+\emph{Cortex} \textbf{113}, 357--359 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-opensciencecollaboration2015}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Open Science Collaboration.
+\href{https://doi.org/10.1126/science.aac4716}{Estimating the reproducibility of psychological science}.
+\emph{Science} \textbf{349}, aac4716--aac4716 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-buttrick2020}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{Buttrick, N.
+R.
+\emph{et al.} \href{https://doi.org/10.1177/2515245920917931}{Many Labs 5: Registered Replication of Vohs and Schooler (2008), Experiment 1}.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{3}, 429--438 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ebersole2016}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{Ebersole, C.
+R.
+\emph{et al.} \href{https://doi.org/10.1016/j.jesp.2015.10.012}{Many Labs 3: Evaluating participant pool quality across the academic semester via replication}.
+\emph{Journal of Experimental Social Psychology} \textbf{67}, 68--82 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Ebersole, C.
+R.
+\emph{et al.} \href{https://doi.org/10.1177/2515245920958687}{Many Labs 5: Testing Pre-Data-Collection Peer Review as an Intervention to Increase Replicability}.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{3}, 309--331 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{Klein, R.
+A.
+\emph{et al.} \href{https://doi.org/10.1177/2515245918810225}{Many Labs 2: Investigating Variation in Replicability Across Samples and Settings}.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}, 443--490 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{Klein, R.
+A.
+\emph{et al.} \href{https://doi.org/10.1525/collabra.35271}{Many Labs 4: Failure to Replicate Mortality Salience Effect With and Without Original Author Involvement}.
+\emph{Collabra: Psychology} \textbf{8}, 35271 (2022).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
-Mathur, M.
-B., Bart-Plange, D.-J., Aczel, B., Bernstein, M.
-H., Ciunci, A.
-M., Ebersole, C.
-R., \ldots{} Frank, M.
+\CSLLeftMargin{19. }%
+\CSLRightInline{Mathur, M.
+B.
+\emph{et al.} \href{https://doi.org/10.1177/2515245918785165}{Many Labs 5: Registered Multisite Replication of the Tempting-Fate Effects in Risen and Gilovich (2008)}.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{3}, 394--404 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-skorb2020}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Skorb, L.
+\emph{et al.} \href{https://doi.org/10.1177/2515245920927643}{Many Labs 5: Replication of van Dijk, van Kleef, Steinel, and van Beest (2008)}.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{3}, 418--428 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bago2022}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{Bago, B.
+\emph{et al.} \href{https://doi.org/10.1038/s41562-022-01319-5}{Situational factors shape moral judgements in the trolley dilemma in Eastern, Southern and Western countries in a culturally diverse sample}.
+\emph{Nature Human Behaviour} \textbf{6}, 880--895 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-buchanan2023}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{Buchanan, E.
+M.
+\emph{et al.} \href{https://doi.org/10.1038/s41597-022-01811-7}{The psychological science accelerator{'}s COVID-19 rapid-response dataset}.
+\emph{Scientific Data} \textbf{10}, 87 (2023).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dorison2022}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{Dorison, C.
+A.
+\emph{et al.} \href{https://doi.org/10.1007/s42761-022-00128-3}{In {COVID}-19 {Health} {Messaging}, {Loss} {Framing} {Increases} {Anxiety} with {Little}-to-{No} {Concomitant} {Benefits}: {Experimental} {Evidence} from 84 {Countries}}.
+\emph{Affective Science} \textbf{3}, 577--602 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jones2021}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{Jones, B.
 C.
-(2020).
-Many Labs 5: Registered Multisite Replication of the Tempting-Fate Effects in Risen and Gilovich (2008).
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 394--404.
-\url{https://doi.org/10.1177/2515245918785165}
-
-\leavevmode\vadjust pre{\hypertarget{ref-maxwell2015}{}}%
-Maxwell, S.
-E., Lau, M.
-Y., \& Howard, G.
-S.
-(2015).
-Is psychology suffering from a replication crisis?: What does 'failure to replicate' really mean?
-\emph{American Psychologist}, \emph{70}(6), 487--498.
-\url{https://doi.org/10.1037/a0039400}
+\emph{et al.} \href{https://doi.org/10.1038/s41562-020-01007-2}{To which world regions does the valence{\textendash}dominance model of social perception apply?} \emph{Nature Human Behaviour} \textbf{5}, 159--169 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-psychologicalscienceacceleratorself-determinationtheorycollaboration2022}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{Psychological Science Accelerator Self-Determination Theory Collaboration.
+\href{https://doi.org/10.1073/pnas.2111091119}{A global experiment on motivating social distancing during the COVID-19 pandemic}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{119}, e2111091119 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moshontz2018}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{Moshontz, H.
+\emph{et al.} \href{https://doi.org/10.1177/2515245918797607}{The Psychological Science Accelerator: Advancing Psychology Through a Distributed Collaborative Network}.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}, 501--515 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wang2021}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{Wang, K.
+\emph{et al.} \href{https://doi.org/10.1038/s41562-021-01173-x}{A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic}.
+\emph{Nature Human Behaviour} \textbf{5}, 1089--1110 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-franco2014}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Franco, A., Malhotra, N.
+\& Simonovits, G.
+\href{https://doi.org/10.1126/science.1255484}{Publication bias in the social sciences: Unlocking the file drawer}.
+\emph{Science} \textbf{345}, 1502--1505 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hubbard1997}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{Hubbard, R. \& Armstrong, J. S. \href{https://doi.org/10.2466/pr0.1997.80.1.337}{Publication Bias against Null Results}. \emph{Psychological Reports} \textbf{80}, 337--338 (1997).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2012}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Nosek, B.
+A., Spies, J.
+R.
+\& Motyl, M.
+\href{https://doi.org/10.1177/1745691612459058}{Scientific Utopia: II.
+Restructuring Incentives and Practices to Promote Truth Over Publishability}.
+\emph{Perspectives on Psychological Science} \textbf{7}, 615--631 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-isager2021}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{Isager, P.
+M., van 't Veer, A.
+E.
+\& Lakens, D.
+\emph{Replication value as a function of citation impact and sample size}.
+\url{https://osf.io/knjea} (2021) doi:\href{https://doi.org/10.31222/osf.io/knjea}{10.31222/osf.io/knjea}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-isager2021a}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{Isager, P.
+M.
+\emph{et al.} \href{https://doi.org/10.1037/met0000438}{Deciding what to replicate: {A} decision model for replication study selection under resource and knowledge constraints.} \emph{Psychological Methods} \textbf{28}, 438--451 (2023).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-10.7554ux2feLife.71601}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{Errington, T. M. \emph{et al.} \href{https://doi.org/10.7554/eLife.71601}{Investigating the replicability of preclinical cancer biology}. \emph{eLife} \textbf{10}, e71601 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{Silberzahn, R.
+\emph{et al.} Many analysts, one data set: Making transparent how variations in analytic choices affect results.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}, 337356 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-john2012}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{John, L.
+K., Loewenstein, G.
+\& Prelec, D.
+\href{https://doi.org/10.1177/0956797611430953}{Measuring the Prevalence of Questionable Research Practices With Incentives for Truth Telling}.
+\emph{Psychological Science} \textbf{23}, 524--532 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grahe2014}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Grahe, J.
+E.
+\href{https://doi.org/10.1080/00224545.2014.853582}{Announcing open science badges and reaching for the sky}.
+\emph{The Journal of Social Psychology} \textbf{154}, 1--3 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kidwell2016}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{Kidwell, M.
+C.
+\emph{et al.} \href{https://doi.org/10.1371/journal.pbio.1002456}{Badges to Acknowledge Open Practices: A Simple, Low-Cost, Effective Method for Increasing Transparency}.
+\emph{PLOS Biology} \textbf{14}, e1002456 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2015}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{Nosek, B. A. \emph{et al.} \href{https://doi.org/10.1126/science.aab2374}{Promoting an open research culture}. \emph{Science} \textbf{348}, 1422--1425 (2015).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-mayo-wilson2021}{}}%
-Mayo-Wilson, E., Grant, S., Supplee, L., Kianersi, S., Amin, A., DeHaven, A., \& Mellor, D.
-(2021).
-Evaluating implementation of the transparency and openness promotion~(TOP) guidelines:~The TRUST process for rating journal policies, procedures, and practices.
-\emph{Research Integrity and Peer Review}, \emph{6}(1), 9.
-\url{https://doi.org/10.1186/s41073-021-00112-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-moshontz2018}{}}%
-Moshontz, H., Campbell, L., Ebersole, C.
-R., IJzerman, H., Urry, H.
-L., Forscher, P.
-S., \ldots{} Chartier, C.
+\CSLLeftMargin{39. }%
+\CSLRightInline{Mayo-Wilson, E.
+\emph{et al.} \href{https://doi.org/10.1186/s41073-021-00112-8}{Evaluating implementation of the transparency and openness promotion~(TOP) guidelines:~The TRUST process for rating journal policies, procedures, and practices}.
+\emph{Research Integrity and Peer Review} \textbf{6}, 9 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{Nosek, B.
+A.
+\& Lakens, D.
+\href{https://doi.org/10.1027/1864-9335/a000192}{Registered Reports: A Method to Increase the Credibility of Published Results}.
+\emph{Social Psychology} \textbf{45}, 137--141 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stewart2020}{}}%
+\CSLLeftMargin{41. }%
+\CSLRightInline{Stewart, S.
+\emph{et al.} \emph{Pre-registration and registered reports: A primer from UKRN}.
+\url{https://osf.io/8v2n7} (2020) doi:\href{https://doi.org/10.31219/osf.io/8v2n7}{10.31219/osf.io/8v2n7}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-allen2019}{}}%
+\CSLLeftMargin{42. }%
+\CSLRightInline{Allen, L., O'Connell, A.
+\& Kiermer, V.
+\href{https://doi.org/10.1002/leap.1210}{How can we ensure visibility and diversity in research contributions?
+How the Contributor Role Taxonomy (CRediT) is helping the shift from authorship to contributorship}.
+\emph{Learned Publishing} \textbf{32}, 71--74 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-henrich2010}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{Henrich, J., Heine, S.
+J.
+\& Norenzayan, A.
+\href{https://doi.org/10.1017/S0140525X0999152X}{The weirdest people in the world?} \emph{Behavioral and Brain Sciences} \textbf{33}, 61--83 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-newson2021}{}}%
+\CSLLeftMargin{44. }%
+\CSLRightInline{Newson, M., Buhrmester, M., Xygalatas, D.
+\& Whitehouse, H.
+\href{https://doi.org/10.1558/jcsr.38413}{Go WILD, not WEIRD}.
+\emph{Journal for the Cognitive Science of Religion} \textbf{6}, (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rad2018}{}}%
+\CSLLeftMargin{45. }%
+\CSLRightInline{Rad, M.
+S., Martingano, A.
+J.
+\& Ginges, J.
+\href{https://doi.org/10.1073/pnas.1721165115}{Toward a psychology of homo sapiens: Making psychological science more representative of the human population}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 11401--11405 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-aphilos2021}{}}%
+\CSLLeftMargin{46. }%
+\CSLRightInline{\href{https://doi.org/10.1038/s41567-021-01278-0}{A philosophical case for big physics}. \emph{Nature Physics} \textbf{17}, 661--661 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-castelnovo2018}{}}%
+\CSLLeftMargin{47. }%
+\CSLRightInline{Castelnovo, P., Florio, M., Forte, S., Rossi, L.
+\& Sirtori, E.
+\href{https://doi.org/10.1016/j.respol.2018.06.018}{The economic impact of technological procurement for large-scale research infrastructures: Evidence from the Large Hadron Collider at CERN}.
+\emph{Research Policy} \textbf{47}, 1853--1867 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-collins2003}{}}%
+\CSLLeftMargin{48. }%
+\CSLRightInline{Collins, F.
+S., Morgan, M.
+\& Patrinos, A.
+\href{https://doi.org/10.1126/science.1084564}{The human genome project: Lessons from large-scale biology}.
+\emph{Science} \textbf{300}, 286--290 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vanbavel2022}{}}%
+\CSLLeftMargin{49. }%
+\CSLRightInline{Van Bavel, J.
+J.
+\emph{et al.} \href{https://doi.org/10.1038/s41467-021-27668-9}{National identity predicts public health support during a global pandemic}.
+\emph{Nature Communications} \textbf{13}, 517 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sinatra2015}{}}%
+\CSLLeftMargin{50. }%
+\CSLRightInline{Sinatra, R., Deville, P., Szell, M., Wang, D. \& Barabási, A.-L. \href{https://doi.org/10.1038/nphys3494}{A century of physics}. \emph{Nature Physics} \textbf{11}, 791--796 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wuchty2007}{}}%
+\CSLLeftMargin{51. }%
+\CSLRightInline{Wuchty, S., Jones, B.
+F.
+\& Uzzi, B.
+\href{https://doi.org/10.1126/science.1136099}{The increasing dominance of teams in production of knowledge}.
+\emph{Science} \textbf{316}, 1036--1039 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hunter2008}{}}%
+\CSLLeftMargin{52. }%
+\CSLRightInline{Hunter, L.
+\& Leahey, E.
+\href{https://doi.org/10.1007/s12108-008-9042-1}{Collaborative Research in Sociology: Trends and Contributing Factors}.
+\emph{The American Sociologist} \textbf{39}, 290--306 (2008).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lariviuxe8re2015}{}}%
+\CSLLeftMargin{53. }%
+\CSLRightInline{Larivière, V., Gingras, Y., Sugimoto, C.
 R.
-(2018).
-The Psychological Science Accelerator: Advancing Psychology Through a Distributed Collaborative Network.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 501--515.
-\url{https://doi.org/10.1177/2515245918797607}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
-Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
-
-\leavevmode\vadjust pre{\hypertarget{ref-newson2021}{}}%
-Newson, M., Buhrmester, M., Xygalatas, D., \& Whitehouse, H. (2021). Go WILD, not WEIRD. \emph{Journal for the Cognitive Science of Religion}, \emph{6}(1-2). \url{https://doi.org/10.1558/jcsr.38413}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2015}{}}%
-Nosek, B.
-A., Alter, G., Banks, G.
-C., Borsboom, D., Bowman, S.
-D., Breckler, S.
-J., \ldots{} Yarkoni, T.
-(2015).
-Promoting an open research culture.
-\emph{Science}, \emph{348}(6242), 1422--1425.
-\url{https://doi.org/10.1126/science.aab2374}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
-Nosek, Brian A., \& Lakens, D. (2014a). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137141.
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
-Nosek, Brian A., \& Lakens, D.
-(2014b).
-Registered Reports: A Method to Increase the Credibility of Published Results.
-\emph{Social Psychology}, \emph{45}(3), 137--141.
-\url{https://doi.org/10.1027/1864-9335/a000192}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2012}{}}%
-Nosek, Brian A., Spies, J.
-R., \& Motyl, M.
-(2012).
-Scientific Utopia: II.
-Restructuring Incentives and Practices to Promote Truth Over Publishability.
-\emph{Perspectives on Psychological Science}, \emph{7}(6), 615--631.
-\url{https://doi.org/10.1177/1745691612459058}
-
-\leavevmode\vadjust pre{\hypertarget{ref-oed2016}{}}%
-OED. (2016). \emph{Collaboration}. Oxford: Oxford University.
-
-\leavevmode\vadjust pre{\hypertarget{ref-opensciencecollaboration2015}{}}%
-Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716--aac4716. \url{https://doi.org/10.1126/science.aac4716}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rad2018}{}}%
-Rad, M.
-S., Martingano, A.
-J., \& Ginges, J.
-(2018).
-Toward a psychology of homo sapiens: Making psychological science more representative of the human population.
-\emph{Proceedings of the National Academy of Sciences}, \emph{115}(45), 11401--11405.
-\url{https://doi.org/10.1073/pnas.1721165115}
-
-\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
-Silberzahn, R., Uhlmann, E.
-L., Martin, D.
-P., Anselmi, P., Aust, F., Awtrey, E., \ldots{} others.
-(2018).
-Many analysts, one data set: Making transparent how variations in analytic choices affect results.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337356.
-
-\leavevmode\vadjust pre{\hypertarget{ref-skorb2020}{}}%
-Skorb, L., Aczel, B., Bakos, B.
-E., Feinberg, L., Hałasa, E., Kauff, M., \ldots{} Hartshorne, J.
-K.
-(2020).
-Many Labs 5: Replication of van Dijk, van Kleef, Steinel, and van Beest (2008).
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 418--428.
-\url{https://doi.org/10.1177/2515245920927643}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stewart2017}{}}%
-Stewart, N., Chandler, J., \& Paolacci, G.
-(2017).
-Crowdsourcing samples in cognitive science.
-\emph{Trends in Cognitive Sciences}, \emph{21}(10), 736--748.
-\url{https://doi.org/10.1016/j.tics.2017.06.007}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stewart2020}{}}%
-Stewart, S., Rinke, E.
-M., McGarrigle, R., Lynott, D., Lunny, C., Lautarescu, A., \ldots{} Crook, Z.
-(2020).
-\emph{Pre-registration and registered reports: A primer from UKRN}.
-\url{https://doi.org/10.31219/osf.io/8v2n7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vanbavel2022}{}}%
-Van Bavel, J.
-J., Cichocka, A., Capraro, V., Sjåstad, H., Nezlek, J.
-B., Pavlović, T., \ldots{} Boggio, P.
-S.
-(2022).
-National identity predicts public health support during a global pandemic.
-\emph{Nature Communications}, \emph{13}(1), 517.
-\url{https://doi.org/10.1038/s41467-021-27668-9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
-Vazire, S., Schiavone, S.
-R., \& Bottesini, J.
-G.
-(2022).
-Credibility Beyond Replicability: Improving the Four Validities in Psychological Science.
-\emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168.
-\url{https://doi.org/10.1177/09637214211067779}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wang2021}{}}%
-Wang, K., Goldenberg, A., Dorison, C.
-A., Miller, J.
-K., Uusberg, A., Lerner, J.
-S., \ldots{} Moshontz, H.
-(2021).
-A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic.
-\emph{Nature Human Behaviour}, \emph{5}(8), 1089--1110.
-\url{https://doi.org/10.1038/s41562-021-01173-x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
-Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
+\& Tsou, A.
+\href{https://doi.org/10.1002/asi.23266}{Team size matters: Collaboration and scientific impact since 1900}.
+\emph{Journal of the Association for Information Science and Technology} \textbf{66}, 1323--1332 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lu2007}{}}%
+\CSLLeftMargin{54. }%
+\CSLRightInline{Lu, Y.
+\href{https://doi.org/10.1016/j.lisr.2006.10.007}{The human in human information acquisition: Understanding gatekeeping and proposing new directions in scholarship}.
+\emph{Library \& Information Science Research} \textbf{29}, 103--123 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-siler2015}{}}%
+\CSLLeftMargin{55. }%
+\CSLRightInline{Siler, K., Lee, K.
+\& Bero, L.
+\href{https://doi.org/10.1073/pnas.1418218112}{Measuring the effectiveness of scientific gatekeeping}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{112}, 360--365 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-caplow2017}{}}%
+\CSLLeftMargin{56. }%
+\CSLRightInline{Caplow, T. \emph{The academic marketplace}. (Routledge, 2017). doi:\href{https://doi.org/10.4324/9781351305969}{10.4324/9781351305969}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kyvik2003}{}}%
+\CSLLeftMargin{57. }%
+\CSLRightInline{Kyvik, S.
+\href{https://doi.org/10.1023/A:1025475423482}{Changing trends in publishing behaviour among university faculty, 1980-2000}.
+\emph{Scientometrics} \textbf{58}, 35--48 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xie2014}{}}%
+\CSLLeftMargin{58. }%
+\CSLRightInline{Xie, Y. \href{https://doi.org/10.1126/science.1252743}{{``}Undemocracy{''}: Inequalities in science}. \emph{Science} \textbf{344}, 809--810 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2015}{}}%
+\CSLLeftMargin{59. }%
+\CSLRightInline{Freeman, R.
+B.
+\& Huang, W.
+\href{https://doi.org/10.1086/678973}{Collaborating with People Like Me: Ethnic Coauthorship within the United States}.
+\emph{Journal of Labor Economics} \textbf{33}, S289--S318 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hinnant2012}{}}%
+\CSLLeftMargin{60. }%
+\CSLRightInline{Hinnant, C.
+C.
+\emph{et al.} \href{https://doi.org/10.1016/j.lisr.2012.03.001}{Author-team diversity and the impact of scientific publications: Evidence from physics research at a national science lab}.
+\emph{Library \& Information Science Research} \textbf{34}, 249--257 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jones2008}{}}%
+\CSLLeftMargin{61. }%
+\CSLRightInline{Jones, B.
+F., Wuchty, S.
+\& Uzzi, B.
+\href{https://doi.org/10.1126/science.1158357}{Multi-university research teams: Shifting impact, geography, and stratification in science}.
+\emph{Science} \textbf{322}, 1259--1262 (2008).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-yang2022}{}}%
+\CSLLeftMargin{62. }%
+\CSLRightInline{Yang, Y., Tian, T.
+Y., Woodruff, T.
+K., Jones, B.
+F.
+\& Uzzi, B.
+\href{https://doi.org/10.1073/pnas.2200841119}{Gender-diverse teams produce more novel and higher-impact scientific ideas}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{119}, e2200841119 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-albarillo2014}{}}%
+\CSLLeftMargin{63. }%
+\CSLRightInline{Albarillo, F.
+\href{https://doi.org/10.1080/01639269.2014.904693}{Language in social science databases: English versus non-english articles in JSTOR and scopus}.
+\emph{Behavioral \& Social Sciences Librarian} \textbf{33}, 77--90 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meneghini2007}{}}%
+\CSLLeftMargin{64. }%
+\CSLRightInline{Meneghini, R. \& Packer, A. L. \href{https://doi.org/10.1038/sj.embor.7400906}{Is there science beyond english?} \emph{EMBO reports} \textbf{8}, 112--116 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ramuxedrez-castauxf1eda2020}{}}%
+\CSLLeftMargin{65. }%
+\CSLRightInline{Ramírez-Castañeda, V.
+\href{https://doi.org/10.1371/journal.pone.0238372}{Disadvantages in preparing and publishing scientific papers caused by the dominance of the English language in science: The case of Colombian researchers in biological sciences}.
+\emph{PLOS ONE} \textbf{15}, e0238372 (2020).}
 
@@
 
-\hypertarget{rq1-publisher-information.-2}{%
-\subsection{RQ1: Publisher Information.}\label{rq1-publisher-information.-2}}
+\hypertarget{rq1-publisher-information.-1}{%
+\subsection{RQ1: Publisher Information.}\label{rq1-publisher-information.-1}}
 
@@
 
-\hypertarget{rq2-publication-information.-2}{%
-\subsection{RQ2: Publication Information.}\label{rq2-publication-information.-2}}
+\hypertarget{rq2-publication-information.-1}{%
+\subsection{RQ2: Publication Information.}\label{rq2-publication-information.-1}}
 
@@
 Institution was normalized by taking the total number of unique institutions and dividing by the total number of institution listings.
-The patterns are similar for each decade in that papers are often either half unique institutions or mostly unique institutions overall as show in Figure \ref{fig:fig-inst}.
+The patterns are similar for each decade in that papers are often either half unique institutions or mostly unique institutions overall as shown in Figure \ref{fig:fig-inst}.
 
@@
 The patterns of publications are roughly similar for big team science authors and all authors.
-It appears that porportionally, big team members are more likely to post preprints in comparison to all authors.
+It appears that proportionally, big team members are more likely to post preprints in comparison to all authors.
 

### 2023-08-29 manuscript_scopus.Rmd
typo

@@
 materials, reliability, generalizability and more robust sample sizes
-(when necessary) in a study [@auspurg2021]; @nosek2014method;
+(when necessary) in a study [@auspurg2021; @nosek2014method;
 @lebel2018].

### 2023-08-29 manuscript_scopus.tex
typo

@@
 materials, reliability, generalizability and more robust sample sizes
-(when necessary) in a study\textsuperscript{8};\textsuperscript{9};\textsuperscript{10}{]}.
+(when necessary) in a study\textsuperscript{8--10}.
 

### 2023-08-29 manuscript_scopus.Rmd
updating manuscript

@@
 @yang2022] with higher citation metrics for more diverse author lists.
-The introduction of contributorship models [e.g., CRediT @allen2019]
+The introduction of contributorship models (e.g., CRediT[@allen2019])
 will hopefully continue to push these effects down, as they highlight

### 2023-08-29 manuscript_scopus.tex
updating manuscript

@@
 papers with stronger ``impact''\textsuperscript{59--62} with higher citation metrics for more diverse author lists.
-The introduction of contributorship models\textsuperscript{e.g., CRediT 42}
+The introduction of contributorship models (e.g., CRediT\textsuperscript{42})
 will hopefully continue to push these effects down, as they highlight

### 2023-09-18 manuscript_scopus.Rmd
fixing author typo

@@
 # updated
-total_authors <- 510334
+total_authors <- 3047067
 avg_authors <- apa_num(49.30516877182394)

### 2023-09-18 manuscript_scopus.tex
fixing author typo

@@
 The total number of unique authors across all publications was
-510334. The mean number of authors per publication was \emph{M} =
+3047067. The mean number of authors per publication was \emph{M} =
 49.31 (\emph{SD} = 212.98, \emph{Med} = 18) with a
@@
 The keywords were tokenized into single tokens.
-Keywords were then lowercased, and all stop words (for example, the, an, of, into, for) were removed.
+Keywords were then lower cased, and all stop words (for example, the, an, of, into, for) were removed.
 Finally, a frequency count of tokens was tabulated for each subject area, and this count is used to create the final word cloud presented.

### 2023-10-02 manuscript_scopus.Rmd
adding significance statement

@@
   Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript.
+
+  Significance statement: This work is the first to examine big team science authorship (i.e., 10+ authors) across millions of published works.
+Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing numbers of publications that increasingly represent earlier career and varied scholars.
+The number of geopolitical entities for researcher affiliation is increasing over time, showing the results of globalization and the ability to connect across time zones and cultures.
+While publications are generally diversifying, we did not yet find equality in the representation for first or corresponding authors.
+First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
 abstract: |

### 2023-10-02 manuscript_scopus.tex
adding significance statement

@@
 
+Significance statement: This work is the first to examine big team science authorship (i.e., 10+ authors) across millions of published works.
+Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing numbers of publications that increasingly represent earlier career and varied scholars.
+The number of geopolitical entities for researcher affiliation is increasing over time, showing the results of globalization and the ability to connect across time zones and cultures.
+While publications are generally diversifying, we did not yet find equality in the representation for first or corresponding authors.
+First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
+
 The authors made the following contributions.

### 2023-10-25 manuscript_scopus.Rmd
notes updated

@@
 @moshontz2018; @wang2021]. Generally, the researcher incentive for
-replication was low for three reasons. First, journals often prioritize
+replication and/or involvement in big-team projects was low for three reasons. First, journals often prioritize
 "novel" or new results which led to rejection of replication manuscripts
@@
 in participating in large-scale replication studies [@grahe2014;
-@kidwell2016; @nosek2015; @mayo-wilson2021]. For example, the support
+@kidwell2016; @nosek2015; @mayo-wilson2021]. In some fields, the 
+replication movement demonstrated that large-scale teams were a 
+practical (and publishable) solution to answering research questions 
+in generalizable way. The support
 for Registered Reports, papers accepted before the data has been
-collected [@nosek2014; @stewart2020], and entire sub-sections of
-journals devoted to only replication studies (e.g., *Nature, Royal
-Society Open Science, Advances in Methods and Practices in Psychological
-Science*) has allowed researchers to invest in projects that they know
+collected [@nosek2014; @stewart2020], has allowed researchers to 
+invest in projects that they know
 should be published when the project is complete. Further, the
@@
 
-The credibility movement has been mirrored by the calls for
+Beyond the replication movement, the credibility movement has  
+mirrored calls for
 diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
@@
 
+RELATE THIS MORE TO THE RQS ### 
 Therefore, the goal of this manuscript is to examine the *people*
@@
 authors at ten different institutions that were published in
-peer-reviewed journals or had posted a full paper pre-print. We used
+peer-reviewed journals or had posted a full paper pre-print. While this 
+definition is a somewhat arbitrary choice, we separate this research 
+from research on team science that uses any multi-university collaboration 
+as a definition [@jones2008] to focus on larger sized teams rather 
+than teams of any size. With at least ten institutions, the complexities 
+of infrastructure, resources, tenure and promotion policies, ethics review, and more can occur [@forscher2022a].
+Therefore, we believe this choice selects publications that would be "big" teams and those potential obstacles.
+
+We used
 data from 1970 and forward in the Scopus database, as it is noted online
@@
 *h*-count was only used for descriptive statistics.
+
+### SAV WHY H INDEX IS USEFUL HERE ###
 
@@
 ```
+
+### MORE EXPLAIN HERE ####
 
@@
 
+### MORE EXPLAIN HERE ###
+
 ```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.

### 2023-11-01 manuscript_scopus.Rmd
updating the manuscript

@@
 
-RELATE THIS MORE TO THE RQS ### 
-Therefore, the goal of this manuscript is to examine the *people*
-involved in BTS projects. We specifically examined the themes of
-inclusivity, research careers, and research globalization. We see an
-increasing interest and number of publications in BTS but we do not yet
+Therefore, the goal of this manuscript is to examine both the *publications* and *people* involved in BTS projects.
+We present descriptive information about the publication sources and types of articles that we classified as BTS projects to demonstrate what areas of research show large-scale research.
+Next, we examine the individuals involved in those projects for descriptive and predictive purposes.
+To describe the people involved in BTS projects, we used education, types of publications (i.e., articles, preprints, books, etc.) from BTS individuals, and publication metrics.
+
+For predictive statistics, we explored the change in diversity of authors over time. We see an increasing interest and number of publications in BTS but we do not yet
 know if this uptick in large-scale projects has diversified the *people*
@@
 -   Research Question 3: Who is involved in big team science?
+-   Research Question 4: How has the diversity of those involved in big team science changed over time?
 
@@
 
-### RQ3: Author Information
+### RQ3: Author Descriptive Statistics
 
@@
 
-***Career Length***. Career length for each author was defined as the
-year of the first publication minus the current year listed for each
-author.
-
-***Institution and Geopolitical Region***. We used the affiliation ids
-and country to gather information about the places of education and/or
-employment for authors. Geopolitical region was created by binning these
-codes into United Nation Regions.
-
 ***Education***. We collected degree information from the author table.
@@
 
-***Publication Metrics***. For each author, we calculated the total
-number of publications, and the h-index. The h-index represents the
-highest *h* number of publications that have at least *h* citations.
-*h*-count was only used for descriptive statistics.
-
-### SAV WHY H INDEX IS USEFUL HERE ###
+***Publication Metrics***. For each author, we calculated the number of publications and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.
+
+***Institutions***. We report the number of institutions involved in big team science publications.
+
+### RQ4: Author Diversity Statistics \
+
+***Seniority***. Career length for each author was defined as the
+year of the first publication minus the current year listed for each
+author.
+Number of publications included the number of unique entries an author was included in the database.
+Career length and number of publications was used as a proxy for the "age" or "seniority" of a scholar to assess if only senior scholars were
+
+***Geopolitical Region***. Geopolitical region was created by binning country code identifiers into the 17 identified United Nation Regions.
 
@@
 
-## RQ3: Authors.
+## RQ3: Author Descriptive Statistics
 
@@
 
-***Career Length***.
-
-Figure \@ref(fig:fig-career) portrays the average career length for
+```{r pub-hindex}
+avg_pub_count_author	<- apa_num(38.368910766896065)
+std_pub_count_author <- apa_num(102.53740454680472)
+
+avg_pub_count_paper <- apa_num(162.50184385336053)
+sd_pub_count_paper <- apa_num(155.1665533053519)
+avg_SD_pub_count_paper <- apa_num(164.27249797983876)
+SD_SD_pub_count_paper <- apa_num(127.20989934008757)
+
+avg_HIndex <- apa_num(33.64589690529209)
+std_HIndex <- apa_num(127.33565834550778)
+med_HIndex <- apa_num(8.0)
+
+avg_of_avg_HIndex <- apa_num(198.87318851400775)
+std_of_avg_HIndex <- apa_num(248.7847084313958)
+avg_of_std_HIndex <- apa_num(211.7985924228093)
+std_of_std_HIndex <- apa_num(238.53141146314053)
+med_of_med_HIndex <- apa_num(68.0)
+```
+
+***Publication Metrics***. The average number of publications by authors on big team science papers
+is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`). The
+publication counts were averaged across authors for each publication,
+and then these average publication counts were averaged across
+publications *M* = `r avg_pub_count_paper` (*SD* =
+`r sd_pub_count_paper`). The average variability (i.e., the average
+standard deviation with authors of a manuscript) with publication counts
+of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
+`r SD_SD_pub_count_paper`).
+
+The same process was completed with *h*-index for each author and
+publication. The average *h*-index for authors overall was *M* =
+`r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`). The
+average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD*
+= `r std_of_avg_HIndex`), and the variability of *h*-index across
+manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ =
+`r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).
+
+```{r total-aff}
+# updated
+affs <- 463876
+```
+
+***Institutions***. The total number of unique affiliation across all papers was `r affs`.
+
+## RQ4: Author Diversity Statistics
+
+***Seniority***. Figure \@ref(fig:fig-career) portrays the average career length for
 authors involved in BTS publications across years. Career length was
@@
 
-### MORE EXPLAIN HERE ####
-
 ```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region.
+Each square represents a *b* value or the slope of the predictor (x-axis) onto the dependent variable (each panel).
+Slopes included both the overall value of the predictor ($b$, $b_M$) and the standard deviation of the predictor over time ($b_{SD}$).
+The color of the square represents the strength of the predictor.
 The top figure represents all results together for comparison across analyses.
@@
 
-***Institution***.
-
-```{r total-aff}
-# updated
-affs <- 463876
-```
-
-The total number of unique affiliation across all papers was `r affs`.
-
-***Publication Metrics***.
-
-```{r pub-hindex}
-avg_pub_count_author	<- apa_num(38.368910766896065)
-std_pub_count_author <- apa_num(102.53740454680472)
-
-avg_pub_count_paper <- apa_num(162.50184385336053)
-sd_pub_count_paper <- apa_num(155.1665533053519)
-avg_SD_pub_count_paper <- apa_num(164.27249797983876)
-SD_SD_pub_count_paper <- apa_num(127.20989934008757)
-
-avg_HIndex <- apa_num(33.64589690529209)
-std_HIndex <- apa_num(127.33565834550778)
-med_HIndex <- apa_num(8.0)
-
-avg_of_avg_HIndex <- apa_num(198.87318851400775)
-std_of_avg_HIndex <- apa_num(248.7847084313958)
-avg_of_std_HIndex <- apa_num(211.7985924228093)
-std_of_std_HIndex <- apa_num(238.53141146314053)
-med_of_med_HIndex <- apa_num(68.0)
-```
-
-The average number of publications by authors on big team science papers
-is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`). The
-publication counts were averaged across authors for each publication,
-and then these average publication counts were averaged across
-publications *M* = `r avg_pub_count_paper` (*SD* =
-`r sd_pub_count_paper`). The average variability (i.e., the average
-standard deviation with authors of a manuscript) with publication counts
-of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
-`r SD_SD_pub_count_paper`).
-
-The same process was completed with *h*-index for each author and
-publication. The average *h*-index for authors overall was *M* =
-`r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`). The
-average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD*
-= `r std_of_avg_HIndex`), and the variability of *h*-index across
-manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ =
-`r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).
-
-We used the same analyses described in the career length section to
-analyze trends over time. An increasing slope over time indicates that
+We used the same analyses using number of publications to represent diversity instead of career length. An increasing slope over time indicates that
 individuals who are publishing more are more represented in BTS over
@@
 
-### MORE EXPLAIN HERE ###
-
 ```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.
-The mosaic plot is grouped by UN subregion with the largest number of publications on the left and smallest on the top right.
-", fig.width=10, fig.height=6}
+The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right.
+Therefore, North America represents the largest number of authors within BTS (i.e., bottom right, then separated into the geopolitical areas within that subregion), followed by Eastern Europe (top left), and so on.", fig.width=10, fig.height=6}
 bin_country + ggtitle("Big-Team Publication Map") + 

### 2023-11-01 manuscript_scopus.tex
updating the manuscript

@@
 Psychological Science Accelerator\textsuperscript{21--27}. Generally, the researcher incentive for
-replication was low for three reasons. First, journals often prioritize
+replication and/or involvement in big-team projects was low for three reasons. First, journals often prioritize
 ``novel'' or new results which led to rejection of replication manuscripts
@@
 change in journal guidelines and incentives for researchers interested
-in participating in large-scale replication studies\textsuperscript{36--39}. For example, the support
+in participating in large-scale replication studies\textsuperscript{36--39}. In some fields, the
+replication movement demonstrated that large-scale teams were a
+practical (and publishable) solution to answering research questions
+in generalizable way. The support
 for Registered Reports, papers accepted before the data has been
-collected\textsuperscript{40,41}, and entire sub-sections of
-journals devoted to only replication studies (e.g., \emph{Nature, Royal
-Society Open Science, Advances in Methods and Practices in Psychological
-Science}) has allowed researchers to invest in projects that they know
+collected\textsuperscript{40,41}, has allowed researchers to
+invest in projects that they know
 should be published when the project is complete. Further, the
@@
 
-The credibility movement has been mirrored by the calls for
+Beyond the replication movement, the credibility movement has\\
+mirrored calls for
 diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
@@
 
-Therefore, the goal of this manuscript is to examine the \emph{people}
-involved in BTS projects. We specifically examined the themes of
-inclusivity, research careers, and research globalization. We see an
-increasing interest and number of publications in BTS but we do not yet
+Therefore, the goal of this manuscript is to examine both the \emph{publications} and \emph{people} involved in BTS projects.
+We present descriptive information about the publication sources and types of articles that we classified as BTS projects to demonstrate what areas of research show large-scale research.
+Next, we examine the individuals involved in those projects for descriptive and predictive purposes.
+To describe the people involved in BTS projects, we used education, types of publications (i.e., articles, preprints, books, etc.) from BTS individuals, and publication metrics.
+
+For predictive statistics, we explored the change in diversity of authors over time. We see an increasing interest and number of publications in BTS but we do not yet
 know if this uptick in large-scale projects has diversified the \emph{people}
@@
   Research Question 3: Who is involved in big team science?
+\item
+  Research Question 4: How has the diversity of those involved in big team science changed over time?
 \end{itemize}
@@
 authors at ten different institutions that were published in
-peer-reviewed journals or had posted a full paper pre-print. We used
+peer-reviewed journals or had posted a full paper pre-print. While this
+definition is a somewhat arbitrary choice, we separate this research
+from research on team science that uses any multi-university collaboration
+as a definition\textsuperscript{50} to focus on larger sized teams rather
+than teams of any size. With at least ten institutions, the complexities
+of infrastructure, resources, tenure and promotion policies, ethics review, and more can occur\textsuperscript{3}.
+Therefore, we believe this choice selects publications that would be ``big'' teams and those potential obstacles.
+
+We used
 data from 1970 and forward in the Scopus database, as it is noted online
@@
 
-\hypertarget{rq3-author-information}{%
-\subsubsection{RQ3: Author Information}\label{rq3-author-information}}
+\hypertarget{rq3-author-descriptive-statistics}{%
+\subsubsection{RQ3: Author Descriptive Statistics}\label{rq3-author-descriptive-statistics}}
 
@@
 
-\textbf{\emph{Career Length}}. Career length for each author was defined as the
-year of the first publication minus the current year listed for each
-author.
-
-\textbf{\emph{Institution and Geopolitical Region}}. We used the affiliation ids
-and country to gather information about the places of education and/or
-employment for authors. Geopolitical region was created by binning these
-codes into United Nation Regions.
-
 \textbf{\emph{Education}}. We collected degree information from the author table.
@@
 
-\textbf{\emph{Publication Metrics}}. For each author, we calculated the total
-number of publications, and the h-index. The h-index represents the
-highest \emph{h} number of publications that have at least \emph{h} citations.
-\emph{h}-count was only used for descriptive statistics.
+\textbf{\emph{Publication Metrics}}.
+For each author, we calculated the number of publications and the h-index.
+The h-index represents the highest \emph{h} number of publications that have at least \emph{h} citations.
+
+\textbf{\emph{Institutions}}. We report the number of institutions involved in big team science publications.
+
+\hypertarget{rq4-author-diversity-statistics}{%
+\subsubsection{RQ4: Author Diversity Statistics ~}\label{rq4-author-diversity-statistics}}
+
+\textbf{\emph{Seniority}}. Career length for each author was defined as the
+year of the first publication minus the current year listed for each
+author.
+Number of publications included the number of unique entries an author was included in the database.
+Career length and number of publications was used as a proxy for the ``age'' or ``seniority'' of a scholar to assess if only senior scholars were
+
+\textbf{\emph{Geopolitical Region}}. Geopolitical region was created by binning country code identifiers into the 17 identified United Nation Regions.
 
@@
 
-\hypertarget{rq3-authors.}{%
-\subsection{RQ3: Authors.}\label{rq3-authors.}}
+\hypertarget{rq3-author-descriptive-statistics-1}{%
+\subsection{RQ3: Author Descriptive Statistics}\label{rq3-author-descriptive-statistics-1}}
 
@@
 
-\textbf{\emph{Career Length}}.
-
-Figure \ref{fig:fig-career} portrays the average career length for
+\textbf{\emph{Publication Metrics}}. The average number of publications by authors on big team science papers
+is \emph{M} = 38.37 (\emph{SD} = 102.54). The
+publication counts were averaged across authors for each publication,
+and then these average publication counts were averaged across
+publications \emph{M} = 162.50 (\emph{SD} =
+155.17). The average variability (i.e., the average
+standard deviation with authors of a manuscript) with publication counts
+of a paper was \(M_{SD}\) = 164.27 (\(SD_{SD}\) =
+127.21).
+
+The same process was completed with \emph{h}-index for each author and
+publication. The average \emph{h}-index for authors overall was \emph{M} =
+33.65 (\emph{SD} = 127.34, \emph{Med} = 8.00). The
+average \emph{h}-index for publications was \emph{M} = 198.87 (\emph{SD}
+= 248.78), and the variability of \emph{h}-index across
+manuscripts was \(M_{SD}\) = 211.80 (\(SD_{SD}\) =
+238.53, \(Med_{Med}\) = 68.00).
+
+\textbf{\emph{Institutions}}. The total number of unique affiliation across all papers was 463876.
+
+\hypertarget{rq4-author-diversity-statistics-1}{%
+\subsection{RQ4: Author Diversity Statistics}\label{rq4-author-diversity-statistics-1}}
+
+\textbf{\emph{Seniority}}. Figure \ref{fig:fig-career} portrays the average career length for
 authors involved in BTS publications across years. Career length was
@@
 \caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region.
+Each square represents a \emph{b} value or the slope of the predictor (x-axis) onto the dependent variable (each panel).
+Slopes included both the overall value of the predictor (\(b\), \(b_M\)) and the standard deviation of the predictor over time (\(b_{SD}\)).
+The color of the square represents the strength of the predictor.
 The top figure represents all results together for comparison across analyses.
@@
 
-\textbf{\emph{Institution}}.
-
-The total number of unique affiliation across all papers was 463876.
-
-\textbf{\emph{Publication Metrics}}.
-
-The average number of publications by authors on big team science papers
-is \emph{M} = 38.37 (\emph{SD} = 102.54). The
-publication counts were averaged across authors for each publication,
-and then these average publication counts were averaged across
-publications \emph{M} = 162.50 (\emph{SD} =
-155.17). The average variability (i.e., the average
-standard deviation with authors of a manuscript) with publication counts
-of a paper was \(M_{SD}\) = 164.27 (\(SD_{SD}\) =
-127.21).
-
-The same process was completed with \emph{h}-index for each author and
-publication. The average \emph{h}-index for authors overall was \emph{M} =
-33.65 (\emph{SD} = 127.34, \emph{Med} = 8.00). The
-average \emph{h}-index for publications was \emph{M} = 198.87 (\emph{SD}
-= 248.78), and the variability of \emph{h}-index across
-manuscripts was \(M_{SD}\) = 211.80 (\(SD_{SD}\) =
-238.53, \(Med_{Med}\) = 68.00).
-
-We used the same analyses described in the career length section to
-analyze trends over time. An increasing slope over time indicates that
+We used the same analyses using number of publications to represent diversity instead of career length. An increasing slope over time indicates that
 individuals who are publishing more are more represented in BTS over
@@
 \caption{\label{fig:fig-map-both}Geopolitical regions represented in big-team science publications versus all publications.
-The mosaic plot is grouped by UN subregion with the largest number of publications on the left and smallest on the top right.}
+The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right.
+Therefore, North America represents the largest number of authors within BTS (i.e., bottom right, then separated into the geopolitical areas within that subregion), followed by Eastern Europe (top left), and so on.}
 \end{figure}
@@
 authors included on manuscripts, replicating previous investigations
-into this topic area\textsuperscript{50--52}.
+into this topic area\textsuperscript{51--53}.
 
@@
 has shown that larger-team publications do receive more citations and
-appear to have higher impact\textsuperscript{53}.
+appear to have higher impact\textsuperscript{54}.
 
@@
 are potentially driving forces behind our results, but, hopefully, the
-results also point to a decline in scientific gatekeeping\textsuperscript{54,55}.
+results also point to a decline in scientific gatekeeping\textsuperscript{55,56}.
 
@@
 positions, one potential way to distinguish their application would be a
-larger number of publications in their early career\textsuperscript{56,57}.
+larger number of publications in their early career\textsuperscript{57,58}.
 
@@
 increasing over time, showing the results of globalization and the
-ability to connect across time zones and cultures\textsuperscript{58}. While our
+ability to connect across time zones and cultures\textsuperscript{59}. While our
 definition of big team science required at least ten different
@@
 if they are slowly decreasing. Diverse teams are more likely to have
-papers with stronger ``impact''\textsuperscript{59--62} with higher citation metrics for more diverse author lists.
+papers with stronger ``impact''\textsuperscript{50,60--62} with higher citation metrics for more diverse author lists.
 The introduction of contributorship models (e.g., CRediT\textsuperscript{42})
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-jones2008}{}}%
+\CSLLeftMargin{50. }%
+\CSLRightInline{Jones, B.
+F., Wuchty, S.
+\& Uzzi, B.
+\href{https://doi.org/10.1126/science.1158357}{Multi-university research teams: Shifting impact, geography, and stratification in science}.
+\emph{Science} \textbf{322}, 1259--1262 (2008).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-sinatra2015}{}}%
-\CSLLeftMargin{50. }%
+\CSLLeftMargin{51. }%
 \CSLRightInline{Sinatra, R., Deville, P., Szell, M., Wang, D. \& Barabási, A.-L. \href{https://doi.org/10.1038/nphys3494}{A century of physics}. \emph{Nature Physics} \textbf{11}, 791--796 (2015).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wuchty2007}{}}%
-\CSLLeftMargin{51. }%
+\CSLLeftMargin{52. }%
 \CSLRightInline{Wuchty, S., Jones, B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hunter2008}{}}%
-\CSLLeftMargin{52. }%
+\CSLLeftMargin{53. }%
 \CSLRightInline{Hunter, L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lariviuxe8re2015}{}}%
-\CSLLeftMargin{53. }%
+\CSLLeftMargin{54. }%
 \CSLRightInline{Larivière, V., Gingras, Y., Sugimoto, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lu2007}{}}%
-\CSLLeftMargin{54. }%
+\CSLLeftMargin{55. }%
 \CSLRightInline{Lu, Y.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-siler2015}{}}%
-\CSLLeftMargin{55. }%
+\CSLLeftMargin{56. }%
 \CSLRightInline{Siler, K., Lee, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-caplow2017}{}}%
-\CSLLeftMargin{56. }%
+\CSLLeftMargin{57. }%
 \CSLRightInline{Caplow, T. \emph{The academic marketplace}. (Routledge, 2017). doi:\href{https://doi.org/10.4324/9781351305969}{10.4324/9781351305969}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kyvik2003}{}}%
-\CSLLeftMargin{57. }%
+\CSLLeftMargin{58. }%
 \CSLRightInline{Kyvik, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-xie2014}{}}%
-\CSLLeftMargin{58. }%
+\CSLLeftMargin{59. }%
 \CSLRightInline{Xie, Y. \href{https://doi.org/10.1126/science.1252743}{{``}Undemocracy{''}: Inequalities in science}. \emph{Science} \textbf{344}, 809--810 (2014).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-freeman2015}{}}%
-\CSLLeftMargin{59. }%
+\CSLLeftMargin{60. }%
 \CSLRightInline{Freeman, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hinnant2012}{}}%
-\CSLLeftMargin{60. }%
+\CSLLeftMargin{61. }%
 \CSLRightInline{Hinnant, C.
@@
 \emph{Library \& Information Science Research} \textbf{34}, 249--257 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jones2008}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{Jones, B.
-F., Wuchty, S.
-\& Uzzi, B.
-\href{https://doi.org/10.1126/science.1158357}{Multi-university research teams: Shifting impact, geography, and stratification in science}.
-\emph{Science} \textbf{322}, 1259--1262 (2008).}
 

### 2023-11-01 manuscript_scopus.Rmd
adding one more sentence

@@
 ```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region.
-Each square represents a *b* value or the slope of the predictor (x-axis) onto the dependent variable (each panel).
+Each square represents a *b* value or the slope of the predictor (x-axis) onto the dependent variable (each panel), with the exception of the bottom row which is the effect size of each regression analysis $R^2$.
 Slopes included both the overall value of the predictor ($b$, $b_M$) and the standard deviation of the predictor over time ($b_{SD}$).

### 2023-11-01 manuscript_scopus.tex
adding one more sentence

@@
 \caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region.
-Each square represents a \emph{b} value or the slope of the predictor (x-axis) onto the dependent variable (each panel).
+Each square represents a \emph{b} value or the slope of the predictor (x-axis) onto the dependent variable (each panel), with the exception of the bottom row which is the effect size of each regression analysis \(R^2\).
 Slopes included both the overall value of the predictor (\(b\), \(b_M\)) and the standard deviation of the predictor over time (\(b_{SD}\)).

### 2023-11-01 manuscript_scopus.Rmd
updated formatting

@@
 bibliography: references.bib
-# header-includes:
-csl               : "includes/nature.csl"
-# documentclass     : "apa7"
-output            : papaja::apa6_pdf
 appendix          :
   - "appendix.Rmd"
+
+header-includes:
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass     : "apa7"
+output            : papaja::apa6_pdf
 ---
@@
 
-Beyond the replication movement, the credibility movement has  
-mirrored calls for
-diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
+Beyond the replication movement, the credibility movement has mirrored calls for diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
 Rich, and Democratic) scientific research [@henrich2010; @newson2021;
@@
 
-***Education***. We collected degree information from the author table.
+#### Education
+
+We collected degree information from the author table.
 Information on this variable is in the appendix.
 
-***Types of Publications***. We took information from the publication
+#### Types of Publications
+
+We took information from the publication
 type variable for each author's publications to present information
@@
 
-***Publication Metrics***. For each author, we calculated the number of publications and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.
-
-***Institutions***. We report the number of institutions involved in big team science publications.
-
-### RQ4: Author Diversity Statistics \
-
-***Seniority***. Career length for each author was defined as the
+#### Publication Metrics
+
+For each author, we calculated the number of publications and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.
+
+#### Institutions
+
+We report the number of institutions involved in big team science publications.
+
+### RQ4: Author Diversity Statistics
+
+#### Seniority
+
+Career length for each author was defined as the
 year of the first publication minus the current year listed for each
@@
 Number of publications included the number of unique entries an author was included in the database.
-Career length and number of publications was used as a proxy for the "age" or "seniority" of a scholar to assess if only senior scholars were
-
-***Geopolitical Region***. Geopolitical region was created by binning country code identifiers into the 17 identified United Nation Regions.
+Career length and number of publications was used as a proxy for the "age" or "seniority" of a scholar.
+
+#### Geopolitical Region
+
+Geopolitical region was created by binning country code identifiers into the 17 identified United Nation subregions.
 
@@
 
-*Number of articles*. The total number of articles included in this
+### Number of articles
+
+The total number of articles included in this
 analysis was `r total_num` including `r health_num` Health Sciences
@@
 
-*Number of journals*. The number of distinct journals big team science
+### Number of journals
+
+The number of distinct journals big team science
 articles were published in was `r journals` with `r health_journal`
@@
 
-***Publication Metrics***. The average number of publications by authors on big team science papers
+### Publication Metrics
+
+The average number of publications by authors on big team science papers
 is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`). The
@@
 
-***Institutions***. The total number of unique affiliation across all papers was `r affs`.
+### Institutions
+
+The total number of unique affiliation across all papers was `r affs`.
 
@@
 
-***Seniority***. Figure \@ref(fig:fig-career) portrays the average career length for
+### Seniority
+
+Figure \@ref(fig:fig-career) portrays the average career length for
 authors involved in BTS publications across years. Career length was
@@
 
-***Geopolitical Regions***.
-
 ```{r geo-map}
@@
 ```
+
+### Geopolitical Regions
 
@@
 Our investigation expands into an exploration of the researchers who
-publish in big teams focusing on career length, publication metrics, and
+publish in big teams focusing on diversity in seniority of authors and
 geopolitical affiliation. The number of earlier career scholars is

### 2023-11-01 manuscript_scopus.tex
updated formatting

@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{csquotes}
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 \ifLuaTeX
@@
 According to the Oxford English dictionary, collaboration is two or more
-people working together to achieve a certain goal\textsuperscript{1}.
+people working together to achieve a certain goal (OED, 2016).
 Collaboration in scientific endeavors involves multiple researchers at
@@
 perspectives of collaborators. While collaboration is not new in
-science, the current interest of ``big team science'' is increasing\textsuperscript{2--4}. Big team science projects
+science, the current interest of ``big team science'' is increasing
+(Coles et al., 2022; Forscher et al., 2022; N. Stewart et al., 2017). Big team science projects
 and/or organizations utilize and run on large-scale collaboration to
@@
 research, and 2) expanding interest in reproducibility, replication, and
-generalizability\textsuperscript{5--7}. Technological
+generalizability (Maxwell et al., 2015; Nelson et al., 2018; Zwaan et al., 2018). Technological
 advances have provided easier ways to collaborate with people who are
@@
 materials, reliability, generalizability and more robust sample sizes
-(when necessary) in a study\textsuperscript{8--10}.
+(when necessary) in a study (Auspurg \& Brüderl, 2021; LeBel et al., 2018; Nosek \& Lakens, 2014a).
 
 The credibility movement was originally defined by a focus on large
-scale replications used in collaborative environments\textsuperscript{11}.
+scale replications used in collaborative environments (Vazire et al., 2022).
 Generally, the movement appears to have been driven by early career
 researchers (i.e., those who are within five years of their first
-appointment)\textsuperscript{12}; however, there are no large meta-scientific
+appointment) (Maizey \& Tzavella, 2019); however, there are no large meta-scientific
 investigations on this specific topic to date. Potentially, the lack of
@@
 fields, as it is only in recent years that publications like the Open
-Science Collaboration\textsuperscript{13}, Many Labs
-Collaborations\textsuperscript{14--20} or the first papers from the
-Psychological Science Accelerator\textsuperscript{21--27}. Generally, the researcher incentive for
+Science Collaboration (Open Science Collaboration, 2015), Many Labs
+Collaborations (Buttrick et al., 2020; Ebersole et al., 2016, 2020; Klein et al., 2018; Klein et al., 2022; Mathur et al., 2020; Skorb et al., 2020) or the first papers from the
+Psychological Science Accelerator (Bago et al., 2022; Buchanan et al., 2023; Dorison et al., 2022; B.
+C.
+Jones et al., 2021; Moshontz et al., 2018; Psychological Science Accelerator Self-Determination Theory Collaboration, 2022; Wang et al., 2021).
+Generally, the researcher incentive for
 replication and/or involvement in big-team projects was low for three reasons. First, journals often prioritize
 ``novel'' or new results which led to rejection of replication manuscripts
-and publication bias\textsuperscript{28--30}. Second,
+and publication bias (Franco et al., 2014; Hubbard \& Armstrong, 1997; Nosek et al., 2012). Second,
 the ``failure'' to replicate was often placed on the replication team as
 ``bad science'' rather than a careful consideration of publication biases
-and (potential) questionable research practices\textsuperscript{5,18}. Last, why should someone want to spend time and resources
-on an answer we already ``know''\textsuperscript{31,32}?
+and (potential) questionable research practices (Klein et al., 2022; Maxwell et al., 2015). Last, why should someone want to spend time and resources
+on an answer we already ``know'' (Isager et al., 2021, 2023)?
 
 However, the success and interest in the large-scale reproducibility
-projects\textsuperscript{13,33}, paired
+projects (Errington et al., 2021; Open Science Collaboration, 2015), paired
 with the meta-scientific publications focusing on researcher practices
-and incentive structures\textsuperscript{34,35} led to a
+and incentive structures (John et al., 2012; Silberzahn et al., 2018) led to a
 change in journal guidelines and incentives for researchers interested
-in participating in large-scale replication studies\textsuperscript{36--39}. In some fields, the
+in participating in large-scale replication studies (Grahe, 2014; Kidwell et al., 2016; Mayo-Wilson et al., 2021; Nosek et al., 2015). In some fields, the
 replication movement demonstrated that large-scale teams were a
@@
 for Registered Reports, papers accepted before the data has been
-collected\textsuperscript{40,41}, has allowed researchers to
+collected (Nosek \& Lakens, 2014b; S. Stewart et al., 2020), has allowed researchers to
 invest in projects that they know
 should be published when the project is complete. Further, the
-implementation of the Transparency and Openness Guidelines\textsuperscript{38}
-and the Contributor Role Taxonomy (CRediT) system\textsuperscript{42} have
+implementation of the Transparency and Openness Guidelines (Nosek et al., 2015)
+and the Contributor Role Taxonomy (CRediT) system (Allen et al., 2019) have
 pushed journals and researchers to promote more open, inclusive
@@
 
-Beyond the replication movement, the credibility movement has\\
-mirrored calls for
-diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
-Rich, and Democratic) scientific research\textsuperscript{43--45} by improving representation in research samples. Like the
-large-scale studies in Physics\textsuperscript{46,47} and
-Biology\textsuperscript{48}, the Social Sciences struggle to represent the
+Beyond the replication movement, the credibility movement has mirrored calls for diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
+Rich, and Democratic) scientific research (Henrich et al., 2010; Newson et al., 2021; Rad et al., 2018) by improving representation in research samples. Like the
+large-scale studies in Physics ({``A Philosophical Case for Big Physics,''} 2021; Castelnovo et al., 2018) and
+Biology (Collins et al., 2003), the Social Sciences struggle to represent the
 breadth of humanity across both researcher and population
 characteristics. Now, grassroots organizations, such as the
-Psychological Science Accelerator\textsuperscript{26}, ManyBabies
+Psychological Science Accelerator (Moshontz et al., 2018), ManyBabies
 (\url{https://manybabies.github.io/}), NutNet (\url{https://nutnet.org/}), and
@@
 Publications have examined the global understanding of morality, face
-processing, COVID-19 information signaling, and more\textsuperscript{21,23--25,27,49}. While these organizations and one-time groups
+processing, COVID-19 information signaling, and more (Bago et al., 2022; Dorison et al., 2022; B.
+C.
+Jones et al., 2021; Psychological Science Accelerator Self-Determination Theory Collaboration, 2022; Van Bavel et al., 2022; Wang et al., 2021).
+While these organizations and one-time groups
 for BTS studies have provided an incredible wealth of data for the
@@
 and benefits from, the BTS and credibility movement. Publications on BTS
-generally explore challenges, lessons learned, and the need for BTS\textsuperscript{2,3}.
+generally explore challenges, lessons learned, and the need for BTS
+(Coles et al., 2022; Forscher et al., 2022).
 
@@
 involved in BTS. While a few publications have noted that BTS appears to
-be early career researchers\textsuperscript{12}, no one has systematically
+be early career researchers (Maizey \& Tzavella, 2019), no one has systematically
 investigated this perception. Further, it is unclear if the focus of
@@
 from research on team science that uses any multi-university collaboration
-as a definition\textsuperscript{50} to focus on larger sized teams rather
+as a definition (B. F. Jones et al., 2008) to focus on larger sized teams rather
 than teams of any size. With at least ten institutions, the complexities
-of infrastructure, resources, tenure and promotion policies, ethics review, and more can occur\textsuperscript{3}.
+of infrastructure, resources, tenure and promotion policies, ethics review, and more can occur (Forscher et al., 2022).
 Therefore, we believe this choice selects publications that would be ``big'' teams and those potential obstacles.
@@
 
-\textbf{\emph{Education}}. We collected degree information from the author table.
+\hypertarget{education}{%
+\paragraph{Education}\label{education}}
+
+We collected degree information from the author table.
 Information on this variable is in the appendix.
 
-\textbf{\emph{Types of Publications}}. We took information from the publication
+\hypertarget{types-of-publications}{%
+\paragraph{Types of Publications}\label{types-of-publications}}
+
+We took information from the publication
 type variable for each author's publications to present information
@@
 
-\textbf{\emph{Publication Metrics}}.
-For each author, we calculated the number of publications and the h-index.
-The h-index represents the highest \emph{h} number of publications that have at least \emph{h} citations.
-
-\textbf{\emph{Institutions}}. We report the number of institutions involved in big team science publications.
+\hypertarget{publication-metrics}{%
+\paragraph{Publication Metrics}\label{publication-metrics}}
+
+For each author, we calculated the number of publications and the h-index. The h-index represents the highest \emph{h} number of publications that have at least \emph{h} citations.
+
+\hypertarget{institutions}{%
+\paragraph{Institutions}\label{institutions}}
+
+We report the number of institutions involved in big team science publications.
 
 \hypertarget{rq4-author-diversity-statistics}{%
-\subsubsection{RQ4: Author Diversity Statistics ~}\label{rq4-author-diversity-statistics}}
-
-\textbf{\emph{Seniority}}. Career length for each author was defined as the
+\subsubsection{RQ4: Author Diversity Statistics}\label{rq4-author-diversity-statistics}}
+
+\hypertarget{seniority}{%
+\paragraph{Seniority}\label{seniority}}
+
+Career length for each author was defined as the
 year of the first publication minus the current year listed for each
@@
 Number of publications included the number of unique entries an author was included in the database.
-Career length and number of publications was used as a proxy for the ``age'' or ``seniority'' of a scholar to assess if only senior scholars were
-
-\textbf{\emph{Geopolitical Region}}. Geopolitical region was created by binning country code identifiers into the 17 identified United Nation Regions.
+Career length and number of publications was used as a proxy for the ``age'' or ``seniority'' of a scholar.
+
+\hypertarget{geopolitical-region}{%
+\paragraph{Geopolitical Region}\label{geopolitical-region}}
+
+Geopolitical region was created by binning country code identifiers into the 17 identified United Nation subregions.
 
@@
 
-\emph{Number of articles}. The total number of articles included in this
+\hypertarget{number-of-articles}{%
+\subsubsection{Number of articles}\label{number-of-articles}}
+
+The total number of articles included in this
 analysis was 510334 including 445301 Health Sciences
@@
 
-\emph{Number of journals}. The number of distinct journals big team science
+\hypertarget{number-of-journals}{%
+\subsubsection{Number of journals}\label{number-of-journals}}
+
+The number of distinct journals big team science
 articles were published in was 14924 with 6559
@@
 
-\textbf{\emph{Publication Metrics}}. The average number of publications by authors on big team science papers
+\hypertarget{publication-metrics-1}{%
+\subsubsection{Publication Metrics}\label{publication-metrics-1}}
+
+The average number of publications by authors on big team science papers
 is \emph{M} = 38.37 (\emph{SD} = 102.54). The
@@
 
-\textbf{\emph{Institutions}}. The total number of unique affiliation across all papers was 463876.
+\hypertarget{institutions-1}{%
+\subsubsection{Institutions}\label{institutions-1}}
+
+The total number of unique affiliation across all papers was 463876.
 
@@
 
-\textbf{\emph{Seniority}}. Figure \ref{fig:fig-career} portrays the average career length for
+\hypertarget{seniority-1}{%
+\subsubsection{Seniority}\label{seniority-1}}
+
+Figure \ref{fig:fig-career} portrays the average career length for
 authors involved in BTS publications across years. Career length was
@@
 
-\textbf{\emph{Geopolitical Regions}}.
-
 \begin{figure}
@@
 \end{figure}
+
+\hypertarget{geopolitical-regions}{%
+\subsubsection{Geopolitical Regions}\label{geopolitical-regions}}
 
@@
 authors included on manuscripts, replicating previous investigations
-into this topic area\textsuperscript{51--53}.
+into this topic area (Hunter \& Leahey, 2008; Sinatra et al., 2015; Wuchty et al., 2007).
 
 Our investigation expands into an exploration of the researchers who
-publish in big teams focusing on career length, publication metrics, and
+publish in big teams focusing on diversity in seniority of authors and
 geopolitical affiliation. The number of earlier career scholars is
@@
 has shown that larger-team publications do receive more citations and
-appear to have higher impact\textsuperscript{54}.
+appear to have higher impact (Larivière et al., 2015).
 
@@
 are potentially driving forces behind our results, but, hopefully, the
-results also point to a decline in scientific gatekeeping\textsuperscript{55,56}.
+results also point to a decline in scientific gatekeeping (Lu, 2007; Siler et al., 2015).
 
@@
 positions, one potential way to distinguish their application would be a
-larger number of publications in their early career\textsuperscript{57,58}.
+larger number of publications in their early career (Caplow, 2017; Kyvik, 2003).
 
@@
 increasing over time, showing the results of globalization and the
-ability to connect across time zones and cultures\textsuperscript{59}. While our
+ability to connect across time zones and cultures (Xie, 2014). While our
 definition of big team science required at least ten different
@@
 with an increased interest in big team science publications in
-psychology\textsuperscript{2,3}, and the desire to diversify the
-populations represented in psychological research\textsuperscript{43,44}.
+psychology (Coles et al., 2022; Forscher et al., 2022), and the desire to diversify the
+populations represented in psychological research (Henrich et al., 2010; Newson et al., 2021).
 
@@
 if they are slowly decreasing. Diverse teams are more likely to have
-papers with stronger ``impact''\textsuperscript{50,60--62} with higher citation metrics for more diverse author lists.
-The introduction of contributorship models (e.g., CRediT\textsuperscript{42})
+papers with stronger ``impact'' (Freeman \& Huang, 2015; Hinnant et al., 2012; B. F. Jones et al., 2008; Yang et al., 2022) with higher citation metrics for more diverse author lists.
+The introduction of contributorship models (e.g., CRediT(Allen et al., 2019))
 will hopefully continue to push these effects down, as they highlight
@@
 study indicates that the majority of publications in big databases are
-in English\textsuperscript{63}. Certainly, publications in non-English
+in English (Albarillo, 2014). Certainly, publications in non-English
 languages would improve the statistics on diversity in scientific
 publishing - but the English language barrier likely exists regardless
-of inclusion in databases\textsuperscript{64,65}.
+of inclusion in databases (Meneghini \& Packer, 2007; Ramírez-Castañeda, 2020).
 
@@
 collaboration from interpersonal conflict, infrastructure, incentives,
-to international political situations\textsuperscript{3}. Directed studies
+to international political situations (Forscher et al., 2022). Directed studies
 into ways to navigate these situations would be beneficial for policy
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-oed2016}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{OED. Collaboration. vol. 3 (2016).}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-aphilos2021}{}}%
+A philosophical case for big physics. (2021). \emph{Nature Physics}, \emph{17}(6), 661--661. \url{https://doi.org/10.1038/s41567-021-01278-0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-albarillo2014}{}}%
+Albarillo, F.
+(2014).
+Language in social science databases: English versus non-english articles in JSTOR and scopus.
+\emph{Behavioral \& Social Sciences Librarian}, \emph{33}(2), 77--90.
+\url{https://doi.org/10.1080/01639269.2014.904693}
+
+\leavevmode\vadjust pre{\hypertarget{ref-allen2019}{}}%
+Allen, L., O'Connell, A., \& Kiermer, V.
+(2019).
+How can we ensure visibility and diversity in research contributions?
+How the Contributor Role Taxonomy (CRediT) is helping the shift from authorship to contributorship.
+\emph{Learned Publishing}, \emph{32}(1), 71--74.
+\url{https://doi.org/10.1002/leap.1210}
+
+\leavevmode\vadjust pre{\hypertarget{ref-auspurg2021}{}}%
+Auspurg, K., \& Brüderl, J.
+(2021).
+Has the Credibility of the Social Sciences Been Credibly Destroyed?
+Reanalyzing the {``}Many Analysts, One Data Set{''} Project.
+\emph{Socius: Sociological Research for a Dynamic World}, \emph{7}.
+\url{https://doi.org/10.1177/23780231211024421}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bago2022}{}}%
+Bago, B., Kovacs, M., Protzko, J., Nagy, T., Kekecs, Z., Palfi, B., Adamkovic, M., Adamus, S., Albalooshi, S., Albayrak-Aydemir, N., Alfian, I.
+N., Alper, S., Alvarez-Solas, S., Alves, S.
+G., Amaya, S., Andresen, P.
+K., Anjum, G., Ansari, D., Arriaga, P., \ldots{} Aczel, B.
+(2022).
+Situational factors shape moral judgements in the trolley dilemma in Eastern, Southern and Western countries in a culturally diverse sample.
+\emph{Nature Human Behaviour}, \emph{6}, 880--895.
+\url{https://doi.org/10.1038/s41562-022-01319-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-buchanan2023}{}}%
+Buchanan, E.
+M., Lewis, S.
+C., Paris, B., Forscher, P.
+S., Pavlacic, J.
+M., Beshears, J.
+E., Drexler, S.
+M., Gourdon-Kanhukamwe, A., Mallik, P.
+R., Silan, M.
+A.
+A., Miller, J.
+K., IJzerman, H., Moshontz, H., Beaudry, J.
+L., Suchow, J.
+W., Chartier, C.
+R., Coles, N.
+A., Sharifian, M., Todsen, A.
+L., \ldots{} McFall, J.
+P.
+(2023).
+The psychological science accelerator{'}s COVID-19 rapid-response dataset.
+\emph{Scientific Data}, \emph{10}(1), 87.
+\url{https://doi.org/10.1038/s41597-022-01811-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-buttrick2020}{}}%
+Buttrick, N.
+R., Aczel, B., Aeschbach, L.
+F., Bakos, B.
+E., Brühlmann, F., Claypool, H.
+M., Hüffmeier, J., Kovacs, M., Schuepfer, K., Szecsi, P., Szuts, A., Szöke, O., Thomae, M., Torka, A.-K., Walker, R.
+J., \& Wood, M.
+J.
+(2020).
+Many Labs 5: Registered Replication of Vohs and Schooler (2008), Experiment 1.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 429--438.
+\url{https://doi.org/10.1177/2515245920917931}
+
+\leavevmode\vadjust pre{\hypertarget{ref-caplow2017}{}}%
+Caplow, T. (2017). \emph{The academic marketplace} (2nd ed.). Routledge. \url{https://doi.org/10.4324/9781351305969}
+
+\leavevmode\vadjust pre{\hypertarget{ref-castelnovo2018}{}}%
+Castelnovo, P., Florio, M., Forte, S., Rossi, L., \& Sirtori, E.
+(2018).
+The economic impact of technological procurement for large-scale research infrastructures: Evidence from the Large Hadron Collider at CERN.
+\emph{Research Policy}, \emph{47}(9), 1853--1867.
+\url{https://doi.org/10.1016/j.respol.2018.06.018}
 
 \leavevmode\vadjust pre{\hypertarget{ref-coles2022}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{Coles, N.
+Coles, N.
 A., Hamlin, J.
@@
 L., Parker, T.
-H.
-\& Altschul, D.
-\href{https://doi.org/10.1038/d41586-022-00150-2}{Build up big-team science}.
-\emph{Nature} \textbf{601}, 505--507 (2022).}
+H., \& Altschul, D.
+(2022).
+Build up big-team science.
+\emph{Nature}, \emph{601}(7894), 505--507.
+\url{https://doi.org/10.1038/d41586-022-00150-2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-collins2003}{}}%
+Collins, F.
+S., Morgan, M., \& Patrinos, A.
+(2003).
+The human genome project: Lessons from large-scale biology.
+\emph{Science}, \emph{300}(5617), 286--290.
+\url{https://doi.org/10.1126/science.1084564}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dorison2022}{}}%
+Dorison, C.
+A., Lerner, J.
+S., Heller, B.
+H., Rothman, A.
+J., Kawachi, I.
+I., Wang, K., Rees, V.
+W., Gill, B.
+P., Gibbs, N., Ebersole, C.
+R., Vally, Z., Tajchman, Z., Zsido, A.
+N., Zrimsek, M., Chen, Z., Ziano, I., Gialitaki, Z., Ceary, C.
+D., Lin, Y., \ldots{} Coles, N.
+A.
+(2022).
+In {COVID}-19 {Health} {Messaging}, {Loss} {Framing} {Increases} {Anxiety} with {Little}-to-{No} {Concomitant} {Benefits}: {Experimental} {Evidence} from 84 {Countries}.
+\emph{Affective Science}, \emph{3}(3), 577--602.
+\url{https://doi.org/10.1007/s42761-022-00128-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ebersole2016}{}}%
+Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., Baranski, E., Bernstein, M.
+J., Bonfiglio, D.
+B.
+V., Boucher, L., Brown, E.
+R., Budiman, N.
+I., Cairo, A.
+H., Capaldi, C.
+A., Chartier, C.
+R., Chung, J.
+M., Cicero, D.
+C., Coleman, J.
+A., Conway, J.
+G., \ldots{} Nosek, B.
+A.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.
+\emph{Journal of Experimental Social Psychology}, \emph{67}, 68--82.
+\url{https://doi.org/10.1016/j.jesp.2015.10.012}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
+Ebersole, C.
+R., Mathur, M.
+B., Baranski, E., Bart-Plange, D.-J., Buttrick, N.
+R., Chartier, C.
+R., Corker, K.
+S., Corley, M., Hartshorne, J.
+K., IJzerman, H., Lazarević, L.
+B., Rabagliati, H., Ropovik, I., Aczel, B., Aeschbach, L.
+F., Andrighetto, L., Arnal, J.
+D., Arrow, H., Babincak, P., \ldots{} Nosek, B.
+A.
+(2020).
+Many Labs 5: Testing Pre-Data-Collection Peer Review as an Intervention to Increase Replicability.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 309--331.
+\url{https://doi.org/10.1177/2515245920958687}
+
+\leavevmode\vadjust pre{\hypertarget{ref-10.7554ux2feLife.71601}{}}%
+Errington, T.
+M., Mathur, M., Soderberg, C.
+K., Denis, A., Perfito, N., Iorns, E., \& Nosek, B.
+A.
+(2021).
+Investigating the replicability of preclinical cancer biology.
+\emph{eLife}, \emph{10}, e71601.
+\url{https://doi.org/10.7554/eLife.71601}
 
 \leavevmode\vadjust pre{\hypertarget{ref-forscher2022a}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{Forscher, P.
-S.
-\emph{et al.} \href{https://doi.org/10.1177/17456916221082970}{The Benefits, Barriers, and Risks of Big-Team Science}.
-\emph{Perspectives on Psychological Science} \textbf{18}, 607623 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stewart2017}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{Stewart, N., Chandler, J.
-\& Paolacci, G.
-\href{https://doi.org/10.1016/j.tics.2017.06.007}{Crowdsourcing samples in cognitive science}.
-\emph{Trends in Cognitive Sciences} \textbf{21}, 736--748 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-maxwell2015}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{Maxwell, S.
-E., Lau, M.
-Y.
-\& Howard, G.
-S.
-\href{https://doi.org/10.1037/a0039400}{Is psychology suffering from a replication crisis?: What does 'failure to replicate' really mean?} \emph{American Psychologist} \textbf{70}, 487--498 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{Nelson, L.
-D., Simmons, J.
-\& Simonsohn, U.
-\href{https://doi.org/10.1146/annurev-psych-122216-011836}{Psychology's renaissance}.
-\emph{Annual Review of Psychology} \textbf{69}, 511--534 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{Zwaan, R.
-A., Etz, A., Lucas, R.
-E.
-\& Donnellan, M.
-B.
-\href{https://doi.org/10.1017/S0140525X17001972}{Making replication mainstream}.
-\emph{Behavioral and Brain Sciences} \textbf{41}, e120 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-auspurg2021}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{Auspurg, K.
-\& Brüderl, J.
-\href{https://doi.org/10.1177/23780231211024421}{Has the Credibility of the Social Sciences Been Credibly Destroyed?
-Reanalyzing the {``}Many Analysts, One Data Set{''} Project}.
-\emph{Socius: Sociological Research for a Dynamic World} \textbf{7}, (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{Nosek, B. A. \& Lakens, D. A method to increase the credibility of published results. \emph{Social Psychology} \textbf{45}, 137141 (2014).}
+Forscher, P.
+S., Wagenmakers, E.-J., Coles, N.
+A., Silan, M.
+A., Dutra, N., Basnight-Brown, D., \& IJzerman, H.
+(2022).
+The Benefits, Barriers, and Risks of Big-Team Science.
+\emph{Perspectives on Psychological Science}, \emph{18}(3), 607623.
+\url{https://doi.org/10.1177/17456916221082970}
+
+\leavevmode\vadjust pre{\hypertarget{ref-franco2014}{}}%
+Franco, A., Malhotra, N., \& Simonovits, G.
+(2014).
+Publication bias in the social sciences: Unlocking the file drawer.
+\emph{Science}, \emph{345}(6203), 1502--1505.
+\url{https://doi.org/10.1126/science.1255484}
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2015}{}}%
+Freeman, R.
+B., \& Huang, W.
+(2015).
+Collaborating with People Like Me: Ethnic Coauthorship within the United States.
+\emph{Journal of Labor Economics}, \emph{33}(S1), S289--S318.
+\url{https://doi.org/10.1086/678973}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grahe2014}{}}%
+Grahe, J. E. (2014). Announcing open science badges and reaching for the sky. \emph{The Journal of Social Psychology}, \emph{154}(1), 1--3. \url{https://doi.org/10.1080/00224545.2014.853582}
+
+\leavevmode\vadjust pre{\hypertarget{ref-henrich2010}{}}%
+Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--83. \url{https://doi.org/10.1017/S0140525X0999152X}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hinnant2012}{}}%
+Hinnant, C.
+C., Stvilia, B., Wu, S., Worrall, A., Burnett, G., Burnett, K., Kazmer, M.
+M., \& Marty, P.
+F.
+(2012).
+Author-team diversity and the impact of scientific publications: Evidence from physics research at a national science lab.
+\emph{Library \& Information Science Research}, \emph{34}(4), 249--257.
+\url{https://doi.org/10.1016/j.lisr.2012.03.001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hubbard1997}{}}%
+Hubbard, R., \& Armstrong, J. S. (1997). Publication Bias against Null Results. \emph{Psychological Reports}, \emph{80}(1), 337--338. \url{https://doi.org/10.2466/pr0.1997.80.1.337}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hunter2008}{}}%
+Hunter, L., \& Leahey, E.
+(2008).
+Collaborative Research in Sociology: Trends and Contributing Factors.
+\emph{The American Sociologist}, \emph{39}(4), 290--306.
+\url{https://doi.org/10.1007/s12108-008-9042-1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-isager2021a}{}}%
+Isager, P.
+M., Van Aert, R.
+C.
+M., Bahník, Š., Brandt, M.
+J., DeSoto, K.
+A., Giner-Sorolla, R., Krueger, J.
+I., Perugini, M., Ropovik, I., Van 'T Veer, A.
+E., Vranka, M., \& Lakens, D.
+(2023).
+Deciding what to replicate: {A} decision model for replication study selection under resource and knowledge constraints.
+\emph{Psychological Methods}, \emph{28}(2), 438--451.
+\url{https://doi.org/10.1037/met0000438}
+
+\leavevmode\vadjust pre{\hypertarget{ref-isager2021}{}}%
+Isager, P. M., van 't Veer, A. E., \& Lakens, D. (2021). \emph{Replication value as a function of citation impact and sample size}. \url{https://doi.org/10.31222/osf.io/knjea}
+
+\leavevmode\vadjust pre{\hypertarget{ref-john2012}{}}%
+John, L.
+K., Loewenstein, G., \& Prelec, D.
+(2012).
+Measuring the Prevalence of Questionable Research Practices With Incentives for Truth Telling.
+\emph{Psychological Science}, \emph{23}(5), 524--532.
+\url{https://doi.org/10.1177/0956797611430953}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jones2021}{}}%
+Jones, B.
+C., DeBruine, L.
+M., Flake, J.
+K., Liuzza, M.
+T., Antfolk, J., Arinze, N.
+C., Ndukaihe, I.
+L.
+G., Bloxsom, N.
+G., Lewis, S.
+C., Foroni, F., Willis, M.
+L., Cubillas, C.
+P., Vadillo, M.
+A., Turiegano, E., Gilead, M., Simchon, A., Saribay, S.
+A., Owsley, N.
+C., Jang, C., \ldots{} Coles, N.
+A.
+(2021).
+To which world regions does the valence{\textendash}dominance model of social perception apply?
+\emph{Nature Human Behaviour}, \emph{5}(1), 159--169.
+\url{https://doi.org/10.1038/s41562-020-01007-2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jones2008}{}}%
+Jones, B.
+F., Wuchty, S., \& Uzzi, B.
+(2008).
+Multi-university research teams: Shifting impact, geography, and stratification in science.
+\emph{Science}, \emph{322}(5905), 1259--1262.
+\url{https://doi.org/10.1126/science.1158357}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kidwell2016}{}}%
+Kidwell, M.
+C., Lazarević, L.
+B., Baranski, E., Hardwicke, T.
+E., Piechowski, S., Falkenberg, L.-S., Kennett, C., Slowik, A., Sonnleitner, C., Hess-Holden, C., Errington, T.
+M., Fiedler, S., \& Nosek, B.
+A.
+(2016).
+Badges to Acknowledge Open Practices: A Simple, Low-Cost, Effective Method for Increasing Transparency.
+\emph{PLOS Biology}, \emph{14}(5), e1002456.
+\url{https://doi.org/10.1371/journal.pbio.1002456}
+
+\leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
+Klein, R.
+A., Cook, C.
+L., Ebersole, C.
+R., Vitiello, C., Nosek, B.
+A., Hilgard, J., Ahn, P.
+H., Brady, A.
+J., Chartier, C.
+R., Christopherson, C.
+D., Clay, S., Collisson, B., Crawford, J.
+T., Cromar, R., Gardiner, G., Gosnell, C.
+L., Grahe, J., Hall, C., Howard, I., \ldots{} Ratliff, K.
+A.
+(2022).
+Many Labs 4: Failure to Replicate Mortality Salience Effect With and Without Original Author Involvement.
+\emph{Collabra: Psychology}, \emph{8}(1), 35271.
+\url{https://doi.org/10.1525/collabra.35271}
+
+\leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
+Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams, R.
+B., Alper, S., Aveyard, M., Axt, J.
+R., Babalola, M.
+T., Bahník, Š., Batra, R., Berkics, M., Bernstein, M.
+J., Berry, D.
+R., Bialobrzeska, O., Binan, E.
+D., Bocian, K., Brandt, M.
+J., Busching, R., \ldots{} Nosek, B.
+A.
+(2018).
+Many Labs 2: Investigating Variation in Replicability Across Samples and Settings.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490.
+\url{https://doi.org/10.1177/2515245918810225}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kyvik2003}{}}%
+Kyvik, S. (2003). Changing trends in publishing behaviour among university faculty, 1980-2000. \emph{Scientometrics}, \emph{58}(1), 35--48. \url{https://doi.org/10.1023/A:1025475423482}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lariviuxe8re2015}{}}%
+Larivière, V., Gingras, Y., Sugimoto, C.
+R., \& Tsou, A.
+(2015).
+Team size matters: Collaboration and scientific impact since 1900.
+\emph{Journal of the Association for Information Science and Technology}, \emph{66}(7), 1323--1332.
+\url{https://doi.org/10.1002/asi.23266}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lebel2018}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{LeBel, E.
+LeBel, E.
 P., McCarthy, R.
 J., Earp, B.
-D., Elson, M.
-\& Vanpaemel, W.
-\href{https://doi.org/10.1177/2515245918787489}{A Unified Framework to Quantify the Credibility of Scientific Findings}.
-\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}, 389--402 (2018).}
+D., Elson, M., \& Vanpaemel, W.
+(2018).
+A Unified Framework to Quantify the Credibility of Scientific Findings.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 389--402.
+\url{https://doi.org/10.1177/2515245918787489}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lu2007}{}}%
+Lu, Y.
+(2007).
+The human in human information acquisition: Understanding gatekeeping and proposing new directions in scholarship.
+\emph{Library \& Information Science Research}, \emph{29}(1), 103--123.
+\url{https://doi.org/10.1016/j.lisr.2006.10.007}
+
+\leavevmode\vadjust pre{\hypertarget{ref-maizey2019}{}}%
+Maizey, L., \& Tzavella, L.
+(2019).
+Barriers and solutions for early career researchers in tackling the reproducibility crisis in cognitive neuroscience.
+\emph{Cortex}, \emph{113}, 357--359.
+\url{https://doi.org/10.1016/j.cortex.2018.12.015}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
+Mathur, M.
+B., Bart-Plange, D.-J., Aczel, B., Bernstein, M.
+H., Ciunci, A.
+M., Ebersole, C.
+R., Falcão, F., Ashbaugh, K., Hilliard, R.
+A., Jern, A., Kellier, D.
+J., Kessinger, G., Kolb, V.
+S., Kovacs, M., Lage, C.
+A., Langford, E.
+V., Lins, S., Manfredi, D., Meyet, V., \ldots{} Frank, M.
+C.
+(2020).
+Many Labs 5: Registered Multisite Replication of the Tempting-Fate Effects in Risen and Gilovich (2008).
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 394--404.
+\url{https://doi.org/10.1177/2515245918785165}
+
+\leavevmode\vadjust pre{\hypertarget{ref-maxwell2015}{}}%
+Maxwell, S.
+E., Lau, M.
+Y., \& Howard, G.
+S.
+(2015).
+Is psychology suffering from a replication crisis?: What does 'failure to replicate' really mean?
+\emph{American Psychologist}, \emph{70}(6), 487--498.
+\url{https://doi.org/10.1037/a0039400}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mayo-wilson2021}{}}%
+Mayo-Wilson, E., Grant, S., Supplee, L., Kianersi, S., Amin, A., DeHaven, A., \& Mellor, D.
+(2021).
+Evaluating implementation of the transparency and openness promotion~(TOP) guidelines:~The TRUST process for rating journal policies, procedures, and practices.
+\emph{Research Integrity and Peer Review}, \emph{6}(1), 9.
+\url{https://doi.org/10.1186/s41073-021-00112-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meneghini2007}{}}%
+Meneghini, R., \& Packer, A. L. (2007). Is there science beyond english? \emph{EMBO Reports}, \emph{8}(2), 112--116. \url{https://doi.org/10.1038/sj.embor.7400906}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moshontz2018}{}}%
+Moshontz, H., Campbell, L., Ebersole, C.
+R., IJzerman, H., Urry, H.
+L., Forscher, P.
+S., Grahe, J.
+E., McCarthy, R.
+J., Musser, E.
+D., Antfolk, J., Castille, C.
+M., Evans, T.
+R., Fiedler, S., Flake, J.
+K., Forero, D.
+A., Janssen, S.
+M.
+J., Keene, J.
+R., Protzko, J., Aczel, B., \ldots{} Chartier, C.
+R.
+(2018).
+The Psychological Science Accelerator: Advancing Psychology Through a Distributed Collaborative Network.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 501--515.
+\url{https://doi.org/10.1177/2515245918797607}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
+Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
+
+\leavevmode\vadjust pre{\hypertarget{ref-newson2021}{}}%
+Newson, M., Buhrmester, M., Xygalatas, D., \& Whitehouse, H. (2021). Go WILD, not WEIRD. \emph{Journal for the Cognitive Science of Religion}, \emph{6}(1-2). \url{https://doi.org/10.1558/jcsr.38413}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2015}{}}%
+Nosek, B.
+A., Alter, G., Banks, G.
+C., Borsboom, D., Bowman, S.
+D., Breckler, S.
+J., Buck, S., Chambers, C.
+D., Chin, G., Christensen, G., Contestabile, M., Dafoe, A., Eich, E., Freese, J., Glennerster, R., Goroff, D., Green, D.
+P., Hesse, B., Humphreys, M., \ldots{} Yarkoni, T.
+(2015).
+Promoting an open research culture.
+\emph{Science}, \emph{348}(6242), 1422--1425.
+\url{https://doi.org/10.1126/science.aab2374}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
+Nosek, B. A., \& Lakens, D. (2014a). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137141.
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
+Nosek, B.
+A., \& Lakens, D.
+(2014b).
+Registered Reports: A Method to Increase the Credibility of Published Results.
+\emph{Social Psychology}, \emph{45}(3), 137--141.
+\url{https://doi.org/10.1027/1864-9335/a000192}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2012}{}}%
+Nosek, B.
+A., Spies, J.
+R., \& Motyl, M.
+(2012).
+Scientific Utopia: II.
+Restructuring Incentives and Practices to Promote Truth Over Publishability.
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 615--631.
+\url{https://doi.org/10.1177/1745691612459058}
+
+\leavevmode\vadjust pre{\hypertarget{ref-oed2016}{}}%
+OED. (2016). \emph{Collaboration} (Vol. 3). Oxford University.
+
+\leavevmode\vadjust pre{\hypertarget{ref-opensciencecollaboration2015}{}}%
+Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716--aac4716. \url{https://doi.org/10.1126/science.aac4716}
+
+\leavevmode\vadjust pre{\hypertarget{ref-psychologicalscienceacceleratorself-determinationtheorycollaboration2022}{}}%
+Psychological Science Accelerator Self-Determination Theory Collaboration.
+(2022).
+A global experiment on motivating social distancing during the COVID-19 pandemic.
+\emph{Proceedings of the National Academy of Sciences}, \emph{119}(22), e2111091119.
+\url{https://doi.org/10.1073/pnas.2111091119}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rad2018}{}}%
+Rad, M.
+S., Martingano, A.
+J., \& Ginges, J.
+(2018).
+Toward a psychology of homo sapiens: Making psychological science more representative of the human population.
+\emph{Proceedings of the National Academy of Sciences}, \emph{115}(45), 11401--11405.
+\url{https://doi.org/10.1073/pnas.1721165115}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ramuxedrez-castauxf1eda2020}{}}%
+Ramírez-Castañeda, V.
+(2020).
+Disadvantages in preparing and publishing scientific papers caused by the dominance of the English language in science: The case of Colombian researchers in biological sciences.
+\emph{PLOS ONE}, \emph{15}(9), e0238372.
+\url{https://doi.org/10.1371/journal.pone.0238372}
+
+\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
+Silberzahn, R., Uhlmann, E.
+L., Martin, D.
+P., Anselmi, P., Aust, F., Awtrey, E., Bahník, Š., Bai, F., Bannard, C., Bonnier, E., \& others.
+(2018).
+Many analysts, one data set: Making transparent how variations in analytic choices affect results.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337356.
+
+\leavevmode\vadjust pre{\hypertarget{ref-siler2015}{}}%
+Siler, K., Lee, K., \& Bero, L.
+(2015).
+Measuring the effectiveness of scientific gatekeeping.
+\emph{Proceedings of the National Academy of Sciences}, \emph{112}(2), 360--365.
+\url{https://doi.org/10.1073/pnas.1418218112}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sinatra2015}{}}%
+Sinatra, R., Deville, P., Szell, M., Wang, D., \& Barabási, A.-L. (2015). A century of physics. \emph{Nature Physics}, \emph{11}(10), 791--796. \url{https://doi.org/10.1038/nphys3494}
+
+\leavevmode\vadjust pre{\hypertarget{ref-skorb2020}{}}%
+Skorb, L., Aczel, B., Bakos, B.
+E., Feinberg, L., Hałasa, E., Kauff, M., Kovacs, M., Krasuska, K., Kuchno, K., Manfredi, D., Montealegre, A., Pękala, E., Pieńkosz, D., Ravid, J., Rentzsch, K., Szaszi, B., Schulz-Hardt, S., Sioma, B., Szecsi, P., \ldots{} Hartshorne, J.
+K.
+(2020).
+Many Labs 5: Replication of van Dijk, van Kleef, Steinel, and van Beest (2008).
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 418--428.
+\url{https://doi.org/10.1177/2515245920927643}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stewart2017}{}}%
+Stewart, N., Chandler, J., \& Paolacci, G.
+(2017).
+Crowdsourcing samples in cognitive science.
+\emph{Trends in Cognitive Sciences}, \emph{21}(10), 736--748.
+\url{https://doi.org/10.1016/j.tics.2017.06.007}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stewart2020}{}}%
+Stewart, S., Rinke, E.
+M., McGarrigle, R., Lynott, D., Lunny, C., Lautarescu, A., Galizzi, M.
+M., Farran, E.
+K., \& Crook, Z.
+(2020).
+\emph{Pre-registration and registered reports: A primer from UKRN}.
+\url{https://doi.org/10.31219/osf.io/8v2n7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vanbavel2022}{}}%
+Van Bavel, J.
+J., Cichocka, A., Capraro, V., Sjåstad, H., Nezlek, J.
+B., Pavlović, T., Alfano, M., Gelfand, M.
+J., Azevedo, F., Birtel, M.
+D., Cislak, A., Lockwood, P.
+L., Ross, R.
+M., Abts, K., Agadullina, E., Aruta, J.
+J.
+B., Besharati, S.
+N., Bor, A., Choma, B.
+L., \ldots{} Boggio, P.
+S.
+(2022).
+National identity predicts public health support during a global pandemic.
+\emph{Nature Communications}, \emph{13}(1), 517.
+\url{https://doi.org/10.1038/s41467-021-27668-9}
 
 \leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{Vazire, S., Schiavone, S.
-R.
-\& Bottesini, J.
+Vazire, S., Schiavone, S.
+R., \& Bottesini, J.
 G.
-\href{https://doi.org/10.1177/09637214211067779}{Credibility Beyond Replicability: Improving the Four Validities in Psychological Science}.
-\emph{Current Directions in Psychological Science} \textbf{31}, 162--168 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-maizey2019}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Maizey, L.
-\& Tzavella, L.
-\href{https://doi.org/10.1016/j.cortex.2018.12.015}{Barriers and solutions for early career researchers in tackling the reproducibility crisis in cognitive neuroscience}.
-\emph{Cortex} \textbf{113}, 357--359 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-opensciencecollaboration2015}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Open Science Collaboration.
-\href{https://doi.org/10.1126/science.aac4716}{Estimating the reproducibility of psychological science}.
-\emph{Science} \textbf{349}, aac4716--aac4716 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buttrick2020}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Buttrick, N.
-R.
-\emph{et al.} \href{https://doi.org/10.1177/2515245920917931}{Many Labs 5: Registered Replication of Vohs and Schooler (2008), Experiment 1}.
-\emph{Advances in Methods and Practices in Psychological Science} \textbf{3}, 429--438 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ebersole2016}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{Ebersole, C.
-R.
-\emph{et al.} \href{https://doi.org/10.1016/j.jesp.2015.10.012}{Many Labs 3: Evaluating participant pool quality across the academic semester via replication}.
-\emph{Journal of Experimental Social Psychology} \textbf{67}, 68--82 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Ebersole, C.
-R.
-\emph{et al.} \href{https://doi.org/10.1177/2515245920958687}{Many Labs 5: Testing Pre-Data-Collection Peer Review as an Intervention to Increase Replicability}.
-\emph{Advances in Methods and Practices in Psychological Science} \textbf{3}, 309--331 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{Klein, R.
-A.
-\emph{et al.} \href{https://doi.org/10.1177/2515245918810225}{Many Labs 2: Investigating Variation in Replicability Across Samples and Settings}.
-\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}, 443--490 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{Klein, R.
-A.
-\emph{et al.} \href{https://doi.org/10.1525/collabra.35271}{Many Labs 4: Failure to Replicate Mortality Salience Effect With and Without Original Author Involvement}.
-\emph{Collabra: Psychology} \textbf{8}, 35271 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Mathur, M.
-B.
-\emph{et al.} \href{https://doi.org/10.1177/2515245918785165}{Many Labs 5: Registered Multisite Replication of the Tempting-Fate Effects in Risen and Gilovich (2008)}.
-\emph{Advances in Methods and Practices in Psychological Science} \textbf{3}, 394--404 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-skorb2020}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Skorb, L.
-\emph{et al.} \href{https://doi.org/10.1177/2515245920927643}{Many Labs 5: Replication of van Dijk, van Kleef, Steinel, and van Beest (2008)}.
-\emph{Advances in Methods and Practices in Psychological Science} \textbf{3}, 418--428 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bago2022}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Bago, B.
-\emph{et al.} \href{https://doi.org/10.1038/s41562-022-01319-5}{Situational factors shape moral judgements in the trolley dilemma in Eastern, Southern and Western countries in a culturally diverse sample}.
-\emph{Nature Human Behaviour} \textbf{6}, 880--895 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buchanan2023}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{Buchanan, E.
-M.
-\emph{et al.} \href{https://doi.org/10.1038/s41597-022-01811-7}{The psychological science accelerator{'}s COVID-19 rapid-response dataset}.
-\emph{Scientific Data} \textbf{10}, 87 (2023).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dorison2022}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Dorison, C.
-A.
-\emph{et al.} \href{https://doi.org/10.1007/s42761-022-00128-3}{In {COVID}-19 {Health} {Messaging}, {Loss} {Framing} {Increases} {Anxiety} with {Little}-to-{No} {Concomitant} {Benefits}: {Experimental} {Evidence} from 84 {Countries}}.
-\emph{Affective Science} \textbf{3}, 577--602 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jones2021}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{Jones, B.
-C.
-\emph{et al.} \href{https://doi.org/10.1038/s41562-020-01007-2}{To which world regions does the valence{\textendash}dominance model of social perception apply?} \emph{Nature Human Behaviour} \textbf{5}, 159--169 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-psychologicalscienceacceleratorself-determinationtheorycollaboration2022}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Psychological Science Accelerator Self-Determination Theory Collaboration.
-\href{https://doi.org/10.1073/pnas.2111091119}{A global experiment on motivating social distancing during the COVID-19 pandemic}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{119}, e2111091119 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-moshontz2018}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{Moshontz, H.
-\emph{et al.} \href{https://doi.org/10.1177/2515245918797607}{The Psychological Science Accelerator: Advancing Psychology Through a Distributed Collaborative Network}.
-\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}, 501--515 (2018).}
+(2022).
+Credibility Beyond Replicability: Improving the Four Validities in Psychological Science.
+\emph{Current Directions in Psychological Science}, \emph{31}(2), 162--168.
+\url{https://doi.org/10.1177/09637214211067779}
 
 \leavevmode\vadjust pre{\hypertarget{ref-wang2021}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Wang, K.
-\emph{et al.} \href{https://doi.org/10.1038/s41562-021-01173-x}{A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic}.
-\emph{Nature Human Behaviour} \textbf{5}, 1089--1110 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-franco2014}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{Franco, A., Malhotra, N.
-\& Simonovits, G.
-\href{https://doi.org/10.1126/science.1255484}{Publication bias in the social sciences: Unlocking the file drawer}.
-\emph{Science} \textbf{345}, 1502--1505 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hubbard1997}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{Hubbard, R. \& Armstrong, J. S. \href{https://doi.org/10.2466/pr0.1997.80.1.337}{Publication Bias against Null Results}. \emph{Psychological Reports} \textbf{80}, 337--338 (1997).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2012}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Nosek, B.
-A., Spies, J.
-R.
-\& Motyl, M.
-\href{https://doi.org/10.1177/1745691612459058}{Scientific Utopia: II.
-Restructuring Incentives and Practices to Promote Truth Over Publishability}.
-\emph{Perspectives on Psychological Science} \textbf{7}, 615--631 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-isager2021}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Isager, P.
-M., van 't Veer, A.
-E.
-\& Lakens, D.
-\emph{Replication value as a function of citation impact and sample size}.
-\url{https://osf.io/knjea} (2021) doi:\href{https://doi.org/10.31222/osf.io/knjea}{10.31222/osf.io/knjea}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-isager2021a}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{Isager, P.
-M.
-\emph{et al.} \href{https://doi.org/10.1037/met0000438}{Deciding what to replicate: {A} decision model for replication study selection under resource and knowledge constraints.} \emph{Psychological Methods} \textbf{28}, 438--451 (2023).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-10.7554ux2feLife.71601}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{Errington, T. M. \emph{et al.} \href{https://doi.org/10.7554/eLife.71601}{Investigating the replicability of preclinical cancer biology}. \emph{eLife} \textbf{10}, e71601 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{Silberzahn, R.
-\emph{et al.} Many analysts, one data set: Making transparent how variations in analytic choices affect results.
-\emph{Advances in Methods and Practices in Psychological Science} \textbf{1}, 337356 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-john2012}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{John, L.
-K., Loewenstein, G.
-\& Prelec, D.
-\href{https://doi.org/10.1177/0956797611430953}{Measuring the Prevalence of Questionable Research Practices With Incentives for Truth Telling}.
-\emph{Psychological Science} \textbf{23}, 524--532 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grahe2014}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{Grahe, J.
-E.
-\href{https://doi.org/10.1080/00224545.2014.853582}{Announcing open science badges and reaching for the sky}.
-\emph{The Journal of Social Psychology} \textbf{154}, 1--3 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kidwell2016}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{Kidwell, M.
-C.
-\emph{et al.} \href{https://doi.org/10.1371/journal.pbio.1002456}{Badges to Acknowledge Open Practices: A Simple, Low-Cost, Effective Method for Increasing Transparency}.
-\emph{PLOS Biology} \textbf{14}, e1002456 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2015}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{Nosek, B. A. \emph{et al.} \href{https://doi.org/10.1126/science.aab2374}{Promoting an open research culture}. \emph{Science} \textbf{348}, 1422--1425 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mayo-wilson2021}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Mayo-Wilson, E.
-\emph{et al.} \href{https://doi.org/10.1186/s41073-021-00112-8}{Evaluating implementation of the transparency and openness promotion~(TOP) guidelines:~The TRUST process for rating journal policies, procedures, and practices}.
-\emph{Research Integrity and Peer Review} \textbf{6}, 9 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{Nosek, B.
-A.
-\& Lakens, D.
-\href{https://doi.org/10.1027/1864-9335/a000192}{Registered Reports: A Method to Increase the Credibility of Published Results}.
-\emph{Social Psychology} \textbf{45}, 137--141 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stewart2020}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{Stewart, S.
-\emph{et al.} \emph{Pre-registration and registered reports: A primer from UKRN}.
-\url{https://osf.io/8v2n7} (2020) doi:\href{https://doi.org/10.31219/osf.io/8v2n7}{10.31219/osf.io/8v2n7}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-allen2019}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{Allen, L., O'Connell, A.
-\& Kiermer, V.
-\href{https://doi.org/10.1002/leap.1210}{How can we ensure visibility and diversity in research contributions?
-How the Contributor Role Taxonomy (CRediT) is helping the shift from authorship to contributorship}.
-\emph{Learned Publishing} \textbf{32}, 71--74 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-henrich2010}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Henrich, J., Heine, S.
-J.
-\& Norenzayan, A.
-\href{https://doi.org/10.1017/S0140525X0999152X}{The weirdest people in the world?} \emph{Behavioral and Brain Sciences} \textbf{33}, 61--83 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-newson2021}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Newson, M., Buhrmester, M., Xygalatas, D.
-\& Whitehouse, H.
-\href{https://doi.org/10.1558/jcsr.38413}{Go WILD, not WEIRD}.
-\emph{Journal for the Cognitive Science of Religion} \textbf{6}, (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rad2018}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Rad, M.
-S., Martingano, A.
-J.
-\& Ginges, J.
-\href{https://doi.org/10.1073/pnas.1721165115}{Toward a psychology of homo sapiens: Making psychological science more representative of the human population}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 11401--11405 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-aphilos2021}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{\href{https://doi.org/10.1038/s41567-021-01278-0}{A philosophical case for big physics}. \emph{Nature Physics} \textbf{17}, 661--661 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-castelnovo2018}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Castelnovo, P., Florio, M., Forte, S., Rossi, L.
-\& Sirtori, E.
-\href{https://doi.org/10.1016/j.respol.2018.06.018}{The economic impact of technological procurement for large-scale research infrastructures: Evidence from the Large Hadron Collider at CERN}.
-\emph{Research Policy} \textbf{47}, 1853--1867 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-collins2003}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{Collins, F.
-S., Morgan, M.
-\& Patrinos, A.
-\href{https://doi.org/10.1126/science.1084564}{The human genome project: Lessons from large-scale biology}.
-\emph{Science} \textbf{300}, 286--290 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vanbavel2022}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{Van Bavel, J.
-J.
-\emph{et al.} \href{https://doi.org/10.1038/s41467-021-27668-9}{National identity predicts public health support during a global pandemic}.
-\emph{Nature Communications} \textbf{13}, 517 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jones2008}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{Jones, B.
-F., Wuchty, S.
-\& Uzzi, B.
-\href{https://doi.org/10.1126/science.1158357}{Multi-university research teams: Shifting impact, geography, and stratification in science}.
-\emph{Science} \textbf{322}, 1259--1262 (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sinatra2015}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{Sinatra, R., Deville, P., Szell, M., Wang, D. \& Barabási, A.-L. \href{https://doi.org/10.1038/nphys3494}{A century of physics}. \emph{Nature Physics} \textbf{11}, 791--796 (2015).}
+Wang, K., Goldenberg, A., Dorison, C.
+A., Miller, J.
+K., Uusberg, A., Lerner, J.
+S., Gross, J.
+J., Agesin, B.
+B., Bernardo, M., Campos, O., Eudave, L., Grzech, K., Ozery, D.
+H., Jackson, E.
+A., Garcia, E.
+O.
+L., Drexler, S.
+M., Jurković, A.
+P., Rana, K., Wilson, J.
+P., \ldots{} Moshontz, H.
+(2021).
+A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic.
+\emph{Nature Human Behaviour}, \emph{5}(8), 1089--1110.
+\url{https://doi.org/10.1038/s41562-021-01173-x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-wuchty2007}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{Wuchty, S., Jones, B.
-F.
-\& Uzzi, B.
-\href{https://doi.org/10.1126/science.1136099}{The increasing dominance of teams in production of knowledge}.
-\emph{Science} \textbf{316}, 1036--1039 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hunter2008}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Hunter, L.
-\& Leahey, E.
-\href{https://doi.org/10.1007/s12108-008-9042-1}{Collaborative Research in Sociology: Trends and Contributing Factors}.
-\emph{The American Sociologist} \textbf{39}, 290--306 (2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lariviuxe8re2015}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{Larivière, V., Gingras, Y., Sugimoto, C.
-R.
-\& Tsou, A.
-\href{https://doi.org/10.1002/asi.23266}{Team size matters: Collaboration and scientific impact since 1900}.
-\emph{Journal of the Association for Information Science and Technology} \textbf{66}, 1323--1332 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lu2007}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{Lu, Y.
-\href{https://doi.org/10.1016/j.lisr.2006.10.007}{The human in human information acquisition: Understanding gatekeeping and proposing new directions in scholarship}.
-\emph{Library \& Information Science Research} \textbf{29}, 103--123 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-siler2015}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{Siler, K., Lee, K.
-\& Bero, L.
-\href{https://doi.org/10.1073/pnas.1418218112}{Measuring the effectiveness of scientific gatekeeping}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{112}, 360--365 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-caplow2017}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{Caplow, T. \emph{The academic marketplace}. (Routledge, 2017). doi:\href{https://doi.org/10.4324/9781351305969}{10.4324/9781351305969}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kyvik2003}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Kyvik, S.
-\href{https://doi.org/10.1023/A:1025475423482}{Changing trends in publishing behaviour among university faculty, 1980-2000}.
-\emph{Scientometrics} \textbf{58}, 35--48 (2003).}
+Wuchty, S., Jones, B. F., \& Uzzi, B. (2007). The increasing dominance of teams in production of knowledge. \emph{Science}, \emph{316}(5827), 1036--1039. \url{https://doi.org/10.1126/science.1136099}
 
 \leavevmode\vadjust pre{\hypertarget{ref-xie2014}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{Xie, Y. \href{https://doi.org/10.1126/science.1252743}{{``}Undemocracy{''}: Inequalities in science}. \emph{Science} \textbf{344}, 809--810 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2015}{}}%
-\CSLLeftMargin{60. }%
-\CSLRightInline{Freeman, R.
-B.
-\& Huang, W.
-\href{https://doi.org/10.1086/678973}{Collaborating with People Like Me: Ethnic Coauthorship within the United States}.
-\emph{Journal of Labor Economics} \textbf{33}, S289--S318 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hinnant2012}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{Hinnant, C.
-C.
-\emph{et al.} \href{https://doi.org/10.1016/j.lisr.2012.03.001}{Author-team diversity and the impact of scientific publications: Evidence from physics research at a national science lab}.
-\emph{Library \& Information Science Research} \textbf{34}, 249--257 (2012).}
+Xie, Y. (2014). {``}Undemocracy{''}: Inequalities in science. \emph{Science}, \emph{344}(6186), 809--810. \url{https://doi.org/10.1126/science.1252743}
 
 \leavevmode\vadjust pre{\hypertarget{ref-yang2022}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{Yang, Y., Tian, T.
+Yang, Y., Tian, T.
 Y., Woodruff, T.
 K., Jones, B.
-F.
-\& Uzzi, B.
-\href{https://doi.org/10.1073/pnas.2200841119}{Gender-diverse teams produce more novel and higher-impact scientific ideas}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{119}, e2200841119 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-albarillo2014}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Albarillo, F.
-\href{https://doi.org/10.1080/01639269.2014.904693}{Language in social science databases: English versus non-english articles in JSTOR and scopus}.
-\emph{Behavioral \& Social Sciences Librarian} \textbf{33}, 77--90 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-meneghini2007}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Meneghini, R. \& Packer, A. L. \href{https://doi.org/10.1038/sj.embor.7400906}{Is there science beyond english?} \emph{EMBO reports} \textbf{8}, 112--116 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ramuxedrez-castauxf1eda2020}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{Ramírez-Castañeda, V.
-\href{https://doi.org/10.1371/journal.pone.0238372}{Disadvantages in preparing and publishing scientific papers caused by the dominance of the English language in science: The case of Colombian researchers in biological sciences}.
-\emph{PLOS ONE} \textbf{15}, e0238372 (2020).}
+F., \& Uzzi, B.
+(2022).
+Gender-diverse teams produce more novel and higher-impact scientific ideas.
+\emph{Proceedings of the National Academy of Sciences}, \emph{119}(36), e2200841119.
+\url{https://doi.org/10.1073/pnas.2200841119}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
+Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
 
@@
 
-\textbf{Number of Journals}.
+\hypertarget{number-of-journals-1}{%
+\subsubsection{Number of Journals}\label{number-of-journals-1}}
 
@@
 
-\textbf{Keywords}.
+\hypertarget{keywords}{%
+\subsubsection{Keywords}\label{keywords}}
+
 Figure \ref{fig:fig-keywords} indicates the most common keywords present for the BTS publications by subject area.
@@
 
-\textbf{Institution}.
+\hypertarget{institution}{%
+\subsubsection{Institution}\label{institution}}
 
@@
 
-\textbf{\emph{Education}}.
+\hypertarget{education-1}{%
+\subsubsection{Education}\label{education-1}}
+
 As noted in our pre-registration, we would only present this variable if we could obtain at least 50\% information on the authors who publish in big team science papers.
@@
 
-\textbf{\emph{Types of Publications}}.
+\hypertarget{types-of-publications-1}{%
+\subsubsection{Types of Publications}\label{types-of-publications-1}}
 

### 2023-11-01 manuscript_scopus.Rmd
so many edits for submission

@@
 First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
+
+  Preprint: https://osf.io/hqta4/
 abstract: |
@@
 linenumbers       : yes
-mask              : no
+mask              : yes
 draft             : no
@@
 This manuscript was preregistered with the same conceptual ideas using
-Google Scholar and ORC-ID databases (<https://osf.io/f2dtr>) but then
+Google Scholar and ORC-ID databases (<https://osf.io/f2dtr/?view_only=66e5608437994f288d03a7c8163c0c8c>) but then
 was updated with access to the Scopus database for a broader picture of
-BTS projects (<https://osf.io/fheun>). All materials and code can be
-found on our OSF page: <https://osf.io/cgx6u/> or corresponding GitHub
-archive: <https://github.com/doomlab/big_team_who>.
+BTS projects (<https://osf.io/fheun/?view_only=f563879af9e942f7bc49bac937fd3048>). All materials and code can be
+found on our OSF page: <https://osf.io/cgx6u/?view_only=7ea2adf9ea7c4995af0d60dde795db6d> or corresponding GitHub
+archive: ANONYMIZED.
 

### 2023-11-01 manuscript_scopus.tex
so many edits for submission

@@
 \documentclass[
-  man,floatsintext]{apa7}
+  man,mask,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
   pdftitle={Who does big team science?},
-  pdfauthor={Erin M. Buchanan1 \& Savannah C. Lewis2},
   pdflang={en-EN},
@@
 First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
+
+Preprint: \url{https://osf.io/hqta4/}
 
@@
 This manuscript was preregistered with the same conceptual ideas using
-Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr}) but then
+Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr/?view_only=66e5608437994f288d03a7c8163c0c8c}) but then
 was updated with access to the Scopus database for a broader picture of
-BTS projects (\url{https://osf.io/fheun}). All materials and code can be
-found on our OSF page: \url{https://osf.io/cgx6u/} or corresponding GitHub
-archive: \url{https://github.com/doomlab/big_team_who}.
+BTS projects (\url{https://osf.io/fheun/?view_only=f563879af9e942f7bc49bac937fd3048}). All materials and code can be
+found on our OSF page: \url{https://osf.io/cgx6u/?view_only=7ea2adf9ea7c4995af0d60dde795db6d} or corresponding GitHub
+archive: ANONYMIZED.
 

### 2023-12-06 manuscript_scopus.Rmd
fully anon

@@
 This manuscript was preregistered with the same conceptual ideas using
-Google Scholar and ORC-ID databases (<https://osf.io/f2dtr/?view_only=66e5608437994f288d03a7c8163c0c8c>) but then
+Google Scholar and ORC-ID databases (MASKED FOR REVIEW^[Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal]) but then
 was updated with access to the Scopus database for a broader picture of
-BTS projects (<https://osf.io/fheun/?view_only=f563879af9e942f7bc49bac937fd3048>). All materials and code can be
-found on our OSF page: <https://osf.io/cgx6u/?view_only=7ea2adf9ea7c4995af0d60dde795db6d> or corresponding GitHub
-archive: ANONYMIZED.
+BTS projects (MASKED FOR REVIEW). All materials and code can be
+found on our OSF page: MASKED FOR REVIEW or corresponding GitHub
+archive: MASKED FOR REVIEW.
 

### 2023-12-06 manuscript_scopus.tex
fully anon

@@
 This manuscript was preregistered with the same conceptual ideas using
-Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr/?view_only=66e5608437994f288d03a7c8163c0c8c}) but then
+Google Scholar and ORC-ID databases (MASKED FOR REVIEW\footnote{Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal}) but then
 was updated with access to the Scopus database for a broader picture of
-BTS projects (\url{https://osf.io/fheun/?view_only=f563879af9e942f7bc49bac937fd3048}). All materials and code can be
-found on our OSF page: \url{https://osf.io/cgx6u/?view_only=7ea2adf9ea7c4995af0d60dde795db6d} or corresponding GitHub
-archive: ANONYMIZED.
+BTS projects (MASKED FOR REVIEW). All materials and code can be
+found on our OSF page: MASKED FOR REVIEW or corresponding GitHub
+archive: MASKED FOR REVIEW.
 

### 2024-01-16 manuscript_scopus.Rmd
updating
changes to resubmit

@@
 
-  Significance statement: This work is the first to examine big team science authorship (i.e., 10+ authors) across millions of published works.
-Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing numbers of publications that increasingly represent earlier career and varied scholars.
-The number of geopolitical entities for researcher affiliation is increasing over time, showing the results of globalization and the ability to connect across time zones and cultures.
-While publications are generally diversifying, we did not yet find equality in the representation for first or corresponding authors.
-First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
-
   Preprint: https://osf.io/hqta4/
@@
 However, the increase in preprints, BTS articles, and non-WEIRD authors across time demonstrate the efforts of the science community to diversify its researchers.
+
+    Significance statement: This work is the first to examine big team science authorship (i.e., 10+ authors) across millions of published works.
+Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing numbers of publications that increasingly represent earlier career and varied scholars.
+The number of geopolitical entities for researcher affiliation is increasing over time, showing the results of globalization and the ability to connect across time zones and cultures.
+While publications are generally diversifying, we did not yet find equality in the representation for first or corresponding authors.
+First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
+
+  # General Disclosures
+
+  Conflicts of interest: Both authors declare no conflicts of interest.
+
+  Funding: No funding was obtained for this project.
+
+  Artificial intelligence: No AI resources were used for this manuscript.
+
+  Ethics: No ethics review was necessary for this project.
+
+  Computational reproducibility: All materials and code can be found on our OSF page: MASKED FOR REVIEW or corresponding GitHub archive: MASKED FOR REVIEW.
+Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review.
+
+  Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (MASKED FOR REVIEW^[Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal, this work has been uploaded a deidentified zip file]) but then was updated with access to the Scopus database for a broader picture of BTS projects (MASKED FOR REVIEW).
+
+  Materials: MASKED FOR REVIEW (see uploaded zip file).
+
+  Data: MASKED FOR REVIEW (see uploaded zip file).
+
+  Analysis scripts: MASKED FOR REVIEW (see uploaded zip file).
 
@@
 
-According to the Oxford English dictionary, collaboration is two or more
-people working together to achieve a certain goal [@oed2016].
 Collaboration in scientific endeavors involves multiple researchers at
@@
 perspectives of collaborators. While collaboration is not new in
-science, the current interest of "big team science" is increasing
-[@coles2022; @forscher2022a; @stewart2017]. Big team science projects
-and/or organizations utilize and run on large-scale collaboration to
-ensure that diverse populations and ideas are brought into research
+science, the interest in "big team science" is increasing
+[@coles2022; @forscher2022a; @stewart2017]. Big team science (BTS) projects
+and/or organizations utilize and run large-scale collaborations to
+ensure that diverse populations and ideas manifest in research
 projects, which in turn allows for more reliability and generalizability
-in the results and method of the study.
-
-BTS appears to be expanding as a result of two sources: 1) increasing
+in the results and methods of the study.
+
+BTS appears to be expanding because of two sources: 1) increasing
 globalization and technology that allows for real-time interdisciplinary
 research, and 2) expanding interest in reproducibility, replication, and
-generalizability [@maxwell2015; @nelson2018; @zwaan2018]. Technological
+generalizability [i.e., the credibility movement, 
+@maxwell2015; @nelson2018; @zwaan2018; @vazire2022]. Technological
 advances have provided easier ways to collaborate with people who are
@@
 and education levels should help to drive science in the path of better
-materials, reliability, generalizability and more robust sample sizes
+materials, reliability, generalizability, and more robust sample sizes
 (when necessary) in a study [@auspurg2021; @nosek2014method;
@@
 
-The credibility movement was originally defined by a focus on large
-scale replications used in collaborative environments [@vazire2022].
-Generally, the movement appears to have been driven by early career
-researchers (i.e., those who are within five years of their first
-appointment) [@maizey2019]; however, there are no large meta-scientific
-investigations on this specific topic to date. Potentially, the lack of
-investigation is tied to the newness of the large-scale research in many
-fields, as it is only in recent years that publications like the Open
+Generally, the credibility movement appears to have been driven by early career
+researchers [i.e., those who are within five years of their first
+appointment, @maizey2019]; however, there are no large meta-scientific
+investigations on this specific topic to date.
+The newness of large-scale research in many fields could be the culprit for the lack of investigation into this area.
+For example, psychology has had an increase in BTS publications like the Open
 Science Collaboration [@opensciencecollaboration2015], Many Labs
@@
 
-Beyond the replication movement, the credibility movement has mirrored calls for diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
+Beyond replication concerns, the credibility movement has mirrored calls for diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
 Rich, and Democratic) scientific research [@henrich2010; @newson2021;
@@
 Therefore, the goal of this manuscript is to examine both the *publications* and *people* involved in BTS projects.
-We present descriptive information about the publication sources and types of articles that we classified as BTS projects to demonstrate what areas of research show large-scale research.
-Next, we examine the individuals involved in those projects for descriptive and predictive purposes.
-To describe the people involved in BTS projects, we used education, types of publications (i.e., articles, preprints, books, etc.) from BTS individuals, and publication metrics.
-
-For predictive statistics, we explored the change in diversity of authors over time. We see an increasing interest and number of publications in BTS but we do not yet
-know if this uptick in large-scale projects has diversified the *people*
-involved in BTS. While a few publications have noted that BTS appears to
-be early career researchers [@maizey2019], no one has systematically
-investigated this perception. Further, it is unclear if the focus of
-de-WEIRDing science has only focused on the representation of the
+We present descriptive information about the publication sources and types of articles to demonstrate large-scale research.
+Next, we examine the individuals involved in BTS for descriptive and predictive purposes.
+To describe the people involved in BTS projects, we planned to use education, types of publications from BTS individuals, and publication metrics.
+For predictive statistics, we explored the change in diversity of authors over time.
+It is unclear if the focus of de-WEIRDing science has only focused on the representation of the
 research participants or if it has also improved the representation of
-researchers outside of North America and Europe. Last, who runs these
-BTS projects? Do we see an increase in diversity for the authors who
-generally receive the most credit for these projects (i.e., first
-several author(s) and last author)? As hiring and promoting practices
-often place a heavy weight on publications and especially "influential"
-publications, it becomes necessary to critically examine the
-representation present in authorship in BTS projects.
+researchers outside of North America and Europe.
+Last, we examined for a change in diversity within first author(s) and the last author across time.
+As hiring and promoting practices often place a heavy weight on publications and especially “influential” publications, it becomes necessary to critically examine the representation present in authorship in BTS projects.
 
@@
 -   Research Question 4: How has the diversity of those involved in big team science changed over time?
-
-This manuscript was preregistered with the same conceptual ideas using
-Google Scholar and ORC-ID databases (MASKED FOR REVIEW^[Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal]) but then
-was updated with access to the Scopus database for a broader picture of
-BTS projects (MASKED FOR REVIEW). All materials and code can be
-found on our OSF page: MASKED FOR REVIEW or corresponding GitHub
-archive: MASKED FOR REVIEW.
 
@@
 
-### Number of articles
+### Number of Articles
 
@@
 
-### Number of journals
+### Number of Journals
 
@@
 
+\newpage
+
 # Discussion
 
-In this investigation, we explored the publication rates, areas, and
-researchers involved in big team science publications. Over a
-half-million articles were published in nearly 15,000 journals since
-1970 that qualified as big team science articles (at least ten authors
-and ten different affiliations). The areas of publication were aligned
-to cancer and genetics research in medicine and oncology for Health and
-Life Sciences, physics and chemistry for the Physical Sciences, and
-psychology for the Social Sciences All areas of research show an
-explosion in growth in the number of publications and the number of
-authors included on manuscripts, replicating previous investigations
-into this topic area [@sinatra2015; @wuchty2007; @hunter2008].
-
-Our investigation expands into an exploration of the researchers who
-publish in big teams focusing on diversity in seniority of authors and
-geopolitical affiliation. The number of earlier career scholars is
-increasing in publications across the years, indicating that big teams
-may be more accessible to different types of individuals, not just
-older, more established researchers. This result is especially
-interesting given the publish-or-perish model still present in most
-institutions, as it may seem that large-scale projects could be a risky
-choice for non-permanent researchers. In the authors' experience, big
-team projects are often quite slow to publication, incentives may be low
-for non corresponding authors if institutions do not value papers
-without lead authorship, and there is no guarantee for publication even
-with a large group. However, with a large team the distribution of work
-could imply less effort on individual non-leading members, and research
-has shown that larger-team publications do receive more citations and
-appear to have higher impact [@larivière2015].
-
-The results for the number of publications by big team researchers
-mimics the findings from career length, with a smaller effect size. In
-general, it appears that there is a decrease in the average number of
-publications a researcher has when publishing on a big team science
-paper over time. This result is likely attributable to the number of
-early career scholars joining projects, but also may support increased
-accessibility for individuals to be involved in this type of research.
-Globalization, the internet, and the focus on interdisciplinary research
-are potentially driving forces behind our results, but, hopefully, the
-results also point to a decline in scientific gatekeeping [@lu2007;
-@siler2015].
+In this investigation, we explored the publication rates, areas, and researchers involved in BTS publications.
+Over a half-million articles were published in nearly 15,000 journals since 1970 that qualified as BTS articles.
+The areas of publication were aligned to cancer and genetics research in medicine and oncology for Health and Life Sciences, physics and chemistry for the Physical Sciences, and psychology for the Social Sciences.
+All areas of research show growth in the number of publications and authors included on manuscripts, replicating previous investigations [@sinatra2015; @wuchty2007; @hunter2008].
+
+Our investigation expands previous research by additionally focusing on diversity in seniority of authors and geopolitical affiliation.
+The number of earlier career scholars increased across years, indicating that big teams may be accessible to different types of individuals, not just older, established researchers.
+This result is especially interesting given the publish-or-perish model still present in most institutions, as it may seem that large-scale projects could be a risky choice for non-permanent researchers.
+BTS projects are often slow to publish, there is no guarantee for publication, and incentives are often lower for non-corresponding authors.
+However, with a large team, the distribution of work could imply less effort on individual non-leading members, and research has shown that larger-team publications do receive more citations and appear to have higher impact  [@larivière2015].
+
+In general, it appears that there is a decrease in the average number of publications a researcher has when publishing in a BTS paper over time, mirroring career length results.
+This result is likely attributable to the number of early career scholars joining projects, but also may support increased accessibility for individuals to be involved.
+Globalization, the internet, and the focus on interdisciplinary research are potentially driving forces behind our results, but, hopefully, the results also point to a decline in scientific gatekeeping [@lu2007; @siler2015].
 
@@
 ability to connect across time zones and cultures [@xie2014]. While our
-definition of big team science required at least ten different
+definition of BTS required at least ten different
 institutional affiliations, we did not filter papers by geopolitical
@@
 
-While publications on the whole are diversifying, we did not yet find
-equality in the representation for first/corresponding author spots
-versus all other authors. In general, first authors appear to be less
-diverse, representing more European and North American authors, while
-other authors include more Asian and African authors. These effect sizes
-were often small, but the inequality still persists across years, even
-if they are slowly decreasing. Diverse teams are more likely to have
-papers with stronger "impact" [@freeman2015; @hinnant2012; @jones2008;
+While publications overall are diversifying, we found differences in the representation for first/corresponding authors versus all other authors.
+In general, first authors appear to be less diverse, representing European and North American authors, while other authors include more Asian and African authors.
+These effect sizes were often small, but the inequality persists across years.
+Diverse teams are more likely to have papers with stronger “impact” [@freeman2015; @hinnant2012; @jones2008;
 @yang2022] with higher citation metrics for more diverse author lists.
-The introduction of contributorship models (e.g., CRediT[@allen2019])
+The introduction of contributorship models [e.g., CRediT, @allen2019]
 will hopefully continue to push these effects down, as they highlight
@@
 
-The limitations for this research are tied to the availability and
-curation of the Scopus dataset. While the number of articles analyzed
-for this investigation was large, the criteria for inclusion requires
-the correct entry of author affiliations, the correct author linkages
-for career length and publication rates, and the correctly marked
-geopolitical entity. We had planned to analyze educational levels to
-determine if the number of student coauthors (i.e., non-terminal degree)
-had increased over time; however, this data was mostly blank within the
-Scopus archive. Scopus is a carefully curated dataset, but these
-limitations must be kept in mind when interpreting the results.
-Publication language diversity was not investigated, and a previous
-study indicates that the majority of publications in big databases are
-in English [@albarillo2014]. Certainly, publications in non-English
+The limitations for this research are tied to the curation of the Scopus dataset: the correct author affiliations, the correct author publication information, and the correctly marked geopolitical entity.
+We had planned to analyze educational levels change over time; however, this data was mostly blank within the Scopus archive.
+Scopus is a carefully curated and large dataset, but these limitations must be kept in mind when interpreting the results.
+Publication language diversity was not investigated, and a previous study indicates that most publications in big databases are in English [@albarillo2014].
+Certainly, publications in non-English
 languages would improve the statistics on diversity in scientific
@@
 
-Big teams have the ability to provide high-impact, important research
-within scientific publishing, and this report suggests a promising trend
-of increasing numbers of publications that include earlier career and
-more diverse scholars. These partnerships introduce new challenges to
-collaboration from interpersonal conflict, infrastructure, incentives,
-to international political situations [@forscher2022a]. Directed studies
-into ways to navigate these situations would be beneficial for policy
-makers at institutions, as well as lead teams who organize and complete
-these projects. The implications for retention and promotion processes
-across a broad span of regions should be explored to improve diversity
-with the understanding of the differential impact of incentives for
-participating in big team studies.
+Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing publications that include earlier career and more diverse scholars.
+These partnerships introduce new challenges to collaboration from interpersonal conflict, infrastructure, incentives, to international political situations [@forscher2022a].
+The implications for retention and promotion processes across a broad span of regions should be explored to improve diversity with the understanding of the differential impact of incentives for participating in big team studies.
 
@@
 \setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+
 ```

### 2024-01-16 manuscript_scopus.tex
changes to resubmit

@@
 
-Significance statement: This work is the first to examine big team science authorship (i.e., 10+ authors) across millions of published works.
-Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing numbers of publications that increasingly represent earlier career and varied scholars.
-The number of geopolitical entities for researcher affiliation is increasing over time, showing the results of globalization and the ability to connect across time zones and cultures.
-While publications are generally diversifying, we did not yet find equality in the representation for first or corresponding authors.
-First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
-
 Preprint: \url{https://osf.io/hqta4/}
@@
 However, the increase in preprints, BTS articles, and non-WEIRD authors across time demonstrate the efforts of the science community to diversify its researchers.
+
+Significance statement: This work is the first to examine big team science authorship (i.e., 10+ authors) across millions of published works.
+Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing numbers of publications that increasingly represent earlier career and varied scholars.
+The number of geopolitical entities for researcher affiliation is increasing over time, showing the results of globalization and the ability to connect across time zones and cultures.
+While publications are generally diversifying, we did not yet find equality in the representation for first or corresponding authors.
+First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
+
+\hypertarget{general-disclosures}{%
+\section{General Disclosures}\label{general-disclosures}}
+
+Conflicts of interest: Both authors declare no conflicts of interest.
+
+Funding: No funding was obtained for this project.
+
+Artificial intelligence: No AI resources were used for this manuscript.
+
+Ethics: No ethics review was necessary for this project.
+
+Computational reproducibility: All materials and code can be found on our OSF page: MASKED FOR REVIEW or corresponding GitHub archive: MASKED FOR REVIEW.
+Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review.
+
+Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (MASKED FOR REVIEW\footnote{Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal, this work has been uploaded a deidentified zip file}) but then was updated with access to the Scopus database for a broader picture of BTS projects (MASKED FOR REVIEW).
+
+Materials: MASKED FOR REVIEW (see uploaded zip file).
+
+Data: MASKED FOR REVIEW (see uploaded zip file).
+
+Analysis scripts: MASKED FOR REVIEW (see uploaded zip file).
 }
@@
 
-According to the Oxford English dictionary, collaboration is two or more
-people working together to achieve a certain goal (OED, 2016).
 Collaboration in scientific endeavors involves multiple researchers at
@@
 perspectives of collaborators. While collaboration is not new in
-science, the current interest of ``big team science'' is increasing
-(Coles et al., 2022; Forscher et al., 2022; N. Stewart et al., 2017). Big team science projects
-and/or organizations utilize and run on large-scale collaboration to
-ensure that diverse populations and ideas are brought into research
+science, the interest in ``big team science'' is increasing
+(Coles et al., 2022; Forscher et al., 2022; N. Stewart et al., 2017). Big team science (BTS) projects
+and/or organizations utilize and run large-scale collaborations to
+ensure that diverse populations and ideas manifest in research
 projects, which in turn allows for more reliability and generalizability
-in the results and method of the study.
-
-BTS appears to be expanding as a result of two sources: 1) increasing
+in the results and methods of the study.
+
+BTS appears to be expanding because of two sources: 1) increasing
 globalization and technology that allows for real-time interdisciplinary
 research, and 2) expanding interest in reproducibility, replication, and
-generalizability (Maxwell et al., 2015; Nelson et al., 2018; Zwaan et al., 2018). Technological
+generalizability (i.e., the credibility movement, Maxwell et al., 2015; Nelson et al., 2018; Vazire et al., 2022; Zwaan et al., 2018). Technological
 advances have provided easier ways to collaborate with people who are
@@
 and education levels should help to drive science in the path of better
-materials, reliability, generalizability and more robust sample sizes
+materials, reliability, generalizability, and more robust sample sizes
 (when necessary) in a study (Auspurg \& Brüderl, 2021; LeBel et al., 2018; Nosek \& Lakens, 2014a).
 
-The credibility movement was originally defined by a focus on large
-scale replications used in collaborative environments (Vazire et al., 2022).
-Generally, the movement appears to have been driven by early career
+Generally, the credibility movement appears to have been driven by early career
 researchers (i.e., those who are within five years of their first
-appointment) (Maizey \& Tzavella, 2019); however, there are no large meta-scientific
-investigations on this specific topic to date. Potentially, the lack of
-investigation is tied to the newness of the large-scale research in many
-fields, as it is only in recent years that publications like the Open
+appointment, Maizey \& Tzavella, 2019); however, there are no large meta-scientific
+investigations on this specific topic to date.
+The newness of large-scale research in many fields could be the culprit for the lack of investigation into this area.
+For example, psychology has had an increase in BTS publications like the Open
 Science Collaboration (Open Science Collaboration, 2015), Many Labs
@@
 
-Beyond the replication movement, the credibility movement has mirrored calls for diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
+Beyond replication concerns, the credibility movement has mirrored calls for diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
 Rich, and Democratic) scientific research (Henrich et al., 2010; Newson et al., 2021; Rad et al., 2018) by improving representation in research samples. Like the
@@
 Therefore, the goal of this manuscript is to examine both the \emph{publications} and \emph{people} involved in BTS projects.
-We present descriptive information about the publication sources and types of articles that we classified as BTS projects to demonstrate what areas of research show large-scale research.
-Next, we examine the individuals involved in those projects for descriptive and predictive purposes.
-To describe the people involved in BTS projects, we used education, types of publications (i.e., articles, preprints, books, etc.) from BTS individuals, and publication metrics.
-
-For predictive statistics, we explored the change in diversity of authors over time. We see an increasing interest and number of publications in BTS but we do not yet
-know if this uptick in large-scale projects has diversified the \emph{people}
-involved in BTS. While a few publications have noted that BTS appears to
-be early career researchers (Maizey \& Tzavella, 2019), no one has systematically
-investigated this perception. Further, it is unclear if the focus of
-de-WEIRDing science has only focused on the representation of the
+We present descriptive information about the publication sources and types of articles to demonstrate large-scale research.
+Next, we examine the individuals involved in BTS for descriptive and predictive purposes.
+To describe the people involved in BTS projects, we planned to use education, types of publications from BTS individuals, and publication metrics.
+For predictive statistics, we explored the change in diversity of authors over time.
+It is unclear if the focus of de-WEIRDing science has only focused on the representation of the
 research participants or if it has also improved the representation of
-researchers outside of North America and Europe. Last, who runs these
-BTS projects? Do we see an increase in diversity for the authors who
-generally receive the most credit for these projects (i.e., first
-several author(s) and last author)? As hiring and promoting practices
-often place a heavy weight on publications and especially ``influential''
-publications, it becomes necessary to critically examine the
-representation present in authorship in BTS projects.
+researchers outside of North America and Europe.
+Last, we examined for a change in diversity within first author(s) and the last author across time.
+As hiring and promoting practices often place a heavy weight on publications and especially ``influential'' publications, it becomes necessary to critically examine the representation present in authorship in BTS projects.
 
@@
 
-This manuscript was preregistered with the same conceptual ideas using
-Google Scholar and ORC-ID databases (MASKED FOR REVIEW\footnote{Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal}) but then
-was updated with access to the Scopus database for a broader picture of
-BTS projects (MASKED FOR REVIEW). All materials and code can be
-found on our OSF page: MASKED FOR REVIEW or corresponding GitHub
-archive: MASKED FOR REVIEW.
-
 \hypertarget{method}{%
@@
 \hypertarget{number-of-articles}{%
-\subsubsection{Number of articles}\label{number-of-articles}}
+\subsubsection{Number of Articles}\label{number-of-articles}}
 
@@
 \hypertarget{number-of-journals}{%
-\subsubsection{Number of journals}\label{number-of-journals}}
+\subsubsection{Number of Journals}\label{number-of-journals}}
 
@@
 
+\newpage
+
 \hypertarget{discussion}{%
@@
 
-In this investigation, we explored the publication rates, areas, and
-researchers involved in big team science publications. Over a
-half-million articles were published in nearly 15,000 journals since
-1970 that qualified as big team science articles (at least ten authors
-and ten different affiliations). The areas of publication were aligned
-to cancer and genetics research in medicine and oncology for Health and
-Life Sciences, physics and chemistry for the Physical Sciences, and
-psychology for the Social Sciences All areas of research show an
-explosion in growth in the number of publications and the number of
-authors included on manuscripts, replicating previous investigations
-into this topic area (Hunter \& Leahey, 2008; Sinatra et al., 2015; Wuchty et al., 2007).
-
-Our investigation expands into an exploration of the researchers who
-publish in big teams focusing on diversity in seniority of authors and
-geopolitical affiliation. The number of earlier career scholars is
-increasing in publications across the years, indicating that big teams
-may be more accessible to different types of individuals, not just
-older, more established researchers. This result is especially
-interesting given the publish-or-perish model still present in most
-institutions, as it may seem that large-scale projects could be a risky
-choice for non-permanent researchers. In the authors' experience, big
-team projects are often quite slow to publication, incentives may be low
-for non corresponding authors if institutions do not value papers
-without lead authorship, and there is no guarantee for publication even
-with a large group. However, with a large team the distribution of work
-could imply less effort on individual non-leading members, and research
-has shown that larger-team publications do receive more citations and
-appear to have higher impact (Larivière et al., 2015).
-
-The results for the number of publications by big team researchers
-mimics the findings from career length, with a smaller effect size. In
-general, it appears that there is a decrease in the average number of
-publications a researcher has when publishing on a big team science
-paper over time. This result is likely attributable to the number of
-early career scholars joining projects, but also may support increased
-accessibility for individuals to be involved in this type of research.
-Globalization, the internet, and the focus on interdisciplinary research
-are potentially driving forces behind our results, but, hopefully, the
-results also point to a decline in scientific gatekeeping (Lu, 2007; Siler et al., 2015).
+In this investigation, we explored the publication rates, areas, and researchers involved in BTS publications.
+Over a half-million articles were published in nearly 15,000 journals since 1970 that qualified as BTS articles.
+The areas of publication were aligned to cancer and genetics research in medicine and oncology for Health and Life Sciences, physics and chemistry for the Physical Sciences, and psychology for the Social Sciences.
+All areas of research show growth in the number of publications and authors included on manuscripts, replicating previous investigations (Hunter \& Leahey, 2008; Sinatra et al., 2015; Wuchty et al., 2007).
+
+Our investigation expands previous research by additionally focusing on diversity in seniority of authors and geopolitical affiliation.
+The number of earlier career scholars increased across years, indicating that big teams may be accessible to different types of individuals, not just older, established researchers.
+This result is especially interesting given the publish-or-perish model still present in most institutions, as it may seem that large-scale projects could be a risky choice for non-permanent researchers.
+BTS projects are often slow to publish, there is no guarantee for publication, and incentives are often lower for non-corresponding authors.
+However, with a large team, the distribution of work could imply less effort on individual non-leading members, and research has shown that larger-team publications do receive more citations and appear to have higher impact (Larivière et al., 2015).
+
+In general, it appears that there is a decrease in the average number of publications a researcher has when publishing in a BTS paper over time, mirroring career length results.
+This result is likely attributable to the number of early career scholars joining projects, but also may support increased accessibility for individuals to be involved.
+Globalization, the internet, and the focus on interdisciplinary research are potentially driving forces behind our results, but, hopefully, the results also point to a decline in scientific gatekeeping (Lu, 2007; Siler et al., 2015).
 
@@
 ability to connect across time zones and cultures (Xie, 2014). While our
-definition of big team science required at least ten different
+definition of BTS required at least ten different
 institutional affiliations, we did not filter papers by geopolitical
@@
 
-While publications on the whole are diversifying, we did not yet find
-equality in the representation for first/corresponding author spots
-versus all other authors. In general, first authors appear to be less
-diverse, representing more European and North American authors, while
-other authors include more Asian and African authors. These effect sizes
-were often small, but the inequality still persists across years, even
-if they are slowly decreasing. Diverse teams are more likely to have
-papers with stronger ``impact'' (Freeman \& Huang, 2015; Hinnant et al., 2012; B. F. Jones et al., 2008; Yang et al., 2022) with higher citation metrics for more diverse author lists.
-The introduction of contributorship models (e.g., CRediT(Allen et al., 2019))
+While publications overall are diversifying, we found differences in the representation for first/corresponding authors versus all other authors.
+In general, first authors appear to be less diverse, representing European and North American authors, while other authors include more Asian and African authors.
+These effect sizes were often small, but the inequality persists across years.
+Diverse teams are more likely to have papers with stronger ``impact'' (Freeman \& Huang, 2015; Hinnant et al., 2012; B.
+F.
+Jones et al., 2008; Yang et al., 2022) with higher citation metrics for more diverse author lists.
+The introduction of contributorship models (e.g., CRediT, Allen et al., 2019)
 will hopefully continue to push these effects down, as they highlight
@@
 
-The limitations for this research are tied to the availability and
-curation of the Scopus dataset. While the number of articles analyzed
-for this investigation was large, the criteria for inclusion requires
-the correct entry of author affiliations, the correct author linkages
-for career length and publication rates, and the correctly marked
-geopolitical entity. We had planned to analyze educational levels to
-determine if the number of student coauthors (i.e., non-terminal degree)
-had increased over time; however, this data was mostly blank within the
-Scopus archive. Scopus is a carefully curated dataset, but these
-limitations must be kept in mind when interpreting the results.
-Publication language diversity was not investigated, and a previous
-study indicates that the majority of publications in big databases are
-in English (Albarillo, 2014). Certainly, publications in non-English
+The limitations for this research are tied to the curation of the Scopus dataset: the correct author affiliations, the correct author publication information, and the correctly marked geopolitical entity.
+We had planned to analyze educational levels change over time; however, this data was mostly blank within the Scopus archive.
+Scopus is a carefully curated and large dataset, but these limitations must be kept in mind when interpreting the results.
+Publication language diversity was not investigated, and a previous study indicates that most publications in big databases are in English (Albarillo, 2014).
+Certainly, publications in non-English
 languages would improve the statistics on diversity in scientific
@@
 
-Big teams have the ability to provide high-impact, important research
-within scientific publishing, and this report suggests a promising trend
-of increasing numbers of publications that include earlier career and
-more diverse scholars. These partnerships introduce new challenges to
-collaboration from interpersonal conflict, infrastructure, incentives,
-to international political situations (Forscher et al., 2022). Directed studies
-into ways to navigate these situations would be beneficial for policy
-makers at institutions, as well as lead teams who organize and complete
-these projects. The implications for retention and promotion processes
-across a broad span of regions should be explored to improve diversity
-with the understanding of the differential impact of incentives for
-participating in big team studies.
+Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing publications that include earlier career and more diverse scholars.
+These partnerships introduce new challenges to collaboration from interpersonal conflict, infrastructure, incentives, to international political situations (Forscher et al., 2022).
+The implications for retention and promotion processes across a broad span of regions should be explored to improve diversity with the understanding of the differential impact of incentives for participating in big team studies.
 
@@
 \setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-oed2016}{}}%
-OED. (2016). \emph{Collaboration} (Vol. 3). Oxford University.
-
 \leavevmode\vadjust pre{\hypertarget{ref-opensciencecollaboration2015}{}}%
@@
 
+\newpage
+
 \begin{table}[tbp]

### 2024-02-07 manuscript_scopus_unmasked.Rmd
unmasked paper

--- 2024-01-16 manuscript_scopus.Rmd
@@
 
-  Computational reproducibility: All materials and code can be found on our OSF page: MASKED FOR REVIEW or corresponding GitHub archive: MASKED FOR REVIEW.
+  Computational reproducibility: All materials and code can be found on our OSF page: https://osf.io/cgx6u/ or corresponding GitHub archive: https://github.com/doomlab/big_team_who.
 Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review.
 
-  Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (MASKED FOR REVIEW^[Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal, this work has been uploaded a deidentified zip file]) but then was updated with access to the Scopus database for a broader picture of BTS projects (MASKED FOR REVIEW).
-
-  Materials: MASKED FOR REVIEW (see uploaded zip file).
-
-  Data: MASKED FOR REVIEW (see uploaded zip file).
-
-  Analysis scripts: MASKED FOR REVIEW (see uploaded zip file).
+  Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (https://osf.io/f2dtr) but then was updated with access to the Scopus database for a broader picture of BTS projects (https://osf.io/fheun).
+
+  Materials, Data, Analysis Scripts: All materials and code can be found on our OSF page: https://osf.io/cgx6u/ or corresponding GitHub archive: https://github.com/doomlab/big_team_who.
 
@@
 linenumbers       : yes
-mask              : yes
+mask              : no
 draft             : no

### 2024-08-25 manuscript_definition.Rmd
updating new manuscript

--- 2024-02-07 manuscript_scopus_unmasked.Rmd
@@
 
--   Research Question 1: What publication sources publish big team
-    science papers?
--   Research Question 2: What are the types of articles that are being
-    published in big team science?
--   Research Question 3: Who is involved in big team science?
--   Research Question 4: How has the diversity of those involved in big team science changed over time?
+-   Research Question 1: Using current publication values, what should define big team science versus team science? (and change across time)
+-   Research Question 2: How has the diversity of those involved in big team science versus team science changed over time?
 
@@
 
-## RQ1: Publisher Information.
-
-```{r total-articles}
-# updated 
-total_num <- 510334
-health_num <- 445301
-physical_num <- 228194
-social_num <- 26652
-life_num <- 307514
-```
-
-### Number of Articles
-
-The total number of articles included in this
-analysis was `r total_num` including `r health_num` Health Sciences
-articles, `r physical_num` Physical Sciences articles, `r social_num`
-Social Sciences articles, and `r life_num` Life Sciences articles.
-Articles could be classified into multiple categories. Figure
-\@ref(fig:fig-pub-time) shows the number of articles published across
-time for each of the four large subject areas.
-
-```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years.
-All four subject areas show an exponential number of publications in the last decade.
-", fig.width=10, fig.height=6}
-ggplot(DF$pub_time_count %>% 
-         filter(SubjectArea != "Multidisciplinary") %>% 
-         filter(Year < 2023), 
-       aes(Year, count, color = SubjectArea)) + 
-  theme_classic(base_size = 15) + 
-  geom_point() + 
-  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
-  ylab("Number of Articles Per Year") + 
-  xlab("Publication Year") + 
-  theme(legend.position = "bottom")
-
-ggsave(filename = "figure/figure_1_pub_time.png", width = 10, height = 6)
-```
-
-```{r total-journals}
-# updated
-journals <- 14924
-health_journal <- 6559
-physical_journal <- 5787
-social_journal <- 2500
-life_journal <- 4187
-```
-
-### Number of Journals
-
-The number of distinct journals big team science
-articles were published in was `r journals` with `r health_journal`
-journals in Health Sciences, `r physical_journal` journals in Physical
-Sciences, `r social_journal` journals in Social Sciences, and
-`r life_journal` journals in Life Sciences. The descriptive statistics
-for the Source Normalized Impact per Paper is presented in the
-supplemental materials with a comparison for all papers.
-
-## RQ2: Publication Information.
-
-Publication interest area was summarized by the four large subject areas
-creating a word cloud plot of the total number of publications within
-the ASJCs. Figure \@ref(fig:fig-clouds) displays that the Health
-Sciences tends to publish within medicine and oncology, with a
-corresponding focus of cancer research and genetics for the Life
-Sciences. The Physical Sciences was mostly dominated by physics
-research, chemistry, and ecology. The BTS publications in the Social
-Sciences are mostly within psychology, education, and health.
-
-```{r make-clouds, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
-### NOTE YOU WILL NEED TO RUN THIS ###
-#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
-pub_total <- DF$pub_time_subject %>% 
-  group_by(SubjectArea, ASJC) %>% 
-  summarize(Count_Size = sum(count), .groups = "keep") %>% 
-  filter(SubjectArea != "Multidisciplinary") %>% 
-  left_join(DF$ASJC_codes %>% select(Name, Code), by = c("ASJC" = "Code"))
-
-# health
-health_cloud <- pub_total %>% 
-  filter(SubjectArea == "Health Sciences") %>% 
-  ungroup() %>%
-  arrange(desc(Count_Size)) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/health_cloud.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# physical
-physical_cloud <- pub_total %>% 
-  filter(SubjectArea == "Physical Sciences") %>% 
-  ungroup() %>%
-  arrange(desc(Count_Size)) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/physical_cloud.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# life
-life_cloud <- pub_total %>% 
-  filter(SubjectArea == "Life Sciences") %>% 
-  ungroup() %>%
-  arrange(desc(Count_Size)) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/life_cloud.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# social
-social_cloud <- pub_total %>% 
-  filter(SubjectArea == "Social Sciences") %>% 
-  ungroup() %>%
-  arrange(desc(Count_Size)) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/social_cloud.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-```
-
-```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area.
-Larger words indicate more publications in those ASJC areas.
-", fig.width=10, fig.height=6}
-
-health_cloud <- fig("figure/health_cloud.png")
-physical_cloud <- fig("figure/physical_cloud.png") 
-life_cloud <- fig("figure/life_cloud.png") 
-social_cloud <- fig("figure/social_cloud.png")
-
-health_cloud + ggtitle("Health Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-physical_cloud + ggtitle("Physical Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-life_cloud + ggtitle("Life Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-social_cloud + ggtitle("Social Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) +
-  plot_layout(ncol = 2, 
-              nrow = 2)
-
-ggsave(filename = "figure/figure_2_cloud.png", width = 10, height = 6)
-```
-
-## RQ3: Author Descriptive Statistics
+## RQ1: definition shit
 
@@
 the last few decades.
+
+## data split
+
+- "teams": 2-10 authors, 2-4 inst
+- "big ass": 11+, 5+
+
+## RQ1
+
+pattern of author numbers over time --> just the median because of the data split 
+four panel figure one for each area --> with two sets of dots for teams, "team", and BAT 
+since there's a restriction of range, do we need to calculate based on the proportion of the data or proportion of the range that it could increase
 
@@
 ```
-
-```{r pub-hindex}
-avg_pub_count_author	<- apa_num(38.368910766896065)
-std_pub_count_author <- apa_num(102.53740454680472)
-
-avg_pub_count_paper <- apa_num(162.50184385336053)
-sd_pub_count_paper <- apa_num(155.1665533053519)
-avg_SD_pub_count_paper <- apa_num(164.27249797983876)
-SD_SD_pub_count_paper <- apa_num(127.20989934008757)
-
-avg_HIndex <- apa_num(33.64589690529209)
-std_HIndex <- apa_num(127.33565834550778)
-med_HIndex <- apa_num(8.0)
-
-avg_of_avg_HIndex <- apa_num(198.87318851400775)
-std_of_avg_HIndex <- apa_num(248.7847084313958)
-avg_of_std_HIndex <- apa_num(211.7985924228093)
-std_of_std_HIndex <- apa_num(238.53141146314053)
-med_of_med_HIndex <- apa_num(68.0)
-```
-
-### Publication Metrics
-
-The average number of publications by authors on big team science papers
-is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`). The
-publication counts were averaged across authors for each publication,
-and then these average publication counts were averaged across
-publications *M* = `r avg_pub_count_paper` (*SD* =
-`r sd_pub_count_paper`). The average variability (i.e., the average
-standard deviation with authors of a manuscript) with publication counts
-of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
-`r SD_SD_pub_count_paper`).
-
-The same process was completed with *h*-index for each author and
-publication. The average *h*-index for authors overall was *M* =
-`r avg_HIndex` (*SD* = `r std_HIndex`, *Med* = `r med_HIndex`). The
-average *h*-index for publications was *M* = `r avg_of_avg_HIndex` (*SD*
-= `r std_of_avg_HIndex`), and the variability of *h*-index across
-manuscripts was $M_{SD}$ = `r avg_of_std_HIndex` ($SD_{SD}$ =
-`r std_of_std_HIndex`, $Med_{Med}$ = `r med_of_med_HIndex`).
-
-```{r total-aff}
-# updated
-affs <- 463876
-```
-
-### Institutions
-
-The total number of unique affiliation across all papers was `r affs`.
 
@@
 All values and their confidence intervals can be found on our OSF page.
+
+- four panel figure for subject area by total team, "team", BAT 
+- just in general people are having to publish much younger than we used to so here's how to view that
 

### 2024-09-11 manuscript_definition.Rmd
updating with outline

@@
 
+outline:
+
+- what is team science / collaboration 
+- research on how it's grown / changed over time? 
+- Any research diversification?
+  - on who is publishing 
+  - on where is represented 
+- "big" teams - unanswered question ... people are now using term "big team" but it's not defined - can we define it and see if it's any different or just a product of growth/internet over time?
+
 Collaboration in scientific endeavors involves multiple researchers at
@@
 
-## RQ1
+## RQ1 change over time
 
@@
 
+updated binning:
+
+- teams: 2-10 authors, 2-5 inst
+  - first and last author only versus everyone else
+- big ass teams: 6+ affs
+  - small: 11-49
+    - first three plus last versus everyone else
+  - medium: 50-99
+    - first five plus last versus everyone else
+  - large: 100+
+    - first 10 plus last versus everyone else
+
+for time:
+ teams versus big teams combining results
+ separate panel of the big teams separated (not by time)
+
 ```{r small-effects, warning = FALSE}

### 2024-10-15 manuscript_scopus/manuscript_scopus.Rmd
updated with new manuscript

--- 2024-01-16 manuscript_scopus.Rmd
@@
 
-var_list_import <- paste0("data/scopus_outputs/", var_list, ".xlsx")
+var_list_import <- paste0("../data/scopus_outputs/", var_list, ".xlsx")
 

### 2024-10-15 manuscript_scopus/manuscript_scopus_unmasked.Rmd
updated with new manuscript

--- 2024-02-07 manuscript_scopus_unmasked.Rmd
@@
 
--   Research Question 1: What publication sources publish big team
-    science papers?
--   Research Question 2: What are the types of articles that are being
-    published in big team science?
+-   Research Question 1: What should define big team science versus team science? 
+-   Research Question 2: What are differences in big team science compared to team science? 
 -   Research Question 3: Who is involved in big team science?

### 2024-10-15 manuscript_scopus/manuscript_scopus_unmasked.tex
updated with new manuscript

--- 2024-01-16 manuscript_scopus.tex
@@
 \documentclass[
-  man,mask,floatsintext]{apa7}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
   pdftitle={Who does big team science?},
+  pdfauthor={Erin M. Buchanan1 \& Savannah C. Lewis2},
   pdflang={en-EN},
@@
 
-Computational reproducibility: All materials and code can be found on our OSF page: MASKED FOR REVIEW or corresponding GitHub archive: MASKED FOR REVIEW.
+Computational reproducibility: All materials and code can be found on our OSF page: \url{https://osf.io/cgx6u/} or corresponding GitHub archive: \url{https://github.com/doomlab/big_team_who}.
 Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review.
 
-Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (MASKED FOR REVIEW\footnote{Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal, this work has been uploaded a deidentified zip file}) but then was updated with access to the Scopus database for a broader picture of BTS projects (MASKED FOR REVIEW).
-
-Materials: MASKED FOR REVIEW (see uploaded zip file).
-
-Data: MASKED FOR REVIEW (see uploaded zip file).
-
-Analysis scripts: MASKED FOR REVIEW (see uploaded zip file).
+Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr}) but then was updated with access to the Scopus database for a broader picture of BTS projects (\url{https://osf.io/fheun}).
+
+Materials, Data, Analysis Scripts: All materials and code can be found on our OSF page: \url{https://osf.io/cgx6u/} or corresponding GitHub archive: \url{https://github.com/doomlab/big_team_who}.
 }
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-time-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-pub-time-1.pdf}
 \caption{\label{fig:fig-pub-time}Number of big-team science publications separated by four large subject areas across years.
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-clouds-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-clouds-1.pdf}
 \caption{\label{fig:fig-clouds}Journal Areas for Big-Team Science Publications by Subject Area. Larger words indicate more publications in those ASJC areas.}
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-author-year-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-author-year-1.pdf}
 \caption{\label{fig:fig-author-year}Number of authors included on big-team science papers per year by subject area.
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-career-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-career-1.pdf}
 \caption{\label{fig:fig-career}Average career length for big-team science authors.
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-heatmap-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-heatmap-1.pdf}
 \caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region.
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-map-both-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-map-both-1.pdf}
 \caption{\label{fig:fig-map-both}Geopolitical regions represented in big-team science publications versus all publications.
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-author-gpe-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-author-gpe-1.pdf}
 \caption{\label{fig:fig-author-gpe}A comparison of author affiliation geopolitical regions across decades. F stands for first authors and O stands for other authors.}
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-effect-gpe-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-effect-gpe-1.pdf}
 \caption{\label{fig:fig-effect-gpe}Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-keywords-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-keywords-1.pdf}
 \caption{\label{fig:fig-keywords}Keyword Analysis for Each of the Four Subject Areas.}
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-inst-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-inst-1.pdf}
 \caption{\label{fig:fig-inst}Number of unique institutions involved in big-team science papers across decades.}
@@
 \centering
-\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-types-1.pdf}
+\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-pub-types-1.pdf}
 \caption{\label{fig:fig-pub-types}Types of publications for big-team science and all authors.}

### 2024-11-12 manuscript_definition.Rmd
Update manuscript_definition.Rmd

@@
 perspectives of collaborators. While collaboration is not new in
-science, the interest in "big team science" is increasing
-[@coles2022; @forscher2022a; @stewart2017]. Big team science (BTS) projects
-and/or organizations utilize and run large-scale collaborations to
-ensure that diverse populations and ideas manifest in research
-projects, which in turn allows for more reliability and generalizability
-in the results and methods of the study.
+science, interest in "team science is growing as individual researcher seek a interdisciplinary approach to research or bring on more students to their project.
+Team science leverages a more organized structure between the collaborator to divide the workload to more complex questions.
+
+"Big team science" (BTS) builds on team science by scaling efforts to include larger, often globally diverse teams, which requires significant coordination and infrastructure [@coles2022; @forscher2022a; @stewart2017].
+BTS projects and organizations organize extensive collaborations, intentionally incorporating diverse populations and perspectives into research.
+This large-scale approach enhances the reliability and generalizability of findings by integrating varied methodologies and viewpoints, leading to more robust and inclusive scientific outcomes.
+BTS organizations often pool extensive networks of researchers and resources, aiming to tackle grand scientific challenges that would be difficult to address within smaller or less coordinated collaborations.
 

### 2024-11-12 manuscript_definition.Rmd
updating the manuscript analyses, adding two of the outputs and renaming the final output

@@
 library(latex2exp)
+library(patchwork)
 
@@
 # things to import
-var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
-              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
-              "medium_other_gp", "normal_pub_type", "pub_time_count", 
-              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
-              "snip", "ASJC_codes", "snip_all")
-
-var_list_import <- paste0("data/scopus_outputs/", var_list, ".xlsx")
+var_list <- c("author_stats", "paper_stats")
+
+var_list_import <- paste0("data/scopus_outputs_2/", var_list, ".xlsx")
 
@@
 
-# Research Questions
-
--   Research Question 1: Using current publication values, what should define big team science versus team science? (and change across time)
--   Research Question 2: How has the diversity of those involved in big team science versus team science changed over time?
-
-# Method
-
-## Publications
-
 We have defined BTS publications as publications with at least ten
@@
 
-We used
-data from 1970 and forward in the Scopus database, as it is noted online
+# Research Questions
+
+-   Research Question 1: Using current publication values, what should define big team science versus team science? 
+  - Question 1A: What number of authors and institutional affiliations should designate the differences between team science and big team science?
+  - Question 1B: Using the definition from 1A, are there changes in the number of publications over time?
+
+  ### come back to this ###
+-   Research Question 2: How has the diversity of those involved in big team science versus team science changed over time?
+
+# Method
+
+## Publications
+
+We used data from 1970 and forward in the Scopus database, as it is noted online
 that this time period includes cited references for calculation of
-several of our variables described below. We will analyze our results
+several of our variables described below. We analyzed our results
 based on four subject areas present in the Scopus database: Physical
@@
 
-### RQ1: Publisher Information
-
-We extracted the following information for publication sources: the name
-of the publication (source title), subject area (both the large four
-subject areas and the smaller four digit all science journal
-classification [ASJC] code), and the journal impact using the Source
-Normalized Impact per Paper (SNIP).
-
-### RQ2: Publication Information
-
-For each publication of the identified BTS publications, we examined the
-full four digit ASJC subject areas codes for each of the larger four
-subject areas and the keywords present for these publications.
-
-### RQ3: Author Descriptive Statistics
-
-The author list was extracted from each publication. Next, we used the
-author and affiliation arrays to curate a list of all publications and
-author information included in BTS papers to calculate the variables
-described below.
-
-#### Education
-
-We collected degree information from the author table.
-Information on this variable is in the appendix.
-
-#### Types of Publications
-
-We took information from the publication
-type variable for each author's publications to present information
-about the types of papers BTS authors publish. Information on this
-variable is in the appendix.
-
-#### Publication Metrics
-
-For each author, we calculated the number of publications and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.
-
-#### Institutions
-
-We report the number of institutions involved in big team science publications.
-
-### RQ4: Author Diversity Statistics
+### RQ1: Defining BTS
+
+For each of the publications in Scopus, we calculated the number of distinct authors and institutions.
+If an author had multiple affiliations, we used the first affiliation listed.
+Each publication was classified into the four subject areas based on the All Journal Subject Codes present in the database.
+Publications can be included in multiple subject codes.
+For example, a medical paper may be listed in both life sciences and health sciences.
+
+### RQ2: Author Diversity Statistics
 
@@
 
-## RQ1: definition shit
+## RQ1: Defining BTS
+
+```{r total-papers}
+total_papers <- 97532104 # the entire database
+total_papers_past1970 <- 62966549 # past 1970, in our article types
+distinct_authors_past1970 <- 53622443 # all authors
+
+# one row per author per paper with all authors with at least two  
+team_author_aff_combo <- 196835398
+team_author_aff_papers <- 32454393
+team_author_aff_author <- 28353445
+team_author_aff_subject_noNA <- 241269297
+team_author_aff_papers_noNA <- 32448373
+team_author_aff_author_noNA <- 28350468
+```
+
+WRITE THE THING --> mention max in the text because too crazy for the graph
+
+```{r stats-authors}
+temp_graph <- DF$author_stats %>% 
+  filter(SubjectArea != "Multidisciplinary")
+
+auth_plot <- 
+  ggplot(temp_graph, aes(x = SubjectArea)) + 
+  geom_boxplot(
+    aes(
+      ymin = Min_Num_Authors,
+      lower = lower_IQR,
+      middle = Med_Num_Authors,
+      upper = upper_IQR,
+      ymax = very_high_90
+    ),
+    stat = "identity"
+  ) + 
+  theme_bw() + 
+  xlab("Subject Area") + 
+  ylab("Number of Authors") +
+  coord_cartesian(ylim = c(0,12)) + 
+  scale_y_continuous(breaks = c(0,2,4,6,8,10,12)) +
+  geom_point(aes(x = SubjectArea, y = Average_Num_Authors, 
+                 size = SD_Num_Authors)) +
+  theme(legend.position = "none")
+
+aff_plot <- 
+  ggplot(temp_graph, aes(x = SubjectArea)) + 
+  geom_boxplot(
+    aes(
+      ymin = Min_Num_Aff,
+      lower = lower_IQR_Aff,
+      middle = Med_Num_Aff,
+      upper = upper_IQR_Aff,
+      ymax = very_high_90_Aff
+    ),
+    stat = "identity"
+  ) + 
+  theme_bw() + 
+  xlab("Subject Area") + 
+  ylab("Number of First Affiliations") +
+  coord_cartesian(ylim = c(0,12)) + 
+  scale_y_continuous(breaks = c(0,2,4,6,8,10,12)) +
+  geom_point(aes(x = SubjectArea, y = Average_Num_Aff, 
+               size = SD_Num_Authors)) +
+  theme(legend.position = "none")
+
+auth_plot | aff_plot
+```
+
+WRITE THE THING --> make this a table to import
+
+NEED TO RUN ALL TEAMS SUBJECT AREA GRAPH
+
+```{r big-teams, results = 'asis'}
+big_teams_papers <- 968765
+big_teams_authors <- 4541369
+
+kable(DF$paper_stats %>% 
+        arrange(Statistic))
+```
+
+##rq1b
 

### 2024-11-12 manuscript_definition.Rmd
updating with estimates over time need to look at nonlinear models

@@
 library(patchwork)
+library(broom)
+library(minpack.lm)
+
+options(scipen = 99)
 
@@
 # things to import
-var_list <- c("author_stats", "paper_stats")
+var_list <- c("author_stats", "paper_stats", "author_paper_year")
 
@@
 
-## RQ1: Defining BTS
+## RQ1A: Defining BTS
 
@@
 
-##rq1b
+## RQ1B: Changes over Time
+
+SEE IF YOU CAN GET ALL THE NUMBERS SOME ARE MISSING
+
+```{r}
+temp <- DF$author_paper_year %>% 
+  filter(SubjectArea != "Multidisciplinary") %>% 
+  filter(Year < 2024)
+
+# temp %>% 
+#   group_by(SubjectArea, Year, group) %>% 
+#   summarize(n = n())
+
+p1 <- ggplot(temp %>% 
+         filter(group == "regular"), aes(x = Year, y = Number_Papers, colour = SubjectArea)) + 
+  geom_point() + 
+  theme_minimal() + 
+  theme(legend.position = "none")
+
+p2 <- ggplot(temp %>% 
+         filter(group == "big"), aes(x = Year, y = Number_Papers, colour = SubjectArea)) + 
+  geom_point() + 
+  theme_minimal() + 
+  theme(legend.position = "bottom")
+
+p1 | p2
+```
+
+```{r}
+group <- unique(temp$group)
+subjarea <- unique(temp$SubjectArea)
+corr.results <- list()
+
+for (group_label in group){
+  for (SA in subjarea){
+    stuff <- temp %>% 
+      filter(group == group_label) %>% 
+      filter(SubjectArea == SA) 
+    # Attempt with nlsLM for more robust optimization
+    fit <- nlsLM(Number_Papers ~ a * exp(r * Year), 
+             start = list(a = 0.2, r = 0.05), 
+             data = stuff)
+    corr.results[[paste0(group_label, "_", SA)]] <- tidy(fit)
+
+  }
+}
+
+corr.DF <- bind_rows(corr.results) %>% 
+  mutate(group = rep(group, each = 8)) %>% 
+  mutate(SubjectArea = c(
+    rep(subjarea, each = 2),
+    rep(subjarea, each = 2)
+    ))
+
+ggplot(corr.DF, aes(x = SubjectArea, y = estimate, color = group)) + 
+  geom_point() +
+  theme_minimal() + 
+  geom_linerange(aes(ymin = conf.low, ymax = conf.high))
+```
+
+In the exponential model ￼, the parameters ￼ and ￼ have specific interpretations:
+	1.	Parameter ￼ (Initial Value or Scale):
+	•	￼ represents the initial value or the scaling factor of the exponential function.
+It indicates the starting level of the dependent variable (in this case, Number_Papers) when the Year is at its baseline (e.g., the first year in your dataset or zero if Year is centered).
+	•	A larger value of ￼ would mean a higher starting point for the number of papers.
+	2.	Parameter ￼ (Growth Rate):
+	•	￼ is the growth rate parameter. It indicates how quickly the number of papers grows over time.
+	•	If ￼ is positive, the model shows exponential growth, meaning the number of papers increases over time at an accelerating rate.
+	•	If ￼ is negative, the model would represent exponential decay, suggesting that the number of papers decreases over time.
+	•	The magnitude of ￼ affects the steepness of the growth or decay curve, with larger values (in absolute terms) indicating a more rapid change.
+
+Interpretation Example:
+	•	If ￼ and ￼, then:
+	•	The starting number of papers is about 2 (when Year is zero or the baseline year).
+	•	The number of papers grows by about ￼ per unit of Year, as ￼ implies a growth rate of ￼ per year.
+	•	If ￼, the model would predict a constant number of papers over time, as the exponential term ￼ becomes 1.
+
+Let me know if you’d like help with the interpretation for specific values in your fitted model.
 

### 2024-12-05 manuscript_definition.Rmd
Sav intro edits

@@
 
-Collaboration in scientific endeavors involves multiple researchers at
-(potentially) multiple institutions to communicate and work together to
-advance knowledge in their chosen field. Collaboration can manifest
-uniquely in each project dependent on the skill sets, hypotheses, and
-perspectives of collaborators. While collaboration is not new in
-science, interest in "team science is growing as individual researcher seek a interdisciplinary approach to research or bring on more students to their project.
-Team science leverages a more organized structure between the collaborator to divide the workload to more complex questions.
-
-"Big team science" (BTS) builds on team science by scaling efforts to include larger, often globally diverse teams, which requires significant coordination and infrastructure [@coles2022; @forscher2022a; @stewart2017].
+SAVS NEW VERSION!
+
+Collaboration in scientific endeavors involves multiple researchers at (potentially) multiple institutions to communicate and work together to advance knowledge in their chosen field.
+Collaboration can manifest uniquely in each project dependent on the skill sets, hypotheses, and perspectives of collaborators.
+One key aspect of collaboration is the flexibility allotted as it is shaped by the needs of the project and the participants involved.
+
+While collaboration is not new in science, interest in "team science" is growing as individual researchers seek an interdisciplinary approach to research or bring on more students to their project.
+Unlike general collaboration, team science involves structured roles, coordinated workflows, and shared resources to address challenges that would be difficult for individual researchers or one small team to solve independently.
+Team science often brings in some aspect of diversity but likely is still very homogenous in several aspects.
+
+The evolution of team science reflects broader shifts in research practices, driven by two sources: 1) increasing globalization and technology that allows for real-time interdisciplinary research, and 2) expanding interest in reproducibility, replication, and generalizability [i.e., the credibility movement, @maxwell2015; @nelson2018; @zwaan2018; @vazire2022].
+Technological advances have provided easier ways to collaborate with people who are from other universities and countries through document sharing platforms (e.g., Google, GitHub, and the Open Science Framework), video chatting platforms (e.g., Zoom, Microsoft Teams), and messaging and project management platforms (e.g., Slack, Trello, when2meet, etc.).
+
+The credibility movement has been the main catalyst for the increased interest and broader shift of research practices.
+The movement emphasizes reproducibility and transparency in science, encouraging researchers to form new ways to increase the rigor in scientific endeavors.
+As the movement has adapted throughout the last decade, the idea to form larger, more diverse teams and to include participants from varied backgrounds has become even more a goal to not only increase the credibility but the generalizability and reliability of scientific findings.
+This form of collaboration has been coined “Big Team Science.”
+
+“Big Team Science” builds on team science by scaling efforts to include larger, often globally diverse teams, which requires significant coordination and infrastructure [@coles2022; @forscher2022a; @stewart2017].
 BTS projects and organizations organize extensive collaborations, intentionally incorporating diverse populations and perspectives into research.
@@
 BTS organizations often pool extensive networks of researchers and resources, aiming to tackle grand scientific challenges that would be difficult to address within smaller or less coordinated collaborations.
-
-BTS appears to be expanding because of two sources: 1) increasing
-globalization and technology that allows for real-time interdisciplinary
-research, and 2) expanding interest in reproducibility, replication, and
-generalizability [i.e., the credibility movement, 
-@maxwell2015; @nelson2018; @zwaan2018; @vazire2022]. Technological
-advances have provided easier ways to collaborate with people who are
-from other universities and countries through document sharing platforms
-(e.g., Google, GitHub, and the Open Science Framework), video chatting
-platforms (e.g., Zoom, Microsoft Teams), and messaging and project
-management platforms (e.g., Slack, Trello, when2meet, etc.). The
-credibility movement seems to suggest that by having both collaborations
-that span across the globe and subfields of research areas, age groups,
-and education levels should help to drive science in the path of better
-materials, reliability, generalizability, and more robust sample sizes
-(when necessary) in a study [@auspurg2021; @nosek2014method;
-@lebel2018].
-
-Generally, the credibility movement appears to have been driven by early career
-researchers [i.e., those who are within five years of their first
-appointment, @maizey2019]; however, there are no large meta-scientific
-investigations on this specific topic to date.
+By having both collaborations that span across the globe and subfields of research areas, age groups, and education levels should help to drive science in the path of better materials, reliability, generalizability, and more robust sample sizes (when necessary) in a study [@auspurg2021; @nosek2014method; @lebel2018].
+
+Generally, the credibility movement appears to have been driven by early career researchers [i.e., those who are within five years of their first appointment, @maizey2019]; however, there are no large meta-scientific investigations on this specific topic to date.
 The newness of large-scale research in many fields could be the culprit for the lack of investigation into this area.
-For example, psychology has had an increase in BTS publications like the Open
-Science Collaboration [@opensciencecollaboration2015], Many Labs
-Collaborations [@buttrick2020; @ebersole2016; @ebersole2020; @klein2018;
-@klein2022; @mathur2020; @skorb2020] or the first papers from the
-Psychological Science Accelerator [@bago2022; @buchanan2023;
-@dorison2022; @jones2021;
-@psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
-@moshontz2018; @wang2021]. Generally, the researcher incentive for
-replication and/or involvement in big-team projects was low for three reasons. First, journals often prioritize
-"novel" or new results which led to rejection of replication manuscripts
-and publication bias [@franco2014; @hubbard1997; @nosek2012]. Second,
-the "failure" to replicate was often placed on the replication team as
-"bad science" rather than a careful consideration of publication biases
-and (potential) questionable research practices [@klein2022;
-@maxwell2015]. Last, why should someone want to spend time and resources
-on an answer we already "know" [@isager2021; @isager2021a]?
-
-However, the success and interest in the large-scale reproducibility
-projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired
-with the meta-scientific publications focusing on researcher practices
-and incentive structures [@silberzahn2018many; @john2012] led to a
-change in journal guidelines and incentives for researchers interested
-in participating in large-scale replication studies [@grahe2014;
-@kidwell2016; @nosek2015; @mayo-wilson2021]. In some fields, the 
-replication movement demonstrated that large-scale teams were a 
-practical (and publishable) solution to answering research questions 
-in generalizable way. The support
-for Registered Reports, papers accepted before the data has been
-collected [@nosek2014; @stewart2020], has allowed researchers to 
-invest in projects that they know
-should be published when the project is complete. Further, the
-implementation of the Transparency and Openness Guidelines [@nosek2015]
-and the Contributor Role Taxonomy (CRediT) system [@allen2019] have
-pushed journals and researchers to promote more open, inclusive
-publication practices.
-
-Beyond replication concerns, the credibility movement has mirrored calls for diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
-Rich, and Democratic) scientific research [@henrich2010; @newson2021;
-@rad2018] by improving representation in research samples. Like the
-large-scale studies in Physics [@aphilos2021; @castelnovo2018] and
-Biology [@collins2003], the Social Sciences struggle to represent the
-breadth of humanity across both researcher and population
-characteristics. Now, grassroots organizations, such as the
-Psychological Science Accelerator [@moshontz2018], ManyBabies
-(<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and
-DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these
-issues by recruiting research labs from all over the globe to provide
-diversity in geographic, linguistic, and researcher representation.
+For example, psychology has had an increase in BTS publications like the Open Science Collaboration [@opensciencecollaboration2015], Many Labs Collaborations [@buttrick2020; @ebersole2016; @ebersole2020; @klein2018; @klein2022; @mathur2020; @skorb2020] or the first papers from the Psychological Science Accelerator [@bago2022; @buchanan2023;
+@dorison2022; @jones2021; @psychologicalscienceacceleratorself-determinationtheorycollaboration2022; @moshontz2018; @wang2021].
+Generally, the researcher incentive for replication and/or involvement in big-team projects was low for three reasons.
+First, journals often prioritize "novel" or new results which led to rejection of replication manuscripts and publication bias [@franco2014; @hubbard1997; @nosek2012].
+Second, the "failure" to replicate was often placed on the replication team as "bad science" rather than a careful consideration of publication biases and (potential) questionable research practices [@klein2022; @maxwell2015].
+Last, why should someone want to spend time and resources on an answer we already "know" [@isager2021; @isager2021a]?
+
+However, the success and interest in the large-scale reproducibility projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired with the meta-scientific publications focusing on researcher practices  and incentive structures [@silberzahn2018many; @john2012] led to a change in journal guidelines and incentives for researchers interested in participating in large-scale replication studies [@grahe2014; @kidwell2016; @nosek2015; @mayo-wilson2021].
+In some fields, the replication movement demonstrated that large-scale teams were a practical (and publishable) solution to answering research questions in generalizable way.
+The support for Registered Reports, papers accepted before the data has been collected [@nosek2014; @stewart2020], has allowed researchers to  invest in projects that they know should be published when the project is complete.
+Further, the implementation of the Transparency and Openness Guidelines [@nosek2015] and the Contributor Role Taxonomy (CRediT) system [@allen2019] have pushed journals and researchers to promote more open, inclusive publication practices.
+
+Beyond replication concerns, the credibility movement has mirrored calls for diversification or  de-WEIRDing (e.g., Western, Educated, Industrialized, Rich, and Democratic) scientific research [@henrich2010; @newson2021; @rad2018] by improving representation in research samples.
+Like the large-scale studies in Physics [@aphilos2021; @castelnovo2018] and Biology [@collins2003], the Social Sciences struggle to represent the breadth of humanity across both researcher and population characteristics.
+Now, grassroots organizations, such as the Psychological Science Accelerator [@moshontz2018], ManyBabies (<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these issues by recruiting research labs from all over the globe to provide diversity in geographic, linguistic, and researcher representation.
 Publications have examined the global understanding of morality, face
-processing, COVID-19 information signaling, and more [@bago2022;
-@dorison2022; @jones2021;
-@psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
-@vanbavel2022; @wang2021]. While these organizations and one-time groups
-for BTS studies have provided an incredible wealth of data for the
-scientific community, we do not yet know exactly *who* is involved with,
-and benefits from, the BTS and credibility movement. Publications on BTS
-generally explore challenges, lessons learned, and the need for BTS
+processing, COVID-19 information signaling, and more [@bago2022; @dorison2022; @jones2021; @psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
+@vanbavel2022; @wang2021].
+While these organizations and one-time groups for BTS studies have provided an incredible wealth of data for the scientific community, we do not yet know exactly *who* is involved with, and benefits from, the BTS and credibility movement.
+Publications on BTS generally explore challenges, lessons learned, and the need for BTS
 [@forscher2022a; @coles2022].
 
-Therefore, the goal of this manuscript is to examine both the *publications* and *people* involved in BTS projects.
-We present descriptive information about the publication sources and types of articles to demonstrate large-scale research.
-Next, we examine the individuals involved in BTS for descriptive and predictive purposes.
-To describe the people involved in BTS projects, we planned to use education, types of publications from BTS individuals, and publication metrics.
+There is no universally agreed-upon definition of BTS, raising questions about whether it represents a distinct phenomenon or simply a natural extension of team science.
+Therefore, we originally arbitrarily chose a definition for BTS publication which we had decided to be publications with at least ten authors at ten different institutions that were published in peer-reviewed journals or had posted a full paper pre-print.
+While this definition is a somewhat arbitrary choice, we separate this research from research on team science that uses any multi-university collaboration as a definition [@jones2008] to focus on larger sized teams rather than teams of any size.
+With at least ten institutions, the complexities of infrastructure, resources, tenure and promotion policies, ethics review, and more can occur [@forscher2022a].
+Therefore, we believe this choice selects publications that would be "big" teams and those potential obstacles.
+
+This manuscript seeks not only to evaluate whether this definition is an appropriate fit for BTS but also to explore whether the criteria for defining BTS should vary by subject area or evolve over time.
+Understanding these nuances will help clarify whether BTS represents a fundamentally new approach to collaboration or a natural progression of team science in response to global and technological trends.
+
+We then will examine if there is a true difference between “Team Science” and "Big Team Science”.
+Therefore, the goal of this manuscript is to examine both the *publications* and *people* involved in BTS projects and “Team Science.” We present descriptive information about the publication sources and types of articles to demonstrate large-scale research.
+Next, we examine the individuals involved in BTS and “Team Science” for descriptive and predictive purposes.
+To describe the people involved in BTS projects vs “Team Science”, we planned to use types of publications from individuals.
 For predictive statistics, we explored the change in diversity of authors over time.
-It is unclear if the focus of de-WEIRDing science has only focused on the representation of the
-research participants or if it has also improved the representation of
-researchers outside of North America and Europe.
+It is unclear if the focus of de-WEIRDing science has only focused on the representation of the research participants or if it has also improved the representation of researchers outside of North America and Europe.
 Last, we examined for a change in diversity within first author(s) and the last author across time.
-As hiring and promoting practices often place a heavy weight on publications and especially “influential” publications, it becomes necessary to critically examine the representation present in authorship in BTS projects.
-
-We have defined BTS publications as publications with at least ten
-authors at ten different institutions that were published in
-peer-reviewed journals or had posted a full paper pre-print. While this 
-definition is a somewhat arbitrary choice, we separate this research 
-from research on team science that uses any multi-university collaboration 
-as a definition [@jones2008] to focus on larger sized teams rather 
-than teams of any size. With at least ten institutions, the complexities 
-of infrastructure, resources, tenure and promotion policies, ethics review, and more can occur [@forscher2022a].
-Therefore, we believe this choice selects publications that would be "big" teams and those potential obstacles.
+As hiring and promoting practices often place a heavy weight on publications and especially “influential” publications, it becomes necessary to critically examine the representation present in authorship in BTS and Team Science” projects.
 

### 2024-12-05 manuscript_definition.Rmd
updated with RQ1 results

@@
 # things to import
-var_list <- c("author_stats", "paper_stats", "author_paper_year")
+var_list <- c("author_stats", "paper_stats", "author_paper_year",
+              "career_time")
 
@@
     -   on where is represented
-- "big" teams - unanswered question ... people are now using term "big team" but it's not defined - can we define it and see if it's any different or just a product of growth/internet over time?
+-   "big" teams - unanswered question ... people are now using term "big
+    team" but it's not defined - can we define it and see if it's any
+    different or just a product of growth/internet over time?
 
@@
 
-Collaboration in scientific endeavors involves multiple researchers at (potentially) multiple institutions to communicate and work together to advance knowledge in their chosen field.
-Collaboration can manifest uniquely in each project dependent on the skill sets, hypotheses, and perspectives of collaborators.
-One key aspect of collaboration is the flexibility allotted as it is shaped by the needs of the project and the participants involved.
-
-While collaboration is not new in science, interest in "team science" is growing as individual researchers seek an interdisciplinary approach to research or bring on more students to their project.
-Unlike general collaboration, team science involves structured roles, coordinated workflows, and shared resources to address challenges that would be difficult for individual researchers or one small team to solve independently.
-Team science often brings in some aspect of diversity but likely is still very homogenous in several aspects.
-
-The evolution of team science reflects broader shifts in research practices, driven by two sources: 1) increasing globalization and technology that allows for real-time interdisciplinary research, and 2) expanding interest in reproducibility, replication, and generalizability [i.e., the credibility movement, @maxwell2015; @nelson2018; @zwaan2018; @vazire2022].
-Technological advances have provided easier ways to collaborate with people who are from other universities and countries through document sharing platforms (e.g., Google, GitHub, and the Open Science Framework), video chatting platforms (e.g., Zoom, Microsoft Teams), and messaging and project management platforms (e.g., Slack, Trello, when2meet, etc.).
-
-The credibility movement has been the main catalyst for the increased interest and broader shift of research practices.
-The movement emphasizes reproducibility and transparency in science, encouraging researchers to form new ways to increase the rigor in scientific endeavors.
-As the movement has adapted throughout the last decade, the idea to form larger, more diverse teams and to include participants from varied backgrounds has become even more a goal to not only increase the credibility but the generalizability and reliability of scientific findings.
-This form of collaboration has been coined “Big Team Science.”
-
-“Big Team Science” builds on team science by scaling efforts to include larger, often globally diverse teams, which requires significant coordination and infrastructure [@coles2022; @forscher2022a; @stewart2017].
-BTS projects and organizations organize extensive collaborations, intentionally incorporating diverse populations and perspectives into research.
-This large-scale approach enhances the reliability and generalizability of findings by integrating varied methodologies and viewpoints, leading to more robust and inclusive scientific outcomes.
-BTS organizations often pool extensive networks of researchers and resources, aiming to tackle grand scientific challenges that would be difficult to address within smaller or less coordinated collaborations.
-By having both collaborations that span across the globe and subfields of research areas, age groups, and education levels should help to drive science in the path of better materials, reliability, generalizability, and more robust sample sizes (when necessary) in a study [@auspurg2021; @nosek2014method; @lebel2018].
-
-Generally, the credibility movement appears to have been driven by early career researchers [i.e., those who are within five years of their first appointment, @maizey2019]; however, there are no large meta-scientific investigations on this specific topic to date.
-The newness of large-scale research in many fields could be the culprit for the lack of investigation into this area.
-For example, psychology has had an increase in BTS publications like the Open Science Collaboration [@opensciencecollaboration2015], Many Labs Collaborations [@buttrick2020; @ebersole2016; @ebersole2020; @klein2018; @klein2022; @mathur2020; @skorb2020] or the first papers from the Psychological Science Accelerator [@bago2022; @buchanan2023;
-@dorison2022; @jones2021; @psychologicalscienceacceleratorself-determinationtheorycollaboration2022; @moshontz2018; @wang2021].
-Generally, the researcher incentive for replication and/or involvement in big-team projects was low for three reasons.
-First, journals often prioritize "novel" or new results which led to rejection of replication manuscripts and publication bias [@franco2014; @hubbard1997; @nosek2012].
-Second, the "failure" to replicate was often placed on the replication team as "bad science" rather than a careful consideration of publication biases and (potential) questionable research practices [@klein2022; @maxwell2015].
-Last, why should someone want to spend time and resources on an answer we already "know" [@isager2021; @isager2021a]?
-
-However, the success and interest in the large-scale reproducibility projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired with the meta-scientific publications focusing on researcher practices  and incentive structures [@silberzahn2018many; @john2012] led to a change in journal guidelines and incentives for researchers interested in participating in large-scale replication studies [@grahe2014; @kidwell2016; @nosek2015; @mayo-wilson2021].
-In some fields, the replication movement demonstrated that large-scale teams were a practical (and publishable) solution to answering research questions in generalizable way.
-The support for Registered Reports, papers accepted before the data has been collected [@nosek2014; @stewart2020], has allowed researchers to  invest in projects that they know should be published when the project is complete.
-Further, the implementation of the Transparency and Openness Guidelines [@nosek2015] and the Contributor Role Taxonomy (CRediT) system [@allen2019] have pushed journals and researchers to promote more open, inclusive publication practices.
-
-Beyond replication concerns, the credibility movement has mirrored calls for diversification or  de-WEIRDing (e.g., Western, Educated, Industrialized, Rich, and Democratic) scientific research [@henrich2010; @newson2021; @rad2018] by improving representation in research samples.
-Like the large-scale studies in Physics [@aphilos2021; @castelnovo2018] and Biology [@collins2003], the Social Sciences struggle to represent the breadth of humanity across both researcher and population characteristics.
-Now, grassroots organizations, such as the Psychological Science Accelerator [@moshontz2018], ManyBabies (<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these issues by recruiting research labs from all over the globe to provide diversity in geographic, linguistic, and researcher representation.
+Collaboration in scientific endeavors involves multiple researchers at
+(potentially) multiple institutions to communicate and work together to
+advance knowledge in their chosen field. Collaboration can manifest
+uniquely in each project dependent on the skill sets, hypotheses, and
+perspectives of collaborators. One key aspect of collaboration is the
+flexibility allotted as it is shaped by the needs of the project and the
+participants involved.
+
+While collaboration is not new in science, interest in "team science" is
+growing as individual researchers seek an interdisciplinary approach to
+research or bring on more students to their project. Unlike general
+collaboration, team science involves structured roles, coordinated
+workflows, and shared resources to address challenges that would be
+difficult for individual researchers or one small team to solve
+independently. Team science often brings in some aspect of diversity but
+likely is still very homogenous in several aspects.
+
+The evolution of team science reflects broader shifts in research
+practices, driven by two sources: 1) increasing globalization and
+technology that allows for real-time interdisciplinary research, and 2)
+expanding interest in reproducibility, replication, and generalizability
+[i.e., the credibility movement, @maxwell2015; @nelson2018; @zwaan2018;
+@vazire2022]. Technological advances have provided easier ways to
+collaborate with people who are from other universities and countries
+through document sharing platforms (e.g., Google, GitHub, and the Open
+Science Framework), video chatting platforms (e.g., Zoom, Microsoft
+Teams), and messaging and project management platforms (e.g., Slack,
+Trello, when2meet, etc.).
+
+The credibility movement has been the main catalyst for the increased
+interest and broader shift of research practices. The movement
+emphasizes reproducibility and transparency in science, encouraging
+researchers to form new ways to increase the rigor in scientific
+endeavors. As the movement has adapted throughout the last decade, the
+idea to form larger, more diverse teams and to include participants from
+varied backgrounds has become even more a goal to not only increase the
+credibility but the generalizability and reliability of scientific
+findings. This form of collaboration has been coined “Big Team Science.”
+
+“Big Team Science” builds on team science by scaling efforts to include
+larger, often globally diverse teams, which requires significant
+coordination and infrastructure [@coles2022; @forscher2022a;
+@stewart2017]. BTS projects and organizations organize extensive
+collaborations, intentionally incorporating diverse populations and
+perspectives into research. This large-scale approach enhances the
+reliability and generalizability of findings by integrating varied
+methodologies and viewpoints, leading to more robust and inclusive
+scientific outcomes. BTS organizations often pool extensive networks of
+researchers and resources, aiming to tackle grand scientific challenges
+that would be difficult to address within smaller or less coordinated
+collaborations. By having both collaborations that span across the globe
+and subfields of research areas, age groups, and education levels should
+help to drive science in the path of better materials, reliability,
+generalizability, and more robust sample sizes (when necessary) in a
+study [@auspurg2021; @nosek2014method; @lebel2018].
+
+Generally, the credibility movement appears to have been driven by early
+career researchers [i.e., those who are within five years of their first
+appointment, @maizey2019]; however, there are no large meta-scientific
+investigations on this specific topic to date. The newness of
+large-scale research in many fields could be the culprit for the lack of
+investigation into this area. For example, psychology has had an
+increase in BTS publications like the Open Science Collaboration
+[@opensciencecollaboration2015], Many Labs Collaborations
+[@buttrick2020; @ebersole2016; @ebersole2020; @klein2018; @klein2022;
+@mathur2020; @skorb2020] or the first papers from the Psychological
+Science Accelerator [@bago2022; @buchanan2023; @dorison2022; @jones2021;
+@psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
+@moshontz2018; @wang2021]. Generally, the researcher incentive for
+replication and/or involvement in big-team projects was low for three
+reasons. First, journals often prioritize "novel" or new results which
+led to rejection of replication manuscripts and publication bias
+[@franco2014; @hubbard1997; @nosek2012]. Second, the "failure" to
+replicate was often placed on the replication team as "bad science"
+rather than a careful consideration of publication biases and
+(potential) questionable research practices [@klein2022; @maxwell2015].
+Last, why should someone want to spend time and resources on an answer
+we already "know" [@isager2021; @isager2021a]?
+
+However, the success and interest in the large-scale reproducibility
+projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired
+with the meta-scientific publications focusing on researcher practices
+and incentive structures [@silberzahn2018many; @john2012] led to a
+change in journal guidelines and incentives for researchers interested
+in participating in large-scale replication studies [@grahe2014;
+@kidwell2016; @nosek2015; @mayo-wilson2021]. In some fields, the
+replication movement demonstrated that large-scale teams were a
+practical (and publishable) solution to answering research questions in
+generalizable way. The support for Registered Reports, papers accepted
+before the data has been collected [@nosek2014; @stewart2020], has
+allowed researchers to invest in projects that they know should be
+published when the project is complete. Further, the implementation of
+the Transparency and Openness Guidelines [@nosek2015] and the
+Contributor Role Taxonomy (CRediT) system [@allen2019] have pushed
+journals and researchers to promote more open, inclusive publication
+practices.
+
+Beyond replication concerns, the credibility movement has mirrored calls
+for diversification or de-WEIRDing (e.g., Western, Educated,
+Industrialized, Rich, and Democratic) scientific research [@henrich2010;
+@newson2021; @rad2018] by improving representation in research samples.
+Like the large-scale studies in Physics [@aphilos2021; @castelnovo2018]
+and Biology [@collins2003], the Social Sciences struggle to represent
+the breadth of humanity across both researcher and population
+characteristics. Now, grassroots organizations, such as the
+Psychological Science Accelerator [@moshontz2018], ManyBabies
+(<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and
+DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these
+issues by recruiting research labs from all over the globe to provide
+diversity in geographic, linguistic, and researcher representation.
 Publications have examined the global understanding of morality, face
-processing, COVID-19 information signaling, and more [@bago2022; @dorison2022; @jones2021; @psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
-@vanbavel2022; @wang2021].
-While these organizations and one-time groups for BTS studies have provided an incredible wealth of data for the scientific community, we do not yet know exactly *who* is involved with, and benefits from, the BTS and credibility movement.
-Publications on BTS generally explore challenges, lessons learned, and the need for BTS
+processing, COVID-19 information signaling, and more [@bago2022;
+@dorison2022; @jones2021;
+@psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
+@vanbavel2022; @wang2021]. While these organizations and one-time groups
+for BTS studies have provided an incredible wealth of data for the
+scientific community, we do not yet know exactly *who* is involved with,
+and benefits from, the BTS and credibility movement. Publications on BTS
+generally explore challenges, lessons learned, and the need for BTS
 [@forscher2022a; @coles2022].
 
-There is no universally agreed-upon definition of BTS, raising questions about whether it represents a distinct phenomenon or simply a natural extension of team science.
-Therefore, we originally arbitrarily chose a definition for BTS publication which we had decided to be publications with at least ten authors at ten different institutions that were published in peer-reviewed journals or had posted a full paper pre-print.
-While this definition is a somewhat arbitrary choice, we separate this research from research on team science that uses any multi-university collaboration as a definition [@jones2008] to focus on larger sized teams rather than teams of any size.
-With at least ten institutions, the complexities of infrastructure, resources, tenure and promotion policies, ethics review, and more can occur [@forscher2022a].
-Therefore, we believe this choice selects publications that would be "big" teams and those potential obstacles.
-
-This manuscript seeks not only to evaluate whether this definition is an appropriate fit for BTS but also to explore whether the criteria for defining BTS should vary by subject area or evolve over time.
-Understanding these nuances will help clarify whether BTS represents a fundamentally new approach to collaboration or a natural progression of team science in response to global and technological trends.
-
-We then will examine if there is a true difference between “Team Science” and "Big Team Science”.
-Therefore, the goal of this manuscript is to examine both the *publications* and *people* involved in BTS projects and “Team Science.” We present descriptive information about the publication sources and types of articles to demonstrate large-scale research.
-Next, we examine the individuals involved in BTS and “Team Science” for descriptive and predictive purposes.
-To describe the people involved in BTS projects vs “Team Science”, we planned to use types of publications from individuals.
-For predictive statistics, we explored the change in diversity of authors over time.
-It is unclear if the focus of de-WEIRDing science has only focused on the representation of the research participants or if it has also improved the representation of researchers outside of North America and Europe.
-Last, we examined for a change in diversity within first author(s) and the last author across time.
-As hiring and promoting practices often place a heavy weight on publications and especially “influential” publications, it becomes necessary to critically examine the representation present in authorship in BTS and Team Science” projects.
+There is no universally agreed-upon definition of BTS, raising questions
+about whether it represents a distinct phenomenon or simply a natural
+extension of team science. Therefore, we originally arbitrarily chose a
+definition for BTS publication which we had decided to be publications
+with at least ten authors at ten different institutions that were
+published in peer-reviewed journals or had posted a full paper
+pre-print. While this definition is a somewhat arbitrary choice, we
+separate this research from research on team science that uses any
+multi-university collaboration as a definition [@jones2008] to focus on
+larger sized teams rather than teams of any size. With at least ten
+institutions, the complexities of infrastructure, resources, tenure and
+promotion policies, ethics review, and more can occur [@forscher2022a].
+Therefore, we believe this choice selects publications that would be
+"big" teams and those potential obstacles.
+
+This manuscript seeks not only to evaluate whether this definition is an
+appropriate fit for BTS but also to explore whether the criteria for
+defining BTS should vary by subject area or evolve over time.
+Understanding these nuances will help clarify whether BTS represents a
+fundamentally new approach to collaboration or a natural progression of
+team science in response to global and technological trends.
+
+We then will examine if there is a true difference between “Team
+Science” and "Big Team Science”. Therefore, the goal of this manuscript
+is to examine both the *publications* and *people* involved in BTS
+projects and “Team Science.” We present descriptive information about
+the publication sources and types of articles to demonstrate large-scale
+research. Next, we examine the individuals involved in BTS and “Team
+Science” for descriptive and predictive purposes. To describe the people
+involved in BTS projects vs “Team Science”, we planned to use types of
+publications from individuals. For predictive statistics, we explored
+the change in diversity of authors over time. It is unclear if the focus
+of de-WEIRDing science has only focused on the representation of the
+research participants or if it has also improved the representation of
+researchers outside of North America and Europe. Last, we examined for a
+change in diversity within first author(s) and the last author across
+time. As hiring and promoting practices often place a heavy weight on
+publications and especially “influential” publications, it becomes
+necessary to critically examine the representation present in authorship
+in BTS and Team Science” projects.
 
@@
 
--   Research Question 1: Using current publication values, what should define big team science versus team science? 
-  - Question 1A: What number of authors and institutional affiliations should designate the differences between team science and big team science?
-  - Question 1B: Using the definition from 1A, are there changes in the number of publications over time?
-
-  ### come back to this ###
--   Research Question 2: How has the diversity of those involved in big team science versus team science changed over time?
+- Research Question 1: Exploring historical and current publication
+    values, what should define big team science versus team science?
+  - Question 1A: What number of authors and institutional affiliations
+    should designate the differences between team science and big team
+    science?
+  - Question 1B: Using the definition from 1A, are there changes in the
+    number of publications over time?
+- Research Question 2: How has the diversity of those involved in big
+    team science versus team science changed over time?
 
@@
 
-We used data from 1970 and forward in the Scopus database, as it is noted online
-that this time period includes cited references for calculation of
-several of our variables described below. We analyzed our results
+We used data from 1970-2024 in the Scopus database, as it is noted
+online that 1970 and forward includes cited references for calculation
+of several of our variables described below. We analyzed our results
 based on four subject areas present in the Scopus database: Physical
@@
 
-For each of the publications in Scopus, we calculated the number of distinct authors and institutions.
-If an author had multiple affiliations, we used the first affiliation listed.
-Each publication was classified into the four subject areas based on the All Journal Subject Codes present in the database.
-Publications can be included in multiple subject codes.
-For example, a medical paper may be listed in both life sciences and health sciences.
+For each of the publications in Scopus, we calculated the number of
+distinct authors and institutions. If an author had multiple
+affiliations, we used the first affiliation listed. Each publication was
+classified into the four subject areas based on the All Journal Subject
+Codes present in the database. Publications can be included in multiple
+subject codes. For example, a medical paper may be listed in both life
+sciences and health sciences.
 
@@
 
-Career length for each author was defined as the
-year of the first publication minus the current year listed for each
-author.
-Number of publications included the number of unique entries an author was included in the database.
-Career length and number of publications was used as a proxy for the "age" or "seniority" of a scholar.
+Career length for each author was defined as the year of the first
+publication minus the current year listed for each author. Number of
+publications included the number of unique entries an author was
+included in the database. Career length and number of publications was
+used as a proxy for the "age" or "seniority" of a scholar.
 
@@
 
-Geopolitical region was created by binning country code identifiers into the 17 identified United Nation subregions.
+Geopolitical region was created by binning country code identifiers into
+the 17 identified United Nation subregions.
 
@@
 team_author_aff_author <- 28353445
+
 team_author_aff_subject_noNA <- 241269297
@@
 
-WRITE THE THING --> mention max in the text because too crazy for the graph
-
-```{r stats-authors}
+The total number of papers included in the Scopus database at the time
+of this analysis was `r total_papers`. `r total_papers_past1970`
+articles were included past 1970 in the defined article types, which
+included `r distinct_authors_past1970` distinct authors. We then
+filtered the data to include only teams, which was defined as two
+authors from at least two institutions. The total number of papers for
+team projects was `r team_author_aff_papers` and
+`r team_author_aff_author` distinct authors. The data was then
+classified into subject areas by paper, which lead to missing data. The
+final number of papers included was `r team_author_aff_papers_noNA` with
+`r team_author_aff_author_noNA` distinct authors. The dataset was
+curated to include one row per author, paper, and subject area (i.e.,
+long format [@wickham2007]) which included `r team_author_aff_subject_noNA` total rows of data. For analyses and descriptive statistics below, we include sample sizes for clarity.
+
+```{r stats-authors-fig, include = F, fig.cap="The left panel depicts the number of authors included on a paper by subject area, and the right panel demonstrates the number of affiliations by subject area.
+The boxplot shows the median (bold line), the interquartile range (the box), and the minimum to the 90th percentile of the number of authors/affiliations as the range line.
+Normally these plots include the entire range of the data, but these extreme range made the boxplot information unreadable.
+The dots indicate the average number of authors/affiliations for each area with the size of the dot indicating the standard deviation of the statistic.
+Therefore, larger dots indicate more variability in the number of authors and affiliations.
+"}
 temp_graph <- DF$author_stats %>% 
@@
 
-WRITE THE THING --> make this a table to import
+\@ref(fig:stats-authors-fig) displays the number of authors and affiliations by subject area.
+The figure demonstrates that the median number of authors is largest for health sciences, followed by life science, physical sciences, and then social sciences.
+The general pattern of team authorship includes about 2-8 authors, from about 2-4 institutions.
+We used the maximum (i.e., across all subject areas) 90th percentile as our exploratory definition for big team papers after examining the results from this analysis.
+We selected this percentile to have the high of the distribution, but also to be able to include enough papers for analysis across time.
+Therefore, big teams were defined as 11 authors from at least 6 different institutions[^In a previous version of this manuscript, we defined big teams as 10 authors from at least 10 institutions based on our own experiences working with research consortium.
+All definitions are likely subjective, but the definition in this manuscript represents the top 10% of author and affiliations in a large body of papers].
 
@@
 
-```{r big-teams, results = 'asis'}
+```{r big-teams-table, results = 'asis'}
 big_teams_papers <- 968765
@@
 
-kable(DF$paper_stats %>% 
-        arrange(Statistic))
-```
+apa_table(DF$paper_stats %>% 
+        arrange(Statistic), 
+        caption = "Number of Authors and Papers by Subject Area",
+        note = "Papers can be classified into multiple categories.", 
+        align = c("l", rep("c", 5)), 
+        digits = 0)
+```
+
+\@ref(tab:big-teams-table) includes the number of distinct authors and papers for each subject area by overall teams and big teams using our 90th percentile definition.
+The total number of distinct authors for big team papers was `r big_teams_papers` with `r big_teams_authors` distinct authors.
+In RQ2, we split the big team data into small (6-10), medium, and large big team grouping for convenience to display/analyze geopolitical regions.
+The table shows the number of authors and papers for those analyses.
 
@@
 
-```{r}
+For analyzing changes across time, we split the data into regular teams (2-10 authors, 2-5 affiliations) and big teams (as defined above, 11+ authors, 6+ affiliations).
+The number of papers found in Scopus across time for each subject area are displayed in Figure \@ref(paper-time-fig).
+The visual results indicated that the number of regular team papers was increasing the most in physical sciences for all manuscripts, followed by life and health sciences, and the last is social sciences.
+Examining only big teams shows that the rate is also increasing across time.
+All teams appear to start increasing in the 1990s, while big teams do not start increasing off floor effects until past 2000.
+The health and life sciences show the largest increases across time in big teams with the smallest trend in the social sciences.
+
+```{r paper-time-fig, include = F, fig.cap = "The number of manuscripts across time for all team science papers (left) and big team science papers (right)."}
 temp <- DF$author_paper_year %>% 
   filter(SubjectArea != "Multidisciplinary") %>% 
-  filter(Year < 2024)
+  filter(Year < 2024) %>% 
+  mutate(SubjectArea = gsub("Sciences", "", SubjectArea))
 
@@
 p1 <- ggplot(temp %>% 
-         filter(group == "regular"), aes(x = Year, y = Number_Papers, colour = SubjectArea)) + 
+         filter(group == "regular"), 
+         aes(x = Year, y = Number_Papers, 
+             colour = SubjectArea)) + 
   geom_point() + 
   theme_minimal() + 
-  theme(legend.position = "none")
+  scale_color_discrete(name = "Subject Area") + 
+  theme(legend.position = "bottom",
+        axis.text.y = element_text(angle = 45, hjust = 1)) + # Angles the y-axis text
+  ylab("Number of Papers") + 
+  ggtitle("Regular Teams")
 
 p2 <- ggplot(temp %>% 
-         filter(group == "big"), aes(x = Year, y = Number_Papers, colour = SubjectArea)) + 
+         filter(group == "big"), 
+         aes(x = Year, y = Number_Papers, 
+             colour = SubjectArea)) + 
   geom_point() + 
   theme_minimal() + 
-  theme(legend.position = "bottom")
-
-p1 | p2
-```
-
-```{r}
+  scale_color_discrete(name = "Subject Area") + 
+  theme(legend.position = "bottom",
+        axis.text.y = element_text(angle = 45, hjust = 1)) + # Angles the y-axis text
+  ylab(NULL) +  # Removes the y-axis label
+  ggtitle("Big Teams")
+
+combined_plot <- p1 + p2 +
+  plot_layout(guides = "collect") & # Collect shared legend
+  theme(legend.position = "bottom")  # Center the legend at the bottom
+
+combined_plot
+```
+
+```{r rate-estimates-fig, include = F, fig.cap = "Exponential growth rate estimates with 95% confidence intervals."}
+# Initialize the results list
+corr.results <- list()
+
+# Ensure 'group' and 'subjarea' are defined
 group <- unique(temp$group)
 subjarea <- unique(temp$SubjectArea)
-corr.results <- list()
-
-for (group_label in group){
-  for (SA in subjarea){
+
+# Loop through groups and subject areas
+for (group_label in group) {
+  for (SA in subjarea) {
     stuff <- temp %>%
@@
       filter(SubjectArea == SA)
-    # Attempt with nlsLM for more robust optimization
-    fit <- nlsLM(Number_Papers ~ a * exp(r * Year), 
-             start = list(a = 0.2, r = 0.05), 
-             data = stuff)
+
+    if (nrow(stuff) < 3 || any(stuff$Number_Papers <= 0)) {
+      message("Skipping ", group_label, " - ", SA, ": insufficient or invalid data")
+      next
+    }
+
+    # Calculate starting values
+    a_start <- mean(stuff$Number_Papers, na.rm = TRUE)
+    log_y <- log(stuff$Number_Papers)
+    b_start <- coef(lm(log_y ~ stuff$Year))[2]
+
+    tryCatch({
+      fit <- nlsLM(
+        Number_Papers ~ a * exp(b * Year), 
+        data = stuff, 
+        start = list(a = a_start, b = b_start)
+      )
       corr.results[[paste0(group_label, "_", SA)]] <- tidy(fit)
-
+    }, error = function(e) {
+      message("Fit failed for ", group_label, " - ", SA, ": ", e$message)
+    })
   }
@@
     rep(subjarea, each = 2)
-    ))
+    )) %>% 
+  filter(term != "a") %>% 
+  mutate(conf.low = estimate-2*std.error,
+         conf.high = estimate+2*std.error)
 
@@
   theme_minimal() + 
-  geom_linerange(aes(ymin = conf.low, ymax = conf.high))
-```
-
-In the exponential model ￼, the parameters ￼ and ￼ have specific interpretations:
-	1.	Parameter ￼ (Initial Value or Scale):
-	•	￼ represents the initial value or the scaling factor of the exponential function.
-It indicates the starting level of the dependent variable (in this case, Number_Papers) when the Year is at its baseline (e.g., the first year in your dataset or zero if Year is centered).
-	•	A larger value of ￼ would mean a higher starting point for the number of papers.
-	2.	Parameter ￼ (Growth Rate):
-	•	￼ is the growth rate parameter. It indicates how quickly the number of papers grows over time.
-	•	If ￼ is positive, the model shows exponential growth, meaning the number of papers increases over time at an accelerating rate.
-	•	If ￼ is negative, the model would represent exponential decay, suggesting that the number of papers decreases over time.
-	•	The magnitude of ￼ affects the steepness of the growth or decay curve, with larger values (in absolute terms) indicating a more rapid change.
-
-Interpretation Example:
-	•	If ￼ and ￼, then:
-	•	The starting number of papers is about 2 (when Year is zero or the baseline year).
-	•	The number of papers grows by about ￼ per unit of Year, as ￼ implies a growth rate of ￼ per year.
-	•	If ￼, the model would predict a constant number of papers over time, as the exponential term ￼ becomes 1.
-
-Let me know if you’d like help with the interpretation for specific values in your fitted model.
-
-```{r total-authors}
-# updated
-total_authors <- 3047067
-avg_authors <- apa_num(49.30516877182394)
-sd_authors <- apa_num(212.9786134634032)
-min_authors <- 10
-med_authors <- 18
-max_authors <- 5568
-```
-
-The total number of unique authors across all publications was
-`r total_authors`. The mean number of authors per publication was *M* =
-`r avg_authors` (*SD* = `r sd_authors`, *Med* = `r med_authors`) with a
-range of `r min_authors` to `r max_authors`. The median and average
-number of authors by subject area are displayed in Figure
-\@ref(fig:fig-author-year). In general, the average and median number of
-authors increased over time, with the exception of the skew in the
-Physical Sciences. Interestingly, the effect in the Physical Sciences
-appears to be declining toward the general trends seen in other areas in
-the last few decades.
-
-## data split
-
-- "teams": 2-10 authors, 2-4 inst
-- "big ass": 11+, 5+
-
-## RQ1 change over time
-
-pattern of author numbers over time --> just the median because of the data split 
-four panel figure one for each area --> with two sets of dots for teams, "team", and BAT 
-since there's a restriction of range, do we need to calculate based on the proportion of the data or proportion of the range that it could increase
-
-```{r fig-author-year, include = TRUE, fig.cap="Number of authors included on big-team science papers per year by subject area.
-Given the large skew in the data, the left panel presents the median number of authors per manuscript, and the right panel presents the average number of authors per manuscript by year.", fig.width=10, fig.height=6}
-avg_author_time <- 
-  DF$author_time %>% 
-  filter(SubjectArea != "Multidisciplinary") %>% 
-  # filter(Number_Papers >= 3) %>% 
-  mutate(low = (Average_Num_Authors - as.numeric(SD_Num_Authors)), 
-         high = (Average_Num_Authors + as.numeric(SD_Num_Authors)))
-
-# ggplot(avg_author_time, aes(Year, Med_Num_Authors)) + 
-#   theme_classic() + 
-#   geom_point(aes(size = Number_Papers)) + 
-#   geom_point(aes(Year, Average_Num_Authors, color = "red")) + 
-#   #geom_pointrange(aes(ymin = low, ymax = high)) + 
-#   facet_wrap(~SubjectArea) + 
-#   ylab("Average Number of Authors") + 
-#   xlab("Publication Year") + 
-#   theme(legend.position = "bottom") + 
-#   guides(color = "none") + 
-#   scale_size_continuous(name = "Number Papers")
-
-median_authors <- 
-  ggplot(avg_author_time, aes(Year, Med_Num_Authors, color = SubjectArea)) + 
-  theme_classic(base_size = 15) + 
-  geom_point() + 
-    ylab("Median Number of Authors") + 
-    xlab("Publication Year")
-
-mean_authors <- 
-  ggplot(avg_author_time, aes(Year, Average_Num_Authors, color = SubjectArea)) + 
-  theme_classic(base_size = 15) + 
-  geom_point() + 
-    ylab("Average Number of Authors") + 
-    xlab("Publication Year")
-
-median_authors + 
-  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
-  mean_authors + 
-  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
-  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
-
-ggsave(filename = "figure/figure_3_num_authors.png", width = 10, height = 6)
-```
-
-## RQ4: Author Diversity Statistics
+  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
+                width = .2) + 
+  ylab("Rate Estimate") + 
+  xlab("Subject Area") + 
+  scale_color_discrete(name = "Team Size", 
+                       labels = c("Big", "Regular")) + 
+  theme(legend.position = "bottom") + 
+  geom_hline(yintercept = 0)
+```
+
+Using the `minpack.lm` library [CITE ME], we calculated the exponential rate of growth for regular teams and big teams, and these results are shown in \@ref(fig:rate-estimates-fig).
+All growth rate confidence intervals excluded zero, indicating an exponential increase in the number of team papers over time.
+Big team growth rates were always higher than their regular team counterparts, but the 95% confidence intervals for the growth estimate overlapped for all statistics.
+Therefore, the growth trends, while visually appearing to be different, were likely similar for each subject area and team size when examined by estimating exponential growth statistics.
+
+## RQ2: Diversity Statistics
 
@@
 higher numbers mean longer careers. To analyze trends over time, we
-calculated the average career length for each publication (i.e., average
-author career lengths to create one score for each paper) and analyzed a
+calculated the average career length for each publication (i.e., averaging author career lengths to create one score for each paper) and analyzed a
 regression analysis using career length to predict year of publication.
@@
 each hypothesis.
+
+### Edit me
 
@@
 -   four panel figure for subject area by total team, "team", BAT
-- just in general people are having to publish much younger than we used to so here's how to view that
+-   just in general people are having to publish much younger than we
+    used to so here's how to view that
 
@@
 The data has been filtered to at least 10 publications in a year for this graph.", fig.width=10, fig.height=6}
-temp <- ggplot(DF$career_time %>% 
+ggplot(DF$career_time %>% 
          filter(SubjectArea != "Multidisciplinary") %>% 
          filter(num_papers >= 10) %>% 
-         filter(Year < 2024), 
-       aes(Year, avg_career, color = SubjectArea)) +
+         filter(Year < 2024) %>% 
+         mutate(Team = factor(Team, 
+                              levels = c("Regular", "Big"))), 
+       aes(Year, avg_career, color = Team)) +
   theme_classic(base_size = 15) + 
@@
   # geom_point() + 
-  # facet_wrap(~SubjectArea) + 
+  facet_wrap(~SubjectArea) + 
   theme(legend.position = "bottom") + 
@@
   xlab("Year of Publication") + 
-  scale_color_brewer(palette = "Spectral", name = "Subject Area") +
+  scale_color_brewer(palette = "Dark2", name = "Subject Area") +
   guides(size = "none")  
   #scale_size_continuous(name = "Number Papers")
-
-suppressWarnings(suppressMessages(temp))
 
@@
 
-We used the same analyses using number of publications to represent diversity instead of career length. An increasing slope over time indicates that
-individuals who are publishing more are more represented in BTS over
-time (i.e., increasing numbers of scholars with higher publication
-rates), while a negative slope indicates more researchers with less
-publications. A positive slope for the standard deviation of publication
-metrics indicates increasing variance over time (i.e., more diversity in
-the individual publication rates), while a negative slope would indicate
-less diversity in researchers over time. While publication rates do not
-represent value as a researcher, they are often used in hiring and
-promotion decisions, and we used this variable as a proxy to gauge the
-diversity in scholars represented in big teams. As shown in Figure
-\@ref(fig:fig-heatmap) publication metrics were generally negative for
-the average publication metrics, indicating more scholars over time with
-lower numbers of publications with the strongest effects in Health and
-Social Sciences. The variability of publication counts was not
-significant for the Life Sciences but was negative for the Physical
-Sciences (less variability over time) and positive for Social and Health
-Sciences (more variability and over time). This result indicates that
-the Physical Sciences are trending toward scholars with less
-publications but also less diverse in number of publications, while the
-Health and Social Sciences see more diversity in publication counts and
-less published scholars overall.
+We used the same analyses using number of publications to represent
+diversity instead of career length. An increasing slope over time
+indicates that individuals who are publishing more are more represented
+in BTS over time (i.e., increasing numbers of scholars with higher
+publication rates), while a negative slope indicates more researchers
+with less publications. A positive slope for the standard deviation of
+publication metrics indicates increasing variance over time (i.e., more
+diversity in the individual publication rates), while a negative slope
+would indicate less diversity in researchers over time. While
+publication rates do not represent value as a researcher, they are often
+used in hiring and promotion decisions, and we used this variable as a
+proxy to gauge the diversity in scholars represented in big teams. As
+shown in Figure \@ref(fig:fig-heatmap) publication metrics were
+generally negative for the average publication metrics, indicating more
+scholars over time with lower numbers of publications with the strongest
+effects in Health and Social Sciences. The variability of publication
+counts was not significant for the Life Sciences but was negative for
+the Physical Sciences (less variability over time) and positive for
+Social and Health Sciences (more variability and over time). This result
+indicates that the Physical Sciences are trending toward scholars with
+less publications but also less diverse in number of publications, while
+the Health and Social Sciences see more diversity in publication counts
+and less published scholars overall.
 
@@
 
-for time:
- teams versus big teams combining results
- separate panel of the big teams separated (not by time)
+for time: teams versus big teams combining results separate panel of the
+big teams separated (not by time)
 
@@
 
-In this investigation, we explored the publication rates, areas, and researchers involved in BTS publications.
-Over a half-million articles were published in nearly 15,000 journals since 1970 that qualified as BTS articles.
-The areas of publication were aligned to cancer and genetics research in medicine and oncology for Health and Life Sciences, physics and chemistry for the Physical Sciences, and psychology for the Social Sciences.
-All areas of research show growth in the number of publications and authors included on manuscripts, replicating previous investigations [@sinatra2015; @wuchty2007; @hunter2008].
-
-Our investigation expands previous research by additionally focusing on diversity in seniority of authors and geopolitical affiliation.
-The number of earlier career scholars increased across years, indicating that big teams may be accessible to different types of individuals, not just older, established researchers.
-This result is especially interesting given the publish-or-perish model still present in most institutions, as it may seem that large-scale projects could be a risky choice for non-permanent researchers.
-BTS projects are often slow to publish, there is no guarantee for publication, and incentives are often lower for non-corresponding authors.
-However, with a large team, the distribution of work could imply less effort on individual non-leading members, and research has shown that larger-team publications do receive more citations and appear to have higher impact  [@larivière2015].
-
-In general, it appears that there is a decrease in the average number of publications a researcher has when publishing in a BTS paper over time, mirroring career length results.
-This result is likely attributable to the number of early career scholars joining projects, but also may support increased accessibility for individuals to be involved.
-Globalization, the internet, and the focus on interdisciplinary research are potentially driving forces behind our results, but, hopefully, the results also point to a decline in scientific gatekeeping [@lu2007; @siler2015].
+In this investigation, we explored the publication rates, areas, and
+researchers involved in BTS publications. Over a half-million articles
+were published in nearly 15,000 journals since 1970 that qualified as
+BTS articles. The areas of publication were aligned to cancer and
+genetics research in medicine and oncology for Health and Life Sciences,
+physics and chemistry for the Physical Sciences, and psychology for the
+Social Sciences. All areas of research show growth in the number of
+publications and authors included on manuscripts, replicating previous
+investigations [@sinatra2015; @wuchty2007; @hunter2008].
+
+Our investigation expands previous research by additionally focusing on
+diversity in seniority of authors and geopolitical affiliation. The
+number of earlier career scholars increased across years, indicating
+that big teams may be accessible to different types of individuals, not
+just older, established researchers. This result is especially
+interesting given the publish-or-perish model still present in most
+institutions, as it may seem that large-scale projects could be a risky
+choice for non-permanent researchers. BTS projects are often slow to
+publish, there is no guarantee for publication, and incentives are often
+lower for non-corresponding authors. However, with a large team, the
+distribution of work could imply less effort on individual non-leading
+members, and research has shown that larger-team publications do receive
+more citations and appear to have higher impact [@larivière2015].
+
+In general, it appears that there is a decrease in the average number of
+publications a researcher has when publishing in a BTS paper over time,
+mirroring career length results. This result is likely attributable to
+the number of early career scholars joining projects, but also may
+support increased accessibility for individuals to be involved.
+Globalization, the internet, and the focus on interdisciplinary research
+are potentially driving forces behind our results, but, hopefully, the
+results also point to a decline in scientific gatekeeping [@lu2007;
+@siler2015].
 
@@
 ability to connect across time zones and cultures [@xie2014]. While our
-definition of BTS required at least ten different
-institutional affiliations, we did not filter papers by geopolitical
-region, and thus, a manuscript could rely solely on institutions within
-a single country. The Physical Sciences did not show an increase in
-diversity of regions represented, however, it could be argued that the
-development of large research centers like CERN forced earlier diversity
-than other sciences (i.e., because CERN specifically recruited
-scientists from sponsoring nations). The Life, Health, and Social
-Sciences saw an increase in the number of regions represented with the
-highest increase in the Social Sciences. This result likely corresponds
-with an increased interest in big team science publications in
-psychology [@coles2022; @forscher2022a], and the desire to diversify the
-populations represented in psychological research [@henrich2010;
-@newson2021].
-
-While publications overall are diversifying, we found differences in the representation for first/corresponding authors versus all other authors.
-In general, first authors appear to be less diverse, representing European and North American authors, while other authors include more Asian and African authors.
-These effect sizes were often small, but the inequality persists across years.
-Diverse teams are more likely to have papers with stronger “impact” [@freeman2015; @hinnant2012; @jones2008;
+definition of BTS required at least ten different institutional
+affiliations, we did not filter papers by geopolitical region, and thus,
+a manuscript could rely solely on institutions within a single country.
+The Physical Sciences did not show an increase in diversity of regions
+represented, however, it could be argued that the development of large
+research centers like CERN forced earlier diversity than other sciences
+(i.e., because CERN specifically recruited scientists from sponsoring
+nations). The Life, Health, and Social Sciences saw an increase in the
+number of regions represented with the highest increase in the Social
+Sciences. This result likely corresponds with an increased interest in
+big team science publications in psychology [@coles2022;
+@forscher2022a], and the desire to diversify the populations represented
+in psychological research [@henrich2010; @newson2021].
+
+While publications overall are diversifying, we found differences in the
+representation for first/corresponding authors versus all other authors.
+In general, first authors appear to be less diverse, representing
+European and North American authors, while other authors include more
+Asian and African authors. These effect sizes were often small, but the
+inequality persists across years. Diverse teams are more likely to have
+papers with stronger “impact” [@freeman2015; @hinnant2012; @jones2008;
 @yang2022] with higher citation metrics for more diverse author lists.
@@
 
-The limitations for this research are tied to the curation of the Scopus dataset: the correct author affiliations, the correct author publication information, and the correctly marked geopolitical entity.
-We had planned to analyze educational levels change over time; however, this data was mostly blank within the Scopus archive.
-Scopus is a carefully curated and large dataset, but these limitations must be kept in mind when interpreting the results.
-Publication language diversity was not investigated, and a previous study indicates that most publications in big databases are in English [@albarillo2014].
-Certainly, publications in non-English
-languages would improve the statistics on diversity in scientific
-publishing - but the English language barrier likely exists regardless
-of inclusion in databases [@meneghini2007; @ramírez-castañeda2020].
-
-Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing publications that include earlier career and more diverse scholars.
-These partnerships introduce new challenges to collaboration from interpersonal conflict, infrastructure, incentives, to international political situations [@forscher2022a].
-The implications for retention and promotion processes across a broad span of regions should be explored to improve diversity with the understanding of the differential impact of incentives for participating in big team studies.
+The limitations for this research are tied to the curation of the Scopus
+dataset: the correct author affiliations, the correct author publication
+information, and the correctly marked geopolitical entity. We had
+planned to analyze educational levels change over time; however, this
+data was mostly blank within the Scopus archive. Scopus is a carefully
+curated and large dataset, but these limitations must be kept in mind
+when interpreting the results. Publication language diversity was not
+investigated, and a previous study indicates that most publications in
+big databases are in English [@albarillo2014]. Certainly, publications
+in non-English languages would improve the statistics on diversity in
+scientific publishing - but the English language barrier likely exists
+regardless of inclusion in databases [@meneghini2007;
+@ramírez-castañeda2020].
+
+Big teams can provide high-impact, important research within scientific
+publishing, and this report suggests a promising trend of increasing
+publications that include earlier career and more diverse scholars.
+These partnerships introduce new challenges to collaboration from
+interpersonal conflict, infrastructure, incentives, to international
+political situations [@forscher2022a]. The implications for retention
+and promotion processes across a broad span of regions should be
+explored to improve diversity with the understanding of the differential
+impact of incentives for participating in big team studies.
 
@@
 
-```{=tex}
 \begingroup
@@
 
-```
 ::: {#refs custom-style="Bibliography"}
@@
 
-```{=tex}
 \endgroup
-```
+
 \newpage

### 2025-01-14 manuscript_definition.Rmd
updating with new manuscript information

@@
     \makeatletter
-    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+    \renewcommand{\paragraph}{@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip @plus 0.2ex @minus 0.2ex}%
       {-1em}%
@@
 
-    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+    \renewcommand{\subparagraph}[1]{@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip @plus 0.2ex @minus 0.2ex}%
       {-\z@\relax}%
@@
 var_list <- c("author_stats", "paper_stats", "author_paper_year",
-              "career_time")
+              "career_time", "lm_coefficients")
 
@@
 
-outline:
-
--   what is team science / collaboration
--   research on how it's grown / changed over time?
--   Any research diversification?
-    -   on who is publishing
-    -   on where is represented
--   "big" teams - unanswered question ... people are now using term "big
-    team" but it's not defined - can we define it and see if it's any
-    different or just a product of growth/internet over time?
-
-SAVS NEW VERSION!
-
-Collaboration in scientific endeavors involves multiple researchers at
-(potentially) multiple institutions to communicate and work together to
-advance knowledge in their chosen field. Collaboration can manifest
-uniquely in each project dependent on the skill sets, hypotheses, and
-perspectives of collaborators. One key aspect of collaboration is the
-flexibility allotted as it is shaped by the needs of the project and the
-participants involved.
-
-While collaboration is not new in science, interest in "team science" is
+Scientific discovery has increasingly become a collaborative process,
+and the scale and scope of team science have dramatically expanded in
+recent years [@council2015]. Collaboration in scientific endeavors
+involves multiple researchers at (potentially) multiple institutions to
+communicate and work together to advance knowledge in their chosen
+field(s). Collaboration can manifest uniquely in each project dependent
+on the skill sets, hypotheses, and perspectives of collaborators. One
+key aspect of collaboration is the flexibility allotted as it is shaped
+by the needs of the project and the researcher involved. While
+collaboration is not new in science, interest in "team science" is
 growing as individual researchers seek an interdisciplinary approach to
-research or bring on more students to their project. Unlike general
+research or bring on more students to their project. Team science is
+often defined as groups of researchers with various expertise working
+together to investigate complex problems [@fiore2008]. Unlike general
 collaboration, team science involves structured roles, coordinated
@@
 difficult for individual researchers or one small team to solve
-independently. Team science often brings in some aspect of diversity but
-likely is still very homogenous in several aspects.
-
-The evolution of team science reflects broader shifts in research
-practices, driven by two sources: 1) increasing globalization and
-technology that allows for real-time interdisciplinary research, and 2)
-expanding interest in reproducibility, replication, and generalizability
-[i.e., the credibility movement, @maxwell2015; @nelson2018; @zwaan2018;
+independently.
+
+The movement toward team science reflects demands of modern research to
+answer increasingly complex questions, meet funder and university desire
+for interdisciplinary research, and the desire to increase diversity of
+scientific representation [@council2015]. Further, the evolution of team
+science reflects broader shifts in research practices, driven by two
+sources: 1) increasing globalization and technology that allows for
+real-time interdisciplinary research [@jones2008], and 2) expanding
+interest in reproducibility, replication, and generalizability [i.e.,
+the credibility movement, @maxwell2015; @nelson2018; @zwaan2018;
 @vazire2022]. Technological advances have provided easier ways to
@@
 findings. This form of collaboration has been coined “Big Team Science.”
-
-“Big Team Science” builds on team science by scaling efforts to include
-larger, often globally diverse teams, which requires significant
+Big Team Science (BTS) builds on team science by scaling efforts to
+include larger, often globally diverse teams, which requires significant
 coordination and infrastructure [@coles2022; @forscher2022a;
@@
 
-Generally, the credibility movement appears to have been driven by early
-career researchers [i.e., those who are within five years of their first
-appointment, @maizey2019]; however, there are no large meta-scientific
-investigations on this specific topic to date. The newness of
-large-scale research in many fields could be the culprit for the lack of
-investigation into this area. For example, psychology has had an
-increase in BTS publications like the Open Science Collaboration
-[@opensciencecollaboration2015], Many Labs Collaborations
-[@buttrick2020; @ebersole2016; @ebersole2020; @klein2018; @klein2022;
-@mathur2020; @skorb2020] or the first papers from the Psychological
-Science Accelerator [@bago2022; @buchanan2023; @dorison2022; @jones2021;
+For example, psychology has had an increase in BTS publications like the
+Open Science Collaboration [@opensciencecollaboration2015], Many Labs
+Collaborations [@buttrick2020; @ebersole2016; @ebersole2020; @klein2018;
+@klein2022; @mathur2020; @skorb2020] or the first papers from the
+Psychological Science Accelerator [@bago2022; @buchanan2023;
+@dorison2022; @jones2021;
 @psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
-@moshontz2018; @wang2021]. Generally, the researcher incentive for
-replication and/or involvement in big-team projects was low for three
-reasons. First, journals often prioritize "novel" or new results which
-led to rejection of replication manuscripts and publication bias
-[@franco2014; @hubbard1997; @nosek2012]. Second, the "failure" to
-replicate was often placed on the replication team as "bad science"
-rather than a careful consideration of publication biases and
-(potential) questionable research practices [@klein2022; @maxwell2015].
-Last, why should someone want to spend time and resources on an answer
-we already "know" [@isager2021; @isager2021a]?
-
-However, the success and interest in the large-scale reproducibility
-projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired
-with the meta-scientific publications focusing on researcher practices
-and incentive structures [@silberzahn2018many; @john2012] led to a
-change in journal guidelines and incentives for researchers interested
-in participating in large-scale replication studies [@grahe2014;
-@kidwell2016; @nosek2015; @mayo-wilson2021]. In some fields, the
-replication movement demonstrated that large-scale teams were a
-practical (and publishable) solution to answering research questions in
-generalizable way. The support for Registered Reports, papers accepted
-before the data has been collected [@nosek2014; @stewart2020], has
-allowed researchers to invest in projects that they know should be
-published when the project is complete. Further, the implementation of
-the Transparency and Openness Guidelines [@nosek2015] and the
-Contributor Role Taxonomy (CRediT) system [@allen2019] have pushed
-journals and researchers to promote more open, inclusive publication
-practices.
+@moshontz2018; @wang2021]. The success and interest in the large-scale
+reproducibility projects [@opensciencecollaboration2015;
+@10.7554/eLife.71601], paired with the meta-scientific publications
+focusing on researcher practices and incentive structures
+[@silberzahn2018many; @john2012] led to a change in journal guidelines
+and incentives for researchers interested in participating in
+large-scale studies overall [@grahe2014; @kidwell2016; @nosek2015;
+@mayo-wilson2021]. In some fields, the BTS movement demonstrated that
+large-scale teams were a practical (and publishable) solution to
+answering research questions in generalizable way. The support for
+Registered Reports, papers accepted before the data has been collected
+[@nosek2014; @stewart2020], has allowed researchers to invest in
+projects that they know should be published when the project is
+complete. Further, the implementation of the Transparency and Openness
+Guidelines [@nosek2015] and the Contributor Role Taxonomy (CRediT)
+system [@allen2019] have pushed journals and researchers to promote more
+open, inclusive publication practices.
 
@@
 for BTS studies have provided an incredible wealth of data for the
-scientific community, we do not yet know exactly *who* is involved with,
-and benefits from, the BTS and credibility movement. Publications on BTS
-generally explore challenges, lessons learned, and the need for BTS
+scientific community, we do not yet know exactly how to define BTS -
+which is generally termed "an unusually large number of collaborators"
 [@forscher2022a; @coles2022].
 
-There is no universally agreed-upon definition of BTS, raising questions
-about whether it represents a distinct phenomenon or simply a natural
-extension of team science. Therefore, we originally arbitrarily chose a
-definition for BTS publication which we had decided to be publications
-with at least ten authors at ten different institutions that were
-published in peer-reviewed journals or had posted a full paper
-pre-print. While this definition is a somewhat arbitrary choice, we
-separate this research from research on team science that uses any
-multi-university collaboration as a definition [@jones2008] to focus on
-larger sized teams rather than teams of any size. With at least ten
-institutions, the complexities of infrastructure, resources, tenure and
-promotion policies, ethics review, and more can occur [@forscher2022a].
-Therefore, we believe this choice selects publications that would be
-"big" teams and those potential obstacles.
-
-This manuscript seeks not only to evaluate whether this definition is an
-appropriate fit for BTS but also to explore whether the criteria for
-defining BTS should vary by subject area or evolve over time.
-Understanding these nuances will help clarify whether BTS represents a
-fundamentally new approach to collaboration or a natural progression of
-team science in response to global and technological trends.
-
-We then will examine if there is a true difference between “Team
-Science” and "Big Team Science”. Therefore, the goal of this manuscript
-is to examine both the *publications* and *people* involved in BTS
-projects and “Team Science.” We present descriptive information about
-the publication sources and types of articles to demonstrate large-scale
-research. Next, we examine the individuals involved in BTS and “Team
-Science” for descriptive and predictive purposes. To describe the people
-involved in BTS projects vs “Team Science”, we planned to use types of
-publications from individuals. For predictive statistics, we explored
-the change in diversity of authors over time. It is unclear if the focus
-of de-WEIRDing science has only focused on the representation of the
-research participants or if it has also improved the representation of
-researchers outside of North America and Europe. Last, we examined for a
-change in diversity within first author(s) and the last author across
-time. As hiring and promoting practices often place a heavy weight on
-publications and especially “influential” publications, it becomes
-necessary to critically examine the representation present in authorship
-in BTS and Team Science” projects.
+The lack of formal definition raises questions about whether it
+represents a distinct phenomenon or simply a natural extension of team
+science. These big teams pose unique challenges, including coordinating
+work across diverse time zones, managing conflicts in decision-making,
+and ensuring fair distribution of credit for contributions
+[@cummings2007; @wuchty2007], but also could provide big rewards by
+pooling expertise and increased interdisciplinary funding [@fiore2008].
+This paper seeks to clarify the concept of BTS by first establishing a
+data-driven definition based on publication patterns. With this
+quantitative distinction in place, we analyze publication trends over
+time to assess the trajectories of both traditional team science and
+BTS. Furthermore, we investigate the diversity of authors involved in
+these collaborations to explore whether shifts in the scientific
+landscape—such as efforts to de-WEIRD science and the expansion of
+collaborative opportunities—have influenced who participates in team
+science and BTS. By synthesizing insights from the growth and
+diversification of team science, this paper seeks to critically examine
+the emergence of big teams. Specifically, it aims to explore whether big
+teams are quantitatively different from traditional collaboration models
+with the following research questions.
 
@@
     values, what should define big team science versus team science?
-  - Question 1A: What number of authors and institutional affiliations
-    should designate the differences between team science and big team
-    science?
-  - Question 1B: Using the definition from 1A, are there changes in the
-    number of publications over time?
+    -   Question 1A: What number of authors and institutional
+        affiliations should designate the differences between team
+        science and big team science?
+    -   Question 1B: Using the definition from 1A, are there changes in
+        the number of publications over time?
 -   Research Question 2: How has the diversity of those involved in big
@@
 curated to include one row per author, paper, and subject area (i.e.,
-long format [@wickham2007]) which included `r team_author_aff_subject_noNA` total rows of data. For analyses and descriptive statistics below, we include sample sizes for clarity.
+long format [@wickham2007]) which included
+`r team_author_aff_subject_noNA` total rows of data. For analyses and
+descriptive statistics below, we include sample sizes for clarity.
 
@@
 The dots indicate the average number of authors/affiliations for each area with the size of the dot indicating the standard deviation of the statistic.
-Therefore, larger dots indicate more variability in the number of authors and affiliations.
-"}
+Therefore, larger dots indicate more variability in the number of authors and affiliations."}
 temp_graph <- DF$author_stats %>% 
@@
 
-\@ref(fig:stats-authors-fig) displays the number of authors and affiliations by subject area.
-The figure demonstrates that the median number of authors is largest for health sciences, followed by life science, physical sciences, and then social sciences.
-The general pattern of team authorship includes about 2-8 authors, from about 2-4 institutions.
-We used the maximum (i.e., across all subject areas) 90th percentile as our exploratory definition for big team papers after examining the results from this analysis.
-We selected this percentile to have the high of the distribution, but also to be able to include enough papers for analysis across time.
-Therefore, big teams were defined as 11 authors from at least 6 different institutions[^In a previous version of this manuscript, we defined big teams as 10 authors from at least 10 institutions based on our own experiences working with research consortium.
-All definitions are likely subjective, but the definition in this manuscript represents the top 10% of author and affiliations in a large body of papers].
-
-NEED TO RUN ALL TEAMS SUBJECT AREA GRAPH
+\@ref(fig:stats-authors-fig) displays the number of authors and
+affiliations by subject area. The figure demonstrates that the median
+number of authors is largest for health sciences, followed by life
+science, physical sciences, and then social sciences. The general
+pattern of team authorship includes about 2-8 authors, from about 2-4
+institutions. We used the maximum (i.e., across all subject areas) 90th
+percentile as our exploratory definition for big team papers after
+examining the results from this analysis. We selected this percentile to
+have the high of the distribution, but also to be able to include enough
+papers for analysis across time. Therefore, big teams were defined as 11
+authors from at least 6 different institutions[\^In a previous version
+of this manuscript, we defined big teams as 10 authors from at least 10
+institutions based on our own experiences working with research
+consortium. All definitions are likely subjective, but the definition in
+this manuscript represents the top 10% of author and affiliations in a
+large body of papers].
+
+NEED TO RUN ALL TEAMS SUBJECT AREA
 
@@
 
-\@ref(tab:big-teams-table) includes the number of distinct authors and papers for each subject area by overall teams and big teams using our 90th percentile definition.
-The total number of distinct authors for big team papers was `r big_teams_papers` with `r big_teams_authors` distinct authors.
-In RQ2, we split the big team data into small (6-10), medium, and large big team grouping for convenience to display/analyze geopolitical regions.
-The table shows the number of authors and papers for those analyses.
+\@ref(tab:big-teams-table) includes the number of distinct authors and
+papers for each subject area by overall teams and big teams using our
+90th percentile definition. The total number of distinct authors for big
+team papers was `r big_teams_papers` with `r big_teams_authors` distinct
+authors. In RQ2, we split the big team data into small (11-49), medium
+(50-99), and large big team (100+) groupings for convenience to
+display/analyze geopolitical regions. The table shows the number of
+authors and papers for those analyses.
 
@@
 
-For analyzing changes across time, we split the data into regular teams (2-10 authors, 2-5 affiliations) and big teams (as defined above, 11+ authors, 6+ affiliations).
-The number of papers found in Scopus across time for each subject area are displayed in Figure \@ref(paper-time-fig).
-The visual results indicated that the number of regular team papers was increasing the most in physical sciences for all manuscripts, followed by life and health sciences, and the last is social sciences.
-Examining only big teams shows that the rate is also increasing across time.
-All teams appear to start increasing in the 1990s, while big teams do not start increasing off floor effects until past 2000.
-The health and life sciences show the largest increases across time in big teams with the smallest trend in the social sciences.
+For analyzing changes across time, we split the data into team science
+projects (2-10 authors, 2-5 affiliations) and BTS projects (as defined
+above, 11+ authors, 6+ affiliations). The number of papers found in
+Scopus across time for each subject area are displayed in Figure
+\@ref(paper-time-fig). The visual results indicated that the number of
+team science papers was increasing the most in physical sciences for all
+manuscripts, followed by life and health sciences, and the last is
+social sciences. Examining only BTS projects shows that the rate is also
+increasing across time. All teams appear to start increasing in the
+1990s, while BTS projects do not start increasing off floor effects
+until past 2000. The health and life sciences show the largest increases
+across time in big teams with the smallest trend in the social sciences.
 
@@
   ylab("Number of Papers") + 
-  ggtitle("Regular Teams")
+  ggtitle("Team Science Projects")
 
@@
   ylab(NULL) +  # Removes the y-axis label
-  ggtitle("Big Teams")
+  ggtitle("BTS Projects")
 
@@
   scale_color_discrete(name = "Team Size", 
-                       labels = c("Big", "Regular")) + 
+                       labels = c("BTS", "Team Science")) + 
   theme(legend.position = "bottom") + 
@@
 
-Using the `minpack.lm` library [CITE ME], we calculated the exponential rate of growth for regular teams and big teams, and these results are shown in \@ref(fig:rate-estimates-fig).
-All growth rate confidence intervals excluded zero, indicating an exponential increase in the number of team papers over time.
-Big team growth rates were always higher than their regular team counterparts, but the 95% confidence intervals for the growth estimate overlapped for all statistics.
-Therefore, the growth trends, while visually appearing to be different, were likely similar for each subject area and team size when examined by estimating exponential growth statistics.
+Using the `minpack.lm` library [@elzhov2023], we calculated the
+exponential rate of growth for team science and BTS projects, and these
+results are shown in \@ref(fig:rate-estimates-fig). All growth rate
+confidence intervals excluded zero, indicating an exponential increase
+in the number of team papers over time. BTS growth rates were
+always higher than their team science counterparts, but the 95%
+confidence intervals for the growth estimate overlapped for all
+statistics. Therefore, the growth trends, while visually appearing to be
+different, were likely similar for each subject area and team size when
+examined by estimating exponential growth statistics.
 
@@
 
+```{r fig-career, include = TRUE,  warning = FALSE, message = FALSE, fig.cap = "Average career length for big-team science authors.
+Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year.
+The data has been filtered to at least 10 publications in a year for this graph.", fig.width=10, fig.height=6}
+ggplot(DF$career_time %>% 
+         filter(SubjectArea != "Multidisciplinary") %>% 
+         filter(num_papers >= 10) %>% 
+         filter(Year < 2024) %>% 
+         mutate(Team = factor(Team, 
+                              levels = c("Regular", "Big"),
+                              labels = c("Team Science", "BTS"))), 
+       aes(Year, avg_career, color = Team)) +
+  theme_classic(base_size = 15) + 
+  geom_point(aes(size = sd_career)) +
+  facet_wrap(~SubjectArea) + 
+  theme(legend.position = "bottom") + 
+  ylab("Average Career Length") +
+  xlab("Year of Publication") + 
+  scale_color_manual(values = c("#CA0020", "#0571B0"), name = "Team Size") + # Red and Blue from RdBu ends
+  guides(size = "none")
+  #scale_size_continuous(name = "Number Papers")
+
+ggsave(filename = "figure/figure_4_career.png", width = 10, height = 6)
+```
+
 Figure \@ref(fig:fig-career) portrays the average career length for
-authors involved in BTS publications across years. Career length was
-defined as the year of first publication minus the current year, and
-higher numbers mean longer careers. To analyze trends over time, we
-calculated the average career length for each publication (i.e., averaging author career lengths to create one score for each paper) and analyzed a
-regression analysis using career length to predict year of publication.
-In order to show variance between individuals, we calculated the
-standard deviation of career length for each publication and used this
-variance as an additional predictor.
-
-Negative career length slopes would indicate more young scholars in
+authors involved in team science and BTS projects over time.
+Career length was defined as the year of first publication minus the current year, and higher numbers mean longer careers.
+The general pattern for team science and BTS projects is a decrease in average career length over time.
+However, it appears that, in at least the last two decades, BTS projects average a longer career length than team science projects.
+This trend is visually consistent across all four subject areas examined.
+
+To analyze these trends over time, we calculated the average career length for each publication (i.e., averaging author career lengths to create one score for each paper) and analyzed a regression analysis using career length to predict year of
+publication. In order to show variance between individuals, we
+calculated the standard deviation of career length for each publication
+and used this variance as an additional predictor. Negative career length slopes would indicate more young scholars in
 later years (i.e., lower average career length as time increases).
@@
 
-### Edit me
+```{r lm-coefficients}
+sample_size <- 1000000
+DF$lm_coefficients$r2_low <- DF$lm_coefficients$r2_high <- NA
+
+# add upper and lower Rsquared values
+for (i in 1:nrow(DF$lm_coefficients)){
+  temp <- ci.R2(R2 = DF$lm_coefficients$rsquared[i], 1, sample_size)
+  DF$lm_coefficients$r2_low[i] <- temp$Lower.Conf.Limit.R2
+  DF$lm_coefficients$r2_high[i] <- temp$Upper.Conf.Limit.R2
+}
+
+# create upper and lower CIs for each coefficient
+DF$lm_coefficients <- DF$lm_coefficients %>% 
+  mutate(b_avg_low = b_avg_effect - qt(.025, sample_size, lower.tail = F)*se_avg_effect,
+         b_avg_high = b_avg_effect + qt(.025, sample_size, lower.tail = F)*se_avg_effect,
+         b_std_low = b_std_effect - qt(.025, sample_size, lower.tail = F)*se_std_effect,
+         b_std_high = b_std_effect - qt(.025, sample_size, lower.tail = F)*se_std_effect)
+
+```
+
+### Edit me starting here ###
 
@@
 
-```{r fig-career, include = TRUE,  warning = FALSE, message = FALSE, fig.cap = "Average career length for big-team science authors.
-Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year.
-The data has been filtered to at least 10 publications in a year for this graph.", fig.width=10, fig.height=6}
-ggplot(DF$career_time %>% 
-         filter(SubjectArea != "Multidisciplinary") %>% 
-         filter(num_papers >= 10) %>% 
-         filter(Year < 2024) %>% 
-         mutate(Team = factor(Team, 
-                              levels = c("Regular", "Big"))), 
-       aes(Year, avg_career, color = Team)) +
-  theme_classic(base_size = 15) + 
-  geom_point(aes(size = sd_career)) +
-  # geom_point() + 
-  facet_wrap(~SubjectArea) + 
-  theme(legend.position = "bottom") + 
-  ylab("Average Career Length") +
-  xlab("Year of Publication") + 
-  scale_color_brewer(palette = "Dark2", name = "Subject Area") +
-  guides(size = "none")  
-  #scale_size_continuous(name = "Number Papers")
-
-ggsave(filename = "figure/figure_4_career.png", width = 10, height = 6)
-```
-
-```{r career-results, include = FALSE}
-
+```{r career-results-teams, include = FALSE}
 label <- c("Physical", "Social", "Health", "Life")
@@
 r2_values <- c(0.465446, 0.254312, 0.303781, 0.350923)
-sample_size <- total_num
+sample_size <- total_num <- 10000000
 
@@
 graph_data$analysis <- "Career"
-
-# ggplot(graph_data, aes(label, estimate)) + 
-#   geom_point() +
-#   geom_pointrange(aes(ymin = low, ymax = high)) +
-#   theme_classic() + 
-#   facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
-#   geom_hline(yintercept = 0) + 
-#   coord_flip() + 
-#   xlab("Subject Area") + 
-#   ylab("")
+```
+
+```{r career-results-bts, include = FALSE}
+label <- c("Physical", "Social", "Health", "Life")
+avg_b_values <- c(-0.692014, -0.365357, -0.451827, -0.508350)
+avg_se_values <- c(0.002727, 0.005525, 0.001348, 0.001786)
+sd_b_values <- c(-0.265538, -0.097108, -0.096730, -0.013958)
+sd_se_values <- c(0.007018, 0.013409, 0.003451, 0.004523)
+r2_values <- c(0.465446, 0.254312, 0.303781, 0.350923)
+sample_size <- total_num
+
+r2_low <- 1:length(r2_values)
+r2_high <- 1:length(r2_values)
+for (i in 1:length(r2_values)){
+  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
+  r2_low[i] <- temp$Lower.Conf.Limit.R2
+  r2_high[i] <- temp$Upper.Conf.Limit.R2
+}
+
+graph_data_bts <- data.frame(
+  "label" = label,
+  "estimate" = avg_b_values,
+  "type" = "Coefficient",
+  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
+  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
+    bind_rows(
+    data.frame(
+    "label" = label,
+    "estimate" = sd_b_values,
+    "type" = "SD Coefficient",
+    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
+    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
+    ) %>% 
+  bind_rows(
+    data.frame(  
+      "label" = label, 
+      "estimate" = r2_values,
+      "type" = "Effect Size",
+      "low" = r2_low,
+      "high" = r2_high)
+  )
+
+graph_data_bts$type <- factor(
+  graph_data_bts$type, 
+  levels = c("Coefficient", "SD Coefficient", "Effect Size")
+)
+
+graph_data_bts$analysis <- "Career"
 ```
@@
 
-```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region.
+```{r fig-heatmap}
+
+, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical 
+within the region.
 Each square represents a *b* value or the slope of the predictor (x-axis) onto the dependent variable (each panel), with the exception of the bottom row which is the effect size of each regression analysis $R^2$.
@@
 The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.
-Non-significant results are indicated with NS on the plot.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6}
+Non-significant results are indicated with NS on the plot.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6
+
 graph_overall <- graph_data %>% 

### 2025-05-13 manuscript_definition.Rmd
update the author years

@@
 ---
-title             : "Who does big team science?"
+title             : "What defines big team science?"
 shorttitle        : "Big Team Science"
@@
 library(latex2exp)
-library(patchwork)
 library(broom)
@@
   "M Coefficient " = b[M],
+  "Coefficient" = b,
   "SD Coefficient" = b[SD],
-  "Effect Size" = R^2,
-  "Coefficient" = b
+  "Effect Size" = R^2
+)
+
+strip_labels <- c(
+  "M Coefficient" = "b[M]",
+  "SD Coefficient" = "b[SD]",
+  "Effect Size" = "R^2",
+  "Coefficient" = "b"
 )
@@
 var_list <- c("author_stats", "paper_stats", "author_paper_year",
-              "career_time", "lm_coefficients")
+              "career_time", "lm_coefficients", "geo_country")
 
@@
 key aspect of collaboration is the flexibility allotted as it is shaped
-by the needs of the project and the researcher involved. While
+by the needs of the project and the researchers involved. While
 collaboration is not new in science, interest in "team science" is
@@
 The movement toward team science reflects demands of modern research to
-answer increasingly complex questions, meet funder and university desire
+answer increasingly complex questions, meet funder and university desires
 for interdisciplinary research, and the desire to increase diversity of
@@
 researchers to form new ways to increase the rigor in scientific
-endeavors. As the movement has adapted throughout the last decade, the
-idea to form larger, more diverse teams and to include participants from
-varied backgrounds has become even more a goal to not only increase the
-credibility but the generalizability and reliability of scientific
-findings. This form of collaboration has been coined “Big Team Science.”
+endeavors.
+Throughout the last decade, the credibility movement has pushed for larger, more diverse teams and the involvement of participants from varied backgrounds.
+This shift in teams and participants focuses on increasing credibility, generalizability, and reliability of scientific findings.
+This form of collaboration has been coined “Big Team Science.”
 Big Team Science (BTS) builds on team science by scaling efforts to
@@
 
-For example, psychology has had an increase in BTS publications like the
+For example, psychology has seen an increase in BTS publications like the
 Open Science Collaboration [@opensciencecollaboration2015], Many Labs
@@
 
-NEED TO RUN ALL TEAMS SUBJECT AREA
+--NEED TO RUN ALL TEAMS SUBJECT AREA----> set up in chunk 14
 
@@
   mutate(SubjectArea = gsub("Sciences", "", SubjectArea))
-
-# temp %>% 
-#   group_by(SubjectArea, Year, group) %>% 
-#   summarize(n = n())
 
@@
   xlab("Year of Publication") + 
-  scale_color_manual(values = c("#CA0020", "#0571B0"), name = "Team Size") + # Red and Blue from RdBu ends
+  scale_color_manual(values = c("#D55E00", "#0072B2"), name = "Team Size") + # Red and Blue from RdBu ends
   guides(size = "none")
@@
 scholars). Figure \@ref(fig:fig-heatmap) displays the results for all
-regression analyses to compare coefficient strength across and within
-each hypothesis.
+regression analyses.
 
@@
 
-### Edit me starting here ###
-
-All values for these analyses were different from zero. The slopes for
+```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopoliticalwithin the region.
+Each square represents a *b* value or the slope of the predictor (x-axis) onto the dependent variable (each panel), with the exception of the bottom row which is the effect size of each regression analysis $R^2$.
+Slopes included both the overall value of the predictor ($b$, $b_M$) and the standard deviation of the predictor over time ($b_{SD}$).
+The color of the square represents the strength of the predictor.
+The top figure represents all results together for comparison across analyses.
+The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.
+Non-significant results are indicated with NS on the plot.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6}
+
+graphDF <- DF$lm_coefficients %>% 
+  select(Discipline, b_avg_effect, b_std_effect, type, rsquared, coefficient) %>% 
+  pivot_longer(cols = c(b_avg_effect, b_std_effect, rsquared)) %>% 
+    left_join(
+    DF$lm_coefficients %>% 
+  select(Discipline, type, coefficient, r2_high:b_std_high) %>% 
+  pivot_longer(cols = c(-Discipline, -type, -coefficient)) %>% 
+  mutate(ci_name = ifelse(
+    grepl("low", name), "low", "high"
+  ),
+  name = gsub("r2_low|r2_high", "rsquared", name),
+  name = gsub("b_avg_low|b_avg_high", "b_avg_effect", name),
+  name = gsub("b_std_low|b_std_high", "b_std_effect", name)),
+  by = c("Discipline", "type", "coefficient", "name")
+  ) %>% 
+  mutate(name = ifelse(
+    coefficient == "diversity" & name != "rsquared", "b_effect", name
+  )) %>% 
+  mutate(name = factor(name, 
+                levels = c("b_avg_effect", "b_effect", 
+                           "b_std_effect", "rsquared"),
+                labels = c("M Coefficient", "Coefficient", 
+                           "SD Coefficient", "Effect Size"))) %>%
+  rename(Estimate = value.x,
+         Regression = coefficient,
+         CI = value.y,
+         Size = type,
+         Coefficient = name) %>% 
+  mutate(Discipline = gsub(" Sciences", "", Discipline)) %>% 
+  pivot_wider(
+    id_cols = c(Discipline, Size, Regression, Coefficient, Estimate),
+    names_from = ci_name,
+    values_from = CI
+  ) %>%
+  mutate(heat_label = ifelse(
+    low < .00001 & high > .00001, "NS", ""
+  )) %>% 
+  mutate(Size = factor(Size, 
+                       levels = c("regular", "big"),
+                       labels = c("Regular", "Big")))
+
+career_heat <- ggplot(graphDF %>% 
+                        filter(Regression == "career"), 
+       aes(x = Discipline, y = Size, fill = Estimate)) + 
+  geom_tile(color = "white") +  
+  geom_text(aes(label = format(round(Estimate, 4), digits = 4))) +  
+  facet_grid(~ Coefficient, labeller = labeller(Coefficient = as_labeller(strip_labels, label_parsed))) +
+  theme_minimal(base_size = 15) +
+  scale_fill_distiller(palette = "RdBu", direction = 1) + 
+  theme(
+    # axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
+    panel.border = element_rect(color = "black", fill = NA, size = 0.5)  # Add borders between facets
+  ) + 
+  xlab(NULL) +
+  ylab("Career Length")
+
+pub_heat <- ggplot(graphDF %>% 
+                        filter(Regression == "pub_count"), 
+       aes(x = Discipline, y = Size, fill = Estimate)) + 
+  geom_tile(color = "white") +  
+  geom_text(aes(label = format(round(Estimate, 4), digits = 4))) +  
+  facet_grid(~ Coefficient, labeller = labeller(Coefficient = as_labeller(strip_labels, label_parsed))) + 
+  theme_minimal(base_size = 15) +
+  scale_fill_distiller(palette = "PuOr", direction = 1) + 
+  theme(
+    # axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
+    panel.border = element_rect(color = "black", fill = NA, size = 0.5)  # Add borders between facets
+  ) +
+  xlab(NULL) + 
+  ylab("Pub Count")
+
+diversity_heat <- ggplot(graphDF %>% 
+                        filter(Regression == "diversity") %>% 
+                          filter(!is.na(Estimate)) %>% 
+                          mutate(Coefficient = droplevels(Coefficient)), 
+       aes(x = Discipline, y = Size, fill = Estimate)) + 
+  geom_tile(color = "white") +  
+  geom_text(aes(label = format(round(Estimate, 4), digits = 4))) +  
+  facet_grid(~ Coefficient, labeller = labeller(Coefficient = as_labeller(strip_labels, label_parsed))) +
+  theme_minimal(base_size = 15) +
+  scale_fill_distiller(palette = "BrBG", direction = 1) + 
+  theme(
+    # axis.text.x = element_text(angle = 15, hjust = 1),  # Rotate x-axis labels for readability
+    panel.border = element_rect(color = "black", fill = NA, size = 0.5)  # Add borders between facets
+  ) +
+  ylab("Geopolitical Diversity")
+
+career_heat / pub_heat / diversity_heat
+
+ggsave(filename = "figure/figure_5_heatmap.png", width = 12, height = 10, units = "in")
+```
+
+The average career length of authors on a manuscript was negatively related to time, indicating that career lengths are decreasing over time (i.e., more earlier career individuals included on manuscripts).
+The standard deviation of career length was also negatively related to publication year suggesting that the variability of authors is similarly decreasing toward authors who are less senior.
+These patterns were consistent across regular sized and big teams, and all coefficients were different from zero.
+
+- overall coefficients not zero 
+- big versus regular are not different
+- pattern across disciplines - differences within them
+
+All values for career length were different from our defined confidence interval zero cut off (i.e., .00001). The slopes for
 the average career length were negative for all four subject areas,
 indicating a trend toward younger scientist involvement over time for
-each area, with the strongest effect in the Physical Sciences. The
+each area in both regular and big teams. The confidence intervals for
+
+, with the strongest effect in the Physical Sciences.
+
+The
 coefficient for variability in career length was also negative for each
@@
 
-```{r career-results-teams, include = FALSE}
-label <- c("Physical", "Social", "Health", "Life")
-avg_b_values <- c(-0.692014, -0.365357, -0.451827, -0.508350)
-avg_se_values <- c(0.002727, 0.005525, 0.001348, 0.001786)
-sd_b_values <- c(-0.265538, -0.097108, -0.096730, -0.013958)
-sd_se_values <- c(0.007018, 0.013409, 0.003451, 0.004523)
-r2_values <- c(0.465446, 0.254312, 0.303781, 0.350923)
-sample_size <- total_num <- 10000000
-
-r2_low <- 1:length(r2_values)
-r2_high <- 1:length(r2_values)
-for (i in 1:length(r2_values)){
-  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
-  r2_low[i] <- temp$Lower.Conf.Limit.R2
-  r2_high[i] <- temp$Upper.Conf.Limit.R2
-}
-
-graph_data <- data.frame(
-  "label" = label,
-  "estimate" = avg_b_values,
-  "type" = "Coefficient",
-  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
-  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
-    bind_rows(
-    data.frame(
-    "label" = label,
-    "estimate" = sd_b_values,
-    "type" = "SD Coefficient",
-    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
-    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
-    ) %>% 
-  bind_rows(
-    data.frame(  
-      "label" = label, 
-      "estimate" = r2_values,
-      "type" = "Effect Size",
-      "low" = r2_low,
-      "high" = r2_high)
-  )
-
-graph_data$type <- factor(
-  graph_data$type, 
-  levels = c("Coefficient", "SD Coefficient", "Effect Size")
-)
-
-graph_data$analysis <- "Career"
-```
-
-```{r career-results-bts, include = FALSE}
-label <- c("Physical", "Social", "Health", "Life")
-avg_b_values <- c(-0.692014, -0.365357, -0.451827, -0.508350)
-avg_se_values <- c(0.002727, 0.005525, 0.001348, 0.001786)
-sd_b_values <- c(-0.265538, -0.097108, -0.096730, -0.013958)
-sd_se_values <- c(0.007018, 0.013409, 0.003451, 0.004523)
-r2_values <- c(0.465446, 0.254312, 0.303781, 0.350923)
-sample_size <- total_num
-
-r2_low <- 1:length(r2_values)
-r2_high <- 1:length(r2_values)
-for (i in 1:length(r2_values)){
-  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
-  r2_low[i] <- temp$Lower.Conf.Limit.R2
-  r2_high[i] <- temp$Upper.Conf.Limit.R2
-}
-
-graph_data_bts <- data.frame(
-  "label" = label,
-  "estimate" = avg_b_values,
-  "type" = "Coefficient",
-  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
-  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
-    bind_rows(
-    data.frame(
-    "label" = label,
-    "estimate" = sd_b_values,
-    "type" = "SD Coefficient",
-    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
-    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
-    ) %>% 
-  bind_rows(
-    data.frame(  
-      "label" = label, 
-      "estimate" = r2_values,
-      "type" = "Effect Size",
-      "low" = r2_low,
-      "high" = r2_high)
-  )
-
-graph_data_bts$type <- factor(
-  graph_data_bts$type, 
-  levels = c("Coefficient", "SD Coefficient", "Effect Size")
-)
-
-graph_data_bts$analysis <- "Career"
-```
-
-```{r pub-results, include = FALSE}
-
-label <- c("Physical", "Social", "Health", "Life")
-avg_b_values <- c(0.004248, -0.027315, -0.021713, -0.009466)
-avg_se_values <- c(0.000179, 0.001073, 0.000211, 0.000213)
-sd_b_values <- c(-0.021552, 0.016810, 0.010139, -0.000378)
-sd_se_values <- c(0.000241, 0.000921, 0.000198, 0.000235)
-r2_values <- c(0.135965, 0.035968, 0.048999, 0.030748)
-sample_size <- total_num
-
-r2_low <- 1:length(r2_values)
-r2_high <- 1:length(r2_values)
-for (i in 1:length(r2_values)){
-  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
-  r2_low[i] <- temp$Lower.Conf.Limit.R2
-  r2_high[i] <- temp$Upper.Conf.Limit.R2
-}
-
-graph_data_2 <- data.frame(
-  "label" = label,
-  "estimate" = avg_b_values,
-  "type" = "Coefficient",
-  "low" = avg_b_values - qt(.025, sample_size, lower.tail = F)*avg_se_values,
-  "high" = avg_b_values + qt(.025, sample_size, lower.tail = F)*avg_se_values) %>% 
-    bind_rows(
-    data.frame(
-    "label" = label,
-    "estimate" = sd_b_values,
-    "type" = "SD Coefficient",
-    "low" = sd_b_values - qt(.025, sample_size, lower.tail = F)*sd_se_values,
-    "high" = sd_b_values + qt(.025, sample_size, lower.tail = F)*sd_se_values) 
-    ) %>% 
-  bind_rows(
-    data.frame(  
-      "label" = label, 
-      "estimate" = r2_values,
-      "type" = "Effect Size",
-      "low" = r2_low,
-      "high" = r2_high)
-  )
-
-graph_data_2$type <- factor(
-  graph_data_2$type, 
-  levels = c("Coefficient", "SD Coefficient", "Effect Size")
-)
-
-graph_data_2$analysis <- "Publication"
-
-# ggplot(graph_data, aes(label, estimate)) + 
-#   geom_point() +
-#   geom_pointrange(aes(ymin = low, ymax = high)) +
-#   theme_classic() + 
-#   facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
-#   geom_hline(yintercept = 0) + 
-#   coord_flip() + 
-#   xlab("Subject Area") + 
-#   ylab("")
-```
-
-```{r diversity-results, include = FALSE}
-
-label <- c("Physical", "Social", "Health", "Life")
-b_values <- c(0.002175, 0.033175, 0.016824, 0.008029)
-se_values <- c(0.002578, 0.006039, 0.001150, 0.001476)
-r2_values <- c(0.000006, 0.001542, 0.000708, 0.000170)
-sample_size <- total_num
-
-r2_low <- 1:length(r2_values)
-r2_high <- 1:length(r2_values)
-for (i in 1:length(r2_values)){
-  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
-  r2_low[i] <- temp$Lower.Conf.Limit.R2
-  r2_high[i] <- temp$Upper.Conf.Limit.R2
-}
-
-graph_data_3 <- data.frame(
-  "label" = label,
-  "estimate" = b_values,
-  "type" = "Coefficient",
-  "low" = b_values - qt(.025, sample_size, lower.tail = F)*se_values,
-  "high" = b_values + qt(.025, sample_size, lower.tail = F)*se_values) %>% 
-  bind_rows(
-    data.frame(  
-      "label" = label, 
-      "estimate" = r2_values,
-      "type" = "Effect Size",
-      "low" = r2_low,
-      "high" = r2_high)
-  )
-
-graph_data_3$type <- factor(
-  graph_data_3$type,
-  levels = c("Coefficient", "Effect Size")
-)
-
-graph_data_3$analysis <- "Regions"
-
-# ggplot(graph_data, aes(label, estimate)) + 
-#   geom_point() +
-#   geom_pointrange(aes(ymin = low, ymax = high)) +
-#   theme_classic() + 
-#   facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels_2))) + 
-#   geom_hline(yintercept = 0) + 
-#   coord_flip() + 
-#   xlab("Subject Area") + 
-#   ylab("")
-```
-
-```{r fig-heatmap}
-
-, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical 
-within the region.
-Each square represents a *b* value or the slope of the predictor (x-axis) onto the dependent variable (each panel), with the exception of the bottom row which is the effect size of each regression analysis $R^2$.
-Slopes included both the overall value of the predictor ($b$, $b_M$) and the standard deviation of the predictor over time ($b_{SD}$).
-The color of the square represents the strength of the predictor.
-The top figure represents all results together for comparison across analyses.
-The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.
-Non-significant results are indicated with NS on the plot.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6
-
-graph_overall <- graph_data %>% 
-  bind_rows(graph_data_2) %>% 
-  bind_rows(graph_data_3) %>% 
-  mutate(type = factor(type, levels = c("Effect Size", "SD Coefficient", "Coefficient"))) %>% 
-  mutate(Estimate = estimate) %>% 
-  mutate(heat_label = ifelse(
-    low < .00001 & high > .00001, "NS", ""
-  ))
-
-heat_results <- ggplot(graph_overall, aes(label, type, fill = Estimate)) + 
-  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
-  coord_fixed() + 
-  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b$"))) + 
-  ylab("") + 
-  xlab("") + 
-  facet_wrap(~analysis) + 
-  theme_classic(base_size = 15) + 
-  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
-        legend.position = "right", 
-        legend.key.size = unit(.75, 'cm')) + 
-  scale_fill_distiller(palette = "Spectral") + 
-  geom_text(aes(label=heat_label))
-
-# heat_results
-
-heat_results_1 <- ggplot(graph_overall %>% 
-                           filter(analysis == "Career"), 
-                         aes(label, type, fill = Estimate)) + 
-  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
-  coord_fixed() + 
-  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b_M$"))) + 
-  ylab("") + 
-  xlab("") + 
-  theme_classic(base_size = 15) + 
-  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
-        legend.position = "right") + 
-  scale_fill_distiller(palette = "RdBu") + 
-  ggtitle("Career")  + 
-  geom_text(aes(label=heat_label))
-
-heat_results_2 <- ggplot(graph_overall %>% 
-                           filter(analysis == "Publication"), 
-                         aes(label, type, fill = Estimate)) + 
-  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
-  coord_fixed() + 
-  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b_M$"))) + 
-  ylab("") + 
-  xlab("") + 
-  theme_classic(base_size = 15) + 
-  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
-        legend.position = "right") + 
-  scale_fill_distiller(palette = "PuOr") + 
-  ggtitle("Publication") + 
-  geom_text(aes(label=heat_label))
-
-heat_results_3 <- ggplot(graph_overall %>% 
-                           filter(analysis == "Regions"), 
-                         aes(label, type, fill = Estimate)) + 
-  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
-  coord_fixed() + 
-  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b$"))) + 
-  ylab("") + 
-  xlab("") + 
-  theme_classic(base_size = 15) + 
-  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
-        legend.position = "right") + 
-  scale_fill_distiller(palette = "PiYG") +
-  ggtitle("Regions") + 
-  geom_text(aes(label=heat_label))
-
-layout <- "
-AAA
-BCD
-"
-suppressMessages(suppressWarnings(heat_results + 
-  heat_results_1 + heat_results_2 + heat_results_3 + 
-  plot_layout(design = layout)))
-
-ggsave(filename = "figure/figure_5_heatmap.png", width = 10, height = 6, units = "in")
-```
+### Edit me starting here ###
 
@@
   group_by(affiliation_tag_country) %>% 
-  summarize(count = sum(count),
-            count_all = sum(all_count))
+  summarize(count = sum(big),
+            count_all = sum(regular))
 
@@
   theme(plot.title = element_text(hjust = 0.5)) + 
-  theme(legend.position = "none") + 
+  guides(fill = "none") +
 tree + ggtitle("Big-Team Publication Mosiac Chart") + 
@@
   guides(fill = "none") + 
-bin_country_all + ggtitle("All Publications Map") + 
+bin_country_all + ggtitle("Regular Teams Publications Map") + 
   theme(plot.title = element_text(hjust = 0.5)) + 
   guides(fill = "none") + 
-tree_all + ggtitle("All Publications Mosiac Chart") + 
+tree_all + ggtitle("Regular Teams Publications Mosiac Chart") + 
   theme(plot.title = element_text(hjust = 0.5)) + 
-  guides(fill = "none") + 
+  theme(legend.position = "none") +  
   plot_layout(ncol = 2, 

### 2025-05-13 manuscript_definition.Rmd
add new files for finalized data

@@
 
---NEED TO RUN ALL TEAMS SUBJECT AREA----> set up in chunk 14
-
 ```{r big-teams-table, results = 'asis'}
@@
 p1 <- ggplot(temp %>% 
-         filter(group == "regular"), 
+         filter(team_size == "regular"), 
          aes(x = Year, y = Number_Papers, 
@@
 p2 <- ggplot(temp %>% 
-         filter(group == "big"), 
+         filter(team_size == "big"), 
          aes(x = Year, y = Number_Papers, 
@@
 # Ensure 'group' and 'subjarea' are defined
-group <- unique(temp$group)
+group <- unique(temp$team_size)
 subjarea <- unique(temp$SubjectArea)
@@
     stuff <- temp %>%
-      filter(group == group_label) %>%
+      filter(team_size == group_label) %>%
       filter(SubjectArea == SA)

### 2025-06-03 manuscript_definition.Rmd
updating figures, references, and discussionn

@@
 
-    Significance statement: This work is the first to examine big team science authorship (i.e., 10+ authors) across millions of published works.
-Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing numbers of publications that increasingly represent earlier career and varied scholars.
-The number of geopolitical entities for researcher affiliation is increasing over time, showing the results of globalization and the ability to connect across time zones and cultures.
-While publications are generally diversifying, we did not yet find equality in the representation for first or corresponding authors.
-First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
+    Significance statement: This study is the first large-scale, data-driven analysis of authorship in Big Team Science (BTS), defined here as collaborations with 11 or more authors across six or more institutions.
+Drawing on millions of published works across four scientific domains, we show that BTS has grown rapidly in recent years and increasingly includes early-career researchers and contributors from a broader range of geopolitical regions.
+However, inclusion in BTS is not equally distributed.
+While author lists are becoming more globally diverse overall, leadership roles—particularly first and corresponding authorships, remain disproportionately concentrated in high-income countries, especially in Europe and North America.
+These findings highlight both the promise and limitations of BTS as a vehicle for global, inclusive science, underscoring the need for structural reforms to ensure equity in recognition and participation.
 
@@
   Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (https://osf.io/f2dtr) but then was updated with access to the Scopus database for a broader picture of BTS projects (https://osf.io/fheun).
+After review, we updated the manuscript to reflect that the definition of big team science is unclear, and focused on a data-driven definition to explore our research questions.
 
@@
 bibliography: references.bib
-appendix          :
-  - "appendix.Rmd"
 
@@
 var_list <- c("author_stats", "paper_stats", "author_paper_year",
-              "career_time", "lm_coefficients", "geo_country")
+              "career_time", "lm_coefficients", "geo_country",
+              "effect_size_gp")
 
@@
 The movement toward team science reflects demands of modern research to
-answer increasingly complex questions, meet funder and university desires
-for interdisciplinary research, and the desire to increase diversity of
+answer complex questions, meet funder and university desires for
+interdisciplinary research, and the desire to increase diversity of
 scientific representation [@council2015]. Further, the evolution of team
@@
 researchers to form new ways to increase the rigor in scientific
-endeavors.
-Throughout the last decade, the credibility movement has pushed for larger, more diverse teams and the involvement of participants from varied backgrounds.
-This shift in teams and participants focuses on increasing credibility, generalizability, and reliability of scientific findings.
-This form of collaboration has been coined “Big Team Science.”
-Big Team Science (BTS) builds on team science by scaling efforts to
-include larger, often globally diverse teams, which requires significant
-coordination and infrastructure [@coles2022; @forscher2022a;
-@stewart2017]. BTS projects and organizations organize extensive
-collaborations, intentionally incorporating diverse populations and
-perspectives into research. This large-scale approach enhances the
-reliability and generalizability of findings by integrating varied
-methodologies and viewpoints, leading to more robust and inclusive
-scientific outcomes. BTS organizations often pool extensive networks of
-researchers and resources, aiming to tackle grand scientific challenges
-that would be difficult to address within smaller or less coordinated
-collaborations. By having both collaborations that span across the globe
-and subfields of research areas, age groups, and education levels should
-help to drive science in the path of better materials, reliability,
-generalizability, and more robust sample sizes (when necessary) in a
-study [@auspurg2021; @nosek2014method; @lebel2018].
-
-For example, psychology has seen an increase in BTS publications like the
-Open Science Collaboration [@opensciencecollaboration2015], Many Labs
-Collaborations [@buttrick2020; @ebersole2016; @ebersole2020; @klein2018;
-@klein2022; @mathur2020; @skorb2020] or the first papers from the
-Psychological Science Accelerator [@bago2022; @buchanan2023;
+endeavors. Throughout the last decade, the credibility movement has
+pushed for larger, more diverse teams and the involvement of
+participants from varied backgrounds. This shift in teams and
+participants focuses on increasing credibility, generalizability, and
+reliability of scientific findings. This form of collaboration has been
+coined "Big Team Science." Big Team Science (BTS) builds on team science
+by scaling efforts to include larger, often globally diverse teams,
+which requires significant coordination and infrastructure [@coles2022;
+@forscher2022a; @stewart2017]. BTS projects and organizations organize
+extensive collaborations, intentionally incorporating diverse
+populations and perspectives into research. This large-scale approach
+enhances the reliability and generalizability of findings by integrating
+varied methodologies and viewpoints, leading to more robust and
+inclusive scientific outcomes. BTS organizations often pool extensive
+networks of researchers and resources, aiming to tackle grand scientific
+challenges that would be difficult to address within smaller or less
+coordinated collaborations. By having both collaborations that span
+across the globe and subfields of research areas, age groups, and
+education levels should help to drive science in the path of better
+materials, reliability, generalizability, and more robust sample sizes
+in a study [@auspurg2021; @nosek2014method; @lebel2018].
+
+For example, psychology has seen an increase in BTS publications like
+the Open Science Collaboration [@opensciencecollaboration2015], Many
+Labs Collaborations [@buttrick2020; @ebersole2016; @ebersole2020;
+@klein2018; @klein2022; @mathur2020; @skorb2020] or the first papers
+from the Psychological Science Accelerator [@bago2022; @buchanan2023;
 @dorison2022; @jones2021;
@@
 Psychological Science Accelerator [@moshontz2018], ManyBabies
-(<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and
-DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these
-issues by recruiting research labs from all over the globe to provide
-diversity in geographic, linguistic, and researcher representation.
-Publications have examined the global understanding of morality, face
-processing, COVID-19 information signaling, and more [@bago2022;
-@dorison2022; @jones2021;
+(<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>),
+DRAGNet (<https://dragnetglobal.weebly.com/>), and IceCube
+(<https://icecube.wisc.edu/>) can begin to tackle these issues by
+recruiting research labs from all over the globe to provide diversity in
+geographic, linguistic, and researcher representation. Publications have
+examined the global understanding of morality, face processing, COVID-19
+information signaling, and more [@bago2022; @dorison2022; @jones2021;
 @psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
@@
 these collaborations to explore whether shifts in the scientific
-landscape—such as efforts to de-WEIRD science and the expansion of
-collaborative opportunities—have influenced who participates in team
+landscape, such as efforts to de-WEIRD science and the expansion of
+collaborative opportunities, have influenced who participates in team
 science and BTS. By synthesizing insights from the growth and
@@
         the number of publications over time?
--   Research Question 2: How has the diversity of those involved in big
-    team science versus team science changed over time?
+-   Research Question 2: How has the diversity of those involved in team
+    science and big team science changed over time?
 
@@
 based on four subject areas present in the Scopus database: Physical
-Sciences, Health Sciences, Social Sciences, and Life Sciences. We
-filtered the database to include articles, articles in press, business
-articles, conference papers, data papers, preprints, and surveys using
-Elsevier's classification system. This project was supported by access
-to the Scopus database through the International Center for the Study of
-Research.
+Sciences, Health Sciences, Social Sciences, and Life Sciences. We used
+the subject area split to ensure one field did not dominate BTS
+definitions and determine differences in trends across sub-areas of
+science. We filtered the database to include articles, articles in
+press, business articles, conference papers, data papers, preprints, and
+surveys using Elsevier's classification system. This project was
+supported by access to the Scopus database through the International
+Center for the Study of Research.
 
@@
 
-### RQ2: Author Diversity Statistics
-
-#### Seniority
+### RQ2: Seniority
 
@@
 
-#### Geopolitical Region
+### RQ2: Geopolitical Region
 
@@
 long format [@wickham2007]) which included
-`r team_author_aff_subject_noNA` total rows of data. For analyses and
-descriptive statistics below, we include sample sizes for clarity.
-
-```{r stats-authors-fig, include = F, fig.cap="The left panel depicts the number of authors included on a paper by subject area, and the right panel demonstrates the number of affiliations by subject area.
+`r team_author_aff_subject_noNA` total rows of data.
+
+```{r fig-stats-authors, include = TRUE, fig.cap="The left panel depicts the number of authors included on a paper by subject area, and the right panel demonstrates the number of affiliations by subject area.
 The boxplot shows the median (bold line), the interquartile range (the box), and the minimum to the 90th percentile of the number of authors/affiliations as the range line.
@@
 The dots indicate the average number of authors/affiliations for each area with the size of the dot indicating the standard deviation of the statistic.
-Therefore, larger dots indicate more variability in the number of authors and affiliations."}
+Therefore, larger dots indicate more variability in the number of authors and affiliations.", fig.width = 10, fig.height = 6}
 temp_graph <- DF$author_stats %>% 
@@
 auth_plot | aff_plot
-```
-
-\@ref(fig:stats-authors-fig) displays the number of authors and
+
+ggsave(filename = "figure/figure_1_number.png", width = 10, height = 6)
+```
+
+Figure \@ref(fig:fig-stats-authors) displays the number of authors and
 affiliations by subject area. The figure demonstrates that the median
@@
 pattern of team authorship includes about 2-8 authors, from about 2-4
-institutions. We used the maximum (i.e., across all subject areas) 90th
-percentile as our exploratory definition for big team papers after
-examining the results from this analysis. We selected this percentile to
-have the high of the distribution, but also to be able to include enough
-papers for analysis across time. Therefore, big teams were defined as 11
-authors from at least 6 different institutions[\^In a previous version
-of this manuscript, we defined big teams as 10 authors from at least 10
-institutions based on our own experiences working with research
-consortium. All definitions are likely subjective, but the definition in
-this manuscript represents the top 10% of author and affiliations in a
-large body of papers].
-
-```{r big-teams-table, results = 'asis'}
+institutions. We used the maximum value (i.e., across all subject areas)
+for the 90th percentile as our exploratory definition for big team
+papers after examining the results from this analysis. We selected this
+percentile to have the high of the distribution, but also to be able to
+include enough papers for analysis across time. Therefore, big teams
+were defined as 11 authors from at least 6 different institutions.[^1]
+
+[^1]: In a previous version of this manuscript, we defined big teams as
+    10 authors from at least 10 institutions based on our own
+    experiences working within a research consortium. All definitions
+    are likely subjective, but the definition in this manuscript
+    represents the top 10% of author and affiliations in a large body of
+    papers.
+
+```{r echo = FALSE}
 big_teams_papers <- 968765
 big_teams_authors <- 4541369
-
-apa_table(DF$paper_stats %>% 
-        arrange(Statistic), 
-        caption = "Number of Authors and Papers by Subject Area",
-        note = "Papers can be classified into multiple categories.", 
-        align = c("l", rep("c", 5)), 
-        digits = 0)
-```
-
-\@ref(tab:big-teams-table) includes the number of distinct authors and
-papers for each subject area by overall teams and big teams using our
-90th percentile definition. The total number of distinct authors for big
-team papers was `r big_teams_papers` with `r big_teams_authors` distinct
-authors. In RQ2, we split the big team data into small (11-49), medium
-(50-99), and large big team (100+) groupings for convenience to
-display/analyze geopolitical regions. The table shows the number of
-authors and papers for those analyses.
+```
+
+Supplemental Table \@ref(tab:big-teams-table) includes the number of
+distinct authors and papers for each subject area by overall teams and
+big teams using our 90th percentile definition. The total number of
+distinct authors for big team papers was `r big_teams_papers` with
+`r big_teams_authors` distinct authors. In RQ2, we split the big team
+data into small (11-49), medium (50-99), and large big team (100+)
+groupings for convenience to display/analyze geopolitical regions. The
+table shows the number of authors and papers for those analyses.
 
 ## RQ1B: Changes over Time
-
-SEE IF YOU CAN GET ALL THE NUMBERS SOME ARE MISSING
 
@@
 Scopus across time for each subject area are displayed in Figure
-\@ref(paper-time-fig). The visual results indicated that the number of
-team science papers was increasing the most in physical sciences for all
-manuscripts, followed by life and health sciences, and the last is
+\@ref(fig:fig-paper-time). The visual results indicated that the number
+of team science papers was increasing the most in physical sciences for
+all manuscripts, followed by life and health sciences, and the last is
 social sciences. Examining only BTS projects shows that the rate is also
@@
 
-```{r paper-time-fig, include = F, fig.cap = "The number of manuscripts across time for all team science papers (left) and big team science papers (right)."}
+```{r fig-paper-time, include = TRUE, fig.cap = "The number of manuscripts across time for all team science papers (left) and big team science papers (right).", fig.width = 10, fig.height = 6}
 temp <- DF$author_paper_year %>% 
   filter(SubjectArea != "Multidisciplinary") %>% 
-  filter(Year < 2024) %>% 
+  filter(Year < 2025) %>% 
   mutate(SubjectArea = gsub("Sciences", "", SubjectArea))
@@
   ylab("Number of Papers") + 
-  ggtitle("Team Science Projects")
+  ggtitle("Team Science Projects") +
+  theme(legend.title = element_text(size = 15),
+    legend.text = element_text(size = 12))
 
@@
   ylab(NULL) +  # Removes the y-axis label
-  ggtitle("BTS Projects")
+  ggtitle("BTS Projects") + 
+  theme(legend.title = element_text(size = 15),
+    legend.text = element_text(size = 15))
 
@@
 combined_plot
-```
-
-```{r rate-estimates-fig, include = F, fig.cap = "Exponential growth rate estimates with 95% confidence intervals."}
+
+ggsave(filename = "figure/figure_2_acrosstime.png", width = 10, height = 6)
+```
+
+Using the `minpack.lm` library [@elzhov2023], we calculated the
+exponential rate of growth for team science and BTS projects, and these
+results are shown in Supplemental Figure \@ref(fig:rate-estimates-fig). All growth rate
+confidence intervals excluded zero, indicating an exponential increase
+in the number of team papers over time. BTS growth rates were always
+higher than their team science counterparts, but the 95% confidence
+intervals for the growth estimate overlapped for all statistics.
+Therefore, the growth trends, while visually appearing to be different,
+were likely similar for each subject area and team size when examined by
+estimating exponential growth statistics.
+
+```{r echo = FALSE, include=FALSE}
 # Initialize the results list
@@
   mutate(conf.low = estimate-2*std.error,
-         conf.high = estimate+2*std.error)
+         conf.high = estimate+2*std.error) %>% 
+  mutate(group = factor(group, 
+                        levels = c("regular", "big"),
+                        labels = c("Team Science", "BTS")))
 
@@
   xlab("Subject Area") + 
-  scale_color_discrete(name = "Team Size", 
-                       labels = c("BTS", "Team Science")) + 
+  scale_color_manual(values = c("#D55E00", "#0072B2"), name = "Team Size") + 
   theme(legend.position = "bottom") + 
   geom_hline(yintercept = 0)
-```
-
-Using the `minpack.lm` library [@elzhov2023], we calculated the
-exponential rate of growth for team science and BTS projects, and these
-results are shown in \@ref(fig:rate-estimates-fig). All growth rate
-confidence intervals excluded zero, indicating an exponential increase
-in the number of team papers over time. BTS growth rates were
-always higher than their team science counterparts, but the 95%
-confidence intervals for the growth estimate overlapped for all
-statistics. Therefore, the growth trends, while visually appearing to be
-different, were likely similar for each subject area and team size when
-examined by estimating exponential growth statistics.
-
-## RQ2: Diversity Statistics
-
-### Seniority
+
+ggsave(filename = "figure/figure_3_growth.png", width = 10, height = 6)
+```
+
+## RQ2: Seniority
 
@@
          filter(num_papers >= 10) %>% 
-         filter(Year < 2024) %>% 
+         filter(Year < 2025) %>% 
          mutate(Team = factor(Team, 
@@
 Figure \@ref(fig:fig-career) portrays the average career length for
-authors involved in team science and BTS projects over time.
-Career length was defined as the year of first publication minus the current year, and higher numbers mean longer careers.
-The general pattern for team science and BTS projects is a decrease in average career length over time.
-However, it appears that, in at least the last two decades, BTS projects average a longer career length than team science projects.
-This trend is visually consistent across all four subject areas examined.
-
-To analyze these trends over time, we calculated the average career length for each publication (i.e., averaging author career lengths to create one score for each paper) and analyzed a regression analysis using career length to predict year of
-publication. In order to show variance between individuals, we
-calculated the standard deviation of career length for each publication
-and used this variance as an additional predictor. Negative career length slopes would indicate more young scholars in
-later years (i.e., lower average career length as time increases).
-Positive career length slopes would indicate older scholars in later
-years (i.e., higher average career length as time increases). Negative
-career variance slopes imply that variability decreases over the years,
-so the average career length is more homogeneous. Positive career length
-slopes imply that variability increases over the years, so the average
-career length is varied across individuals (i.e., different stages of
-scholars). Figure \@ref(fig:fig-heatmap) displays the results for all
-regression analyses.
+authors involved in team science and BTS projects over time. Career
+length was defined as the year of first publication minus the current
+year, and higher numbers mean longer careers. The general pattern for
+team science and BTS projects is a decrease in average career length
+over time. However, it appears that, in at least the last two decades,
+BTS projects average a longer career length than team science projects.
+This trend is visually consistent across all four subject areas
+examined.
+
+### Career Length
+
+To analyze these trends over time, we calculated the average career
+length for each publication (i.e., averaging author career lengths to
+create one score for each paper) and analyzed a regression analysis
+using career length to predict year of publication. In order to show
+variance between individuals, we calculated the standard deviation of
+career length for each publication and used this variance as an
+additional predictor. Negative career length slopes would indicate more
+young scholars in later years (i.e., lower average career length as time
+increases). Positive career length slopes would indicate older scholars
+in later years (i.e., higher average career length as time increases).
+Negative career variance slopes imply that variability decreases over
+the years, so the average career length is more homogeneous. Positive
+career length slopes imply that variability increases over the years, so
+the average career length is varied across individuals (i.e., different
+stages of scholars). Figure \@ref(fig:fig-heatmap) displays the results
+for all regression analyses.
 
@@
          b_std_low = b_std_effect - qt(.025, sample_size, lower.tail = F)*se_std_effect,
-         b_std_high = b_std_effect - qt(.025, sample_size, lower.tail = F)*se_std_effect)
+         b_std_high = b_std_effect + qt(.025, sample_size, lower.tail = F)*se_std_effect)
 
@@
 The top figure represents all results together for comparison across analyses.
-The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.
-Non-significant results are indicated with NS on the plot.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6}
+The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6}
 
@@
   mutate(Size = factor(Size, 
-                       levels = c("regular", "big"),
-                       labels = c("Regular", "Big")))
+                       levels = c("big", "regular"),
+                       labels = c("BTS", "TS")))
 
@@
 
-The average career length of authors on a manuscript was negatively related to time, indicating that career lengths are decreasing over time (i.e., more earlier career individuals included on manuscripts).
-The standard deviation of career length was also negatively related to publication year suggesting that the variability of authors is similarly decreasing toward authors who are less senior.
-These patterns were consistent across regular sized and big teams, and all coefficients were different from zero.
-
-- overall coefficients not zero 
-- big versus regular are not different
-- pattern across disciplines - differences within them
-
-All values for career length were different from our defined confidence interval zero cut off (i.e., .00001). The slopes for
-the average career length were negative for all four subject areas,
-indicating a trend toward younger scientist involvement over time for
-each area in both regular and big teams. The confidence intervals for
-
-, with the strongest effect in the Physical Sciences.
-
-The
-coefficient for variability in career length was also negative for each
-of the four subject areas with the highest in the Physical Sciences and
-lowest in the Life Sciences. This result indicates a decrease in the
-variability of career lengths over time, likely from two sources: 1)
-more publications with more authors, thus, lowering variance
-estimations, and 2) more young scholars overall. The effect sizes for
-this analysis were surprisingly large ranging from $R^2$ = .25 to .47.
-All values and their confidence intervals can be found on our OSF page.
-
--   four panel figure for subject area by total team, "team", BAT
--   just in general people are having to publish much younger than we
-    used to so here's how to view that
-
-### Edit me starting here ###
+As shown in Figure \@ref(fig:fig-heatmap), all estimated slopes were
+negative, indicating that author teams are, on average, composed of
+younger scholars over time. The slope of the mean career length ($b_M$)
+and variability in career length ($b_{SD}$) was consistently negative
+across disciplines and team sizes, with all estimates falling outside
+the defined null threshold (i.e., $|b| > 0.00001$). Most subject areas
+showed significantly different slopes within their respective team size,
+as evidenced by non-overlapping 95% confidence intervals for both $b_M$
+and $b_{SD}$. The Physical Sciences exhibited the steepest declines in
+both average career length and its variability (e.g., $b_M$ = -0.7134,
+$b_{SD}$ = -0.2202 for big teams), suggesting a sharp shift toward
+younger and more uniformly early-career author teams. In comparison,
+life sciences showed a slightly smaller shift toward earlier career
+scholars with less variability, followed by health and social sciences.
+The only non-significant difference was found between life and social
+sciences in big teams for author career variability.
+
+These findings suggest a widespread trend toward younger, less-senior
+authorship over time. However, this trend was more pronounced in team
+science-sized teams than in BTS teams. In all four subject areas, team
+science teams showed steeper declines in both the average and
+variability of author career length, as reflected by significantly
+different slopes with no overlapping confidence intervals. This finding
+indicates that regular teams are more strongly influenced by the
+increasing participation of earlier-career researchers, whereas big
+teams exhibit the same general trend but to a lesser extent. Effect
+sizes were substantial across all models, with $R^2$ values ranging from
+.2818 to .4910. The largest effect was observed in the Physical Sciences
+for big teams ($R^2$ = .4910), reflecting the strongest association
+between author career stage and publication timing. Together, these
+results indicate that the shift toward younger, more early-career author
+teams is widespread but not uniform across disciplines, and that team
+size plays a meaningful role in moderating the strength of these
+temporal trends. Full model estimates and confidence intervals are
+available on the OSF repository.
+
+### Publication Count
 
@@
 used in hiring and promotion decisions, and we used this variable as a
-proxy to gauge the diversity in scholars represented in big teams. As
-shown in Figure \@ref(fig:fig-heatmap) publication metrics were
-generally negative for the average publication metrics, indicating more
-scholars over time with lower numbers of publications with the strongest
-effects in Health and Social Sciences. The variability of publication
-counts was not significant for the Life Sciences but was negative for
-the Physical Sciences (less variability over time) and positive for
-Social and Health Sciences (more variability and over time). This result
-indicates that the Physical Sciences are trending toward scholars with
-less publications but also less diverse in number of publications, while
-the Health and Social Sciences see more diversity in publication counts
-and less published scholars overall.
+proxy to gauge the diversity in scholars represented in BTS teams.
+
+All slopes for both the average ($b_M$) and standard deviation
+($b_{SD}$) of publication count were significantly different from zero,
+indicating meaningful change over time in the types of researchers
+contributing to publications across subject areas and team sizes (see
+Figure \@ref(fig:fig-heatmap)). Most subject areas differed
+significantly from one another within their team size, with the
+exception of Health Sciences and Physical Sciences for team science
+teams, whose $b_M$ values overlapped in their confidence intervals.
+Across the remaining comparisons, Life Sciences showed the steepest
+decline in average publication count over time for regular teams ($b_M$
+= -0.0588), suggesting a shift toward including authors with fewer
+publications. In contrast, the smallest change in publication count was
+observed in Physical Sciences for big teams ($b_M$ = -0.0005),
+indicating some stability scholar publication count when examining
+diversity. Standard deviation slopes ($b_{SD}$) were generally low in
+magnitude, with both positive and negative values depending on subject
+area. This suggests some variation in the diversity of publication rates
+across disciplines, with no uniform pattern of increasing or decreasing
+diversity.
+
+All subject areas showed significant differences between BTS and team
+science teams in both $b_M$ and $b_{SD}$, as indicated by
+non-overlapping confidence intervals. Team science teams consistently
+exhibited stronger negative slopes for average publication count than
+BTS teams, reflecting a more pronounced trend toward authors with fewer
+publications appearing over time. This suggests that smaller teams are
+increasingly composed of researchers with lower overall publication
+counts, whereas BTS teams show a more muted shift. Effect sizes for
+these models were smaller than those observed for career length, with
+$R^2$ values ranging from .0335 to .0977. The strongest association was
+observed in the Physical Sciences for big teams ($R^2$ = .0977), though
+all models showed low-to-moderate predictive ability.
 
@@
 
-```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.
+```{r fig-map-both-calc, include = FALSE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.
 The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right.
@@
 
-Author geopolitical region is displayed in Figure
-\@ref(fig:fig-map-both). Big team publications appear to be led by North
-America and Western Europe, while all publications are led by North
-America and East Asia. To understand the change in representation
-diversity, we examined if the number of regions in a publication is
-predicted by the year of publication. Increasing diversity would be
-represented by a positive slope, while decreasing diversity would be
-represented by a negative slope. As shown in Figure
-\@ref(fig:fig-heatmap), the Physical Sciences do not show a trend of
-change in representation, while all other sciences showed a positive
-effect increasing in the number of geopolitical regions authors
-represent on publications.
+Geographic patterns in authorship differed notably between BTS and team
+science publications, as shown in the publication maps and mosaic charts
+(Supplemental Figure \@ref(fig:fig-map-both)). BTS publications were overwhelmingly
+concentrated in high-income countries, particularly the United States,
+Western European nations (e.g., Germany, the United Kingdom, France, and
+the Netherlands), and East Asian countries (e.g., China, Japan, and
+South Korea). In contrast, team science publications showed broader
+geographic distribution, with relatively higher representation from
+Latin America (e.g., Brazil, Mexico), South and Southeast Asia (e.g.,
+India, Pakistan, Indonesia), and parts of Africa and the Middle East.
+While both team types were led by traditionally defined Global North
+institutions, the mosaic charts revealed that team science teams
+included a more diverse range of countries contributing at moderate
+levels. These patterns suggest that although BTS involves international
+collaborations, it remains more centralized in historically dominant
+research regions, whereas team science may offer relatively greater
+global inclusivity at a smaller scale.
+
+To understand the change in representation diversity, we examined if the
+number of regions in a publication is predicted by the year of
+publication. Increasing diversity would be represented by a positive
+slope, while decreasing diversity would be represented by a negative
+slope. All slopes predicting geopolitical diversity over time were
+significantly different from zero, indicating small but non-zero changes
+in the number of regions represented on publications across disciplines
+and team types. Additionally, all slopes differed significantly between
+BTS and team science publications, suggesting distinct patterns in the
+evolution of international collaboration. Within BTS publications, Life
+Sciences and Social Sciences showed statistically indistinguishable
+trends in regional diversity over time, as did Social Sciences and
+Health Sciences. In contrast, all other within-BTS comparisons differed
+significantly. For team science publications, all four disciplines
+showed significantly different slopes, although the magnitudes of these
+differences were relatively small. Overall, the results suggest modest
+increases in geopolitical diversity in most disciplines, with a small
+decline observed only in Physical Sciences within BTS publications ($b$
+= -0.0129). Despite small effect sizes (all $R^2 < .012$), the
+consistent differences between BTS and team science teams point to
+structural differences in how global participation is evolving across
+large-scale versus more traditional collaborations.
 
@@
 
-updated binning:
-
--   teams: 2-10 authors, 2-5 inst
-    -   first and last author only versus everyone else
--   big ass teams: 6+ affs
-    -   small: 11-49
-        -   first three plus last versus everyone else
-    -   medium: 50-99
-        -   first five plus last versus everyone else
-    -   large: 100+
-        -   first 10 plus last versus everyone else
-
-for time: teams versus big teams combining results separate panel of the
-big teams separated (not by time)
-
-```{r small-effects, warning = FALSE}
-DF$small_first_gp <- DF$small_first_gp %>% 
-  filter(aff_un != "other") %>% 
+```{r xsmall-effects, warning = FALSE}
+DF$effect_size_gp <- DF$effect_size_gp %>% 
+  mutate(aff_un = gsub("Mirconesia", "Micronesia", aff_un)) %>% 
+  filter(Year < 2025)
+
+DF$effect_size_gp_xsmall_first <- DF$effect_size_gp %>% 
+  filter(tolower(aff_un) != "other") %>% 
+  filter(source_file == "xsmall_first") %>% 
   pivot_wider(id_cols = Year, 
@@
 
-DF$small_other_gp <- DF$small_other_gp %>% 
-  filter(aff_un != "other") %>% 
+DF$effect_size_gp_xsmall_other <- DF$effect_size_gp %>% 
+  filter(tolower(aff_un) != "other") %>% 
+  filter(source_file == "xsmall_other") %>% 
   pivot_wider(id_cols = Year, 
@@
               values_fill = 0) %>% 
-  select(colnames(DF$small_first_gp))
-
-small_effect <- data.frame(
-  year = 1:length(unique(DF$small_first_gp$Year)),
-  v = 1:length(unique(DF$small_first_gp$Year)),
-  low = 1:length(unique(DF$small_first_gp$Year)),
-  high = 1:length(unique(DF$small_first_gp$Year))
+  select(colnames(DF$effect_size_gp_xsmall_first))
+
+xsmall_effect <- data.frame(
+  year = 1:length(unique(DF$effect_size_gp_xsmall_first$Year)),
+  v = 1:length(unique(DF$effect_size_gp_xsmall_first$Year)),
+  low = 1:length(unique(DF$effect_size_gp_xsmall_first$Year)),
+  high = 1:length(unique(DF$effect_size_gp_xsmall_first$Year))
 )
 i <- 1
-for (year in unique(DF$small_first_gp$Year)){
-  temp_table <- DF$small_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
-    bind_rows(DF$small_other_gp %>% filter(Year == year) %>% select(-Year))
+for (year in unique(DF$effect_size_gp_xsmall_first$Year)){
+  temp_table <- DF$effect_size_gp_xsmall_first %>% filter(Year == year) %>% select(-Year) %>% 
+    bind_rows(DF$effect_size_gp_xsmall_other %>% filter(Year == year) %>% select(-Year))
 
@@
 
-  small_effect$year[i] <- year
-  small_effect$v[i] <- mote_temp$v
-  small_effect$low[i] <- mote_temp$vlow
-  small_effect$high[i] <- mote_temp$vhigh
-  small_effect$people[i] <- mote_temp$n
+  xsmall_effect$year[i] <- year
+  xsmall_effect$v[i] <- mote_temp$v
+  xsmall_effect$low[i] <- mote_temp$vlow
+  xsmall_effect$high[i] <- mote_temp$vhigh
+  xsmall_effect$people[i] <- mote_temp$n
   i <- i + 1
@@
 
-small_effect$high[is.na(small_effect$high)] <- 0
-small_effect <- 
-  small_effect %>% 
+xsmall_effect$high[is.na(xsmall_effect$high)] <- 0
+xsmall_effect <- 
+  xsmall_effect %>% 
   filter(v != Inf)
 
-small_dot <- ggplot(small_effect, aes(year,v)) + 
+xsmall_dot <- ggplot(xsmall_effect, aes(year,v)) + 
   geom_point(aes(size = people)) + 
@@
 
-DF_decade <- DF$small_first_gp %>% 
+DF_decade <- DF$effect_size_gp_xsmall_first %>% 
   mutate(who = "F") %>% 
   bind_rows(
-    DF$small_other_gp %>% 
+    DF$effect_size_gp_xsmall_other %>% 
       mutate(who = "O")
@@
 DF_decade$Country_2 <- gsub("Central Asia|South-Eastern Asia|Southern Asia|Western Asia", "Asia", DF_decade$Country_2)
-DF_decade$Country_2 <- gsub("Melanesia|Mirconesia|New zealand and Australia|Polynesia", "Other", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Melanesia|Micronesia|New zealand and Australia|Polynesia", "Other", DF_decade$Country_2)
 
@@
                                          "NWS Europe", "Other"))
-DF_decade_sm <- DF_decade %>% 
+DF_decade_xsm <- DF_decade %>% 
   group_by(Country_2, Decade, who) %>% 
@@
 
-small_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
+xsmall_author <- ggplot(DF_decade_xsm, aes(who, Count, fill = Country_2)) + 
     geom_bar(position="fill", stat="identity", color = "black") + 
@@
 
-```{r medium-effects, warning = FALSE}
-DF$medium_first_gp <- DF$medium_first_gp %>% 
-  filter(aff_un != "other") %>% 
+```{r small-effects, warning = FALSE}
+DF$effect_size_gp_small_first <- DF$effect_size_gp %>% 
+  filter(tolower(aff_un) != "other") %>% 
+  filter(source_file == "small_first") %>% 
   pivot_wider(id_cols = Year, 
@@
 
-DF$medium_other_gp <- DF$medium_other_gp %>% 
-  filter(aff_un != "other") %>% 
+DF$effect_size_gp_small_other <- DF$effect_size_gp %>% 
+  filter(tolower(aff_un) != "other") %>% 
+  filter(source_file == "small_other") %>% 
   pivot_wider(id_cols = Year, 
@@
               values_fill = 0) %>% 
-  select(colnames(DF$medium_first_gp))
-
-medium_effect <- data.frame(
-  year = 1:length(unique(DF$medium_first_gp$Year)),
-  v = 1:length(unique(DF$medium_first_gp$Year)),
-  low = 1:length(unique(DF$medium_first_gp$Year)),
-  high = 1:length(unique(DF$medium_first_gp$Year))
+  select(colnames(DF$effect_size_gp_small_first))
+
+small_effect <- data.frame(
+  year = 1:length(unique(DF$effect_size_gp_small_first$Year)),
+  v = 1:length(unique(DF$effect_size_gp_small_first$Year)),
+  low = 1:length(unique(DF$effect_size_gp_small_first$Year)),
+  high = 1:length(unique(DF$effect_size_gp_small_first$Year))
 )
 i <- 1
-for (year in unique(DF$medium_first_gp$Year)){
-  temp_table <- DF$medium_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
-    bind_rows(DF$medium_other_gp %>% filter(Year == year) %>% select(-Year))
+for (year in unique(DF$effect_size_gp_small_first$Year)){
+  temp_table <- DF$effect_size_gp_small_first %>% filter(Year == year) %>% select(-Year) %>% 
+    bind_rows(DF$effect_size_gp_small_other %>% filter(Year == year) %>% select(-Year))
 
@@
   temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
+
   tryCatch(mote_temp <- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
@@
   )
-  medium_effect$year[i] <- year
-  medium_effect$v[i] <- mote_temp$v
-  medium_effect$low[i] <- mote_temp$vlow
-  medium_effect$high[i] <- mote_temp$vhigh
-  medium_effect$people[i] <- mote_temp$n
+
+  small_effect$year[i] <- year
+  small_effect$v[i] <- mote_temp$v
+  small_effect$low[i] <- mote_temp$vlow
+  small_effect$high[i] <- mote_temp$vhigh
+  small_effect$people[i] <- mote_temp$n
   i <- i + 1
@@
 
-medium_effect$high[is.na(medium_effect$high)] <- 0
-medium_effect <- 
-  medium_effect %>% 
+small_effect$high[is.na(small_effect$high)] <- 0
+small_effect <- 
+  small_effect %>% 
   filter(v != Inf)
 
-medium_dot <- ggplot(medium_effect, aes(year,v)) + 
+small_dot <- ggplot(small_effect, aes(year,v)) + 
   geom_point(aes(size = people)) + 
@@
 
-DF_decade <- DF$medium_first_gp %>% 
+DF_decade <- DF$effect_size_gp_small_first %>% 
   mutate(who = "F") %>% 
   bind_rows(
-    DF$medium_other_gp %>% 
+    DF$effect_size_gp_small_other %>% 
       mutate(who = "O")
@@
                                          "NWS Europe", "Other"))
-
 DF_decade_sm <- DF_decade %>% 
@@
 
-medium_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
+small_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
     geom_bar(position="fill", stat="identity", color = "black") + 
@@
 
-```{r large-effects, warning = FALSE}
-DF$large_first_gp <- DF$large_first_gp %>% 
-  filter(aff_un != "other") %>% 
+```{r medium-effects, warning = FALSE}
+DF$effect_size_gp_medium_first <- DF$effect_size_gp %>% 
+  filter(tolower(aff_un) != "other") %>% 
+  filter(source_file == "medium_first") %>% 
   pivot_wider(id_cols = Year, 
@@
 
-DF$large_other_gp <- DF$large_other_gp %>% 
-  filter(aff_un != "other") %>% 
+DF$effect_size_gp_medium_other <- DF$effect_size_gp %>% 
+  filter(tolower(aff_un) != "other") %>% 
+  filter(source_file == "medium_other") %>% 
   pivot_wider(id_cols = Year, 
@@
               values_fill = 0) %>% 
-  select(colnames(DF$large_first_gp))
-
-large_effect <- data.frame(
-  year = 1:length(unique(DF$large_first_gp$Year)),
-  v = 1:length(unique(DF$large_first_gp$Year)),
-  low = 1:length(unique(DF$large_first_gp$Year)),
-  high = 1:length(unique(DF$large_first_gp$Year))
+  select(colnames(DF$effect_size_gp_medium_first))
+
+medium_effect <- data.frame(
+  year = 1:length(unique(DF$effect_size_gp_medium_first$Year)),
+  v = 1:length(unique(DF$effect_size_gp_medium_first$Year)),
+  low = 1:length(unique(DF$effect_size_gp_medium_first$Year)),
+  high = 1:length(unique(DF$effect_size_gp_medium_first$Year))
 )
 i <- 1
-for (year in unique(DF$large_first_gp$Year)){
-  temp_table <- DF$large_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
-    bind_rows(DF$large_other_gp %>% filter(Year == year) %>% select(-Year))
+for (year in unique(DF$effect_size_gp_medium_first$Year)){
+  temp_table <- DF$effect_size_gp_medium_first %>% filter(Year == year) %>% select(-Year) %>% 
+    bind_rows(DF$effect_size_gp_medium_other %>% filter(Year == year) %>% select(-Year))
 
@@
   )
-  large_effect$year[i] <- year
-  large_effect$v[i] <- mote_temp$v
-  large_effect$low[i] <- mote_temp$vlow
-  large_effect$high[i] <- mote_temp$vhigh
-  large_effect$people[i] <- mote_temp$n
+
+  medium_effect$year[i] <- year
+  medium_effect$v[i] <- mote_temp$v
+  medium_effect$low[i] <- mote_temp$vlow
+  medium_effect$high[i] <- mote_temp$vhigh
+  medium_effect$people[i] <- mote_temp$n
   i <- i + 1
@@
 
-large_effect$high[is.na(large_effect$high)] <- 0
-large_effect <- 
-  large_effect %>% 
+medium_effect$high[is.na(medium_effect$high)] <- 0
+medium_effect <- 
+  medium_effect %>% 
   filter(v != Inf)
 
-large_dot <- ggplot(large_effect, aes(year,v)) + 
+medium_dot <- ggplot(medium_effect, aes(year,v)) + 
   geom_point(aes(size = people)) + 
@@
 
-DF_decade <- DF$large_first_gp %>% 
+DF_decade <- DF$effect_size_gp_medium_first %>% 
   mutate(who = "F") %>% 
   bind_rows(
-    DF$large_other_gp %>% 
+    DF$effect_size_gp_medium_other %>% 
       mutate(who = "O")
@@
                                          "NWS Europe", "Other"))
-
-DF_decade_sm <- DF_decade %>% 
+DF_decade_md <- DF_decade %>% 
   group_by(Country_2, Decade, who) %>% 
@@
 
-large_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
+medium_author <- ggplot(DF_decade_md, aes(who, Count, fill = Country_2)) + 
     geom_bar(position="fill", stat="identity", color = "black") + 
@@
 
+```{r large-effects, warning = FALSE}
+DF$effect_size_gp_large_first <- DF$effect_size_gp %>% 
+  filter(tolower(aff_un) != "other") %>% 
+  filter(source_file == "large_first") %>% 
+  pivot_wider(id_cols = Year, 
+              names_from = aff_un, 
+              values_from = count,
+              values_fill = 0)
+
+DF$effect_size_gp_large_other <- DF$effect_size_gp %>% 
+  filter(tolower(aff_un) != "other") %>% 
+  filter(source_file == "large_other") %>% 
+  pivot_wider(id_cols = Year, 
+              names_from = aff_un, 
+              values_from = count,
+              values_fill = 0) %>% 
+  select(colnames(DF$effect_size_gp_large_first))
+
+large_effect <- data.frame(
+  year = 1:length(unique(DF$effect_size_gp_large_first$Year)),
+  v = 1:length(unique(DF$effect_size_gp_large_first$Year)),
+  low = 1:length(unique(DF$effect_size_gp_large_first$Year)),
+  high = 1:length(unique(DF$effect_size_gp_large_first$Year))
+)
+i <- 1
+for (year in unique(DF$effect_size_gp_large_first$Year)){
+  temp_table <- DF$effect_size_gp_large_first %>% filter(Year == year) %>% select(-Year) %>% 
+    bind_rows(DF$effect_size_gp_large_other %>% filter(Year == year) %>% select(-Year))
+
+  col_total <- colSums(temp_table)
+  temp_table <- temp_table %>% 
+    select(names(col_total)[col_total > 0])
+  temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
+
+  tryCatch(mote_temp <- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
+                        r = nrow(temp_table), c = ncol(temp_table), 
+                        a = .05), 
+       warning = function(w) { 
+         mote_temp <<- v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
+                        r = nrow(temp_table), c = ncol(temp_table), 
+                        a = .05)
+         mote_temp$vlow <<- 0
+  }
+  )
+
+  large_effect$year[i] <- year
+  large_effect$v[i] <- mote_temp$v
+  large_effect$low[i] <- mote_temp$vlow
+  large_effect$high[i] <- mote_temp$vhigh
+  large_effect$people[i] <- mote_temp$n
+  i <- i + 1
+}
+
+large_effect$high[is.na(large_effect$high)] <- 0
+large_effect <- 
+  large_effect %>% 
+  filter(v != Inf)
+
+large_dot <- ggplot(large_effect, aes(year,v)) + 
+  geom_point(aes(size = people)) + 
+  theme_classic(base_size = 15) + 
+  geom_pointrange(aes(ymin = low, ymax = high)) + 
+  xlab("Year") + 
+  ylab(expression(phi)) + 
+  scale_size_continuous(name = "Num Authors")
+
+DF_decade <- DF$effect_size_gp_large_first %>% 
+  mutate(who = "F") %>% 
+  bind_rows(
+    DF$effect_size_gp_large_other %>% 
+      mutate(who = "O")
+  ) %>% 
+  mutate(Decade = ifelse(Year < 1990, "1980s", 
+                         ifelse(Year < 2000, "1990s", 
+                                ifelse(Year < 2010, "2000s", 
+                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
+  group_by(who, Decade) %>% 
+  summarize_all(sum) %>% 
+  pivot_longer(cols = -c(who, Decade, Year),
+               names_to = "Country", 
+               values_to = "Count")
+
+# North America, Africa (combine), NWS Europe, Eastern Asia, Latin America, Rest of Europe, Rest of Asia, Everything Else
+
+DF_decade$Country_2 <- DF_decade$Country
+DF_decade$Country_2 <- gsub(".*Africa.*", "Africa", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Northern Europe|Southern Europe|Western Europe", "NWS Europe", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("South-Eastern Europe|Eastern Europe", "ESE Europe", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Central Asia|South-Eastern Asia|Southern Asia|Western Asia", "Asia", DF_decade$Country_2)
+DF_decade$Country_2 <- gsub("Melanesia|Micronesia|New zealand and Australia|Polynesia", "Other", DF_decade$Country_2)
+
+DF_decade$Country_2 <- factor(DF_decade$Country_2, 
+                              levels = c("Africa", "Asia", "Eastern Asia", 
+                                         "ESE Europe", 
+                                         "Latin America and the Caribbean",
+                                         "North America", 
+                                         "NWS Europe", "Other"))
+DF_decade_lg <- DF_decade %>% 
+  group_by(Country_2, Decade, who) %>% 
+  summarize(Count = sum(Count), .groups = "keep")
+
+large_author <- ggplot(DF_decade_lg, aes(who, Count, fill = Country_2)) + 
+    geom_bar(position="fill", stat="identity", color = "black") + 
+  theme_classic(base_size = 15) + 
+  facet_grid(~Decade) + 
+  xlab("Author Type") + 
+  ylab("Percent of Authors") + 
+  scale_fill_brewer(name = "Region", palette = "Spectral", drop = FALSE)
+```
+
 ```{r fig-author-gpe, include = TRUE, fig.cap="A comparison of author affiliation geopolitical regions across decades.
-F stands for first authors and O stands for other authors.", fig.width=10, fig.height=6}
-small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
-medium_author + ggtitle("50-99 Authors") + #theme(legend.position = "none") + 
-large_author + ggtitle("100 + Authors") + #theme(legend.position = "none") + 
-guide_area() + 
-plot_layout(
-  ncol = 2,
-  nrow = 2, 
-  guides = "collect")
-
-ggsave("figure/figure_7_author_gpe.png", width = 10, height = 6, units = "in")
-```
-
-```{r fig-effect-gpe, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
+F stands for first authors and O stands for other authors.", fig.width=10, fig.height=8}
+plot1 <- xsmall_author + ggtitle("2-10 Authors") + xlab(NULL)
+plot2 <- small_author + ggtitle("11-49 Authors") + xlab(NULL)
+plot3 <- medium_author + ggtitle("50-99 Authors") + xlab(NULL)
+plot4 <- large_author + ggtitle("100+ Authors") + xlab(NULL)
+
+# Combine plots in a 2x2 grid with a third row for the shared legend
+layout_plot <- (
+  (plot1 + plot2) /
+  (plot3 + plot4) /
+  guide_area()
+) + 
+  plot_layout(guides = "collect") &
+  theme(legend.position = "bottom")  # or "right", depending on your preference
+
+layout_plot
+
+ggsave("figure/figure_7_author_gpe.png", width = 10, height = 8, units = "in")
+```
+
+```{r fig-effect-gpe-calc, include = FALSE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
 Larger dots indicate more papers and authors represented in the calculation of effect size.", fig.width=10, fig.height=6}
 all_effects <- bind_rows(
+  xsmall_effect %>% 
+    mutate(type = "2-10 Authors"),
   small_effect %>% 
-    mutate(type = "Small"),
+    mutate(type = "11-49 Authors"),
   medium_effect %>% 
-    mutate(type = "Medium"), 
+    mutate(type = "50-99 Authors"), 
   large_effect %>% 
-    mutate(type = "Large") 
+    mutate(type = "100+ Authors") 
 ) %>% 
-  mutate(type = factor(type, levels = c("Small", "Medium", "Large"),
-                       labels = c("10-49 Authors", 
+  mutate(type = factor(type, 
+                       levels = c("2-10 Authors",
+                                  "11-49 Authors",
                                   "50-99 Authors",
@@
          mutate(count = 1:nrow(all_effects)) %>% 
-         filter(year < 2024),
+         filter(year < 2025),
        aes(year, v)) + 
@@
   xlab("Year of Publication") + 
-  ylab("Cramer's V")
+  ylab("Cramer's V") + 
+  coord_cartesian(ylim = c(0,.45))
 
@@
 
-Figure \@ref(fig:fig-author-gpe) indicates the percent of authors in
-regions. In general, we found the same pattern as the overall analysis
-wherein most authors are from Europe and North America. The pattern of
-representation is roughly similar for the separation of small, medium,
-and large numbers of authors on papers. Across time, the representation
-does appear to diversify, with more representation in Asia, Latin
-American, and Africa. Figure \@ref(fig:fig-effect-gpe) represents the
-size of the differences in first/corresponding authors and other authors
-across time and number of authors. The differences in representation are
-larger for papers with more authors; however, the effects are non-zero
-for many of the comparisons. Encouragingly, over time these effects
-appear to diminish in size. One limitation with the calculation of
-effect sizes for count data is the sensitivity of the data to sample
-size (i.e., $\chi^2$ is upwardly biased by sample size, and $V$ is
-calculated based on this value). While we used the inclusion of zero as
-our boundary for "significance", the interpretation of the effects is
-that most are likely small: $V$ \< .05:
-`r apa_num(sum(all_effects$v <.05)/nrow(all_effects)*100)`%, $V$ \< .10:
-`r apa_num(sum(all_effects$v < .10)/nrow(all_effects)*100)`%, $V$ \<
-.20: `r apa_num(sum(all_effects$v < .20)/nrow(all_effects)*100)`%.
-
-\newpage
+Across all decades and team sizes, North America and Northwestern Europe
+consistently made up the majority of corresponding authors, as shown in
+Figure \@ref(fig:fig-author-gpe). This pattern held even as total
+team size increased, though the proportion of corresponding authors from
+other regions (e.g., Asia, Latin America and the Caribbean, and Africa)
+showed gradual increases over time. For team science teams (2–10
+authors), the dominance of North America and Western Europe in
+corresponding author roles was particularly pronounced. In contrast, for
+very large teams (100+ authors), regional diversity appeared somewhat
+more balanced, with more visible contributions from Asia and other
+regions among both corresponding and non-corresponding authors. However,
+visual inspection suggests that corresponding author sets remained less
+regionally diverse than the rest of the author team, particularly in
+earlier decades. While representation from regions like Africa and Latin
+America grew slightly among non-corresponding authors, they remained
+minimally represented in lead authorship positions. Notably, Eastern
+Asia’s representation increased more substantially over time, especially
+in teams with 50 or more authors. These visual trends suggest persistent
+regional disparities in leadership roles within scientific publications,
+despite increasing global collaboration. Quantitative effect sizes
+(Cramer’s *V*) and confidence intervals are reported in the following
+section to determine the importance of these observed differences.
+
+Supplemental Figure \@ref(fig:fig-effect-gpe) shows the magnitude of the difference in
+regional representation between corresponding authors and all other
+authors over time. A value of zero would indicate perfectly balanced
+regional diversity between the two groups, whereas larger values reflect
+increasing skew toward certain regions being more prominent in lead
+authorship positions. Effect sizes were often non-zero across much of
+the time span, particularly in publications with larger team sizes.
+Papers with 50–99 authors and 100+ authors showed the highest effect
+sizes in the 1970s through the 1990s, with *V* values frequently
+exceeding .20. This suggests that early large-team collaborations were
+especially likely to concentrate lead authorship within a narrow set of
+regions. However, across all team sizes, there was a clear downward
+trend in effect sizes over time, indicating that the regional
+composition of corresponding authors has become more similar to the rest
+of the author team. In recent decades, effect sizes for team science and
+mid-sized BTS teams (11–49 authors) have generally remained below 0.05,
+suggesting relatively balanced representation. For larger teams, effect
+sizes have also decreased, although they remain slightly elevated in
+more recent years compared to smaller teams. As a reference for
+interpretation, the vast majority of observed effects were small:
+`r apa_num(sum(all_effects$v <.05)/nrow(all_effects)*100)`% of
+comparisons had $V$ \< .05,
+`r apa_num(sum(all_effects$v < .10)/nrow(all_effects)*100)`% had $V$ \<
+.10, and `r apa_num(sum(all_effects$v < .20)/nrow(all_effects)*100)`%
+had $V$ \< .20. These results suggest that while regional imbalances in
+leadership authorship persist, they have gradually diminished in
+magnitude over time.
 
@@
 
-In this investigation, we explored the publication rates, areas, and
-researchers involved in BTS publications. Over a half-million articles
-were published in nearly 15,000 journals since 1970 that qualified as
-BTS articles. The areas of publication were aligned to cancer and
-genetics research in medicine and oncology for Health and Life Sciences,
-physics and chemistry for the Physical Sciences, and psychology for the
-Social Sciences. All areas of research show growth in the number of
+This study expands on prior efforts to characterize Big Team Science
+(BTS) by providing a systematic, field-wide analysis of authorship
+composition across time, team size, and geography. While BTS efforts
+have been increasingly promoted as vehicles for collaboration, scale,
+and rigor [@adams2012; @uhlmann2019], questions remain about who gets
+included, who leads, and how equitably credit is distributed. A key
+contribution of our study is that it is the first to propose a
+data-driven operationalization of "big" teams: defined here as
+publications with 11 or more authors and contributions from at least 6
+institutions, grounded in the empirical distribution of team sizes and
+affiliations across millions of papers. By comparing BTS publications
+with Team Science publications across four major scientific domains, we
+clarify how BTS compares with traditional team science and how it is
+evolving. All areas of research show growth in the number of
 publications and authors included on manuscripts, replicating previous
@@
 
-Our investigation expands previous research by additionally focusing on
-diversity in seniority of authors and geopolitical affiliation. The
-number of earlier career scholars increased across years, indicating
-that big teams may be accessible to different types of individuals, not
-just older, established researchers. This result is especially
-interesting given the publish-or-perish model still present in most
-institutions, as it may seem that large-scale projects could be a risky
-choice for non-permanent researchers. BTS projects are often slow to
-publish, there is no guarantee for publication, and incentives are often
-lower for non-corresponding authors. However, with a large team, the
-distribution of work could imply less effort on individual non-leading
-members, and research has shown that larger-team publications do receive
-more citations and appear to have higher impact [@larivière2015].
-
-In general, it appears that there is a decrease in the average number of
-publications a researcher has when publishing in a BTS paper over time,
-mirroring career length results. This result is likely attributable to
-the number of early career scholars joining projects, but also may
-support increased accessibility for individuals to be involved.
-Globalization, the internet, and the focus on interdisciplinary research
-are potentially driving forces behind our results, but, hopefully, the
-results also point to a decline in scientific gatekeeping [@lu2007;
-@siler2015].
-
-The variability in the types of researchers involved in publications
-also decreased across time in most areas of science with a decrease in
-variability for career length. As mentioned, an increase in early career
-researchers and numbers of publications could explain this effect
-mathematically, potentially with other social influences mentioned
-above. The variability in the number of publications is decreasing in
-the Physical Sciences, mirroring the career length results, but the
-opposite effect was found in the Health and Social Sciences. We see no
-clear reason why career variability would decrease while the variability
-in the number of publications would increase. The effect sizes for
-career length were much larger than the effects for number of
-publications. One speculation is the increasing requirements for a
-competitive faculty role application. Given the limited number of
-positions, one potential way to distinguish their application would be a
-larger number of publications in their early career [@caplow2017;
-@kyvik2003].
-
-The number of geopolitical entities for researcher affiliation is
-increasing over time, showing the results of globalization and the
-ability to connect across time zones and cultures [@xie2014]. While our
-definition of BTS required at least ten different institutional
-affiliations, we did not filter papers by geopolitical region, and thus,
-a manuscript could rely solely on institutions within a single country.
-The Physical Sciences did not show an increase in diversity of regions
-represented, however, it could be argued that the development of large
-research centers like CERN forced earlier diversity than other sciences
-(i.e., because CERN specifically recruited scientists from sponsoring
-nations). The Life, Health, and Social Sciences saw an increase in the
-number of regions represented with the highest increase in the Social
-Sciences. This result likely corresponds with an increased interest in
-big team science publications in psychology [@coles2022;
-@forscher2022a], and the desire to diversify the populations represented
-in psychological research [@henrich2010; @newson2021].
-
-While publications overall are diversifying, we found differences in the
-representation for first/corresponding authors versus all other authors.
-In general, first authors appear to be less diverse, representing
-European and North American authors, while other authors include more
-Asian and African authors. These effect sizes were often small, but the
-inequality persists across years. Diverse teams are more likely to have
-papers with stronger “impact” [@freeman2015; @hinnant2012; @jones2008;
-@yang2022] with higher citation metrics for more diverse author lists.
-The introduction of contributorship models [e.g., CRediT, @allen2019]
-will hopefully continue to push these effects down, as they highlight
-each individual's contribution to a manuscript.
+Next, we find that early-career researchers are increasingly represented
+in both BTS and smaller teams. Across all disciplines, the average
+career length of authors decreased significantly over time. Team Science
+teams exhibited even steeper declines in both average and variability of
+career length than big teams, suggesting that smaller teams may be an
+especially important entry point for early-career researchers. These
+trends echo broader shifts in academia’s incentive structures, where
+publishing early and often is increasingly required for career
+advancement [@milojevic2014; @larivière2015]. Publication counts showed
+similar but smaller effects. The average number of publications per
+author declined over time in both big and small teams, with smaller
+teams again showing more pronounced shifts. These findings support
+claims that collaborative science is no longer dominated exclusively by
+elite or high-output researchers [@milojevic2014], but may instead be
+expanding to include contributors with more varied publication
+histories.
+
+Our findings build on previous research by also examining diversity in
+author seniority and geopolitical affiliation. The growing participation
+of early-career scholars over time suggests that big team science may be
+increasingly accessible to a broader range of researchers, not just
+senior or established scientists. This trend is interesting given the
+challenges BTS projects can pose for non-permanent researchers: slow
+publication timelines, uncertain publication outcomes, and fewer
+incentives for non-corresponding authors. Yet, large teams may allow for
+more distributed workloads and reduced individual time investment, which
+could make them appealing even for early-career researchers. Moreover,
+prior work has shown that publications from larger teams tend to receive
+more citations and have broader impact [[@larivière2015], which may
+further incentivize early-career involvement despite the structural
+risks. Globalization, the internet, and the focus on interdisciplinary
+research are potentially driving forces behind our results, but,
+hopefully, the results also point to a decline in scientific gatekeeping
+[@lu2007; @siler2015].
+
+Our results confirm and extend prior observations that both Team Science
+and BTS are disproportionately concentrated in high-resource, highly
+networked regions, namely, North America and Western Europe [@singh2023;
+@adams2012; @sugimoto2017]. However, this study offers a more nuanced
+picture. We observed modest increases in the geographic diversity of
+authorship. Yet, lead authorship remained concentrated in a relatively
+narrow set of regions. These findings parallel previous critiques of
+global equity in scientific collaboration, where authors from the Global
+South are often included in co-authorship lists but remain
+underrepresented in leadership roles [@chan2011; @sumathipala2004].
+Though Cramer’s *V* values reflecting geographic imbalance decreased
+over time, especially for small and mid-sized teams, some asymmetries
+persist in large teams, reinforcing concerns about exclusion even within
+globally scoped research efforts [@abimbola2019].
+
+Diverse teams are more likely to produce research with stronger impact,
+as reflected in higher citation metrics and broader dissemination,
+particularly when author lists include individuals from varied
+backgrounds and institutions [@freeman2014; @jones2008; @yang2022].
+These patterns underscore a broader shift in how scholarly contributions
+are valued and attributed. As scientific teams become larger and more
+interdisciplinary, traditional authorship conventions, especially the
+emphasis on first and last author positions, become less informative
+indicators of individual contribution [@allen2019; @brand2015]. In
+response, initiatives like the CRediT taxonomy have emerged to increase
+transparency around contributor roles [@allen2014]. Our findings
+reinforce the importance of such systems: as early-career and
+less-published researchers increasingly participate in both BTS and
+regular teams, formal recognition of diverse contributions becomes
+essential for equitable credit and career advancement.
 
@@
 dataset: the correct author affiliations, the correct author publication
-information, and the correctly marked geopolitical entity. We had
-planned to analyze educational levels change over time; however, this
-data was mostly blank within the Scopus archive. Scopus is a carefully
-curated and large dataset, but these limitations must be kept in mind
-when interpreting the results. Publication language diversity was not
-investigated, and a previous study indicates that most publications in
-big databases are in English [@albarillo2014]. Certainly, publications
-in non-English languages would improve the statistics on diversity in
-scientific publishing - but the English language barrier likely exists
-regardless of inclusion in databases [@meneghini2007;
-@ramírez-castañeda2020].
-
-Big teams can provide high-impact, important research within scientific
-publishing, and this report suggests a promising trend of increasing
-publications that include earlier career and more diverse scholars.
-These partnerships introduce new challenges to collaboration from
-interpersonal conflict, infrastructure, incentives, to international
-political situations [@forscher2022a]. The implications for retention
-and promotion processes across a broad span of regions should be
-explored to improve diversity with the understanding of the differential
-impact of incentives for participating in big team studies.
+information, and the correctly marked geopolitical entity. Scopus is a
+carefully curated and large dataset, but these limitations must be kept
+in mind when interpreting the results. Publication language diversity
+was not investigated, and a previous study indicates that most
+publications in big databases are in English [@albarillo2014].
+Certainly, publications in non-English languages would improve the
+statistics on diversity in scientific publishing - but the English
+language barrier likely exists regardless of inclusion in databases
+[@meneghini2007; @ramírez-castañeda2020].
+
+Taken together, our findings suggest that BTS is evolving to include a
+broader and more diverse range of contributors, but also that smaller
+teams may remain more flexible or inclusive in incorporating
+early-career and globally distributed researchers. This result carries
+important implications for funders and institutions encouraging
+large-scale collaboration. Without structural support for equitable
+leadership, credit, and inclusion, particularly for authors from
+underrepresented regions, BTS risks reinforcing the very hierarchies it
+seeks to eliminate [@forscher2022a].
 
@@
 # References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
 
@@
 
-\endgroup
-
 \newpage
 
-# (APPENDIX) Appendix {.unnumbered}
-
-```{r child = "appendix.Rmd"}
-```
+# Supplement
+
+We have included several supplemental tables and figures for visualization of results discussed in the manuscript.
+
+```{r rate-estimates-fig, include = TRUE, fig.cap = "Exponential growth rate estimates with 95% confidence intervals.", out.width='100%'}
+knitr::include_graphics("figure/figure_3_growth.png")
+```
+
+```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.
+The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right.
+Therefore, North America represents the largest number of authors within BTS (i.e., bottom right, then separated into the geopolitical areas within that subregion), followed by Eastern Europe (top left), and so on.", out.width='100%'}
+knitr::include_graphics("figure/figure_6_map.png")
+```
+
+```{r fig-effect-gpe, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
+Larger dots indicate more papers and authors represented in the calculation of effect size.", out.width='100%'}
+knitr::include_graphics("figure/figure_8_author_effect_gpe.png")
+```
+
+```{r big-teams-table, results = 'asis'}
+big_teams_papers <- 968765
+big_teams_authors <- 4541369
+
+apa_table(DF$paper_stats %>% 
+        arrange(Statistic), 
+        caption = "Number of Authors and Papers by Subject Area",
+        note = "Papers can be classified into multiple categories.", 
+        align = c("l", rep("c", 5)), 
+        digits = 0)
+```

### 2025-06-03 manuscript_definition.tex
updating figures, references, and discussionn

--- 2024-10-15 manuscript_scopus/manuscript_scopus_unmasked.tex
@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \def\languageshorthands#1{}
+\ifLuaTeX
+  \usepackage[english]{selnolig} % disable illegal ligatures
+\fi
 % Manuscript styling
@@
   {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
     {}{\InnerPatchFailed}%
@@
 {}{\PatchFailed}
+\makeatother
 \keywords{big team, science, authorship, credit}
@@
 \makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+\renewcommand{\paragraph}{@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip @plus 0.2ex @minus 0.2ex}%
   {-1em}%
@@
 
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+\renewcommand{\subparagraph}[1]{@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip @plus 0.2ex @minus 0.2ex}%
   {-\z@\relax}%
@@
 
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 \hypersetup{
-  pdftitle={Who does big team science?},
+  pdftitle={What defines big team science?},
   pdfauthor={Erin M. Buchanan1 \& Savannah C. Lewis2},
@@
 
-\title{Who does big team science?}
+\title{What defines big team science?}
 \author{Erin M. Buchanan\textsuperscript{1} \& Savannah C. Lewis\textsuperscript{2}}
@@
 
-Significance statement: This work is the first to examine big team science authorship (i.e., 10+ authors) across millions of published works.
-Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing numbers of publications that increasingly represent earlier career and varied scholars.
-The number of geopolitical entities for researcher affiliation is increasing over time, showing the results of globalization and the ability to connect across time zones and cultures.
-While publications are generally diversifying, we did not yet find equality in the representation for first or corresponding authors.
-First authors appear to be less diverse, representing more European and North American authors, while other authors include more Asian and African authors.
-
-\hypertarget{general-disclosures}{%
-\section{General Disclosures}\label{general-disclosures}}
+Significance statement: This study is the first large-scale, data-driven analysis of authorship in Big Team Science (BTS), defined here as collaborations with 11 or more authors across six or more institutions.
+Drawing on millions of published works across four scientific domains, we show that BTS has grown rapidly in recent years and increasingly includes early-career researchers and contributors from a broader range of geopolitical regions.
+However, inclusion in BTS is not equally distributed.
+While author lists are becoming more globally diverse overall, leadership roles---particularly first and corresponding authorships, remain disproportionately concentrated in high-income countries, especially in Europe and North America.
+These findings highlight both the promise and limitations of BTS as a vehicle for global, inclusive science, underscoring the need for structural reforms to ensure equity in recognition and participation.
+
+\section{General Disclosures}\label{general-disclosures}
 
@@
 Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr}) but then was updated with access to the Scopus database for a broader picture of BTS projects (\url{https://osf.io/fheun}).
+After review, we updated the manuscript to reflect that the definition of big team science is unclear, and focused on a data-driven definition to explore our research questions.
 
@@
 
-Collaboration in scientific endeavors involves multiple researchers at
-(potentially) multiple institutions to communicate and work together to
-advance knowledge in their chosen field. Collaboration can manifest
-uniquely in each project dependent on the skill sets, hypotheses, and
-perspectives of collaborators. While collaboration is not new in
-science, the interest in ``big team science'' is increasing
-(Coles et al., 2022; Forscher et al., 2022; N. Stewart et al., 2017). Big team science (BTS) projects
-and/or organizations utilize and run large-scale collaborations to
-ensure that diverse populations and ideas manifest in research
-projects, which in turn allows for more reliability and generalizability
-in the results and methods of the study.
-
-BTS appears to be expanding because of two sources: 1) increasing
-globalization and technology that allows for real-time interdisciplinary
-research, and 2) expanding interest in reproducibility, replication, and
-generalizability (i.e., the credibility movement, Maxwell et al., 2015; Nelson et al., 2018; Vazire et al., 2022; Zwaan et al., 2018). Technological
-advances have provided easier ways to collaborate with people who are
-from other universities and countries through document sharing platforms
-(e.g., Google, GitHub, and the Open Science Framework), video chatting
-platforms (e.g., Zoom, Microsoft Teams), and messaging and project
-management platforms (e.g., Slack, Trello, when2meet, etc.). The
-credibility movement seems to suggest that by having both collaborations
-that span across the globe and subfields of research areas, age groups,
-and education levels should help to drive science in the path of better
+Scientific discovery has increasingly become a collaborative process,
+and the scale and scope of team science have dramatically expanded in
+recent years (Council et al., 2015). Collaboration in scientific endeavors
+involves multiple researchers at (potentially) multiple institutions to
+communicate and work together to advance knowledge in their chosen
+field(s). Collaboration can manifest uniquely in each project dependent
+on the skill sets, hypotheses, and perspectives of collaborators. One
+key aspect of collaboration is the flexibility allotted as it is shaped
+by the needs of the project and the researchers involved. While
+collaboration is not new in science, interest in ``team science'' is
+growing as individual researchers seek an interdisciplinary approach to
+research or bring on more students to their project. Team science is
+often defined as groups of researchers with various expertise working
+together to investigate complex problems (Fiore, 2008). Unlike general
+collaboration, team science involves structured roles, coordinated
+workflows, and shared resources to address challenges that would be
+difficult for individual researchers or one small team to solve
+independently.
+
+The movement toward team science reflects demands of modern research to
+answer complex questions, meet funder and university desires for
+interdisciplinary research, and the desire to increase diversity of
+scientific representation (Council et al., 2015). Further, the evolution of team
+science reflects broader shifts in research practices, driven by two
+sources: 1) increasing globalization and technology that allows for
+real-time interdisciplinary research (B. F. Jones et al., 2008), and 2) expanding
+interest in reproducibility, replication, and generalizability (i.e.,
+the credibility movement, Maxwell et al., 2015; Nelson et al., 2018; Vazire et al., 2022; Zwaan et al., 2018). Technological advances have provided easier ways to
+collaborate with people who are from other universities and countries
+through document sharing platforms (e.g., Google, GitHub, and the Open
+Science Framework), video chatting platforms (e.g., Zoom, Microsoft
+Teams), and messaging and project management platforms (e.g., Slack,
+Trello, when2meet, etc.).
+
+The credibility movement has been the main catalyst for the increased
+interest and broader shift of research practices. The movement
+emphasizes reproducibility and transparency in science, encouraging
+researchers to form new ways to increase the rigor in scientific
+endeavors. Throughout the last decade, the credibility movement has
+pushed for larger, more diverse teams and the involvement of
+participants from varied backgrounds. This shift in teams and
+participants focuses on increasing credibility, generalizability, and
+reliability of scientific findings. This form of collaboration has been
+coined ``Big Team Science.'' Big Team Science (BTS) builds on team science
+by scaling efforts to include larger, often globally diverse teams,
+which requires significant coordination and infrastructure (Coles et al., 2022; Forscher et al., 2022; N. Stewart et al., 2017). BTS projects and organizations organize
+extensive collaborations, intentionally incorporating diverse
+populations and perspectives into research. This large-scale approach
+enhances the reliability and generalizability of findings by integrating
+varied methodologies and viewpoints, leading to more robust and
+inclusive scientific outcomes. BTS organizations often pool extensive
+networks of researchers and resources, aiming to tackle grand scientific
+challenges that would be difficult to address within smaller or less
+coordinated collaborations. By having both collaborations that span
+across the globe and subfields of research areas, age groups, and
+education levels should help to drive science in the path of better
 materials, reliability, generalizability, and more robust sample sizes
-(when necessary) in a study (Auspurg \& Brüderl, 2021; LeBel et al., 2018; Nosek \& Lakens, 2014a).
-
-Generally, the credibility movement appears to have been driven by early career
-researchers (i.e., those who are within five years of their first
-appointment, Maizey \& Tzavella, 2019); however, there are no large meta-scientific
-investigations on this specific topic to date.
-The newness of large-scale research in many fields could be the culprit for the lack of investigation into this area.
-For example, psychology has had an increase in BTS publications like the Open
-Science Collaboration (Open Science Collaboration, 2015), Many Labs
-Collaborations (Buttrick et al., 2020; Ebersole et al., 2016, 2020; Klein et al., 2018; Klein et al., 2022; Mathur et al., 2020; Skorb et al., 2020) or the first papers from the
-Psychological Science Accelerator (Bago et al., 2022; Buchanan et al., 2023; Dorison et al., 2022; B.
+in a study (Auspurg \& Brüderl, 2021; LeBel et al., 2018; Nosek \& Lakens, 2014a).
+
+For example, psychology has seen an increase in BTS publications like
+the Open Science Collaboration (Open Science Collaboration, 2015), Many
+Labs Collaborations (Buttrick et al., 2020; Ebersole et al., 2016, 2020; Klein et al., 2018; Klein et al., 2022; Mathur et al., 2020; Skorb et al., 2020) or the first papers
+from the Psychological Science Accelerator (Bago et al., 2022; Buchanan et al., 2023; Dorison et al., 2022; B.
 C.
 Jones et al., 2021; Moshontz et al., 2018; Psychological Science Accelerator Self-Determination Theory Collaboration, 2022; Wang et al., 2021).
-Generally, the researcher incentive for
-replication and/or involvement in big-team projects was low for three reasons. First, journals often prioritize
-``novel'' or new results which led to rejection of replication manuscripts
-and publication bias (Franco et al., 2014; Hubbard \& Armstrong, 1997; Nosek et al., 2012). Second,
-the ``failure'' to replicate was often placed on the replication team as
-``bad science'' rather than a careful consideration of publication biases
-and (potential) questionable research practices (Klein et al., 2022; Maxwell et al., 2015). Last, why should someone want to spend time and resources
-on an answer we already ``know'' (Isager et al., 2021, 2023)?
-
-However, the success and interest in the large-scale reproducibility
-projects (Errington et al., 2021; Open Science Collaboration, 2015), paired
-with the meta-scientific publications focusing on researcher practices
-and incentive structures (John et al., 2012; Silberzahn et al., 2018) led to a
-change in journal guidelines and incentives for researchers interested
-in participating in large-scale replication studies (Grahe, 2014; Kidwell et al., 2016; Mayo-Wilson et al., 2021; Nosek et al., 2015). In some fields, the
-replication movement demonstrated that large-scale teams were a
-practical (and publishable) solution to answering research questions
-in generalizable way. The support
-for Registered Reports, papers accepted before the data has been
-collected (Nosek \& Lakens, 2014b; S. Stewart et al., 2020), has allowed researchers to
-invest in projects that they know
-should be published when the project is complete. Further, the
-implementation of the Transparency and Openness Guidelines (Nosek et al., 2015)
-and the Contributor Role Taxonomy (CRediT) system (Allen et al., 2019) have
-pushed journals and researchers to promote more open, inclusive
-publication practices.
-
-Beyond replication concerns, the credibility movement has mirrored calls for diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
-Rich, and Democratic) scientific research (Henrich et al., 2010; Newson et al., 2021; Rad et al., 2018) by improving representation in research samples. Like the
-large-scale studies in Physics ({``A Philosophical Case for Big Physics,''} 2021; Castelnovo et al., 2018) and
-Biology (Collins et al., 2003), the Social Sciences struggle to represent the
-breadth of humanity across both researcher and population
+The success and interest in the large-scale
+reproducibility projects (Errington et al., 2021; Open Science Collaboration, 2015), paired with the meta-scientific publications
+focusing on researcher practices and incentive structures
+(John et al., 2012; Silberzahn et al., 2018) led to a change in journal guidelines
+and incentives for researchers interested in participating in
+large-scale studies overall (Grahe, 2014; Kidwell et al., 2016; Mayo-Wilson et al., 2021; Nosek et al., 2015). In some fields, the BTS movement demonstrated that
+large-scale teams were a practical (and publishable) solution to
+answering research questions in generalizable way. The support for
+Registered Reports, papers accepted before the data has been collected
+(Nosek \& Lakens, 2014b; S. Stewart et al., 2020), has allowed researchers to invest in
+projects that they know should be published when the project is
+complete. Further, the implementation of the Transparency and Openness
+Guidelines (Nosek et al., 2015) and the Contributor Role Taxonomy (CRediT)
+system (Allen et al., 2019) have pushed journals and researchers to promote more
+open, inclusive publication practices.
+
+Beyond replication concerns, the credibility movement has mirrored calls
+for diversification or de-WEIRDing (e.g., Western, Educated,
+Industrialized, Rich, and Democratic) scientific research (Henrich et al., 2010; Newson et al., 2021; Rad et al., 2018) by improving representation in research samples.
+Like the large-scale studies in Physics ({``A Philosophical Case for Big Physics,''} 2021; Castelnovo et al., 2018)
+and Biology (Collins et al., 2003), the Social Sciences struggle to represent
+the breadth of humanity across both researcher and population
 characteristics. Now, grassroots organizations, such as the
 Psychological Science Accelerator (Moshontz et al., 2018), ManyBabies
-(\url{https://manybabies.github.io/}), NutNet (\url{https://nutnet.org/}), and
-DRAGNet (\url{https://dragnetglobal.weebly.com/}) can begin to tackle these
-issues by recruiting research labs from all over the globe to provide
-diversity in geographic, linguistic, and researcher representation.
-Publications have examined the global understanding of morality, face
-processing, COVID-19 information signaling, and more (Bago et al., 2022; Dorison et al., 2022; B.
+(\url{https://manybabies.github.io/}), NutNet (\url{https://nutnet.org/}),
+DRAGNet (\url{https://dragnetglobal.weebly.com/}), and IceCube
+(\url{https://icecube.wisc.edu/}) can begin to tackle these issues by
+recruiting research labs from all over the globe to provide diversity in
+geographic, linguistic, and researcher representation. Publications have
+examined the global understanding of morality, face processing, COVID-19
+information signaling, and more (Bago et al., 2022; Dorison et al., 2022; B.
 C.
@@
 for BTS studies have provided an incredible wealth of data for the
-scientific community, we do not yet know exactly \emph{who} is involved with,
-and benefits from, the BTS and credibility movement. Publications on BTS
-generally explore challenges, lessons learned, and the need for BTS
+scientific community, we do not yet know exactly how to define BTS -
+which is generally termed ``an unusually large number of collaborators''
 (Coles et al., 2022; Forscher et al., 2022).
 
-Therefore, the goal of this manuscript is to examine both the \emph{publications} and \emph{people} involved in BTS projects.
-We present descriptive information about the publication sources and types of articles to demonstrate large-scale research.
-Next, we examine the individuals involved in BTS for descriptive and predictive purposes.
-To describe the people involved in BTS projects, we planned to use education, types of publications from BTS individuals, and publication metrics.
-For predictive statistics, we explored the change in diversity of authors over time.
-It is unclear if the focus of de-WEIRDing science has only focused on the representation of the
-research participants or if it has also improved the representation of
-researchers outside of North America and Europe.
-Last, we examined for a change in diversity within first author(s) and the last author across time.
-As hiring and promoting practices often place a heavy weight on publications and especially ``influential'' publications, it becomes necessary to critically examine the representation present in authorship in BTS projects.
-
-\hypertarget{research-questions}{%
-\section{Research Questions}\label{research-questions}}
+The lack of formal definition raises questions about whether it
+represents a distinct phenomenon or simply a natural extension of team
+science. These big teams pose unique challenges, including coordinating
+work across diverse time zones, managing conflicts in decision-making,
+and ensuring fair distribution of credit for contributions
+(Cummings \& Kiesler, 2007; Wuchty et al., 2007), but also could provide big rewards by
+pooling expertise and increased interdisciplinary funding (Fiore, 2008).
+This paper seeks to clarify the concept of BTS by first establishing a
+data-driven definition based on publication patterns. With this
+quantitative distinction in place, we analyze publication trends over
+time to assess the trajectories of both traditional team science and
+BTS. Furthermore, we investigate the diversity of authors involved in
+these collaborations to explore whether shifts in the scientific
+landscape, such as efforts to de-WEIRD science and the expansion of
+collaborative opportunities, have influenced who participates in team
+science and BTS. By synthesizing insights from the growth and
+diversification of team science, this paper seeks to critically examine
+the emergence of big teams. Specifically, it aims to explore whether big
+teams are quantitatively different from traditional collaboration models
+with the following research questions.
+
+\section{Research Questions}\label{research-questions}
 
@@
 \item
-  Research Question 1: What publication sources publish big team
-  science papers?
+  Research Question 1: Exploring historical and current publication
+  values, what should define big team science versus team science?
+
+  \begin{itemize}
+  \tightlist
   \item
-  Research Question 2: What are the types of articles that are being
-  published in big team science?
+    Question 1A: What number of authors and institutional
+    affiliations should designate the differences between team
+    science and big team science?
   \item
-  Research Question 3: Who is involved in big team science?
+    Question 1B: Using the definition from 1A, are there changes in
+    the number of publications over time?
+  \end{itemize}
 \item
-  Research Question 4: How has the diversity of those involved in big team science changed over time?
+  Research Question 2: How has the diversity of those involved in team
+  science and big team science changed over time?
 \end{itemize}
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
-
-\hypertarget{publications}{%
-\subsection{Publications}\label{publications}}
-
-We have defined BTS publications as publications with at least ten
-authors at ten different institutions that were published in
-peer-reviewed journals or had posted a full paper pre-print. While this
-definition is a somewhat arbitrary choice, we separate this research
-from research on team science that uses any multi-university collaboration
-as a definition (B. F. Jones et al., 2008) to focus on larger sized teams rather
-than teams of any size. With at least ten institutions, the complexities
-of infrastructure, resources, tenure and promotion policies, ethics review, and more can occur (Forscher et al., 2022).
-Therefore, we believe this choice selects publications that would be ``big'' teams and those potential obstacles.
-
-We used
-data from 1970 and forward in the Scopus database, as it is noted online
-that this time period includes cited references for calculation of
-several of our variables described below. We will analyze our results
+\section{Method}\label{method}
+
+\subsection{Publications}\label{publications}
+
+We used data from 1970-2024 in the Scopus database, as it is noted
+online that 1970 and forward includes cited references for calculation
+of several of our variables described below. We analyzed our results
 based on four subject areas present in the Scopus database: Physical
-Sciences, Health Sciences, Social Sciences, and Life Sciences. We
-filtered the database to include articles, articles in press, business
-articles, conference papers, data papers, preprints, and surveys using
-Elsevier's classification system. This project was supported by access
-to the Scopus database through the International Center for the Study of
-Research.
-
-\hypertarget{data-curation}{%
-\subsection{Data Curation}\label{data-curation}}
-
-\hypertarget{rq1-publisher-information}{%
-\subsubsection{RQ1: Publisher Information}\label{rq1-publisher-information}}
-
-We extracted the following information for publication sources: the name
-of the publication (source title), subject area (both the large four
-subject areas and the smaller four digit all science journal
-classification {[}ASJC{]} code), and the journal impact using the Source
-Normalized Impact per Paper (SNIP).
-
-\hypertarget{rq2-publication-information}{%
-\subsubsection{RQ2: Publication Information}\label{rq2-publication-information}}
-
-For each publication of the identified BTS publications, we examined the
-full four digit ASJC subject areas codes for each of the larger four
-subject areas and the keywords present for these publications.
-
-\hypertarget{rq3-author-descriptive-statistics}{%
-\subsubsection{RQ3: Author Descriptive Statistics}\label{rq3-author-descriptive-statistics}}
-
-The author list was extracted from each publication. Next, we used the
-author and affiliation arrays to curate a list of all publications and
-author information included in BTS papers to calculate the variables
-described below.
-
-\hypertarget{education}{%
-\paragraph{Education}\label{education}}
-
-We collected degree information from the author table.
-Information on this variable is in the appendix.
-
-\hypertarget{types-of-publications}{%
-\paragraph{Types of Publications}\label{types-of-publications}}
-
-We took information from the publication
-type variable for each author's publications to present information
-about the types of papers BTS authors publish. Information on this
-variable is in the appendix.
-
-\hypertarget{publication-metrics}{%
-\paragraph{Publication Metrics}\label{publication-metrics}}
-
-For each author, we calculated the number of publications and the h-index. The h-index represents the highest \emph{h} number of publications that have at least \emph{h} citations.
-
-\hypertarget{institutions}{%
-\paragraph{Institutions}\label{institutions}}
-
-We report the number of institutions involved in big team science publications.
-
-\hypertarget{rq4-author-diversity-statistics}{%
-\subsubsection{RQ4: Author Diversity Statistics}\label{rq4-author-diversity-statistics}}
-
-\hypertarget{seniority}{%
-\paragraph{Seniority}\label{seniority}}
-
-Career length for each author was defined as the
-year of the first publication minus the current year listed for each
-author.
-Number of publications included the number of unique entries an author was included in the database.
-Career length and number of publications was used as a proxy for the ``age'' or ``seniority'' of a scholar.
-
-\hypertarget{geopolitical-region}{%
-\paragraph{Geopolitical Region}\label{geopolitical-region}}
-
-Geopolitical region was created by binning country code identifiers into the 17 identified United Nation subregions.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
+Sciences, Health Sciences, Social Sciences, and Life Sciences. We used
+the subject area split to ensure one field did not dominate BTS
+definitions and determine differences in trends across sub-areas of
+science. We filtered the database to include articles, articles in
+press, business articles, conference papers, data papers, preprints, and
+surveys using Elsevier's classification system. This project was
+supported by access to the Scopus database through the International
+Center for the Study of Research.
+
+\subsection{Data Curation}\label{data-curation}
+
+\subsubsection{RQ1: Defining BTS}\label{rq1-defining-bts}
+
+For each of the publications in Scopus, we calculated the number of
+distinct authors and institutions. If an author had multiple
+affiliations, we used the first affiliation listed. Each publication was
+classified into the four subject areas based on the All Journal Subject
+Codes present in the database. Publications can be included in multiple
+subject codes. For example, a medical paper may be listed in both life
+sciences and health sciences.
+
+\subsubsection{RQ2: Seniority}\label{rq2-seniority}
+
+Career length for each author was defined as the year of the first
+publication minus the current year listed for each author. Number of
+publications included the number of unique entries an author was
+included in the database. Career length and number of publications was
+used as a proxy for the ``age'' or ``seniority'' of a scholar.
+
+\subsubsection{RQ2: Geopolitical Region}\label{rq2-geopolitical-region}
+
+Geopolitical region was created by binning country code identifiers into
+the 17 identified United Nation subregions.
+
+\section{Results}\label{results}
 
@@
 
-\hypertarget{rq1-publisher-information.}{%
-\subsection{RQ1: Publisher Information.}\label{rq1-publisher-information.}}
-
-\hypertarget{number-of-articles}{%
-\subsubsection{Number of Articles}\label{number-of-articles}}
-
-The total number of articles included in this
-analysis was 510334 including 445301 Health Sciences
-articles, 228194 Physical Sciences articles, 26652
-Social Sciences articles, and 307514 Life Sciences articles.
-Articles could be classified into multiple categories. Figure
-\ref{fig:fig-pub-time} shows the number of articles published across
-time for each of the four large subject areas.
+\subsection{RQ1A: Defining BTS}\label{rq1a-defining-bts}
+
+The total number of papers included in the Scopus database at the time
+of this analysis was 97532104. 62966549
+articles were included past 1970 in the defined article types, which
+included 53622443 distinct authors. We then
+filtered the data to include only teams, which was defined as two
+authors from at least two institutions. The total number of papers for
+team projects was 32454393 and
+28353445 distinct authors. The data was then
+classified into subject areas by paper, which lead to missing data. The
+final number of papers included was 32448373 with
+28350468 distinct authors. The dataset was
+curated to include one row per author, paper, and subject area (i.e.,
+long format (Wickham, 2007)) which included
+241269297 total rows of data.
 
@@
 \centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-pub-time-1.pdf}
-\caption{\label{fig:fig-pub-time}Number of big-team science publications separated by four large subject areas across years.
-All four subject areas show an exponential number of publications in the last decade.}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_definition_files/figure-latex/fig-stats-authors-1.pdf}}
+\caption{\label{fig:fig-stats-authors}The left panel depicts the number of authors included on a paper by subject area, and the right panel demonstrates the number of affiliations by subject area.
+The boxplot shows the median (bold line), the interquartile range (the box), and the minimum to the 90th percentile of the number of authors/affiliations as the range line.
+Normally these plots include the entire range of the data, but these extreme range made the boxplot information unreadable.
+The dots indicate the average number of authors/affiliations for each area with the size of the dot indicating the standard deviation of the statistic.
+Therefore, larger dots indicate more variability in the number of authors and affiliations.}
 \end{figure}
 
-\hypertarget{number-of-journals}{%
-\subsubsection{Number of Journals}\label{number-of-journals}}
-
-The number of distinct journals big team science
-articles were published in was 14924 with 6559
-journals in Health Sciences, 5787 journals in Physical
-Sciences, 2500 journals in Social Sciences, and
-4187 journals in Life Sciences. The descriptive statistics
-for the Source Normalized Impact per Paper is presented in the
-supplemental materials with a comparison for all papers.
-
-\hypertarget{rq2-publication-information.}{%
-\subsection{RQ2: Publication Information.}\label{rq2-publication-information.}}
-
-Publication interest area was summarized by the four large subject areas
-creating a word cloud plot of the total number of publications within
-the ASJCs. Figure \ref{fig:fig-clouds} displays that the Health
-Sciences tends to publish within medicine and oncology, with a
-corresponding focus of cancer research and genetics for the Life
-Sciences. The Physical Sciences was mostly dominated by physics
-research, chemistry, and ecology. The BTS publications in the Social
-Sciences are mostly within psychology, education, and health.
+Figure \ref{fig:fig-stats-authors} displays the number of authors and
+affiliations by subject area. The figure demonstrates that the median
+number of authors is largest for health sciences, followed by life
+science, physical sciences, and then social sciences. The general
+pattern of team authorship includes about 2-8 authors, from about 2-4
+institutions. We used the maximum value (i.e., across all subject areas)
+for the 90th percentile as our exploratory definition for big team
+papers after examining the results from this analysis. We selected this
+percentile to have the high of the distribution, but also to be able to
+include enough papers for analysis across time. Therefore, big teams
+were defined as 11 authors from at least 6 different institutions.\footnote{In a previous version of this manuscript, we defined big teams as
+  10 authors from at least 10 institutions based on our own
+  experiences working within a research consortium. All definitions
+  are likely subjective, but the definition in this manuscript
+  represents the top 10\% of author and affiliations in a large body of
+  papers.}
+
+Supplemental Table \ref{tab:big-teams-table} includes the number of
+distinct authors and papers for each subject area by overall teams and
+big teams using our 90th percentile definition. The total number of
+distinct authors for big team papers was 968765 with
+4541369 distinct authors. In RQ2, we split the big team
+data into small (11-49), medium (50-99), and large big team (100+)
+groupings for convenience to display/analyze geopolitical regions. The
+table shows the number of authors and papers for those analyses.
+
+\subsection{RQ1B: Changes over Time}\label{rq1b-changes-over-time}
+
+For analyzing changes across time, we split the data into team science
+projects (2-10 authors, 2-5 affiliations) and BTS projects (as defined
+above, 11+ authors, 6+ affiliations). The number of papers found in
+Scopus across time for each subject area are displayed in Figure
+\ref{fig:fig-paper-time}. The visual results indicated that the number
+of team science papers was increasing the most in physical sciences for
+all manuscripts, followed by life and health sciences, and the last is
+social sciences. Examining only BTS projects shows that the rate is also
+increasing across time. All teams appear to start increasing in the
+1990s, while BTS projects do not start increasing off floor effects
+until past 2000. The health and life sciences show the largest increases
+across time in big teams with the smallest trend in the social sciences.
 
@@
 \centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-clouds-1.pdf}
-\caption{\label{fig:fig-clouds}Journal Areas for Big-Team Science Publications by Subject Area. Larger words indicate more publications in those ASJC areas.}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_definition_files/figure-latex/fig-paper-time-1.pdf}}
+\caption{\label{fig:fig-paper-time}The number of manuscripts across time for all team science papers (left) and big team science papers (right).}
 \end{figure}
 
-\hypertarget{rq3-author-descriptive-statistics-1}{%
-\subsection{RQ3: Author Descriptive Statistics}\label{rq3-author-descriptive-statistics-1}}
-
-The total number of unique authors across all publications was
-3047067. The mean number of authors per publication was \emph{M} =
-49.31 (\emph{SD} = 212.98, \emph{Med} = 18) with a
-range of 10 to 5568. The median and average
-number of authors by subject area are displayed in Figure
-\ref{fig:fig-author-year}. In general, the average and median number of
-authors increased over time, with the exception of the skew in the
-Physical Sciences. Interestingly, the effect in the Physical Sciences
-appears to be declining toward the general trends seen in other areas in
-the last few decades.
+Using the \texttt{minpack.lm} library (Elzhov et al., 2023), we calculated the
+exponential rate of growth for team science and BTS projects, and these
+results are shown in Supplemental Figure \ref{fig:rate-estimates-fig}. All growth rate
+confidence intervals excluded zero, indicating an exponential increase
+in the number of team papers over time. BTS growth rates were always
+higher than their team science counterparts, but the 95\% confidence
+intervals for the growth estimate overlapped for all statistics.
+Therefore, the growth trends, while visually appearing to be different,
+were likely similar for each subject area and team size when examined by
+estimating exponential growth statistics.
+
+\subsection{RQ2: Seniority}\label{rq2-seniority-1}
 
@@
 \centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-author-year-1.pdf}
-\caption{\label{fig:fig-author-year}Number of authors included on big-team science papers per year by subject area.
-Given the large skew in the data, the left panel presents the median number of authors per manuscript, and the right panel presents the average number of authors per manuscript by year.}
-\end{figure}
-
-\hypertarget{publication-metrics-1}{%
-\subsubsection{Publication Metrics}\label{publication-metrics-1}}
-
-The average number of publications by authors on big team science papers
-is \emph{M} = 38.37 (\emph{SD} = 102.54). The
-publication counts were averaged across authors for each publication,
-and then these average publication counts were averaged across
-publications \emph{M} = 162.50 (\emph{SD} =
-155.17). The average variability (i.e., the average
-standard deviation with authors of a manuscript) with publication counts
-of a paper was \(M_{SD}\) = 164.27 (\(SD_{SD}\) =
-127.21).
-
-The same process was completed with \emph{h}-index for each author and
-publication. The average \emph{h}-index for authors overall was \emph{M} =
-33.65 (\emph{SD} = 127.34, \emph{Med} = 8.00). The
-average \emph{h}-index for publications was \emph{M} = 198.87 (\emph{SD}
-= 248.78), and the variability of \emph{h}-index across
-manuscripts was \(M_{SD}\) = 211.80 (\(SD_{SD}\) =
-238.53, \(Med_{Med}\) = 68.00).
-
-\hypertarget{institutions-1}{%
-\subsubsection{Institutions}\label{institutions-1}}
-
-The total number of unique affiliation across all papers was 463876.
-
-\hypertarget{rq4-author-diversity-statistics-1}{%
-\subsection{RQ4: Author Diversity Statistics}\label{rq4-author-diversity-statistics-1}}
-
-\hypertarget{seniority-1}{%
-\subsubsection{Seniority}\label{seniority-1}}
-
-Figure \ref{fig:fig-career} portrays the average career length for
-authors involved in BTS publications across years. Career length was
-defined as the year of first publication minus the current year, and
-higher numbers mean longer careers. To analyze trends over time, we
-calculated the average career length for each publication (i.e., average
-author career lengths to create one score for each paper) and analyzed a
-regression analysis using career length to predict year of publication.
-In order to show variance between individuals, we calculated the
-standard deviation of career length for each publication and used this
-variance as an additional predictor.
-
-Negative career length slopes would indicate more young scholars in
-later years (i.e., lower average career length as time increases).
-Positive career length slopes would indicate older scholars in later
-years (i.e., higher average career length as time increases). Negative
-career variance slopes imply that variability decreases over the years,
-so the average career length is more homogeneous. Positive career length
-slopes imply that variability increases over the years, so the average
-career length is varied across individuals (i.e., different stages of
-scholars). Figure \ref{fig:fig-heatmap} displays the results for all
-regression analyses to compare coefficient strength across and within
-each hypothesis.
-
-All values for these analyses were different from zero. The slopes for
-the average career length were negative for all four subject areas,
-indicating a trend toward younger scientist involvement over time for
-each area, with the strongest effect in the Physical Sciences. The
-coefficient for variability in career length was also negative for each
-of the four subject areas with the highest in the Physical Sciences and
-lowest in the Life Sciences. This result indicates a decrease in the
-variability of career lengths over time, likely from two sources: 1)
-more publications with more authors, thus, lowering variance
-estimations, and 2) more young scholars overall. The effect sizes for
-this analysis were surprisingly large ranging from \(R^2\) = .25 to .47.
-All values and their confidence intervals can be found on our OSF page.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-career-1.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_definition_files/figure-latex/fig-career-1.pdf}}
 \caption{\label{fig:fig-career}Average career length for big-team science authors.
@@
 
+Figure \ref{fig:fig-career} portrays the average career length for
+authors involved in team science and BTS projects over time. Career
+length was defined as the year of first publication minus the current
+year, and higher numbers mean longer careers. The general pattern for
+team science and BTS projects is a decrease in average career length
+over time. However, it appears that, in at least the last two decades,
+BTS projects average a longer career length than team science projects.
+This trend is visually consistent across all four subject areas
+examined.
+
+\subsubsection{Career Length}\label{career-length}
+
+To analyze these trends over time, we calculated the average career
+length for each publication (i.e., averaging author career lengths to
+create one score for each paper) and analyzed a regression analysis
+using career length to predict year of publication. In order to show
+variance between individuals, we calculated the standard deviation of
+career length for each publication and used this variance as an
+additional predictor. Negative career length slopes would indicate more
+young scholars in later years (i.e., lower average career length as time
+increases). Positive career length slopes would indicate older scholars
+in later years (i.e., higher average career length as time increases).
+Negative career variance slopes imply that variability decreases over
+the years, so the average career length is more homogeneous. Positive
+career length slopes imply that variability increases over the years, so
+the average career length is varied across individuals (i.e., different
+stages of scholars). Figure \ref{fig:fig-heatmap} displays the results
+for all regression analyses.
+
 \begin{figure}
 \centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-heatmap-1.pdf}
-\caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region.
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_definition_files/figure-latex/fig-heatmap-1.pdf}}
+\caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopoliticalwithin the region.
 Each square represents a \emph{b} value or the slope of the predictor (x-axis) onto the dependent variable (each panel), with the exception of the bottom row which is the effect size of each regression analysis \(R^2\).
@@
 The top figure represents all results together for comparison across analyses.
-The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.
-Non-significant results are indicated with NS on the plot.}
+The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions.}
 \end{figure}
 
-We used the same analyses using number of publications to represent diversity instead of career length. An increasing slope over time indicates that
-individuals who are publishing more are more represented in BTS over
-time (i.e., increasing numbers of scholars with higher publication
-rates), while a negative slope indicates more researchers with less
-publications. A positive slope for the standard deviation of publication
-metrics indicates increasing variance over time (i.e., more diversity in
-the individual publication rates), while a negative slope would indicate
-less diversity in researchers over time. While publication rates do not
-represent value as a researcher, they are often used in hiring and
-promotion decisions, and we used this variable as a proxy to gauge the
-diversity in scholars represented in big teams. As shown in Figure
-\ref{fig:fig-heatmap} publication metrics were generally negative for
-the average publication metrics, indicating more scholars over time with
-lower numbers of publications with the strongest effects in Health and
-Social Sciences. The variability of publication counts was not
-significant for the Life Sciences but was negative for the Physical
-Sciences (less variability over time) and positive for Social and Health
-Sciences (more variability and over time). This result indicates that
-the Physical Sciences are trending toward scholars with less
-publications but also less diverse in number of publications, while the
-Health and Social Sciences see more diversity in publication counts and
-less published scholars overall.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-map-both-1.pdf}
-\caption{\label{fig:fig-map-both}Geopolitical regions represented in big-team science publications versus all publications.
-The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right.
-Therefore, North America represents the largest number of authors within BTS (i.e., bottom right, then separated into the geopolitical areas within that subregion), followed by Eastern Europe (top left), and so on.}
-\end{figure}
-
-\hypertarget{geopolitical-regions}{%
-\subsubsection{Geopolitical Regions}\label{geopolitical-regions}}
-
-Author geopolitical region is displayed in Figure
-\ref{fig:fig-map-both}. Big team publications appear to be led by North
-America and Western Europe, while all publications are led by North
-America and East Asia. To understand the change in representation
-diversity, we examined if the number of regions in a publication is
-predicted by the year of publication. Increasing diversity would be
-represented by a positive slope, while decreasing diversity would be
-represented by a negative slope. As shown in Figure
-\ref{fig:fig-heatmap}, the Physical Sciences do not show a trend of
-change in representation, while all other sciences showed a positive
-effect increasing in the number of geopolitical regions authors
-represent on publications.
+As shown in Figure \ref{fig:fig-heatmap}, all estimated slopes were
+negative, indicating that author teams are, on average, composed of
+younger scholars over time. The slope of the mean career length (\(b_M\))
+and variability in career length (\(b_{SD}\)) was consistently negative
+across disciplines and team sizes, with all estimates falling outside
+the defined null threshold (i.e., \(|b| > 0.00001\)). Most subject areas
+showed significantly different slopes within their respective team size,
+as evidenced by non-overlapping 95\% confidence intervals for both \(b_M\)
+and \(b_{SD}\). The Physical Sciences exhibited the steepest declines in
+both average career length and its variability (e.g., \(b_M\) = -0.7134,
+\(b_{SD}\) = -0.2202 for big teams), suggesting a sharp shift toward
+younger and more uniformly early-career author teams. In comparison,
+life sciences showed a slightly smaller shift toward earlier career
+scholars with less variability, followed by health and social sciences.
+The only non-significant difference was found between life and social
+sciences in big teams for author career variability.
+
+These findings suggest a widespread trend toward younger, less-senior
+authorship over time. However, this trend was more pronounced in team
+science-sized teams than in BTS teams. In all four subject areas, team
+science teams showed steeper declines in both the average and
+variability of author career length, as reflected by significantly
+different slopes with no overlapping confidence intervals. This finding
+indicates that regular teams are more strongly influenced by the
+increasing participation of earlier-career researchers, whereas big
+teams exhibit the same general trend but to a lesser extent. Effect
+sizes were substantial across all models, with \(R^2\) values ranging from
+.2818 to .4910. The largest effect was observed in the Physical Sciences
+for big teams (\(R^2\) = .4910), reflecting the strongest association
+between author career stage and publication timing. Together, these
+results indicate that the shift toward younger, more early-career author
+teams is widespread but not uniform across disciplines, and that team
+size plays a meaningful role in moderating the strength of these
+temporal trends. Full model estimates and confidence intervals are
+available on the OSF repository.
+
+\subsubsection{Publication Count}\label{publication-count}
+
+We used the same analyses using number of publications to represent
+diversity instead of career length. An increasing slope over time
+indicates that individuals who are publishing more are more represented
+in BTS over time (i.e., increasing numbers of scholars with higher
+publication rates), while a negative slope indicates more researchers
+with less publications. A positive slope for the standard deviation of
+publication metrics indicates increasing variance over time (i.e., more
+diversity in the individual publication rates), while a negative slope
+would indicate less diversity in researchers over time. While
+publication rates do not represent value as a researcher, they are often
+used in hiring and promotion decisions, and we used this variable as a
+proxy to gauge the diversity in scholars represented in BTS teams.
+
+All slopes for both the average (\(b_M\)) and standard deviation
+(\(b_{SD}\)) of publication count were significantly different from zero,
+indicating meaningful change over time in the types of researchers
+contributing to publications across subject areas and team sizes (see
+Figure \ref{fig:fig-heatmap}). Most subject areas differed
+significantly from one another within their team size, with the
+exception of Health Sciences and Physical Sciences for team science
+teams, whose \(b_M\) values overlapped in their confidence intervals.
+Across the remaining comparisons, Life Sciences showed the steepest
+decline in average publication count over time for regular teams (\(b_M\)
+= -0.0588), suggesting a shift toward including authors with fewer
+publications. In contrast, the smallest change in publication count was
+observed in Physical Sciences for big teams (\(b_M\) = -0.0005),
+indicating some stability scholar publication count when examining
+diversity. Standard deviation slopes (\(b_{SD}\)) were generally low in
+magnitude, with both positive and negative values depending on subject
+area. This suggests some variation in the diversity of publication rates
+across disciplines, with no uniform pattern of increasing or decreasing
+diversity.
+
+All subject areas showed significant differences between BTS and team
+science teams in both \(b_M\) and \(b_{SD}\), as indicated by
+non-overlapping confidence intervals. Team science teams consistently
+exhibited stronger negative slopes for average publication count than
+BTS teams, reflecting a more pronounced trend toward authors with fewer
+publications appearing over time. This suggests that smaller teams are
+increasingly composed of researchers with lower overall publication
+counts, whereas BTS teams show a more muted shift. Effect sizes for
+these models were smaller than those observed for career length, with
+\(R^2\) values ranging from .0335 to .0977. The strongest association was
+observed in the Physical Sciences for big teams (\(R^2\) = .0977), though
+all models showed low-to-moderate predictive ability.
+
+\subsubsection{Geopolitical Regions}\label{geopolitical-regions}
+
+Geographic patterns in authorship differed notably between BTS and team
+science publications, as shown in the publication maps and mosaic charts
+(Supplemental Figure \ref{fig:fig-map-both}). BTS publications were overwhelmingly
+concentrated in high-income countries, particularly the United States,
+Western European nations (e.g., Germany, the United Kingdom, France, and
+the Netherlands), and East Asian countries (e.g., China, Japan, and
+South Korea). In contrast, team science publications showed broader
+geographic distribution, with relatively higher representation from
+Latin America (e.g., Brazil, Mexico), South and Southeast Asia (e.g.,
+India, Pakistan, Indonesia), and parts of Africa and the Middle East.
+While both team types were led by traditionally defined Global North
+institutions, the mosaic charts revealed that team science teams
+included a more diverse range of countries contributing at moderate
+levels. These patterns suggest that although BTS involves international
+collaborations, it remains more centralized in historically dominant
+research regions, whereas team science may offer relatively greater
+global inclusivity at a smaller scale.
+
+To understand the change in representation diversity, we examined if the
+number of regions in a publication is predicted by the year of
+publication. Increasing diversity would be represented by a positive
+slope, while decreasing diversity would be represented by a negative
+slope. All slopes predicting geopolitical diversity over time were
+significantly different from zero, indicating small but non-zero changes
+in the number of regions represented on publications across disciplines
+and team types. Additionally, all slopes differed significantly between
+BTS and team science publications, suggesting distinct patterns in the
+evolution of international collaboration. Within BTS publications, Life
+Sciences and Social Sciences showed statistically indistinguishable
+trends in regional diversity over time, as did Social Sciences and
+Health Sciences. In contrast, all other within-BTS comparisons differed
+significantly. For team science publications, all four disciplines
+showed significantly different slopes, although the magnitudes of these
+differences were relatively small. Overall, the results suggest modest
+increases in geopolitical diversity in most disciplines, with a small
+decline observed only in Physical Sciences within BTS publications (\(b\)
+= -0.0129). Despite small effect sizes (all \(R^2 < .012\)), the
+consistent differences between BTS and team science teams point to
+structural differences in how global participation is evolving across
+large-scale versus more traditional collaborations.
 
@@
 \centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-author-gpe-1.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{manuscript_definition_files/figure-latex/fig-author-gpe-1.pdf}}
 \caption{\label{fig:fig-author-gpe}A comparison of author affiliation geopolitical regions across decades. F stands for first authors and O stands for other authors.}
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-effect-gpe-1.pdf}
-\caption{\label{fig:fig-effect-gpe}Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
-Larger dots indicate more papers and authors represented in the calculation of effect size.}
-\end{figure}
-
-Figure \ref{fig:fig-author-gpe} indicates the percent of authors in
-regions. In general, we found the same pattern as the overall analysis
-wherein most authors are from Europe and North America. The pattern of
-representation is roughly similar for the separation of small, medium,
-and large numbers of authors on papers. Across time, the representation
-does appear to diversify, with more representation in Asia, Latin
-American, and Africa. Figure \ref{fig:fig-effect-gpe} represents the
-size of the differences in first/corresponding authors and other authors
-across time and number of authors. The differences in representation are
-larger for papers with more authors; however, the effects are non-zero
-for many of the comparisons. Encouragingly, over time these effects
-appear to diminish in size. One limitation with the calculation of
-effect sizes for count data is the sensitivity of the data to sample
-size (i.e., \(\chi^2\) is upwardly biased by sample size, and \(V\) is
-calculated based on this value). While we used the inclusion of zero as
-our boundary for ``significance'', the interpretation of the effects is
-that most are likely small: \(V\) \textless{} .05:
-31.79\%, \(V\) \textless{} .10:
-70.20\%, \(V\) \textless{}
-.20: 94.04\%.
+Across all decades and team sizes, North America and Northwestern Europe
+consistently made up the majority of corresponding authors, as shown in
+Figure \ref{fig:fig-author-gpe}. This pattern held even as total
+team size increased, though the proportion of corresponding authors from
+other regions (e.g., Asia, Latin America and the Caribbean, and Africa)
+showed gradual increases over time. For team science teams (2--10
+authors), the dominance of North America and Western Europe in
+corresponding author roles was particularly pronounced. In contrast, for
+very large teams (100+ authors), regional diversity appeared somewhat
+more balanced, with more visible contributions from Asia and other
+regions among both corresponding and non-corresponding authors. However,
+visual inspection suggests that corresponding author sets remained less
+regionally diverse than the rest of the author team, particularly in
+earlier decades. While representation from regions like Africa and Latin
+America grew slightly among non-corresponding authors, they remained
+minimally represented in lead authorship positions. Notably, Eastern
+Asia's representation increased more substantially over time, especially
+in teams with 50 or more authors. These visual trends suggest persistent
+regional disparities in leadership roles within scientific publications,
+despite increasing global collaboration. Quantitative effect sizes
+(Cramer's \emph{V}) and confidence intervals are reported in the following
+section to determine the importance of these observed differences.
+
+Supplemental Figure \ref{fig:fig-effect-gpe} shows the magnitude of the difference in
+regional representation between corresponding authors and all other
+authors over time. A value of zero would indicate perfectly balanced
+regional diversity between the two groups, whereas larger values reflect
+increasing skew toward certain regions being more prominent in lead
+authorship positions. Effect sizes were often non-zero across much of
+the time span, particularly in publications with larger team sizes.
+Papers with 50--99 authors and 100+ authors showed the highest effect
+sizes in the 1970s through the 1990s, with \emph{V} values frequently
+exceeding .20. This suggests that early large-team collaborations were
+especially likely to concentrate lead authorship within a narrow set of
+regions. However, across all team sizes, there was a clear downward
+trend in effect sizes over time, indicating that the regional
+composition of corresponding authors has become more similar to the rest
+of the author team. In recent decades, effect sizes for team science and
+mid-sized BTS teams (11--49 authors) have generally remained below 0.05,
+suggesting relatively balanced representation. For larger teams, effect
+sizes have also decreased, although they remain slightly elevated in
+more recent years compared to smaller teams. As a reference for
+interpretation, the vast majority of observed effects were small:
+49.52\% of
+comparisons had \(V\) \textless{} .05,
+78.57\% had \(V\) \textless{}
+.10, and 92.38\%
+had \(V\) \textless{} .20. These results suggest that while regional imbalances in
+leadership authorship persist, they have gradually diminished in
+magnitude over time.
+
+\section{Discussion}\label{discussion}
+
+This study expands on prior efforts to characterize Big Team Science
+(BTS) by providing a systematic, field-wide analysis of authorship
+composition across time, team size, and geography. While BTS efforts
+have been increasingly promoted as vehicles for collaboration, scale,
+and rigor (Adams, 2012; Uhlmann et al., 2019), questions remain about who gets
+included, who leads, and how equitably credit is distributed. A key
+contribution of our study is that it is the first to propose a
+data-driven operationalization of ``big'' teams: defined here as
+publications with 11 or more authors and contributions from at least 6
+institutions, grounded in the empirical distribution of team sizes and
+affiliations across millions of papers. By comparing BTS publications
+with Team Science publications across four major scientific domains, we
+clarify how BTS compares with traditional team science and how it is
+evolving. All areas of research show growth in the number of
+publications and authors included on manuscripts, replicating previous
+investigations (Hunter \& Leahey, 2008; Sinatra et al., 2015; Wuchty et al., 2007).
+
+Next, we find that early-career researchers are increasingly represented
+in both BTS and smaller teams. Across all disciplines, the average
+career length of authors decreased significantly over time. Team Science
+teams exhibited even steeper declines in both average and variability of
+career length than big teams, suggesting that smaller teams may be an
+especially important entry point for early-career researchers. These
+trends echo broader shifts in academia's incentive structures, where
+publishing early and often is increasingly required for career
+advancement (Larivière et al., 2015; Milojević, 2014). Publication counts showed
+similar but smaller effects. The average number of publications per
+author declined over time in both big and small teams, with smaller
+teams again showing more pronounced shifts. These findings support
+claims that collaborative science is no longer dominated exclusively by
+elite or high-output researchers (Milojević, 2014), but may instead be
+expanding to include contributors with more varied publication
+histories.
+
+Our findings build on previous research by also examining diversity in
+author seniority and geopolitical affiliation. The growing participation
+of early-career scholars over time suggests that big team science may be
+increasingly accessible to a broader range of researchers, not just
+senior or established scientists. This trend is interesting given the
+challenges BTS projects can pose for non-permanent researchers: slow
+publication timelines, uncertain publication outcomes, and fewer
+incentives for non-corresponding authors. Yet, large teams may allow for
+more distributed workloads and reduced individual time investment, which
+could make them appealing even for early-career researchers. Moreover,
+prior work has shown that publications from larger teams tend to receive
+more citations and have broader impact {[}(Larivière et al., 2015), which may
+further incentivize early-career involvement despite the structural
+risks. Globalization, the internet, and the focus on interdisciplinary
+research are potentially driving forces behind our results, but,
+hopefully, the results also point to a decline in scientific gatekeeping
+(Lu, 2007; Siler et al., 2015).
+
+Our results confirm and extend prior observations that both Team Science
+and BTS are disproportionately concentrated in high-resource, highly
+networked regions, namely, North America and Western Europe (Adams, 2012; Singh et al., 2023; Sugimoto et al., 2017). However, this study offers a more nuanced
+picture. We observed modest increases in the geographic diversity of
+authorship. Yet, lead authorship remained concentrated in a relatively
+narrow set of regions. These findings parallel previous critiques of
+global equity in scientific collaboration, where authors from the Global
+South are often included in co-authorship lists but remain
+underrepresented in leadership roles (Chan et al., 2011; Sumathipala et al., 2004).
+Though Cramer's \emph{V} values reflecting geographic imbalance decreased
+over time, especially for small and mid-sized teams, some asymmetries
+persist in large teams, reinforcing concerns about exclusion even within
+globally scoped research efforts (Abimbola, 2019).
+
+Diverse teams are more likely to produce research with stronger impact,
+as reflected in higher citation metrics and broader dissemination,
+particularly when author lists include individuals from varied
+backgrounds and institutions (Freeman \& Huang, 2014; B. F. Jones et al., 2008; Yang et al., 2022).
+These patterns underscore a broader shift in how scholarly contributions
+are valued and attributed. As scientific teams become larger and more
+interdisciplinary, traditional authorship conventions, especially the
+emphasis on first and last author positions, become less informative
+indicators of individual contribution (Allen et al., 2019; Brand et al., 2015). In
+response, initiatives like the CRediT taxonomy have emerged to increase
+transparency around contributor roles (Allen et al., 2014). Our findings
+reinforce the importance of such systems: as early-career and
+less-published researchers increasingly participate in both BTS and
+regular teams, formal recognition of diverse contributions becomes
+essential for equitable credit and career advancement.
+
+The limitations for this research are tied to the curation of the Scopus
+dataset: the correct author affiliations, the correct author publication
+information, and the correctly marked geopolitical entity. Scopus is a
+carefully curated and large dataset, but these limitations must be kept
+in mind when interpreting the results. Publication language diversity
+was not investigated, and a previous study indicates that most
+publications in big databases are in English (Albarillo, 2014).
+Certainly, publications in non-English languages would improve the
+statistics on diversity in scientific publishing - but the English
+language barrier likely exists regardless of inclusion in databases
+(Meneghini \& Packer, 2007; Ramírez-Castañeda, 2020).
+
+Taken together, our findings suggest that BTS is evolving to include a
+broader and more diverse range of contributors, but also that smaller
+teams may remain more flexible or inclusive in incorporating
+early-career and globally distributed researchers. This result carries
+important implications for funders and institutions encouraging
+large-scale collaboration. Without structural support for equitable
+leadership, credit, and inclusion, particularly for authors from
+underrepresented regions, BTS risks reinforcing the very hierarchies it
+seeks to eliminate (Forscher et al., 2022).
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-In this investigation, we explored the publication rates, areas, and researchers involved in BTS publications.
-Over a half-million articles were published in nearly 15,000 journals since 1970 that qualified as BTS articles.
-The areas of publication were aligned to cancer and genetics research in medicine and oncology for Health and Life Sciences, physics and chemistry for the Physical Sciences, and psychology for the Social Sciences.
-All areas of research show growth in the number of publications and authors included on manuscripts, replicating previous investigations (Hunter \& Leahey, 2008; Sinatra et al., 2015; Wuchty et al., 2007).
-
-Our investigation expands previous research by additionally focusing on diversity in seniority of authors and geopolitical affiliation.
-The number of earlier career scholars increased across years, indicating that big teams may be accessible to different types of individuals, not just older, established researchers.
-This result is especially interesting given the publish-or-perish model still present in most institutions, as it may seem that large-scale projects could be a risky choice for non-permanent researchers.
-BTS projects are often slow to publish, there is no guarantee for publication, and incentives are often lower for non-corresponding authors.
-However, with a large team, the distribution of work could imply less effort on individual non-leading members, and research has shown that larger-team publications do receive more citations and appear to have higher impact (Larivière et al., 2015).
-
-In general, it appears that there is a decrease in the average number of publications a researcher has when publishing in a BTS paper over time, mirroring career length results.
-This result is likely attributable to the number of early career scholars joining projects, but also may support increased accessibility for individuals to be involved.
-Globalization, the internet, and the focus on interdisciplinary research are potentially driving forces behind our results, but, hopefully, the results also point to a decline in scientific gatekeeping (Lu, 2007; Siler et al., 2015).
-
-The variability in the types of researchers involved in publications
-also decreased across time in most areas of science with a decrease in
-variability for career length. As mentioned, an increase in early career
-researchers and numbers of publications could explain this effect
-mathematically, potentially with other social influences mentioned
-above. The variability in the number of publications is decreasing in
-the Physical Sciences, mirroring the career length results, but the
-opposite effect was found in the Health and Social Sciences. We see no
-clear reason why career variability would decrease while the variability
-in the number of publications would increase. The effect sizes for
-career length were much larger than the effects for number of
-publications. One speculation is the increasing requirements for a
-competitive faculty role application. Given the limited number of
-positions, one potential way to distinguish their application would be a
-larger number of publications in their early career (Caplow, 2017; Kyvik, 2003).
-
-The number of geopolitical entities for researcher affiliation is
-increasing over time, showing the results of globalization and the
-ability to connect across time zones and cultures (Xie, 2014). While our
-definition of BTS required at least ten different
-institutional affiliations, we did not filter papers by geopolitical
-region, and thus, a manuscript could rely solely on institutions within
-a single country. The Physical Sciences did not show an increase in
-diversity of regions represented, however, it could be argued that the
-development of large research centers like CERN forced earlier diversity
-than other sciences (i.e., because CERN specifically recruited
-scientists from sponsoring nations). The Life, Health, and Social
-Sciences saw an increase in the number of regions represented with the
-highest increase in the Social Sciences. This result likely corresponds
-with an increased interest in big team science publications in
-psychology (Coles et al., 2022; Forscher et al., 2022), and the desire to diversify the
-populations represented in psychological research (Henrich et al., 2010; Newson et al., 2021).
-
-While publications overall are diversifying, we found differences in the representation for first/corresponding authors versus all other authors.
-In general, first authors appear to be less diverse, representing European and North American authors, while other authors include more Asian and African authors.
-These effect sizes were often small, but the inequality persists across years.
-Diverse teams are more likely to have papers with stronger ``impact'' (Freeman \& Huang, 2015; Hinnant et al., 2012; B.
-F.
-Jones et al., 2008; Yang et al., 2022) with higher citation metrics for more diverse author lists.
-The introduction of contributorship models (e.g., CRediT, Allen et al., 2019)
-will hopefully continue to push these effects down, as they highlight
-each individual's contribution to a manuscript.
-
-The limitations for this research are tied to the curation of the Scopus dataset: the correct author affiliations, the correct author publication information, and the correctly marked geopolitical entity.
-We had planned to analyze educational levels change over time; however, this data was mostly blank within the Scopus archive.
-Scopus is a carefully curated and large dataset, but these limitations must be kept in mind when interpreting the results.
-Publication language diversity was not investigated, and a previous study indicates that most publications in big databases are in English (Albarillo, 2014).
-Certainly, publications in non-English
-languages would improve the statistics on diversity in scientific
-publishing - but the English language barrier likely exists regardless
-of inclusion in databases (Meneghini \& Packer, 2007; Ramírez-Castañeda, 2020).
-
-Big teams can provide high-impact, important research within scientific publishing, and this report suggests a promising trend of increasing publications that include earlier career and more diverse scholars.
-These partnerships introduce new challenges to collaboration from interpersonal conflict, infrastructure, incentives, to international political situations (Forscher et al., 2022).
-The implications for retention and promotion processes across a broad span of regions should be explored to improve diversity with the understanding of the differential impact of incentives for participating in big team studies.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-
-\hypertarget{refs}{}
+\section{References}\label{references}
+
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-aphilos2021}{}}%
+\bibitem[\citeproctext]{ref-aphilos2021}
 A philosophical case for big physics. (2021). \emph{Nature Physics}, \emph{17}(6), 661--661. \url{https://doi.org/10.1038/s41567-021-01278-0}
 
-\leavevmode\vadjust pre{\hypertarget{ref-albarillo2014}{}}%
+\bibitem[\citeproctext]{ref-abimbola2019}
+Abimbola, S. (2019). The foreign gaze: authorship in academic global health. \emph{BMJ Global Health}, \emph{4}(5). \url{https://doi.org/10.1136/bmjgh-2019-002068}
+
+\bibitem[\citeproctext]{ref-adams2012}
+Adams, J. (2012). The rise of research networks. \emph{Nature}, \emph{490}(7420), 335--336. \url{https://doi.org/10.1038/490335a}
+
+\bibitem[\citeproctext]{ref-albarillo2014}
 Albarillo, F.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-allen2019}{}}%
+\bibitem[\citeproctext]{ref-allen2019}
 Allen, L., O'Connell, A., \& Kiermer, V.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-auspurg2021}{}}%
+\bibitem[\citeproctext]{ref-allen2014}
+Allen, L., Scott, J., Brand, A., Hlava, M., \& Altman, M. (2014). Publishing: Credit where credit is due. \emph{Nature}, \emph{508}(7496), 312--313. \url{https://doi.org/10.1038/508312a}
+
+\bibitem[\citeproctext]{ref-auspurg2021}
 Auspurg, K., \& Brüderl, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bago2022}{}}%
+\bibitem[\citeproctext]{ref-bago2022}
 Bago, B., Kovacs, M., Protzko, J., Nagy, T., Kekecs, Z., Palfi, B., Adamkovic, M., Adamus, S., Albalooshi, S., Albayrak-Aydemir, N., Alfian, I.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-buchanan2023}{}}%
+\bibitem[\citeproctext]{ref-brand2015}
+Brand, A., Allen, L., Altman, M., Hlava, M., \& Scott, J.
+(2015).
+Beyond authorship: attribution, contribution, collaboration, and credit.
+\emph{Learned Publishing}, \emph{28}(2), 151--155.
+\url{https://doi.org/10.1087/20150211}
+
+\bibitem[\citeproctext]{ref-buchanan2023}
 Buchanan, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-buttrick2020}{}}%
+\bibitem[\citeproctext]{ref-buttrick2020}
 Buttrick, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-caplow2017}{}}%
-Caplow, T. (2017). \emph{The academic marketplace} (2nd ed.). Routledge. \url{https://doi.org/10.4324/9781351305969}
-
-\leavevmode\vadjust pre{\hypertarget{ref-castelnovo2018}{}}%
+\bibitem[\citeproctext]{ref-castelnovo2018}
 Castelnovo, P., Florio, M., Forte, S., Rossi, L., \& Sirtori, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-coles2022}{}}%
+\bibitem[\citeproctext]{ref-chan2011}
+Chan, L., Kirsop, B., \& Arunachalam, S.
+(2011).
+Towards Open and Equitable Access to Research and Knowledge for Development.
+\emph{PLoS Medicine}, \emph{8}(3), e1001016.
+\url{https://doi.org/10.1371/journal.pmed.1001016}
+
+\bibitem[\citeproctext]{ref-coles2022}
 Coles, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-collins2003}{}}%
+\bibitem[\citeproctext]{ref-collins2003}
 Collins, F.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-dorison2022}{}}%
+\bibitem[\citeproctext]{ref-council2015}
+Council, N.
+R., Education, D.
+of B., Sciences, S., Sciences, B.
+on B.
+C.
+and S.
+and, \& Science, C.
+on the S.
+of T.
+(2015).
+\emph{Enhancing the Effectiveness of Team Science}.
+National Academies Press.
+
+\bibitem[\citeproctext]{ref-cummings2007}
+Cummings, J.
+N., \& Kiesler, S.
+(2007).
+Coordination costs and project outcomes in multi-university collaborations.
+\emph{Research Policy}, \emph{36}(10), 1620--1634.
+\url{https://doi.org/10.1016/j.respol.2007.09.001}
+
+\bibitem[\citeproctext]{ref-dorison2022}
 Dorison, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ebersole2016}{}}%
+\bibitem[\citeproctext]{ref-ebersole2016}
 Ebersole, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ebersole2020}{}}%
+\bibitem[\citeproctext]{ref-ebersole2020}
 Ebersole, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-10.7554ux2feLife.71601}{}}%
+\bibitem[\citeproctext]{ref-elzhov2023}
+Elzhov, T.
+V., Mullen, K.
+M., Spiess, A.-N., \& Bolker, B.
+(2023).
+\emph{Minpack.lm: R interface to the levenberg-marquardt nonlinear least-squares algorithm found in MINPACK, plus support for bounds}.
+\url{https://cran.r-project.org/web/packages/minpack.lm/index.html}
+
+\bibitem[\citeproctext]{ref-10.7554ux2feLife.71601}
 Errington, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-forscher2022a}{}}%
+\bibitem[\citeproctext]{ref-fiore2008}
+Fiore, S.
+M.
+(2008).
+Interdisciplinarity as Teamwork: How the Science of Teams Can Inform Team Science.
+\emph{Small Group Research}, \emph{39}(3), 251--277.
+\url{https://doi.org/10.1177/1046496408317797}
+
+\bibitem[\citeproctext]{ref-forscher2022a}
 Forscher, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-franco2014}{}}%
-Franco, A., Malhotra, N., \& Simonovits, G.
-(2014).
-Publication bias in the social sciences: Unlocking the file drawer.
-\emph{Science}, \emph{345}(6203), 1502--1505.
-\url{https://doi.org/10.1126/science.1255484}
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2015}{}}%
-Freeman, R.
-B., \& Huang, W.
-(2015).
-Collaborating with People Like Me: Ethnic Coauthorship within the United States.
-\emph{Journal of Labor Economics}, \emph{33}(S1), S289--S318.
-\url{https://doi.org/10.1086/678973}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grahe2014}{}}%
+\bibitem[\citeproctext]{ref-freeman2014}
+Freeman, R. B., \& Huang, W. (2014). Collaboration: Strength in diversity. \emph{Nature}, \emph{513}(7518), 305--305. \url{https://doi.org/10.1038/513305a}
+
+\bibitem[\citeproctext]{ref-grahe2014}
 Grahe, J. E. (2014). Announcing open science badges and reaching for the sky. \emph{The Journal of Social Psychology}, \emph{154}(1), 1--3. \url{https://doi.org/10.1080/00224545.2014.853582}
 
-\leavevmode\vadjust pre{\hypertarget{ref-henrich2010}{}}%
+\bibitem[\citeproctext]{ref-henrich2010}
 Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--83. \url{https://doi.org/10.1017/S0140525X0999152X}
 
-\leavevmode\vadjust pre{\hypertarget{ref-hinnant2012}{}}%
-Hinnant, C.
-C., Stvilia, B., Wu, S., Worrall, A., Burnett, G., Burnett, K., Kazmer, M.
-M., \& Marty, P.
-F.
-(2012).
-Author-team diversity and the impact of scientific publications: Evidence from physics research at a national science lab.
-\emph{Library \& Information Science Research}, \emph{34}(4), 249--257.
-\url{https://doi.org/10.1016/j.lisr.2012.03.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hubbard1997}{}}%
-Hubbard, R., \& Armstrong, J. S. (1997). Publication Bias against Null Results. \emph{Psychological Reports}, \emph{80}(1), 337--338. \url{https://doi.org/10.2466/pr0.1997.80.1.337}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hunter2008}{}}%
+\bibitem[\citeproctext]{ref-hunter2008}
 Hunter, L., \& Leahey, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-isager2021a}{}}%
-Isager, P.
-M., Van Aert, R.
-C.
-M., Bahník, Š., Brandt, M.
-J., DeSoto, K.
-A., Giner-Sorolla, R., Krueger, J.
-I., Perugini, M., Ropovik, I., Van 'T Veer, A.
-E., Vranka, M., \& Lakens, D.
-(2023).
-Deciding what to replicate: {A} decision model for replication study selection under resource and knowledge constraints.
-\emph{Psychological Methods}, \emph{28}(2), 438--451.
-\url{https://doi.org/10.1037/met0000438}
-
-\leavevmode\vadjust pre{\hypertarget{ref-isager2021}{}}%
-Isager, P. M., van 't Veer, A. E., \& Lakens, D. (2021). \emph{Replication value as a function of citation impact and sample size}. \url{https://doi.org/10.31222/osf.io/knjea}
-
-\leavevmode\vadjust pre{\hypertarget{ref-john2012}{}}%
+\bibitem[\citeproctext]{ref-john2012}
 John, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-jones2021}{}}%
+\bibitem[\citeproctext]{ref-jones2021}
 Jones, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-jones2008}{}}%
+\bibitem[\citeproctext]{ref-jones2008}
 Jones, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kidwell2016}{}}%
+\bibitem[\citeproctext]{ref-kidwell2016}
 Kidwell, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-klein2022}{}}%
+\bibitem[\citeproctext]{ref-klein2022}
 Klein, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-klein2018}{}}%
+\bibitem[\citeproctext]{ref-klein2018}
 Klein, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kyvik2003}{}}%
-Kyvik, S. (2003). Changing trends in publishing behaviour among university faculty, 1980-2000. \emph{Scientometrics}, \emph{58}(1), 35--48. \url{https://doi.org/10.1023/A:1025475423482}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lariviuxe8re2015}{}}%
+\bibitem[\citeproctext]{ref-lariviuxe8re2015}
 Larivière, V., Gingras, Y., Sugimoto, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lebel2018}{}}%
+\bibitem[\citeproctext]{ref-lebel2018}
 LeBel, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lu2007}{}}%
+\bibitem[\citeproctext]{ref-lu2007}
 Lu, Y.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-maizey2019}{}}%
-Maizey, L., \& Tzavella, L.
-(2019).
-Barriers and solutions for early career researchers in tackling the reproducibility crisis in cognitive neuroscience.
-\emph{Cortex}, \emph{113}, 357--359.
-\url{https://doi.org/10.1016/j.cortex.2018.12.015}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mathur2020}{}}%
+\bibitem[\citeproctext]{ref-mathur2020}
 Mathur, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-maxwell2015}{}}%
+\bibitem[\citeproctext]{ref-maxwell2015}
 Maxwell, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mayo-wilson2021}{}}%
+\bibitem[\citeproctext]{ref-mayo-wilson2021}
 Mayo-Wilson, E., Grant, S., Supplee, L., Kianersi, S., Amin, A., DeHaven, A., \& Mellor, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-meneghini2007}{}}%
+\bibitem[\citeproctext]{ref-meneghini2007}
 Meneghini, R., \& Packer, A. L. (2007). Is there science beyond english? \emph{EMBO Reports}, \emph{8}(2), 112--116. \url{https://doi.org/10.1038/sj.embor.7400906}
 
-\leavevmode\vadjust pre{\hypertarget{ref-moshontz2018}{}}%
+\bibitem[\citeproctext]{ref-milojevic2014}
+Milojević, S.
+(2014).
+Principles of scientific research team formation and evolution.
+\emph{Proceedings of the National Academy of Sciences}, \emph{111}(11), 3984--3989.
+\url{https://doi.org/10.1073/pnas.1309723111}
+
+\bibitem[\citeproctext]{ref-moshontz2018}
 Moshontz, H., Campbell, L., Ebersole, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-nelson2018}{}}%
+\bibitem[\citeproctext]{ref-nelson2018}
 Nelson, L. D., Simmons, J., \& Simonsohn, U. (2018). Psychology's renaissance. \emph{Annual Review of Psychology}, \emph{69}(1), 511--534. \url{https://doi.org/10.1146/annurev-psych-122216-011836}
 
-\leavevmode\vadjust pre{\hypertarget{ref-newson2021}{}}%
+\bibitem[\citeproctext]{ref-newson2021}
 Newson, M., Buhrmester, M., Xygalatas, D., \& Whitehouse, H. (2021). Go WILD, not WEIRD. \emph{Journal for the Cognitive Science of Religion}, \emph{6}(1-2). \url{https://doi.org/10.1558/jcsr.38413}
 
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2015}{}}%
+\bibitem[\citeproctext]{ref-nosek2015}
 Nosek, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
+\bibitem[\citeproctext]{ref-nosek2014method}
 Nosek, B. A., \& Lakens, D. (2014a). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137141.
 
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2014}{}}%
+\bibitem[\citeproctext]{ref-nosek2014}
 Nosek, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2012}{}}%
-Nosek, B.
-A., Spies, J.
-R., \& Motyl, M.
-(2012).
-Scientific Utopia: II.
-Restructuring Incentives and Practices to Promote Truth Over Publishability.
-\emph{Perspectives on Psychological Science}, \emph{7}(6), 615--631.
-\url{https://doi.org/10.1177/1745691612459058}
-
-\leavevmode\vadjust pre{\hypertarget{ref-opensciencecollaboration2015}{}}%
+\bibitem[\citeproctext]{ref-opensciencecollaboration2015}
 Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716--aac4716. \url{https://doi.org/10.1126/science.aac4716}
 
-\leavevmode\vadjust pre{\hypertarget{ref-psychologicalscienceacceleratorself-determinationtheorycollaboration2022}{}}%
+\bibitem[\citeproctext]{ref-psychologicalscienceacceleratorself-determinationtheorycollaboration2022}
 Psychological Science Accelerator Self-Determination Theory Collaboration.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rad2018}{}}%
+\bibitem[\citeproctext]{ref-rad2018}
 Rad, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ramuxedrez-castauxf1eda2020}{}}%
+\bibitem[\citeproctext]{ref-ramuxedrez-castauxf1eda2020}
 Ramírez-Castañeda, V.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
+\bibitem[\citeproctext]{ref-silberzahn2018many}
 Silberzahn, R., Uhlmann, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-siler2015}{}}%
+\bibitem[\citeproctext]{ref-siler2015}
 Siler, K., Lee, K., \& Bero, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sinatra2015}{}}%
+\bibitem[\citeproctext]{ref-sinatra2015}
 Sinatra, R., Deville, P., Szell, M., Wang, D., \& Barabási, A.-L. (2015). A century of physics. \emph{Nature Physics}, \emph{11}(10), 791--796. \url{https://doi.org/10.1038/nphys3494}
 
-\leavevmode\vadjust pre{\hypertarget{ref-skorb2020}{}}%
+\bibitem[\citeproctext]{ref-singh2023}
+Singh, L., Killen, M., Smetana, \& G., J.
+(2023).
+Global Science Requires Greater Equity, Diversity, and Cultural Precision.
+\emph{APS Observer}, \emph{36}.
+\url{https://www.psychologicalscience.org/observer/gs-equity-diversity-cultural-precision}
+
+\bibitem[\citeproctext]{ref-skorb2020}
 Skorb, L., Aczel, B., Bakos, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-stewart2017}{}}%
+\bibitem[\citeproctext]{ref-stewart2017}
 Stewart, N., Chandler, J., \& Paolacci, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-stewart2020}{}}%
+\bibitem[\citeproctext]{ref-stewart2020}
 Stewart, S., Rinke, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-vanbavel2022}{}}%
+\bibitem[\citeproctext]{ref-sugimoto2017}
+Sugimoto, C.
+R., Robinson-Garcia, N., Murray, D.
+S., Yegros-Yegros, A., Costas, R., \& Larivière, V.
+(2017).
+Scientists have most impact when they're free to move.
+\emph{Nature}, \emph{550}(7674), 29--31.
+\url{https://doi.org/10.1038/550029a}
+
+\bibitem[\citeproctext]{ref-sumathipala2004}
+Sumathipala, A., Siribaddana, S., \& Patel, V.
+(2004).
+Under-representation of developing countries in the research literature: ethical issues arising from a survey of five leading medical journals.
+\emph{BMC Medical Ethics}, \emph{5}(1), 5.
+\url{https://doi.org/10.1186/1472-6939-5-5}
+
+\bibitem[\citeproctext]{ref-uhlmann2019}
+Uhlmann, E.
+L., Ebersole, C.
+R., Chartier, C.
+R., Errington, T.
+M., Kidwell, M.
+C., Lai, C.
+K., McCarthy, R.
+J., Riegelman, A., Silberzahn, R., \& Nosek, B.
+A.
+(2019).
+Scientific Utopia III: Crowdsourcing Science.
+\emph{Perspectives on Psychological Science}, \emph{14}(5), 711--733.
+\url{https://doi.org/10.1177/1745691619850561}
+
+\bibitem[\citeproctext]{ref-vanbavel2022}
 Van Bavel, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-vazire2022}{}}%
+\bibitem[\citeproctext]{ref-vazire2022}
 Vazire, S., Schiavone, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wang2021}{}}%
+\bibitem[\citeproctext]{ref-wang2021}
 Wang, K., Goldenberg, A., Dorison, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wuchty2007}{}}%
+\bibitem[\citeproctext]{ref-wickham2007}
+Wickham, H. (2007). Reshaping Data with the reshape Package. \emph{Journal of Statistical Software}, \emph{21}(1), 1--20. \url{https://doi.org/10.18637/jss.v021.i12}
+
+\bibitem[\citeproctext]{ref-wuchty2007}
 Wuchty, S., Jones, B. F., \& Uzzi, B. (2007). The increasing dominance of teams in production of knowledge. \emph{Science}, \emph{316}(5827), 1036--1039. \url{https://doi.org/10.1126/science.1136099}
 
-\leavevmode\vadjust pre{\hypertarget{ref-xie2014}{}}%
-Xie, Y. (2014). {``}Undemocracy{''}: Inequalities in science. \emph{Science}, \emph{344}(6186), 809--810. \url{https://doi.org/10.1126/science.1252743}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yang2022}{}}%
+\bibitem[\citeproctext]{ref-yang2022}
 Yang, Y., Tian, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-zwaan2018}{}}%
+\bibitem[\citeproctext]{ref-zwaan2018}
 Zwaan, R. A., Etz, A., Lucas, R. E., \& Donnellan, M. B. (2018). Making replication mainstream. \emph{Behavioral and Brain Sciences}, \emph{41}, e120. \url{https://doi.org/10.1017/S0140525X17001972}
@@
 
-\endgroup
-
 \newpage
 
-\hypertarget{appendix-appendix}{%
-\appendix}
-
-\hypertarget{supplemental-materials}{%
-\section{Supplemental Materials}\label{supplemental-materials}}
-
-\hypertarget{rq1-publisher-information.-1}{%
-\subsection{RQ1: Publisher Information.}\label{rq1-publisher-information.-1}}
-
-\hypertarget{number-of-journals-1}{%
-\subsubsection{Number of Journals}\label{number-of-journals-1}}
-
-Table \ref{tab:tab-snip} indicates the SNIP values for BTS publications, while Table \ref{tab:tab-snip-all}.
-The results from these tables indicate that impact values are slightly higher for BTS publications, while the overall median, minimum, and maximum are the same for each grouping.
-
-\newpage
+\section{Supplement}\label{supplement}
+
+We have included several supplemental tables and figures for visualization of results discussed in the manuscript.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{figure/figure_3_growth} \caption{Exponential growth rate estimates with 95\% confidence intervals.}\label{fig:rate-estimates-fig}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{figure/figure_6_map} \caption{Geopolitical regions represented in big-team science publications versus all publications.
+The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right.
+Therefore, North America represents the largest number of authors within BTS (i.e., bottom right, then separated into the geopolitical areas within that subregion), followed by Eastern Europe (top left), and so on.}\label{fig:fig-map-both}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{figure/figure_8_author_effect_gpe} \caption{Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
+Larger dots indicate more papers and authors represented in the calculation of effect size.}\label{fig:fig-effect-gpe}
+\end{figure}
 
@@
 
-\caption{\label{tab:tab-snip}Big-Team Science SNIP Values}
-
-\begin{tabular}{llllll}
+\caption{\label{tab:big-teams-table}Number of Authors and Papers by Subject Area}
+
+\begin{tabular}{lccccc}
 \toprule
-Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
+Number of Authors & \multicolumn{1}{c}{Statistic} & \multicolumn{1}{c}{Health Sciences} & \multicolumn{1}{c}{Physical Sciences} & \multicolumn{1}{c}{Social Sciences} & \multicolumn{1}{c}{Life Sciences}\\
 \midrule
-Health Sciences & 2.36 & 3.59 & 0.00 & 1.58 & 173.93\\
-Physical Sciences & 1.57 & 1.17 & 0.00 & 1.27 & 30.40\\
-Social Sciences & 1.94 & 1.72 & 0.00 & 1.52 & 30.40\\
-Life Sciences & 2.02 & 1.60 & 0.00 & 1.51 & 19.07\\
+2+ & Authors & 12,096,908 & 15,366,570 & 5,182,626 & 11,557,780\\
+11+ & Authors & 2,726,450 & 1,513,520 & 445,271 & 2,208,278\\
+50+ & Authors & 767,322 & 319,453 & 65,409 & 378,522\\
+100+ & Authors & 502,493 & 217,863 & 34,708 & 214,346\\
+2+ & Papers & 8,758,846 & 17,195,880 & 3,441,064 & 8,705,266\\
+11+ & Papers & 507,871 & 255,587 & 38,011 & 352,012\\
+50+ & Papers & 17,184 & 26,010 & 894 & 8,690\\
+100+ & Papers & 5,429 & 15,009 & 242 & 2,622\\
 \bottomrule
+\addlinespace
 \end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Papers can be classified into multiple categories.}
+\end{tablenotes}
 
@@
 
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tab-snip-all}All Journal Articles SNIP Values}
-
-\begin{tabular}{llllll}
-\toprule
-Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
-\midrule
-Health Sciences & 1.45 & 2.87 & 0.00 & 1.15 & 173.93\\
-Physical Sciences & 1.08 & 0.77 & 0.00 & 0.97 & 30.40\\
-Social Sciences & 1.32 & 1.03 & 0.00 & 1.15 & 30.40\\
-Life Sciences & 1.19 & 0.86 & 0.00 & 1.06 & 19.07\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{rq2-publication-information.-1}{%
-\subsection{RQ2: Publication Information.}\label{rq2-publication-information.-1}}
-
-\hypertarget{keywords}{%
-\subsubsection{Keywords}\label{keywords}}
-
-Figure \ref{fig:fig-keywords} indicates the most common keywords present for the BTS publications by subject area.
-The keywords were tokenized into single tokens.
-Keywords were then lower cased, and all stop words (for example, the, an, of, into, for) were removed.
-Finally, a frequency count of tokens was tabulated for each subject area, and this count is used to create the final word cloud presented.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-keywords-1.pdf}
-\caption{\label{fig:fig-keywords}Keyword Analysis for Each of the Four Subject Areas.}
-\end{figure}
-
-\hypertarget{rq3-authors}{%
-\subsection{RQ3: Authors}\label{rq3-authors}}
-
-\hypertarget{institution}{%
-\subsubsection{Institution}\label{institution}}
-
-Institution was normalized by taking the total number of unique institutions and dividing by the total number of institution listings.
-The patterns are similar for each decade in that papers are often either half unique institutions or mostly unique institutions overall as shown in Figure \ref{fig:fig-inst}.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-inst-1.pdf}
-\caption{\label{fig:fig-inst}Number of unique institutions involved in big-team science papers across decades.}
-\end{figure}
-
-\hypertarget{education-1}{%
-\subsubsection{Education}\label{education-1}}
-
-As noted in our pre-registration, we would only present this variable if we could obtain at least 50\% information on the authors who publish in big team science papers.
-95.83\% of the data was not available.
-
-\hypertarget{types-of-publications-1}{%
-\subsubsection{Types of Publications}\label{types-of-publications-1}}
-
-Types of publications are presented in Figure \ref{fig:fig-pub-types}.
-The patterns of publications are roughly similar for big team science authors and all authors.
-It appears that proportionally, big team members are more likely to post preprints in comparison to all authors.
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_scopus_unmasked_files/figure-latex/fig-pub-types-1.pdf}
-\caption{\label{fig:fig-pub-types}Types of publications for big-team science and all authors.}
-\end{figure}
-
 \end{document}

### 2025-06-10 manuscript_definition.Rmd
edits edits edits

@@
 
-  Funding: No funding was obtained for this project.
+  Funding: No funding was obtained for this project. #we staying with this even though it helped with coding errors?
 
@@
   Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (https://osf.io/f2dtr) but then was updated with access to the Scopus database for a broader picture of BTS projects (https://osf.io/fheun).
-After review, we updated the manuscript to reflect that the definition of big team science is unclear, and focused on a data-driven definition to explore our research questions.
+After peer review, the preregisteration was updated to address the unclear definition of big team science to focus on a data-driven definition to explore the research questions.
 
@@
 
-keywords          : "big team, science, authorship, credit"
+keywords          : "big team science, team science, authorship, credit"
 floatsintext      : yes
@@
 Scientific discovery has increasingly become a collaborative process,
-and the scale and scope of team science have dramatically expanded in
+with the scale and scope of team science have dramatically expanded in
 recent years [@council2015]. Collaboration in scientific endeavors
-involves multiple researchers at (potentially) multiple institutions to
+involves multiple researchers (potentiality) at multiple institutions to
 communicate and work together to advance knowledge in their chosen
-field(s). Collaboration can manifest uniquely in each project dependent
-on the skill sets, hypotheses, and perspectives of collaborators. One
-key aspect of collaboration is the flexibility allotted as it is shaped
-by the needs of the project and the researchers involved. While
-collaboration is not new in science, interest in "team science" is
+field(s). This unique composition of a collaboration for each project is 
+dependent on the skill sets, hypotheses, and perspectives of collaborators 
+involved. A key strength of collaboration lies in its flexibility, allowing it 
+to adapt to the needs of the project and the researchers themselves.
+
+While collaboration is not new in science, interest in "team science" is
 growing as individual researchers seek an interdisciplinary approach to
@@
 The movement toward team science reflects demands of modern research to
-answer complex questions, meet funder and university desires for
-interdisciplinary research, and the desire to increase diversity of
-scientific representation [@council2015]. Further, the evolution of team
-science reflects broader shifts in research practices, driven by two
-sources: 1) increasing globalization and technology that allows for
-real-time interdisciplinary research [@jones2008], and 2) expanding
-interest in reproducibility, replication, and generalizability [i.e.,
-the credibility movement, @maxwell2015; @nelson2018; @zwaan2018;
-@vazire2022]. Technological advances have provided easier ways to
+answer complex questions, meet funding agencies and universities desires for
+interdisciplinary research, and the desire to increase scientific representation
+[@council2015]. Further, the evolution of team science reflects broader shifts
+in research practices, driven by two sources: 1) increasing globalization 
+and technology that allows for real-time interdisciplinary research [
+@jones2008], and 2) expanding interest in reproducibility, replication, 
+and generalizability [i.e., the credibility movement, @maxwell2015; @nelson2018; 
+@zwaan2018; @vazire2022]. Technological advances have provided easier ways to
 collaborate with people who are from other universities and countries
@@
 prior work has shown that publications from larger teams tend to receive
-more citations and have broader impact [[@larivière2015], which may
+more citations and have broader impact [@larivière2015], which may
 further incentivize early-career involvement despite the structural

### 2025-06-10 manuscript_definition.tex
edits edits edits

@@
 \makeatother
-\keywords{big team, science, authorship, credit}
+\keywords{big team science, team science, authorship, credit}
 \usepackage{lineno}
@@
   pdflang={en-EN},
-  pdfkeywords={big team, science, authorship, credit},
+  pdfkeywords={big team science, team science, authorship, credit},
   hidelinks,
@@
 
-Funding: No funding was obtained for this project.
+Funding: No funding was obtained for this project. \#we staying with this even though it helped with coding errors?
 
@@
 Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr}) but then was updated with access to the Scopus database for a broader picture of BTS projects (\url{https://osf.io/fheun}).
-After review, we updated the manuscript to reflect that the definition of big team science is unclear, and focused on a data-driven definition to explore our research questions.
+After peer review, the preregisteration was updated to address the unclear definition of big team science to focus on a data-driven definition to explore the research questions.
 
@@
 Scientific discovery has increasingly become a collaborative process,
-and the scale and scope of team science have dramatically expanded in
+with the scale and scope of team science have dramatically expanded in
 recent years (Council et al., 2015). Collaboration in scientific endeavors
-involves multiple researchers at (potentially) multiple institutions to
+involves multiple researchers (potentiality) at multiple institutions to
 communicate and work together to advance knowledge in their chosen
-field(s). Collaboration can manifest uniquely in each project dependent
-on the skill sets, hypotheses, and perspectives of collaborators. One
-key aspect of collaboration is the flexibility allotted as it is shaped
-by the needs of the project and the researchers involved. While
-collaboration is not new in science, interest in ``team science'' is
+field(s). This unique composition of a collaboration for each project is
+dependent on the skill sets, hypotheses, and perspectives of collaborators
+involved. A key strength of collaboration lies in its flexibility, allowing it
+to adapt to the needs of the project and the researchers themselves.
+
+While collaboration is not new in science, interest in ``team science'' is
 growing as individual researchers seek an interdisciplinary approach to
@@
 The movement toward team science reflects demands of modern research to
-answer complex questions, meet funder and university desires for
-interdisciplinary research, and the desire to increase diversity of
-scientific representation (Council et al., 2015). Further, the evolution of team
-science reflects broader shifts in research practices, driven by two
-sources: 1) increasing globalization and technology that allows for
-real-time interdisciplinary research (B. F. Jones et al., 2008), and 2) expanding
-interest in reproducibility, replication, and generalizability (i.e.,
-the credibility movement, Maxwell et al., 2015; Nelson et al., 2018; Vazire et al., 2022; Zwaan et al., 2018). Technological advances have provided easier ways to
+answer complex questions, meet funding agencies and universities desires for
+interdisciplinary research, and the desire to increase scientific representation
+(Council et al., 2015). Further, the evolution of team science reflects broader shifts
+in research practices, driven by two sources: 1) increasing globalization
+and technology that allows for real-time interdisciplinary research (B. F. Jones et al., 2008), and 2) expanding interest in reproducibility, replication,
+and generalizability (i.e., the credibility movement, Maxwell et al., 2015; Nelson et al., 2018; Vazire et al., 2022; Zwaan et al., 2018). Technological advances have provided easier ways to
 collaborate with people who are from other universities and countries
@@
 prior work has shown that publications from larger teams tend to receive
-more citations and have broader impact {[}(Larivière et al., 2015), which may
+more citations and have broader impact (Larivière et al., 2015), which may
 further incentivize early-career involvement despite the structural

### 2025-06-17 manuscript_definition.Rmd
updating for publication

@@
 
-  Funding: No funding was obtained for this project. #we staying with this even though it helped with coding errors?
-
-  Artificial intelligence: No AI resources were used for this manuscript.
+  Funding: No funding was obtained for this project.
+
+  Artificial Intelligence: Artificial Intelligence tools (e.g., ChatGPT) were used to assist in debugging and resolving coding errors.
 
@@
 involved. A key strength of collaboration lies in its flexibility, allowing it 
-to adapt to the needs of the project and the researchers themselves.
-
-While collaboration is not new in science, interest in "team science" is
+to adapt to the needs of the project and the researchers themselves.  While collaboration is not new in science, interest in "team science" is
 growing as individual researchers seek an interdisciplinary approach to
@@
 characteristics. Now, grassroots organizations, such as the
-Psychological Science Accelerator [@moshontz2018], ManyBabies
+Psychological Science Accelerator (<https://psysciacc.org>), ManyBabies
 (<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>),
@@
 for BTS studies have provided an incredible wealth of data for the
-scientific community, we do not yet know exactly how to define BTS -
-which is generally termed "an unusually large number of collaborators"
+scientific community, we do not yet know exactly how to define BTS: which is generally termed "an unusually large number of collaborators"
 [@forscher2022a; @coles2022].
@@
 -   Research Question 1: Exploring historical and current publication
-    values, what should define big team science versus team science?
+    values, what should define big team science versus traditional team science?
     -   Question 1A: What number of authors and institutional
-        affiliations should designate the differences between team
-        science and big team science?
+        affiliations should designate the differences between traditional team science and big team science?
     -   Question 1B: Using the definition from 1A, are there changes in
         the number of publications over time?
--   Research Question 2: How has the diversity of those involved in team
+-   Research Question 2: How has the diversity of those involved in traditional team
     science and big team science changed over time?
@@
 ```{r total-papers}
+num <- function(x){
+  format(x, big.mark = ",", scientific = FALSE)
+}
+
 total_papers <- 97532104 # the entire database
@@
 The total number of papers included in the Scopus database at the time
-of this analysis was `r total_papers`. `r total_papers_past1970`
+of this analysis was `r num(total_papers)`. `r num(total_papers_past1970)`
 articles were included past 1970 in the defined article types, which
-included `r distinct_authors_past1970` distinct authors. We then
+included `r num(distinct_authors_past1970)` distinct authors. We then
 filtered the data to include only teams, which was defined as two
 authors from at least two institutions. The total number of papers for
-team projects was `r team_author_aff_papers` and
-`r team_author_aff_author` distinct authors. The data was then
+team projects was `r num(team_author_aff_papers)` and
+`r num(team_author_aff_author)` distinct authors. The data was then
 classified into subject areas by paper, which lead to missing data. The
-final number of papers included was `r team_author_aff_papers_noNA` with
-`r team_author_aff_author_noNA` distinct authors. The dataset was
+final number of papers included was `r num(team_author_aff_papers_noNA)` with
+`r num(team_author_aff_author_noNA)` distinct authors. The dataset was
 curated to include one row per author, paper, and subject area (i.e.,
 long format [@wickham2007]) which included
-`r team_author_aff_subject_noNA` total rows of data.
+`r num(team_author_aff_subject_noNA)` total rows of data.
 
@@
 
+We applied a consistent definition of Big Team Science (BTS) across all four research domains in our analysis.
+As shown in Figure \@ref(fig:fig-stats-authors), the 90th percentile of team size is consistent across subject areas, varying by only four authors (e.g., from 7 to 11), which supports the use of a unified threshold.
+Over time (Figure \@ref(fig:fig-paper-time)), we observe increasing publication counts in all fields.
+While social sciences currently lag behind in both volume and growth rate, we anticipate continued growth as more infrastructure and funding are directed toward collaborative efforts in this area.
+Unlike fields such as health sciences, which often benefit from greater financial resources and institutional support (e.g., through IRBs and clinical networks), social science collaborations face unique structural barriers that may slow their expansion.
+Additionally, defining BTS consistently across fields is methodologically important because many publications are interdisciplinary and assigned to multiple subject categories.
+A unified operationalization allows for clearer comparisons and avoids arbitrary distinctions between overlapping research areas.
+
 ```{r echo = FALSE}
@@
 big teams using our 90th percentile definition. The total number of
-distinct authors for big team papers was `r big_teams_papers` with
-`r big_teams_authors` distinct authors. In RQ2, we split the big team
-data into small (11-49), medium (50-99), and large big team (100+)
-groupings for convenience to display/analyze geopolitical regions. The
+distinct authors for big team papers was `r num(big_teams_papers)` with
+`r num(big_teams_authors)` distinct authors. In RQ2, we split the big team
+data into bins using 11-49 authors, 50-99 authors, and 100+ authors groupings for convenience to display/analyze geopolitical regions. The
 table shows the number of authors and papers for those analyses.
@@
 
-For analyzing changes across time, we split the data into team science
+For analyzing changes across time, we split the data into traditional team science
 projects (2-10 authors, 2-5 affiliations) and BTS projects (as defined
@@
 \@ref(fig:fig-paper-time). The visual results indicated that the number
-of team science papers was increasing the most in physical sciences for
+of traditional team science papers was increasing the most in physical sciences for
 all manuscripts, followed by life and health sciences, and the last is
@@
 
-```{r fig-paper-time, include = TRUE, fig.cap = "The number of manuscripts across time for all team science papers (left) and big team science papers (right).", fig.width = 10, fig.height = 6}
+```{r fig-paper-time, include = TRUE, fig.cap = "The number of manuscripts across time for all traditional team science papers (left) and big team science papers (right).", fig.width = 10, fig.height = 6}
 temp <- DF$author_paper_year %>% 
@@
   ylab("Number of Papers") + 
-  ggtitle("Team Science Projects") +
+  ggtitle("Traditional Team Science Projects") +
   theme(legend.title = element_text(size = 15),
@@
 Using the `minpack.lm` library [@elzhov2023], we calculated the
-exponential rate of growth for team science and BTS projects, and these
+exponential rate of growth for traditional team science and BTS projects, and these
 results are shown in Supplemental Figure \@ref(fig:rate-estimates-fig). All growth rate
@@
 in the number of team papers over time. BTS growth rates were always
-higher than their team science counterparts, but the 95% confidence
+higher than their traditional team science counterparts, but the 95% confidence
 intervals for the growth estimate overlapped for all statistics.
@@
                         levels = c("regular", "big"),
-                        labels = c("Team Science", "BTS")))
+                        labels = c("Traditional Team Science", "BTS")))
 
@@
                               levels = c("Regular", "Big"),
-                              labels = c("Team Science", "BTS"))), 
+                              labels = c("Traditional Team Science", "BTS"))), 
        aes(Year, avg_career, color = Team)) +
@@
 Figure \@ref(fig:fig-career) portrays the average career length for
-authors involved in team science and BTS projects over time. Career
+authors involved in traditional team science and BTS projects over time. Career
 length was defined as the year of first publication minus the current
 year, and higher numbers mean longer careers. The general pattern for
-team science and BTS projects is a decrease in average career length
+traditional team science and BTS projects is a decrease in average career length
 over time. However, it appears that, in at least the last two decades,
-BTS projects average a longer career length than team science projects.
+BTS projects average a longer career length than traditional team science projects.
 This trend is visually consistent across all four subject areas
@@
 significantly from one another within their team size, with the
-exception of Health Sciences and Physical Sciences for team science
-teams, whose $b_M$ values overlapped in their confidence intervals.
+exception of Health Sciences and Physical Sciences for traditional team science, whose $b_M$ values overlapped in their confidence intervals.
 Across the remaining comparisons, Life Sciences showed the steepest
@@
 science teams in both $b_M$ and $b_{SD}$, as indicated by
-non-overlapping confidence intervals. Team science teams consistently
+non-overlapping confidence intervals. Traditional team science consistently
 exhibited stronger negative slopes for average publication count than
 BTS teams, reflecting a more pronounced trend toward authors with fewer
-publications appearing over time. This suggests that smaller teams are
+publications appearing over time. This result suggests that smaller teams are
 increasingly composed of researchers with lower overall publication
@@
 the Netherlands), and East Asian countries (e.g., China, Japan, and
-South Korea). In contrast, team science publications showed broader
+South Korea). In contrast, traditional team science publications showed broader
 geographic distribution, with relatively higher representation from
@@
 While both team types were led by traditionally defined Global North
-institutions, the mosaic charts revealed that team science teams
+institutions, the mosaic charts revealed that traditional team science 
 included a more diverse range of countries contributing at moderate
@@
 collaborations, it remains more centralized in historically dominant
-research regions, whereas team science may offer relatively greater
+research regions, whereas traditional team science may offer relatively greater
 global inclusivity at a smaller scale.
@@
 and team types. Additionally, all slopes differed significantly between
-BTS and team science publications, suggesting distinct patterns in the
+BTS and traditional team science publications, suggesting distinct patterns in the
 evolution of international collaboration. Within BTS publications, Life
@@
 Health Sciences. In contrast, all other within-BTS comparisons differed
-significantly. For team science publications, all four disciplines
+significantly. For traditional team science publications, all four disciplines
 showed significantly different slopes, although the magnitudes of these
@@
 = -0.0129). Despite small effect sizes (all $R^2 < .012$), the
-consistent differences between BTS and team science teams point to
+consistent differences between BTS and traditional team science point to
 structural differences in how global participation is evolving across
@@
 other regions (e.g., Asia, Latin America and the Caribbean, and Africa)
-showed gradual increases over time. For team science teams (2–10
+showed gradual increases over time. For traditional team science (2–10
 authors), the dominance of North America and Western Europe in
@@
 affiliations across millions of papers. By comparing BTS publications
-with Team Science publications across four major scientific domains, we
+with traditional team science publications across four major scientific domains, we
 clarify how BTS compares with traditional team science and how it is
@@
 in both BTS and smaller teams. Across all disciplines, the average
-career length of authors decreased significantly over time. Team Science
-teams exhibited even steeper declines in both average and variability of
+career length of authors decreased significantly over time. Traditional team science exhibited even steeper declines in both average and variability of
 career length than big teams, suggesting that smaller teams may be an
@@
 research are potentially driving forces behind our results, but,
-hopefully, the results also point to a decline in scientific gatekeeping
+hopefully, the results also point to a decline in scientific gate keeping
 [@lu2007; @siler2015].
 
-Our results confirm and extend prior observations that both Team Science
+Our results confirm and extend prior observations that both traditional team science
 and BTS are disproportionately concentrated in high-resource, highly
@@
 [@meneghini2007; @ramírez-castañeda2020].
+Another limitation is the process of indexing across time has significantly changed with the availability of the internet.
+For example, in Figure \@ref(fig:fig-paper-time), traditional team science papers show a bump in the number of publications around approximately 1995, and the Web of Science came online in 1997, which included back indexing of journals not previous indexed.
 

### 2025-06-17 manuscript_definition.tex
updating for publication

@@
 
-Funding: No funding was obtained for this project. \#we staying with this even though it helped with coding errors?
-
-Artificial intelligence: No AI resources were used for this manuscript.
+Funding: No funding was obtained for this project.
+
+Artificial Intelligence: Artificial Intelligence tools (e.g., ChatGPT) were used to assist in debugging and resolving coding errors.
 
@@
 involved. A key strength of collaboration lies in its flexibility, allowing it
-to adapt to the needs of the project and the researchers themselves.
-
-While collaboration is not new in science, interest in ``team science'' is
+to adapt to the needs of the project and the researchers themselves. While collaboration is not new in science, interest in ``team science'' is
 growing as individual researchers seek an interdisciplinary approach to
@@
 characteristics. Now, grassroots organizations, such as the
-Psychological Science Accelerator (Moshontz et al., 2018), ManyBabies
+Psychological Science Accelerator (\url{https://psysciacc.org}), ManyBabies
 (\url{https://manybabies.github.io/}), NutNet (\url{https://nutnet.org/}),
@@
 for BTS studies have provided an incredible wealth of data for the
-scientific community, we do not yet know exactly how to define BTS -
-which is generally termed ``an unusually large number of collaborators''
+scientific community, we do not yet know exactly how to define BTS: which is generally termed ``an unusually large number of collaborators''
 (Coles et al., 2022; Forscher et al., 2022).
@@
   Research Question 1: Exploring historical and current publication
-  values, what should define big team science versus team science?
+  values, what should define big team science versus traditional team science?
 
@@
     Question 1A: What number of authors and institutional
-    affiliations should designate the differences between team
-    science and big team science?
+    affiliations should designate the differences between traditional team science and big team science?
   \item
@@
 \item
-  Research Question 2: How has the diversity of those involved in team
+  Research Question 2: How has the diversity of those involved in traditional team
   science and big team science changed over time?
@@
 The total number of papers included in the Scopus database at the time
-of this analysis was 97532104. 62966549
+of this analysis was 97,532,104. 62,966,549
 articles were included past 1970 in the defined article types, which
-included 53622443 distinct authors. We then
+included 53,622,443 distinct authors. We then
 filtered the data to include only teams, which was defined as two
 authors from at least two institutions. The total number of papers for
-team projects was 32454393 and
-28353445 distinct authors. The data was then
+team projects was 32,454,393 and
+28,353,445 distinct authors. The data was then
 classified into subject areas by paper, which lead to missing data. The
-final number of papers included was 32448373 with
-28350468 distinct authors. The dataset was
+final number of papers included was 32,448,373 with
+28,350,468 distinct authors. The dataset was
 curated to include one row per author, paper, and subject area (i.e.,
 long format (Wickham, 2007)) which included
-241269297 total rows of data.
+241,269,297 total rows of data.
 
@@
 
+We applied a consistent definition of Big Team Science (BTS) across all four research domains in our analysis.
+As shown in Figure \ref{fig:fig-stats-authors}, the 90th percentile of team size is consistent across subject areas, varying by only four authors (e.g., from 7 to 11), which supports the use of a unified threshold.
+Over time (Figure \ref{fig:fig-paper-time}), we observe increasing publication counts in all fields.
+While social sciences currently lag behind in both volume and growth rate, we anticipate continued growth as more infrastructure and funding are directed toward collaborative efforts in this area.
+Unlike fields such as health sciences, which often benefit from greater financial resources and institutional support (e.g., through IRBs and clinical networks), social science collaborations face unique structural barriers that may slow their expansion.
+Additionally, defining BTS consistently across fields is methodologically important because many publications are interdisciplinary and assigned to multiple subject categories.
+A unified operationalization allows for clearer comparisons and avoids arbitrary distinctions between overlapping research areas.
+
 Supplemental Table \ref{tab:big-teams-table} includes the number of
@@
 big teams using our 90th percentile definition. The total number of
-distinct authors for big team papers was 968765 with
-4541369 distinct authors. In RQ2, we split the big team
-data into small (11-49), medium (50-99), and large big team (100+)
-groupings for convenience to display/analyze geopolitical regions. The
+distinct authors for big team papers was 968,765 with
+4,541,369 distinct authors. In RQ2, we split the big team
+data into bins using 11-49 authors, 50-99 authors, and 100+ authors groupings for convenience to display/analyze geopolitical regions. The
 table shows the number of authors and papers for those analyses.
@@
 \ref{fig:fig-paper-time}. The visual results indicated that the number
-of team science papers was increasing the most in physical sciences for
+of traditional team science papers was increasing the most in physical sciences for
 all manuscripts, followed by life and health sciences, and the last is
@@
 \pandocbounded{\includegraphics[keepaspectratio]{manuscript_definition_files/figure-latex/fig-paper-time-1.pdf}}
-\caption{\label{fig:fig-paper-time}The number of manuscripts across time for all team science papers (left) and big team science papers (right).}
+\caption{\label{fig:fig-paper-time}The number of manuscripts across time for all traditional team science papers (left) and big team science papers (right).}
 \end{figure}
@@
 Using the \texttt{minpack.lm} library (Elzhov et al., 2023), we calculated the
-exponential rate of growth for team science and BTS projects, and these
+exponential rate of growth for traditional team science and BTS projects, and these
 results are shown in Supplemental Figure \ref{fig:rate-estimates-fig}. All growth rate
@@
 in the number of team papers over time. BTS growth rates were always
-higher than their team science counterparts, but the 95\% confidence
+higher than their traditional team science counterparts, but the 95\% confidence
 intervals for the growth estimate overlapped for all statistics.
@@
 Figure \ref{fig:fig-career} portrays the average career length for
-authors involved in team science and BTS projects over time. Career
+authors involved in traditional team science and BTS projects over time. Career
 length was defined as the year of first publication minus the current
 year, and higher numbers mean longer careers. The general pattern for
-team science and BTS projects is a decrease in average career length
+traditional team science and BTS projects is a decrease in average career length
 over time. However, it appears that, in at least the last two decades,
-BTS projects average a longer career length than team science projects.
+BTS projects average a longer career length than traditional team science projects.
 This trend is visually consistent across all four subject areas
@@
 significantly from one another within their team size, with the
-exception of Health Sciences and Physical Sciences for team science
-teams, whose \(b_M\) values overlapped in their confidence intervals.
+exception of Health Sciences and Physical Sciences for traditional team science, whose \(b_M\) values overlapped in their confidence intervals.
 Across the remaining comparisons, Life Sciences showed the steepest
@@
 science teams in both \(b_M\) and \(b_{SD}\), as indicated by
-non-overlapping confidence intervals. Team science teams consistently
+non-overlapping confidence intervals. Traditional team science consistently
 exhibited stronger negative slopes for average publication count than
 BTS teams, reflecting a more pronounced trend toward authors with fewer
-publications appearing over time. This suggests that smaller teams are
+publications appearing over time. This result suggests that smaller teams are
 increasingly composed of researchers with lower overall publication
@@
 While both team types were led by traditionally defined Global North
-institutions, the mosaic charts revealed that team science teams
+institutions, the mosaic charts revealed that traditional team science
 included a more diverse range of countries contributing at moderate
@@
 = -0.0129). Despite small effect sizes (all \(R^2 < .012\)), the
-consistent differences between BTS and team science teams point to
+consistent differences between BTS and traditional team science point to
 structural differences in how global participation is evolving across
@@
 other regions (e.g., Asia, Latin America and the Caribbean, and Africa)
-showed gradual increases over time. For team science teams (2--10
+showed gradual increases over time. For traditional team science (2--10
 authors), the dominance of North America and Western Europe in
@@
 research are potentially driving forces behind our results, but,
-hopefully, the results also point to a decline in scientific gatekeeping
+hopefully, the results also point to a decline in scientific gate keeping
 (Lu, 2007; Siler et al., 2015).
 
-Our results confirm and extend prior observations that both Team Science
+Our results confirm and extend prior observations that both traditional team science
 and BTS are disproportionately concentrated in high-resource, highly
@@
 (Meneghini \& Packer, 2007; Ramírez-Castañeda, 2020).
+Another limitation is the process of indexing across time has significantly changed with the availability of the internet.
+For example, in Figure \ref{fig:fig-paper-time}, traditional team science papers show a bump in the number of publications around approximately 1995, and the Web of Science came online in 1997, which included back indexing of journals not previous indexed.
 

### 2025-07-15 appendix.Rmd
fixing author typo
updated formatting
changes to resubmit
updating manuscript

--- 2023-08-15 appendix.Rmd
@@
----
-appendix: "appendix.Rmd"
----
+# Supplemental Material
 
-# Supplemental Materials
+We have included several supplemental tables and figures for visualization of results discussed in the manuscript.
 
-## RQ1: Publisher Information.
-
-```{r setup-appendix}
-knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, error = FALSE)
-library(papaja)
-library(knitr)
-library(ggplot2)
-library(treemapify)
-library(countrycode)
-library(rio)
-library(maps)
-library(dplyr)
-library(tidyr)
-library(MOTE)
-library(MBESS)
-library(patchwork)
-library(ggplot2)
-library(ggwordcloud)
-library(figpatch)
-library(RColorBrewer)
-library(latex2exp)
-library(ggridges)
+```{r rate-estimates-fig, include = TRUE, fig.cap = "Exponential growth rate estimates with 95% confidence intervals.", out.width='100%'}
+knitr::include_graphics("figure/figure_3_growth.png")
 ```
 
-**Number of Journals**.
-
-Table \@ref(tab:tab-snip) indicates the SNIP values for BTS publications, while Table \@ref(tab:tab-snip-all).
-The results from these tables indicate that impact values are slightly higher for BTS publications, while the overall median, minimum, and maximum are the same for each grouping.
-
-```{r tab-snip, results = 'asis', include = TRUE}
-# updated
-apa_table(
-  DF$snip %>% 
-    filter(`Subject Area` != "Multidisciplinary") %>% 
-    mutate(M = apa_num(M), 
-           SD = apa_num(SD), 
-           Minimum = apa_num(Minimum), 
-           Median = apa_num(Median), 
-           Maximum = apa_num(Maximum)), 
-  caption = "Big-Team Science SNIP Values")
+```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.
+The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right.
+Therefore, North America represents the largest number of authors within BTS (i.e., bottom right, then separated into the geopolitical areas within that subregion), followed by Eastern Europe (top left), and so on.", out.width='100%'}
+knitr::include_graphics("figure/figure_6_map.png")
 ```
 
-```{r tab-snip-all, results = 'asis', include = TRUE}
-# updated
-apa_table(
-  DF$snip_all %>% 
-    filter(`Subject Area` != "Multidisciplinary") %>% 
-    mutate(M = apa_num(M), 
-           SD = apa_num(SD), 
-           Minimum = apa_num(Minimum), 
-           Median = apa_num(Median), 
-           Maximum = apa_num(Maximum)),
-  caption = "All Journal Articles SNIP Values")
+```{r fig-effect-gpe, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
+Larger dots indicate more papers and authors represented in the calculation of effect size.", out.width='100%'}
+knitr::include_graphics("figure/figure_8_author_effect_gpe.png")
 ```
 
-## RQ2: Publication Information.
+```{r big-teams-table, results = 'asis'}
+big_teams_papers <- 968765
+big_teams_authors <- 4541369
 
-**Keywords**.
-Figure \@ref(fig:fig-keywords) indicates the most common keywords present for the BTS publications by subject area.
-The keywords were tokenized into single tokens.
-Keywords were then lowercased, and all stop words (for example, the, an, of, into, for) were removed.
-Finally, a frequency count of tokens was tabulated for each subject area, and this count is used to create the final word cloud presented.
-
-```{r make-clouds2, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
-### NOTE YOU WILL NEED TO RERUN THIS ###
-# health
-health_cloud <- DF$keywords %>% 
-   filter(SubjectArea == "Health Sciences") %>% 
-   ungroup() %>% 
-   select(keywords_nostop, count) %>% 
-  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/health_key.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# physical
-physical_cloud <- DF$keywords %>% 
-   filter(SubjectArea == "Physical Sciences") %>% 
-   ungroup() %>% 
-   select(keywords_nostop, count) %>% 
-  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/physical_key.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# life
-life_cloud <- DF$keywords %>% 
-   filter(SubjectArea == "Life Sciences") %>% 
-   ungroup() %>% 
-   select(keywords_nostop, count) %>% 
-  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/life_key.png", dpi = 300, width = 8,
-       height = 4, units = "in")
-
-# social 
-social_cloud <- DF$keywords %>% 
-   filter(SubjectArea == "Social Sciences") %>% 
-   ungroup() %>% 
-   select(keywords_nostop, count) %>% 
-  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
-  ggplot() + 
-  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
-  theme_minimal() + 
-  scale_size_area(max_size = 15)
-
-ggsave("figure/social_key.png", dpi = 300, width = 8,
-       height = 4, units = "in")
+apa_table(DF$paper_stats %>% 
+        arrange(Statistic), 
+        caption = "Number of Authors and Papers by Subject Area",
+        note = "Papers can be classified into multiple categories.", 
+        align = c("l", rep("c", 5)), 
+        digits = 0)
 ```
-
-```{r fig-keywords, include = TRUE, fig.cap="Keyword Analysis for Each of the Four Subject Areas."}
-health_key <- fig("figure/health_key.png")
-physical_key <- fig("figure/physical_key.png") 
-life_key <- fig("figure/life_key.png") 
-social_key <- fig("figure/social_key.png")
-
-health_key + ggtitle("Health Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-physical_key + ggtitle("Physical Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-life_key + ggtitle("Life Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) + 
-social_key + ggtitle("Social Sciences") + 
-  theme(plot.title = element_text(hjust = 0.5)) +
-  plot_layout(ncol = 2, 
-              nrow = 2)
-
-ggsave("figure/figure_app_1.png")
-```
-
-## RQ3: Authors
-
-**Institution**.
-
-Institution was normalized by taking the total number of unique institutions and dividing by the total number of institution listings.
-The patterns are similar for each decade in that papers are often either half unique institutions or mostly unique institutions overall as show in Figure \@ref(fig:fig-inst).
-
-```{r fig-inst, include = TRUE, fig.cap="Number of unique institutions involved in big-team science papers across decades."}
-DF$inst_time$normalized <- DF$inst_time$unique / DF$inst_time$total * 100
-
-graph_data_inst <- DF$inst_time %>% 
-         filter(SubjectArea != "Multidisciplinary") %>% 
-         mutate(Decade = ifelse(Year < 1990, "1980s", 
-                         ifelse(Year < 2000, "1990s", 
-                                ifelse(Year < 2010, "2000s", 
-                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
-  mutate(Decade = as.factor(Decade))
-
-picture <- ggplot(graph_data_inst,
-                  aes(y = Decade, x = normalized)) + 
-  geom_density_ridges2() + 
-  theme_classic() + 
-  facet_wrap(~SubjectArea) + 
-  xlab("Percent of Unique Affiliations") + 
-  ylab("Decade") +
-  coord_cartesian(xlim = c(0, 100))
-
-suppressWarnings(print(picture))
-
-ggsave("figure/figure_app_2.png")
-```
-
-***Education***.
-As noted in our pre-registration, we would only present this variable if we could obtain at least 50% information on the authors who publish in big team science papers.
-`r apa_num(24228428/25282810*100)`% of the data was not available.
-
-***Types of Publications***.
-
-Types of publications are presented in Figure \@ref(fig:fig-pub-types).
-The patterns of publications are roughly similar for big team science authors and all authors.
-It appears that porportionally, big team members are more likely to post preprints in comparison to all authors.
-
-```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
-pub_levels <- c("ab", "ar", "ip", "bk", "bz", "ch", "cp", 
-                "cr", "dp", "ed", "er", "le", "no", "pp", 
-                "pr", "rp", "re", "sh", "tb")
-pub_labels <- c("Abstract", "Article", "In Press", "Book", "Business", "Book Chapter", "Conference Paper", 
-                "Conference Report", "Data Paper", "Editorial", "Erratum", "Letter", "Note", 
-                "Preprint", "Press Release", "Report", "Review", "Survey", "Retracted")
-
-pub_types <- bind_rows(
-  DF$pub_types %>% mutate(type = "Big Team"), 
-  DF$normal_pub_type %>% mutate(type = "All Papers")) %>% 
-    filter(!is.na(publication_type)) %>% 
-  filter(publication_type != "cb") %>% 
-  mutate(publication_type = factor(publication_type, 
-                                   levels = pub_levels,
-                                   labels = pub_labels)) %>% 
-  mutate(binned_count = ifelse(
-    count < 10000, "< 10,000", ifelse(
-      count > 10000 & count < 100000, "10,000 - 99,999", ifelse(
-        count > 100000 & count < 1000000, "100,000 - 999,999", ifelse(
-          count > 1000000 & count < 10000000, "1,000,000 - 9,999,999", "> 10,000,000"
-        )
-      )
-    )
-  )) %>% 
-  mutate(binned_count = factor(binned_count,
-                               levels = c("< 10,000", 
-                                          "10,000 - 99,999",
-                                          "100,000 - 999,999", 
-                                          "1,000,000 - 9,999,999",
-                                          "> 10,000,000")))
-
-ggplot(pub_types, aes(area = count, fill = binned_count,
-               label = publication_type)) +
-  geom_treemap() +
-  facet_wrap(~type) + 
-  geom_treemap_text(colour = "black", place = "centre",
-                    size = 15, grow = FALSE) +  
-  # scale_fill_brewer(name = "Sample Size", palette = "Spectral") +
-  theme_classic()
-
-ggsave("figure/figure_app_3.png")
-# can probably figure out how to combine these feasibly to make it readable
-# ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.
-```

### 2025-07-15 manuscript_definition.Rmd
updating manuscript

@@
 output            : papaja::apa6_pdf
+appendix          : "appendix.Rmd"
 ---
@@
 
-# Supplement
-
-We have included several supplemental tables and figures for visualization of results discussed in the manuscript.
-
-```{r rate-estimates-fig, include = TRUE, fig.cap = "Exponential growth rate estimates with 95% confidence intervals.", out.width='100%'}
-knitr::include_graphics("figure/figure_3_growth.png")
+# (APPENDIX) Appendix {.unnumbered}
+
+```{r child = "appendix.Rmd"}
 ```
-
-```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.
-The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right.
-Therefore, North America represents the largest number of authors within BTS (i.e., bottom right, then separated into the geopolitical areas within that subregion), followed by Eastern Europe (top left), and so on.", out.width='100%'}
-knitr::include_graphics("figure/figure_6_map.png")
-```
-
-```{r fig-effect-gpe, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year.
-Larger dots indicate more papers and authors represented in the calculation of effect size.", out.width='100%'}
-knitr::include_graphics("figure/figure_8_author_effect_gpe.png")
-```
-
-```{r big-teams-table, results = 'asis'}
-big_teams_papers <- 968765
-big_teams_authors <- 4541369
-
-apa_table(DF$paper_stats %>% 
-        arrange(Statistic), 
-        caption = "Number of Authors and Papers by Subject Area",
-        note = "Papers can be classified into multiple categories.", 
-        align = c("l", rep("c", 5)), 
-        digits = 0)
-```

### 2025-08-11 manuscript_definition.Rmd
fixing figure

@@
 abstract: |
-  This paper examined the nature of publications in Big Team Science (BTS): large-scale collaborations between multiple researchers at multiple institutions.
-These projects can improve research by initiating collaborations that span across the globe, age groups, education levels, and subfields of research.
-As the number of BTS publications increase, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
-We examined the diversity of BTS publications and authors across more than half a million articles to investigate where and what is currently published, and author characteristics including differences in career length, publication metrics, affiliation, and affiliation geopolitical regions.
-Interestingly, BTS publications are increasingly dominated by early career researchers from WEIRD geopolitical regions with Health and Physical Science accounting for the majority of BTS articles.
-However, the increase in preprints, BTS articles, and non-WEIRD authors across time demonstrate the efforts of the science community to diversify its researchers.
-
-    Significance statement: This study is the first large-scale, data-driven analysis of authorship in Big Team Science (BTS), defined here as collaborations with 11 or more authors across six or more institutions.
-Drawing on millions of published works across four scientific domains, we show that BTS has grown rapidly in recent years and increasingly includes early-career researchers and contributors from a broader range of geopolitical regions.
-However, inclusion in BTS is not equally distributed.
-While author lists are becoming more globally diverse overall, leadership roles—particularly first and corresponding authorships, remain disproportionately concentrated in high-income countries, especially in Europe and North America.
-These findings highlight both the promise and limitations of BTS as a vehicle for global, inclusive science, underscoring the need for structural reforms to ensure equity in recognition and participation.
+  This study presents the first large-scale, data-driven analysis of authorship in Big Team Science (BTS) drawing on over half a million articles across four scientific domains.
+Using the top decile of the data, we defined BTS as collaborations with 11+ authors across six or more institutions.
+We compared BTS with traditional team science to investigate changes in publication rates, authorship characteristics, and global representation.
+Publication rates for traditional team science and BTS have both risen over time, but the growth trajectory varies depending on the subject area.
+We found that early-career researchers are increasingly represented in both BTS and smaller teams, suggesting greater accessibility over time.
+Leadership roles remain concentrated in high-income, WEIRD regions for smaller teams.
+This work contributes a replicable, empirical definition of BTS and highlights the need for more equitable recognition and inclusion in large-scale scientific collaboration.
 
@@
 Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review.
-
-  Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (https://osf.io/f2dtr) but then was updated with access to the Scopus database for a broader picture of BTS projects (https://osf.io/fheun).
-After peer review, the preregisteration was updated to address the unclear definition of big team science to focus on a data-driven definition to explore the research questions.
-
-  Materials, Data, Analysis Scripts: All materials and code can be found on our OSF page: https://osf.io/cgx6u/ or corresponding GitHub archive: https://github.com/doomlab/big_team_who.
+A reproducible version of this manuscript can be found at: https://doi.org/10.24433/CO.2018846.v1.
+
+  Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (https://doi.org/10.17605/OSF.IO/F2DTR) but then was updated with access to the Scopus database for a broader picture of BTS projects (https://doi.org/10.17605/OSF.IO/FHEUN).
+After peer review, the pre-registration was updated to address the unclear definition of big team science to focus on a data-driven definition to explore the research questions.
+
+  Materials: All study materials are publicly available (https://doi.org/10.5281/zenodo.15936025).
+
+  Data: Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review (https://doi.org/10.5281/zenodo.15936025).
+
+  Analysis scripts: All analysis scripts are publicly available (https://doi.org/10.5281/zenodo.15936025).
 
@@
   theme(legend.title = element_text(size = 15),
-    legend.text = element_text(size = 12))
+    legend.text = element_text(size = 15))
 

### 2025-08-11 manuscript_definition.Rmd
updating disclosures

@@
 
-  Computational reproducibility: All materials and code can be found on our OSF page: https://osf.io/cgx6u/ or corresponding GitHub archive: https://github.com/doomlab/big_team_who.
-Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review.
-A reproducible version of this manuscript can be found at: https://doi.org/10.24433/CO.2018846.v1.
+  Computational reproducibility: A reproducible version of this manuscript can be found at: https://doi.org/10.24433/CO.2018846.v1, which is linked to GitHub (https://github.com/doomlab/big_team_who) and archived at Zenodo (https://doi.org/10.5281/zenodo.15936025).
+Elsevier has authorized use of the Scopus database to execute and validate the code for retrieving and summarizing article records.
+Although we cannot distribute Scopus data directly, we provide all code, processing steps, and derived outputs necessary to reproduce the analyses presented in this manuscript.
 
@@
 
-  Data: Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review (https://doi.org/10.5281/zenodo.15936025).
+  Data: All data from Scopus outputs are publicly available (https://doi.org/10.5281/zenodo.15936025).
 
@@
 library(tidyr)
-library(MOTE)
-library(MBESS)
+library(MOTE) # use the dev version
+# devtools::install_github("doomlab/MOTE")
+# updated to lessen dependencies
 library(patchwork)
 library(ggplot2)
-library(ggwordcloud)
-library(figpatch)
 library(RColorBrewer)
@@
 for (i in 1:nrow(DF$lm_coefficients)){
-  temp <- ci.R2(R2 = DF$lm_coefficients$rsquared[i], 1, sample_size)
+  temp <- MOTE::ci.R2(R2 = DF$lm_coefficients$rsquared[i], 1, sample_size)
   DF$lm_coefficients$r2_low[i] <- temp$Lower.Conf.Limit.R2

### 2025-08-11 manuscript_definition.tex
updating manuscript
updating disclosures

@@
 \abstract{%
-This paper examined the nature of publications in Big Team Science (BTS): large-scale collaborations between multiple researchers at multiple institutions.
-These projects can improve research by initiating collaborations that span across the globe, age groups, education levels, and subfields of research.
-As the number of BTS publications increase, it is useful to explore who is currently involved in BTS projects to determine diversity in both research subject and researcher representation.
-We examined the diversity of BTS publications and authors across more than half a million articles to investigate where and what is currently published, and author characteristics including differences in career length, publication metrics, affiliation, and affiliation geopolitical regions.
-Interestingly, BTS publications are increasingly dominated by early career researchers from WEIRD geopolitical regions with Health and Physical Science accounting for the majority of BTS articles.
-However, the increase in preprints, BTS articles, and non-WEIRD authors across time demonstrate the efforts of the science community to diversify its researchers.
-
-Significance statement: This study is the first large-scale, data-driven analysis of authorship in Big Team Science (BTS), defined here as collaborations with 11 or more authors across six or more institutions.
-Drawing on millions of published works across four scientific domains, we show that BTS has grown rapidly in recent years and increasingly includes early-career researchers and contributors from a broader range of geopolitical regions.
-However, inclusion in BTS is not equally distributed.
-While author lists are becoming more globally diverse overall, leadership roles---particularly first and corresponding authorships, remain disproportionately concentrated in high-income countries, especially in Europe and North America.
-These findings highlight both the promise and limitations of BTS as a vehicle for global, inclusive science, underscoring the need for structural reforms to ensure equity in recognition and participation.
+This study presents the first large-scale, data-driven analysis of authorship in Big Team Science (BTS) drawing on over half a million articles across four scientific domains.
+Using the top decile of the data, we defined BTS as collaborations with 11+ authors across six or more institutions.
+We compared BTS with traditional team science to investigate changes in publication rates, authorship characteristics, and global representation.
+Publication rates for traditional team science and BTS have both risen over time, but the growth trajectory varies depending on the subject area.
+We found that early-career researchers are increasingly represented in both BTS and smaller teams, suggesting greater accessibility over time.
+Leadership roles remain concentrated in high-income, WEIRD regions for smaller teams.
+This work contributes a replicable, empirical definition of BTS and highlights the need for more equitable recognition and inclusion in large-scale scientific collaboration.
 
@@
 
-Computational reproducibility: All materials and code can be found on our OSF page: \url{https://osf.io/cgx6u/} or corresponding GitHub archive: \url{https://github.com/doomlab/big_team_who}.
-Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review.
-
-Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (\url{https://osf.io/f2dtr}) but then was updated with access to the Scopus database for a broader picture of BTS projects (\url{https://osf.io/fheun}).
-After peer review, the preregisteration was updated to address the unclear definition of big team science to focus on a data-driven definition to explore the research questions.
-
-Materials, Data, Analysis Scripts: All materials and code can be found on our OSF page: \url{https://osf.io/cgx6u/} or corresponding GitHub archive: \url{https://github.com/doomlab/big_team_who}.
+Computational reproducibility: A reproducible version of this manuscript can be found at: \url{https://doi.org/10.24433/CO.2018846.v1}, which is linked to GitHub (\url{https://github.com/doomlab/big_team_who}) and archived at Zenodo (\url{https://doi.org/10.5281/zenodo.15936025}).
+Elsevier has authorized use of the Scopus database to execute and validate the code for retrieving and summarizing article records.
+Although we cannot distribute Scopus data directly, we provide all code, processing steps, and derived outputs necessary to reproduce the analyses presented in this manuscript.
+
+Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (\url{https://doi.org/10.17605/OSF.IO/F2DTR}) but then was updated with access to the Scopus database for a broader picture of BTS projects (\url{https://doi.org/10.17605/OSF.IO/FHEUN}).
+After peer review, the pre-registration was updated to address the unclear definition of big team science to focus on a data-driven definition to explore the research questions.
+
+Materials: All study materials are publicly available (\url{https://doi.org/10.5281/zenodo.15936025}).
+
+Data: All data from Scopus outputs are publicly available (\url{https://doi.org/10.5281/zenodo.15936025}).
+
+Analysis scripts: All analysis scripts are publicly available (\url{https://doi.org/10.5281/zenodo.15936025}).
 }
@@
 
-\section{Supplement}\label{supplement}
+\appendix
+
+\section{Supplemental Material}\label{supplemental-material}
 
